### 2020-01-21 Notes/Fourier_Series_v0.tex
20 January 2020
- Progress on Fourier Series Paper

% ================
% Landon Buell
% Kevin Short
% PHYS 799.37
% 17 January 2020
% ================

% ================================

\documentclass[12pt,letterpaper]{article}

\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage[style=numeric]{biblatex}

% ================================

\begin{document}

% ================================================================

\title{An Introduction to Fourier Series and Fourier Transformations}
\author{Landon Buell}
\date{17 January 2020}
\maketitle

% ================================================================

\section{Introduction}

\paragraph*{}This paper is designed to serve as an an introduction to the concepts underlying Fourier Analysis. In this paper, we will introduce Fourier's theorem, understand it's motivation and show how it works analytically. Afterwards, I will provide an in depth explanation of the formulation, use, and properties of Numerical Fourier Series.

% ================================================================

\section{Fourier's Theorem}

\paragraph*{}Jean Baptiste Fourier spent much of his time studying partial differential equations. In solving equations with methods of separation, and then imposing boundary conditions, the function could only be fully solve by including an infinite linear combination of sine or cosine functions \textit{(Haberman,86)}. In some cases, only sine or cosine functions were used, but in other cases, combinations of sines and cosines were used. 
\paragraph*{}Fourier took this idea and expanded to cover periodic functions in general. For this work, we will define a period function with time, $f(t)$, to be a function that has the property:
\begin{equation}
\label{period def}
f(t) = f(t + nT)
\end{equation} 
\textit{(Tolstov,1)}Where $n$ is an integer value and $T$ is some constant value that it takes for the function to complete one cycle, called a \textit{period}.
Fourier's theorem states that an periodic function (of time, in this case), $f(t)$, with period $T$, over the range $L$ can be expressed as an infinite series of orthogonal trigonometric functions \textit{(Taylor,194)}. This is commonly written as:
\begin{equation}
\label{Fourier Theorem Def}
f(t) = a_0 + \sum_{n=1}^{\infty} a_n \cos\Big(\frac{n\pi t}{L}\Big) + b_n \sin\Big(\frac{n\pi t}{L}\Big)
\end{equation} 
\paragraph*{}Here, the index variable $n$ is taken to be only positive integer values. By filling in or solving for the appropriate values of $a_n$ and $b_n$, one can approximate any periodic function by including enough terms in the series. This of course raises the issue of how to find the Fourier coefficients.

% ================================

\subsection{Finding $a_0$}
\paragraph*{}To find the $a_0$ coefficient, also called the \textit{zero-th Fourier Coefficient}, we begin with the series definition, as given in equation (\ref{Fourier Theorem Def}). Both sides of this whole function can be integrated with respect to time, from the bounds $0$ to $L$.
\begin{equation}
\label{step1}
\int_0^L f(t) dt = \int_0^L a_0 dt + 
\int_0^L \Bigg[ \sum_{n=1}^{\infty} a_n \cos\Big(\frac{n\pi t}{L}\Big) + 
b_n \sin\Big(\frac{n\pi t}{L}\Big) \Bigg] dt
\end{equation} 
\paragraph*{}Because of the linearity of the integral operator, the operation is effectively 'distributed' to every term in the infinite series. Furthermore, by dividing the argument of each trig function by $L$, we have forced each term by itself to fit exactly an integer amount of periods $nT$ into this region from $0$ to $L$. Sine and cosine functions also have a property where when integrated over an integer multiple of a full period, $nT$, the integral becomes identically $0$.
\begin{equation}
\int_0^{nT}\cos\Big(\frac{n\pi t}{L}\Big) dt = 
\int_0^{nT}\sin\Big(\frac{n\pi t}{L}\Big) = 0 
\end{equation}
\paragraph*{}Thus, the entire right-most integral in equation (\ref{step1}) evalute to $0$. Only the two left most integrals remain:
\begin{equation}
\int_0^L f(t) dt = a_0 \int_0^L dt 
\end{equation}
This equation can be evaluated, and then algebraically rearranged to solve for $a_0$:
\begin{equation}
\label{a_0}
a_0 = \frac{1}{L}\int_0^L f(t) dt
\end{equation}
\paragraph*{}Notice that (\ref{a_0}) is just the average of the function $f(t)$ over the time span $L$. Thus, every other term in the infinite sum of functions oscillates about that scalar value.

% ================================

\subsection{Finding $a_n$}
\paragraph*{}Finding the $n$-th cosine coefficient follows from a similar manner. We begin with equation (\ref{Fourier Theorem Def}). Before we integrate the full series again, we multiple the entire equation through by a $\cos(\frac{m\pi t}{L})$ term, where $m$ is an arbitrary integer value. Thus when integrated over the same bounds again, the new series becomes:
\begin{multline}
\label{step2}
\int_0^L f(t)\cos\Big(\frac{m\pi t}{L}\Big) dt = 
\int_0^L a_0\cos\Big(\frac{m\pi t}{L}\Big) dt +  \\
\int_0^L \Bigg[ \sum_{n=1}^{\infty} 
a_n \cos\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) + 
b_n \sin\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) \Bigg] dt
\end{multline}
\paragraph*{}Just line before, we turn our attention to the rightmost integral, the infinite sum. Sine and cosine functions also have the property of orthogonality, which is where their dot products (or integrals in our case) evaluate to zero if the functions have different argumnets for $n$ and $m$. Thus mathematically,
\begin{equation}
\label{othog1}
\int \cos\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) dt = \delta_{n,m}
\end{equation}
Where $\delta_{n,m}$ is the Kronecker Delta which has the property that it becomes $0$ is $m \neq n$ and $1$ if $m = n$.
\paragraph*{}So, in the entire infinite series, every single term goes to $0$ (again the integral is applied to every term in the series), except for the one where the arbitrary integer $m$ is equal to $n$. Thus the surviving term becomes:
\begin{equation}
\int \cos\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) dt =
\int \cos^2\Big(\frac{n\pi t}{L}\Big) dt
\end{equation}
Therefore, the remaining terms in the equation become:
\begin{equation}
\int_0^L f(t)\cos\Big(\frac{n\pi t}{L}\Big) dt = 
a_n \int_0^L \cos^2\Big(\frac{n\pi t}{L}\Big) dt
\end{equation}
Recall that the term with $a_0$ again evaluates to $0$ and $m$ becomes $n$ because they are equal.
\paragraph*{}The integral on the right side of the equation can be evaluated with an identity, and once again, we can solve for the $n$-th $a$ coefficient. The result is:
\begin{equation}
\label{a_n}
a_n = \frac{2}{L}\int_0^L f(t)\cos\Big(\frac{n\pi t}{L}\Big) dt
\end{equation}

% ================================

\subsection{Finding $b_n$}
\paragraph*{}Finally, to find the $n$-th sine coefficient, we use the exact same set of rules as before. We start with the series definition and multiply through every term by $\sin(\frac{m\pi t}{L})$ and then integrate from $0$ to $L$. The new series is now:
\begin{multline}
\label{step3}
\int_0^L f(t)\sin\Big(\frac{m\pi t}{L}\Big) dt = 
\int_0^L a_0\sin\Big(\frac{m\pi t}{L}\Big) dt +  \\
\int_0^L \Bigg[ \sum_{n=1}^{\infty} 
a_n \cos\Big(\frac{n\pi t}{L}\Big)\sin\Big(\frac{m\pi t}{L}\Big) + 
b_n \sin\Big(\frac{n\pi t}{L}\Big)\sin\Big(\frac{m\pi t}{L}\Big) \Bigg] dt
\end{multline}
\paragraph*{}Once again, the orthogonality of trig functions steps into play. Just line cosine, sine has the property:
\begin{equation}
\label{othog1}
\int \sin\Big(\frac{n\pi t}{L}\Big)\sin\Big(\frac{m\pi t}{L}\Big) dt = \delta_{n,m}
\end{equation}
And just as before, this forces every term in the entire infinite series to evalue to $0$, except for the sole case where $m = n$. Thus the surviving terms in the series becomes:
\begin{equation}
\int_0^L f(t)\sin\Big(\frac{n\pi t}{L}\Big) dt = 
a_n \int_0^L \sin^2\Big(\frac{n\pi t}{L}\Big) dt
\end{equation}
\paragraph*{}Which can the right integral can again be evaluated and the coefficient $b_n$ can be solved for:
\begin{equation}
\label{b_n}
b_n = \frac{2}{L}\int_0^L f(t) \sin\Big(\frac{n\pi t}{L}\Big) dt
\end{equation}

% ================================

\subsection{Results}
\paragraph*{}Recall again that the Fourier Series expansion of a periodic function $f(t)$ with period $T$, over region $L$ is given by equation (\ref{Fourier Theorem Def})
\begin{equation}
f(t) = a_0 + \sum_{n=1}^{\infty} a_n \cos\Big(\frac{n\pi t}{L}\Big) + b_n \sin\Big(\frac{n\pi t}{L}\Big)
\end{equation} 
Where the values of $a_0$, $a_n$ and $b_n$ are given by (\ref{a_0}), (\ref{a_n}), and (\ref{b_n}) respectively:
\begin{equation}
a_0 = \frac{1}{L}\int_0^L f(t) dt
\end{equation}
\begin{equation}
a_n = \frac{2}{L}\int_0^L f(t)\cos\Big(\frac{n\pi t}{L}\Big) dt
\end{equation}
\begin{equation}
b_n = \frac{2}{L}\int_0^L f(t)\sin\Big(\frac{n\pi t}{L}\Big) dt
\end{equation}
\paragraph*{}Also note, that regardless of the exact bounds of the integral, as long as the difference between the bounds is $L$, there relations hold. For example, $-L/2$ to $+L/2$ is a value bound for this function. Additionally, if the bounds change to some arbitrary time, $\tau_0$ to $\tau_1$, then the constant $L$ in each coefficient gets replaced with $(\tau_1 - \tau_0)$.

% ================================================================

\section{Complex Fourier Series}
\paragraph*{}The concept of Fourier Series is very useful, but often difficult in practice. In many cases the integrals cannot be evaluated exactly, especially for more complicated functions of time. Even when done with a computer, only a finite amount of coefficients can be computed, and it comes with gret computational costs. For example, to compute the first $N$ terms in the series, $2N + 1$ definite integrals mist be numerically evaluated.
\paragraph*{}In addition to Fourier series expansions, the \textit{Fourier Transform} is a more common tool to use. To build the Fourier transform, we are going to express the original series expansion definition as a complex exponential, rather than a sum of trigonometric functions. Recall Euler's formula which states that for some angle $\phi$, trig functions are related to a complex exponential such that:
\begin{equation}
\label{euler}
\cos(\phi) + i\sin(\phi) = e^{i\phi}
\end{equation}
Which allows for the relations:
\begin{equation}
\cos(\phi) = \frac{e^{i\phi}+e^{-i\phi}}{2}
\end{equation}
and:
\begin{equation}
\sin(\phi) = \frac{e^{i\phi}-e^{-i\phi}}{2i}
\end{equation}
\paragraph*{}Thus, we can rewrite our original expansion with these complex exponentials such that:
\begin{equation}
f(t) = a_0 + \frac{1}{2} \sum_{n=1}^{\infty} (a_n - ib_n)e^{i\pi\frac{n}{L}t} +
\frac{1}{2} \sum_{n=1}^{\infty} (a_n + ib_n)e^{-i\pi\frac{n}{L}t}
\end{equation}
Now the coefficients $a_n$ and $b_n$ are combined to form a complex number, 
$(a_n + ib_n)/2$ often shortened to $c_n$. We also want to include only the exponential sum that includes the $e^{-i\pi\frac{n}{L}t}$ term. To do this, we index the first sum to go from $n = -1$ to $n = -\infty$.
This now allows us to express this sum in a more condensed form:
\begin{equation}
\label{complex series def}
f(t) = \sum_{n=-\infty}^{+\infty} c_n e^{i\pi\frac{n}{L}t}
\end{equation}
This is known as the complex Fourier Series Definition.

% ================================================================

% ================================================================

\end{document}

### 2020-01-22 Notes/Fourier_Series_v0.tex
21 January 2020
- Progress on Fourier Series Paper

@@
 \usepackage{multicol}
-\usepackage[style=numeric]{biblatex}
 
@@
 \paragraph*{}Jean Baptiste Fourier spent much of his time studying partial differential equations.
-In solving equations with methods of separation, and then imposing boundary conditions, the function could only be fully solve by including an infinite linear combination of sine or cosine functions \textit{(Haberman,86)}.
+In solving equations with methods of separation, and then imposing boundary conditions, the function could only be fully solved by including an infinite linear combination of sine or cosine functions \cite{Haberman}.
 In some cases, only sine or cosine functions were used, but in other cases, combinations of sines and cosines were used.
@@
 \end{equation} 
-\textit{(Tolstov,1)}Where $n$ is an integer value and $T$ is some constant value that it takes for the function to complete one cycle, called a \textit{period}.
-Fourier's theorem states that an periodic function (of time, in this case), $f(t)$, with period $T$, over the range $L$ can be expressed as an infinite series of orthogonal trigonometric functions \textit{(Taylor,194)}.
+Where $n$ is an integer value and $T$ is some constant value that it takes for the function to complete one cycle, called a \textit{period} \cite{Tolstov}.
+Fourier's theorem states that any periodic function (of time, in this case), $f(t)$, with period $T$, over the range $L$, (where $L = nT$) can be expressed as an infinite series of orthogonal trigonometric functions \cite{Taylor}.
 This is commonly written as:
@@
 \paragraph*{}Just line before, we turn our attention to the rightmost integral, the infinite sum.
-Sine and cosine functions also have the property of orthogonality, which is where their dot products (or integrals in our case) evaluate to zero if the functions have different argumnets for $n$ and $m$.
+Sine and cosine functions also have the property of orthogonality, which is where their dot products (or integrals in our case) evaluate to zero if the functions have different arguments for $n$ and $m$.
 Thus mathematically,
 \begin{equation}
-\label{othog1}
+\label{orthog1}
 \int \cos\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) dt = \delta_{n,m}
@@
 \begin{equation}
-\label{othog1}
+\label{orthog2}
 \int \sin\Big(\frac{n\pi t}{L}\Big)\sin\Big(\frac{m\pi t}{L}\Big) dt = \delta_{n,m}
@@
 \int_0^L f(t)\sin\Big(\frac{n\pi t}{L}\Big) dt = 
-a_n \int_0^L \sin^2\Big(\frac{n\pi t}{L}\Big) dt
+b_n \int_0^L \sin^2\Big(\frac{n\pi t}{L}\Big) dt
 \end{equation}
-\paragraph*{}Which can the right integral can again be evaluated and the coefficient $b_n$ can be solved for:
+Which then the right integral can again be evaluated and the coefficient $b_n$ can be solved for:
 \begin{equation}
@@
 Additionally, if the bounds change to some arbitrary time, $\tau_0$ to $\tau_1$, then the constant $L$ in each coefficient gets replaced with $(\tau_1 - \tau_0)$.
+\paragraph*{}All we have done with this series expansion of $f(t)$ is use rules of orthogonality to produce coefficients.
+All these coefficients do is control the amplitude of each respective integer angular frequency.
+In some cases, the values of $a_n$ or $b_n$ might be zero, in some cases it may be very strong compared to it's neighboring frequency.
 
@@
 \section{Complex Fourier Series}
-\paragraph*{}The concept of Fourier Series is very useful, but often difficult in practice.
-In many cases the integrals cannot be evaluated exactly, especially for more complicated functions of time.
-Even when done with a computer, only a finite amount of coefficients can be computed, and it comes with gret computational costs.
-For example, to compute the first $N$ terms in the series, $2N + 1$ definite integrals mist be numerically evaluated.
-\paragraph*{}In addition to Fourier series expansions, the \textit{Fourier Transform} is a more common tool to use.
-To build the Fourier transform, we are going to express the original series expansion definition as a complex exponential, rather than a sum of trigonometric functions.
+\paragraph*{}In addition to use sine and cosine functions to expand $f(t)$, we can also use another mathematical too - complex exponential functions.
 Recall Euler's formula which states that for some angle $\phi$, trig functions are related to a complex exponential such that:
@@
 \end{equation}
-This is known as the complex Fourier Series Definition.
+This is known as the complex Fourier Series Definition \cite{Haberman}.
+Since we have defined $c_n$ to be equivalent to: $(a_n + ib_n)/2$, and we know how to find both $a_n$ and $b_n$, we can say that each coefficient, $c_n$ is given:
+\begin{equation}
+c_n = \frac{1}{2}(a_n + ib_n) = \frac{1}{2}\Bigg(
+\frac{2}{L}\int_0^L f(t)\cos\Big(\frac{n\pi t}{L}\Big) dt +
+\frac{2i}{L}\int_0^L f(t)\sin\Big(\frac{n\pi t}{L}\Big) dt \Bigg)
+\end{equation}
+Which can be conveniently simplified to:
+\begin{equation}
+\label{c_n}
+c_n = \frac{1}{L}\int_0^L f(t) e^{i\pi\frac{n}{L}t} dt
+\end{equation}
+
+% ================================================================
+
+\section{The Fourier Transform}
+\paragraph*{}The concept of Fourier Series is very useful, but often difficult in practice.
+In many cases the integrals cannot be evaluated exactly, especially for more complicated functions of time or space.
+Even when done with a computer, only a finite amount of coefficients can be computed, and it comes with great computational costs.
+For example, to compute the first $N$ terms in the series, $2N + 1$ definite integrals must be numerically evaluated.
+\paragraph*{}In addition to Fourier series expansions, the \textit{Fourier Transform} is a very common tool to use.
+To build the Fourier transform, we are going to begin with the complex  definition of the Fourier Series expansion from equation (\ref{complex series def}), where the $c_n$ coefficients are given by equation (\ref{c_n}).
+\paragraph*{}Suppose we have a signal function of time, $g(t)$ and we want to transform it into it's frequency domain.
+The resulting function will be of frequency, $g(f)$, not time.
+Suppose we want to transform with over the domain
+$-L < t < +L$. Thus our Fourier series representation is given by:
+\begin{equation}
+g(t) = \sum_{n=-\infty}^{\infty} c_n e^{i\pi\frac{n}{L}t}
+\end{equation}
+with the $c_n$ coefficients given by:
+\begin{equation}
+c_n = \frac{1}{2L}\int_{-L}^{+L} g(t) e^{i\pi\frac{n}{L}t} dt
+\end{equation}
+\paragraph*{}Now we can define a discrete index variable, $\xi$ to be:
+\begin{equation}
+\xi = \frac{n\pi}{L} 
+\end{equation}
+\begin{flushright}
+Where $n = 0, \pm 1, \pm 2, \pm3, ...$
+\end{flushright}
+And also the difference between adjacent values of $\xi$ is given by:
+\begin{equation}
+\Delta \xi = \xi_{n+1} - \xi_{n} = \frac{\pi}{L}
+\end{equation}
+The partial Fourier transform of $g(t)$ on the interval $-L < t < +L$ is then given by:
+\begin{equation}
+F_L(\xi) = \frac{1}{2L} \int_{-L}^{+L} g(t) e^{-i\xi t} dt =
+\frac{1}{2L} \int_{-L}^{+L} g(t) e^{-i\frac{\pi}{L}t} dt
+\end{equation}
+\paragraph*{}
 
@@
 
+\begin{thebibliography}{9}
+\bibliographystyle{apalike}
+
+\bibitem{Haberman}
+Haberman, Richard. \textit{Applied Partial Differential Equations: with Fourier Series and Boundary Value Problems}. 5th ed., Pearson Education, 2014.
+
+\bibitem{Pinsky}
+Pinsky, Mark A. \textit{Partial Differential Equations and Boundary-Value Problems with Applications}. 3rd ed., American Mathematical Society, 2011.
+
+\bibitem{Taylor}
+Taylor, John R. \textit{Classical Mechanics}. Univ. Science Books, 2005.
+
+\bibitem{Tolstov}
+Tolstov, Georgy Pavlovich. \textit{Fourier Series}. Translated by Richard Allan. Silverman, London; Printed in U.S.A., 1962.
+
+\end{thebibliography}
+
+% ================================================================
+
 \end{document}

### 2020-01-23 Notes/Fourier_Series_v0.tex
23 January 2020
- Progress on Fourier Series v0 Paper

@@
 \paragraph*{}In addition to Fourier series expansions, the \textit{Fourier Transform} is a very common tool to use.
-To build the Fourier transform, we are going to begin with the complex  definition of the Fourier Series expansion from equation (\ref{complex series def}), where the $c_n$ coefficients are given by equation (\ref{c_n}).
-\paragraph*{}Suppose we have a signal function of time, $g(t)$ and we want to transform it into it's frequency domain.
-The resulting function will be of frequency, $g(f)$, not time.
-Suppose we want to transform with over the domain
-$-L < t < +L$. Thus our Fourier series representation is given by:
+To build the Fourier transform, let us consider just the complex exponential function in the form:
 \begin{equation}
-g(t) = \sum_{n=-\infty}^{\infty} c_n e^{i\pi\frac{n}{L}t}
+\label{comp exp}
+F(t) = e^{it}
 \end{equation}
-with the $c_n$ coefficients given by:
+Physically, the variable $t$ gives the arclength distance traverse by the tip of a rotating vector within a unit circle.
+So if we have $t=2$, then the tip of this rotating vector has traversed $2$ radians of arc around the circle.
+If we wanted to describe a vector that then rotates around this unit circle once per second, we would then multiply the exponent in equation (\ref{comp exp}) by the constant $2\pi$.
+Thus at $t=0$ and $t=1$, the expression evaluates to the same complex value: $(1 + 0i)$.
+\paragraph*{}We can also extend this idea to allow the vector to rotate with an arbitrary frequency, $\nu$.
+It is also convention to use a negative value in the exponent.
+Thus the complex exponential becomes:
 \begin{equation}
-c_n = \frac{1}{2L}\int_{-L}^{+L} g(t) e^{i\pi\frac{n}{L}t} dt
+\label{comp exp 2}
+F(t) = e^{-2\pi i\nu t}
 \end{equation}
-\paragraph*{}Now we can define a discrete index variable, $\xi$ to be:
+Now, the value of $t$ has to increase to $\frac{1}{\nu}$ for the full exponent to take the form $2\pi i$ again (one full revolution).
+This, the rotating vector return to the point $(1 + 0i)$ at integer multiples of $1/\nu$.
+\paragraph*{}Now suppose we have some perfectly continuous, periodic function of time, given by $f(t)$, with period $T$.
+We want to use build the Fourier transform to move ths function from a time domain, into a frequency domain, $f(\nu)$.
+We can actually multiply this $f(t)$ function by equation (\ref{comp exp 2}) and arrive at the equation:
 \begin{equation}
-\xi = \frac{n\pi}{L} 
+f(t) e^{-2\pi i\nu t}
 \end{equation}
-\begin{flushright}
-Where $n = 0, \pm 1, \pm 2, \pm3, ...$
-\end{flushright}
-And also the difference between adjacent values of $\xi$ is given by:
+\paragraph*{}Now instead of our complex exponential function rotating about a simple unit circle of radius $1$, the rotating vector's magnitude is now scaled by this function $f(t)$.
+So not only is the vector rotating around the origin with some arbitrary frequency , $\nu$, it's length is also begin scaled with respect to \textit{time}, according to $f(t)$.
+Conceptually, this is like taking the function $f(t)$ and winding it up in a circular fashion about the origin.
+The tip of this vector still lies within complex space.
+\paragraph*{}We can now integrate this function with respect to time, from 
+$\tau_1$ to $\tau_2$m and scale it by the inverse of that interval.
 \begin{equation}
-\Delta \xi = \xi_{n+1} - \xi_{n} = \frac{\pi}{L}
+\frac{1}{\tau_2 - \tau_1}\int_{\tau_1}^{\tau_2} f(t) e^{-2\pi i\nu t} dt
 \end{equation}
-The partial Fourier transform of $g(t)$ on the interval $-L < t < +L$ is then given by:
+This whole function is very analogous to finding the center of mass of this wound up graph \cite{Sanderson}.
+This "center - of - mass" idea will result in a vector, once again in complex space.
+Finally, we can just remove this $\frac{1}{\tau_2 - \tau_1}$ coefficient And the result is the canonical Fourier Transform.
+So our new function of linear frequency becomes:
 \begin{equation}
-F_L(\xi) = \frac{1}{2L} \int_{-L}^{+L} g(t) e^{-i\xi t} dt =
-\frac{1}{2L} \int_{-L}^{+L} g(t) e^{-i\frac{\pi}{L}t} dt
+\label{Fourier Transform}
+f(\nu) = \int_{\tau_1}^{\tau_2} f(t) e^{-2\pi i\nu t} dt
 \end{equation}
-\paragraph*{}
+Similarly, to recover the original function of time, we can apply the \textit{inverse} Fourier Transform:
+\begin{equation}
+\label{Inv Fourier Transform}
+f(t) = \int_{\tau_1}^{\tau_2} f(\nu) e^{+2\pi i\nu t} d\nu
+\end{equation}
+\paragraph*{}These transform pairs are a bit tough to reason through, but we can rewrite equation (\ref{Fourier Transform}) use the help of Euler's identity (\ref{euler}) again:
+\begin{equation}
+\label{Fourier Transform}
+f(\nu) = 
+\int_{\tau_1}^{\tau_2} f(t) e^{-2\pi i\nu t} dt =
+\int_{\tau_1}^{\tau_2} f(t) \Big[\cos(2\pi\nu t) - i\sin(2\pi\nu t)\Big] dt
+\end{equation}
+We can distribute the $f(t)$ function to each term, and then divide it into two separate integrals:
+\begin{equation}
+f(\nu) = 
+\int_{\tau_1}^{\tau_2} f(t)\cos(2\pi\nu t)dt -
+i\int_{\tau_1}^{\tau_2} f(t)\sin(2\pi\nu t)dt
+\end{equation}
+\paragraph*{}Now, this equation tells use to scale our $f(t)$ function with either a sine or cosine containing an arbitrary frequency, $\nu$, and then integrate over the bounds.
+Each respective area represents the real and imaginary components of some number in complex space.
+The magnitude of that number is the magnitude of the Fourier transform at that particular frequency, $\nu$.
+Thus the larger the value of the integrals, the more prevalent that angular frequency is in the signal $f(t)$.
 
 % ================================================================
+
+\section{Numerical Fourier Transform}
+\paragraph*{}In reality, a well defined signal $f(t)$ already has a set of known 
+constituent frequencies.
+In most cases, signals from the real world are not defined by some perfect and smooth function.
+Furthermore, actually evaluating the integrals in the transforms completely may prove to even be impossible.
+\paragraph*{}With this comes the need to use computers to evaluate Fourier Transforms numerically.
+Furthermore, this allows for us not not have a function, $f(t)$, but rather some array full of arbitrary amplitude values.
+So we return to our transform definition, (\ref{Fourier Transform}):
+\begin{equation}
+f(\nu) = \int_{\tau_1}^{\tau_2} f(t) e^{-2\pi i\nu t} dt
+\end{equation}
+Firstly, $f(t)$ is no longer a continuous function, but an array discrete entries.
+Similarly, $f(\nu)$ will also become an array of discrete points as well.
+We then name them: $f(t) \rightarrow x$ and $f(\nu) \rightarrow y$.
+For this derivation I will be using syntax and concepts (such as libraries) from Python 3.
+\paragraph*{}Now suppose that we want our output array, $y$ to be an array containing $n$ discrete entries in it:
+\begin{equation}
+y = [y_0 , y_1 , y_2 , y_3 , ... , y _{n-2} , y_{n-1} ]
+\end{equation}
+This will determine the number of frequency values, $\nu$ that we have to test.
 
@@
 
+\bibitem{Sanderson}
+Sanderson, Grant. \textit{But What Is the Fourier Transform? A Visual Introduction}. YouTube, 26 Jan. 2018.
+
 \bibitem{Taylor}

### 2020-01-29 Notes/Fourier Series/Fourier_Series_v0.tex
28 January 2020
- Updated & organized notes on Fourier Series
- Updated read_wavs program

--- 2020-01-23 Notes/Fourier_Series_v0.tex
@@
 \begin{equation}
-\label{Fourier Transform}
 f(\nu) = 
@@
 \paragraph*{}With this comes the need to use computers to evaluate Fourier Transforms numerically.
-Furthermore, this allows for us not not have a function, $f(t)$, but rather some array full of arbitrary amplitude values.
+This allows for us not not have a function, $f(t)$, but rather some array full of arbitrary amplitude values.
 So we return to our transform definition, (\ref{Fourier Transform}):
@@
 Similarly, $f(\nu)$ will also become an array of discrete points as well.
-We then name them: $f(t) \rightarrow x$ and $f(\nu) \rightarrow y$.
+We then name them: $f(t) \rightarrow \vec{x}$ and $f(\nu) \rightarrow \vec{y}$.
 For this derivation I will be using syntax and concepts (such as libraries) from Python 3.
-\paragraph*{}Now suppose that we want our output array, $y$ to be an array containing $n$ discrete entries in it:
+\paragraph*{}Now suppose that we want our output array, $\vec{y}$ to be an array containing $n$ discrete entries in it:
 \begin{equation}
-y = [y_0 , y_1 , y_2 , y_3 , ... , y _{n-2} , y_{n-1} ]
+\vec{y} = [y_0 , y_1 , y_2 , y_3 , ... , y _{n-2} , y_{n-1} ]
 \end{equation}
-This will determine the number of frequency values, $\nu$ that we have to test.
+And suppose the input array, $\vec{x}$ has $N$ discrete components in it:
+\begin{equation}
+\vec{x} = [x_0 , x_1 , x_2 , x_3 , ... , x _{N-2} , x_{N-1} ]
+\end{equation}
+\paragraph*{}Each entry in this $\vec{y}$ array will correspond to a particular linear frequency value.
+In we use a sort of dimensional ambiguity, and normalize each frequency values such that $y_0$ represents $0$ cycles per unit time, and $y_{n-1}$ represents 1 cycle per unit time.
+After we compute the full $y$ array, we can then go back a multiply the full array by a constant to account for the particular unit.
+\paragraph*{}Now, for each index, $y_k$, we need to evaluate the full Fourier transform (\ref{Fourier Transform}) for a particular frequency, $\nu$.
+So we need to set the particular frequency value, and evaluate equation (\ref{Fourier Transform}) for that value.
+Thus, no using these discrete variables, we can write our Discrete Fourier Transform as:
+\begin{equation}
+\label{Discrete Fourier Transform}
+\vec{y} = \sum_{j=0}^{N-1} \vec{x}_j e^{-2\pi i \vec{\nu}}
+\end{equation}
+Thus each individual entry in the the $\vec{y}$ vector is given:
+\begin{equation}
+\label{kth DFT}
+\vec{y}_k = \sum_{j=0}^{N-1} \vec{x}_j e^{-2\pi ik \vec{\nu}}
+\end{equation}
+\paragraph*{}Lastly, we mist choose the elements of the linear frequency array $\vec{\nu}$ such that they are dimensionless.
+Since we want our output vector $\vec{y}$ to contain $n$ points, the array $\vec{\nu}$ must also contain $n$ points, even spaced between $0$ and $1$.
+Thus now, when we multiply $\vec{\nu}$ by the index $k$ in (\ref{kth DFT}), we have the effect of evaluating the transform for that particular, normalized frequency value.
+\paragraph*{}So if we wanted, to code this transform "from scratch" in python, we would start by creating a time axis, $t$, the number of point in our output transform, $n$, and a signal $x$ to transform, with the help of numpy:
+\begin{verbatim}
+>>> import numpy as np
+>>> n = 1024
+>>> t = np.arrange(0,5,0.01)
+>>> x = 2*np.sin(2*np.pi*4*t) + 3*np.cos(2*np.pi*3*t)
+
+\end{verbatim}
+\paragraph*{}We also need to create the frequency vector, $\vec{\nu}$, and an empty array, $y$, to hold our output:
+\begin{verbatim}
+>>> nu = np.arange(n)/n
+>>> y = np.array([])
+\end{verbatim}
+\paragraph*{}Now, we need to create a loop that indexes from the $0$-th to the $n-1$-th element in the output array.
+Each element is them given by equation (\ref{kth DFT})Note that $x$ must be truncated to have $n$ points.
+\begin{verbatim}
+>>> x1 = x[0:n]
+>>> for k in range (0,len(n),1):
+>>>     y_k = np.sum(x1 * np.exp(2*np.pi*-1j*k*nu))
+>>>     y = np.append(y,y_k)  
+\end{verbatim}
+\paragraph*{}When this loop completes, there will be an array $y$ that is filled with $n$ entries.
+Each entry is given by the discrete Fourier Transform in equation (\ref{kth DFT}).
+To dimensional the frequencies, we simply need to create the frequency spectrum axis.
+If our original $\vec{x}$ array is sampled at some frequency, $f_0$, then the highest and lowest frequency that we can sample is $\pm\frac{f_0}{2}$.
+This means that the sampled frequencies are from $-\frac{f_0}{2}$ to $+\frac{f_0}{2}$ evenly spaced such that there are $n$ points.
 

### 2020-01-29 read_wavs/read_wavs_func.py

@@ -25,14 +25,6 @@ class wav_file ():
         self.filename = file                    # filename
         self.instrument = file.split('.')[0]    # Instrument name
         self.rate = 44100                       # sample rate
-    
-    def pitch_to_freq (self,pitchdict):
-        """ Assign numerical frequency based on pitch label """
-        note = self.filename.split('.')[-3]     # isolate pitch string
-        freq = pitchdict[str(note)]             # find frequency value
-        setattr(self,'note',note)               # set attribute
-        setattr(self,'freq',freq)               # set attribute
-        return note,freq                        # return note name & frequency
 
     def read_raw_wav(self):
         """ Read Raw data from directory file """      
@@ -40,70 +32,26 @@ class wav_file ():
         data = np.transpose(data)               # tranpose
         data = data/np.max(np.abs(data))        # normalize
         setattr(self,'data',data)               # set attrb to self
-        return data,rate                        # return values
+        return data                             # return waveform
 
-    def timespace (self,rate,npts):
-        """ Create timespace axis """
-        time = np.arange(0,npts)    # create axis
-        #time = time/rate            # divide by sample rate
-        setattr(self,'time',time)   # set attribute
-        return time                 # return the array
-
-    def attack (self,value):
-        """ Find ATTACK section of waveform """
-        pass
-
-    def decay (self,attr,value):
-        """ Find DECAY section of waveform """
-        pass
-
-    def sustain (self,attr,value):
-        """ Find SUSTAIN section of waveform """
-        pass
-
-    def release (self,attr,value):
-        """ Find RELEASE section of waveform """
-        pass
-
-    def freqspace(self,npts=441000,rate=44100):
-        """ Create frequency space axis """          
-        fspace = fftpack.fftfreq(n=npts,d=rate)     # create f-axis
-        pts = np.where((fspace>=0))                 # pos freqs
-        fspace = fspace[pts]                        # index array
-        setattr(self,'fspace',fspace)               # self self attrb
-        return fspace                               # return f-axis
-
-    def FFT (self,attr,npts=441000):
-        """ Discrete Fast Fourier Transform """
-        data = self.__getattribute__(attr)      # isolate attribute
-        fftdata = fftpack.fft(x=data,n=npts)    # compute fft
-        power = np.abs(fftdata)**2              # power spectrum
-        power = power/np.max(power)             # normalize amplitude
-        return power                            # return power & freq space
-
-    def freq_band (self,label,power,pts):
[…]

### 2020-01-29 read_wavs/timeseries.py

@@ -1,0 +1,35 @@
+"""
+Landon Buell
+Wav file to Frequency Bands
+PHYS 799
+28 December 2019
+"""
+
+        #### IMPORTS ####
+
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import os
+import time
+import read_wavs_func as readwavs
+
+if __name__ == '__main__':
+
+    int_dir = 'C:/Users/Landon/Documents/GitHub/Buell-Senior-Thesis/read_wavs'
+    wav_dir = 'C:/Users/Landon/Documents/wav_audio'
+    out_dir = 'C:/Users/Landon/Documents/wav_data/time_series'
+
+    readwavs.make_paths([out_dir])          # create the output tpath if needed
+    wavfiles = readwavs.read_directory()    # create all class instances
+    N = 2**10                               # number of features
+    class_num = 0                           # class indentifier
+    targets = np.array([])                  # array to hold target labels
+
+    for file in wavfiles:                       # for each class instance
+        os.chdir(file.dirpath)                  # move to the directory path
+        waveform = file.read_raw_wav()          # extract waveform
+        samples,M = file.split_timeseries(N)    # split into M samples
+
+
+

### 2020-01-29 read_wavs/wavs_to_freqbands.py

@@ -1,9 +1,11 @@
 """
 Landon Buell
 Wav file to Frequency Bands
-Main
+PHYS 799
 28 December 2019
 """
+
+        #### IMPORTS ####
 
 import numpy as np
 import matplotlib.pyplot as plt
@@ -11,7 +13,6 @@ import pandas as pd
 import os
 import time
 import read_wavs_func as readwavs
-
 
 if __name__ == '__main__':
 
@@ -22,7 +23,6 @@ if __name__ == '__main__':
     csv_dir = 'C:/Users/Landon/Documents/wav_data/Frequency_Bands'
     
     readwavs.make_paths([csv_dir])
-    #notefreq = readwavs.notefreq_dict()             # note to freq dictionary
     rate = 44100
 
             #### BUILDING FREQUENCY BANDS ####

### 2020-05-05 Notes/Fourier Series/Fourier_Series_v0.tex
5 May 2020
- Began Paper on Fourier Analysis
- Add citations

--- 2020-01-22 Notes/Fourier_Series_v0.tex
@@
 % Kevin Short
-% PHYS 799.37
-% 17 January 2020
+% PHYS 799 
+% 5 May 2020
 % ================
-
-% ================================
 
@@
 
-\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{multicol}
+\usepackage[left=2.5cm,right=2.5cm,top=2.5cm]{geometry}
+\usepackage{float}
 \usepackage{graphicx}
-\usepackage{float}
-\usepackage{amsmath}
-\usepackage{multicol}
+\usepackage{fancyhdr}
 
-% ================================
+% ================================================================
+
+\pagestyle{fancy}
+\fancyhf{}
+\lhead{An Introduction to Fourier Analysis}
+\rhead{Landon Buell}
+\cfoot{\thepage}
+
+% ================================================================
 
@@
 
-% ================================================================
-
-\title{An Introduction to Fourier Series and Fourier Transformations}
+\title{An Introduction to Fourier Analysis}
 \author{Landon Buell}
-\date{17 January 2020}
+\date{5 May 2020}
 \maketitle
@@
 
-\section{Introduction}
-
-\paragraph*{}This paper is designed to serve as an an introduction to the concepts underlying Fourier Analysis.
-In this paper, we will introduce Fourier's theorem, understand it's motivation and show how it works analytically.
-Afterwards, I will provide an in depth explanation of the formulation, use, and properties of Numerical Fourier Series.
+\section*{Introduction}
+\paragraph*{}Just after the turn of the 18-th century French Mathematician Jean Baptiste Fourier had spent a great deal of his time in the subjects of various partial differential equations and boundary value problems.
+In particular, he found that analytical solutions to \textit{The Heat Transfer Equation} involved an infinite series of orthogonal trigonometric functions \cite{Pinsky,Olver}.
+This lead Fourier to extent his findings and propose that \textit{any} function that was periodic with space or time could similarly be expressed as this series of sine and cosine functions.
+For this work, we will take explore time-domain related derivation, behavior, and analysis of the properties of and related to Fourier Series, Analysis and Transforms, both analytically and computationally.
 
@@
 
-\section{Fourier's Theorem}
-
-\paragraph*{}Jean Baptiste Fourier spent much of his time studying partial differential equations.
-In solving equations with methods of separation, and then imposing boundary conditions, the function could only be fully solved by including an infinite linear combination of sine or cosine functions \cite{Haberman}.
-In some cases, only sine or cosine functions were used, but in other cases, combinations of sines and cosines were used.
-\paragraph*{}Fourier took this idea and expanded to cover periodic functions in general. For this work, we will define a period function with time, $f(t)$, to be a function that has the property:
+\section*{Fourier Series Definition}
+\paragraph{}Since the series revolves around the idea of converging around approximations of period functions, let us define a continuous function, 
+$f$, that is periodic in time-space, to have the property \cite{Tolstov}:
 \begin{equation}
-\label{period def}
+\label{periodic definition}
 f(t) = f(t + nT)
 \end{equation}
-Where $n$ is an integer value and $T$ is some constant value that it takes for the function to complete one cycle, called a \textit{period} \cite{Tolstov}.
-Fourier's theorem states that any periodic function (of time, in this case), $f(t)$, with period $T$, over the range $L$, (where $L = nT$) can be expressed as an infinite series of orthogonal trigonometric functions \cite{Taylor}.
-This is commonly written as:
+Where $T$ is the \textit{period} of the function with units of time ($T \neq 0$), and $n$ is an integer to indicate that the function repeats for any integer $n$.
+More intuitively, this is function when evaluated at time $t$ takes on some value, and then will return to that same value when progressing forward or backward in time, by some integer multiple of the period.
+\paragraph*{}With this distinction made, we can examine Fourier's claim that we can approximate this function, over some length of time, $L$, as a sum of sine and cosine functions \cite{Pinsky,Tolstov}.
+Mathematically:
 \begin{equation}
-\label{Fourier Theorem Def}
-f(t) = a_0 + \sum_{n=1}^{\infty} a_n \cos\Big(\frac{n\pi t}{L}\Big) + b_n \sin\Big(\frac{n\pi t}{L}\Big)
+\label{Series Def}
+f(t) = a_0 + \sum_{n=1}^{+\infty} \Bigg[ a_n \cos\Big(\frac{n\pi t}{L}\Big) + b_n \sin\Big(\frac{n\pi t}{L}\Big) \Bigg]
 \end{equation}
-\paragraph*{}Here, the index variable $n$ is taken to be only positive integer values.
-By filling in or solving for the appropriate values of $a_n$ and $b_n$, one can approximate any periodic function by including enough terms in the series.
-This of course raises the issue of how to find the Fourier coefficients.
+Were $a_0$ , $a_n$ and $b_n$ are coefficients $L$ is the bound of time which we are concerned with and $n$ is an integer that indicates that we want our analysis to include integer multiples of unit frequencies.
+\paragraph*{}This serves as a sort of starting point or baseline for most of Fourier Analysis.
+If we can accept, or at least humor this, idea, we can use this foundation to break some sort of function, $f(t)$ down into a collection of functions of a single frequency.
+To do this more practically, we need to derive an expression for each of the infinitely many $a_n$ and $b_n$ coefficients.
+In order to construct expression for them, we require three very important properties of trigonometric functions:
 
-% ================================
-
-\subsection{Finding $a_0$}
-\paragraph*{}To find the $a_0$ coefficient, also called the \textit{zero-th Fourier Coefficient}, we begin with the series definition, as given in equation (\ref{Fourier Theorem Def}).
-Both sides of this whole function can be integrated with respect to time, from the bounds $0$ to $L$.
+\begin{enumerate}
+\item[•]\textbf{Orthogonality of Cosine}
 \begin{equation}
-\label{step1}
-\int_0^L f(t) dt = \int_0^L a_0 dt + 
-\int_0^L \Bigg[ \sum_{n=1}^{\infty} a_n \cos\Big(\frac{n\pi t}{L}\Big) + 
-b_n \sin\Big(\frac{n\pi t}{L}\Big) \Bigg] dt
+\label{cos orth}
+\int_{0}^{L} \cos\Big(\frac{n\pi t}{L}\Big) \cos\Big(\frac{m\pi t}{L}\Big) dt = 
+	\left\{
+        \begin{array}{ll}
+            0 	&, n \neq m \\
+            2/L	&, n = m \neq 0 \\
+            L 	&, n = m = 0\\
+        \end{array}
+    \right.
 \end{equation}
-\paragraph*{}Because of the linearity of the integral operator, the operation is effectively 'distributed' to every term in the infinite series.
-Furthermore, by dividing the argument of each trig function by $L$, we have forced each term by itself to fit exactly an integer amount of periods $nT$ into this region from $0$ to $L$.
-Sine and cosine functions also have a property where when integrated over an integer multiple of a full period, $nT$, the integral becomes identically $0$.
+\item[•]\textbf{Orthogonality of Sine}
 \begin{equation}
-\int_0^{nT}\cos\Big(\frac{n\pi t}{L}\Big) dt = 
-\int_0^{nT}\sin\Big(\frac{n\pi t}{L}\Big) = 0 
+\label{sin orth}
+\int_{0}^{L} \sin\Big(\frac{n\pi t}{L}\Big) \sin\Big(\frac{m\pi t}{L}\Big) dt = 
+	\left\{
+        \begin{array}{ll}
+            0 	&, n \neq m \\
+            2/L	&, n = m \neq 0 \\
+            L 	&, n = m = 0\\
+        \end{array}
+    \right.
 \end{equation}
-\paragraph*{}Thus, the entire right-most integral in equation (\ref{step1}) evalute to $0$. Only the two left most integrals remain:
+\item[•]\textbf{Mutual Orthogonality}
 \begin{equation}
-\int_0^L f(t) dt = a_0 \int_0^L dt 
+\label{mutual orth}
+\int_{0}^{L} \cos\Big(\frac{n\pi t}{L}\Big) \sin\Big(\frac{m\pi t}{L}\Big) dt = 0 ,
+\hspace*{1cm} \forall m,n
 \end{equation}
-This equation can be evaluated, and then algebraically rearranged to solve for $a_0$:
-\begin{equation}
-\label{a_0}
-a_0 = \frac{1}{L}\int_0^L f(t) dt
-\end{equation}
-\paragraph*{}Notice that (\ref{a_0}) is just the average of the function $f(t)$ over the time span $L$. Thus, every other term in the infinite sum of functions oscillates about that scalar value.
-
-% ================================
-
-\subsection{Finding $a_n$}
-\paragraph*{}Finding the $n$-th cosine coefficient follows from a similar manner.
-We begin with equation (\ref{Fourier Theorem Def}).
-Before we integrate the full series again, we multiple the entire equation through by a $\cos(\frac{m\pi t}{L})$ term, where $m$ is an arbitrary integer value.
-Thus when integrated over the same bounds again, the new series becomes:
-\begin{multline}
-\label{step2}
-\int_0^L f(t)\cos\Big(\frac{m\pi t}{L}\Big) dt = 
-\int_0^L a_0\cos\Big(\frac{m\pi t}{L}\Big) dt +  \\
-\int_0^L \Bigg[ \sum_{n=1}^{\infty} 
-a_n \cos\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) + 
-b_n \sin\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) \Bigg] dt
-\end{multline}
-\paragraph*{}Just line before, we turn our attention to the rightmost integral, the infinite sum.
-Sine and cosine functions also have the property of orthogonality, which is where their dot products (or integrals in our case) evaluate to zero if the functions have different arguments for $n$ and $m$.
-Thus mathematically,
-\begin{equation}
-\label{orthog1}
-\int \cos\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) dt = \delta_{n,m}
-\end{equation}
-Where $\delta_{n,m}$ is the Kronecker Delta which has the property that it becomes $0$ is $m \neq n$ and $1$ if $m = n$.
-\paragraph*{}So, in the entire infinite series, every single term goes to $0$ (again the integral is applied to every term in the series), except for the one where the arbitrary integer $m$ is equal to $n$.
-Thus the surviving term becomes:
-\begin{equation}
-\int \cos\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) dt =
-\int \cos^2\Big(\frac{n\pi t}{L}\Big) dt
-\end{equation}
-Therefore, the remaining terms in the equation become:
-\begin{equation}
-\int_0^L f(t)\cos\Big(\frac{n\pi t}{L}\Big) dt = 
-a_n \int_0^L \cos^2\Big(\frac{n\pi t}{L}\Big) dt
-\end{equation}
-Recall that the term with $a_0$ again evaluates to $0$ and $m$ becomes $n$ because they are equal.
-\paragraph*{}The integral on the right side of the equation can be evaluated with an identity, and once again, we can solve for the $n$-th $a$ coefficient. The result is:
-\begin{equation}
-\label{a_n}
-a_n = \frac{2}{L}\int_0^L f(t)\cos\Big(\frac{n\pi t}{L}\Big) dt
-\end{equation}
-
-% ================================
-
-\subsection{Finding $b_n$}
-\paragraph*{}Finally, to find the $n$-th sine coefficient, we use the exact same set of rules as before.
-We start with the series definition and multiply through every term by $\sin(\frac{m\pi t}{L})$ and then integrate from $0$ to $L$.
-The new series is now:
-\begin{multline}
-\label{step3}
-\int_0^L f(t)\sin\Big(\frac{m\pi t}{L}\Big) dt = 
-\int_0^L a_0\sin\Big(\frac{m\pi t}{L}\Big) dt +  \\
-\int_0^L \Bigg[ \sum_{n=1}^{\infty} 
-a_n \cos\Big(\frac{n\pi t}{L}\Big)\sin\Big(\frac{m\pi t}{L}\Big) + 
-b_n \sin\Big(\frac{n\pi t}{L}\Big)\sin\Big(\frac{m\pi t}{L}\Big) \Bigg] dt
-\end{multline}
-\paragraph*{}Once again, the orthogonality of trig functions steps into play. Just line cosine, sine has the property:
-\begin{equation}
-\label{orthog2}
-\int \sin\Big(\frac{n\pi t}{L}\Big)\sin\Big(\frac{m\pi t}{L}\Big) dt = \delta_{n,m}
-\end{equation}
-And just as before, this forces every term in the entire infinite series to evalue to $0$, except for the sole case where $m = n$. Thus the surviving terms in the series becomes:
-\begin{equation}
-\int_0^L f(t)\sin\Big(\frac{n\pi t}{L}\Big) dt = 
-b_n \int_0^L \sin^2\Big(\frac{n\pi t}{L}\Big) dt
-\end{equation}
-Which then the right integral can again be evaluated and the coefficient $b_n$ can be solved for:
-\begin{equation}
-\label{b_n}
-b_n = \frac{2}{L}\int_0^L f(t) \sin\Big(\frac{n\pi t}{L}\Big) dt
-\end{equation}
-
-% ================================
-
-\subsection{Results}
-\paragraph*{}Recall again that the Fourier Series expansion of a periodic function $f(t)$ with period $T$, over region $L$ is given by equation (\ref{Fourier Theorem Def})
-\begin{equation}
-f(t) = a_0 + \sum_{n=1}^{\infty} a_n \cos\Big(\frac{n\pi t}{L}\Big) + b_n \sin\Big(\frac{n\pi t}{L}\Big)
-\end{equation} 
-Where the values of $a_0$, $a_n$ and $b_n$ are given by (\ref{a_0}), (\ref{a_n}), and (\ref{b_n}) respectively:
-\begin{equation}
-a_0 = \frac{1}{L}\int_0^L f(t) dt
-\end{equation}
-\begin{equation}
-a_n = \frac{2}{L}\int_0^L f(t)\cos\Big(\frac{n\pi t}{L}\Big) dt
-\end{equation}
-\begin{equation}
-b_n = \frac{2}{L}\int_0^L f(t)\sin\Big(\frac{n\pi t}{L}\Big) dt
-\end{equation}
-\paragraph*{}Also note, that regardless of the exact bounds of the integral, as long as the difference between the bounds is $L$, there relations hold.
-For example, $-L/2$ to $+L/2$ is a value bound for this function.
-Additionally, if the bounds change to some arbitrary time, $\tau_0$ to $\tau_1$, then the constant $L$ in each coefficient gets replaced with $(\tau_1 - \tau_0)$.
-\paragraph*{}All we have done with this series expansion of $f(t)$ is use rules of orthogonality to produce coefficients.
-All these coefficients do is control the amplitude of each respective integer angular frequency.
-In some cases, the values of $a_n$ or $b_n$ might be zero, in some cases it may be very strong compared to it's neighboring frequency.
+Note that is last property holds in $m$ or $n$ are $0$, which causes that function to oscillate with $0$ frequency, this remain constant.
+\end{enumerate}
+\paragraph*{}Using these three identities, we can show uncover the coefficients.
 
@@
 
-\section{Complex Fourier Series}
-\paragraph*{}In addition to use sine and cosine functions to expand $f(t)$, we can also use another mathematical too - complex exponential functions.
-Recall Euler's formula which states that for some angle $\phi$, trig functions are related to a complex exponential such that:
-\begin{equation}
-\label{euler}
-\cos(\phi) + i\sin(\phi) = e^{i\phi}
-\end{equation}
-Which allows for the relations:
-\begin{equation}
-\cos(\phi) = \frac{e^{i\phi}+e^{-i\phi}}{2}
-\end{equation}
-and:
-\begin{equation}
-\sin(\phi) = \frac{e^{i\phi}-e^{-i\phi}}{2i}
-\end{equation}
-\paragraph*{}Thus, we can rewrite our original expansion with these complex exponentials such that:
-\begin{equation}
-f(t) = a_0 + \frac{1}{2} \sum_{n=1}^{\infty} (a_n - ib_n)e^{i\pi\frac{n}{L}t} +
-\frac{1}{2} \sum_{n=1}^{\infty} (a_n + ib_n)e^{-i\pi\frac{n}{L}t}
-\end{equation}
-Now the coefficients $a_n$ and $b_n$ are combined to form a complex number, 
-$(a_n + ib_n)/2$ often shortened to $c_n$.
-We also want to include only the exponential sum that includes the $e^{-i\pi\frac{n}{L}t}$ term.
-To do this, we index the first sum to go from $n = -1$ to $n = -\infty$.
-This now allows us to express this sum in a more condensed form:
-\begin{equation}
-\label{complex series def}
-f(t) = \sum_{n=-\infty}^{+\infty} c_n e^{i\pi\frac{n}{L}t}
-\end{equation}
-This is known as the complex Fourier Series Definition \cite{Haberman}.
-Since we have defined $c_n$ to be equivalent to: $(a_n + ib_n)/2$, and we know how to find both $a_n$ and $b_n$, we can say that each coefficient, $c_n$ is given:
-\begin{equation}
-c_n = \frac{1}{2}(a_n + ib_n) = \frac{1}{2}\Bigg(
-\frac{2}{L}\int_0^L f(t)\cos\Big(\frac{n\pi t}{L}\Big) dt +
-\frac{2i}{L}\int_0^L f(t)\sin\Big(\frac{n\pi t}{L}\Big) dt \Bigg)
-\end{equation}
-Which can be conveniently simplified to:
-\begin{equation}
-\label{c_n}
-c_n = \frac{1}{L}\int_0^L f(t) e^{i\pi\frac{n}{L}t} dt
-\end{equation}
+% ================================================================
 
 % ================================================================
-
-\section{The Fourier Transform}
-\paragraph*{}The concept of Fourier Series is very useful, but often difficult in practice.
-In many cases the integrals cannot be evaluated exactly, especially for more complicated functions of time or space.
-Even when done with a computer, only a finite amount of coefficients can be computed, and it comes with great computational costs.
-For example, to compute the first $N$ terms in the series, $2N + 1$ definite integrals must be numerically evaluated.
-\paragraph*{}In addition to Fourier series expansions, the \textit{Fourier Transform} is a very common tool to use.
-To build the Fourier transform, we are going to begin with the complex  definition of the Fourier Series expansion from equation (\ref{complex series def}), where the $c_n$ coefficients are given by equation (\ref{c_n}).
-\paragraph*{}Suppose we have a signal function of time, $g(t)$ and we want to transform it into it's frequency domain.
-The resulting function will be of frequency, $g(f)$, not time.
-Suppose we want to transform with over the domain
-$-L < t < +L$. Thus our Fourier series representation is given by:
-\begin{equation}
-g(t) = \sum_{n=-\infty}^{\infty} c_n e^{i\pi\frac{n}{L}t}
-\end{equation}
-with the $c_n$ coefficients given by:
-\begin{equation}
-c_n = \frac{1}{2L}\int_{-L}^{+L} g(t) e^{i\pi\frac{n}{L}t} dt
-\end{equation}
-\paragraph*{}Now we can define a discrete index variable, $\xi$ to be:
-\begin{equation}
-\xi = \frac{n\pi}{L} 
-\end{equation}
-\begin{flushright}
-Where $n = 0, \pm 1, \pm 2, \pm3, ...$
-\end{flushright}
-And also the difference between adjacent values of $\xi$ is given by:
-\begin{equation}
-\Delta \xi = \xi_{n+1} - \xi_{n} = \frac{\pi}{L}
-\end{equation}
-The partial Fourier transform of $g(t)$ on the interval $-L < t < +L$ is then given by:
-\begin{equation}
-F_L(\xi) = \frac{1}{2L} \int_{-L}^{+L} g(t) e^{-i\xi t} dt =
-\frac{1}{2L} \int_{-L}^{+L} g(t) e^{-i\frac{\pi}{L}t} dt
-\end{equation}
-\paragraph*{}
 
@@
 \begin{thebibliography}{9}
-\bibliographystyle{apalike}
+
+\bibitem{Debnath}
+Debnath, Lokenath, and Dambaru Bhatta. \textit{Integral Transforms and Their Applications}. CRC Press/Taylor \& Francis Group, 2015.
 
@@
 
+\bibitem{Olver}
+Olver, Peter J. Introduction to Partial Differential Equations. Springer International, 2016.
+
+\bibitem{Oppenheim}
+Oppenheim, Alan S., et al. \textit{Signals and Systems}. Prentice-Hall, 1983.
+
+\bibitem{Peatross}
+Peatross, Justin, and Michael Ware. \textit{Physics of Light and Optics}. Brigham Young University, Department of Physics, 2015.
+
 \bibitem{Pinsky}
-Pinsky, Mark A. \textit{Partial Differential Equations and Boundary-Value Problems with Applications}. 3rd ed., American Mathematical Society, 2011.
-
-\bibitem{Taylor}
-Taylor, John R. \textit{Classical Mechanics}. Univ. Science Books, 2005.
+Pinsky, Mark A. \textit{Partial Differential Equations with Boundary-Value Problems with Applications}. 3rd ed., American Mathematical Society, 2010.
 

### 2020-05-08 Notes/Fourier Series/Fourier_Analysis_v0.tex
Fourier Transform testing

% ================
% Landon Buell
% Kevin Short
% PHYS 799 
% 5 May 2020
% ================

\documentclass[12pt,letterpaper]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm]{geometry}
\usepackage{float}
\usepackage{graphicx}
\usepackage{fancyhdr}

% ================================================================

\pagestyle{fancy}
\fancyhf{}
\lhead{An Introduction to Fourier Analysis}
\rhead{Landon Buell}
\cfoot{\thepage}

% ================================================================

\begin{document}

\title{An Introduction to Fourier Analysis}
\author{Landon Buell}
\date{5 May 2020}
\maketitle

% ================================================================

\section*{Introduction}
\paragraph*{}Just after the turn of the 18-th century French Mathematician Jean Baptiste Fourier had spent a great deal of his time in the subjects of various partial differential equations and boundary value problems. In particular, he found that analytical solutions to \textit{The Heat Transfer Equation} involved an infinite series of orthogonal trigonometric functions \cite{Pinsky,Olver}. This lead Fourier to extent his findings and propose that \textit{any} function that was periodic with space or time could similarly be expressed as this series of sine and cosine functions. For this work, we will take explore time-domain related derivation, behavior, and analysis of the properties of and related to Fourier Series, Analysis and Transforms, both analytically and computationally.

% ================================================================

\section*{Trigonometric Fourier Series}
\paragraph{}Since the series revolves around the idea of converging around approximations of period functions, let us define a continuous function or signal, $S$, that is periodic in time-space, to have the property \cite{Tolstov}:
\begin{equation}
\label{periodic definition}
S(t) = S(t + nT)
\end{equation}
Where $T$ is the \textit{period} of the function with units of time ($T \neq 0$), and $n$ is an integer to indicate that the function repeats for any integer $n$. More intuitively, this is function when evaluated at time $t$ takes on some value, and then will return to that same value when progressing forward or backward in time, by some integer multiple of the period. 
\paragraph*{}With this distinction made, we can examine Fourier's claim that we can approximate this function, over some length of time, $L$, as a sum of sine and cosine functions \cite{Pinsky,Tolstov}, hence this section being \textit{trigonometric} Fourier Series . Mathematically:
\begin{equation}
\label{Series Def}
S(t) = a_0 + \sum_{n=1}^{+\infty} \Bigg[ a_n \cos\Big(\frac{n\pi t}{L}\Big) + b_n \sin\Big(\frac{n\pi t}{L}\Big) \Bigg]
\end{equation}
Were $a_0$ , $a_n$ and $b_n$ are coefficients $L$ is the bound of time which we are concerned with and $n$ is an integer that indicates that we want our analysis to include integer multiples of unit frequencies.
\paragraph*{}This serves as a sort of starting point or baseline for most of Fourier Analysis. If we can accept, or at least humor this, idea, we can use this foundation to break some sort of function, $S(t)$ down into a collection of functions of a single frequency. To do this more practically, we need to derive an expression for each of the infinitely many $a_n$ and $b_n$ coefficients. In order to construct expression for them, we require three very important properties of trigonometric functions:

\begin{enumerate}
\item[•]\textbf{Orthogonality of Cosine}
\begin{equation}
\label{cos orth}
\int_{0}^{L} \cos\Big(\frac{n\pi t}{L}\Big) \cos\Big(\frac{m\pi t}{L}\Big) dt = 
	\left\{
        \begin{array}{ll}
            0 	&, n \neq m \\
            L/2	&, n = m \neq 0 \\
            L 	&, n = m = 0\\
        \end{array}
    \right.
\end{equation}
\item[•]\textbf{Orthogonality of Sine}
\begin{equation}
\label{sin orth}
\int_{0}^{L} \sin\Big(\frac{n\pi t}{L}\Big) \sin\Big(\frac{m\pi t}{L}\Big) dt = 
	\left\{
        \begin{array}{ll}
            0 	&, n \neq m \\
            L/2	&, n = m \neq 0 \\
            L 	&, n = m = 0\\
        \end{array}
    \right.
\end{equation}
\item[•]\textbf{Mutual Orthogonality}
\begin{equation}
\label{mutual orth}
\int_{0}^{L} \cos\Big(\frac{n\pi t}{L}\Big) \sin\Big(\frac{m\pi t}{L}\Big) dt = 0 ,
\hspace*{1cm} \forall m,n
\end{equation}
\end{enumerate}
Note that each of these hold in the case that either $m$ or $n$ are $0$, which causes that function to oscillate with $0$ frequency, thus remains constant \cite{Tolstov}. With these three identities, we can now derive the coefficients.

% ================================

\subsection*{Finding $a_0$}
\paragraph*{}To find $a_0$, we integrate both sides of the equation (\ref{Series Def}) from $0$ to $L$ with respect to time:
\begin{equation}
\int_{0}^{L}S(t)dt = \int_{0}^{L}a_0dt + \int_{0}^{L}\sum_{n=1}^{+\infty} 
\Bigg[ a_n \cos\Big(\frac{n\pi t}{L}\Big) + b_n \sin\Big(\frac{n\pi t}{L}\Big) \Bigg] dt
\end{equation}
Because of the linearity of the integral operator, the integration can be distributed identically to every term in the infinite sum. We can now recognize that each term inside the sum resembles equation (\ref{cos orth}) or (\ref{sin orth}), for sequential $n$ and $m = 0$. This causes every single one of those terms to vanish to $0$. Thus the remaining equation becomes:
\begin{equation}
\int_{0}^{L}S(t)dt = a_0\int_{0}^{L}dt
\end{equation}
Where $a_0$ is factored out due to it being a constant. We can then evaluate the right-hand integral and then solve for $a_0$ \cite{Haberman}:
\begin{equation}
\label{a_0}
a_0 = \frac{1}{L}\int_{0}^{L}S(t)dt
\end{equation}
\paragraph*{}Physically, we can actually interpret the constant $a_0$ as the \textit{average} value of the function $S(t)$ over the range $0$ to $L$. This makes sense, as it's the only constant value in the series, thus serving as the basis for all other functions to oscillate about.

% ================================

\subsection*{Finding $a_n$ and $b_n$}
\paragraph*{}Due to the similar properties of sine and cosine as outline above, the process for finding the $a_n$ and $b_n$ coefficients are almost identical. For practical purposes, we will derive just $a_n$ and then show how it also applies the the $b_n$ coefficients. For the cosine function coefficients, we start again with equation (\ref{Series Def}). To start, we multiply both sides of the function with $\cos(m\pi t/L)$. Again, this distributes to every term in the infinite series as well.
\begin{equation}
\label{S(t)cos(t)}
\begin{split}
S(t)\cos\Big(\frac{m\pi t}{L}\Big) = &  a_0\cos\Big(\frac{m\pi t}{L}\Big) + \\
\sum_{n=1}^{+\infty} & \Bigg[ a_n \cos\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) \Bigg] +  
\sum_{n=1}^{+\infty} \Bigg[ b_n \sin\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) \Bigg]
\end{split}
\end{equation}
Note that I have split the infinite sum into two separate (but still infinite) sums, the first containing only cosine terms and the 2nd containing both cosine and sine.
\paragraph*{}Just as before, we will integrate every term in equation (\ref{S(t)cos(t)}) with respect to time from $0$ to $L$. In the 2nd sum, with the sines and cosines together, we can use equation (\ref{mutual orth}) to show that every term in the sum vanishes to $0$, when integrating over our chosen bounds. Furthermore, the $a_0$ term also goes to $0$ for the same reason, This means that we now have:
\begin{equation}
\int_{0}^{L}S(t)\cos\Big(\frac{m\pi t}{L}\Big)dt = 
\int_{0}^{L}\sum_{n=1}^{+\infty} \Bigg[ a_n \cos\Big(\frac{n\pi t}{L}\Big)\cos\Big(\frac{m\pi t}{L}\Big) \Bigg]dt
\end{equation}
Once again, we exploit the linear property of the integral, and distribute it to each term in the infinite sum. Every single term in that infnite sum then integrates to $0$ due to identity (\ref{cos orth}), except for the single case where $m = n$. The result is a much cleaner expression:
\begin{equation}
\int_{0}^{L}S(t)\cos\Big(\frac{n\pi t}{L}\Big)dt = 
a_n\int_{0}^{L} \cos^2\Big(\frac{n\pi t}{L}\Big)dt
\end{equation}
I have replaced all $m$'s with $n$'s due to their equivalence. Finally, the integral on the right side can be evaluated, and then we solve for $a_n$ and reveal:
\begin{equation}
\label{a_n}
a_n = \frac{2}{L}\int_{0}^{L}S(t)\cos\Big(\frac{n\pi t}{L}\Big)dt
\end{equation}
\paragraph*{}To derive the $b_n$ coefficients, we need only to repeat the process, this time replace the inserted cosine functions in equatiion (\ref{S(t)cos(t)}) with sine functions. Following all of the same steps and similar rules brings us to:
\begin{equation}
\int_{0}^{L}S(t)\sin\Big(\frac{m\pi t}{L}\Big)dt = 
\int_{0}^{L}\sum_{n=1}^{+\infty} \Bigg[ b_n \sin\Big(\frac{n\pi t}{L}\Big)\sin\Big(\frac{m\pi t}{L}\Big) \Bigg]dt
\end{equation}And finally given the rules of orthogonality in equation (\ref{sin orth}), we can again remove all terms in this sum, except for where $m = n$, and then solve for $b_n$ to show:
\begin{equation}
\label{b_n}
b_n = \frac{2}{L}\int_{0}^{L}S(t)\sin\Big(\frac{n\pi t}{L}\Big)dt
\end{equation}

% ================================

\subsection*{Summary of trigonometric Fourier Series}
\paragraph*{}Beginning with Fourier's assertion that a continuous function of time, $S(t)$, can be expanded as an infinite linear combination of orthogonal trigonometric functions, we have shown to use the properties of the sine and cosine functions to generate the coefficients in the combination. Thus, we arrive at the expressions, very compactly:
\begin{equation}
S(t) = a_0 + \sum_{n=1}^{+\infty} \Bigg[ a_n \cos\Big(\frac{n\pi t}{L}\Big) + b_n \sin\Big(\frac{n\pi t}{L}\Big) \Bigg]
\end{equation}
Where \cite{Pinsky,Tolstov,Peatross}:
\begin{equation}
\begin{split}
a_0 =& \frac{1}{L}\int_{0}^{L}S(t)dt \\
a_n =& \frac{2}{L}\int_{0}^{L}S(t)\cos\Big(\frac{n\pi t}{L}\Big)dt \\
b_n =& \frac{2}{L}\int_{0}^{L}S(t)\sin\Big(\frac{n\pi t}{L}\Big)dt \\
\end{split}
\end{equation}
This may leave us with more questions that answers. What happens when we want to change the bounds of the integral? What happens if the period of the signal is a non-integer or is much greater than the bounds? If we have a well-defined function, why would be want to approximate it anyways?
\paragraph*{}We'll, because of many of these concerns, trigonometric series expansions are not commonly used to break down a function, especially in digital signal processing, it just isn't reasonable do, especialy when signals like $S(t)$ are not continuous functions, but rather composed of discrete floating-point entries. Ideally, what we want it a \textit{transform} that allows us to take a function of time $S(t)$ and convert it into an equivalent function of frequency, $S(f)$ without getting bogged down in trigonometry. For this, we need to use \textit{Complex} Fourier Series to derive the \textit{Fourier Transform}.

% ================================================================

\section*{Fourier Transform}
\paragraph*{}To build the transform, we need to eliminate the sine and cosine expansion in favor of a complex exponential function. Thanks to German mathematician, Leonard Euler, and his work with complex-space and the complex unit circle, we have the infamous Euler's Identity:
\begin{equation}
\label{Euler}
e^{i\varphi} = \cos(\varphi) + i\sin(\varphi)
\end{equation}
As a direct consequence, we can also show the two following very important relations:
\begin{equation}
\cos(\varphi) = \frac{e^{i\varphi} + e^{-i\varphi}}{2}
\end{equation}
\begin{equation}
\sin(\varphi) = \frac{e^{i\varphi} - e^{-i\varphi}}{2i}
\end{equation}
\paragraph*{}With these in our back pocket, we can now take Fourier's original claim aout decomposing it into sine and cosine function, (\ref{Series Def}) and instead decompose it into a sum of complex exponential functions:
\begin{equation}
S(t) = a_0 +  \sum_{n=1}^{+\infty} \Bigg[
\frac{a_n}{2} \Big( e^{i\big(\frac{n\pi t}{L}\big)} + e^{-i\big(\frac{n\pi t}{L}\big)} \Big)+
\frac{b_n}{2i}\Big( e^{i\big(\frac{n\pi t}{L}\big)} - e^{-i\big(\frac{n\pi t}{L}\big)} \Big)\Bigg]
\end{equation}
\paragraph*{}We can now rearrange the terms with the sum, and combine like-exponentials. We will also split the single sum into two sums, all still infinite in length:
\begin{equation}
S(t) =  a_0 +
\sum_{n=0}^{+\infty} \Big(\frac{a_n - ib_n}{2}\Big) e^{+i\big(\frac{n\pi t}{L}\big)} +
\sum_{n=0}^{+\infty} \Big(\frac{a_n + ib_n}{2}\Big) e^{-i\big(\frac{n\pi t}{L}\big)}
\end{equation}
Next, lets create new variables $c_n^+$ and $c_n^-$ to replace the coefficients inside each sum respectively. Since the complex exponential evaluates to $1$ when $n=0$, we will absorb it into the same, and change the index to include $n = 0$. Now, when all said is done, we can simply state:
\begin{equation}
S(t) = \sum_{n = -\infty}^{+\infty} c_n e^{+i\big(\frac{n\pi t}{L}\big)}
\end{equation}
Where:
\begin{equation}
\begin{split}
c_n^+ = & c_{n>0} = \frac{a_n - ib_n}{2} \\
c_n^- = & c_{n<0} = \frac{a_n + ib_n}{2} \\
c_0   = & a_n
\end{split}
\end{equation}

% ================================================================

% ================================================================

% ================================================================

% ================================================================

\begin{thebibliography}{9}

\bibitem{Debnath}
Debnath, Lokenath, and Dambaru Bhatta. \textit{Integral Transforms and Their Applications}. CRC Press/Taylor \& Francis Group, 2015.

\bibitem{Haberman}
Haberman, Richard. \textit{Applied Partial Differential Equations: with Fourier Series and Boundary Value Problems}. 5th ed., Pearson Education, 2014.

\bibitem{Olver}
Olver, Peter J. Introduction to Partial Differential Equations. Springer International, 2016.

\bibitem{Oppenheim}
Oppenheim, Alan S., et al. \textit{Signals and Systems}. Prentice-Hall, 1983.

\bibitem{Peatross}
Peatross, Justin, and Michael Ware. \textit{Physics of Light and Optics}. Brigham Young University, Department of Physics, 2015.

\bibitem{Pinsky}
Pinsky, Mark A. \textit{Partial Differential Equations with Boundary-Value Problems with Applications}. 3rd ed., American Mathematical Society, 2010.

\bibitem{Tolstov}
Tolstov, Georgy Pavlovich. \textit{Fourier Series}. Translated by Richard Allan. Silverman, London; Printed in U.S.A., 1962.

\end{thebibliography}

% ================================================================

\end{document}

### 2020-05-08 Instrument_Classifier_v0/INST_CLF_v0/INST_CLF_v0_machine_learning_utilities.py

@@ -71,7 +71,9 @@ def Design_Matrix_Scaler (X):
     --------------------------------
     Return scaled design matrix
     """
-    scalar = StandardScaler()
+    scaler = StandardScaler()       # scaler obj inst
+    scaler = scaler.fit(X)
+    X = scaler.transform(X)
     return X
 
 

### 2020-05-18 Thesis/MLP.tex
18 May 2020
- Cleaned up function to extract energy from frequency banks
- Reran classification usuing instruments, not just families (Seemed to work well!)
- Added method to visualize confusion matrix
- Begun Notes on Multilayer Perceptron for Final Thesis writeup

% ================
% Landon Buell
% Kevin Short
% PHYS 799
% 18 May 2020
% ================

\documentclass[12pt,letterpaper]{article}

\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm]{geometry}

\begin{document}

% ================================

\title{On the Functionality of the Multilayer Perceptron}
\date{18 May 2020}
\author{Landon Buell}
\maketitle

% ================================================================

\section*{Introduction}

\paragraph*{}In 1943, neurophysiologist Warren McCulloch and mathematician Walter Pitts published \textit{A Logical Calculus of the Ideas Immanent in Nervous Activity} \cite{McCulloch}, which paved the way for the fields of computational neuroscience and early mathematical models of the brain. McCulloch and Pitts proposed that one could loosely mimic the behavior of a brain as a series of mathematical calculations. They realized that the smallest known element of the brain, a \textit{neuron}, acts as a simple on/off switch, much like computers have been designed to. Furthermore, single neurons by themselves do very little, but instead it is the organization of these cells into collections that make up functional networks \cite{Geron,Levine,McCulloch}.

\paragraph*{}The mathematical model could be augmented by trading the simple Boolean (T/F) value, with a continuously ranging number referred to as an \textit{activation}. By producing different types of artificial neurons and establishing a series of synapses, it then became apparent that different organization of these elements could produce networks of solving increasingly advanced problems \cite{Goodfellow}. To further expand upon this, in 1957, Frank Rosenblatt created a neural network architecture called a Multilayer Perceptron, which uses layers of interacting neurons to create a single mathematical model \cite{Geron,Petrik}. This gives it a simple feed-forward design which has experimentally shown to perform well with tasks related to image and speech recognition \cite{Goodfellow,Loy}.

% ================================================================

\section*{Mathematical Treatment}
\paragraph*{}To build a Multilayer Perceptron (MLP), artificial neurons need to be grouped into multiple structures, each called a \textit{layer}. A single layer is modeled mathematically as a column vector, $\vec{x}$ by convention:
\begin{equation}
\label{layer}
\vec{x}^{(l)} = \big[ x_0 , x_1 , x_2 , ... , x_{n-2} , x_{n-1} \big]^T
\end{equation}
The superscprit $(l)$ is used to indicate the layer number of which this vector represents. Each element inside this vector is a neuron in the MLP model, and the value of that element is the neuron's \textit{activation}.

% ================================================================

\section*{Feed-Forward System}

% ================================================================

\section*{Back Propagation System}

% ================================================================

\section*{Conclusion}

% ================================================================

\begin{thebibliography}{9}
\bibliographystyle{apalike}

\bibitem{Geron}
Géron Aurélien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. O'Reilly, 2017.

\bibitem{Goodfellow}
Goodfellow, Ian, et al.\textit{Deep Learning}. MIT Press, 2017.

\bibitem{James}
James, Gareth, et al. \textit{An Introduction to Statistical Learning with Applications in R}. Springer, 2017.

\bibitem{Levine}
Levine, Daniel S. \textit{Introduction to Neural and Cognitive Modeling}. 3rd ed., Routledge, 2019.

\bibitem{Loy}
Loy, James , \textit{Neural Network Projects with Python}. Packt Publishing, 2019

\bibitem{McCulloch}
McCulloch, Warren S., and Walter Pitts. “A Logical Calculus of the Ideas Immanent in Nervous Activity.” \textit{The Bulletin of Mathematical Biophysics}, vol. 5, no. 4, 1943, pp. 115–133.

\bibitem{Petrik}
Petrik, Marek. “Introduction to Deep Learning.” Machine Learning. 20 April. 2020, Durham, New Hampshire.

\end{thebibliography}

% ================================================================

\end{document}

### 2020-05-18 Instrument_Classifier_v0/INST_CLF_v0/INST_CLF_v0_base_utilities.py

@@ -55,4 +55,10 @@ def Plot_Confusion_Matrix (model,show=True):
     """
     Visualize Confusion Matrix
     """
-    pass
+    plt.figure(figsize=(16,12))
+    plt.title(model.name,size=40,weight='bold')
+    plt.xlabel("Actual Classes",size=20,weight='bold')
+    plt.ylabel("Predicted Classes",size=20,weight='bold')
+    plt.imshow(model.confusion,plt.cm.binary)
+    plt.tight_layout()
+    plt.show()

### 2020-05-18 Instrument_Classifier_v0/INST_CLF_v0/INST_CLF_v0_main.py

@@ -32,7 +32,7 @@ if __name__ == '__main__':
     
     # LOAD DESIGN MATRIX & TARGET VECTORS
     X = pd.read_csv(data_dir+'/X.csv',header=0,index_col=0)
-    y = pd.read_csv(data_dir+'/y.csv',header=0,index_col=0)
+    y = pd.read_csv(data_dir+'/y1.csv',header=0,index_col=0)
    
     X = ML_utils.Design_Matrix_Scaler(X)
     X = ML_utils.Design_Matrix_Labeler(X,True)
@@ -40,26 +40,13 @@ if __name__ == '__main__':
 
     # SPLIT TRAIN-TEST DATA
     X_train,X_test,y_train,y_test = \
-        ML_utils.split_train_test(X,y,test=0.3)
+        ML_utils.split_train_test(X,y,test=0.5)
 
     # NEURAL NETWORK
     NETWORK = ML_utils.Create_MLP_Model('All Features',(20,20),
                                         seed=None)
     NETWORK = NETWORK.fit(X_train,y_train)
     NETWORK = ML_utils.Evaluate_Classifier(NETWORK,X_test,y_test)
-    print(NETWORK.confusion)
-
-    """
-    # SELECT K-BEST
-    X1 = ML_utils.K_Best_Features(X,y,K=10)
-    print(X1.shape)
-    X_train,X_test,y_train,y_test = \
-        ML_utils.split_train_test(X1,y,test=0.3)
-
-    # NEURAL NETWORK
-    NETWORK = ML_utils.Create_MLP_Model('K-Best Features',(20,20),
-                                        seed=0)
-    NETWORK = NETWORK.fit(X_train,y_train)
-    NETWORK = ML_utils.Evaluate_Classifier(NETWORK,X_test,y_test)
-    print(NETWORK.confusion)
-    """
+    #print(NETWORK.confusion)
+    
+    base_utils.Plot_Confusion_Matrix(NETWORK,True)

### 2020-05-18 Instrument_Classifier_v0/INST_FTRS_v0/INST_FTRS_v0_base_utilities.py

@@ -65,13 +65,8 @@ class wavfile():
         self.channel = file.split('.')[-2]      # L or R channel
         self.ext = file.split('.')[-1]          # file ext type (wav)
         self.rate = 44100                       # sample rate
-        # Set target based on family
-        self.set_target(INSTRUMENT_FAMILIES[self.instrument])
-
-    def set_target (self,target,dictionary=None):
-        """ Set integer target value based on instrument/family """
-        self.target = target
-        return self
+        #self.target = INSTRUMENT_FAMILIES[self.instrument]
+        self.target = self.instrument           # instrument as target
 
     def read_raw_wav(self,normalize=True):
         """ Read Raw data from directory file """      

### 2020-05-18 Instrument_Classifier_v0/INST_FTRS_v0/INST_FTRS_v0_feature_utilities.py

@@ -64,13 +64,14 @@ def freqseries (wavfile):
     features = np.array([])
     
     # SPECTROGRAM
-    N_pts = 2**10                # pts in FFT
-    f,t,Sxx = freq_utils.Spectrogram(wavfile.waveform,N=N_pts)
+    N_pts = 2**12               # pts in FFT
+    f,t,Sxx = freq_utils.Spectrogram(wavfile.waveform,N=N_pts,overlap=0.9)
     #base_utils.Plot_Spectrogram(f,t,Sxx,str(wavfile.filename),show=True)
 
     # ENERGY / FREQUENCY BAND
-    banks = np.array([0,32,64,128,256,512,1024,2048,6000])
-    pwr_per_bank = freq_utils.Frequency_Banks(f,t,Sxx,cutoffs=banks)
+    banks = np.array([(0,32),(32,64),(64,128),(128,256),
+                      (256,512),(512,1024),(1024,2048),(2048,6000)])
+    pwr_per_bank = freq_utils.Frequency_Banks(f,t,Sxx,bnd_pairs=banks)
     features = np.append(features,pwr_per_bank)
 
     features = np.ravel(features)   # flatten to 1D

### 2020-05-18 Instrument_Classifier_v0/INST_FTRS_v0/INST_FTRS_v0_freq_utilities.py

@@ -87,7 +87,7 @@ def Spectrogram (waveform,rate=44100,N=2**10,overlap=0.75,
     Return spectrogram of signal
     """
     # Initialize
-    step = int(overlap*N)       # step between frames 
+    step = N - int(overlap*N)   # step between frames 
     Sxx = np.array([])          # init spectrogram
     cntr = 0                    # number of FFT's computed
 
@@ -124,18 +124,19 @@ def CSPE_MATLAB(waveform,n_pts):
                     varargin=['windowed'])
     return None
     
-def Frequency_Banks(f,t,Sxx,cutoffs=[0,6000]):
+def Frequency_Banks(f,t,Sxx,bnd_pairs=[(0,6000)]):
     """
     Compute power within a set of bands of the frequency spectrum
     --------------------------------
     f (arr) : (1 x N) frequency space axis
     t (arr) : (1 x M) time space axis
     Sxx (arr) : (N x M) matrix representing file's spectrogram
-    cutoffs (iter) : iterable of bounds of frequnecy bands
+    bnd_pairs (iter) : iterable of bounds of frequnecy bands
+        recc shape: [(a,b),(b,c),(c,d),...,(x,y),(y,z)]
     --------------------------------
     Return arr of powers in each frequency band
     """
-    n_banks = len(cutoffs) - 1      # number of banks to use
+    n_banks = len(bnd_pairs)        # number of banks to use
     n_frames = t.shape[0]           # number of frames in file
     Sxx = Sxx.transpose()               # transp spectrogram
     bank_pwrs = np.zeros((1,n_banks))   # arr to hold power/banks
@@ -144,8 +145,8 @@ def Frequency_Banks(f,t,Sxx,cutoffs=[0,6000]):
     for frame in Sxx:                       # iterate through time
         frame_pwrs = np.array([])           # bank pwrs for frame
 
-        for I in range (0,len(cutoffs)-1,1):            # each banks
-            low_bnd,high_bnd = cutoffs[I],cutoffs[I+1]  # establish bnds
+        for pair in bnd_pairs:                          # each pair of bnds
+            low_bnd,high_bnd = pair[0],pair[1]          # establish bnds
             pts = np.where((f>=low_bnd)&(f<=high_bnd))  # find idxs of bands
             bank = frame[pts]                           # isolate band
             pwr = integrate.trapz(bank)                 # compute def integral

### 2020-05-18 Instrument_Classifier_v0/INST_FTRS_v0/INST_FTRS_v0_main.py

@@ -55,6 +55,6 @@ if __name__ == '__main__':
     # EXPORT X & Y
     y = pd.DataFrame(data=y,columns=['Target'])
     X.to_csv(out_dir+'/X.csv')
-    y.to_csv(out_dir+'/y.csv')
+    y.to_csv(out_dir+'/y1.csv')
    
     

### 2020-05-19 Thesis/MLP Notes/MLP.tex
19 May 2020
- Reorganized Thesis Folder
- Updated MLP Notes

--- 2020-05-18 Thesis/MLP.tex
@@
 
-\title{On the Functionality of the Multilayer Perceptron}
+\title{On the Functionality of the Multilayer Perceptron Classifiers}
 \date{18 May 2020}
@@
 By producing different types of artificial neurons and establishing a series of synapses, it then became apparent that different organization of these elements could produce networks of solving increasingly advanced problems \cite{Goodfellow}.
-To further expand upon this, in 1957, Frank Rosenblatt created a neural network architecture called a Multilayer Perceptron, which uses layers of interacting neurons to create a single mathematical model \cite{Geron,Petrik}.
+To further expand upon this, in 1957, Frank Rosenblatt created a neural network architecture called a Multilayer Perceptron (MLP), which uses layers of interacting neurons to create a single mathematical model \cite{Geron,Petrik}.
 This gives it a simple feed-forward design which has experimentally shown to perform well with tasks related to image and speech recognition \cite{Goodfellow,Loy}.
+
+\paragraph*{}In general, the goal of an classification MLP is to produce some approximation function, $F^*$ that maps an array or vector of inputs, 
+$\vec{x}$ to a set of discrete classes: $0,1,2,...,k-1$, using a set of parameters $\hat{\theta}$ \cite{Geron,Goodfellow,Petrik}. For a \textit{k-bins} classifier, we notate this as:
+\begin{equation}
+\label{approx}
+F^* : \big\{ \vec{x},\hat{\theta}\big\} \rightarrow \big\{ 0,1,2,...,k-2,k-1 \big\}
+\end{equation}
+This function is in turn composed of layers of smaller repeating functions, which is what gives rise to the \textit{network} concept of the model.
+It is the chains of these smaller functions that allow for the producing of the approximate function $F^*$ to be created and solve a vast range of problems.
 
@@
 
-\section*{Mathematical Treatment}
+\section*{Architecture}
 \paragraph*{}To build a Multilayer Perceptron (MLP), artificial neurons need to be grouped into multiple structures, each called a \textit{layer}.
@@
 \end{equation}
-The superscprit $(l)$ is used to indicate the layer number of which this vector represents.
-Each element inside this vector is a neuron in the MLP model, and the value of that element is the neuron's \textit{activation}.
+The superscript $(l)$ is used to indicate the layer number of which this vector represents.
+Each element inside this vector is a neuron in the MLP model, and the value of that element is the neuron's \textit{activation} \cite{Geron}.
+In term of numerical handling, this structure is an array of floating-point numbers.
+A neural network can have any number of these layers in them, with any number of neurons in each layer.
+The number of these hidden layers is often referred to as the \textit{network depth} and the number of neurons in each layer is often called the \textit{neuron density} or \textit{network width}.
+
+\paragraph*{}In addition to these layers, called \textit{hidden layers}, a neural network also requires an \textit{input layer} and an \textit{output layer}\cite{Goodfellow}.
+As the name implies, the input layer is where initial arrays of data are passed into the network.
+This array is often called a \textit{feature vector} as each element is a feature derived from a potentially larger data set.
+Typically, this feature vector is denoted by
+$\vec{x}^{(0)}$ is also the $\vec{x}$ object in equation (\ref{approx}).
+
+\paragraph*{}In a network with $L$ layers, the output array is also a vector, 
+$\vec{x}^{(L-1)}$ which encodes the final decision made by the network model.
+In a k-bins classifier, there are $k$ neurons, each one corresponding to a different class.
+The neuron with the highest activation value corresponds to the networks prediction for what class the particular sample,
+$\vec{x}^{(0)}$ belongs to. If the output, $\vec{x}^{(L-1)}$ is appropriately normalized, then then activations can be interpreted percentage probabilities of which class the sample belongs to:
+\begin{equation}
+\label{probability}
+P \big( \vec{x}^{(L-1)} \big) = \frac{1}{||\vec{x}^{(L-1)}||} \big[ x_0 , x_1 , x_2 , ... , x_{k-2} , x_{k-1} \big]^T
+\end{equation}
+
+\paragraph*{}In this network of $L$ layers, there are $L-2$ hidden layers whose activations are given by the entries in $\vec{x}^{(1)}$, 
+$\vec{x}^{(2)}$ , ... , $\vec{x}^{(L-3)}$ , $\vec{x}^{(L-2)}$. And again, the input layers and output layers are given by $\vec{x}^{(0)}$ and 
+$\vec{x}^{(L-1)}$ respectively. Throughout the duration of the model's construction, training and evaluation, these objects remain as column vectors / arrays of real floating point values.
+
+\pagebreak
 
@@
 \section*{Feed-Forward System}
+
+\paragraph*{}Just by having systems of discrete layers, there is no way for the network to behave as`
 

### 2020-05-23 Thesis/MLP Notes/MLP.tex
22 May 2020
- Updated MLP Paper

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{float}
@@
 
-\title{On the Functionality of the Multilayer Perceptron Classifiers}
+\title{On the Functionality of the Multilayer Perceptron Classifier Neural Network Architecture}
 \date{18 May 2020}
@@
 $\vec{x}$ to a set of discrete classes: $0,1,2,...,k-1$, using a set of parameters $\hat{\theta}$ \cite{Geron,Goodfellow,Petrik}. For a \textit{k-bins} classifier, we notate this as:
+
 \begin{equation}
@@
 \end{equation}
+
 This function is in turn composed of layers of smaller repeating functions, which is what gives rise to the \textit{network} concept of the model.
@@
 A single layer is modeled mathematically as a column vector, $\vec{x}$ by convention:
+
 \begin{equation}
@@
 \end{equation}
+
 The superscript $(l)$ is used to indicate the layer number of which this vector represents.
@@
 $\vec{x}^{(0)}$ belongs to. If the output, $\vec{x}^{(L-1)}$ is appropriately normalized, then then activations can be interpreted percentage probabilities of which class the sample belongs to:
+
 \begin{equation}
 \label{probability}
-P \big( \vec{x}^{(L-1)} \big) = \frac{1}{||\vec{x}^{(L-1)}||} \big[ x_0 , x_1 , x_2 , ... , x_{k-2} , x_{k-1} \big]^T
+P \big( \vec{x}^{(L-1)} \big) = \frac{1}{||\vec{x}^{(L-1)}||_2} \big[ x_0 , x_1 , x_2 , ... , x_{k-2} , x_{k-1} \big]^T
 \end{equation}
@@
 
-\paragraph*{}Just by having systems of discrete layers, there is no way for the network to behave as`
+\paragraph*{}Just by having systems of discrete layers, there is no way for the network to behave as a single model.
+Thus, we need to connect adjacent layers with synapses.
+These synapses, also called \textit{weights} allow each activation in any given layer to be a linear combination of the activation in the previous layer, with an addition \textit{bais} constant added \cite{Geron,Loy}.
+Keeping in mind the mathematical equivalent to vectors: we can then say that the $i$-th element in some layer $(l+1)$ is given by:
+
+\begin{equation}
+\label{single element}
+x^{(l+1)}_i = b^{(l)}_i + \sum_{j} w^{(l)}_{ij} x^{(l)}_j
+\end{equation}
+
+Where $b^{(l)}_i$ is the bias entry, $w^{(l)}_{ij}$ is the weight coefficient that joins neuron $x_j$ to neuron $x_i$,m adn $x_j$ is the activation of the $j$-th neuron.
+Notice how the combination of elements in layer $(l)$, given by the upper index, combine to produce the $i$-th neuron activation in layer $(l+1)$.
+
+\paragraph*{}Suppose there are $m$ elements in layer $(l)$ and $n$ elements in layer $(l+1)$.
+We can then express all activations in layer $(l+1)$ by expanding out the sum into a system of linear combinations:
+\begin{equation}
+\begin{split}
+\label{system elements}
+x^{(l+1)}_0 &= b^{(l)}_0 + w^{(l)}_{0,0} x^{(l)}_0 + w^{(l)}_{0,1} x^{(l)}_1 + \hdots + w^{(l)}_{0,m-1} x^{(l)}_{m-1}  \\
+x^{(l+1)}_1 &= b^{(l)}_1 + w^{(l)}_{1,0} x^{(l)}_1 + w^{(l)}_{1,1} x^{(l)}_1 + \hdots + w^{(l)}_{1,m-1} x^{(l)}_{m-1}  \\
+\vdots & \text{\hspace{2cm}} \vdots \\
+x^{(l+1)}_{n-1} &= b^{(l)}_{n-1} + w^{(l)}_{1,0} x^{(l)}_{n-1} + w^{(l)}_{n-1,1} x^{(l)}_{n-1} + \hdots + w^{(l)}_{n-1,m-1} x^{(l)}_{m-1}  \\
+\end{split}
+\end{equation}
+
+\paragraph*{}To make this more convenient to read and express mathematically, the entirety of the system (\ref{single element}) can be expresses as a single matrix vector product.
+The elements $x^{(l+1)}_i$ and $x^{(l)}_j$ can be concatenated in column vectors, $\vec{x}^{(l+1)}$ and $\vec{x}^{(l)}$ respectively:
+
+\begin{equation}
+\label{2 layers}
+\begin{split}
+\vec{x}^{(l)} 	&= \big[ x^{(l)}_0 , x^{(l)}_1 , x^{(l)}_2 , ... , x^{(l)}_{m-2} , x^{(l)}_{m-1} \big]^T \\
+\vec{x}^{(l+1)} &= \big[ x^{(l+1)}_0 , x^{(l+1)}_1 , x^{(l+1)}_2 , ... , x^{(l+1)}_{n-2} , x^{(l+1)}_{n-1} \big]^T 
+\end{split}
+\end{equation}
+
+Similarly, we can take all elements $w^{(l)}_{ij}$ and organize them into a single matrix object, which we call $\hat{W}^{(l)}$, defined as:
+
+\begin{equation}
+\label{weights}
+\hat{W}^{(l)} = 
+\begin{bmatrix}
+w^{(l)}_{0,0} & w^{(l)}_{0,1} & w^{(l)}_{0,2} & \hdots & w^{(l)}_{0,m-2} & w^{(l)}_{0,m-1} \\
+w^{(l)}_{1,0} & w^{(l)}_{1,1} & w^{(l)}_{1,2} & \hdots & w^{(l)}_{1,m-2} & w^{(l)}_{1,m-1} \\
+\vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+w^{(l)}_{n-2,0} & w^{(l)}_{n-2,1} & w^{(l)}_{n-2,2} & \hdots & w^{(l)}_{n-2,m-2} & w^{(l)}_{n-2,m-1} \\
+w^{(l)}_{n-1,0} & w^{(l)}_{n-1,1} & w^{(l)}_{n-1,2} & \hdots & w^{(l)}_{n-1,m-2} & w^{(l)}_{n-1,m-1} \\
+\end{bmatrix}
+\end{equation}
+
+And finally, we define a bias vector, $\vec{b}^{(l)}$ for layer $(l)$, such that:
+
+\begin{equation}
+\label{bias}
+\vec{b}^{(l)} = \big[ b^{(l)}_0 , b^{(l)}_1 , b^{(l)}_2 , ... , x^{(l)}_{n-2} , b^{(l)}_{n-1} \big]^T \\
+\end{equation}
+
+With these conventions established, we can then express the system (\ref{system elements}) as a matrix-vector product:
+
+\begin{equation}
+\label{mat-vec}
+\vec{x}^{(l+1)} = \vec{b}^{(l)} + \hat{W}^{(l)} \vec{x}^{(l)}
+\end{equation}
+
+This linear equation is again, a compact way of expressing of expressing the linear relationship between activations in layer $(l)$ and layer $(l+1)$.
+However, this relationship only allows for a linear model as all activations are made of linear combinations.
+This is part of the justification as to why we have chosen to model layers of neuron activations as elements in column vectors in equation (\ref{layer}).
+
+\paragraph*{}Often, in many-real world problems, models confined to provide linear descriptions or create linear decision boundaries are often insufficient descriptions of solutions \cite{James}.
+To combat this, a \textit{non-linear activation function}, $f$, is added to the matrix vector product in equation (\ref{mat-vec}).
+This changes equation (\ref{mat-vec}) to become \cite{Goodfellow,Loy,Petrik} :
+
+\begin{equation}
+\label{mat-vec + act}
+\vec{x}^{(l+1)} = f^{(l)} \Big( \hat{W}^{(l)} \vec{x}^{(l)} + \vec{b}^{(l)} \Big)
+\end{equation}
+
+Where $f^{(l)}$ is the activation function for the $l$-th layer.
+$\vec{x}^{(l+1)}$ has shape $n \times 1$ , $\hat{W}^{(l)}$ has shape $n \times m$, $\vec{x}^{(l)}$ has shape $m \times 1$ and $\vec{b}^{(l)}$ has shape $n \times 1$.
+(For conventional reasons, the baias vector has been moved to the other side of the matrix-vector product.)
+
+\paragraph*{}As the upper indexes imply, this is how the activations in the next layer are produced. By repeating this equation $L-1$ times in an 
+$L$-layered network, information from the feature vector $\vec{x}^{(0)}$ can be successively transformed into the final decision output of the network $\vec{x}^{(L-1)}$.
+Each application of equation (\ref{mat-vec + act}) produces activations in each of the hidden layers.
+Note that in this $L$-layer network, there are $L-1$ weight matrices and $L-1$ bias vectors as well.
+Every single element in all of these arrays can be concatenated to form a larger object, $\hat{\theta}$.
+It is the combination of the elements in $\hat{\theta}$ that allow the network to map an input vector to an output vector as expressed in equation (\ref{approx}).
 
@@
 \section*{Back Propagation System}
+
+\paragraph*{}The logic of using and input $\vec{x}^{(0)}$ and set of parameters $\hat{\theta}$ to produce an output into a set of discrete bins $0$ thorough $k-1$ becomes worrisome when one considers the amount of parameters that make up the object $\hat{\theta}$, and furthermore how to produce these parameters such that the resulting approximation $F^*$ shows experimental validity.
+To remedy this, the model needs some way of using inputs, with known outputs, to find the elements of $\hat{\theta}$ that allow similar, but non-identical inputs to be mapped to correct outputs.
+
+\paragraph*{}To do this, we must treat the behavior of a neural network as an optimization problem.
+The goal of this would then be to find the set of parameters $\hat{\theta}$ that produces the smallest possible output of some \textit{error function}, \cite{Goodfellow,James,Loy}.
+This may also be called a \textit{cost function} or \textit{loss function} as well.
+This function , $J$ takes the predicted output of the network $\vec{x}^{(L-1)}$ and the parameters $\hat{\theta}$ and maps it to a real number, which then measures the \textit{cost} of that particular sample such that:
+
+\begin{equation}
+\label{cost func}
+J : \big\{ \vec{x}^{L-1} , \hat{\theta} \big\} \rightarrow \big\{ \mathbb{R} \big\}
+\end{equation}
+
+\paragraph*{}The larger the value outputted from this function $J$, the further the models prediction differed from the expected value.
+Thus, this function can be through of as a measurement of how \textit{poor} the network's predict was.
+It then becomes appropriate to make the goal of the model to \textit{optimize} $J$, with respect the parameters $\hat{\theta}$ to allow for a generally low cost value for a given input.
 

### 2020-05-31 Thesis/MLP Notes/MLP.tex
26 May 2020
- Updates to MLP breakdown
31 May 2020
- Progress on MLP paper

@@
 \label{cost func}
-J : \big\{ \vec{x}^{L-1} , \hat{\theta} \big\} \rightarrow \big\{ \mathbb{R} \big\}
+J : \big\{ \vec{x}^{(L-1)}} \rightarrow \big\{ \mathbb{R} \big\}
 \end{equation}
@@
 \paragraph*{}The larger the value outputted from this function $J$, the further the models prediction differed from the expected value.
-Thus, this function can be through of as a measurement of how \textit{poor} the network's predict was.
+Thus, this function can be through of as a measurement of how \textit{poor} the network's prediction was.
 It then becomes appropriate to make the goal of the model to \textit{optimize} $J$, with respect the parameters $\hat{\theta}$ to allow for a generally low cost value for a given input.
+
+\paragraph*{}There are many ways to optimize the parameters in a neural network,for this work, we will examine an optimizer algorithm called \textit{Stochastic Gradient Descent} (SGD).
+This is an iterative method that uses repeated a passes over a data set to slowly push the cost function to a smaller and smaller value.
+As the name implies, we compute the gradient of the cost function, which its the partial derivative of each element that makes up the function, at a given step.
+
+\paragraph*{}To compute the gradient of the cost function, we have to examine it's composition.
 

### 2020-06-03 Thesis/MLP Notes/Mutlilayer Perceptron.tex
2 June 2020
- Updates to MLP Paper

--- 2020-05-31 Thesis/MLP Notes/MLP.tex
@@
 \usepackage{amssymb}
-\usepackage{float}
-\usepackage{graphicx}
-\usepackage{multicol}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 \usepackage[left=2.5cm,right=2.5cm,top=2.5cm]{geometry}
+\usepackage{fancyhdr}
+
+% ================================================================
+
+\pagestyle{fancy}
+\fancyhf{}
+\lhead{MLP Classifier Neural Network}
+\rhead{Landon Buell}
+\cfoot{\thepage}
 
@@
 
-\section*{Architecture}
+\section*{Architectural Considerations}
 \paragraph*{}To build a Multilayer Perceptron (MLP), artificial neurons need to be grouped into multiple structures, each called a \textit{layer}.
@@
 
-Where $b^{(l)}_i$ is the bias entry, $w^{(l)}_{ij}$ is the weight coefficient that joins neuron $x_j$ to neuron $x_i$,m adn $x_j$ is the activation of the $j$-th neuron.
+Where $b^{(l)}_i$ is the bias entry, $w^{(l)}_{ij}$ is the weight coefficient that joins neuron $x_j$ to neuron $x_i$, and $x_j$ is the activation of the $j$-th neuron.
 Notice how the combination of elements in layer $(l)$, given by the upper index, combine to produce the $i$-th neuron activation in layer $(l+1)$.
@@
 
-\paragraph*{}To make this more convenient to read and express mathematically, the entirety of the system (\ref{single element}) can be expresses as a single matrix vector product.
-The elements $x^{(l+1)}_i$ and $x^{(l)}_j$ can be concatenated in column vectors, $\vec{x}^{(l+1)}$ and $\vec{x}^{(l)}$ respectively:
+\paragraph*{}To make this more convenient to read and express mathematically, the entirety of the system (\ref{system elements}) can be expressed as a single matrix vector product.
+The elements $x^{(l)}_j$ and $x^{(l+1)}_i$ can be concatenated in column vectors, $\vec{x}^{(l)}$ and  $\vec{x}^{(l+1)}$ respectively:
 
@@
 \label{bias}
-\vec{b}^{(l)} = \big[ b^{(l)}_0 , b^{(l)}_1 , b^{(l)}_2 , ... , x^{(l)}_{n-2} , b^{(l)}_{n-1} \big]^T \\
+\vec{b}^{(l)} = \big[ b^{(l)}_0 , b^{(l)}_1 , b^{(l)}_2 , ... , b^{(l)}_{n-2} , b^{(l)}_{n-1} \big]^T \\
 \end{equation}
@@
 \end{equation}
+For conventional reasons, the bias vector has been moved to the other side of the matrix-vector product. This is also often represented as two separate processes:
+
+\begin{itemize}
+\item[•] The \textit{Pre-activation} linear portion:
+\begin{equation}
+\label{pre-act}
+\vec{z}^{(l)} = \hat{W}^{(l)} \vec{x}^{(l)} + \vec{b}^{(l)}
+\end{equation}
+\item[•] The \textit{final-activation} portion:
+\begin{equation}
+\label{fin-act}
+\vec{x}^{(l+1)} = f^{(l)} \Big( \vec{z}^{(l)} \Big)
+\end{equation}
+\end{itemize}
 
@@
 $\vec{x}^{(l+1)}$ has shape $n \times 1$ , $\hat{W}^{(l)}$ has shape $n \times m$, $\vec{x}^{(l)}$ has shape $m \times 1$ and $\vec{b}^{(l)}$ has shape $n \times 1$.
-(For conventional reasons, the baias vector has been moved to the other side of the matrix-vector product.)
+Note that the inclusion of an activation function by layer, $f^{(l)}$ in eqn.
+(\ref{mat-vec + act}) changes the linear combination in eqn.
+(\ref{single element}) to instead become:
 
-\paragraph*{}As the upper indexes imply, this is how the activations in the next layer are produced. By repeating this equation $L-1$ times in an 
-$L$-layered network, information from the feature vector $\vec{x}^{(0)}$ can be successively transformed into the final decision output of the network $\vec{x}^{(L-1)}$.
+\begin{equation}
+\label{single element + act}
+x^{(l+1)}_i = f^{(l)} \Big( b^{(l)}_i + \sum_{j} w^{(l)}_{ij} x^{(l)}_j \Big)
+\end{equation}
+
+\paragraph*{}As the upper indexes imply, this is how the activations in the \textit{next} sequential layer are produced.
+By repeating this equation $L-1$ times in an $L$-layered network, information from the feature vector $\vec{x}^{(0)}$ can be successively transformed into the final decision output of the network $\vec{x}^{(L-1)}$.
 Each application of equation (\ref{mat-vec + act}) produces activations in each of the hidden layers.
@@
 It is the combination of the elements in $\hat{\theta}$ that allow the network to map an input vector to an output vector as expressed in equation (\ref{approx}).
+
+\paragraph*{}For a fully connected multilayer perceptron model with $L$ layers, we can construct an algorithm to execute the forward pass process.
+The algorithm returns two array-like object containing all final activations (\ref{mat-vec + act}), and pre-activation function (\ref{mat-vec}) values.
+The final object in the list of the output of the network $\vec{x}^{(L-1)}$ (also referred to as $y^*$).
+For a pseudo-code execution, see alg.(\ref{forward-pass}) \cite{Goodfellow}.
+Note that this algorithm uses features from a single training samples, a practical implementation should include batches of samples.
+
+\begin{algorithm}
+\label{forward-pass}
+\caption{Feed-Forward System in a fully-connected Multilayer perceptron model for a single sample.}
+\begin{algorithmic}
+
+\REQUIRE Network depth of $L$ layers
+\REQUIRE Object of weighting matrices: $\hat{W}^{(i)}$ with $i \in [0,1,...,L-3,L-2]$
+\REQUIRE Object of bias vectors: $\vec{b}^{(i)}$ with $i \in [0,1,...,L-3,L-2]$
+\REQUIRE Object of activation functions: $\vec{f}^{(i)}$ with $i \in [0,1,...,L-3,L-2]$
+\REQUIRE Raw input to network: $\vec{a}$
+
+final-activations $\leftarrow \{\}$ \\
+pre-activation $\leftarrow \{\}$	\\
+$x^{(0)} \leftarrow \vec{a}$ 		\\
+
+\FOR{$l = 0,1,2,...,L-2,L-1$} 
+\item $\vec{z}^{(l)} \leftarrow \vec{b}^{(l)} + \hat{W}^{(l)} \vec{a}^{(l)}$
+\item $\vec{x}^{(l+1)} \leftarrow f^{(l)} \big( \vec{z}^{(l)} \big)$
+\item pre-activations.insert($\vec{z}^{(l)}$)
+\item final-activations.insert($\vec{x}^{(l+1)}$)
+\ENDFOR
+\RETURN pre-activations
+\RETURN final-activations
+\end{algorithmic}
+\end{algorithm}
+
+\paragraph*{}Both arrays  that are returned by the alg.
+(\ref{forward-pass}) contain $L-1$ elements.
+The $j$-th element in the \textit{final-activations} array is the element produced by applying an activation function to the $j$-th element of the \textit{pre-activations} array.
+These correspond to layers $l+1$ and $l$ respectively.
 
@@
 
-\paragraph*{}To do this, we must treat the behavior of a neural network as an optimization problem.
-The goal of this would then be to find the set of parameters $\hat{\theta}$ that produces the smallest possible output of some \textit{error function}, \cite{Goodfellow,James,Loy}.
+\paragraph*{}We construct the object $\hat{\theta}$ to be some multidimensional array-like object that contains all of the parameters in the model.
+very generally, it can be thought of as a concatenation of all weighting and bias elements for all of the layers.
+
+\begin{equation}
+\label{theta}
+\hat{\theta} \equiv \big[ \hat{W}^{(0)} , \vec{b}^{(0)} , \hat{W}^{(1)} , \vec{b}^{(1)} ,
+							... , \hat{W}^{(L-2)} , \vec{b}^{(L-2)} 	\big]
+\end{equation}
+
+Where $\hat{W}^{(l)}$ and $\vec{b}^{(l)}$ are given in eqns.
+(\ref{weights}) and (\ref{bias}) respectively.
+For smaller networks, $\hat{\theta}$ may contain several hundred or thousand elements, and for larger deep-learning networks, may contain tens to hundreds of thousands of elements \cite{Goodfellow,Loy}.
+It is the combinations of these elements that allow for some input given $\vec{x}^{(0)}$ to be transformed into an output $\vec{x}^{(L-1)}$.
+
+\paragraph*{}To do this, we treat the behavior of a neural network as a multidimensional optimization problem.
+The goal of this would then be to find the set of parameters $\hat{\theta}$ that produces the smallest possible output of some \textit{error function}, \cite{Goodfellow,James,Petrik}.
 This may also be called a \textit{cost function} or \textit{loss function} as well.
-This function , $J$ takes the predicted output of the network $\vec{x}^{(L-1)}$ and the parameters $\hat{\theta}$ and maps it to a real number, which then measures the \textit{cost} of that particular sample such that:
+This function , $J$, takes the output of the network $\vec{x}^{(L-1)}$ (which we will refer to as $y^*$) to represent a predicted or approximated output) on a given training sample, and compares it to the expected output for that sample $\vec{y}$, and maps it to a real number, which then measures the \textit{cost} of that particular sample such that:
 
@@
 \label{cost func}
-J : \big\{ \vec{x}^{(L-1)}} \rightarrow \big\{ \mathbb{R} \big\}
+J : \big\{ y^* , y  \big\} \rightarrow \big\{ \mathbb{R} \big\}
 \end{equation}
 
-\paragraph*{}The larger the value outputted from this function $J$, the further the models prediction differed from the expected value.
+\paragraph*{}The larger the value outputted from this function $J$, the further the model's prediction differs from the expected value.
 Thus, this function can be through of as a measurement of how \textit{poor} the network's prediction was.
-It then becomes appropriate to make the goal of the model to \textit{optimize} $J$, with respect the parameters $\hat{\theta}$ to allow for a generally low cost value for a given input.
+It then becomes appropriate to make the goal of the neural network to \textit{optimize} $J$, with respect the parameters $\hat{\theta}$ to allow for a generally low cost value for a given input.
 
 \paragraph*{}There are many ways to optimize the parameters in a neural network,for this work, we will examine an optimizer algorithm called \textit{Stochastic Gradient Descent} (SGD).
-This is an iterative method that uses repeated a passes over a data set to slowly push the cost function to a smaller and smaller value.
-As the name implies, we compute the gradient of the cost function, which its the partial derivative of each element that makes up the function, at a given step.
+This is an iterative method that uses repeated a passes over a data set to slowly push the cost function to a smaller and smaller value \cite{Geron,Goodfellow,Loy}.
+As the name implies, we compute the gradient of the cost function with respect to all of the parameters in the model to produce a vector.
+The components of this vector give the direction to which a small change the elements of $\hat{\theta}$ will result in a small reduction of the value of the loss function.
+Recall the gradient vector of some function $h$ of variables $x_0$ , $x_1$ , ...
+,$x_{n-2}$ , $x_{n-1}$ is given by:
 
-\paragraph*{}To compute the gradient of the cost function, we have to examine it's composition.
+\begin{equation}
+\label{gradient}
+\nabla_{\vec{x}}\Big[ h(x_0,x_1,...,x_{n-2},x_{n-1}) \Big] 
+			= \Big[ \frac{\partial h}{\partial x_0} , \frac{\partial h}{\partial x_1} , ...\
+					\frac{\partial h}{\partial x_{n-2}} , \frac{\partial h}{\partial x_{n-1}} \Big]^T
+\end{equation}
+
+\paragraph*{}To build this vector, we need to use the chain rule of multivariate calculus to work \textit{backwards} through the layers of the network to differentiate by layers, hence why the procedure is called \textit{backwards} propagation.
+To ease mathematical notation, we will redefine the forward pass equation (\ref{mat-vec + act}) into two separate procedures:
+
+\begin{equation}
+\label{linear}
+\vec{z}^{(l)} = \hat{W}^{(l)} \vec{x}^{(l)} + \vec{b}^{(l)}
+\end{equation}
+\begin{equation}
+\label{activation}
+\vec{x}^{(l+1)} = f^{(l)} \big( \vec{z}^{(l)} \big)
+\end{equation}
+
+\paragraph*{}We start by differentiating the cost function $J$ with respect to last layer of weights and biases, $\hat{W}^{(L-2})$ and $\vec{b}^{(L-2)}$.
+The cost, $J$, is a function of the output activations, $\vec{x}^{(L-1)}$ which is in turn a function of $\vec{z}^{L-2}$ in eqn.
+(\ref{activation}) which is in turn a function of both $\hat{W}^{(L-2})$ and $\vec{b}^{(L-2)}$ in eqn.
+(\ref{linear}).
+To account for this layered composition, we multiply each partial derivatives in succession to produce the gradient components that correspond to the needed change in those parameters.
+
+\begin{equation}
+\nabla_{W^{(L-2)}} \Big[ J \Big] = 
+\frac{\partial J}{\partial x^{(L-1)}} \frac{\partial f^{(L-2)}}{\partial z^{(L-2)}} \frac{\partial z^{(L-2)}}{\partial W^{(L-2)}}
+\end{equation}
+\begin{equation}
+\nabla_{b^{(L-2)}} \Big[ J \Big] = 
+\frac{\partial J}{\partial x^{(L-1)}} \frac{\partial f^{(L-2)}}{\partial z^{(L-2)}} \frac{\partial z^{(L-2)}}{\partial b^{(L-2)}}
+\end{equation}
+
+Additionally, we compute the gradient with respect to the $L-2$ layer of activations, which will allows for us to move down the to previous sequential layer $L-3$.
+
+\begin{equation}
+\nabla_{x^{(L-2)}} \Big[ J \Big] = 
+\frac{\partial J}{\partial x^{(L-1)}} \frac{\partial f^{(L-2)}}{\partial z^{(L-2)}} \frac{\partial z^{(L-2)}}{\partial x^{(L-2)}}
+\end{equation}
+
+These three equations allow for the model to work backwards through the layers and compute the gradient of the cost function with respect to every paramater in the network.
+The above equations can be generalized for any layer $l$:
+
+\begin{equation}
+\label{dW}
+\nabla_{W^{(l)}} \Big[ J \Big] = 
+\frac{\partial J}{\partial x^{(l+1)}} \frac{\partial f^{(l)}}{\partial z^{(l)}} \frac{\partial z^{(l)}}{\partial W^{(l)}}
+\end{equation}
+\begin{equation}
+\label{db}
+\nabla_{b^{(l)}} \Big[ J \Big] = 
+\frac{\partial J}{\partial x^{(l+1)}} \frac{\partial f^{(l)}}{\partial z^{(l)}} \frac{\partial z^{(l)}}{\partial b^{(l)}}
+\end{equation}
+\begin{equation}
+\label{dx}
+\nabla_{x^{(l)}} \Big[ J \Big] = 
+\frac{\partial J}{\partial x^{(l+1)}} \frac{\partial f^{(l)}}{\partial z^{(l)}} \frac{\partial z^{(l)}}{\partial x^{(l)}}
+\end{equation}
+
+\paragraph*{}It is important to know that due to numerical condiderations, this operation is very computationally expensive, and fine details for improving efficiency not considered in the equations above.
+Additionally, the results from eqns.
+(\ref{dW}), (\ref{db}), and (\ref{dx}).
 
@@
 
-\section*{Conclusion}
+\section*{Summary}
 

### 2020-06-03 Instrument_Classifier_v0/INST_FTRS_v0/INST_FTRS_v0_base_utilities.py

@@ -34,16 +34,16 @@ INSTRUMENT FEATURES V0 - BASE LEVEL UTILITIES
             #### VARIABLE & OBJECT DECLARATIONS ####   
 
 accepted_instruments = [
-                # Woodwinds
-                'AltoFlute','AltoSax','BbClarinet','EbClarinet','Flute',
-                'Oboe','SopSax','EbClarinet','BassClarinet','BassFlute',
-                'Bassoon',
-                # Strings
-                'Bass','Cello','Viola','Violin',
-                # Brass
-                'BassTrombone','Horn','TenorTrombone','Trumpet','Tuba',
-                # Percussion
-                'bells','Marimba','Vibraphone','Xylophone']
+        # Woodwinds
+        'AltoFlute','AltoSax','BbClarinet','EbClarinet','Flute',
+        'Oboe','SopSax','EbClarinet','BassClarinet','BassFlute',
+        'Bassoon',
+        # Strings
+        'Bass','Cello','Viola','Violin',
+        # Brass
+        'BassTrombone','Horn','TenorTrombone','Trumpet','Tuba',
+        # Percussion
+        'bells','Marimba','Vibraphone','Xylophone']
 
 percussion = ['woodblock','triangle','castanet','clave',
               'crotale','tambourine']
@@ -75,15 +75,15 @@ class wavfile():
 
     def assign_instrument (self):
         """ Assign Instrument Attribute to Instance """
-        string = self.filename.split('.')[0]    # 0-th element in name
-        if string in accepted_instruments:      # in valid instruments
+        name = self.filename.split('.')[0]    # 0-th element in name
+        if name in accepted_instruments:      # in valid instruments
             return string.upper()   # set instrument
-        elif string in percussion:      # percussion?
-            return 'PERCUSSION'      # set
-        elif string in cymbals:         # cymbals?
-            return 'CYMBAL'          # set
-        else:                           # not in lists?
-            return 'OTHER'           # set other
+        elif name in percussion:    # percussion?
+            return 'PERCUSSION'     # set
+        elif name in cymbals:       # cymbals?
+            return 'CYMBAL'         # set
+        else:                       # not in lists?
+            return 'OTHER'          # set other
 
 
     def read_raw_wav(self,normalize=True):
@@ -105,13 +105,15 @@ def argument_parser():
     --------------------------------
     *no argumnets*
     --------------------------------
-    Return completetd argument parser class instance
+    Return complete argument parser class instance
     """
[…]

### 2020-06-03 Instrument_Classifier_v0/INST_FTRS_v0/INST_FTRS_v0_main.py

@@ -27,12 +27,11 @@ INSTRUMENT FEATURES V0 - MAIN EXECUTABLE
 if __name__ == '__main__':
 
     # INITIALIZE DIRECTORIES
-    int_dir = os.getcwd()           # home path is CWD
-    out_dir = int_dir + '/extdata'  # path to store extra data
+    int_dir = os.getcwd()           # home path is CWD   
+    wav_dir = 'C:/Users/Landon/Documents/wav_audio'     # for development
+    out_dir = 'C:/Users/Landon/Documents/GitHub/Buell=Senior-Thesis/Instrument_Classifier_v0' 
+    #wav_dir,out_dir = base_utils.argument_parser()     # for command line
     base_utils.make_paths(paths=[out_dir])
-
-    #wav_dir = base_utils.argument_parser()         # for command line 
-    wav_dir = 'C:/Users/Landon/Documents/wav_audio' # for development
     if os.path.exists(wav_dir) == False:
        sys.exit("\n\tERROR - Local Path Does not Exist")
     print("Searching for .wav files in:\n\t",wav_dir)

### 2020-06-03 Thesis/Classification Features/Time-Freq Features.tex
3 June 2020 (1)
- Regorganized Papers Directory
- Begun paper on signal classification features
- Updates on MLP paper

% ================
% Landon Buell
% Kevin Short
% PHYS 799
% 3 June 2020
% ================

\documentclass[12pt,letterpaper]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm]{geometry}
\usepackage{fancyhdr}

% ================================================================

\pagestyle{fancy}
\fancyhf{}
\lhead{MLP Classifier Neural Network}
\rhead{Landon Buell}
\cfoot{\thepage}

\begin{document}

% ================================

\title{Time-Series and Frequency-Series Features for Musical Instrument Classification}
\date{3 June 2020}
\author{Landon Buell}
\maketitle

% ================================================================

\section{Introduction}

% ================================================================

\section{Time Series Features}

\paragraph*{}Time series features (also called time-domain or time-space features) are pieces of information that can be extracted, derived, or otherwise originate from a signal that in expressed with a dependence on time. This can include weather forecasts, year-to-year population of a given demographic, audio information, or economic stock data. In the context of audio data, this is generally referred to as a \textit{waveform}

% ================================

\subsection{Rise and Decay Time}

\paragraph*{}Signal \textit{rise time} measures the amount of time it takes for a time-domain signal, $S(t)$, to leave it's steady-state condition and \textit{rise} to a given maximum $\max\big[|S(t)|\big]$. Signal \textit{decay time} measures the amount of time it takes for a time-domain signal, $S(t)$, to \textit{decay} from a given maximum value and return to it's steady-state value. Due to the nature of digitally stored audio in both time and amplitude, it may be impossible to find entries in the signal that satisfy exact equilibrium values (usually, $0$).

\paragraph*{}To account for this, we employ a function within our feature-extraction program that measures the $10\%$ to $90\%$ amplitude rise time, and the subsequent $90\%$ to $10\%$ amplitude decay time. This means that we build a function within our feature-extraction program that isolates the produces two array-like objects for each signal. The first array will hold the position (or index) of all points that have a value that exceeds $90\%$ of the waveform maximum (counting for negative amplitudes as well). The second array contains similarly index of values that exceed $10\%$ of the maximum, but not $90\%$.

\paragraph*{}If we take the difference between the $0$-th entry of each array, this is the number of samples that it took for the signal to reach (roughly) $10\%$ of it's maximum amplitude to (roughly) $90\%$ - this \textit{rise time}, $\Delta t_{R}$. Similarly, if we take the difference between the final entry in each array, this gives the \textit{decay time}, $\Delta t_{D}$. Both measurements are in units of the \textit{number of samples}; to convert into more traditional units of time (e.g. seconds), one can multiply by the spacing between samples or divide by the sample rate.

\begin{algorithm}
\label{Rise-Decay Time}
\caption{Compute amplitude rise and decay time of a discrete time-domain signal $S(t)$ for aa give lower bound percentage and upper bound percentage.}

\begin{algorithmic}

\REQUIRE Discrete time series signal: $S$ 
\REQUIRE Value to consider lower bound percentage (0,1): \textit{low\_bnd}
\REQUIRE Value to consider upper bound percentage (0,1): \textit{high\_bnd}
\ENSURE low\_bnd $<$ high\_bnd \\

n\_samples $\leftarrow$ length($S$) \\
$S \leftarrow |S|$ \\
max\_amp $\leftarrow$ maximum($S$) \\

\end{algorithmic}
\end{algorithm}

% ================================

\subsection{Root-Mean-Square Energy of all Frames}

\paragraph*{}The Root-Mean-Square energy (RMS energy) of a frame is rough approximation of the energy contained within a slice of time of a waveform. We refer to a slice of time as a \textit{frame} \cite{Kahn}; where each frame is a subset of sequential samples grouped together. When a sequence of frames as concatenated in order that they are produced, they recreate the origina; waveform in it's entirety.`

 Using Hooke's Law, we know that the instantaneous energy of an oscillation is proportional to the square of it's amplitude.

\begin{algorithm}
\label{RMS Energy of Frames}
\caption{Compute the RMS energy of a collection of frames ith}

\begin{algorithmic}

\REQUIRE Discrete time series signal: $S$ 
\REQUIRE Value to consider lower bound percentage (0,1): \textit{low\_bnd}
\REQUIRE Value to consider upper bound percentage (0,1): \textit{high\_bnd}
\ENSURE low\_bnd $<$ high\_bnd \\

n\_samples $\leftarrow$ length($S$) \\
$S \leftarrow |S|$ \\
max\_amp $\leftarrow$ maximum($S$) \\

\end{algorithmic}
\end{algorithm}

% ================================

\subsection{Percentage of Frames with RMS Energy above value}

% ================================

\subsection{Time Spectral Flux}

% ================================

% ================================================================

\section{Frequency Series Features}

% ================================

\subsection{Number of Unique, Isolated Peak}

% ================================

\subsection{Energy of Signal in Select Frequency Bands}

% ================================

% ================================

% ================================================================

\section{Combined Series Features}

% ================================

\subsection{Spectrogram Matrix}

% ================================

\subsection{Phase-Space Matrix}

% ================================

% ================================================================

\section{Additional Features}

% ================================================================

\section*{Summary}

% ================================================================

\begin{thebibliography}{9}
\bibliographystyle{apalike}

\bibitem{Kahn}
Khan, M. Kashif Saeed, and Wasfi G. Al-Khatib. “Machine-Learning Based Classification of Speech and Music.” Multimedia Systems, vol. 12, no. 1, 2006, pp. 55–67., doi:10.1007/s00530-006-0034-0.

\bibitem{Short}
Short, Garcia, “Signal Analysis Using the Complex Spectral Phase Evolution (CSPE) Method”. Journal of the Audio Engineering Society.

\end{thebibliography}

% ================================================================

\end{document}

### 2020-06-05 Instrument_Classifier_v1/INST_CLF_v1/INST_CLF_v1_Network_Models.py
5 June 2020 (3)
- Updated Instrument Classifier
- Finished raw feature extraction
- Exported MLP parameters
- Need to update CNN performance

@@ -12,32 +12,6 @@ import os
 import tensorflow as tf
 import tensorflow.keras as keras
 
-            #### PREPROCESSING FUNCTIONS ####
-
-def Design_Matrix_Scaler (X):
-    """
-    Scale design matrix to have 0 mean, & unit variance
-    --------------------------------
-    X (arr) : (n_samples x n_features) standard Design matrix to scale
-    --------------------------------
-    Return scaled design matrix
-    """
-    scaler = StandardScaler()   # obj inst
-    X = scaler.fit_transform(X) # fit the inst & tranf X
-    return X
-
-def one_hot_encoder (y,n_classes):
-    """
-    One-Hot-Encode array y
-    --------------------------------
-    y (arr) : (n_samples x 1) sample target array
-    n_classes (int) : number of target classes
-    --------------------------------
-    Return matrix Y, (n_samples x n_classes)
-    """
-    y = np.array(y).ravel()     # make into arr & flatten
-    Y = keras.utils.to_categorical(y,n_classes,dtype='int')
-
             #### NEURAL NETWORK MODELS ####
 
 def CNN_2D_Classifier(name,n_classes,path=None,metrics=None): 
@@ -62,11 +36,11 @@ def CNN_2D_Classifier(name,n_classes,path=None,metrics=None):
     model.add(keras.layers.Flatten())
     model.add(keras.layers.Dense(units=40,activation='relu'))
     # Output
-    model.add(keras.layers.Dense(unitss=n_classes,activation='softmax'))
+    model.add(keras.layers.Dense(units=n_classes,activation='softmax'))
     model.compile(optimizer=keras.optimizers.SGD(),
                   loss='categorical_crossentropy',
                   metrics=metrics)
-
+    print(model.summary())
     # Save Locally?
     if path != None:
         filepath = path + '/' + model.name
@@ -91,20 +65,20 @@ def MLP_Classifier (name,n_features,n_classes,path=None,metrics=None):
     """
     # Create Model & add Input Layer
     model = keras.models.Sequential(name=name)
-    model.add(keras.layers.InputLayer(input_shape=(n_features,1)))
+    model.add(keras.layers.InputLayer(input_shape=(n_features,)))
     # Dense Layers
-    model.add(keras.layers.Dense(units=20,activation='relu'))
-    model.add(keras.layers.Dense(units=20,activation='relu'))
+    model.add(keras.layers.Dense(units=40,activation='relu'))
+    model.add(keras.layers.Dense(units=40,activation='relu'))
[…]

### 2020-06-05 Instrument_Classifier_v1/INST_CLF_v1/INST_CLF_v1__Machine_Learning_Utilities.py

@@ -1,0 +1,93 @@
+"""
+Landon Buell
+Instrument Classifier v1
+Classifier - Machine Learning Utility Functions
+1 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+import pandas as pd
+import os
+
+import tensorflow as tf
+import tensorflow.keras as keras
+
+from sklearn.preprocessing import StandardScaler
+from sklearn.model_selection import train_test_split
+import sklearn.metrics as metrics
+
+import INST_CLF_v1_base_utilities as base_utils
+
+"""
+INSTRUMENT CLASSIFIER v1 - MACHINE LEARNING UTILITIES
+        Functions related to machine learning structure & workflow
+    - split_train_test
+    - target_label_encoder
+    - Design_Matric_Scaler
+    - Design_Matrix
+"""
+
+            #### PREPROCESSING FUNCTIONS ####
+
+def split_train_test (X,y,test=0.25,seed=None):
+    """
+    generate a series of indicies for training & testing data
+        Adapted from (Geron, 49) (Note: numpy is Psuedo-Random)
+    --------------------------------
+    X (arr) : Design matrix, (n_samples x n_features)
+    y (arr) : Target vector, (n_samples x 1)
+    test (float) : ratio of testing data size on the bound (0,1)
+    seed (int) : Random state for split
+    --------------------------------
+    return lists of training obj instances & testing obj instances 
+    """
+    return train_test_split(X,y,test_size=test,random_state=seed)
+
+def Scale_Design_Matrix (X):
+    """
+    Scale design Matrix so that Cols have mean=0, var=1
+    --------------------------------
+    X (arr/frame) : Standard design matrix (n_samples x n_features)
+    --------------------------------
+    Return scaled design matrix X
+    """
+    scaler = StandardScaler()   # create inst
+    X = scaler.fit_transform(X) # fit the inst & tranf X
+    return X                    # Return X
+
+def one_hot_encoder (y):
+    """
+    One-Hot-Encode target vector y
+    --------------------------------
+    y (arr) : Standard target vector (n_samples x 1)
+    --------------------------------
+    Return encoded target Matrix Y (n_samples,n_classes)
+    """
+    y = y.ravel()                       # flatten
+    n_classes = np.unique(y).shape[0]   # number of classes
+    Y = keras.utils.to_categorical(y,n_classes)
+    return Y,n_classes                  # return new matrix
+
[…]

### 2020-06-05 Instrument_Classifier_v1/INST_CLF_v1/INST_CLF_v1_base_utilities.py

@@ -1,0 +1,209 @@
+"""
+Landon Buell
+Instrument Classifier v0
+Base Level Utility Functions
+1 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+import pandas as pd
+import os
+import argparse
+import matplotlib.pyplot as plt
+
+
+"""
+INSTRUMENT CLASSIFIER v1 - BASE LEVEL UTILITIES
+            Script contains lowest level function and class defintions that 
+            supports higher end functions 
+        - argumer_parser
+        - make_paths
+        - read_directory
+        - Plot_Time_Spectrum
+        - Plot_Frequency_Spectrum
+        - Plot_Spectrogram
+        - Plot_Features_2D
+"""
+
+            #### VARIABLE & OBJECT DECLARATIONS ####   
+
+                
+            #### DIRECTORY AND OS FUNCTIONS ####
+
+def argument_parser():
+    """
+    Create argument parper object for main executable
+    --------------------------------
+    *no argumnets*
+    --------------------------------
+    Return complete argument parser class instance
+    """
+    parser = argparse.ArgumentParser(prog='Instrument Classifer v1')
+    parser.add_argument('wav_audio',type=str,
+                        help='Local path where raw audio files are stored')
+    args = parser.parse_args()
+    return args.wav_audio
+
+def make_paths(paths=[]):
+    """
+    Create directory paths for each
+    --------------------------------
+    paths (iter) : iterable of folder directory paths to make
+    --------------------------------
+    returns NONE
+    """
+    for path in paths:
+        os.makedirs(path,exist_ok=True)
+    return paths
+
+def read_directory (path,ext='.csv'):
+    """
+    Read through directory and create instance of every file with matching extension
+    --------------------------------
+    path (str) : file path to read data from
+    ext (str) : extension for appropriate file types
+    --------------------------------
+    Return list of wavfile class instances
+    """
+    Xs,ys = []                              # list to hold valid file
+    for roots,dirs,files in os.walk(path):  # walk through the tree
+        for file in files:                  # for each file
+            if file.endswith(ext):          # matching extension
[…]

### 2020-06-05 Instrument_Classifier_v1/INST_CLF_v1/INST_CLF_v1_main.py

@@ -1,0 +1,61 @@
+"""
+Landon Buell
+Instrument Classifier v1
+Classifier - Neural Network Models
+4 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+import pandas as pd
+import sys
+import os
+import time
+
+import INST_CLF_v1__Machine_Learning_Utilities as ML_utils
+import INST_CLF_v1_Network_Models as NN_Models
+import INST_CLF_v1_base_utilities as base_utils
+
+"""
+INSTRUMENT CLASSIFIER v0 - MAIN EXECUTABLE
+    Startup file for feature extraction Program
+"""
+
+            #### MAIN EXECUTABLE ####
+
+if __name__ == '__main__':
+
+    # INITIALIZE DIRECTORIES
+    int_dir = os.getcwd()           # home path is CWD   
+    wav_dir = 'C:/Users/Landon/Documents/wav_data'     # for development
+    #wav_dir = base_utils.argument_parser()     # for command line
+    if os.path.exists(wav_dir) == False:
+       sys.exit("\n\tERROR - Local Path Does not Exist")
+    print("Searching for .wav files in:\n\t",wav_dir)
+ 
+    # IMPORT X,y 
+    DECODE = pd.read_csv(wav_dir+'/DECODE.csv',index_col=0)
+    X = pd.read_csv(wav_dir+'/X.csv',index_col=0)
+    y = pd.read_csv(wav_dir+'/y.csv',index_col=0).to_numpy()
+
+    # PRE-PROCESSING
+    X = ML_utils.Scale_Design_Matrix(X) 
+    X_train,X_test,y_train,y_test = \
+        ML_utils.split_train_test(X,y,test=0.4)
+    Y_train,n_classes = ML_utils.one_hot_encoder(y_train)
+    n_samples,n_features = X.shape
+
+    MLP = False
+    if MLP == True:
+        # MLP MODEL
+        MLP_MODEL = NN_Models.MLP_Classifier('JARVIS',n_features,n_classes,
+                                             path=int_dir,metrics=['Precision','Recall'])
+        MLP_MODEL.fit(x=X_train,y=Y_train,batch_size=128,epochs=200,verbose=2)
+        MLP_MODEL = ML_utils.Evaluate_Model(MLP_MODEL,X_test,y_test)
+        MLP_MODEL.save(int_dir,save_format='tf')
+
+    CNN = True
+    if CNN == True:
[…]

### 2020-06-05 Instrument_Classifier_v1/INST_FTRS_v1/INST_FTRS_v1_machine_learning_utilities.py

@@ -130,6 +130,7 @@ def Design_Matrix (wavfile_objects,wav_path,int_path,exp_path):
         # Export Spectrogram for Single File
         #Spectrogram = pd.DataFrame(data=Spectrogram)           
         #Spectrogram.to_csv(exp_path+'/spectrograms/'+WAVFILE.name+'.csv')
+        #del(Spectrogram)
 
     os.chdir(int_path)          # return home
     return X.reshape(n_samples,-1)     # rehape feature matrix

### 2020-06-05 Instrument_Classifier_v1/INST_FTRS_v1/INST_FTRS_v1_main.py

@@ -1,7 +1,7 @@
 """
 Landon Buell
 Instrument Classifier v1
-Main Script
+Features - Main Script
 1 June 2020
 """
 

### 2020-06-09 Thesis/MLP Notes/Mutlilayer Perceptron.tex
3 June 2020 (1)
- Regorganized Papers Directory
- Begun paper on signal classification features
- Updates on MLP paper
9 June 2020
- Update to MLP notes
- Update TF MLP model

@@
 
-\section*{Introduction}
+\section{Introduction}
 
@@
 
-\section*{Architectural Considerations}
+\section{Architectural Considerations}
 \paragraph*{}To build a Multilayer Perceptron (MLP), artificial neurons need to be grouped into multiple structures, each called a \textit{layer}.
@@
 
-\section*{Feed-Forward System}
+\section{Feed-Forward System}
 
@@
 We can then express all activations in layer $(l+1)$ by expanding out the sum into a system of linear combinations:
+
 \begin{equation}
@@
 \ENDFOR
-\RETURN pre-activations
-\RETURN final-activations
+\RETURN pre-activations: $\big\{ \vec{z}^{(0)} , \vec{z}^{(1)} , ... , \vec{z}^{(L-2)}  \big\}$
+\RETURN final-activations: $\big\{ \vec{x}^{(1)} , \vec{x}^{(2)} , ... , \vec{x}^{(L-1)}  \big\}$
 \end{algorithmic}
@@
 
-\section*{Back Propagation System}
+\section{Back Propagation System}
 
@@
 The cost, $J$, is a function of the output activations, $\vec{x}^{(L-1)}$ which is in turn a function of $\vec{z}^{L-2}$ in eqn.
-(\ref{activation}) which is in turn a function of both $\hat{W}^{(L-2})$ and $\vec{b}^{(L-2)}$ in eqn.
+(\ref{activation}) which is in turn a function of both $\hat{W}^{(L-2)}$ and $\vec{b}^{(L-2)}$ in eqn.
 (\ref{linear}).
@@
 \label{dW}
-\nabla_{W^{(l)}} \Big[ J \Big] = 
+\nabla_{W^{(l)}} \big[ J \big] = 
 \frac{\partial J}{\partial x^{(l+1)}} \frac{\partial f^{(l)}}{\partial z^{(l)}} \frac{\partial z^{(l)}}{\partial W^{(l)}}
@@
 \label{db}
-\nabla_{b^{(l)}} \Big[ J \Big] = 
+\nabla_{b^{(l)}} \big[ J \big] = 
 \frac{\partial J}{\partial x^{(l+1)}} \frac{\partial f^{(l)}}{\partial z^{(l)}} \frac{\partial z^{(l)}}{\partial b^{(l)}}
@@
 \label{dx}
-\nabla_{x^{(l)}} \Big[ J \Big] = 
+\nabla_{x^{(l)}} \big[ J \big] = 
 \frac{\partial J}{\partial x^{(l+1)}} \frac{\partial f^{(l)}}{\partial z^{(l)}} \frac{\partial z^{(l)}}{\partial x^{(l)}}
@@
 Additionally, the results from eqns.
-(\ref{dW}), (\ref{db}), and (\ref{dx}).
+(\ref{dW}), (\ref{db}), and (\ref{dx}) are all array-like objects.
+Each element is the direction and value of the small change needed to push $J$ to a successively lower value.
+after each element of the gradient vector is computed, we simply add the change given by the gradient to the current value of that entry.
+For all parameters in any layer $l$:
+
+\begin{equation}
+\label{update params}
+\begin{split}
+\hat{W}^{(l)} &= \hat{W}^{(l)} + \alpha \nabla_{W^{(1)}} \big[ J \big] \\
+\vec{b}^{(l)} &= \vec{b}^{(l)} + \alpha \nabla_{b^{(1)}} \big[ J \big] \\
+\end{split}
+\end{equation}
+
+\paragraph*{}Where $\alpha$ is a scalar called the \textit{learning rate}, typically $\alpha \in (0,1)$ \cite{Geron,Petrik}.
+It can be intuitively through of as a step size taken by the model at each back-propagation iteration.
+Larger values of $\alpha$ may cause the model to reach a minimum faster, but also cause a possible \textit{overshoot} or missing the target minimum, while smaller values of $\alpha$ may cause the model to reach a more suitable minimum, at the cost of must greater computational time and resources.
+Often, $\alpha$ can be set to have a dynamic value, allowing for the step size at each iteration for a compromise between computation time and selection of a suitable value.
+The act details on the choice of the learning rate is topic of a different study on \textit{model regularization} techniques \cite{Goodfellow,James}.
+
+\paragraph*{}We can express the back-propagation process with an algorithm that executes the Stochastic Gradient Descent algorithm outlined about.
+Note that this algorithm uses the loss from a single training sample, a practical implementation should include batches of samples.
+This algorithm can only be executable after a forward pass prediction is made.
+
+\begin{algorithm}
+\label{back-prop}
+\caption{Back Propagation System in a fully-connected Multilayer perceptron model for a single sample.}
+\begin{algorithmic}
+
+\REQUIRE Network depth of $L$ layers ,  cost function $J$ , learning rate $\alpha$
+\REQUIRE Objects: $\hat{W}^{(i)}$, $\vec{b}^{(i)}$ from previous feed-forward.
+\REQUIRE Object of activation function derivatices: $\partial\vec{f}^{(i)}$ 
+\REQUIRE Object of final activations by layer: $\vec{x}^{(i)}$ with $i \in [1,1,...,L-2,L-1]$
+\REQUIRE Object of pre-actications by layer: $\vec{z}^{(i)}$ with $i \in [0,1,...,L-3,L-2]$
+\REQUIRE Sample target output $y$ (usually one-hot-encoded)
+
+Array to hold weight updates: $dW \leftarrow \big\{ \big\}$ (\ref{dW}) \\
+Array to hold bias updates: $db \leftarrow \big\{ \big\}$ (\ref{db}) \\
+Compute gradient of $J$ w.r.t output layer $\vec{x}^{(0)}$: \\
+
+$dx \leftarrow \nabla_{y^*} \big[ J(y^*,y) \big]$ \\
+
+\FOR {$l = L-2 , L-3 , ... ,1,0$}
+\item $db^{(l)} \leftarrow dx \odot \partial f^{(l)}\big(z^{(l)}\big)$
+\item $dW^{(l)} \leftarrow db^{(l)} \cdot x^{(l)}$
+\item dW.insert($dW^{(l)}$)
+\item db.insert($db^{(l)}$)
+\item $dx \leftarrow dW^{(l)} db^({l})$
+\ENDFOR
+
+ASSERT: $dW^{(i)}$ has same dimension as $W^{(i)}$ for $i \in [0,1,...,L-3,L-2]$ \\
+ASSERT: $db^{(i)}$ has same dimension as $b^{(i)}$ for $i \in [0,1,...,L-3,L-2]$ \\
+
+\FOR {$l = 0,1,...,L-3,L-2$}
+\item $W^{(i)} \leftarrow W^{(i)} + (\alpha) dW^{(i)}$
+\item $b^{(i)} \leftarrow b^{(i)} + (\alpha) db^{(i)}$
+\ENDFOR
+
+\RETURN Object containing updated weights: $\hat{W}^{(i)}$ with $i \in [1,1,...,L-2,L-1]$
+\RETURN Object containing updated biases: $\hat{b}^{(i)}$ with $i \in [1,1,...,L-2,L-1]$
+
+\end{algorithmic}
+\end{algorithm}
+
+\pagebreak
 
@@
 
-\section*{Summary}
+\section{Summary}
 

### 2020-06-09 Instrument_Classifier_v1/INST_CLF_v1/INST_CLF_v1_main.py

@@ -46,16 +46,17 @@ if __name__ == '__main__':
     Y_train,n_classes = ML_utils.one_hot_encoder(y_train)
     n_samples,n_features = X.shape
 
-    MLP = False
+    MLP = True
     if MLP == True:
         # MLP MODEL
         MLP_MODEL = NN_Models.MLP_Classifier('JARVIS',n_features,n_classes,
                                              path=int_dir,metrics=['Precision','Recall'])
         MLP_MODEL.fit(x=X_train,y=Y_train,batch_size=128,epochs=200,verbose=2)
         MLP_MODEL = ML_utils.Evaluate_Model(MLP_MODEL,X_test,y_test)
+        base_utils.Plot_Confusion(MLP_MODEL,show=True)
         MLP_MODEL.save(int_dir,save_format='tf')
 
-    CNN = True
+    CNN = False
     if CNN == True:
         CNN_MODEL = NN_Models.CNN_2D_Classifier('VISION',n_classes,
                                                 path=int_dir,metrics=['Precision','Recall'])

### 2020-06-10 Thesis/Classification Features/Time-Freq Features.tex
5 June 2020 (3)
- Updated Instrument Classifier
- Finished raw feature extraction
- Exported MLP parameters
- Need to update CNN performance
9 June 2020 (1)
- Updated Features Report

@@
 This can include weather forecasts, year-to-year population of a given demographic, audio information, or economic stock data.
-In the context of audio data, this is generally referred to as a \textit{waveform}
+In the context of audio data, this is generally referred to as a \textit{waveform}.
+Given that time-series data (and all data) stored digitally must contain evenly-spaced, discrete samples, $S$ is used to indicate a signal stored in an array-like object with it's elements $S_i$ (where $i \in \{ 0,1,2,...,N-2,N-1\}$) make up the waveform.
+
+\paragraph*{}Additiona
 
@@
 
-\paragraph*{}Signal \textit{rise time} measures the amount of time it takes for a time-domain signal, $S(t)$, to leave it's steady-state condition and \textit{rise} to a given maximum $\max\big[|S(t)|\big]$.
-Signal \textit{decay time} measures the amount of time it takes for a time-domain signal, $S(t)$, to \textit{decay} from a given maximum value and return to it's steady-state value.
+\paragraph*{}Signal \textit{rise time} measures the amount of time it takes for a time-domain signal, $S$, to leave it's steady-state condition and \textit{rise} to a given maximum $\max\big[|S|\big]$.
+Signal \textit{decay time} measures the amount of time it takes for a time-domain signal, $S$, to \textit{decay} from a given maximum value and return to it's steady-state value.
 Due to the nature of digitally stored audio in both time and amplitude, it may be impossible to find entries in the signal that satisfy exact equilibrium values (usually, $0$).
@@
 \paragraph*{}To account for this, we employ a function within our feature-extraction program that measures the $10\%$ to $90\%$ amplitude rise time, and the subsequent $90\%$ to $10\%$ amplitude decay time.
-This means that we build a function within our feature-extraction program that isolates the produces two array-like objects for each signal.
-The first array will hold the position (or index) of all points that have a value that exceeds $90\%$ of the waveform maximum (counting for negative amplitudes as well).
+This means that we produce two array-like objects for each signal.
+The first array will hold the position (or index) of all points that have a value that exceeds $90\%$ of the waveform maximum (accounting for negative amplitudes as well).
 The second array contains similarly index of values that exceed $10\%$ of the maximum, but not $90\%$.
@@
 \label{Rise-Decay Time}
-\caption{Compute amplitude rise and decay time of a discrete time-domain signal $S(t)$ for aa give lower bound percentage and upper bound percentage.}
+\caption{Compute amplitude rise and decay time of a discrete time-domain signal $S$ for a give lower bound percentage and upper bound percentage.
+Note that this uses a brute-force,loop through the full signal.
+Optimization methods for longer signals are encouraged}
 
@@
 
-\REQUIRE Discrete time series signal: $S$ 
+\REQUIRE Discrete time series signal: $S$ of length $N$
 \REQUIRE Value to consider lower bound percentage (0,1): \textit{low\_bnd}
@@
 
-n\_samples $\leftarrow$ length($S$) \\
 $S \leftarrow |S|$ \\
 max\_amp $\leftarrow$ maximum($S$) \\
+above\_upper $\leftarrow \{ \}$ \\
+above\_lower $\leftarrow \{ \}$ \\
+\FOR {$i = 0,1,2,...,N-2,N-1$}
+\item iterate through time, and add \textit{index values} to respective lists
+\IF {$S_i \geq$ high\_bnd}
+		\STATE above\_upper.insert($i$)
+		\ELSIF {$S_i \leq$ high\_bnd \AND $S_i \geq$ low\_bnd}
+		\STATE above\_lower.insert($i$)
+		\ELSE
+		\STATE continue
+\ENDIF
+\ENDFOR \\
+M $\leftarrow$ $||$ above\_lower$_{(0)}$ - above\_lower$_{(-1)}$ $||$ - Length of active waveform by number of samples \\
+risetime $\leftarrow$ $||$ above\_upper$_{(0)}$ - above\_lower$_{(0)}$ $||$/M - Rise time \\
+decaytime $\leftarrow$ $||$ above\_upper$_{(-1)}$ - above\_lower$_{(-1)}$ $||$/M - Decay time \\
+\RETURN risetime , decaytime
+\end{algorithmic}
+\end{algorithm}
+
+\paragraph*{}Additionally, notice we normalize both rise and decay time with respect to the amount of samples between the initial rise and the final decay.
+We do this to eliminate dependence on absolute sample difference.
+If a signal is truncated, contains excessive quiet time or additional zero-padding, the interpretation of rise/decay time is then changed to a percentage or fraction of total active-waveform time.
+
+% ================================
+
+\subsection{Time-Frames}
+
+\paragraph*{}A \textit{frame} is a unit of time discussed by Khan \& Al-Kathib and Liu.
+\cite{Kahn 2006,Liu 1998}.
+Each frame is a collection of points from a discrete time-series waveform that have been concatenated into a new, smaller object.
+For frames of smaller length, a single waveform can produce hundreds or thousands of frames, where larger frame lengths may only permit dozens of frames from a waveform.
+The idea is to divide a waveform into sections with lower time resolution in order to extract additional features.
+A discrete signal $S$ can be decomposed into frames $s$ such that:
+
+\begin{equation}
+\label{many frames}
+S = \big[ s_0 , s_1 , s_2 , .... , s_{N-2} , s_{N-1} \big]
+\end{equation}
+
+Where a single entry $s_i$ contains a subset of samples from the greater signal $S$, and can function as it's own discrete time-series object.
+Frames can also can also be overlapping or non-overlapping.
+It is recommended to use over-lapping frames when producing a spectrogram-like object or producing some sort of energy-amplitude envelope.
+We outline an algorithm that extracts an array-like object of frames from a signal $S$ using freame of fixed length:
+
+\begin{algorithm}
+\label{Time-Frames}
+\caption{Use discrete signal $S$ to produce an array-like object $X$ of time-frame signals of fixed length.}
+\begin{algorithmic}
+\REQUIRE Discrete time series signal: $S$ of length $N$
+\REQUIRE Number of samples per frame: $k$. Recc. $\log_2(k) \in \mathbb{Z}$
+\REQUIRE Percentage of frame overlap: $L$ with $L \in [0,1)$
+\ENSURE $N/k \in \mathbb{Z}$ - Use zero-padding or truncation. This ensures that no frames are partially filled \\
+dt $\leftarrow k * (1 - L)$ - integer step size \\
+X $\leftarrow \{\}$ - array to hold all frame arrays \\
+
+\FOR {$i = 0$ \textbf{to} $i = (N-k-1)$ \textbf{step} dt}
+	\item Create frame using index $i$ to $i+k$ from signal $S$
+	\STATE frame $\leftarrow \big{\{} S[i:i+k] \big{\}}$ 
+	\STATE X.insert(frame)
+\ENDFOR
+
+\RETURN X
 
@@
 
-% ================================
-
-\subsection{Root-Mean-Square Energy of all Frames}
-
-\paragraph*{}The Root-Mean-Square energy (RMS energy) of a frame is rough approximation of the energy contained within a slice of time of a waveform.
-We refer to a slice of time as a \textit{frame} \cite{Kahn}; where each frame is a subset of sequential samples grouped together.
-When a sequence of frames as concatenated in order that they are produced, they recreate the origina; waveform in it's entirety.`
-
- Using Hooke's Law, we know that the instantaneous energy of an oscillation is proportional to the square of it's amplitude.
-
-\begin{algorithm}
-\label{RMS Energy of Frames}
-\caption{Compute the RMS energy of a collection of frames ith}
-
-\begin{algorithmic}
-
-\REQUIRE Discrete time series signal: $S$ 
-\REQUIRE Value to consider lower bound percentage (0,1): \textit{low\_bnd}
-\REQUIRE Value to consider upper bound percentage (0,1): \textit{high\_bnd}
-\ENSURE low\_bnd $<$ high\_bnd \\
-
-n\_samples $\leftarrow$ length($S$) \\
-$S \leftarrow |S|$ \\
-max\_amp $\leftarrow$ maximum($S$) \\
-
-\end{algorithmic}
-\end{algorithm}
+\paragraph*{}When constructing frames from is signal $S$ of $N$ samples, a designer can choose to use produce a set number of frames, or a set number of sample per frame.
+When choosing a fixed number of frames, $m$, there will be $N/m$ samples in each frame.
+When choosing a fixed number of sample per frame, $k$, there will be $N/k$ frames.
+It is necessary to truncate or pad the signal $S$ such that either $N/m \in \mathbb{Z}$ or $N/k \in \mathbb{Z}$.
+It is important to note that the frames themselves are not classification features, but are a vital step in deriving further classification features.
 
@@
 
-\subsection{Percentage of Frames with RMS Energy above value}
+\subsection{Waveform RMS Energy}
+
+\paragraph*{}The Root-mean-squared energy (RMS)of a waveform can be used to approximate the average power in a waveform using Hooke's Law.
+The RMS of some discrete function $S$ with $N$ samples is given by:
+
+\begin{equation}
+\label{RMS}
+S_{RMS} = \sqrt{\frac{1}{N}\sum_{i=0}^{N-1}S_i^2}
+\end{equation}
 
@@
 
+\paragraph*{}Time-Spectral-Flux (TSF) is a feature proposed by \cite{Kahn 2006}.
+It measures the magnitude of the incremental change between adjacent elements in a given sequence.
+For a discrete signal with unit sample rate, this can be loosely though of as a first-derivative approximation.
+Given a signal $S$ with $N$ samples, the TSF, $\Phi$, will be an array-like object $N-1$ samples.
+The $i$-th sample is given by:
+
+\begin{equation}
+\label{TSF}
+\Phi_{i} = \big( S_{i+1} - S_{i} \big)
+\end{equation}
+
+\paragraph*{}TSF can be used with the raw waveform signal $S$ directly, with time-frame-like objects $X$ or any other time-spectral array.
+Depending on the context, the right side of eqn.
+(\ref{TSF}) can be multiplied by come constant $c$ if values need to be scaled.
+This could be used to normalize the array, or to account for physical properties such as sample rate.
+In some cases, it may be beneficial to compute the magnitude of the difference between adjacent elements.
+Below we show an algorithm to compute TSF:
+
+\begin{algorithm}
+\label{TSF alg}
+\caption{Compute Time-Spectral-Flux $\Phi$ of discrete signal $S$}
+\begin{algorithmic}
+\REQUIRE Discrete time series signal: $S$ of length $N$
+
+$\Phi \leftarrow \{\}$
+\FOR {$i = 0,1,2,...,N-3,N-2$}
+	\STATE $\Phi$.insert($S[i+1] - S[i]$)
+\ENDFOR
+
+Optional: Apply additional functions or scaling. Normalization, scaling, absolute value, etc. can also be used and optimized depending on context \\
+\RETURN $\Phi$
+
+\end{algorithmic}
+\end{algorithm}
+
+\paragraph*{}Physically, TSF describes the frame-by-frame or index-by-index change in the shape of a spectrum.
+Signals containing speech have shown to have higher average spectral flux values than than of musical notes \cite{Kahn 2006,Zhang 1998}.
+Similarly, percussive instruments will demonstrate higher average frame TSF values than instruments that demonstrate greater sustain.
+
 % ================================
+
+\subsection*{Interval of Zero-Crossings}
+
+\paragraph*{}Kahn \& Al-Kathib \cite{Kahn 2006} proposed a feature using the difference of maximum and minimum zero crossing in given time intervals as a feature vector when differentiating between speech and audio.
+This produced a much more distinct decision boundary than an ordinary zero crossing counter.
+Building on this, we count the number of zero crossing in each time-frame $X_i$.
 
@@
 \section{Frequency Series Features}
+
+\paragraph*{}Frequency series features (also called frequency-domain or frequency-space features) are peices of information that can be extracted, derived or otherwise originate from a signal that is expressed with a dependence on frequency.
+This is commonly done when needing to break down a give signal into it's simplest possible constituent frequency \cite{Peatross 2015}.
+We move a discrete signal of length $N$ that is a function of time, $S$, into a signal that is a function of frequency $F$, by applying the \textit{Discrete Fourier Transform} (DFT).
+This produces an array of $N$ complex-values numbers, the $k$-th element is given by:
+
+\begin{equation}
+\label{DFT}
+F_{k} =  \sum_{n=0}^{N-1} S_{n} \cdot e^{-2\pi i\frac{kn}{N}}
+\end{equation}
+
+Where $F$ is an array Similarly, we recover the original time-basis signal $S$ with the \textit{Inverse Discrete Fourier transform} (IDFT). The $k$-th element is given by:
+
+\begin{equation}
+\label{IDFT}
+S_{k} =  \frac{1}{N}\sum_{n=0}^{N-1} F_{n} \cdot e^{-2\pi i\frac{kn}{N}}
+\end{equation}
+
+\paragraph*{}Equations (\ref{DFT}) and (\ref{IDFT}) create a \textit{transform pair}.
 
@@
 
-\subsection{Energy of Signal in Select Frequency Bands}
+\subsection{Energy Spectral Density of Frequency Bands}
+
+\paragraph*{}One of the most defining characteristics of the timbre of a sound is the it's distribution of power in frequency space.
+To do this, we divide a section of frequency space into multiple frequency \textit{banks}.
+Each bank is a subset of frequency space.
+Given the physical properties of vibrating strings, membranes and air columns, we know that successive overtones which appear are large isolated \textit{spikes} in the frequency domain tend to occur at positions that are integer multiples of the fundamental frequency.
+
+\paragraph*{}By dividing frequency space into $k$ unique, non-overlapping banks, we can produce an estimate for the power of a musical instrument in each given band.
+For some signal $S$, represented in a frequency-basis $F$, we can compute the power \textit{energy spectral density} (ESD), $\mathbb{E}$ in the band from frequency $f'_a$ to $f'_b$ as given by:
+
+\begin{equation}
+\mathbb{E} = \sum_{i=f'_a}^{f'_b} |F_i|^2 df
+\end{equation}
+
+To improve numerical accuracy,this direct Reimann Summation can be replaced with a different integration method if desired.
+The resulting real floating-point number is the energy density of that signal in that given frequency band.
+We show an algorithm for computing the energy spectral density in of a frequency-space signal $F$.
+
+\begin{algorithm}
+\label{ESD}
+\caption{Compute energy spectral density of banks in frequency space array $F$}
+\begin{algorithmic}
+\REQUIRE Discrete frequency series signal: $F$ of length $N$
+\REQUIRE Array-like object: $x$, length $N$, maps each index of $F$ to a real-valued frequency bin.
+\REQUIRE Array-like object: $P$, containing $k$ upper bound / lower bound pairs.
+\REQUIRE Integration function, method or operation: \textit{INTG}
+
+\ENSURE $P$ array-object has shape $(k \times 2)$, with format resembling: \\
+$P = \Big[ \{P_{(0,0)},P_{(0,1)}\} , \{P_{(1,0)},P_{(1 ,1)}\} ,  ... , \{P_{(k-1,0)},P{(k-1,1)}\} \Big]$\\
+Where $P_{(i,0)}$ is the lower bound on bank $i$ and $P_{(i,1)}$ is the upper bound on bank $i$.\\
+Initialize array-like object to the the Energy-Spectral-Density (ESD) of each frequency bank: \\
+Bin\_ESDs $\leftarrow \{\}$
+
+\FOR {$i = 0,1,2,...,k-2,k-1$}
+	\item Iterate through each bank pair, find indecies where  
+	\STATE low\_bnd , high\_bnd $\leftarrow$ $P_{(i,0)}$ , $P_{(i,1)}$
+	\STATE idxs $\leftarrow \{ $\textbf{where} $x[j] \geq$ low\_bnd \AND $x[j] \leq$ high\_bnd $\}$
+	\item Use entries in "idx" array to find the energy at the frequency band values, integrate the subset of the array to compute ESD of 
+	\STATE E $\leftarrow \text{INTG}\big[ |F[\text{idxs}|^2 \Big]$
+	\STATE Bin\_ESDs.insert(E)
+\ENDFOR
+
+\RETURN Bin\_ESDs
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 
-\bibitem{Kahn}
+\bibitem{Kahn 2006}
 Khan, M. Kashif Saeed, and Wasfi G. Al-Khatib. “Machine-Learning Based Classification of Speech and Music.” Multimedia Systems, vol. 12, no. 1, 2006, pp. 55–67., doi:10.1007/s00530-006-0034-0.
 
-\bibitem{Short}
+\bibitem{Liu 1998}
+Liu, Zhu, et al.
+“Audio Feature Extraction and Analysis for Scene Classification.” Proceedings of First Signal Processing Society Workshop on Multimedia Signal Processing, 1998, pp.
+61–79., doi:10.1109/mmsp.1997.602659.
+
+\bibitem{Peatross 2015}
+Peatross, Justin, and Michael Ware. \textit{Physics of Light and Optics}. Brigham Young University, Department of Physics, 2015.
+
+\bibitem{Short 2006}
 Short, Garcia, “Signal Analysis Using the Complex Spectral Phase Evolution (CSPE) Method”. Journal of the Audio Engineering Society.
+
+\bibitem{Zhang 1998}
+Zhang, Tong, and C.-C.
+Jay Kuo.
+“Content-Based Classification and Retrieval of Audio.” Advanced Signal Processing Algorithms, Architectures, and Implementations VIII, 2 Oct.
+1998, pp.
+432–443., doi:10.1117/12.325703.
 

### 2020-06-10 Thesis/MLP Notes/Mutlilayer Perceptron.tex
9 June 2020 (1)
- Updated Features Report

@@
 
-\pagebreak
-
 % ================================================================
@@
 \section{Summary}
+
+\paragraph*{}The multilayer perceptron has experimentally shown to be a powerful and versatile problem-solving tool.
+It's layered architecture allows for the system to model complex systems and self-optimize given appropriate training data.
+While it's design is considered elementary when put up against newer network designs, it shows to be a remarkable assert in the field of neural network classifiers.
 

### 2020-06-10 Thesis/Classification Features/Time-Freq Features.tex
10 June 2020
- Updates to Feature Extraction paper

@@
 Given that time-series data (and all data) stored digitally must contain evenly-spaced, discrete samples, $S$ is used to indicate a signal stored in an array-like object with it's elements $S_i$ (where $i \in \{ 0,1,2,...,N-2,N-1\}$) make up the waveform.
-
-\paragraph*{}Additiona
 
@@
 \label{IDFT}
-S_{k} =  \frac{1}{N}\sum_{n=0}^{N-1} F_{n} \cdot e^{-2\pi i\frac{kn}{N}}
+S_{k} =  \frac{1}{N}\sum_{n=0}^{N-1} F_{n} \cdot e^{+2\pi i\frac{kn}{N}}
 \end{equation}
@@
 \subsection{Number of Unique, Isolated Peak}
+
+\paragraph*{}Due to the physical properties of various musical instruments, there are often times when overtones from a pitch are not present in a waveform or the presence is very minuscule when producing the frequency spectrum.
 
@@
 \REQUIRE Array-like object: $P$, containing $k$ upper bound / lower bound pairs.
-\REQUIRE Integration function, method or operation: \textit{INTG}
+\REQUIRE Integration or summation function, method, or operation for array of discrete points: \textit{INTG}
 
@@
 \RETURN Bin\_ESDs
-
 \end{algorithmic}
 \end{algorithm}
+
+\paragraph*{}The resulting array of floating-point numbers gives the energy spectral density distribution of the waveform in that frame of time. By choosing frames boundaries:
+
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+\hline
+\textbf{Bounds} & 	\textbf{Bank 1} & \textbf{Bank 2} & \textbf{Bank 3} & \textbf{Bank 4} & 
+					\textbf{Bank 5} & \textbf{Bank 6} & \textbf{Bank 7} & \textbf{Bank 8}  \\ \hline
+\textbf{Low [Hz]}	& 0		& 32	& 64 & 128 & 256 & 512 & 1024 & 2048  		\\ 	\hline
+\textbf{High [Hz]}	& 32	& 64	& 128 & 256 & 512 & 1024 &  2048 & 6000 	\\	\hline
+\end{tabular}
+\end{center}
+
+These set of banks allow for a reasonable range such that every instrument contains at least one overtone in the frequency-spectrum for any given pitch played.
+This ESD distribution shows to be a valuable set of features for classification.
+Since this is largely what shapes human understanding of timbre, it is reasonable to use emphasise the importance of these features.
 

### 2020-06-18 Thesis/Classification Features/Time-Freq Features.tex
17 June 2020
- Updated Features paper
- Inplemented time-domain features into classification program

@@
 \REQUIRE Percentage of frame overlap: $L$ with $L \in [0,1)$
-\ENSURE $N/k \in \mathbb{Z}$ - Use zero-padding or truncation. This ensures that no frames are partially filled \\
 dt $\leftarrow k * (1 - L)$ - integer step size \\
@@
 
-\FOR {$i = 0$ \textbf{to} $i = (N-k-1)$ \textbf{step} dt}
+\FOR {$i = 0$ \textbf{to} $i = (N-1)$ \textbf{step} dt}
 	\item Create frame using index $i$ to $i+k$ from signal $S$
 	\STATE frame $\leftarrow \big{\{} S[i:i+k] \big{\}}$ 
+	\item If $i+k$ out of range, pad with row of zeroes
 	\STATE X.insert(frame)
 \ENDFOR
-
+\ENSURE $X$ has shape: number of frames $\times$ samples per frame, $k$
 \RETURN X
@@
 
-\paragraph*{}The Root-mean-squared energy (RMS)of a waveform can be used to approximate the average power in a waveform using Hooke's Law.
+\paragraph*{}The Root-mean-squared energy (RMS)of a waveform can be used to approximate the energy in a waveform either by frame of by the full signal.
 The RMS of some discrete function $S$ with $N$ samples is given by:
@@
 
-\paragraph*{}Frequency series features (also called frequency-domain or frequency-space features) are peices of information that can be extracted, derived or otherwise originate from a signal that is expressed with a dependence on frequency.
+\paragraph*{}Frequency series features (also called frequency-domain or frequency-space features) are pieces of information that can be extracted, derived or otherwise originate from a signal that is expressed with a dependence on frequency.
 This is commonly done when needing to break down a give signal into it's simplest possible constituent frequency \cite{Peatross 2015}.
@@
 
-\subsection{Number of Unique, Isolated Peak}
+\subsection{Strength Successive Overtones}
 
-\paragraph*{}Due to the physical properties of various musical instruments, there are often times when overtones from a pitch are not present in a waveform or the presence is very minuscule when producing the frequency spectrum.
+\paragraph*{}Because of the physical properties of many instruments and the behavior of the harmonic series, many instruments exhibit overtones several octaves above it's fundamental frequency.
+Often, these over tones are missing
 
@@
 We show an algorithm for computing the energy spectral density in of a frequency-space signal $F$.
+practical implementations should include averages over a set of arrays $F$, such as a spectrogram-like object.
 
@@
 
-These set of banks allow for a reasonable range such that every instrument contains at least one overtone in the frequency-spectrum for any given pitch played.
+\paragraph*{}These set of banks allow for a reasonable range such that almost every instrument contains at least one overtone in the frequency-spectrum for any given pitch played.Higher pitched instruments such as many woodwinds do not show contain much energy in the lowester three bands, and lower instruments like brass and bass do not show much energy in the higher bands.
 This ESD distribution shows to be a valuable set of features for classification.
-Since this is largely what shapes human understanding of timbre, it is reasonable to use emphasise the importance of these features.
+Since this is largely what shapes human understanding of timbre, it is reasonable to emphasize the importance of these features.
 
@@
 
+\paragraph*{}The spectrogram matrix is a common tool use in signal processing.
+It is a 2D array object where the $x$-axis tracks progression through time, and the $y$-axis tracks progression through frequency.
+It provides a user with information of the instantaneous frequency or frequencies of a signal how those values may evolve with time.
+We can produce an spectrogram by taking repeated Fourier transformations of overlapping frames in time.
+The result is then transposed to match axes equivalently.
+
+\paragraph*{}Once constructed, we treat the spectrogram matrix as a single image, with a label corresponding to it's target value.
+The gray-scale image can be use in conjunction with a convolutional neural network classifier model.
+Since each file may have different number of frames, each image may have a difference width.
+In all cases, the height of each image is identical to preserve the frequency space range chosen.
+The convolution layer operation can handel this accordingly.
+
 % ================================
@@
 
+\paragraph*{}Phase-Space is an $n$-dimension real vector space where each basis vector is given by some function $f$ and it's first $n-1$ derivatives.
+In the case of a 2D phase space, we have the function $f$ providing the $0$-th basis vector and the function's first derivative $f'$ providing the $1$-st basis vector.
+In the case of a waveform or signal $S$ and it's discrete derivative $S'$, Plotting the two against each other provides a 2D visualization of the relationship between instantaneous waveform amplitude and change in amplitude.
+
+\paragraph*{}If the a time-frame of a waveform is used as the function $S$ containing, $N$ samples, then we must compute the derivative of
+
 % ================================
-
-% ================================================================
-
-\section{Additional Features}
 
@@
 
+\bibitem{Sauer 2012}
+Sauer, Timothy. Numerical Analysis. 2nd ed., Pearson, 2012.
+
 \bibitem{Short 2006}

### 2020-06-18 Instrument_Classifier_v0/INST_CLF_v0/Freqspace_Features.py

@@ -15,3 +15,37 @@ import scipy.signal as signal
 import Timespace_Features as time_feats
 
             #### TIME SERIES FEATURES ####
+
+def Frequency_Axis (FILE,npts=4096,low=0,high=6000):
+    """
+    Compute Frequenxy Axis
+    --------------------------------
+    FILE (inst) : file_object instance with file.waveform attribute
+    npts (int) : Number of samples in the axis
+    low (float) : Low value for frequency slice
+    high (float) : High value for frequency bound
+    --------------------------------
+    Return frequency axis array between bounds, f
+        and appropriate index, pts
+    """
+    freq = fftpack.fftfreq(n=npts,d=1/FILE.rate)    # comput freq space
+    pts = np.where((f_space>=low)&(f_space<=high))  # get slices
+    freq = freq[pts]                                # truncate space        
+    return freq,pts                                 # return space & pts
+            
+def Power_Spectrum (FILE,pts=None):
+    """
+    Compute Discrete Fourier Transform of arrays in X
+    --------------------------------
+    X (arr) : array to transform and compute power spectrum
+        either shape (n_frames x n_samples) or (1 x n_samples)
+    pts (iter) : int index values to keep in array 
+    --------------------------------
+    Return Z, array
+    """
+    z = fftpack.fft(FILE.waveform,axis=-1)  
+    Z = np.abs(z)**2    # compute power:
+    if pts != None:     # selection of points:
+        Z = Z[:][pts]   # subset of points
+    return Z            # return DFT matrix
+

### 2020-06-18 Instrument_Classifier_v0/INST_CLF_v0/INST_CLF_MAIN.py

@@ -13,7 +13,6 @@ import sys
 
 import Program_Utilities as prog_utils
 import Plotting_Utilities as plot_utils
-import Preprocessing_Utilities as prep_utils
 import Machine_Learning_Utilities as ML_utils
 import Neural_Network_Models as NN_models
 
@@ -30,8 +29,9 @@ if __name__ == '__main__':
     FILEOBJS = prog_utils.create_fileobjs(trgt_path+'/TARGETS.csv')
 
     # Build X & Y
-    Y,n_classes = prep_utils.construct_targets(FILEOBJS)
-    X = ML_utils.Design_Matrix(FILEOBJS)
+    print("Contructing Design Matrix:")
+    Y,n_classes = ML_utils.construct_targets(FILEOBJS)
+    X = ML_utils.Design_Matrix(FILEOBJS[0:1000:100])
     n_samples,n_features = X.shape
 
     # BUILD NEURAL NETWORK MODELS

### 2020-06-18 Instrument_Classifier_v0/INST_CLF_v0/Machine_Learning_Utilities.py

@@ -8,6 +8,10 @@ Instrument Classifier v0
             #### IMPORTS ####
 
 import numpy as np
+import tensorflow.keras as keras
+import time
+
+import Math_Utilities as math_utils
 import Timespace_Features as time_feats
 import Freqspace_Features as freq_feats
 
@@ -20,10 +24,35 @@ def Assemble_Features (FILE):
     FILE (inst) : file_object instance with file.waveform attribute
     --------------------------------
     Return (1 x N) array of features
-    """
-    FILE = time_feats.rise_decay_time(FILE) # rise & decay 
+    """   
+    frames = time_feats.Frames_fixed_length(FILE)               # create frames   
+    waveform_RMS = math_utils.RMS_Energy(FILE.waveform)         # waveform RMS
+      
+    # Add Time-Domain Features
+    FILE = FILE.add_features(time_feats.rise_decay_time(FILE))          # add rise & decay 
+    FILE = FILE.add_features(waveform_RMS)                              # add RMS for full waveform
+    FILE = FILE.add_features(time_feats.RMS_above(frames,waveform_RMS)) # add % above RMS
+
+    # Add Frequency-Domain Features
     
+
     return FILE                    # return file with feature vector
+
+def construct_targets (fileobjs,matrix=True):
+    """
+    Construct target array object 
+    --------------------------------
+    fileobjs (iter) : List of object instances w/ 'target' attribute
+    matrix (bool) : If true, targets are one-hot-encoded into matrix,
+        else a vector is returned
+    --------------------------------
+    Return target object and nmber of unique classes
+    """
+    y = np.array([x.target for x in fileobjs])  # use target attribute
+    n_classes = len(np.unique(y))               # number of classes
+    if matrix == True:                          # if one-hot-enc
+        y = keras.utils.to_categorical(y,n_classes)
+    return y,n_classes                          # return target & classes
 
 def Design_Matrix (FILE_OBJECTS):
     """
@@ -38,15 +67,11 @@ def Design_Matrix (FILE_OBJECTS):
     n_samples = len(FILE_OBJECTS)   # number of file samples
 
     for I,FILE in enumerate(FILE_OBJECTS):  # iterate through samples
-
-        FILE = FILE.read_audio()            # read .WAV file
-        
-        # Assign features to object instance
-        FILE = Assemble_Features(FILE)
-
-        # Extract feature vector from sample
+        print("\tFile:",FILE.filename)      # Current file
[…]

### 2020-06-18 Instrument_Classifier_v0/INST_CLF_v0/Math_Utilities.py

@@ -1,0 +1,38 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+17 June 2020
+"""
+
+            #### IMPORTS ####
+              
+import numpy as np
+from sklearn.preprocessing import StandardScaler
+
+            #### FUNCTION DEFINITIONS ####
+
+def Scale_X (X):
+    """
+    Apply standard preprocessing scaling to design matrix, X
+    --------------------------------
+    X (arr) : Standard design matrix, shape (n_samples x n_features)
+    --------------------------------
+    Return scaled design matrix
+    """
+    scaler = StandardScaler()   # scalar instance
+    scaler = scaler.fit(X)      # fit frame
+    X_new = scaler.transform(X) # transform
+    return X_new                # return new design matrix
+
+def RMS_Energy (X):
+    """
+    Compute RMS energy of object X along last axis
+        Output contains 1 less dimension
+    --------------------------------
+    X (arr) : Array-like of floats 
+    --------------------------------
+    Return RMS of array X
+    """           
+    RMS = np.sqrt(np.mean(X**2,axis=-1))# compute mean
+    return RMS                          # return 

### 2020-06-18 Instrument_Classifier_v0/INST_CLF_v0/Preprocessing_Utilities.py

@@ -1,47 +1,0 @@
-"""
-Landon Buell
-PHYS 799
-Instrument Classifier v0
-12 June 2020
-"""
-
-            #### IMPORTS ####
-
-import numpy as np
-import tensorflow.keras as keras
-import os
-import sys
-
-from sklearn.preprocessing import StandardScalar
-
-            #### FUNCTION DEFINITIONS ####
-
-def construct_targets (fileobjs,matrix=True):
-    """
-    Construct target array object 
-    --------------------------------
-    fileobjs (iter) : List of object instances w/ 'target' attribute
-    matrix (bool) : If true, targets are one-hot-encoded into matrix,
-        else a vector is returned
-    --------------------------------
-    Return target object and nmber of unique classes
-    """
-    y = np.array([x.target for x in fileobjs])  # use target attribute
-    n_classes = len(np.unique(y))               # number of classes
-    if matrix == true:                          # if one-hot-enc
-        y = keras.utils.to_categorical(y,n_classes)
-    return y,n_classes                          # return target & classes
-
-def Scale_X (X):
-    """
-    Apply standard preprocessing scaling to design matrix, X
-    --------------------------------
-    X (arr) : Standard design matrix, shape (n_samples x n_features)
-    --------------------------------
-    Return scaled design matrix
-    """
-    scalar = StandardScalar()   # scalar instance
-    scalar = scalar.fit(X)      # fit frame
-    X_new = scalar.transform(X) # tranform
-    return X_new                # return new design matrix
-

### 2020-06-18 Instrument_Classifier_v0/INST_CLF_v0/Program_Utilities.py

@@ -35,10 +35,10 @@ class file_object ():
         self.target_str = datarow[2]    # target as str
         dir_tree = self.fullpath.split('/')
         self.filename = dir_tree[-1]    # filename
+        # assign target for design matrix   
+        self.target = self.target_int   # set target value
         self.features = np.array([])    # feature vector
-        # assign target for design matrix
-        self.target = self.assign_target(self.target_int)
-        
+
     def assign_target (self,target):
         """ Assign Target value to instance """
         self.target = target    # set y
@@ -48,7 +48,7 @@ class file_object ():
         """ Read raw data from local path """
         rate,data = sciowav.read(self.fullpath)
         self.rate = rate            # set sample rate
-        data = data.reshape(1,-1)   # flatten waveform
+        data = data.reshape(1,-1).ravel()   # flatten waveform
         self.waveform = data/np.abs(np.max(data))
         self.n_samples = len(self.waveform)
         return self             # return self
@@ -64,7 +64,8 @@ class file_object ():
 
     def __delfeatures__ (self):
         """ Delete all features (Save RAM) """
-        pass
+        del(self.features)      # delete all features from array
+        return self             # return new self
 
             #### FUNCTION DEFINITIONS ####
 

### 2020-06-18 Instrument_Classifier_v0/INST_CLF_v0/Timespace_Features.py

@@ -12,48 +12,10 @@ import scipy.fftpack as fftpack
 import scipy.integrate as integ
 import scipy.signal as signal
 
+import Math_Utilities as math_utils
 import Freqspace_Features as freq_feats
 
             #### TIME SERIES FEATURES ####
-
-def rise_decay_time (FILE,low=0.1,high=0.9):
-    """
-    Extract rise/decay time parameter
-    --------------------------------
-    FILE (inst) : file_object instance with file.waveform attribute
-    --------------------------------
-    Return [risetime,decaytime] feature set
-    """
-    x = np.abs(FILE.waveform)       # extract waveform
-    above_low = np.array([])        # above 10%
-    above_high = np.array([])       # above 90%
-    for i,y in enumerate(x):        # index, value in waveform
-        if (y >= low) and (y <= high):
-            above_low = np.append(above_low,i)      # add index
-        elif (y >= high):
-            above_high = np.append(above_high,i)    # add index
-        else:
-            continue
-    rise = np.abs(above_high[0] - above_low[0])     # rise in samples
-    decay = np.abs(above_high[-1] - above_low[-1])  # decay in samples
-    return FILE.add_features([rise,decay])          # set & return 
-
-def RMS_Energy (X):
-    """
-    compute RMS energy of object X.
-        Output contains 1 less dimension
-    --------------------------------
-    X (arr) : Array-like of floats 
-    --------------------------------
-    Return RMS of array in X
-    """
-    if X.ndim == 1:                 # single dimesnion
-        RMS = np.sqrt(np.means(X))  # compute RMS
-    elif X.ndim > 1:                # more than 1 dim
-        RMS = np.array([])          # hold RMS values
-        for x in X:
-            RMS = np.append(RMS,np.sqrt(np.means(x)))  
-    return RMS
 
 def Frames_fixed_length (FILE,N=4096,overlap=0.75):
     """
@@ -68,14 +30,12 @@ def Frames_fixed_length (FILE,N=4096,overlap=0.75):
     Return [risetime,decaytime] feature set
     """
     frames = np.array([])           # array to hold time frames
-    step = N*(1-overlap)            # steps between frames
+    step = int(N*(1-overlap))       # steps between frames
     for I in range(0,FILE.n_samples,step):  # iter through wave form
-        try:                            # attempt to create frame
-            x = FILE.waveform[I:I+N]    # create single frame
-        except IndexError:              # index out of bounds  ?          
[…]

### 2020-07-31 Thesis/Source & Citations/Citations.tex
30 July 2020
- Cleaned up REPO
- Deleted excess files
- Added citations files

% ================================
% Landon Buell
% Kevin Short
% Physics 799%
% 30 July 2020 
% ================================

\documentclass[12pt,letterpaper]{article}
\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}

\begin{document}

% ================================================================

\begin{thebibliography}{9}
\bibliographystyle{apalike}

\bibitem{Geron}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. O'Reilly, 2017.

\bibitem{Geron2}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. 2nd ed., O'Reilly, 2019.

\bibitem{Goodfellow}
Goodfellow, Ian, et al.\textit{Deep Learning}. MIT Press, 2017.

\bibitem{James}
James, Gareth, et al. \textit{An Introduction to Statistical Learning with Applications in R}. Springer, 2017.

\bibitem{Kahn}
Khan, M. Kashif Saeed, and Wasfi G. Al-Khatib. “Machine-Learning Based Classification of Speech and Music.” Multimedia Systems, vol. 12, no. 1, 2006, pp. 55–67., doi:10.1007/s00530-006-0034-0.

\bibitem{Levine}
Levine, Daniel S. \textit{Introduction to Neural and Cognitive Modeling}. 3rd ed., Routledge, 2019.

\bibitem{Liu}
Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classiﬁcation." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.

\bibitem{Loy}
Loy, James , \textit{Neural Network Projects with Python}. Packt Publishing, 2019

\bibitem{McCulloch}
McCulloch, Warren S., and Walter Pitts. "A Logical Calculus of the Ideas Immanent in Nervous Activity." \textit{The Bulletin of Mathematical Biophysics}, vol. 5, no. 4, 1943, pp. 115–133.

\bibitem{Mierswa}
Mierswa, Ingo, and Katharina Morik. "Automatic Feature Extraction for Classifying Audio Data." \textit{Machine Learning}, vol. 58, no. 2-3, 2005, pp. 127–149., doi:10.1007/s10994-005-5824-7.

\bibitem{Peatross}
Peatross, Justin, and Michael Ware. \textit{Physics of Light and Optics.} Brigham Young University, Department of Physics, 2015.

\bibitem{Petrik}
Petrik, Marek. "Introduction to Deep Learning." Machine Learning. 20 April. 2020, Durham, New Hampshire.

\bibitem{Short}
Short, K. and Garcia R.A. 2006. "Signal Analysis Using the Complex Spectral Phase Evolution (CSPE) Method." AES: \textit{Audio Engineering Society Convention Paper}.

\bibitem{Virtanen}
Virtanen, Tuomas, et al. \textit{Computational Analysis of Sound Scenes and Events.} Springer, 2018.

\bibitem{Zhang}
Zhang, Tong, and C.-C. Jay Kuo. “Content-Based Classification and Retrieval of Audio.” \textit{Advanced Signal Processing Algorithms, Architectures, and Implementations VIII}, 2 Oct. 1998, pp. 432–443., doi:10.1117/12.325703.

\end{thebibliography}

% ================================================================

\end{document}

### 2020-07-31 Planar_Data/InputTrainingData_Planar_w_Noise.py

@@ -1,345 +1,0 @@
-import numpy as np
-from mpl_toolkits import mplot3d
-from matplotlib import pyplot as plt
-plt.ion()
-ax = plt.axes(projection="3d")
-
-
-#This program implements a single neuron of a neural net.  The structure is 3 inputs to a single node to a single output.
-#Code is based on example presented at: https://urldefense.proofpoint.com/v2/url?u=https-3A__medium.com_themlblog_a-2Dsimple-2Dneural-2Dnetwork-2Dwith-2Da-2Dsingle-2Dneuron-2D8a4e3b0a4148&d=DwIGAg&c=c6MrceVCY5m5A_KAUkrdoA&r=MqWbypA6xJWFEpQLXyroUCv17OsLpWNnvZ1UzmavYE8&m=v7kMgQh71qyhs8GJRQBuFBkdH0YZzQ7h7s0L126B7qY&s=xv5Z06ECMGNc33BZsJIbrCeH7reJ_obzCaT3dfqEYl8&e= 
-#    x1
-#     \
-#      \
-#        --->  |^^^|
-#   x2 ----->  |   |------> Output
-#        --->  |___|
-#       /
-#      /
-#    x3
-#
-# 
-# %Actually, make the data planar data with noise
-#Data was created in Matlab as follows:
-#A = 0.3; B=0.4; C=0.5; nnoise=randn(1,100);max(nnoise),min(nnoise)
-#xx = rand(1,100); y = rand(1,100);
-#[max(xx),min(xx),max(yy), min(yy)]
-#xx = rand(1,100); yy = rand(1,100);
-#[max(xx),min(xx),max(yy), min(yy)]
-#xx=10*xx;yy=10*yy;
-#zz = A + B*xx+C*yy + 0.01*nnoise;
-#plot3(xx,yy,zz)
-#plot3(xx,yy,zz,'.')
-
-
-
-train_inputs = np.array([[ 1, 6.819719 , 0.942293  ], 
-
-[ 1, 0.424311 , 5.985237  ], 
-
-[ 1, 0.714455 , 4.709243  ], 
-
-[ 1, 5.216498 , 6.959493  ], 
-
-[ 1, 0.967300 , 6.998878  ], 
-
[…]

### 2020-07-31 Planar_Data/planar_data_fit_v0.py

@@ -1,107 +1,0 @@
-"""
-Landon Buell
-Kevin Short
-Plane of Best Fit + Noise v0
-29 March 2020
-"""
-
-            #### IMPORTS ####
-
-import numpy as np
-import pandas as pd
-import time
-
-from sklearn.neural_network import MLPRegressor
-from sklearn.metrics import mean_squared_error
-
-import InputTrainingData_Planar_w_Noise as planardata
-
-            #### FUNCTIONS ####
-
-def percent_errors (approx,exact):
-    """ Compute the percent error of arrays """
-    return (approx - exact)/exact
-
-def scale_matrix (matrix):
-    """ Normalize Columns of matrix s.t. max(col) = 1 """
-    if matrix.ndim > 1:                 # more than 1D
-        matrix = np.transpose(matrix)   # transpose
-        for row in matrix:              # each row
-            row = row/np.max(row)       # divide row by maximum of row
-        return matrix.transpose()       # return the transpose
-    else:
-        matrix = matrix/np.max(matrix)  # divide by max
-        return matrix
-
-def testing_data (N_samples,scale=True):
-    """ Create sample of 'true' data based on linear equation """
-    x = np.random.random(size=N_samples)
-    y = np.random.random(size=N_samples)
-    c = np.ones(N_samples)
-    features = np.array([c,x,y]).transpose()
-    targets = 0.3 + 0.4*x + 0.5*y
-    if scale == True:
-        features = scale_matrix(features)
-        targets = scale_matrix(targets)
-    return features,targets
-
-if __name__ == '__main__':
-
-    # Load in datasets
-    X_train = planardata.train_inputs
-    y_train = planardata.train_outputs.ravel()
-
-    X_train = scale_matrix(X_train)     # scale the training data
-    y_train = scale_matrix(y_train)     # scale the training data
-
-    output_matrix = np.array([])        # this will be written out to CSV
-
-    N_iters = 100
-
-    for I in np.arange(0,N_iters,1):
-        # Create & Fit sklearn MLP Regressor
-        t_0 = time.process_time()
-        MLP_Reg = MLPRegressor(hidden_layer_sizes=(),activation='relu',
-                               solver='sgd',max_iter=1000,tol=1e-4,
-                               random_state=None)
-        t_0 = time.process_time()
-        MLP_Reg.fit(X_train,y_train)
-        t_f = time.process_time()
-
-        # Test the model
[…]

### 2020-08-30 Thesis/Sections/TheNerualNetwork.tex
30 August 2020
- Created Nueral network Section of paper

% ================================
% Landon Buell
% Kevin Short
% Physics 799%
% 30 July 2020 
% ================================

\documentclass[12pt,letterpaper]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{graphicx}
\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}

\begin{document}

% ================================================================

\section{The Neural Network}
\label{sec-TheNeuralNetwork}

% ================================================================

\subsection{An Introduction to Neural Networks}

\paragraph*{}In the present age, some problems have shown themselves to be increasingly difficult to solve through conventional computer programs. The challenge arose as to how to build some sort of computer program that could function at a level above general procedural or explicit instructional rules. Rather than \textit{hard-coding} a set of conditions or parameters for an algorithm, we seek an architecture that allows for a computer to \textit{learn} and change and update itself as it is presented with more data. Such an algorithm exists in the form of a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine}.

\paragraph*{}Former YouTube video Classification team lead, and current Machine Learning consultant, Aurelien Geron writes \cite{Geron}: 
\begin{quote}
Birds inspired us to fly, burdock plants inspired velcro and nature has inspired many other inventions. It seems only logical, then, to look to the brain's architecture for inspiration on how to build an intelligent machine.
\end{quote}
The result of such an analogy is a computer program that is structured like the brain. Typically, a computer program is simply a set of mathematical or logical instructions given to a computer to execute. In 1943, Neuroscientist Warren McCulloch and Mathematician Walter Pitts published a paper \cite{McCulloch} which began to pave the way for developing such a mathematical model of the brain \cite{Geron,Goodfellow,Loy}.

% ================================================================

\subsection{The Structure of a Neural Network}

\paragraph*{}A Neural Network is simply a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Geron,Loy}. Each layer represents an operation that takes some real input, typically an array of real double-precision floating-point numbers, and returns a modified array of new double-precision floating-point numbers. The exact nature of this operation can be very different depending on the layer type or where it sits within the network. It is this process of transforming inputs successively in a particular order until an output is attained \cite{Geron,Loy}. This output encodes the models final "decision" given a unique input.

\paragraph*{}A network model that contains $L$ unique layers is said to be an $L$-Layer Neural Network that are usually index with a superscipt, $0$ through $L-1$. Layer $0$ is said to be the \textit{input layer} and layer $L-1$ is said to be the \textit{output layer}. The function that represents a layer $(l)$ is given by 
\begin{equation}
\label{eqn-LayerFunction}
f^{(l)} : x \in \mathbb{R} \rightarrow y \in \mathbb{R}
\end{equation}
The value of $x$ can also be index by layer, we call the array $x^{(l)}$ the \textit{activations} of layer $l$.

\paragraph*{}The the model is recursive by nature, the activations from one layer, $l-1$, are used to directly produce the activations of the next successive layer $l$. Thus eqn. (\ref{eqn-LayerFunction}) can be alternatively written as:
\begin{equation}
\label{eqn-altLayerFunction}
f^{(l)} : x^{(l-1)} \in \mathbb{R} \rightarrow x^{(l)} \in \mathbb{R}
\end{equation}
The array of activations, $x^{(0)}$, is the raw input given the neural network, most commonly called \textit{features}. Conversely, the activations $x^{(L-1)}$ are commonly called the network \textit{output} \cite{Geron,James,Loy}.

% ================================================================

\subsection{Layers Used in Classification Neural Network}

\paragraph*{}As stated previously, a neural network is composed of a series of functions that are called successively to transform features (an input) into a prediction (an output). As shown in eqn. (\ref{eqn-altLayerFunction}), each function feeds directly into the next as to form a sort of computational graph \cite{Goodfellow}.

\paragraph*{}Typically, a layer function can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation. Many feed-forward network layers follow this structure. Step (i.) is usually in the form of a matrix-vector equation:
\begin{equation}
\label{eqn-matVectEqn}
z^{(l)} = W^{(l)} x^{(l-1)} + b^{(l)}
\end{equation}
Where $W^{(l)}$ is the \textit{weighting-matrix} for layer $l$, $b^{(l)}$ is the \textit{bias-vector} for layer $l$, $z^{(l)}$ are the \textit{linear-activations} for layer $l$ and $x^{(l-1)}$ is the final activations for layer $l-1$.
Step (ii.) is usually given by some \textit{activation function}:
\begin{equation}
\label{eqn-elementActivation}
x^{(l)} = \sigma^{(l)} \big[ z^{(l)} \big]
\end{equation}
Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-matVectEqn}). $\sigma^{(l)}$ is some activation function, which is often use to enable the modeling of more complex-decision boundaries.

Below, we discuss and describe the types of layer functions that are used to produce the classification model in this project.

\subsubsection{Dense Layer}

\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer for short, was one of the earliest function types used in artificial neural network models. A dense layer is simply composed of a layer of \textit{artifical neurons}, each of which holds a numerical value within it, called the \textit{activation} of that neuron. This idea was developed back from McCulloch and Pitts' work \cite{McCulloch}, and was expanded upon by Frank Rosenblatt in  1957 \cite{Geron}.

\paragraph*{}We model a layer of neurons as a vector of floating-point numbers. Typically, it is required that the array be one-dimensional. Suppose a layer $(l)$ contains $n$ artificial neurons. We denote the array that hold those activations as $x^{(l)}$ and is given by:
\begin{equation}
\label{layer-DenseNeurons}
\vec{x}^{(l)} = \Big[ x_0, x_1, x_2, \hdots , x_{n-2}, x_{n-1} \Big]^T
\end{equation}
The activation of each entry is given by a linear-combination of activations from the previous layer, as outlined in eqn.(\ref{eqn-matVectEqn}) and eqn.(\ref{eqn-elementActivation}).

\paragraph*{}Suppose the layer $l-1$ contains $m$ neurons. Then the weighting-matrix, $W^{(l)}$ has shape $m \times n$, the bias-vector $b^{(l)}$ has shape $m \times 1$.
Thus for a dense layer $l$, the exact values of each activation is given by \cite{Geron,Loy}
\begin{equation}
\begin{bmatrix}
x_0 \\ x_1 \\ \vdots \\ x_{n-1}
\end{bmatrix}^{(l)} =
\sigma^{(l)} \Bigg(
\begin{bmatrix}
w_{0,0} & w_{0,1} & \hdots & w_{0,m-1} \\
w_{1,0} & w_{1,1} & \hdots & w_{1,m-1} \\
\vdots & \vdots & \ddots & \vdots  \\
w_{n-1,0} & w_{n-1,1} & \hdots & w_{n-1,m-1} 
\end{bmatrix}^{(l)} 
\begin{bmatrix}
x_0 \\ x_1 \\ \vdots \\ x_{m-1}
\end{bmatrix}^{(l-1)}
\begin{bmatrix}
b_0 \\ b_1 \\ \vdots \\ b_{n-1}
\end{bmatrix}^{(l)} \Bigg)
\end{equation}
or more compactly:
\begin{equation}
\label{eqn-DenseFeedForward}
x^{(l)} = \sigma^{(l)} \Big( W^{(l)} x^{(l-1)} + b^{(l)} \Big)
\end{equation}
Eqn. (\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}.

\subsubsection{2-Dimensional Convolution Layer}

\subsubsection{2-Dimensional Maximum Pooling Layer}

\subsubsection{1-Dimensional Flattening Layer}

\paragraph*{}A flattening layer is used to compress an array with two or more dimensions down into a single dimension. For a flattening layer $l$, multidimensional activations in layer $l-1$ are compressed down into a single dimensional array. We can use function notation to express this as:
\begin{equation}
\label{eqn-FlattenFunction}
f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(M \times N \times ....)} \rightarrow
x^{(l)} \in \mathbb{R}^{(MN...\times 1)}
\end{equation}
The numerical value of each activation is left unchanged. For a layer with activation shape$N \times M$, the resulting activations are reshaped into $NM \times 1$ as shown in eqn (\ref{eqn-FlattenFunction}).

\paragraph*{}Flattening Layer are most commonly used to prepare activations for entry into dense layer or series of dense layers. For example, 2D or 3D images are typically processed with 2D convolution, which may output a 2D or 3D array of activations. Those values are then flattened to 1 dimensions, which can then be passed into dense layers for further processing.

\subsubsection{1-Dimensional Concatenation Layer}

% ================================================================

\subsection{Training a Neural Network}

% ================================================================

\subsection{Chosen Model Architecture}

% ================================================================

% ================================================================

\newpage

\begin{thebibliography}{9}
\bibliographystyle{apalike}

\bibitem{Geron}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. O'Reilly, 2017.

\bibitem{Geron2}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. 2nd ed., O'Reilly, 2019.

\bibitem{Goodfellow}
Goodfellow, Ian, et al.\textit{Deep Learning}. MIT Press, 2017.

\bibitem{James}
James, Gareth, et al. \textit{An Introduction to Statistical Learning with Applications in R}. Springer, 2017.

\bibitem{Kahn}
Khan, M. Kashif Saeed, and Wasfi G. Al-Khatib. “Machine-Learning Based Classification of Speech and Music.” Multimedia Systems, vol. 12, no. 1, 2006, pp. 55–67., doi:10.1007/s00530-006-0034-0.

\bibitem{Levine}
Levine, Daniel S. \textit{Introduction to Neural and Cognitive Modeling}. 3rd ed., Routledge, 2019.

\bibitem{Liu}
Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classification." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.

\bibitem{Loy}
Loy, James , \textit{Neural Network Projects with Python}. Packt Publishing, 2019

\bibitem{McCulloch}
McCulloch, Warren S., and Walter Pitts. "A Logical Calculus of the Ideas Immanent in Nervous Activity." \textit{The Bulletin of Mathematical Biophysics}, vol. 5, no. 4, 1943, pp. 115–133.

\bibitem{Mierswa}
Mierswa, Ingo, and Katharina Morik. "Automatic Feature Extraction for Classifying Audio Data." \textit{Machine Learning}, vol. 58, no. 2-3, 2005, pp. 127–149., doi:10.1007/s10994-005-5824-7.

\bibitem{Peatross}
Peatross, Justin, and Michael Ware. \textit{Physics of Light and Optics.} Brigham Young University, Department of Physics, 2015.

\bibitem{Petrik}
Petrik, Marek. "Introduction to Deep Learning." Machine Learning. 20 April. 2020, Durham, New Hampshire.

\bibitem{Short}
Short, K. and Garcia R.A. 2006. "Signal Analysis Using the Complex Spectral Phase Evolution (CSPE) Method." AES: \textit{Audio Engineering Society Convention Paper}.

\bibitem{Virtanen}
Virtanen, Tuomas, et al. \textit{Computational Analysis of Sound Scenes and Events.} Springer, 2018.

\bibitem{Zhang}
Zhang, Tong, and C.-C. Jay Kuo. “Content-Based Classification and Retrieval of Audio.” \textit{Advanced Signal Processing Algorithms, Architectures, and Implementations VIII}, 2 Oct. 1998, pp. 432–443., doi:10.1117/12.325703.

\end{thebibliography}

% ================================================================

\end{document}

### 2020-08-31 Thesis/Sections/TheNerualNetwork.tex
31 August 2020
- Progress on written Thesis
- Neural Network section

@@
 
+\paragraph*{}A neural network is a mathematical function that seeks to produce an approximation $F^*$, of some unknown function $F$.
+For example, in a $k$-classes classifications setting, a network model is provided with some input array $x$ and tasked to map it to a particular categorical output $0$ through $k-1$, using a set of parameters, $\Theta$ \cite{Goodfellow,James}.
+During a period of training, a model is presented with sample inputs $x$, an expected output $y$, and optimizes the parameters of the set $\Theta$ in order to produce the approximated prediction, $y^*$ which maps to one of $k$ outputs.
+
 \paragraph*{}Former YouTube video Classification team lead, and current Machine Learning consultant, Aurelien Geron writes \cite{Geron}: 
@@
 \end{quote}
-The result of such an analogy is a computer program that is structured like the brain.
+The result of such an analogy is a computer program that is reminiscent of the brain.
 Typically, a computer program is simply a set of mathematical or logical instructions given to a computer to execute.
 In 1943, Neuroscientist Warren McCulloch and Mathematician Walter Pitts published a paper \cite{McCulloch} which began to pave the way for developing such a mathematical model of the brain \cite{Geron,Goodfellow,Loy}.
+This model has been adapted over the last few decades to be able to produce an model that can functionally teach itself how to solve a very particular problem.
 
@@
 
-\paragraph*{}A network model that contains $L$ unique layers is said to be an $L$-Layer Neural Network that are usually index with a superscipt, $0$ through $L-1$.
+\paragraph*{}Other than inspiration from the brain, Neural Networks are name \textit{networks} because of their nested composition nature.
+The model can be represented by a linear or acyclic graphs which successively maps exactly how the repeated composition is structured.
+In a \textit{feed-forward network}, information is passes successively in one direction.
+For example functions could be chained together such as \cite{Goodfellow}
+\begin{equation}
+\label{eqn-FunctionChain}
+F(x) = f^{(L-1)}\big[f^{(L-2)}\big[...f^{(1)}\big[f^{(0)}\big[x]\big]\big]...\big]\big]
+\end{equation}
+Where each function $f^{(l)}$ represents a layer of the network model.
+The number of layers in a neural network is referred to as the network \textit{depth}.
+The dimensionality of each layer is referred to as the network \textit{width} \cite{Geron,Loy}.
+
+\paragraph*{}A network model that contains $L$ unique layers is said to be an $L$-Layer Neural Network, with each layer usually indexed by a superscipt, $0$ through $L-1$.
 Layer $0$ is said to be the \textit{input layer} and layer $L-1$ is said to be the \textit{output layer}.
@@
 \end{equation}
-The value of $x$ can also be index by layer, we call the array $x^{(l)}$ the \textit{activations} of layer $l$.
+The value of $x$ can also be index by layer, we call the array $x^{(l)}$ the \textit{activations} of layer $l$ \cite{Goodfellow,Loy}.
 
-\paragraph*{}The the model is recursive by nature, the activations from one layer, $l-1$, are used to directly produce the activations of the next successive layer $l$.
+\paragraph*{}The model is recursive by nature, the activations from one layer, $l-1$, are used to directly produce the activations of the next successive layer $l$.
 Thus eqn.
@@
 
+\paragraph*{}A neural network's job is to produce an approximation of some function $F$, which we call $F^*$.
+The model must have a procedure for updating the parameters in $\Theta$ to allow for a reasonable approximation of $F$.
+To better understand this, we turn to Tom Mitchell's explanation of a learning algorithm \cite{Goodfellow,Mitchell}:
+\begin{quote}
+A computer program is said to learn from experience $E$ with respect to some class of tasks $T$ and performance measure $P$, if it's performance at tasks in $T$, as measured by $P$, improves with experience $E$.
+\end{quote}
+
 % ================================================================
@@
 
+\bibitem{Mitchell}
+Mitchell, Tom Michael. Machine Learning. 1st ed., McGraw-Hill, 1997.
+
 \bibitem{Peatross}

### 2020-09-03 Thesis/Source & Citations/Citations.tex
31 August 2020
- Progress on written Thesis
- Neural Network section
2 Sept 2020
- Updates to Neural Network Section of Thesis
- Added new citations

@@
 \bibitem{Liu}
-Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classiﬁcation." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.
+Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classification." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.
 
@@
 Mierswa, Ingo, and Katharina Morik. "Automatic Feature Extraction for Classifying Audio Data." \textit{Machine Learning}, vol. 58, no. 2-3, 2005, pp. 127–149., doi:10.1007/s10994-005-5824-7.
+
+\bibitem{Mitchell}
+Mitchell, Tom Michael. Machine Learning. 1st ed., McGraw-Hill, 1997.
+
+\bibitem{Olsen}
+Olson, Harry E. \textit{Music, Physics and Engineering}. 2nd ed., Dover Publications, 1967.
 
@@
 
+\bibitem{White}
+White, Harvey Elliott, and Donald H. White. \textit{Physics and Music: the Science of Musical Sound}. Dover Publications, Inc., 2019.
+
 \bibitem{Zhang}

### 2020-09-05 Thesis/Sections/TheNerualNetwork.tex

@@
 \usepackage{graphicx}
+\usepackage{xcolor}
 \usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}
@@
 
-\paragraph*{}In the present age, some problems have shown themselves to be increasingly difficult to solve through conventional computer programs.
-The challenge arose as to how to build some sort of computer program that could function at a level above general procedural or explicit instructional rules.
-Rather than \textit{hard-coding} a set of conditions or parameters for an algorithm, we seek an architecture that allows for a computer to \textit{learn} and change and update itself as it is presented with more data.
+\paragraph*{}The task of algorithmically matching sound files to musical instrument classes in exceedingly difficult through conventional computer programming techniques.
+Because of the complexity of soundwaves, and human ears and brains interpret them, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
+Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an architecture that allows for a computer to \textit{learn} and change and update itself as it is presented with more data.
 Such an algorithm exists in the form of a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine}.
 
-\paragraph*{}A neural network is a mathematical function that seeks to produce an approximation $F^*$, of some unknown function $F$.
-For example, in a $k$-classes classifications setting, a network model is provided with some input array $x$ and tasked to map it to a particular categorical output $0$ through $k-1$, using a set of parameters, $\Theta$ \cite{Goodfellow,James}.
-During a period of training, a model is presented with sample inputs $x$, an expected output $y$, and optimizes the parameters of the set $\Theta$ in order to produce the approximated prediction, $y^*$ which maps to one of $k$ outputs.
+\paragraph*{}A neural network is a mathematical function that seeks to produce an approximation $F^*$, of some usually unknown function $F$ .
+For audio recognition, $F$ is some function, or series of functions, that occurs in the brain which allows for a listener to take the sensation of audio, and map it to a known musical instrument.
+For a neural network, a model must construct an approximate function $F^*$ using a set of parameters $\Theta$, which allows the model to map a series of inputs, $x$ (called \textit{features}) to a series of outputs, $y$ (called \textit{predictions}) \cite{Goodfellow,James,Virtanen}.
 
-\paragraph*{}Former YouTube video Classification team lead, and current Machine Learning consultant, Aurelien Geron writes \cite{Geron}: 
+\paragraph*{}Former YouTube video Classification team lead, and current Machine Learning consultant, Aurelien Geron writes about the relationship between biological brains and mathematical neural networks \cite{Geron}:
 \begin{quote}
@@
 The result of such an analogy is a computer program that is reminiscent of the brain.
-Typically, a computer program is simply a set of mathematical or logical instructions given to a computer to execute.
-In 1943, Neuroscientist Warren McCulloch and Mathematician Walter Pitts published a paper \cite{McCulloch} which began to pave the way for developing such a mathematical model of the brain \cite{Geron,Goodfellow,Loy}.
-This model has been adapted over the last few decades to be able to produce an model that can functionally teach itself how to solve a very particular problem.
+
+\paragraph*{}Over the course of their lives, humans will learn to map sounds to sources almost effortlessly.
+Given a sample of sound, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olsen,White}.
+Similarly, a neural network uses features of a sound, represented by an array $x$, and learns a series of parameters, $\Theta$, that allow it to map those features to one or more pre-defined sources \cite{Virtanen}.
+
+\paragraph*{}For this particular project, a neural network has been constructed to perform a  \textit{classification} task.
+A classification task involves mapping the input data, $x$ to one of $k$ possible \textit{classes}, each represented by an integer, $0$ through $k-1$.
+Each of the $k$ classes represents a particular musical instrument that could have produced the sound-wave in the audio file.
 
@@
 
+\newpage
+
 \subsection{The Structure of a Neural Network}
 
-\paragraph*{}A Neural Network is simply a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Geron,Loy}.
+\paragraph*{}A Neural Network is simply a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Goodfellow,Loy}.
 Each layer represents an operation that takes some real input, typically an array of real double-precision floating-point numbers, and returns a modified array of new double-precision floating-point numbers.
@@
 \paragraph*{}Other than inspiration from the brain, Neural Networks are name \textit{networks} because of their nested composition nature.
-The model can be represented by a linear or acyclic graphs which successively maps exactly how the repeated composition is structured.
+The model can be represented by a linear or acyclic computational graph which successively maps exactly how the repeated composition is structured.
 In a \textit{feed-forward network}, information is passes successively in one direction.
@@
 
+\newpage
+
 \subsection{Layers Used in Classification Neural Network}
@@
 \paragraph*{}Typically, a layer function can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation.
-Many feed-forward network layers follow this structure.
+This activation function typically is a non-linear function which allows for the modeling of increasingly complex decision-boundaries.
 Step (i.) is usually in the form of a matrix-vector equation:
@@
 
-Below, we discuss and describe the types of layer functions that are used to produce the classification model in this project.
+\paragraph*{}Below, we discuss and describe the types of layer functions that are used to produce the classification model in this project.
+
+% ================
 
@@
 
+% ================
+
 \subsubsection{2-Dimensional Convolution Layer}
 
+% ================
+
 \subsubsection{2-Dimensional Maximum Pooling Layer}
+
+% ================
 
@@
 
+% ================
+
 \subsubsection{1-Dimensional Concatenation Layer}
@@
 % ================================================================
+
+\newpage
 
@@
 
+\newpage
+
 \subsection{Chosen Model Architecture}
+
+\paragraph*{}The success of a neural network algorithm is enormously dependent of the strength of the chosen features, rather than the quantity of available data \cite{Geron,Khan,Liu}.
+We have derived an appropriate set of inputs arrays \textit{[See Section on Features]}, and constructed a neural network architecture to compliment these features.
+
+\paragraph*{}The full classification neural network used for this project consists of two distinct entry points.
+This means that rather than presenting the network with one set of input data, $X$, we present the network with two different arrays, $X_1$ and $X_2$.
+Both arrays are a produce of the same audio file sound wave, and thus share a common training label.
+Each of the two entry points feed into their own, non-related set of layer functions.
+The second-to-last layer, the outputs from both neural networks are concatenated into a single dense layer, which is then passed into the output layer, which contains $k$ neurons, one of reach unique class \cite{Loy,Geron}.
+A visual representation of this architecture can be found in fig.
+(\ref{fig-NetworkArchitecture}).
+
+\begin{figure}[H]
+\label{fig-NetworkArchitecture}
+\begin{center}
+\includegraphics[scale=0.45]{../Figures/NeuralNetworkArchitecture}
+\end{center}
+\caption{The developed architecture of the audio file classification neural network.
+The Left branch process an image-like input, the right branch processes a vector-like input.
+The activations are then merged, and then a single output is produced}
+\end{figure}
+
+% ================
+
+\subsubsection{The Spectrogram Branch}
+
+\paragraph*{}The spectrogram branch is pictured on the left side of fig.
+(\ref{fig-NetworkArchitecture}).
+A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olsen,Kahn}.
+\textcolor{blue}{Details on the creating of the spectrogram can be found in the \textit{features} section of this document.}
+
+\paragraph*{}The input layer of the spectrogram accepts a 4-Dimensional array.
+The axes, in order of indexing, represents (i) the size of the \textit{mini-batch} of samples, (ii) the pixel width of each sample, (iii) the pixel height of each sample, and (iv) the number of channels in each sample.
+As a model hyper-parameter, we have chosen each batch to contain $64$ samples.
+We have also chosen to truncate time and frequency axes (ii \& iii) to contain $560$ frequency bins, and $256$ time-frames.
+Each image also contains a single channel, which make it gray-scale when visualized.
+We can denote the 4D shape of the input object into this branch as:
+\begin{equation}
+\label{eqn-shapeX1}
+X_1 \in \mathbb{R}^{(64 \times 560 \times 256 \times 1)}
+\end{equation}
+Any other shape will be rejected by the model, and an error is raised.
+
+\paragraph*{}After the input layer assert the appropriate shape, the array $X_1$, which is a collection of $64$ spectrograms, is passed into the first of three \textit{Convolution Layer Groups}.
+These layer groups are inspired from the \textit{VGG-16 Neural Network} architecture \textcolor{red}{[citation needed]}.
+Each convolution layer group in composed of three individual layers:
+\begin{enumerate}
+\item A 2-Dimensional Convolution layer, using $32$ filters, a $3 \times 3$ kernel, a $1 \times 1$ step size, and a ReLU activation function,
+\item A 2-Dimensional Convolution layer, using $32$ filters, a $3 \times 3$ kernel, a $1 \times 1$ step size, and a ReLU activation function,
+\item A 2-Dimensional Maximum Pooling layer using a $3 \times 3$ pooling size, and an Identity activation function
+\end{enumerate}  
+The Convolution layers convoluted over the middle two axes of the data (over space and time in the spectrogram).
+
+\paragraph*{}By grouping layers in this structure, each of the $32$ filters passes over a $3 \times 3$ area, and then again. The result is
+
+% ================
+
+\subsubsection{The Perceptron Branch}
+
+\paragraph*{} The Perceptron branch is picture on the right side of fig.
+(\ref{fig-NetworkArchitecture}), notice that it is considerably smaller in side and complexity than it's neighbor.
+Rather than accept an image-like input, the perception simply takes a vector-like input of properties of a larger data set - in this case, each waveform.
+We call these properties \textit{features} \cite{Geron,Kahn,Virtanen}.
+\textcolor{blue}{Details on the creating of these features can be found in the \textit{features} section of this document.}
+
+\paragraph*{}The input layer of the perceptron accepts a 2-Dimensional array.
+The axes, in order of indexing, represent (i) the size of the \textit{mini-batch} of samples, (ii) the number of features for each sample.
+We use the same model hyper-paramater of $64$ samples per batch, and have developed $23$ unique clssification features that have been derived from time-space and frequency-space representations of the audio file data.
+We can denote the 2D shape if the input object into this branch as:
+\begin{equation}
+\label{eqn-shapeX2}
+X_2 \in \mathbb{R}^{(64 \times 23)}
+\end{equation}
+Again, any other shape will be rejected by the model, and an error is raised.
+
+% ================
+
+\subsubsection{The Final Output Branch}
+
+\paragraph*{}
 
@@
 
+\bibitem{Olsen}
+Olson, Harry E. \textit{Music, Physics and Engineering}. 2nd ed., Dover Publications, 1967.
+
 \bibitem{Peatross}
@@
 Virtanen, Tuomas, et al. \textit{Computational Analysis of Sound Scenes and Events.} Springer, 2018.
+
+\bibitem{White}
+White, Harvey Elliott, and Donald H. White. \textit{Physics and Music: the Science of Musical Sound}. Dover Publications, Inc., 2019.
 

### 2020-09-06 Thesis/Sections/FeatureSelections.tex
5 Sept 2020
- Updates to Neural network Section
- Updates to Feature Section
- Removed old notes from Repo

% ================================
% Landon Buell
% Kevin Short
% Physics 799
% 5 September 2020 
% ================================

\documentclass[12pt,letterpaper]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}

\begin{document}

% ================================================================

\section{Feature Selections}
\label{sec-FeatureSelections}

\paragraph*{}Even best minds in the world will perform poorly on test which they have studied the wrong material- neural networks are no different. In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}. It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier. Consider if you were tasked to identify cats and dogs from images, but instead were presented with only the top-most row of pixels- The task would be nearly impossible because of an inappropriate or in complete set of information.

\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" \cite{Virtanen}:
\begin{quote}
For recognition algorithms, the necessary property of the acoustic features is low variability among features extracted from examples assigned to the same class, and at the same time high variability allowing distinction between features extracted from examples assigned to different classes.
\end{quote}
In constructing a neural network classifier, the development of appropriate features is of the utmost importance. To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency space representation of the waveform. It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely on these features.

\paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}. In the training process, this object, along with the appropriate classification label, $y$ is presented to the neural network for processing. This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu}

\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector. These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics. In the following sections, we outline the set of $24$ features used in the classification process

\subsubsection{Audio Preprocessing}

% ================================================================

\subsection{Spectrogram Feature}
\label{subsec-spectrogram}

\paragraph*{}The field of neural classification is well studied in the application of image-processing. Many large-scale, and introductory neural network projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}. As a result, model architectures for image related tasks are well-explored and have experimentally shown successful behavior. Following in those footsteps, it make senses to provide an image-like representation of a sound wave as a feature. We do this in the form of a spectrogram.

\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both space and time. In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis. Thus each point in the 2-Dimensional space is an energy at a given time and frequency. Examples spectrograms from the wave form data set are shown in Fig. (\ref{fig-spectrograms}).

\begin{figure}[H]
\begin{center}
\label{fig-spectrograms}
\textcolor{red}{Insert spectrograms here}
\caption{Spectrogram representations of various waveforms}
\end{center}
\end{figure}

\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification. Frame-blocking creates a set of analysis frames, each of which is $N$ samples in length, and has a fixed overlap with the next adjacent frame. Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhan,Kahn,Virtanen}. For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap. At a sample rate of $f_s = 44100$ samples/second, each frame represents a slice of time that is about $0.1$ seconds long.

\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame. The analysis frame are concatenated into a $k \times N$ sized matrix, $A$, where each row is a frame. A standard \textit{Hann Window} of $N$ samples is generated and reshaped into a $N \times 1$ array,$H$. The $n$-th index in a Hann window with $N$ samples is defined:
\begin{equation}
\label{eqn-Hann}
H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
\end{equation}
The window function is applied to each analysis frame by computing the matrix-product of the $k \times N$ block-frame matrix and the $N \times 1$ window function array. \textcolor{red}{Math is wrong here! Check this, check the code too!}

\paragraph*{}

% ================================================================

\subsection{Time-Space Features}
\label{subsec-time}

% ================================================================

\subsection{Frequency-Space Features}
\label{subsec-frequency}

% ================================================================

\newpage

\begin{thebibliography}{9}
\bibliographystyle{apalike}

\bibitem{Geron}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. O'Reilly, 2017.

\bibitem{Geron2}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. 2nd ed., O'Reilly, 2019.

\bibitem{Goodfellow}
Goodfellow, Ian, et al.\textit{Deep Learning}. MIT Press, 2017.

\bibitem{James}
James, Gareth, et al. \textit{An Introduction to Statistical Learning with Applications in R}. Springer, 2017.

\bibitem{Kahn}
Khan, M. Kashif Saeed, and Wasfi G. Al-Khatib. “Machine-Learning Based Classification of Speech and Music.” Multimedia Systems, vol. 12, no. 1, 2006, pp. 55–67., doi:10.1007/s00530-006-0034-0.

\bibitem{Levine}
Levine, Daniel S. \textit{Introduction to Neural and Cognitive Modeling}. 3rd ed., Routledge, 2019.

\bibitem{Liu}
Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classification." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.

\bibitem{Loy}
Loy, James , \textit{Neural Network Projects with Python}. Packt Publishing, 2019

\bibitem{McCulloch}
McCulloch, Warren S., and Walter Pitts. "A Logical Calculus of the Ideas Immanent in Nervous Activity." \textit{The Bulletin of Mathematical Biophysics}, vol. 5, no. 4, 1943, pp. 115–133.

\bibitem{Mierswa}
Mierswa, Ingo, and Katharina Morik. "Automatic Feature Extraction for Classifying Audio Data." \textit{Machine Learning}, vol. 58, no. 2-3, 2005, pp. 127–149., doi:10.1007/s10994-005-5824-7.

\bibitem{Mitchell}
Mitchell, Tom Michael. Machine Learning. 1st ed., McGraw-Hill, 1997.

\bibitem{Olsen}
Olson, Harry E. \textit{Music, Physics and Engineering}. 2nd ed., Dover Publications, 1967.

\bibitem{Peatross}
Peatross, Justin, and Michael Ware. \textit{Physics of Light and Optics.} Brigham Young University, Department of Physics, 2015.

\bibitem{Petrik}
Petrik, Marek. "Introduction to Deep Learning." Machine Learning. 20 April. 2020, Durham, New Hampshire.

\bibitem{Short}
Short, K. and Garcia R.A. 2006. "Signal Analysis Using the Complex Spectral Phase Evolution (CSPE) Method." AES: \textit{Audio Engineering Society Convention Paper}.

\bibitem{Virtanen}
Virtanen, Tuomas, et al. \textit{Computational Analysis of Sound Scenes and Events.} Springer, 2018.

\bibitem{White}
White, Harvey Elliott, and Donald H. White. \textit{Physics and Music: the Science of Musical Sound}. Dover Publications, Inc., 2019.

\bibitem{Zhang}
Zhang, Tong, and C.-C. Jay Kuo. “Content-Based Classification and Retrieval of Audio.” \textit{Advanced Signal Processing Algorithms, Architectures, and Implementations VIII}, 2 Oct. 1998, pp. 432–443., doi:10.1117/12.325703.

\end{thebibliography}

% ================================================================

\end{document}

### 2020-09-06 Thesis/Sections/TheNerualNetwork.tex
5 Sept 2020
- Updates to Neural network Section
- Updates to Feature Section
- Removed old notes from Repo

@@
 \paragraph*{}The task of algorithmically matching sound files to musical instrument classes in exceedingly difficult through conventional computer programming techniques.
-Because of the complexity of soundwaves, and human ears and brains interpret them, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
+Because of the complexity of sound waves, brain's interpretation them, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
 Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an architecture that allows for a computer to \textit{learn} and change and update itself as it is presented with more data.
@@
 
-\paragraph*{}Former YouTube video Classification team lead, and current Machine Learning consultant, Aurelien Geron writes about the relationship between biological brains and mathematical neural networks \cite{Geron}:
+\paragraph*{}Former YouTube video classification team lead, and current machine learning consultant, Aurelien Geron writes about the relationship between biological brains and mathematical neural networks \cite{Geron}:
 \begin{quote}
@@
 \paragraph*{}Over the course of their lives, humans will learn to map sounds to sources almost effortlessly.
-Given a sample of sound, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olsen,White}.
-Similarly, a neural network uses features of a sound, represented by an array $x$, and learns a series of parameters, $\Theta$, that allow it to map those features to one or more pre-defined sources \cite{Virtanen}.
+Given an example, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olsen,White}.
+We can simplify the idea of humans recognizing sound as some function or operation that occurs within the brain, accepting an input sound, and produces an output label.
+Similarly, a neural network can be constructed, presented with \textit{features} of multiple, labeled sound waves and learns a set of parameters $\Theta$ that allows for the mapping to a source.
 
@@
 \end{quote}
+Without any external intervention, a model must update itself to improve it's performance at a give task a new information is presented to it.
+To do this, the model must be constructed with a training procedure in mind.
+
+\paragraph*{}If we consider the set of parameters $\theta$ as a the concatenation, of each layer's weighting matrix and bias vector such that:
+\begin{equation}
+\label{eqn-Theta}
+\theta = \big\{
+W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)},W^{(L)}, b^{(L-1)},
+\big\}
+\end{equation}
+We can consider each parameter is simply a float-point number.
+Each value for each number contribute to the output of the function.
+In increasing complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is  a very high dimensional parameter-space.
+
+\paragraph*{}Finally,
 

### 2020-09-06 Thesis/Sections/FeatureSelections.tex
6 Sept 2020
- Updates to feature selections paper

@@
 
+\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}.
+In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
+\begin{enumerate}
+\item A suitably sized number of files, of reasonable audio quality.
+\item Audio encoded in a standard, and consistent format
+\item A consistent sample rate between audio files
+\item A consistent number of channels
+\end{enumerate}
+Note that different projects may require a different set of requirement from preprocessing\cite{Virtanen}. For this project, we have chosen to use the following parameters:
+\begin{enumerate}
+\item Roughtly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}
+\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
+\item All audio is sampled at $44,100$ Hz
+\item All audio has been down-mixed into mono-channel waveforms.
+\end{enumerate}
+
 % ================================================================
+
+\newpage
 
@@
 \end{equation}
-The window function is applied to each analysis frame by computing the matrix-product of the $k \times N$ block-frame matrix and the $N \times 1$ window function array.
-\textcolor{red}{Math is wrong here!
-Check this, check the code too!}
+The window function is applied to each analysis frame by computing the dot-product of the Hann window array, $H$ and each row of the analysis frames matrix, $A$.
+This way, the window function has been effectively applied to each frame
 
-\paragraph*{}
+\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring the signal from a time domain into a frequency domain.
+\cite{Olson,Peatross}.
+The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
+Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space containing $N$ samples
+\begin{equation}
+\label{eqn-DFTMatrix}
+\mathbb{W} = \frac{1}{\sqrt{N}}
+\begin{bmatrix}
+1 & 1 & 1 & 1 & \hdots & 1 \\
+1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
+1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
+1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
+\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
+1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
+\end{bmatrix}
+\end{equation}
+Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $A^T$.
+The transpose of $A$ then makes each analysis frame into a column vector, which gives the appropriate dimension from multiplciation.
+
+\paragraph*{}Most standard implementations of neural network require all activations to be real floating-point numbers.
+Since the the DFT matrix introduce complex values, we  compute the Hadamard (element-wise) product of $\mathbb{W}A^T$ and it's complex conjugate as such:
+\begin{equation}
+\label{eqn-Spectrogram}
+\big( \mathbb{W}A^T \big) \odot \big( \mathbb{W}A^T \big)^* = S_{xx}
+\end{equation}
+Where $\mathbb{W}$ is the DFT matrix from eqn.
+(\ref{eqn-DFTMatrix}), $A^T$ is the transpose of the analysis frames matrix, and $^*$ denotes the element-wise complex conjugate.
+The matrix $S_{xx}$, is the spectrogram representation of the initial waveform, and now contains $N \times k$ real floating-point numbers.
+
+\paragraph*{}Each Column of the $S_{xx}$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ analysis frames.
+Given the discretized nature of digital audio, the fequency-sapce representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins.
+Since human hearing extends from about $20$ Hz to around $20$ kHz, audio files, such as music and voice recordings are typically sampled around $44.1$ kHz, to ensure that the full range of audio is held by the recording \cite{Olson,Virtanen}.
+
+\paragraph*{}However, standard musical instruments seldom extend above $8$ kHz \cite{Olson,White}.
+This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency, and the $S_{xx}$ will contain mostly zero, or zero-like entries.
+As a result of this, we can simply crop each matrix, to display frequencies that are only between $0$ Hz and $8000$ Hz.
+This makes the input smaller, and eliminates redundant and non-useful information.
+This brings the number rows in the $S_{xx}$ matrix from $N$ to $N'$.
+lastly, each raw audio file may contain a different number of samples to begin with, thus a different number of analysis frames are created.
+To ensure each sample presented to the classifier, we assert that each matrix must have exactly $k'$ columns.
+If $k < k'$, columns of zeros are added to pad the input, and if $k' < k$, columns are removed.
+
+\paragraph*{}Each spectrogram is now $N' \times k'$ and effectively encodes the energy distribution of the waveform a a function of both time and frequency.
+The spectrogram is the first feature used in this model.
+For this classifier, we have chosen $N' = 560$ and $k' = 256$.
+For training, a mini-batch of $b$ samples are concatenated into a single array object.
+\textcolor{blue}{See Neural Network section for more details}.
+For a batch of $b$ samples of $N' \times k' \times 1$ spectrograms, we shape $X_1$ such that:
+\begin{equation}
+\label{eqn-X1 shape}
+X_1 = \big\{ S_{xx}^{(0)},S_{xx}^{(1)},S_{xx}^{(2)}, ... , S_{xx}^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k' \times 1)}
+\end{equation}
+
+\paragraph*{}The fourth dimension, which contains $1$ element, allows for the spectrogram matrix to be processed identically to how neural networks process gray-scale images.
+For example, and RGB image would have a last-axis shape of $3$ elements.
+This matrix is presented to the \textit{Convolution} branch of the neural network from processing.
+\textcolor{blue}{See Neural Network section for more details}
 
 % ================================================================
+
+\newpage
 
@@
 
+\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. In some cases, this can be from the waveform.
+
 % ================================================================
+
+\newpage
 
@@
 
-\bibitem{Olsen}
+\bibitem{Olson}
 Olson, Harry E. \textit{Music, Physics and Engineering}. 2nd ed., Dover Publications, 1967.

### 2020-09-08 Thesis/Sections/FeatureSelections.tex
8 Sept 2020
- Updates to feature selections section

@@
 \paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification.
-Frame-blocking creates a set of analysis frames, each of which is $N$ samples in length, and has a fixed overlap with the next adjacent frame.
+Frame-blocking creates a set of analysis frames, $a^{(i)}$ each of which is $N$ samples in length, and has a fixed overlap with the next adjacent frame.
 Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhan,Kahn,Virtanen}.
@@
 
+\paragraph*{}We concatenate each analysis frame, $a^{(i)}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
+\begin{equation}
+\label{eqn-FrameMatrix}
+A = \big\{ a^{(0)} , a^{(1)} , a^{(2)} , ... , a^{(k-1)} \big\} = 
+\begin{bmatrix}
+a^{(0)}_{0} & a^{(0)}_{1} & a^{(0)}_{2} & \hdots & a^{(0)}_{N-1} \\
+a^{(1)}_{0} & a^{(1)}_{1} & a^{(1)}_{2} & \hdots & a^{(1)}_{N-1} \\
+a^{(2)}_{0} & a^{(2)}_{1} & a^{(2)}_{2} & \hdots & a^{(2)}_{N-1} \\
+\vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
+a^{(k-1)}_{0} & a^{(k-1)}_{1} & a^{(k-1)}_{2} & \hdots & a^{(k-1)}_{N-1} \\
+\end{bmatrix}
+\end{equation}
+We can also index this matrix, knowing that $A_{i,j} = a^{(i)}_{j}$.
+
 \paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
-The analysis frame are concatenated into a $k \times N$ sized matrix, $A$, where each row is a frame.
-A standard \textit{Hann Window} of $N$ samples is generated and reshaped into a $N \times 1$ array,$H$.
+A standard \textit{Hann Window} of $N$ samples is generated and reshaped into a $N \times 1$ column-array,$H$.
 The $n$-th index in a Hann window with $N$ samples is defined:
@@
 \end{equation}
-The window function is applied to each analysis frame by computing the dot-product of the Hann window array, $H$ and each row of the analysis frames matrix, $A$.
-This way, the window function has been effectively applied to each frame
+The window function is applied to each analysis frame by computing the dot-product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
 
@@
 Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $A^T$.
-The transpose of $A$ then makes each analysis frame into a column vector, which gives the appropriate dimension from multiplciation.
+The transpose of $A$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
 
 \paragraph*{}Most standard implementations of neural network require all activations to be real floating-point numbers.
-Since the the DFT matrix introduce complex values, we  compute the Hadamard (element-wise) product of $\mathbb{W}A^T$ and it's complex conjugate as such:
+Since the the DFT matrix introduce complex values, we compute the square of the element-wise $L2$-norm of the resultant array.
 \begin{equation}
 \label{eqn-Spectrogram}
-\big( \mathbb{W}A^T \big) \odot \big( \mathbb{W}A^T \big)^* = S_{xx}
+S_{xx} = \big{\lVert} \mathbb{W}A^T \big{\rVert}_{2}^{2}
 \end{equation}
 Where $\mathbb{W}$ is the DFT matrix from eqn.
-(\ref{eqn-DFTMatrix}), $A^T$ is the transpose of the analysis frames matrix, and $^*$ denotes the element-wise complex conjugate.
+(\ref{eqn-DFTMatrix}) and $A^T$ is the transpose of the analysis frames matrix from eqn.
+(\ref{eqn-FrameMatrix}).
 The matrix $S_{xx}$, is the spectrogram representation of the initial waveform, and now contains $N \times k$ real floating-point numbers.
@@
 
-\paragraph*{}However, standard musical instruments seldom extend above $8$ kHz \cite{Olson,White}.
-This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency, and the $S_{xx}$ will contain mostly zero, or zero-like entries.
+\paragraph*{}However, standard musical instruments seldom extend above $8$ kHz \cite{Olson,Virtanen,White}.
+This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S_{xx}$ matrix will contain mostly zero, or zero-like entries.
 As a result of this, we can simply crop each matrix, to display frequencies that are only between $0$ Hz and $8000$ Hz.
-This makes the input smaller, and eliminates redundant and non-useful information.
-This brings the number rows in the $S_{xx}$ matrix from $N$ to $N'$.
+This makes the input array smaller, and eliminates redundant and non-useful information.
+This brings the number rows in the $S_{xx}$ matrix from $N$ down to $N'$.
 lastly, each raw audio file may contain a different number of samples to begin with, thus a different number of analysis frames are created.
-To ensure each sample presented to the classifier, we assert that each matrix must have exactly $k'$ columns.
-If $k < k'$, columns of zeros are added to pad the input, and if $k' < k$, columns are removed.
+To ensure all sample are a homogeneous size, we assert that each matrix must have exactly $k'$ columns.
+If $k' < k$, columns of zeros are added to pad the input, and if $k' > k$, columns are removed.
 
-\paragraph*{}Each spectrogram is now $N' \times k'$ and effectively encodes the energy distribution of the waveform a a function of both time and frequency.
+\paragraph*{}Each spectrogram is now $N' \times k' \times 1$ ($1$ representing a single gray-scale channel, as oppose to $3$ for RGB inputs) and effectively encodes the energy distribution of the waveform a a function of both time and frequency.
 The spectrogram is the first feature used in this model.
@@
 \end{equation}
-
-\paragraph*{}The fourth dimension, which contains $1$ element, allows for the spectrogram matrix to be processed identically to how neural networks process gray-scale images.
-For example, and RGB image would have a last-axis shape of $3$ elements.
-This matrix is presented to the \textit{Convolution} branch of the neural network from processing.
-\textcolor{blue}{See Neural Network section for more details}
+This matrix is presented to the \textit{Convolution} branch of the neural network from processing. \textcolor{blue}{See Neural Network section for more details}
 
@@
 
-\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. In some cases, this can be from the waveform.
+\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample.
+In some cases, this can be from the waveform directly, or my manipulation of rows and columns in the analysis frames matrix $A$ from eqn.
+(\ref{eqn-FrameMatrix}).
+For each feature, we detail the physical meaning of each feature, and provide a visualization in feature-space.
+
+\subsubsection{Time Domain Envelope}
+
+\subsubsection{Zero Crossing Rate}
+
+\subsubsection{Center of Mass}
+
+\subsubsection{Statistical Distribution Data}
+
+\subsubsection{Auto Correlation Coefficients}
 
@@
 \label{subsec-frequency}
+
+\paragraph*{}The features described in this section ar ederived from the frequency-domain representations of each audio sample.
+Typically, these features are exacted from the spectrogram representation,$S_xx$, outlined in sec.
+(\ref{subsec-spectrogram}) and computed in eqn.(\ref{eqn-Spectrogram}).
+For each feature, we detail the physical meaning of each feature, and provide a visualization in feature-space.
+
+\subsubsection{Mel Frequency Ceptral Coefficients}
+
+\subsubsection{Center of Mass}
+
+\paragraph*{}The frequency center-of-mass ($f_{CoM}$) for an audio file provides a strong representation of how overtones and energy is distributed in the signal.
+For example, a low instrument such as a tuba or bass may have a very low $f_{CoM}$ while flutes and violins may have a very high $f_{CoM}$.
 

### 2020-09-08 SignalClassifier/ClassifierMain/ClassifierMAIN.py
Added "SignalClassifier" Solution
- Added & Renamed scripts from main Classifier

@@ -1,0 +1,62 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+10 June 2020
+"""
+
+            #### IMPORTS ####
+
+import os
+import sys
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '2'
+
+import ModeUtilities as mode_utils
+import SystemUtilities as sys_utils
+import NeuralNetworkUtilities as NN_utils
+
+            #### MAIN EXECUTABLE ####
+
+if __name__ == '__main__':
+       
+    parent = 'C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\Instrument_Classifier_v0'
+    read = os.path.join(parent,'Target-Data')
+    model = os.path.join(parent,'Model-Data')
+    export = os.path.join(parent,'Output-Data')
+
+    # PRE-PROCESSING FOR PROGRAM
+    ProgramSetup = sys_utils.ProgramInitializer(read,model,export,'train-predict',True)    
+    FILEOBJECTS,N_classes = ProgramSetup.__Call__()
+    exportpath = ProgramSetup.exportpath
+    timestart = ProgramSetup.starttime
+
+    # SETUP NEURAL NETWORK MODELS
+    NeuralNetwork = NN_utils.NetworkContainer(NN_utils.modelName,N_classes,ProgramSetup.modelpath,
+                        NN_utils.inputShapeCNN,NN_utils.inputShapeMLP,ProgramSetup.new_models)
+    modelName = NeuralNetwork.name
+    
+    # DETERMINE WHICH MODE TO RUN PROGRAM
+    if ProgramSetup.program_mode == 'train':
+        ProgramMode = mode_utils.TrainMode(FILEOBJS=FILEOBJECTS,modelName=modelName,
+                                            n_classes=N_classes,timestamp=timestart,exportpath=exportpath,
+                                            show_summary=True,groupSize=256,n_iters=1)
+    elif ProgramSetup.program_mode == 'train-predict':     
+        ProgramMode =  mode_utils.TrainPredictMode(FILEOBJS=FILEOBJECTS,modelName=modelName,
+                                            n_classes=N_classes,timestamp=timestart,exportpath=exportpath,
+                                            show_summary=False,groupSize=256,n_iters=1,testSize=0.1)
+    elif ProgramSetup.program_mode == 'predict':
+        ProgramMode = mode_utils.PredictMode(FILEOBJS=FILEOBJECTS,modelName=modelName,
[…]

### 2020-09-08 SignalClassifier/ClassifierMain/FeatureUtilities.py

@@ -1,0 +1,363 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+12 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+
+import scipy.fftpack as fftpack
+import scipy.integrate as integ
+import scipy.signal as signal
+import scipy.sparse as sparse
+
+import MathUtilities as math_utils
+import PlottingUtilities as plot_utils
+
+"""
+FeaturesUtilities.py - "Feature Extraction Utils"
+    Contains Definitions to extract features and data from
+    time-domain representations of a signal
+"""
+
+        #### CLASS DEFINITIONS ####
+
+class BaseFeatures:
+    """
+    Basic Feature Extraction Class
+        'Time_Series_Features' and 'Frequency_Series_Features' inherit from here
+    Assigns waveform attribute, sample rate, number of samples,
+    divides into time-frames
+    """
+
+    def __init__(self,waveform,rate=44100,frames=None,npts=4096,overlap=0.75):
+        """ Initialize Class Object """
+        self.signal = waveform              # set waveform to self
+        self.n_samples = self.signal.shape[0]   # samples in waveform
+        self.rate = rate                    # sample rate
+        self.npts = npts                    # points per frame
+        self.overlap = overlap              # overlap between frames
+        if frames is None:                  # if not givenframes
+            self.frames = self.TimeFrames() # set create the frames
+        else:                               # otherwise
+            self.frames = frames            # set the framnes
+        self.n_frames = self.frames.shape[0]# number of frames
+
+    def TimeFrames (self):
+        """
+        Divide waveforms into frames of fixed length
+            Waveform in tail-zero padded to adjust length
+            Useful for building spectrogram
+        --------------------------------
+        * no args
+        --------------------------------
+        Return frames object (n_frames = 
+        """
+        frames = np.array([])               # array to hold time frames
+        step = int(self.npts*(1-self.overlap))  # steps between frames
+        for I in range(0,self.n_samples,step):  # iter through wave form
+            x = self.signal[I:I+self.npts]           # create single frame
+            if x.shape[0] != self.npts:         # frame w/o N samples
+                pad = self.npts - x.shape[0]    # number of zeroes to pad
+                x = np.append(x,np.zeros(shape=(1,pad)))  
+            frames = np.append(frames,x)        # add single frame
+        frames = frames.reshape(-1,self.npts)   # reshape (each row is frame)
[…]

### 2020-09-08 SignalClassifier/ClassifierMain/MachineLearningUtilities.py

@@ -1,0 +1,187 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+13 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+import pandas as pd
+import os
+import tensorflow.keras as keras
+import time
+
+"""
+MachineLearningUtilities.py - 'Machine Learning Utilities'
+    Contains Definitions that are relatedto Machine Learning Data Structures & Workflow
+    
+"""
+
+            #### Data Structrue ####
+
+class DesignMatrix:
+    """
+    Construct design-matrix-like object
+    --------------------------------
+    target (int) : Integer target value
+    ndim (int) : Number of dimensions in this array
+    n_classes (int) : Number of unique classes 
+    --------------------------------
+    Return instantiated feature_array instance
+    """
+
+    def __init__(self,ndim,n_classes):
+        """ Initialize Object Instance """
+        self.X = []         # empty data structure
+        self.shapes = []    # store explicit shapes of each samples
+        self.targets = []   # target for each sample
+        self.n_samples = 0  # no samples in design matrix
+        self.ndim = ndim    # number of dimensions in array
+        self.n_classes = n_classes
+
+    def AddSample (self,x):
+        """ Add features 'x' to design matrix, preserve shape """
+        self.X.append(x.GetFeatures())      # add sample to design matrix
+        self.shapes.append(x.GetShape())    # store shape       
+        self.n_samples += 1                 # current number of samples
+        try:                                # attempt
+            self.targets.append(x.target)   # add the target
+        except:                             # otherwise
+            self.targets.append(None)       # add None-type
+        return self
+ 
+    def Pad2D (self,new_shape,offsets=(0,0)):
+        """ Zero-Pad 2D samples to meet shape """
+        new_X = np.zeros(shape=(self.n_samples,new_shape[0],new_shape[1]))   # create new design matrix
+        new_shape = (new_shape[0],new_shape[1])
+        for i in range(self.n_samples):     # iterate by sample
+            dx,dy = offsets[0],offsets[1]   # align upper left     
+            try: 
+                new_X[i][dx:dx+self.X[i].shape[0],dy:dy+self.X[i].shape[1]] += self.X[i] 
+            except:
+                slice = self.X[i][:new_shape[0],:new_shape[1]]
+                shape_diff = np.array(new_shape) - slice.shape      # needed padding
[…]

### 2020-09-08 SignalClassifier/ClassifierMain/ModeUtilities.py

@@ -1,0 +1,311 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+12 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+import os
+from sklearn.model_selection import train_test_split
+from sklearn.preprocessing import StandardScaler
+
+import SystemUtilities as sys_utils
+import FeatureUtilities as feat_utils
+import PlottingUtilities as plot_utils
+import MachineLearningUtilities as ML_utils
+import NeuralNetworkUtilities as NN_utils
+
+
+"""
+ModeUtilities.py - 'Program Mode Utilities'
+    Contains Definitions that are only called directly from MAIN script
+    Functions are large & perform Groups of important operations
+"""
+
+            #### FUNCTION DEFINITIONS ####  
+
+class ProgramMode:
+    """
+    Base Program mode object from which all programs objects inherit from
+    --------------------------------
+    FILEOBJS (iter) : List-like of File_object instances
+    modelName (str) : user-ID-able string to indicate model
+    n_classes (int) : number of discrete classes for models
+    timestamp (str) : String representing time of program start
+    exportpath (str) : Local Path to output filedata
+    show_summary (bool) : If True, result are displayed to user
+    groupSize (int) : number of file samples in each design matrix
+    --------------------------------
+    Execute MAIN program in perscribed mode
+    """
+    def __init__(self,FILEOBJS,modelName,n_classes,timestamp,exportpath=None,
+                 show_summary=True,groupSize=256):
+        """ Inititialize Class Object Instance """
+        self.FILEOBJS = FILEOBJS            # file objects in use
+        self.modelName = modelName          # name of Neural network
+        self.n_classes = n_classes          # number of classes
+        self.timestamp = timestamp          # time when program began
+        self.exportpath = exportpath        # path to push results to
+        self.show_summary = show_summary    # show results of stages      
+        self.groupSize = groupSize          # giles to use in each mega-batch
+        self.n_files = len(self.FILEOBJS)   # number of file objects
+        self.groupCounter = 0
+
+        self.Scaler = StandardScaler()      # design matrix scaler
+    
+    def LoopCounter (self,cntr,max,text):
+        """ Print Loop Counter for User """
+        print('\t\t('+str(cntr)+'/'+str(max)+')',text)
+        return None
+
[…]

### 2020-09-08 SignalClassifier/ClassifierMain/NeuralNetworkUtilities.py

@@ -1,0 +1,209 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+10 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+import os
+
+import tensorflow as tf
+import tensorflow.keras as keras
+
+"""
+NeuralNetworkModels.py - "Neural Network Models"
+    Contains Definitions to wrap and contain creation of
+    Tensorflow/Keras Sequential Neural Network Models
+"""
+
+            #### VARIABLE DECLARATIONS ####
+
+modelName = "VISION"
+inputShapeMLP = (23,)
+inputShapeCNN = (560,256,1)
+
+class NetworkContainer:
+    """
+    Object that creates and contains Neural Network Model objects
+    --------------------------------
+    modelName (str) : user-ID-able string to indicate model
+    n_classes (int) : number of discrete classes for models
+    path (str) : Local parent path object where models are stored
+    inputAShape (iter) : list-like of ints giving shape of CNN branch input shape
+    inputBShape (iter) : list-like of ints giving shape of MLP branch input shape   
+    new (bool) : If true, new Neural Networks are overwritten
+    --------------------------------
+    Return Instantiated Neural Network Model Object
+    """
+    def __init__(self,modelName,n_classes,path,inputAShape,inputBShape,new=True):
+        """ Instantiate Class Object """
+        self.name = modelName
+        self.shapeA = inputAShape
+        self.shapeB = inputBShape
+
+        self.n_classes = n_classes  # number of output classes
+        self.parentPath = os.path.join(path,self.name)  # Set parent path for models      
+        self.newModel = new         # create new models?
+        
+        if self.newModel == True:               # create new networks?
+            self.MODEL = self.CreateNewModel()  # create new
+            self.SaveModel()                    # save locally
+        else:                                   # load exisitng networks
+           self.MODEL = self.LoadExistingModel()# load model
+           self.n_classes = self.MODEL.get_layer(index=-1).output_shape[-1]
+        assert self.n_classes is not None       # make sure we know how many classes
+
+    def __repr__(self):
+        """ Return string representation of NetworkContainer Class """
+        return "-"
+        
+    def CreateNewModel (self):
+        """
+        Create New Neural network to specified Parameters
+        --------------------------------
+        * no args
+        --------------------------------
[…]

### 2020-09-08 SignalClassifier/ClassifierMain/SystemUtilities.py

@@ -1,0 +1,247 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+10 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+import pandas as pd
+import os
+import sys
+import datetime
+import argparse
+
+import scipy.io.wavfile as sciowav
+
+import PlottingUtilities as plot_utils
+
+"""
+SystemUtilities.py - "SystemUtilities"
+    Contains Variables, Classes, and Definitions for Lower program functions
+    Backends, Data structure objects, os & directory organization and validations
+
+"""
+
+            #### DATA STRUCTURE CLASSES ####
+
+class FileObject:
+    """
+    Create File 
+    --------------------------------
+    datarow (arr) : array of shape (1 x 3):
+        has form:
+        | Fullpath  | Target Int    | Target Str |
+    --------------------------------
+    Return instatiated file_object class
+    """
+
+    def __init__(self,datarow):
+        """ Initialize Object Instance """
+        self.fullpath = datarow[0]      # set full file path
+        try:
+            self.target = int(datarow[1])   # target as int           
+        except:
+            self.target = None              # no label
+        dir_tree = self.fullpath.split('/')
+        self.filename = dir_tree[-1]    # filename
+
+    def AssignTarget (self,target):
+        """ Assign Target value to instance """
+        self.target = target    # set y
+        return self             # return self
+
+    def ReadAudio (self):
+        """ Read raw data from local path """
+        rate,data = sciowav.read(self.fullpath)    
+        data = data.reshape(1,-1).ravel()   # flatten waveform
+        self.rate = rate            # set sample rate
+        self.waveform = data/np.abs(np.amax(data))
+        self.n_samples = len(self.waveform)
+        return self             # return self
+
+class OutputStructure :
+    """
+    Data Structure to Store and Output History or Prediction arrays
+    """
+
+    def __init__(self,programMode,exportPath):
+        """ Initialize Class Object instance """
+        if programMode == "Train":      # output for training history
+            self.cols = ["Epoch Num","Loss Score","Precision","Recall"]
+        elif programMode == "Predict":  # output for predictions
+            self.cols = ["Filepath","Label","Prediction"]
+        else:
+            print("\n\tERROR! - File mode not recognized!")
+            self.cols = []
+            raise BaseException()
+        self.exportPath = exportPath
+        self.InitData()
+    
+    def InitData (self):
[…]

### 2020-09-08 SignalClassifierTools/ClassifierAnalysis/AnalysisMAIN.py
Added "SignalClassifierTools" Solution
- Transferred & Renamed Data As needed

@@ -1,0 +1,33 @@
+"""
+Landon Buell
+PHYS 799.32
+Classifier Analysis Main
+28 July 2020
+"""
+
+        #### IMPORTS ####
+
+import numpy as np
+import os
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '2'
+
+import tensorflow.keras as keras
+
+import AnalysisUtilities as utils
+
+        #### MAIN EXECUTABLE ####
+        
+if __name__ == '__main__':
+
+    parent = 'C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\Instrument_Classifier_v0'
+    export = os.path.join(parent,'Output-Data')
+
+    infiles = ['VISION@PREDICTIONS@2020-08-27_13.20.24.810306.csv']
+    n_classes = 25
+
+    for file in infiles:
+        modelName = file.split("@")[0]
+        Program = utils.AnalyzeModels(modelName,export,file,n_classes)
+        Program.__Call__()
+
+    print("=)")

### 2020-09-08 SignalClassifierTools/ClassifierAnalysis/AnalysisUtilities.py

@@ -1,0 +1,86 @@
+"""
+Landon Buell
+PHYS 799.32
+Classifier Analysis Main
+28 July 2020
+"""
+
+        #### IMPORTS ####
+
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import os
+
+import tensorflow as tf
+import tensorflow.keras as keras
+
+        #### OBJECT DEFINITIONS ####
+
+class AnalyzeModels:
+    """
+    Class Object to Analyze performance of model outputs using metrics
+    --------------------------------
+    model_names (iter) : list-like of 3 strings indicating names for models
+    datapath (str) : Local Directory path where input file is held
+    infile (str) : File name w/ ext indicating file to read
+    n_classes (int) : number of discrete classes for models
+    --------------------------------
+    Return Instante of class
+    """
+
+    def __init__(self,modelName,datapath,infile,n_classes):
+        """ Initialize Class Object Instance """
+        self.modelName = modelName
+        self.datapath = datapath
+        self.infile = infile
+        self.n_classes = n_classes
+
+        self.outfile = infile.replace("PREDICTIONS","ANALYSIS")
+        self.full_inpath = os.path.join(self.datapath,self.infile)
+        self.full_outpath = os.path.join(self.datapath,self.outfile)
+
+    def AssignMetrics (self,metrics_list=[]):
+        """ Assign metrics objects to list to self """
+        self.metrics = metrics_list
+        return self
+
+    def ReadData(self):
+        """ Read raw prediction data from local file """
+        self.indata = pd.read_csv(self.full_inpath,header=0,index_col=0)
+        self.truth = self.indata['Label'].to_numpy(dtype=np.int32)
+        self.predictions = self.indata['Prediction'].to_numpy(dtype=np.int32)
+        return self
+
+    def InitOutput(self):
+        """ Initialize Output File data """
+        self.scores = {'Metric':[]}          # column to hold metrics
+        for metric in self.metrics:     # each metric:
+            self.scores['Metric'].append(metric.name)    # add metric to col
+        for model in self.model_names:   # each model:
+            self.scores.update({model:np.array([])})
+        return self
+
+    def WriteOutput (self):
+        """ Write Metric scores to local file """
+        raise NotImplementedError()
+
+    def __Call__(self):
+        """ Call Program Mode """
+        
+        self.ReadData()      
[…]

### 2020-09-08 SignalClassifierTools/ClassifierFeatures/PlottingUtilities.py

@@ -1,0 +1,181 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+10 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+"""
+PlottingUtilities.py - "Plotting Utilities"
+    Contains Definitions to visualize spectral data in
+    time-space, frequency-space, and feature-space
+"""
+
+            #### PLOTTING FUNCTIONS ####
+
+def Plot_Features_2D (X1,X2,classes,labels,title='',
+                      save=False,show=True):
+    """
+    Create 2D visualization Comparing features
+    --------------------------------
+    X1 (arr) : (1 x N) array of data to plot on x-axis
+    X2 (arr) : (1 x N) array of data to plot on y-axis
+    classes (arr) : (1 x N) array of labels use to color-code by class
+    labels (iter) : (2 x 1) iterable containing labels for x & y axes
+    title (str) : Title for plot
+    save (bool) : If true, save MPL figure to cwd (False by Default)
+    show (bool) : If true, shows current figure to User (True by Default)
+    --------------------------------
+    return None
+    """
+    plt.figure(figsize=(16,12))
+    plt.title(title,size=40,weight='bold')
+    plt.xlabel(str(labels[0]),size=20,weight='bold')
+    plt.ylabel(str(labels[1]),size=20,weight='bold')
+
+    for X in [X1/X2]:           # Normalize Each Feature
+        X = X/np.max(np.abs(X))
+
+    plt.scatter(X1,X2,c=classes)
+
+    plt.yticks(np.arange(0,1.1,0.1))
+    plt.hlines(0,0,1,color='black')
+    plt.vlines(0,0,1,color='black')
+
+    plt.grid()
+    plt.tight_layout()
+    if save == True:
+        plt.savefig(title+'.png')
+    if show == True:
+        plt.show()
+
+def Plot_History (History,modelName,save=False,show=True):
+    """
+    Visualize Data from Keras History Object Instance
+    --------------------------------
+    History (Obj) : Keras history object
+    modelName (Obj) : Keras Sequential model w/ name attrb
+    save (bool) : If true, save MPL figure to cwd (False by Default)
+    show (bool) : If true, shows current figure to User (True by Default)
+    --------------------------------
+    Return None
+    """
+    # Initialize Figure
+    eps = np.array(History.epoch)          # arr of epochs
[…]

### 2020-09-08 SignalClassifierTools/ClassifierPreprocessing/PreprocessMAIN.py

@@ -1,0 +1,40 @@
+"""
+Landon Buell
+Classifier Preprocessing Module
+PHYS 799
+16 August 2020
+"""
+
+        #### IMPORTS ####
+
+import numpy as np
+import matplotlib.pyplot as plt
+import os
+import PreprocessUtilities as utils
+
+        #### MAIN EXECUTABLE ####
+
+if __name__ == '__main__':
+
+    # ESTABLISH DIRECTORIES
+    homePath = os.getcwd()
+    exptPath = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\Instrument_Classifier_v0\\Target-Data"
+    dataPath = ["C:\\Users\\Landon\\Documents\\audioWAV2"]  
+    exptFile = ["Y2.csv"]
+
+    # Iteate through pairs of files / directories
+    for path,file in zip(dataPath,exptFile):
+        exportPath = os.path.join(path,file)
+
+        Encoder = utils.TargetLabelEncoder()
+        FilePaths = Encoder.ReadLocalPath(path)
+        TargetStrings = Encoder.AssignTarget(FilePaths)
+        TargetIntegers = Encoder.LabelEncoder(TargetStrings)
+
+        cols = ["Fullpath","Target Int","Target String"]
+        Data = {"Fullpath":FilePaths,
+                "Target Int":TargetIntegers,
+                "target Str":TargetStrings }
+        Encoder.ConstructDataFrame(Data,exportPath)
+
+    print('=)')

### 2020-09-08 SignalClassifierTools/ClassifierPreprocessing/PreprocessUtilities.py

@@ -1,0 +1,82 @@
+"""
+Landon Buell
+Classifier Preprocessing Module
+PHYS 799
+16 August 2020
+"""
+
+        #### IMPORTS ####
+
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import os
+
+        #### CLASS DECLARATIONS ####
+
+class TargetLabelEncoder:
+    """ Encode Files By Name and Integer """
+
+    def __init__(self):
+        """ Initialize Class Object Instance """
+        self.woodWinds = ['AltoFlute','AltoSax','BbClarinet','EbClarinet',
+                    'Flute','Oboe','SopSax','EbClarinet','BassClarinet',
+                    'BassFlute','Bassoon']
+        self.strings = ['banjo','Bass','Cello','Viola','Violin']
+        self.brass = ['BassTrombone','Horn','TenorTrombone','Trumpet','Tuba']
+        self.percussion = ['bells','Marimba','Vibraphone','Xylophone']
+        self.cymbals = ['crash','chinese','orchcrash','windgong','ride',
+                    'hihat','splash','thaigong',]
+
+    @property
+    def AcceptedInstruments (self):
+        """ Accepted Instrument String Titles """
+        return self.woodWinds + self.strings + self.brass + self.percussion + self.cymbals
+
+    def ReadLocalPath (self,path,ext='.wav'):
+        """ Read through directory and collect all files with ext """
+        FILES = []                              # hold filename
+        for roots,dirs,files in os.walk(path):  # walk through tree
+            for file in files:                  # each file
+                if file.endswith(ext):          # .WAV file
+                    fullpath = os.path.join(roots,file)
+                    FILES.append(fullpath)      # add to list
+        return FILES                            # return list of files
+
+    def AssignTarget (self,filelist):
+        """ Assign tagret class value based on name """
+        classes = []
+        for file in filelist:
+            filename = file.split("\\")[-1]     # last element in list
+            name = filename.split(".")[0]       # 0-th element in list
+            if name in self.AcceptedInstruments:    # in valid instruments
+                targetString = name.upper() # set instrument
+            elif name in self.percussion:        # percussion?
+                targetString = 'PERCUSSION' # set
+            elif name in self.cymbals:           # cymbals?
+                targetString = 'CYMBAL'     # set
+            else:                           # not in lists?
+                targetString = 'OTHER'      # set other
+            classes.append(targetString)    # add to class list
+        return classes                      # list
+
+    def LabelEncoder (self,targetVector):
[…]

### 2020-09-08 Instrument_Classifier_v0/Classifier_Analysis/Analysis_Utilities.py
Removed "Instrument_Classifier_v0" Solution
- All needed files have been moved and saved.
- Need to clean up "SignalClassifierTools" Solution

@@ -1,87 +1,0 @@
-"""
-Landon Buell
-PHYS 799.32
-Classifier Analysis Main
-28 July 2020
-"""
-
-        #### IMPORTS ####
-
-import numpy as np
-import matplotlib.pyplot as plt
-import pandas as pd
-import os
-
-import tensorflow as tf
-import tensorflow.keras as keras
-
-        #### OBJECT DEFINITIONS ####
-
-class Analyze_Models:
-    """
-    Class Object to Analyze performance of model outputs using metrics
-    --------------------------------
-    model_names (iter) : list-like of 3 strings indicating names for models
-    datapath (str) : Local Directory path where input file is held
-    infile (str) : File name w/ ext indicating file to read
-    n_classes (int) : number of discrete classes for models
-    --------------------------------
-    Return Instante of class
-    """
-
-    def __init__(self,modelName,datapath,infile,n_classes):
-        """ Initialize Class Object Instance """
-        self.modelName = modelName
-        self.datapath = datapath
-        self.infile = infile
-        self.n_classes = n_classes
-
-        self.outfile = infile.replace("PREDICTIONS","ANALYSIS")
-        self.full_inpath = os.path.join(self.datapath,self.infile)
-        self.full_outpath = os.path.join(self.datapath,self.outfile)
-
-    def AssignMetrics (self,metrics_list=[]):
-        """ Assign metrics objects to list to self """
-        self.metrics = metrics_list
-        return self
-
-    def ReadData(self):
-        """ Read raw prediction data from local file """
-        self.indata = pd.read_csv(self.full_inpath,header=0,index_col=0)
-        self.truth = self.indata['Label'].to_numpy(dtype=np.int32)
-        self.predictions = self.indata['Prediction'].to_numpy(dtype=np.int32)
-        return self
-
-    def InitOutput(self):
-        """ Initialize Output File data """
-        self.scores = {'Metric':[]}          # column to hold metrics
-        for metric in self.metrics:     # each metric:
-            self.scores['Metric'].append(metric.name)    # add metric to col
-        for model in self.model_names:   # each model:
-            self.scores.update({model:np.array([])})
-        return self
-
-    def WriteOutput (self):
-        """ Write Metric scores to local file """
-        raise NotImplementedError()
-
-    def __Call__(self):
-        """ Call Program Mode """
-        
-        self.ReadData()      
[…]

### 2020-09-08 Instrument_Classifier_v0/Classifier_Preprocessing/Preprocessing_MAIN.py

@@ -1,37 +1,0 @@
-"""
-Landon Buell
-Classifier Preprocessing Module
-PHYS 799
-16 August 2020
-"""
-
-        #### IMPORTS ####
-
-import numpy as np
-import matplotlib.pyplot as plt
-import os
-import Preprocessing_Utils as utils
-
-        #### MAIN EXECUTABLE ####
-
-if __name__ == '__main__':
-
-    # ESTABLISH DIRECTORIES
-    homePath = os.getcwd()
-    dataPath = "C:\\Users\\Landon\\Documents\\audioWAV2"
-    exptPath = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\Instrument_Classifier_v0\\Target-Data"
-    exptFile = "Y2.csv"
-    exportPath = os.path.join(exptPath,exptFile)
-
-    Encoder = utils.TargetLabelEncoder()
-    FilePaths = Encoder.ReadLocalPath(dataPath)
-    TargetStrings = Encoder.AssignTarget(FilePaths)
-    TargetIntegers = Encoder.LabelEncoder(TargetStrings)
-
-    cols = ["Fullpath","Target Int","Target String"]
-    Data = {"Fullpath":FilePaths,
-            "Target Int":TargetIntegers,
-            "target Str":TargetStrings }
-    Encoder.ConstructDataFrame(Data,exportPath)
-
-    print('=)')

### 2020-09-08 Instrument_Classifier_v0/Classifier_Preprocessing/Preprocessing_Utils.py

@@ -1,82 +1,0 @@
-"""
-Landon Buell
-Classifier Preprocessing Module
-PHYS 799
-16 August 2020
-"""
-
-        #### IMPORTS ####
-
-import numpy as np
-import matplotlib.pyplot as plt
-import pandas as pd
-import os
-
-        #### CLASS DECLARATIONS ####
-
-class TargetLabelEncoder:
-    """ Encode Files By Name and Integer """
-
-    def __init__(self):
-        """ Initialize Class Object Instance """
-        self.woodWinds = ['AltoFlute','AltoSax','BbClarinet','EbClarinet',
-                    'Flute','Oboe','SopSax','EbClarinet','BassClarinet',
-                    'BassFlute','Bassoon']
-        self.strings = ['banjo','Bass','Cello','Viola','Violin']
-        self.brass = ['BassTrombone','Horn','TenorTrombone','Trumpet','Tuba']
-        self.percussion = ['bells','Marimba','Vibraphone','Xylophone']
-        self.cymbals = ['crash','chinese','orchcrash','windgong','ride',
-                    'hihat','splash','thaigong',]
-
-    @property
-    def AcceptedInstruments (self):
-        """ Accepted Instrument String Titles """
-        return self.woodWinds + self.strings + self.brass + self.percussion + self.cymbals
-
-    def ReadLocalPath (self,path,ext='.wav'):
-        """ Read through directory and collect all files with ext """
-        FILES = []                              # hold filename
-        for roots,dirs,files in os.walk(path):  # walk through tree
-            for file in files:                  # each file
-                if file.endswith(ext):          # .WAV file
-                    fullpath = os.path.join(roots,file)
-                    FILES.append(fullpath)      # add to list
-        return FILES                            # return list of files
-
-    def AssignTarget (self,filelist):
-        """ Assign tagret class value based on name """
-        classes = []
-        for file in filelist:
-            filename = file.split("\\")[-1]     # last element in list
-            name = filename.split(".")[0]       # 0-th element in list
-            if name in self.AcceptedInstruments:    # in valid instruments
-                targetString = name.upper() # set instrument
-            elif name in self.percussion:        # percussion?
-                targetString = 'PERCUSSION' # set
-            elif name in self.cymbals:           # cymbals?
-                targetString = 'CYMBAL'     # set
-            else:                           # not in lists?
-                targetString = 'OTHER'      # set other
-            classes.append(targetString)    # add to class list
-        return classes                      # list
-
-    def LabelEncoder (self,targetVector):
[…]

### 2020-09-08 Instrument_Classifier_v0/External_Utilities/Target_Encoder.py

@@ -1,41 +1,0 @@
-"""
-Landon Buell
-PHYS 799
-External Utilities
-11 June 2020
-"""
-
-        #### IMPORTS ####
-
-import numpy as np
-import pandas as pd
-import os
-
-import Utilities
-
-        #### MAIN EXECUTABLE ####
-
-if __name__ == '__main__':
-
-    # ESTABLISH DIRECTORIES
-    init_path = os.getcwd()
-    data_path = 'C:/Users/Landon/Documents/wav_audio'
-    expt_path = init_path
-
-    # READ THROUGH FULL DIRECTORY
-    FULLPATHS = Utilities.read_directory(data_path,'.wav')  
-    FILENAMES = [x.split('/')[-1] for x in FULLPATHS]
-    print("Files Found:",len(FILENAMES))
-
-    # SET TARGET
-    names = [x.split('.')[0] for x in FILENAMES]
-    classes = Utilities.assign_class(names)
-    y = Utilities.target_label_encoder(classes)
-
-    # CREATE DATAFRAME
-    data = np.array([FULLPATHS,y,classes]).reshape(3,-1) 
-    frame = pd.DataFrame(data=data.transpose(),
-        columns=['Fullpath','Target Int','Target Str'])
-    print(frame.head(-10))
-
-    frame.to_csv('TARGETS.csv')

### 2020-09-08 Instrument_Classifier_v0/External_Utilities/Utilities.py

@@ -1,78 +1,0 @@
-"""
-Landon Buell
-PHYS 799
-External Utilites
-11 June 2020
-"""
-
-            #### IMPORTS ####
-
-import numpy as np
-import pandas as pd
-import os
-
-                        #### VARIABLE & OBJECT DECLARATIONS ####   
-
-accepted_instruments = [
-        # Woodwinds
-        'AltoFlute','AltoSax','BbClarinet','EbClarinet','Flute',
-        'Oboe','SopSax','EbClarinet','BassClarinet','BassFlute',
-        'Bassoon',
-        # Strings
-        'Bass','Cello','Viola','Violin',
-        # Brass
-        'BassTrombone','Horn','TenorTrombone','Trumpet','Tuba',
-        # Percussion
-        'bells','Marimba','Vibraphone','Xylophone']
-
-percussion = ['woodblock','triangle','castanet','clave',
-              'crotale','tambourine']
-
-cymbals = ['crash','chinese','orchcrash','windgong','ride',
-           'hihat','splash','thaigong',]
-
-            #### FUNCTION DEFINITIONS ####
-
-def target_label_encoder(target_vector,write=False):
-    """
-    Create encoding dictiory of strings to classes
-    --------------------------------
-    target_vector (arr) : array of target classes as strings
-    write (bool/str) : If not False, str is path write out dict 
-    --------------------------------
-    Return encoding & decoding dictionary
-    """
-    enc_dict = {}                       # output dictionary
-    class_counter = 0                   # class counter
-    for category in np.unique(target_vector): # unique elements
-        key,val = category,class_counter
-        enc_dict.update({key:val})      # update the dictionary
-        class_counter += 1              # incriment class counter
-    y = [enc_dict[x] for x in target_vector]
-    # return the encoding/decoding dictionary and number of classes
-    return y
-
-def assign_class (filelist):
-    """ Assign class value based on name """
-    classes = []
-    for name in filelist:
-        if name in accepted_instruments:      # in valid instruments
-            y = name.upper()    # set instrument
-        elif name in percussion:# percussion?
-            y = 'PERCUSSION'    # set
-        elif name in cymbals:   # cymbals?
-            y = 'CYMBAL'        # set
-        else:                   # not in lists?
-            y = 'OTHER'         # set other
-        classes.append(y)       # add to class list
-    return classes              # list
-
-def ReadLocalPath (path,ext='.wav'):
-    """ Read through directory and collect all files with ext """
-    FILES = []                              # hold filename
[…]

### 2020-09-08 Instrument_Classifier_v0/Feature_Experiments/Feature_Experiments_MAIN.py

@@ -1,54 +1,0 @@
-"""
-Landon Buell
-Feature - Extraction
-PHYS 799
-6 August 2020
-"""
-
-        #### IMPORTS ####
-
-import numpy as np
-import os 
-import pandas as pd
-
-import tensorflow as tf
-import tensorflow.keras as keras
-
-import System_Utilities as sys_utils
-import Feature_Utilities as feat_utils
-import Plotting_Utilities as plot_utils
-
-        #### MAIN EXECUTABLE ####
-
-if __name__ == '__main__':
-
-    path = 'C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\Instrument_Classifier_v0\\Target-Data'
-    ProgramInitializer = sys_utils.ProgramStart(path)
-    FILEOBJS,N_classes = ProgramInitializer.__call__()
-
-    #Iterator = sys_utils.FileIterator(FILEOBJS,N_classes)
-    #Iterator.__call__()
-    #Iterator.ExportData(str(ProgramInitializer.starttime))
-    
-
-    Analyzer = sys_utils.DataAnalyzer('2020-08-17_15.53.51.124816.csv',N_classes) 
-    Analyzer.__call__(scale=True)
-    #print(Analyzer.ComputeVariance())
-
-    X_train,X_test,Y_train,Y_test = Analyzer.TrainTestSplit()
-
-    MLP_MODEL = sys_utils.NeuralNetworks.Multilayer_Perceptron('JARVIS',N_classes,Analyzer.n_features,
-                                                               layerunits=[64,64])
-    History = MLP_MODEL.fit(X_train,Y_train,batch_size=32,epochs=20,verbose=2)
-
-    plot_utils.Plot_History(History,MLP_MODEL)
-
-    Y_pred = MLP_MODEL.predict(X_test)
-    Y_pred = np.argmax(Y_pred,axis=-1)
-    Y_test = np.argmax(Y_test,axis=-1)
-    confmat = tf.math.confusion_matrix(Y_test,Y_pred,N_classes)
-
-    plot_utils.Plot_Confusion(confmat,np.arange(N_classes),"-")
-    
-
-    print("=)")

### 2020-09-08 Instrument_Classifier_v0/Feature_Experiments/System_Utilities.py

@@ -1,304 +1,0 @@
-"""
-Landon Buell
-PHYS 799
-Instrument Classifier v0
-10 June 2020
-"""
-
-            #### IMPORTS ####
-
-import numpy as np
-import pandas as pd
-import os
-import sys
-import datetime
-
-from sklearn.model_selection import train_test_split
-from sklearn.preprocessing import StandardScaler
-from sklearn.feature_selection import SelectKBest
-import sklearn.feature_selection as feat_sel
-
-import tensorflow.keras as keras
-import scipy.io.wavfile as sciowav
-
-import Feature_Utilities as feat_utils
-
-
-"""
-Program_Utilities.py - "Program Utilities"
-    Contains Variables, Classes, and Definitions for Lower program functions
-    Backends, Data structure objects, os & directory organization and validations
-
-"""
-
-            #### DATA STRUCTURE CLASSES ####
-
-class FileObject:
-    """
-    Create File 
-    --------------------------------
-    datarow (arr) : array of shape (1 x 3):
-        has form:
-        | Fullpath  | Target Int    | Target Str |
-    --------------------------------
-    Return instatiated file_object class
-    """
-
-    def __init__(self,datarow):
-        """ Initialize Object Instance """
-        self.fullpath = datarow[0]      # set full file path
-        try:
-            self.target = int(datarow[1])   # target as int           
-        except:
-            self.target = None              # no label
-        dir_tree = self.fullpath.split('/')
-        self.filename = dir_tree[-1]    # filename
-
-    def AssignTarget (self,target):
-        """ Assign Target value to instance """
-        self.target = target    # set y
-        return self             # return self
-
-    def ReadAudio (self):
-        """ Read raw data from local path """
-        rate,data = sciowav.read(self.fullpath)    
-        data = data.reshape(1,-1).ravel()   # flatten waveform
-        self.rate = rate            # set sample rate
-        self.waveform = data/np.abs(np.amax(data))
-        self.n_samples = len(self.waveform)
-        return self             # return self
-
-            #### PROGRAM PROCESSING CLASSES ####
-
-class DataAnalyzer :
-    """
-    Analyze Desgin Matrix from local CSV file 
-    --------------------------------
-
-    --------------------------------
-
-    """
-
-    def __init__(self,filename,n_classes):
-        """ Initialize Class Object Instance """
-        self.filename = filename
-        self.n_classes = n_classes
-        
-
-    def LoadDataFrame (self):
-        """ Read Local Data Frame-Like Object """
[…]

### 2020-09-08 Instrument_Classifier_v0/Instrument_Classifier/Machine_Learning_Utilities.py

@@ -1,181 +1,0 @@
-"""
-Landon Buell
-PHYS 799
-Instrument Classifier v0
-13 June 2020
-"""
-
-            #### IMPORTS ####
-
-import numpy as np
-import pandas as pd
-import os
-import tensorflow.keras as keras
-import time
-
-            #### Data Structrue ####
-
-class DesignMatrix:
-    """
-    Construct design-matrix-like object
-    --------------------------------
-    target (int) : Integer target value
-    ndim (int) : Number of dimensions in this array
-    n_classes (int) : Number of unique classes 
-    --------------------------------
-    Return instantiated feature_array instance
-    """
-
-    def __init__(self,ndim,n_classes):
-        """ Initialize Object Instance """
-        self.X = []         # empty data structure
-        self.shapes = []    # store explicit shapes of each samples
-        self.targets = []   # target for each sample
-        self.n_samples = 0  # no samples in design matrix
-        self.ndim = ndim    # number of dimensions in array
-        self.n_classes = n_classes
-
-    def AddSample (self,x):
-        """ Add features 'x' to design matrix, preserve shape """
-        self.X.append(x.GetFeatures())      # add sample to design matrix
-        self.shapes.append(x.GetShape())    # store shape       
-        self.n_samples += 1                 # current number of samples
-        try:                                # attempt
-            self.targets.append(x.target)   # add the target
-        except:                             # otherwise
-            self.targets.append(None)       # add None-type
-        return self
- 
-    def Pad2D (self,new_shape,offsets=(0,0)):
-        """ Zero-Pad 2D samples to meet shape """
-        new_X = np.zeros(shape=(self.n_samples,new_shape[0],new_shape[1]))   # create new design matrix
-        new_shape = (new_shape[0],new_shape[1])
-        for i in range(self.n_samples):     # iterate by sample
-            dx,dy = offsets[0],offsets[1]   # align upper left     
-            try: 
-                new_X[i][dx:dx+self.X[i].shape[0],dy:dy+self.X[i].shape[1]] += self.X[i] 
-            except:
-                slice = self.X[i][:new_shape[0],:new_shape[1]]
-                shape_diff = np.array(new_shape) - slice.shape      # needed padding
-                slice = np.pad(slice,[[0,shape_diff[0]],[0,shape_diff[1]]])
-                new_X[i] += slice
-            self.shapes[i] = new_shape      # reset shape
-        self.X = new_X              # overwrite
-        self.X = self.X.reshape(self.n_samples,new_shape[0],new_shape[1],1)
[…]

### 2020-09-08 Instrument_Classifier_v0/Instrument_Classifier/Math_Utilities.py

@@ -1,57 +1,0 @@
-"""
-Landon Buell
-PHYS 799
-Instrument Classifier v0
-17 June 2020
-"""
-
-            #### IMPORTS ####
-              
-import numpy as np
-import scipy.stats as stats
-import tensorflow as tf
-from sklearn.preprocessing import StandardScaler
-
-"""
-Math_Utilities.py - "Math Utilities"
-    Contains Definitions for general mathematical functions
-"""
-
-            #### FUNCTION DEFINITIONS ####
-
-class MathematicalUtilities :
-    """
-    Mathematical Utilites for feature processing
-    --------------------------------
-    * no args
-    --------------------------------
-    All methods are static
-    """
-
-    @staticmethod
-    def DistributionData (X):
-        """
-        Analyze properties of an array of FP values
-        --------------------------------
-        X (arr) : (1 x N) Array of FP numbers to analyze as distribution
-        --------------------------------
-        Return array of [mean,median,mode,variance]
-        """
-        mean = np.mean(X,axis=-1)           # avg        
-        median = np.median(X,axis=-1)       # median
-        var = np.var(X,axis=-1)             # variance
-        return np.array([mean,median,var])  # return data
-
-    @staticmethod
-    def ReimannSum (X,dx):
-        """
-        Compute Reimann Sum of 1D array X with sample spacing dx
-        --------------------------------
-        X (arr) : (1 x N) Array of FP numbers to compute Reimann Sum of
-        dx (float) : Spacing between samples, 1 by default
-        --------------------------------
-        Return Reimann Sum approximation of array
-        """
-        return np.sum(X)*dx
-
-

### 2020-09-08 Instrument_Classifier_v0/Instrument_Classifier/Neural_Network_Utilities.py

@@ -1,209 +1,0 @@
-"""
-Landon Buell
-PHYS 799
-Instrument Classifier v0
-10 June 2020
-"""
-
-            #### IMPORTS ####
-
-import numpy as np
-import os
-
-import tensorflow as tf
-import tensorflow.keras as keras
-
-"""
-Neural_Network_Models.py - "Neural Network Models"
-    Contains Definitions to wrap and contain creation of
-    Tensorflow/Keras Sequential Neural Network Models
-"""
-
-            #### VARIABLE DECLARATIONS ####
-
-modelName = "VISION"
-inputShapeMLP = (23,)
-inputShapeCNN = (560,256,1)
-
-class NetworkContainer:
-    """
-    Object that creates and contains Neural Network Model objects
-    --------------------------------
-    modelName (str) : user-ID-able string to indicate model
-    n_classes (int) : number of discrete classes for models
-    path (str) : Local parent path object where models are stored
-    inputAShape (iter) : list-like of ints giving shape of CNN branch input shape
-    inputBShape (iter) : list-like of ints giving shape of MLP branch input shape   
-    new (bool) : If true, new Neural Networks are overwritten
-    --------------------------------
-    Return Instantiated Neural Network Model Object
-    """
-    def __init__(self,modelName,n_classes,path,inputAShape,inputBShape,new=True):
-        """ Instantiate Class Object """
-        self.name = modelName
-        self.shapeA = inputAShape
-        self.shapeB = inputBShape
-
-        self.n_classes = n_classes  # number of output classes
-        self.parentPath = os.path.join(path,self.name)  # Set parent path for models      
-        self.newModel = new         # create new models?
-        
-        if self.newModel == True:               # create new networks?
-            self.MODEL = self.CreateNewModel()  # create new
-            self.SaveModel()                    # save locally
-        else:                                   # load exisitng networks
-           self.MODEL = self.LoadExistingModel()# load model
-           self.n_classes = self.MODEL.get_layer(index=-1).output_shape[-1]
-        assert self.n_classes is not None       # make sure we know how many classes
-
-    def __repr__(self):
-        """ Return string representation of NetworkContainer Class """
-        return "-"
-        
-    def CreateNewModel (self):
-        """
-        Create New Neural network to specified Parameters
-        --------------------------------
-        * no args
-        --------------------------------
[…]

### 2020-09-08 Instrument_Classifier_v0/Instrument_Classifier/System_Utilities.py

@@ -1,247 +1,0 @@
-"""
-Landon Buell
-PHYS 799
-Instrument Classifier v0
-10 June 2020
-"""
-
-            #### IMPORTS ####
-
-import numpy as np
-import pandas as pd
-import os
-import sys
-import datetime
-import argparse
-
-import scipy.io.wavfile as sciowav
-
-import Plotting_Utilities as plot_utils
-
-"""
-Program_Utilities.py - "Program Utilities"
-    Contains Variables, Classes, and Definitions for Lower program functions
-    Backends, Data structure objects, os & directory organization and validations
-
-"""
-
-            #### DATA STRUCTURE CLASSES ####
-
-class FileObject:
-    """
-    Create File 
-    --------------------------------
-    datarow (arr) : array of shape (1 x 3):
-        has form:
-        | Fullpath  | Target Int    | Target Str |
-    --------------------------------
-    Return instatiated file_object class
-    """
-
-    def __init__(self,datarow):
-        """ Initialize Object Instance """
-        self.fullpath = datarow[0]      # set full file path
-        try:
-            self.target = int(datarow[1])   # target as int           
-        except:
-            self.target = None              # no label
-        dir_tree = self.fullpath.split('/')
-        self.filename = dir_tree[-1]    # filename
-
-    def AssignTarget (self,target):
-        """ Assign Target value to instance """
-        self.target = target    # set y
-        return self             # return self
-
-    def ReadAudio (self):
-        """ Read raw data from local path """
-        rate,data = sciowav.read(self.fullpath)    
-        data = data.reshape(1,-1).ravel()   # flatten waveform
-        self.rate = rate            # set sample rate
-        self.waveform = data/np.abs(np.amax(data))
-        self.n_samples = len(self.waveform)
-        return self             # return self
-
-class OutputStructure :
-    """
-    Data Structure to Store and Output History or Prediction arrays
-    """
-
-    def __init__(self,programMode,exportPath):
-        """ Initialize Class Object instance """
-        if programMode == "Train":      # output for training history
-            self.cols = ["Epoch Num","Loss Score","Precision","Recall"]
-        elif programMode == "Predict":  # output for predictions
-            self.cols = ["Filepath","Label","Prediction"]
-        else:
-            print("\n\tERROR! - File mode not recognized!")
-            self.cols = []
-            raise BaseException()
-        self.exportPath = exportPath
-        self.InitData()
-    
-    def InitData (self):
[…]

### 2020-09-08 Thesis/Sections/FeatureSelections.tex
8 Sept 2020
- Updates to Feature Selections

@@
 \usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}
+
+\DeclareMathOperator{\sign}{\text{sign}}
 
@@
 \begin{enumerate}
-\item A suitably sized number of files, of reasonable audio quality.
+\item A suitably sized number of files, of reasonable audio quality, with normalized ampltudes
 \item Audio encoded in a standard, and consistent format
@@
 \begin{enumerate}
-\item Roughtly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}
+\item Roughtly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
 \item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
@@
 \begin{bmatrix}
-a^{(0)}_{0} & a^{(0)}_{1} & a^{(0)}_{2} & \hdots & a^{(0)}_{N-1} \\
-a^{(1)}_{0} & a^{(1)}_{1} & a^{(1)}_{2} & \hdots & a^{(1)}_{N-1} \\
-a^{(2)}_{0} & a^{(2)}_{1} & a^{(2)}_{2} & \hdots & a^{(2)}_{N-1} \\
+a^{(0)}[0] & a^{(0)}[1] & a^{(0)}[2] & \hdots & a^{(0)}[N-1] \\
+a^{(1)}[0] & a^{(1)}[1] & a^{(1)}[2] & \hdots & a^{(1)}[N-1] \\
+a^{(2)}[0] & a^{(2)}[1] & a^{(2)}[2] & \hdots & a^{(2)}[N-1] \\
 \vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
-a^{(k-1)}_{0} & a^{(k-1)}_{1} & a^{(k-1)}_{2} & \hdots & a^{(k-1)}_{N-1} \\
+a^{(k-1)}[0] & a^{(k-1)}[1] & a^{(k-1)}[2] & \hdots & a^{(k-1)}[N-1] \\
 \end{bmatrix}
 \end{equation}
-We can also index this matrix, knowing that $A_{i,j} = a^{(i)}_{j}$.
+We use bracket notation, $[j]$ to indicate that each object is array-like. Many programming languages could also use the following indexing conventions for matrix 
+$A$:
+\begin{equation}
+\label{eqn-Indexing}
+A_{i,j} = a^{(i)}[j] = A[i][j] = A[i,j]
+\end{equation}
+Note that these all represent equivalent entries.
 
@@
 The window function is applied to each analysis frame by computing the dot-product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
+Result is an $k \times N$ array, $\widetilde{A}$:
+\begin{equation}
+\label{eqn-WindowMatrix}
+\widetilde{A} = A \cdot H^T
+\end{equation}
 
@@
 \end{equation}
-Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $A^T$.
-The transpose of $A$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
+Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $\widetilde{A}^T$.
+The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
 
@@
 \label{eqn-Spectrogram}
-S_{xx} = \big{\lVert} \mathbb{W}A^T \big{\rVert}_{2}^{2}
+S_{xx} = \big{\lVert} \mathbb{W}\widetilde{A}^T \big{\rVert}_{2}^{2}
 \end{equation}
 Where $\mathbb{W}$ is the DFT matrix from eqn.
-(\ref{eqn-DFTMatrix}) and $A^T$ is the transpose of the analysis frames matrix from eqn.
-(\ref{eqn-FrameMatrix}).
+(\ref{eqn-DFTMatrix}) and $\widetilde{A}^T$ is the transpose of the analysis frames matrix from eqn.
+(\ref{eqn-WindowMatrix}).
 The matrix $S_{xx}$, is the spectrogram representation of the initial waveform, and now contains $N \times k$ real floating-point numbers.
@@
 (\ref{eqn-FrameMatrix}).
-For each feature, we detail the physical meaning of each feature, and provide a visualization in feature-space.
+For each feature, we detail the physical significance and provide a visualization in feature-space.
 
@@
 
+\paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal.
+Generally, we start by computing the RMS-Energy of each frame.
+The larger the RMS energy of the frame, the larger the amplitude of the waveform in that frame.
+For frames with smaller amplitude, we conclude that the signal has either not begun, or is decaying.
+The RMS-Energy of a single analysis-frame $a^{(i)}$ is given by \cite{Olson,Virtanen}
+\begin{equation}
+\label{eqn-RMS}
+RMS\big[ a^{(i)} \big] = \sqrt{\frac{1}{N} \sum_{j=0}^{N-1}a^{(i)}[j]}
+\end{equation}
+
+\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}.
+By doing this, we acquire a rough estimate for the energy of a waveform in the entirety of the audio file \cite{Liu}.
+For instruments with long sustain or release times, such as strings or undampened mallet percussion, hold a comparably large waveform RMS when compared to those instruments without sustain such as brass or percussion.
+
+\begin{figure}[H]
+\label{fig-FeatureTDE}
+\begin{center}
+\textcolor{red}{PLOT OF TDE FEATURES HERE}
+\end{center}
+\caption{Time domain envelope visualized in feature-space}
+\end{figure}
+
 \subsubsection{Zero Crossing Rate}
 
+\paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses it's equilibrium point.
+This can be done per total sound wave, or per unit time, such an per analysis-frame.
+In differentiating speech and music, it is commonly to use the difference between the frame with the highest ZXR and the lowest ZXR.
+In some cases, the ZXR can be correlated to frequency as well \cite{Kahn,Zhang}.
+The ZXR for a frame $a^{(i)}$ is given by \cite{Virtanen,Liu}
+\begin{equation}
+\label{eqn-ZXR}
+ZXR\big[ a^{(i)} \big] = \frac{1}{2} \sum_{j=1}^{N-1} \big{|} \sign(a^{(i)}[j]) - \sign(a^{(i)}[j-1]) \big{|} 
+\end{equation}
+Where $\sign(x)$ returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$.
+
+\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}.
+This provides a rough estimate for the average frequency in the full waveform, and can help discern clean periodic signals (low ZXR) from those that may have more volatile behavior (high ZXR)\cite{Virtanen}.
+
+\begin{figure}[H]
+\label{fig-FeatureZXR}
+\begin{center}
+\textcolor{red}{PLOT OF ZXR FEATURES HERE}
+\end{center}
+\caption{Zero crossing rate visualized in feature-space}
+\end{figure}
+
 \subsubsection{Center of Mass}
+
+\paragraph*{}The temporal center of mass (TCM) of a signal is used to compute where in time the amplitude sort of \textit{bunches up}.
+We treat the full waveform array, $a$, with $M$ samples as a 1-Dimensional discrete mass distribution.
+The TCM of that waveform is then given:
+\begin{equation}
+\label{eqn-FeatureTCM}
+TCM\big[ a \big] = \frac{\sum_{j=0}^{M-1}j a[j]}{\sum_{j=0}^{M-1}a[j]}
+\end{equation}
+This includes negative amplitude values acting as "negative masses".
+
+\paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance.
+For instruments with heavier attacks, we expect the TCM to be a very low value as most of the energy and amplitude is concentrated close to the start of the audio file.
+For instruments with long sustain times, we expect a very centrally located center of mass, and for instruments with long release times, we expect a very late TCM value.
+
+\begin{figure}[H]
+\label{fig-FeatureTCM}
+\begin{center}
+\textcolor{red}{PLOT OF TCM FEATURES HERE}
+\end{center}
+\caption{Temporal center-of-mass visualized in feature-space}
+\end{figure}
 
@@
 \subsubsection{Auto Correlation Coefficients}
+
+\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution \cite{Virtanen}.
+We can compute any number of ACC's and their value changed depending on the index chosen.
+It is common to only compute the first $k$ ACC's.
+For a full waveform signal $a$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
+\begin{equation}
+\label{eqn-FeatureACC}
+ACC_k\big[ a \big] = \frac{\sum_{j=0}^{M-k-1}a[j]a[j+k]} {\sqrt{\sum_{j=0}^{M-k-1}a^2[j]} \sqrt{\sum_{j=0}^{M-k-1}a^2[j+k]}}
+\end{equation}
+
+\begin{figure}[H]
+\label{fig-FeatureACC}
+\begin{center}
+\textcolor{red}{PLOT OF ACC FEATURES HERE}
+\end{center}
+\caption{First four auto correlation coefficients visualized in feature-space}
+\end{figure}
 
@@
 
-\paragraph*{}The features described in this section ar ederived from the frequency-domain representations of each audio sample.
+\paragraph*{}The features described in this section are derived from the frequency-domain representations of each audio sample.
 Typically, these features are exacted from the spectrogram representation,$S_xx$, outlined in sec.
 (\ref{subsec-spectrogram}) and computed in eqn.(\ref{eqn-Spectrogram}).
-For each feature, we detail the physical meaning of each feature, and provide a visualization in feature-space.
+For each feature, we detail the physical significance and provide a visualization in feature-space.
 

### 2020-09-11 Thesis/Sections/FeatureSelections.tex
11 Sept 2020
- Updates to NN section
- Updates to feature section

@@
 In the following sections, we outline the set of $24$ features used in the classification process
+
+\newpage
 
@@
 \begin{equation}
-\label{eqn-Indexing}
+\label{eqn-IndexingA}
 A_{i,j} = a^{(i)}[j] = A[i][j] = A[i,j]
@@
 \label{eqn-Spectrogram}
-S_{xx} = \big{\lVert} \mathbb{W}\widetilde{A}^T \big{\rVert}_{2}^{2}
+S = \big{\lVert} \mathbb{W}\widetilde{A}^T \big{\rVert}_{2}^{2}
 \end{equation}
@@
 (\ref{eqn-WindowMatrix}).
-The matrix $S_{xx}$, is the spectrogram representation of the initial waveform, and now contains $N \times k$ real floating-point numbers.
+The matrix $S$, is the spectrogram representation of the initial waveform, and now contains $N \times k$ real floating-point numbers.
+We can index matrix $S$ similarly to that of matrix $A$ in eqn.
+(\ref{eqn-IndexingA}):
+\begin{equation}
+\label{eqn-IndexingS}
+S_{i,j} = s^{(i)}[j] = S[i][j] = S[i,j]
+\end{equation}
 
-\paragraph*{}Each Column of the $S_{xx}$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ analysis frames.
-Given the discretized nature of digital audio, the fequency-sapce representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins.
+\paragraph*{}Each Column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ analysis frames.
+Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins.
 Since human hearing extends from about $20$ Hz to around $20$ kHz, audio files, such as music and voice recordings are typically sampled around $44.1$ kHz, to ensure that the full range of audio is held by the recording \cite{Olson,Virtanen}.
@@
 \paragraph*{}However, standard musical instruments seldom extend above $8$ kHz \cite{Olson,Virtanen,White}.
-This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S_{xx}$ matrix will contain mostly zero, or zero-like entries.
+This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
 As a result of this, we can simply crop each matrix, to display frequencies that are only between $0$ Hz and $8000$ Hz.
 This makes the input array smaller, and eliminates redundant and non-useful information.
-This brings the number rows in the $S_{xx}$ matrix from $N$ down to $N'$.
+The number rows in the $S$ matrix is reduced from $N$ down to $N'$.
 lastly, each raw audio file may contain a different number of samples to begin with, thus a different number of analysis frames are created.
@@
 
-\paragraph*{}Each spectrogram is now $N' \times k' \times 1$ ($1$ representing a single gray-scale channel, as oppose to $3$ for RGB inputs) and effectively encodes the energy distribution of the waveform a a function of both time and frequency.
+\paragraph*{}Each spectrogram is now $N' \times k' \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform a a function of both time and frequency.
 The spectrogram is the first feature used in this model.
@@
 \label{eqn-X1 shape}
-X_1 = \big\{ S_{xx}^{(0)},S_{xx}^{(1)},S_{xx}^{(2)}, ... , S_{xx}^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k' \times 1)}
+X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k' \times 1)}
 \end{equation}
@@
 \label{eqn-RMS}
-RMS\big[ a^{(i)} \big] = \sqrt{\frac{1}{N} \sum_{j=0}^{N-1}a^{(i)}[j]}
+\text{RMS}\big[ a^{(i)} \big] = \sqrt{\frac{1}{N} \sum_{j=0}^{N-1}a^{(i)}[j]}
 \end{equation}
@@
 \label{eqn-ZXR}
-ZXR\big[ a^{(i)} \big] = \frac{1}{2} \sum_{j=1}^{N-1} \big{|} \sign(a^{(i)}[j]) - \sign(a^{(i)}[j-1]) \big{|} 
+\text{ZXR}\big[ a^{(i)} \big] = \frac{1}{2} \sum_{j=1}^{N-1} \big{|} \sign(a^{(i)}[j]) - \sign(a^{(i)}[j-1]) \big{|} 
 \end{equation}
@@
 \label{eqn-FeatureTCM}
-TCM\big[ a \big] = \frac{\sum_{j=0}^{M-1}j a[j]}{\sum_{j=0}^{M-1}a[j]}
+\text{TCM}\big[ a \big] = \frac{\sum_{j=0}^{M-1}j a[j]}{\sum_{j=0}^{M-1}a[j]}
 \end{equation}
@@
 \subsubsection{Statistical Distribution Data}
+\textcolor{red}{Honetly, I may remove these from the classifier}
 
@@
 \label{eqn-FeatureACC}
-ACC_k\big[ a \big] = \frac{\sum_{j=0}^{M-k-1}a[j]a[j+k]} {\sqrt{\sum_{j=0}^{M-k-1}a^2[j]} \sqrt{\sum_{j=0}^{M-k-1}a^2[j+k]}}
+\text{ACC}_k\big[ a \big] = \frac{\sum_{j=0}^{M-k-1}a[j]a[j+k]} {\sqrt{\sum_{j=0}^{M-k-1}a^2[j]} \sqrt{\sum_{j=0}^{M-k-1}a^2[j+k]}}
 \end{equation}
@@
 \paragraph*{}The features described in this section are derived from the frequency-domain representations of each audio sample.
-Typically, these features are exacted from the spectrogram representation,$S_xx$, outlined in sec.
+Each of these features are exacted from the transpose spectrogram representation, $S^T$, where the creation of $S$ is outlined in sec.
 (\ref{subsec-spectrogram}) and computed in eqn.(\ref{eqn-Spectrogram}).
+This is done to return analysis frame into a row-like array, representing frequency space divided into $N'$ bins, with $k'$ analysis frames.
 For each feature, we detail the physical significance and provide a visualization in feature-space.
 
-\subsubsection{Mel Frequency Ceptral Coefficients}
+\subsubsection{Mel Frequency Cepstral Coefficients}
+
+\paragraph*{}Mel Frequency Ceptstral Coefficients (MFCC's) are a very prolific feature used widly in audio classification tasks \cite{Liu,Virtanen,Zhang}.
+MFCC's are produced by converting a linear-frequency axis with units such as Hertz into units of Mels, which are design to account for the non-linear perception of frequency in humans.
+The Hertz to Mel and Mel to Hertz transforms are provided \cite{Virtanen}:
+\begin{equation}
+\label{eqn-HztoMel}
+M_f[h] = 2595 \log_{10}\big(1+ \frac{h}{700}\big)
+\end{equation}
+\begin{equation}
+\label{eqn-MeltoHz}
+H_f[m] = 700 \big(10^{(\frac{m}{2595})}-1\big)
+\end{equation}
+Where $M_f$ is the frequency in units of Mels, given $[h]$, a frequency in Hertz, and $H_f$ is the frequency in Hertz given $[m]$ a frequency in Mels.
+
+\paragraph*{}Mel filters are produced by grouping frequency-space into $R$ overlapping bins called \textit{Mel Filter-banks}.
+In units of Mels, each filter bank, $R_i$ remains a constant width, but when shown in Hertz, the bins increase logarithmically.
+\begin{figure}[H]
+\label{fig-MelFilterBanks}
+\begin{center}
+\textcolor{red}{Figure of a few Mel Filter Banks goes here}
+\end{center}
+\caption{Mel Filter Banks shown in frequency space with units of Hertz}
+\end{figure}
+Each of the $R$ filters is created to be $N'$ samples long, and transformed back into units of Hertz.
+When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
+Thus, each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is a filter.
+We apply the Mel Filter banks to the spectrogram to create matrix $B$:
+\begin{equation}
+\label{eqn-FilterBanks}
+B = S^T M^T
+\end{equation}
+Matrix $B$ has shape $k' \times R$.
+
+\paragraph*{}Using $S^T$ ensure that each row of the matrix is an analysis frame in frequency space.
+Similarly, each column of the matrix $M$ is a appropriately scaled Mel filter-bank.
+This way, the matrix product in eqn.
+(\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
+Finally, we compute the average energy across all $k'$ frames.
+The resulting $R$ floating-point numbers are approximation of the signal's energy in those particular frequency bands.
+For this project, we have chosen to use $R = 12$ filter-banks, which are all used as features.
+
+\begin{figure}[H]
+\label{fig-FeatureMFCC}
+\begin{center}
+\textcolor{red}{PLOT OF MFCC FEATURES HERE}
+\end{center}
+\caption{Mel Frequency Ceptral Coefficients in feature-space}
+\end{figure}
 
@@
 
-\paragraph*{}The frequency center-of-mass ($f_{CoM}$) for an audio file provides a strong representation of how overtones and energy is distributed in the signal.
-For example, a low instrument such as a tuba or bass may have a very low $f_{CoM}$ while flutes and violins may have a very high $f_{CoM}$.
+\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a strong representation of how overtones and energy is distributed in the signal's frequency domain.
+As with the temporal center-of-mass, we treat each row of the $S$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
+This encodes the FCM for a single analysis frame (in frequency-space) in the waveform.
+For an frequency-analysis frame, $s^{(i)}$, the FCM is given by:
+\begin{equation}
+\label{eqn-FeatureFCM}
+\text{TCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
+\end{equation}
+We compute the FCM for each of the $k'$ frames, and then average the results. We use the average FCM across $k'$ frames to compute the FCM feature:
+\begin{equation}
+TCM = \sum_{i=0}^{k'} \text{TCM}_{i}\big[ s^{(i)} \big]
+\end{equation}
+
+\paragraph*{}The average FCM gives a strong approximation of the instrument or signal source's range.
+For example, a flute or violin will have a considerably high FCM value, even in their lower registers.
+Similarly, basses or tubas will have considerably low FCM values.
+Given that the standard frequency range of some musical instruments is fixed, it is guaranteed that for any particular instrument, the FCM will consistently remain within certain bounds \cite{Olson,White}.
+
+\begin{figure}[H]
+\label{fig-FeatureFCM}
+\begin{center}
+\textcolor{red}{PLOT OF FCM FEATURES HERE}
+\end{center}
+\caption{Frequency center-of-mass visualized in feature-space}
+\end{figure}
+
+% ================================================================
+
+\subsection{The Design Matrix}
 

### 2020-09-11 SignalClassifier/ClassifierMain/ClassifierMAIN.py

@@ -18,8 +18,9 @@ import NeuralNetworkUtilities as NN_utils
             #### MAIN EXECUTABLE ####
 
 if __name__ == '__main__':
-       
-    parent = 'C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\Instrument_Classifier_v0'
+    
+    # HARD-CODE DIRECTORIES FOR DEVELOPMENT/DEBUGGING
+    parent = 'C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\SignalClassifier'
     read = os.path.join(parent,'Target-Data')
     model = os.path.join(parent,'Model-Data')
     export = os.path.join(parent,'Output-Data')
@@ -41,7 +42,7 @@ if __name__ == '__main__':
                                             n_classes=N_classes,timestamp=timestart,exportpath=exportpath,
                                             show_summary=True,groupSize=256,n_iters=1)
     elif ProgramSetup.program_mode == 'train-predict':     
-        ProgramMode =  mode_utils.TrainPredictMode(FILEOBJS=FILEOBJECTS,modelName=modelName,
+        ProgramMode = mode_utils.TrainPredictMode(FILEOBJS=FILEOBJECTS,modelName=modelName,
                                             n_classes=N_classes,timestamp=timestart,exportpath=exportpath,
                                             show_summary=False,groupSize=256,n_iters=1,testSize=0.1)
     elif ProgramSetup.program_mode == 'predict':

### 2020-09-12 Thesis/Sections/Abstract.tex
11 Sept 2020
- Added Abstract to sections
- Updates to feature selections section

% ================================
% Landon Buell
% Kevin Short
% Physics 799
% 5 September 2020 
% ================================

\documentclass[12pt,letterpaper]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}

\begin{document}

% ================================================================

\section{Abstract}

\paragraph*{}Machine learning has been a major player in the role of audio processing and classification for decades. In this time, a great deal of work has been devoted to studying the performance of various model architectures and producing sets of features that can represent a waveform in a compact, efficient, and non-redundant way \textcolor{red}{Citation?}. In this work, we explore a hybrid convolutional neural network (CNN) and multilayer perceptron (MLP) model that uses  features derived from the time-series and frequency-series of a waveform to map audio to a potential source. We examine each features used in classification as well as the physical significance and how the choice of feature influences the neural network architecture. In doing so, we show how the appropriate combination of architecture and features can produce a reasonable classification performance when mapping sound files to a potential musical instrument source.

% ================================================================

\end{document}

### 2020-09-12 Thesis/Sections/FeatureSelections.tex
11 Sept 2020
- Added Abstract to sections
- Updates to feature selections section

@@
 
+\subsubsection{The Design Matrix}
+
+\paragraph*{}The $24$ features are from each file are organized into one of two array structures.
+each called a \textit{design matrix}.
+A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest.
+For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.
+each has shape given by:
+\begin{equation}
+\label{eqn-X1Shape}
+X_1 \in \mathbb{R}^{(b \times N' \times k' \times 1)}
+\end{equation}
+\begin{equation}
+\label{eqn-X2Shape}
+X_2 \in \mathbb{R}^{(b \times p)}
+\end{equation}
+Where $N' \times k' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
+(\ref{subsec-spectrogram}), The first axis, with length $b$ indicates that there are $b$ samples stored in that design matrix.
+Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec.
+(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).
+A row of $X_2$ has shape $1 \times p$ where there are $p$ features within the \textit{feature-vector} for each sample.
+Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.
+
 \subsubsection{Audio Preprocessing}
@@
 \begin{enumerate}
-\item A suitably sized number of files, of reasonable audio quality, with normalized ampltudes
+\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
 \item Audio encoded in a standard, and consistent format
-\item A consistent sample rate between audio files
+\item A consistent sample rate and bit depth between audio files
 \item A consistent number of channels
 \end{enumerate}
-Note that different projects may require a different set of requirement from preprocessing\cite{Virtanen}. For this project, we have chosen to use the following parameters:
+Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
 \begin{enumerate}
-\item Roughtly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
+\item Roughly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
 \item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
-\item All audio is sampled at $44,100$ Hz
+\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
 \item All audio has been down-mixed into mono-channel waveforms.
@@
 \paragraph*{}The field of neural classification is well studied in the application of image-processing.
-Many large-scale, and introductory neural network projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
-As a result, model architectures for image related tasks are well-explored and have experimentally shown successful behavior.
-Following in those footsteps, it make senses to provide an image-like representation of a sound wave as a feature.
-We do this in the form of a spectrogram.
+Many large-scale, and even introductory neural network projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
+As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior.
+Following this success, it make senses to provide an image-like representation of a sound wave as a feature.
+We do this in the form of a spectrogram matrix.
 
@@
 \paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification.
-Frame-blocking creates a set of analysis frames, $a^{(i)}$ each of which is $N$ samples in length, and has a fixed overlap with the next adjacent frame.
-Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhan,Kahn,Virtanen}.
+Frame-blocking creates a set of analysis frames, each labeled as $a^{(i)}$ and is $N$ samples in length, and has a fixed overlap with the next adjacent frame.
+Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhang,Kahn,Virtanen}.
 For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
@@
 \paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
-A standard \textit{Hann Window} of $N$ samples is generated and reshaped into a $N \times 1$ column-array,$H$.
+A standard \textit{Hann Window} of $N$ samples is generated and reshaped into a $N \times 1$ column-array, $H$.
 The $n$-th index in a Hann window with $N$ samples is defined:
@@
 
-\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring the signal from a time domain into a frequency domain.
-\cite{Olson,Peatross}.
+\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross}.
 The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
@@
 
-\paragraph*{}Most standard implementations of neural network require all activations to be real floating-point numbers.
-Since the the DFT matrix introduce complex values, we compute the square of the element-wise $L2$-norm of the resultant array.
+\paragraph*{}Most standard implementations of neural network models require all activations, weights, and biases to be real floating-point numbers.
+Since the the DFT matrix introduces complex values, we compute the square of the element-wise $L2$-norm of the resultant array.
 \begin{equation}
@@
 (\ref{eqn-WindowMatrix}).
-The matrix $S$, is the spectrogram representation of the initial waveform, and now contains $N \times k$ real floating-point numbers.
+The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of real floating-point numbers.
 We can index matrix $S$ similarly to that of matrix $A$ in eqn.
@@
 
-\paragraph*{}Each Column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ analysis frames.
+\paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames.
 Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins.
-Since human hearing extends from about $20$ Hz to around $20$ kHz, audio files, such as music and voice recordings are typically sampled around $44.1$ kHz, to ensure that the full range of audio is held by the recording \cite{Olson,Virtanen}.
+Since human hearing extends from $20$ Hz to $20$ kHz, audio files such as music and voice recordings are typically sampled around $44.1$ kHz, to ensure that the full range of audio is held by the recording \cite{Olson,Virtanen}.
 
@@
 lastly, each raw audio file may contain a different number of samples to begin with, thus a different number of analysis frames are created.
-To ensure all sample are a homogeneous size, we assert that each matrix must have exactly $k'$ columns.
+To ensure all samples are a homogeneous size, we assert that each matrix must have exactly $k'$ columns.
 If $k' < k$, columns of zeros are added to pad the input, and if $k' > k$, columns are removed.
@@
 For this classifier, we have chosen $N' = 560$ and $k' = 256$.
-For training, a mini-batch of $b$ samples are concatenated into a single array object.
+For training, a batch of $b$ samples are concatenated into a single array object.
 \textcolor{blue}{See Neural Network section for more details}.
@@
 \end{equation}
-This matrix is presented to the \textit{Convolution} branch of the neural network from processing. \textcolor{blue}{See Neural Network section for more details}
+Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}).
+This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
+\textcolor{blue}{See Neural Network section for more details}
 
@@
 
+\paragraph*{}From time space, we use the following $10$ features:
+
+\begin{itemize}
+
+\item[•] Time Domain Envelope
+
+\item[•] Zero Crossing Rate
+
+\item[•] Temporal Center of Mass
+
+\item[•] Waveform Mean, Median, and Mode
+
+\item[•] Auto Correlation Coefficients ($\times 4$)
+
+\end{itemize}
+
 \subsubsection{Time Domain Envelope}
@@
 \label{eqn-RMS}
-\text{RMS}\big[ a^{(i)} \big] = \sqrt{\frac{1}{N} \sum_{j=0}^{N-1}a^{(i)}[j]}
+\text{RMS}\big[ a^{(i)} \big] = \sqrt{\frac{1}{N} \sum_{j=0}^{N-1} \big( a^{(i)}[j]} \big)^2
 \end{equation}
@@
 
+\paragraph*{}From frequency space, we use the following $13$ features:
+\begin{itemize}
+
+\item[•] Mel Frequency Cepstral Coefficients ($\times 12$)
+
+\item[•] Frequency Center of Mass
+
+\end{itemize}
+
 \subsubsection{Mel Frequency Cepstral Coefficients}
@@
 
-\subsection{The Design Matrix}
-
-% ================================================================
-
 \newpage

### 2020-09-12 Thesis/Sections/FeatureSelections.tex
Reraan Classifier, Updated Features

@@
 These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics.
-In the following sections, we outline the set of $24$ features used in the classification process
+In the following sections, we outline the set of $21$ features used in the classification process
 
@@
 
-\paragraph*{}The $24$ features are from each file are organized into one of two array structures.
+\paragraph*{}The $21$ features are from each file are organized into one of two array structures.
 each called a \textit{design matrix}.
@@
 
-\paragraph*{}From time space, we use the following $10$ features:
+\paragraph*{}From time space, we use the following $7$ features:
 
@@
 \item[•] Temporal Center of Mass
-
-\item[•] Waveform Mean, Median, and Mode
 
@@
 \end{figure}
-
-\subsubsection{Statistical Distribution Data}
-\textcolor{red}{Honetly, I may remove these from the classifier}
 

### 2020-09-12 SignalClassifier/ClassifierMain/FeatureUtilities.py

@@ -98,8 +98,7 @@ class TimeSeriesFeatures (BaseFeatures):
         featureVector = np.array([])
         featureVector = np.append(featureVector,self.TimeDomainEnvelope())
         featureVector = np.append(featureVector,self.ZeroCrossingRate())
-        featureVector = np.append(featureVector,self.CenterOfMass())
-        featureVector = np.append(featureVector,self.WaveformDistributionData())
+        featureVector = np.append(featureVector,self.CenterOfMass())       
         featureVector = np.append(featureVector,self.AutoCorrelationCoefficients())
         return featureVector
     

### 2020-09-12 SignalClassifier/ClassifierMain/NeuralNetworkUtilities.py

@@ -22,7 +22,7 @@ NeuralNetworkModels.py - "Neural Network Models"
             #### VARIABLE DECLARATIONS ####
 
 modelName = "JARVIS"
-inputShapeMLP = (23,)
+inputShapeMLP = (20,)
 inputShapeCNN = (560,256,1)
 
 class NetworkContainer:

### 2020-09-13 Thesis/Sections/TheNerualNetwork.tex
12 Sept 2020
- Updates to Feature Selections

@@
 \usepackage{float}
+\usepackage{caption}
+\usepackage{subcaption}
 \usepackage{graphicx}
@@
 \subsection{An Introduction to Neural Networks}
+\label{sec-NerualNetworkIntro}
 
@@
 \subsection{The Structure of a Neural Network}
+\label{sec-NetworkStructre}
 
@@
 \subsection{Layers Used in Classification Neural Network}
+\label{sec-Layers}
 
@@
 
-\paragraph*{}Below, we discuss and describe the types of layer functions that are used to produce the classification model in this project.
+\paragraph*{}The combination of eqn.
+(\ref{eqn-matVectEqn}) and eqn.
+(\ref{eqn-elementActivation}), for a layer $l$ , make up the function represented by that layer, as in eqn.
+(\ref{eqn-altLayerFunction}).
+Below, we discuss and describe the types of layer functions that are used to produce the classification model in this project.
 
@@
 
-\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer for short, was one of the earliest function types used in artificial neural network models.
-A dense layer is simply composed of a layer of \textit{artifical neurons}, each of which holds a numerical value within it, called the \textit{activation} of that neuron.
+\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer, or \textit{Fully-Connected} layer for short, was one of the earliest function types used in artificial neural network models \cite{Geron2,Loy}.
+They are among the most commonly used layer types.
+A dense layer is composed of a layer of \textit{artifical neurons}, each of which holds a numerical value within it, called the \textit{activation} of that neuron.
 This idea was developed back from McCulloch and Pitts' work \cite{McCulloch}, and was expanded upon by Frank Rosenblatt in  1957 \cite{Geron}.
@@
 
-\paragraph*{}Suppose the layer $l-1$ contains $m$ neurons. Then the weighting-matrix, $W^{(l)}$ has shape $m \times n$, the bias-vector $b^{(l)}$ has shape $m \times 1$.
-Thus for a dense layer $l$, the exact values of each activation is given by \cite{Geron,Loy}
+\paragraph*{}Suppose the layer $l-1$ contains $m$ neurons.
+Then the weighting-matrix, $W^{(l)}$ has shape $m \times n$, the bias-vector $b^{(l)}$ has shape $m \times 1$.
+We can denote the function in a similar manner to eqn.(\ref{eqn-altLayerFunction}) as:
+\begin{equation}
+\label{eqn-FunctionDense}
+f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(m \times 1)} \rightarrow x^{(l)} \in \mathbb{R}^{(n \times 1)}
+\end{equation}
+
+Thus for a dense layer $l$, the exact values of each activation is given by \cite{Geron,Loy}:
 \begin{equation}
@@
 x_0 \\ x_1 \\ \vdots \\ x_{m-1}
-\end{bmatrix}^{(l-1)}
+\end{bmatrix}^{(l-1)} +
 \begin{bmatrix}
@@
 
+\paragraph*{}Convolution layers emerged from studying the brain's visual cortex, and have been used from image recognition related tasks for around 40 years.
+\cite{Geron,Loy}).
+This layer get's it's name from it's implementation of the mathematical \textit{convolution} function.
+The 2D discrete-convolution of function $A(i,j)$ and $B(i,j)$ is given by \cite{Goodfellow}:
+\begin{equation}
+\label{eqn-convolution}
+C(i,j) = (A * B)(i,j) = \sum_{u}\sum_{v} A(i,j)B(i - u,j - v)
+\end{equation}
+Note that convolution is commutative: $(A * B) = (B * A)$.
+We implement a convolutional layer $f^{(l)})$, by creating a series of $K$ weighting matrices, called \textit{filters}, each of size $m \times n$, where $m,n \in \mathbb{Z}$.
+Often we choose $m = n$ and call the shape the \textit{convolution kernel size} \cite{Loy, Goodfellow}.
+
+\paragraph*{}In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(N \times M)}$, the convolutions filters "step" through the input data and repeatedly compute the element-wise product of each $m \times n$ weighting kernel, and the local activation of the $x^{(l-1)}$ array.
+The step size in each of the 2-dimension is known as the \textit{stride}.
+Each of the $K$ filters is used to generate a $m \times n$ feature map from the input activation.
+For an appropriately trained network, some filters may be dedicated to detecting vertical lines, horizontal lines, sharp edges, areas of mostly one color, etc.
+\cite{Loy,Geron}.
+
+\paragraph*{}In general, for an $N \times M$ input, with kernel size $m \times n$, with stride size $1 \times 1$, and $K$ feature maps.
+\begin{equation}
+f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(N \times M)} \rightarrow
+x^{(l)} \in \mathbb{R}^{([N-n+1] \times [M-m+1] \times K)}
+\end{equation}
+As an example, consider a single filter map over input $x \in \mathbb{R}^{(4 \times 3)}$ and filter map $W \in \mathbb{R}^{(2 \times 2)}$ as shown in fig. (\ref{fig-2DConvExample}):
+\begin{figure}[H]
+\label{fig-2DConvExample}
+\begin{center}
+\begin{subfigure}{0.45\textwidth}
+\includegraphics[scale=0.6]{../figures/2DConvExample(a)}
+\caption{Input Activations}
+\end{subfigure}
+\begin{subfigure}{0.45\textwidth}
+\includegraphics[scale=0.6]{../figures/2DConvExample(b)}
+\caption{Convolution Filter}
+\end{subfigure}
+\begin{subfigure}{0.9\textwidth}
+\centering
+\includegraphics[scale=0.6]{../figures/2DConvExample(c)}
+\caption{Convolution Result}
+\end{subfigure}
+\end{center}
+\caption{The result of convolving an input (a) with an filter map (b) is a new set of activations (c). This Image was adapted from Goodfellow, pg. 325 \cite{Goodfellow}}
+\end{figure}
+Note that formal implementations include a bias vector and an activation function.
+
+\paragraph*{}For 2D convolution over input $x^{(l-1)}$ with feature map $W^{(l)}_k$, producing activations $x^{(l)}$, we compute the activations $x^{(l)}_{k}$ as \cite{Goodfellow}
+\begin{equation}
+\label{eqn-ConvFeedForward}
+x^{(l)}_k = \sigma^{(l)}\bigg[ \Big( \sum_{u=0}^{m-1} \sum_{v=0}^{n-1} x^{(l-1)}(i,j) W^{(l)}_k(i - u,j - v) \Big) + b^{(l)}_k \bigg]
+\end{equation}
+\textcolor{red}{Please check my math here!}
+This operation repeats for each of the $K$ feature maps. Each maps has it's own $n \times m$ weighting matrix and appropriately shaped bias .
+
+\paragraph*{}The convolution layers allows for several advantages.
+Among these are (i) \textit{sparse-connectivity}: not every single activation (pixel) is connect to every single output pixel, so it is more computationally efficient, (ii) \textit{positional invariance}: key features can be identified regardless of where they are in the layer
+
 % ================
@@
 \subsubsection{2-Dimensional Maximum Pooling Layer}
+
+\paragraph*{}A Maximum Pooling layers simply returns the maximum neuron activation in a group of neurons.
+In the case of 2D Max Pooling, we choose a kernel size to be $m \times n$, just like in the 2D Convolution layer, and extract the maximum value in each window, and then step along accrdoing to the chosen stride size \cite{Loy,Goodfellow}.As an example, consider again figure (\ref{fig-2DConvExample}).
+Using the $2 \times 2$ kernel on the $3 \times 4$ input, each box would then contain the maximum value of the input activations.
+We detail this in fig.
+(\ref{fig-2DMaxPool}):
+\begin{figure}[h]
+\label{fig-2DMaxPool}
+\begin{center}
+\includegraphics[scale=0.6]{../figures/2DConvExample(d)}
+\end{center}
+\caption{The result of 2D maximum-pooling an input array. This image was adapted from Loy, pg. 126 \cite{Loy}}
+\end{figure}
+
+\paragraph*{}Pooling layers, such as maximum pooling, average pooling, or similar are typically placed after a layer or a set of layers of convolution.
+The purpose of this arrangement is to reduce the number of weights, thereby dropping the complexity of the model and ensuring only features with large activation values are preserved \cite{Geron,Loy,Goodfellow}.
 
@@
 
+\subsection{Activation Functions Used in Network Layers}
+\label{sec-ActivationFunctions}
+
+\paragraph*{}Activation functions are a key parameter in the behavior of neural networks.
+As discussed in sec.
+(\ref{sec-Training}) a layer function, $f^{(l)}$ is generally composed of a linear transformation, as in eqn.
+(\ref{eqn-matVectEqn}), and then an element-wise activation function as in eqn.
+(\ref{eqn-elementActivation}).
+It is this second step that allows for neural networks to model the incredibly complex decision boundaries that are found in real-world problems \cite{Geron,Loy}.
+In this section, we detail the activation functions used in out classification neural network.
+
+\subsubsection{Rectified Linear Unit}
+
+\subsubsection{Softmax}
+
+% ================================================================
+
 \newpage
@@
 \subsection{Training a Neural Network}
+\label{sec-Training}
 
@@
 \end{quote}
-Without any external intervention, a model must update itself to improve it's performance at a give task a new information is presented to it.
+Without any human intervention, a model must update itself to improve it's performance at a give task a new information is presented to it.
 To do this, the model must be constructed with a training procedure in mind.
 
-\paragraph*{}If we consider the set of parameters $\theta$ as a the concatenation, of each layer's weighting matrix and bias vector such that:
+\paragraph*{}We consider the set of parameters $\Theta$ as a concatenation of each applicable layer's weighting matrix and bias vector such that:
 \begin{equation}
@@
 \end{equation}
-We can consider each parameter is simply a float-point number.
-Each value for each number contribute to the output of the function.
-In increasing complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is  a very high dimensional parameter-space.
+We can consider each parameter as just float-point number, which is stored in a weight matrix $W^{(l)}$ or bias vector $b^{(l)}$.
+Each value for each parameter contributes to the output of the function.
+In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is a very high dimensional parameter-space.
 
-\paragraph*{}Finally,
+\subsubsection{The Cost Function}
+
+\paragraph*{}Suppose we pass a training sample $x^{0})$, with expected outcome $y$, into the neural network .
+For a perfectly accurate model, we expect the network's final layer, the output layer, $x^{(L-1)}$ to have activations such that $x^{(L-1)} \approx y$.
+Since the starting parameters of a network are often randomly generated, the prediction for training sample $x^(0)}$ is not likely to be similar to $y$ at all.
+We introduce a \textit{Cost Function} into our model that compares the difference between the neural output $x^{(L-1)}$ (also called $y^*$) and the desired, or expected output $y$ \cite{Goodfellow,James}.
+
+\paragraph*{}There are various types of cost functions
+
+\subsubsection{The Optimizer}
 
@@
 
-\paragraph*{}The success of a neural network algorithm is enormously dependent of the strength of the chosen features, rather than the quantity of available data \cite{Geron,Khan,Liu}.
+\paragraph*{}The success of a neural network algorithm is enormously dependent of the strength of the chosen features, rather than the quantity of available data \cite{Geron,Kahn,Liu}.
 We have derived an appropriate set of inputs arrays \textit{[See Section on Features]}, and constructed a neural network architecture to compliment these features.
@@
 
-\paragraph*{}The spectrogram branch is pictured on the left side of fig.
+\paragraph*{}The spectrogram branch is pictured on the right side of fig.
 (\ref{fig-NetworkArchitecture}).
@@
 \label{eqn-shapeX2}
-X_2 \in \mathbb{R}^{(64 \times 23)}
+X_2 \in \mathbb{R}^{(64 \times 20)}
 \end{equation}

### 2020-09-14 Thesis/Sections/Abstract.tex
Rewrote Abstracr

@@
 % Physics 799
-% 5 September 2020 
+% 13 September 2020 
 % ================================
@@
 In this time, a great deal of work has been devoted to studying the performance of various model architectures and producing sets of features that can represent a waveform in a compact, efficient, and non-redundant way \textcolor{red}{Citation?}.
-In this work, we explore a hybrid convolutional neural network (CNN) and multilayer perceptron (MLP) model that uses  features derived from the time-series and frequency-series of a waveform to map audio to a potential source.
-We examine each features used in classification as well as the physical significance and how the choice of feature influences the neural network architecture.
-In doing so, we show how the appropriate combination of architecture and features can produce a reasonable classification performance when mapping sound files to a potential musical instrument source.
+In this work, we show that a spectrogram matrix and a feature-vector with predictors derived from both time-series and frequency-series representations of audio can be used to map that waveform to a potential source.
+This combination of features warrants a model design that combines a convolutional neural network (CNN) and a multilayer perceptron (MLP) to process the spectogram matrix and the feature-vector respectively.
+We detail the significance and behavior of branch of the network and explore how this hybridization architecture along with the chosen features produces improved classification performance while retaining computational practicality.
 

### 2020-09-14 Thesis/Sections/Abstractv3.tex
Updated Abstract v3

% ================================
% Landon Buell
% Kevin Short
% Physics 799
% 13 September 2020 
% ================================

\documentclass[12pt,letterpaper]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}

\begin{document}

% ================================================================

\section{Abstract}

\paragraph*{}Classifying audio signals by source or by content with machine learning has become a topic of much research in the past few years. Methods often involve the production of a spectrogram or feature vector and passing these arrays into a network of a single type such as an Convolutional Neural Network (CNN) or Multilayer Perceptron (MLP). In this work, we explore a new hybrid neural-network architecture that combines the MLP and CNN models to produce a signal classifier with superior performance over models that rely solely one or the other. This network uses two branches, one that uses a CNN to process an image-like spectrogram, and one that uses an MLP to process a feature vector. The output of each branch is concatenated and the two models are merged to produce a single prediction. We detail the production and usage of the spectrogram and predictors, and how they influence the chosen network architecture. We finish with practical example in using this classifier model to match chaotically generated wave forms to real-world musical instruments.

% ================================================================

\end{document}

### 2020-09-19 Thesis/Sections/TheNerualNetwork.tex
Updates to neural network

@@
 \subsubsection{Dense Layer}
+\label{subsec-DenseLayer}
 
@@
 
-\paragraph*{}A neural network's job is to produce an approximation of some function $F$, which we call $F^*$.
-The model must have a procedure for updating the parameters in $\Theta$ to allow for a reasonable approximation of $F$.
+\paragraph*{}A neural network's purpose is to produce a function $F^*$ that approximates an unknown function $F$, using a set of parameters, $\Theta$.
+The model must have a procedure for updating the parameters in $\Theta$ to allow for a reasonably close approximation of $F$.
 To better understand this, we turn to Tom Mitchell's explanation of a learning algorithm \cite{Goodfellow,Mitchell}:
@@
 \label{eqn-Theta}
-\theta = \big\{
-W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)},W^{(L)}, b^{(L-1)},
+\Theta = \big\{
+W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)}, W^{(L)}, b^{(L-1)},
 \big\}
 \end{equation}
-We can consider each parameter as just float-point number, which is stored in a weight matrix $W^{(l)}$ or bias vector $b^{(l)}$.
+Each parameter is floating-point number, which is stored in a weight matrix $W^{(l)}$ or bias vector $b^{(l)}$.
 Each value for each parameter contributes to the output of the function.
-In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is a very high dimensional parameter-space.
+Note that $W^{(l)}$ or $b^{(l)}$, itself is a parameter to train, but rather the entries that make up those structures must be trained.
+In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow}.
 
@@
 
-\paragraph*{}Suppose we pass a training sample $x^{0})$, with expected outcome $y$, into the neural network .
-For a perfectly accurate model, we expect the network's final layer, the output layer, $x^{(L-1)}$ to have activations such that $x^{(L-1)} \approx y$.
-Since the starting parameters of a network are often randomly generated, the prediction for training sample $x^(0)}$ is not likely to be similar to $y$ at all.
-We introduce a \textit{Cost Function} into our model that compares the difference between the neural output $x^{(L-1)}$ (also called $y^*$) and the desired, or expected output $y$ \cite{Goodfellow,James}.
+\paragraph*{}Suppose we pass a training sample, given by the feature-vector $x^{(0)}$, with an expected outcome given by the vector $y$, into the neural network.
+After the network finishes processing, it's output activations are given by the vector $x^{(L-1)}$, also noted at $y^*$.
+For a reasonably trained model, we expect the vector $y^*$ to be "similar" to $y$, indicating that with the provided data, the network has made a valid prediction.
+Conversely, for an untrained network, $y^*$ is not likely to be "similar" to $y$ at all, indicating that the network has made a poor prediction.
 
-\paragraph*{}There are various types of cost functions
+\paragraph*{}To quantify the difference between the model's prediction,m $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $\mathbb{J}(y^*,y)$, to the network \cite{Goodfellow,James}.The cost function, also called a \textit{loss} or \textit{objective} function, compares the neural networks output, $y^*$ and the expected output $y$.
+It returns a single value, usually a floating-point number which measures the \textit{poorness} of the prediction.
+A high cost value indicates a \textit{poor} prediction, and a low cost indicates a reasonable prediction.
+
+\paragraph*{}$\mathbb{J}(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}.
+For this $k$-classes classification task, we choose to use a \textit{Categorical Crossentropy} (CXE) cost function.
+For a single predictions sample, it is defined \cite{Goodfellow}:
+\begin{equation}
+\label{eqn-CategoricalCrossentropy}
+\text{CXE}\big[ y^* , y \big] = - \sum_{i=0}^{k-1} y^*_i \log_{10}(y_i) 
+\end{equation}
+In practice, this operation is performed over a batch of samples and an average is computed and used a \textit{batch loss} \cite{Goodfellow}.
 
 \subsubsection{The Optimizer}
+
+\paragraph*{}We have developed a method for quantifying the difference between a given output $y^*$ and an expected output $y$ with the inclusion of a cost function.
+For a trained neural network, we expect that samples consistently produce a low cost value, particularly on previous unseen inputs, which indicates that the model has appropriately \textit{generalized}.
+The process of training the model is to choose the parameters in $\Theta$ that allows for this behavior of the cost function.
+We then treat the training process of a neural network as a higher dimensional \textit{optimization} problem.
+
+\paragraph*{}The general process of training
 
@@
 \subsection{Chosen Model Architecture}
+\label{sec-Architecture}
 

### 2020-09-23 Thesis/Sections/TheNerualNetwork.tex
Update Neural network Section
- Added notebook to plot figures for thesis

@@
 \documentclass[12pt,letterpaper]{article}
+
 \usepackage{amsmath}
 \usepackage{amssymb}
+
+\usepackage{algorithm}
+\usepackage{algorithmic}
+
 \usepackage{float}
@@
 \usepackage{xcolor}
+
 \usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}
@@
 Conversely, the activations $x^{(L-1)}$ are commonly called the network \textit{output} \cite{Geron,James,Loy}.
+
+\begin{algorithm}[H]
+\caption{Forward propagation system in a standard deep neural network.
+Each iteration in the main \textit{for-loop} represents the execution of a layer, and passing the result to the "next" layer function.
+A practical application of this algorithm should include batches of samples instead of a single sample.
+\textcolor{red}{I will put this some place better soon! It is here for future placement}}
+\label{algFeedForward}
+
+\begin{algorithmic}
+\REQUIRE Network with $L$ layers - $0,1,2,....,L-2,L-1$
+\REQUIRE Set of weighting parameters - $W^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of bias parameters - $b^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of layer activation function - $a^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Input sample - $x^{(0)}$
+
+$Z = \{\} \leftarrow$ array to hold pre-activations \\
+$X = \{\} \leftarrow$ array to hold final activations
+
+\FOR {$l = 1,2,...,L-2,L-1$}
+	\item Compute pre-nonlinear activation
+	\item $z^{(l)} \leftarrow W^{(l)}x^{(l-1)} + b^{(l)}$
+	\item Apply activation function
+	\item $x^{(l)} \leftarrow a^{(l)}[z^{(l)}]$
+	\item Store values for later use in optimizer
+	\item $Z \leftarrow Z.add(z^{(l)})$
+	\item $X \leftarrow X.add(x^{(l)})$
+\ENDFOR
+
+\item Network final prediction is last object in 'act' array.
+\item $y^* \leftarrow x^{(L-1)} = X[-1]$
+\item Return the pre-nonlinear activations and final-nonlinear activations
+\RETURN $Z , X$
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 This layer get's it's name from it's implementation of the mathematical \textit{convolution} function.
-The 2D discrete-convolution of function $A(i,j)$ and $B(i,j)$ is given by \cite{Goodfellow}:
+The 2D discrete-convolution of function or 2D array $A[i,j]$ and $B[i,j]$ is given by \cite{Goodfellow}:
 \begin{equation}
 \label{eqn-convolution}
-C(i,j) = (A * B)(i,j) = \sum_{u}\sum_{v} A(i,j)B(i - u,j - v)
+C[i,j] = (A * B)[i,j] = \sum_{u}\sum_{v} A[i,j]B[i - u,j - v]
 \end{equation}
@@
 
+\paragraph*{}The 1-Dimensional Concatenation Layer, also called 1D-Concat layer takes separate vectors of activations
+
 % ================================================================
@@
 \subsubsection{Rectified Linear Unit}
+
+\paragraph*{}The Rectified Linear Unit (ReLU) activation function acts element-wise on the activations in a given layer.
+If the activation of a neurons is non-zero or non-negative, the value is untouched, otherwise a $0$ is returned.
+For an input activation $x$, ReLU is defined by:
+\begin{equation}
+\label{eqn-ReLU}
+\text{ReLU}\big[x\big] = \max\big(0,x\big) = \left\{
+\begin{array}{ll}
+    x & \text{if\hspace{0.5cm}} x > 0 \\
+    0 & \text{otherwise}
+\end{array} 
+\right.
+\end{equation}
+ReLU is only defined on a real domain. We provide a visualization of the function in fig. (\ref{fig-ReLU}).
+\begin{figure}[H]
+\label{fig-ReLU}
+\begin{center}
+\includegraphics[scale=0.2]{../Figures/RectifiedLinearUnit}
+\end{center}
+\caption{Rectifed Linear Unit (ReLU) activation function}
+\end{figure}
 
@@
 
-\subsubsection{The Optimizer}
+\subsubsection{Gradient Based Learning}
 
@@
 
-\paragraph*{}The general process of training
+\paragraph*{}A neural network uses \textit{indirect optimization}, which contrasts from pure optimization. Deep Learning expert Ian Goodfellow described this \cite{Goodfellow}:
+\begin{quote}
+In most learning scenarios, we care about some performance measure $P$,... We reduce a different cost function, $J(\theta)$ in the hope that doing so will also imprvce $P$.
+\end{quote}
+By choosing an appropriate cost function, and selecting the parameters $\Theta$ that minimize the average cost over a data set, we also assume that doing so minimized the error in the performance $P$.
+
+\paragraph*{}The cost of a sample is dependent on training labels $y$ and the network output $y^*$.
+The output is given by the final layer activation $x^{(L-1)}$, which in turn are produced by the previous layer and so forth, as demonstrated in eqn.
+(\ref{eqn-altLayerFunction}), This recursive nature combined with the dimensionality of the parameter object $\Theta$ makes an analytical solution to the optimization impractical \cite{Geron,Goodfellow,James}.
+We instead optimize with a gradient-based method.
+
+\paragraph*{}We can reduce the cost given a set of paramaters, $J(\Theta)$, by moving each element in $\Theta$ with small steps in the direction of the negative partial derivative of each parameter.
+In the case of the high-dimensional $\Theta$ object, we compute the partial derivative with respect to each weight and bias in the form of the \textit{gradient vector}.
+We denote the gradient of $J$ with respect to the parameters in $\Theta$ as:
+\begin{equation}
+\label{eqn-CostGradient}
+\nabla_{\Theta}\big[ J \big] = 
+\Big[ 	\frac{\partial J}{\partial W^{(0)}}, \frac{\partial J}{\partial b^{(0)}}, 
+		\frac{\partial J}{\partial W^{(1)}}, \frac{\partial J}{\partial b^{(1)}}, \hdots ,
+		\frac{\partial J}{\partial W^{(L-1)}}, \frac{\partial J}{\partial b^{(L-1)}} \Big]^T
+\end{equation}
+Where $\frac{\partial J}{\partial W^{(l)}}$ is taking the partial derivative of each element in the $W^{(l)}$ matrix, and preserves the shape.
+
+\paragraph*{}Due to the nested composition of the network output in eqn.
+(\ref{eqn-FunctionChain}), and subsequently the cost itself, we must use the chain rule of calculus to work backwards through the neural network to compute the partial derivative with respect to each parameter in $\Theta$.
+The process of working backwards to compute each element in the gradient vector is called \textit{back-propagation} \cite{Geron}.
+Below we detail an algorithm in pseudo-code to back-propagate through a fully-connected nueral network, such as the multilayer perceptron outlines in sec.(\ref{sec-NetworkStructre})
+
+\begin{algorithm}[H]
+\caption{Backwards propagation system, in a standard densely connected deep neural network.
+Each iteration in the \textit{for-loop} computes the gradient of the cost function $J$ with respect to the weight and bias arrays.
+Each element in those arrays is then the discrete gradient of that parameter.
+A practical application of this algorithm should include batches of samples instead of a single sample}
+\label{algBackProp}
+
+\begin{algorithmic}
+\REQUIRE Cost/Objective function $J$ and learning rate $\alpha$
+\REQUIRE Set of weighting parameters - $W^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of bias parameters - $b^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of layer activation function - $a^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of layer activation function derivatives - $\partial a^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of pre-nonlinear activation - $Z^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of post-nonlinear activation - $X^{(i)}, i \in \{0,1,....,L-1\}$
+
+Execute forward pass in algorithm (\ref{algFeedForward}) and compute the gradient of the cost with respect to the final layer activations \\
+$dx \leftarrow \nabla_{(y^*)}J(y,y^*)$ \\
+Intialize $\nabla J$ as output object, should have same shape as $\Theta$
+
+\FOR {$L-1,L-2,...,2,1$}
+	\item Compute gradient w.r.t pre-nonlinear activation portion of layer function
+	\item $dx^{(l)} \leftarrow \nabla_{Z^{(l)}}J = dx^{(l)} \odot \partial a^{(l)}[ Z^{(l)} ]$
+	\item Compute gradient w.r.t weighting and bias elements
+	\item $db \leftarrow \nabla_{b^{(l)}}J = dx^{(l)}$
+	\item $dW \leftarrow \nabla_{W^{(l)}}J = dx^{(l)} \cdot X^{(l-1)}$
+
+	\item Add $db$ and $dW$ steps to $\nabla J$ object
+	\item $\nabla J = \nabla J .Add(dW,db)$
+\ENDFOR
+
+\item Return gradient w.r.t to each parameter in $\Theta$
+\RETURN $\nabla J$
+
+\end{algorithmic}
+\end{algorithm}
+
+\paragraph*{}After (i) computing the gradient, we can scale is by a desired learning rate, $\alpha$ and (ii) add it element-wise to the exisitint elements in $\Theta$.
+By repeating steps (i) and (ii) in sucession, we gradually drive the cost function to produces consistently lower and lower values.
+This is called \textit{gradient descent} and is the basis for many optimization algorithms.
+We show the general update rule on iteration $(i)$ for gradient based learning over a batch of $m$ samples in eqn.
+(\ref{eqn-GradientLearning}).
+\begin{equation}
+\label{eqn-GradientLearning}
+\Theta^{(i)} = \Theta^{(i-1)} + (-\alpha)\frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big] \\
+\end{equation}
+
+\subsubsection{The Optimizer}
+
+\paragraph*{}For this project, we employ an \textit{Adaptive-Moments} optimization algorithm, also called \textit{ADAM} for short.
+It is a powerful variant of algorithms with an adaptive learning rate.
+It tracks an exponentially decaying average of past gradients, as well as exponentially decaying average of past squared gradients \cite{Geron}.
+As an extra step, ADAM also includes correction factors for both first order moments, and uses a combination of them to update the network parameters \cite{Geron,Goodfellow}.
+For a given iteration $(i)$, The ADAM update is given:
+\begin{equation}
+\label{eqn-ADAMupdate}
+\begin{split}
+s^{(i)} &= \rho_1 s^{(i-1)} + (1 - \rho_1) \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]  \\
+r^{(i)} &= \rho_2 r^{(i-1)} + (1 - \rho_2) \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big] \odot
+							\frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]  \\
+s'^{(i)} &= \frac{s^{(i)}}{1-\rho_1^t} \\
+r'^{(i)} &= \frac{r^{(i)}}{1-\rho_2^t} \\
+\Theta^{(i)} &= \Theta^{(i-1)} + (-\alpha)\frac{s'^{(i)}}{\sqrt{r'^{(i)}}+\delta} \\
+\end{split}
+\end{equation}
+
+\paragraph*{}ADAM has experimentally shown to be a very powerful and robust optimizer useful for a wide range of tasks.
+Because of the two decay constants $\rho_1$ and $\rho_2$, we an compound and accumulate the values of past gradients to continue to push the cost to lower and lower values, even if the magnitude of the gradient becomes very small \cite{Geron}.
+
+\begin{algorithm}[H]
+\caption{Adaptive-Moments (ADAM) optimizer for a neural network}
+\label{algAdaGrad}
+
+\begin{algorithmic}
+\REQUIRE Step size $\alpha$
+\REQUIRE Small constant $\delta$ for numerical stabilization, usually about $10^{-7}$.
+\REQUIRE constants $\rho_1$, $\rho_2$ used got exponential decay rates, usually $0.9$ and $0.999$ respectively.
+\REQUIRE Subroutine/function to compute gradient of cost function.
+\REQUIRE Mini-batch size, $m$
+\REQUIRE Stopping criterion $S$
+
+Initialize moment variables and iteration counter $s = 0$, $r = 0$, $i = 0$ \\
+
+\WHILE {Stopping Criterion $S$ is \FALSE}
+	\item Extract a mini-batch of $m$ samples from larger data set $X$. $[x^{(0)},x^{(1)},...,x^{(m-1)}]$ and corresponding target values 
+	$[y^{(0)},y^{(1)},...,y^{(m-1)}]$.
+	\item Compute numerical gradient estimate of each sample in batch. This can be done with standard back-propagation in algorithm (\ref{algBackProp}) and 			 	normalize by batch size $m$:
+	\item $\nabla J \leftarrow \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]$
+
+	\item Compute first bias moment: $s \leftarrow \rho_1 s + (1 - \rho_1) \nabla J$
+	\item Compute second bias moment: $r \leftarrow \rho_2 s + (1 - \rho_2) \nabla J \odot \nabla J$
+	\item First bias correction: $s' \leftarrow \frac{s}{1 - \rho_1^i}$
+	\item Second bias correction: $r' \leftarrow \frac{r}{1 - \rho_2^i}$
+
+	\item Compute And Apply update:	$\Delta \Theta = (-\alpha) \frac{s'}{\sqrt{r'} + \delta}$
+	\item $\Theta = \Theta + \Delta \Theta$	
+	\item Update Iteration number: $i \leftarrow i + 1$
+\ENDWHILE
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 \paragraph*{}The success of a neural network algorithm is enormously dependent of the strength of the chosen features, rather than the quantity of available data \cite{Geron,Kahn,Liu}.
-We have derived an appropriate set of inputs arrays \textit{[See Section on Features]}, and constructed a neural network architecture to compliment these features.
+We have derived an appropriate set of inputs arrays \textcolor{blue}{See Section on Features}, and constructed a neural network architecture to compliment these features.
+From these two input arrays, one being a matrix and the other being a column-vector, we have produced a \textit{multimodal neural network}, that process the two inputs, and combines separate neural networks into a single model to produce a one prediction resulting from both inputs.
 
 \paragraph*{}The full classification neural network used for this project consists of two distinct entry points.
-This means that rather than presenting the network with one set of input data, $X$, we present the network with two different arrays, $X_1$ and $X_2$.
-Both arrays are a produce of the same audio file sound wave, and thus share a common training label.
-Each of the two entry points feed into their own, non-related set of layer functions.
-The second-to-last layer, the outputs from both neural networks are concatenated into a single dense layer, which is then passed into the output layer, which contains $k$ neurons, one of reach unique class \cite{Loy,Geron}.
+Rather than presenting the network with one set of input data, $X$, we present the network with two different arrays, $X_1$ and $X_2$.
+Both arrays are a product of the same audio file sound wave, and thus share a common training label, $y$.
+Each of the two entry layers leads to it's own branch and the given information is process roughly in parallel.
+Once a certain number of layer functions have been applied, each arm of the neural network is left with a single dense layer of activations.
+These two activation vectors are concatenated into a single new dense layer, and then passed through one final layer to generate the model's final output.
 A visual representation of this architecture can be found in fig.
@@
 
-\paragraph*{}The spectrogram branch is pictured on the right side of fig.
+\paragraph*{}The spectrogram branch is pictured on the left side of fig.
 (\ref{fig-NetworkArchitecture}).
@@
 
-\paragraph*{}
+\paragraph*{}The last layer in eachof the two branches is a ReLu-activated Dense layer containing 64 neurons. The activations are concatenated
 

### 2020-09-23 Thesis/Sections/TheNerualNetwork.tex
Updates to NueralNetwork Thesis Section

@@
 
-\paragraph*{}To quantify the difference between the model's prediction,m $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $\mathbb{J}(y^*,y)$, to the network \cite{Goodfellow,James}.The cost function, also called a \textit{loss} or \textit{objective} function, compares the neural networks output, $y^*$ and the expected output $y$.
+\paragraph*{}To quantify the difference between the model's prediction, $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $J(y^*,y)$, to the network \cite{Goodfellow,James}.
+The cost function, also called a \textit{loss} or \textit{objective} function, compares the neural networks output, $y^*$ and the expected output $y$.
 It returns a single value, usually a floating-point number which measures the \textit{poorness} of the prediction.
@@
 
-\paragraph*{}$\mathbb{J}(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}.
+\paragraph*{}$J(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}.
 For this $k$-classes classification task, we choose to use a \textit{Categorical Crossentropy} (CXE) cost function.
@@
 It tracks an exponentially decaying average of past gradients, as well as exponentially decaying average of past squared gradients \cite{Geron}.
-As an extra step, ADAM also includes correction factors for both first order moments, and uses a combination of them to update the network parameters \cite{Geron,Goodfellow}.
+This produces a far more aggressive optimizer at a higher computational cost.
 For a given iteration $(i)$, The ADAM update is given:

### 2020-09-24 Thesis/Sections/Methodology.tex
Updatess to Methodology section

--- 2020-09-19 Thesis/Sections/TheNerualNetwork.tex
@@
 % Physics 799%
-% 30 July 2020 
+% 24 Sept 2020 
 % ================================
@@
 
-\section{The Neural Network}
-\label{sec-TheNeuralNetwork}
+\section{Methodology}
+\label{sec-Methodology}
+
+\paragraph*{}We outline and detail the steps taken to execute this project from beginning to end.
 
@@
 
-\subsection{An Introduction to Neural Networks}
-\label{sec-NerualNetworkIntro}
+\subsection{Designing the Function}
 
-\paragraph*{}The task of algorithmically matching sound files to musical instrument classes in exceedingly difficult through conventional computer programming techniques.
-Because of the complexity of sound waves, brain's interpretation them, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
-Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an architecture that allows for a computer to \textit{learn} and change and update itself as it is presented with more data.
-Such an algorithm exists in the form of a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine}.
-
-\paragraph*{}A neural network is a mathematical function that seeks to produce an approximation $F^*$, of some usually unknown function $F$ .
-For audio recognition, $F$ is some function, or series of functions, that occurs in the brain which allows for a listener to take the sensation of audio, and map it to a known musical instrument.
-For a neural network, a model must construct an approximate function $F^*$ using a set of parameters $\Theta$, which allows the model to map a series of inputs, $x$ (called \textit{features}) to a series of outputs, $y$ (called \textit{predictions}) \cite{Goodfellow,James,Virtanen}.
-
-\paragraph*{}Former YouTube video classification team lead, and current machine learning consultant, Aurelien Geron writes about the relationship between biological brains and mathematical neural networks \cite{Geron}:
-\begin{quote}
-Birds inspired us to fly, burdock plants inspired velcro and nature has inspired many other inventions.
-It seems only logical, then, to look to the brain's architecture for inspiration on how to build an intelligent machine.
-\end{quote}
-The result of such an analogy is a computer program that is reminiscent of the brain.
-
-\paragraph*{}Over the course of their lives, humans will learn to map sounds to sources almost effortlessly.
-Given an example, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olsen,White}.
-We can simplify the idea of humans recognizing sound as some function or operation that occurs within the brain, accepting an input sound, and produces an output label.
-Similarly, a neural network can be constructed, presented with \textit{features} of multiple, labeled sound waves and learns a set of parameters $\Theta$ that allows for the mapping to a source.
-
-\paragraph*{}For this particular project, a neural network has been constructed to perform a \textit{classification} task.
-A classification task involves mapping the input data, $x$ to one of $k$ possible \textit{classes}, each represented by an integer, $0$ through $k-1$.
-Each of the $k$ classes represents a particular musical instrument that could have produced the sound-wave in the audio file.
+\paragraph*{}Consider the biological process of hearing a sound wave and matching it to a source.
+We can model this behavior by some unknown function $F$.
+We produce an approximation of that function $F^*$ that can map the contents of a sound file that have been generated by a chaotic synthesizer to a potential source.
+For a set of inputs $\vec{x} = \big\{ x_0 , x_1 , x_2 , ...
+, x_{p-1} \big\}$ and a set of classes $0$ through $k-1$, we denote this function as:
+\begin{equation}
+\label{eqn-MappingFunction}
+F^*: \vec{x} \rightarrow \big\{ 0 , 1 , 2 , ... , k-1 \big\}
+\end{equation}
 
@@
 
-\newpage
+\subsection{Collecting and Pre-processing Raw Data}
 
-\subsection{The Structure of a Neural Network}
-\label{sec-NetworkStructre}
+\paragraph*{}In order to train the Multimodal neural network to identify musical instrument sources, we need a suitable data set to present to the model.
+University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \textcolor{blue}{Citations!}.
+These contain short segments of musical instruments performing a single note or a collection of notes in succession.
 
-\paragraph*{}A Neural Network is simply a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Goodfellow,Loy}.
-Each layer represents an operation that takes some real input, typically an array of real double-precision floating-point numbers, and returns a modified array of new double-precision floating-point numbers.
-The exact nature of this operation can be very different depending on the layer type or where it sits within the network.
-It is this process of transforming inputs successively in a particular order until an output is attained \cite{Geron,Loy}.
-This output encodes the models final "decision" given a unique input.
-
-\paragraph*{}Other than inspiration from the brain, Neural Networks are name \textit{networks} because of their nested composition nature.
-The model can be represented by a linear or acyclic computational graph which successively maps exactly how the repeated composition is structured.
-In a \textit{feed-forward network}, information is passes successively in one direction.
-For example functions could be chained together such as \cite{Goodfellow}
-\begin{equation}
-\label{eqn-FunctionChain}
-F(x) = f^{(L-1)}\big[f^{(L-2)}\big[...f^{(1)}\big[f^{(0)}\big[x]\big]\big]...\big]\big]
-\end{equation}
-Where each function $f^{(l)}$ represents a layer of the network model.
-The number of layers in a neural network is referred to as the network \textit{depth}.
-The dimensionality of each layer is referred to as the network \textit{width} \cite{Geron,Loy}.
-
-\paragraph*{}A network model that contains $L$ unique layers is said to be an $L$-Layer Neural Network, with each layer usually indexed by a superscipt, $0$ through $L-1$.
-Layer $0$ is said to be the \textit{input layer} and layer $L-1$ is said to be the \textit{output layer}.
-The function that represents a layer $(l)$ is given by
-\begin{equation}
-\label{eqn-LayerFunction}
-f^{(l)} : x \in \mathbb{R} \rightarrow y \in \mathbb{R}
-\end{equation}
-The value of $x$ can also be index by layer, we call the array $x^{(l)}$ the \textit{activations} of layer $l$ \cite{Goodfellow,Loy}.
-
-\paragraph*{}The model is recursive by nature, the activations from one layer, $l-1$, are used to directly produce the activations of the next successive layer $l$.
-Thus eqn.
-(\ref{eqn-LayerFunction}) can be alternatively written as:
-\begin{equation}
-\label{eqn-altLayerFunction}
-f^{(l)} : x^{(l-1)} \in \mathbb{R} \rightarrow x^{(l)} \in \mathbb{R}
-\end{equation}
-The array of activations, $x^{(0)}$, is the raw input given the neural network, most commonly called \textit{features}.
-Conversely, the activations $x^{(L-1)}$ are commonly called the network \textit{output} \cite{Geron,James,Loy}.
+\paragraph*{}To ensure that these data sets are roughly homogeneous, we read each sample from it's original format, \textit{.aif}, \textit{.mp3}, or similar, and rewrite each sample as a new \textit{.wav} files, sampled at 44.1 kHz, with a 16 bit depth \textcolor{red}{check this!}.
+This ensures that all data will have a consistent format when features are extracted.
+We also use this stage to ensure that each audio file has a correct label, and to determine the number of unique output classes.
 
@@
 
-\newpage
+\subsection{Designing Classification Features}
 
-\subsection{Layers Used in Classification Neural Network}
-\label{sec-Layers}
-
-\paragraph*{}As stated previously, a neural network is composed of a series of functions that are called successively to transform features (an input) into a prediction (an output).
-As shown in eqn.
-(\ref{eqn-altLayerFunction}), each function feeds directly into the next as to form a sort of computational graph \cite{Goodfellow}.
-
-\paragraph*{}Typically, a layer function can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation.
-This activation function typically is a non-linear function which allows for the modeling of increasingly complex decision-boundaries.
-Step (i.) is usually in the form of a matrix-vector equation:
-\begin{equation}
-\label{eqn-matVectEqn}
-z^{(l)} = W^{(l)} x^{(l-1)} + b^{(l)}
-\end{equation}
-Where $W^{(l)}$ is the \textit{weighting-matrix} for layer $l$, $b^{(l)}$ is the \textit{bias-vector} for layer $l$, $z^{(l)}$ are the \textit{linear-activations} for layer $l$ and $x^{(l-1)}$ is the final activations for layer $l-1$.
-Step (ii.) is usually given by some \textit{activation function}:
-\begin{equation}
-\label{eqn-elementActivation}
-x^{(l)} = \sigma^{(l)} \big[ z^{(l)} \big]
-\end{equation}
-Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-matVectEqn}).
-$\sigma^{(l)}$ is some activation function, which is often use to enable the modeling of more complex-decision boundaries.
-
-\paragraph*{}The combination of eqn.
-(\ref{eqn-matVectEqn}) and eqn.
-(\ref{eqn-elementActivation}), for a layer $l$ , make up the function represented by that layer, as in eqn.
-(\ref{eqn-altLayerFunction}).
-Below, we discuss and describe the types of layer functions that are used to produce the classification model in this project.
-
-% ================
-
-\subsubsection{Dense Layer}
-\label{subsec-DenseLayer}
-
-\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer, or \textit{Fully-Connected} layer for short, was one of the earliest function types used in artificial neural network models \cite{Geron2,Loy}.
-They are among the most commonly used layer types.
-A dense layer is composed of a layer of \textit{artifical neurons}, each of which holds a numerical value within it, called the \textit{activation} of that neuron.
-This idea was developed back from McCulloch and Pitts' work \cite{McCulloch}, and was expanded upon by Frank Rosenblatt in  1957 \cite{Geron}.
-
-\paragraph*{}We model a layer of neurons as a vector of floating-point numbers.
-Typically, it is required that the array be one-dimensional.
-Suppose a layer $(l)$ contains $n$ artificial neurons.
-We denote the array that hold those activations as $x^{(l)}$ and is given by:
-\begin{equation}
-\label{layer-DenseNeurons}
-\vec{x}^{(l)} = \Big[ x_0, x_1, x_2, \hdots , x_{n-2}, x_{n-1} \Big]^T
-\end{equation}
-The activation of each entry is given by a linear-combination of activations from the previous layer, as outlined in eqn.(\ref{eqn-matVectEqn}) and eqn.(\ref{eqn-elementActivation}).
-
-\paragraph*{}Suppose the layer $l-1$ contains $m$ neurons.
-Then the weighting-matrix, $W^{(l)}$ has shape $m \times n$, the bias-vector $b^{(l)}$ has shape $m \times 1$.
-We can denote the function in a similar manner to eqn.(\ref{eqn-altLayerFunction}) as:
-\begin{equation}
-\label{eqn-FunctionDense}
-f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(m \times 1)} \rightarrow x^{(l)} \in \mathbb{R}^{(n \times 1)}
-\end{equation}
-
-Thus for a dense layer $l$, the exact values of each activation is given by \cite{Geron,Loy}:
-\begin{equation}
-\begin{bmatrix}
-x_0 \\ x_1 \\ \vdots \\ x_{n-1}
-\end{bmatrix}^{(l)} =
-\sigma^{(l)} \Bigg(
-\begin{bmatrix}
-w_{0,0} & w_{0,1} & \hdots & w_{0,m-1} \\
-w_{1,0} & w_{1,1} & \hdots & w_{1,m-1} \\
-\vdots & \vdots & \ddots & \vdots  \\
-w_{n-1,0} & w_{n-1,1} & \hdots & w_{n-1,m-1} 
-\end{bmatrix}^{(l)} 
-\begin{bmatrix}
-x_0 \\ x_1 \\ \vdots \\ x_{m-1}
-\end{bmatrix}^{(l-1)} +
-\begin{bmatrix}
-b_0 \\ b_1 \\ \vdots \\ b_{n-1}
-\end{bmatrix}^{(l)} \Bigg)
-\end{equation}
-or more compactly:
-\begin{equation}
-\label{eqn-DenseFeedForward}
-x^{(l)} = \sigma^{(l)} \Big( W^{(l)} x^{(l-1)} + b^{(l)} \Big)
-\end{equation}
-Eqn. (\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}.
-
-% ================
-
-\subsubsection{2-Dimensional Convolution Layer}
-
-\paragraph*{}Convolution layers emerged from studying the brain's visual cortex, and have been used from image recognition related tasks for around 40 years.
-\cite{Geron,Loy}).
-This layer get's it's name from it's implementation of the mathematical \textit{convolution} function.
-The 2D discrete-convolution of function $A(i,j)$ and $B(i,j)$ is given by \cite{Goodfellow}:
-\begin{equation}
-\label{eqn-convolution}
-C(i,j) = (A * B)(i,j) = \sum_{u}\sum_{v} A(i,j)B(i - u,j - v)
-\end{equation}
-Note that convolution is commutative: $(A * B) = (B * A)$.
-We implement a convolutional layer $f^{(l)})$, by creating a series of $K$ weighting matrices, called \textit{filters}, each of size $m \times n$, where $m,n \in \mathbb{Z}$.
-Often we choose $m = n$ and call the shape the \textit{convolution kernel size} \cite{Loy, Goodfellow}.
-
-\paragraph*{}In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(N \times M)}$, the convolutions filters "step" through the input data and repeatedly compute the element-wise product of each $m \times n$ weighting kernel, and the local activation of the $x^{(l-1)}$ array.
-The step size in each of the 2-dimension is known as the \textit{stride}.
-Each of the $K$ filters is used to generate a $m \times n$ feature map from the input activation.
-For an appropriately trained network, some filters may be dedicated to detecting vertical lines, horizontal lines, sharp edges, areas of mostly one color, etc.
-\cite{Loy,Geron}.
-
-\paragraph*{}In general, for an $N \times M$ input, with kernel size $m \times n$, with stride size $1 \times 1$, and $K$ feature maps.
-\begin{equation}
-f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(N \times M)} \rightarrow
-x^{(l)} \in \mathbb{R}^{([N-n+1] \times [M-m+1] \times K)}
-\end{equation}
-As an example, consider a single filter map over input $x \in \mathbb{R}^{(4 \times 3)}$ and filter map $W \in \mathbb{R}^{(2 \times 2)}$ as shown in fig. (\ref{fig-2DConvExample}):
-\begin{figure}[H]
-\label{fig-2DConvExample}
-\begin{center}
-\begin{subfigure}{0.45\textwidth}
-\includegraphics[scale=0.6]{../figures/2DConvExample(a)}
-\caption{Input Activations}
-\end{subfigure}
-\begin{subfigure}{0.45\textwidth}
-\includegraphics[scale=0.6]{../figures/2DConvExample(b)}
-\caption{Convolution Filter}
-\end{subfigure}
-\begin{subfigure}{0.9\textwidth}
-\centering
-\includegraphics[scale=0.6]{../figures/2DConvExample(c)}
-\caption{Convolution Result}
-\end{subfigure}
-\end{center}
-\caption{The result of convolving an input (a) with an filter map (b) is a new set of activations (c). This Image was adapted from Goodfellow, pg. 325 \cite{Goodfellow}}
-\end{figure}
-Note that formal implementations include a bias vector and an activation function.
-
-\paragraph*{}For 2D convolution over input $x^{(l-1)}$ with feature map $W^{(l)}_k$, producing activations $x^{(l)}$, we compute the activations $x^{(l)}_{k}$ as \cite{Goodfellow}
-\begin{equation}
-\label{eqn-ConvFeedForward}
-x^{(l)}_k = \sigma^{(l)}\bigg[ \Big( \sum_{u=0}^{m-1} \sum_{v=0}^{n-1} x^{(l-1)}(i,j) W^{(l)}_k(i - u,j - v) \Big) + b^{(l)}_k \bigg]
-\end{equation}
-\textcolor{red}{Please check my math here!}
-This operation repeats for each of the $K$ feature maps. Each maps has it's own $n \times m$ weighting matrix and appropriately shaped bias .
-
-\paragraph*{}The convolution layers allows for several advantages.
-Among these are (i) \textit{sparse-connectivity}: not every single activation (pixel) is connect to every single output pixel, so it is more computationally efficient, (ii) \textit{positional invariance}: key features can be identified regardless of where they are in the layer
-
-% ================
-
-\subsubsection{2-Dimensional Maximum Pooling Layer}
-
-\paragraph*{}A Maximum Pooling layers simply returns the maximum neuron activation in a group of neurons.
-In the case of 2D Max Pooling, we choose a kernel size to be $m \times n$, just like in the 2D Convolution layer, and extract the maximum value in each window, and then step along accrdoing to the chosen stride size \cite{Loy,Goodfellow}.As an example, consider again figure (\ref{fig-2DConvExample}).
-Using the $2 \times 2$ kernel on the $3 \times 4$ input, each box would then contain the maximum value of the input activations.
-We detail this in fig.
-(\ref{fig-2DMaxPool}):
-\begin{figure}[h]
-\label{fig-2DMaxPool}
-\begin{center}
-\includegraphics[scale=0.6]{../figures/2DConvExample(d)}
-\end{center}
-\caption{The result of 2D maximum-pooling an input array. This image was adapted from Loy, pg. 126 \cite{Loy}}
-\end{figure}
-
-\paragraph*{}Pooling layers, such as maximum pooling, average pooling, or similar are typically placed after a layer or a set of layers of convolution.
-The purpose of this arrangement is to reduce the number of weights, thereby dropping the complexity of the model and ensuring only features with large activation values are preserved \cite{Geron,Loy,Goodfellow}.
-
-% ================
-
-\subsubsection{1-Dimensional Flattening Layer}
-
-\paragraph*{}A flattening layer is used to compress an array with two or more dimensions down into a single dimension.
-For a flattening layer $l$, multidimensional activations in layer $l-1$ are compressed down into a single dimensional array.
-We can use function notation to express this as:
-\begin{equation}
-\label{eqn-FlattenFunction}
-f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(M \times N \times ....)} \rightarrow
-x^{(l)} \in \mathbb{R}^{(MN...\times 1)}
-\end{equation}
-The numerical value of each activation is left unchanged.
-For a layer with activation shape$N \times M$, the resulting activations are reshaped into $NM \times 1$ as shown in eqn (\ref{eqn-FlattenFunction}).
-
-\paragraph*{}Flattening Layer are most commonly used to prepare activations for entry into dense layer or series of dense layers.
-For example, 2D or 3D images are typically processed with 2D convolution, which may output a 2D or 3D array of activations.
-Those values are then flattened to 1 dimensions, which can then be passed into dense layers for further processing.
-
-% ================
-
-\subsubsection{1-Dimensional Concatenation Layer}
+\paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of classification features.
+These are properties of wave forms that can be represented by a numerical value or several numerical values and are used as the primary tool in classification.
+There are used in place of a full waveform to represent a file's contents We use tools from physics, mathematics, and signal processing to define and explore a comprehensive set of features that enables a high performance of the classifier.
 
@@
 
-\subsection{Activation Functions Used in Network Layers}
-\label{sec-ActivationFunctions}
+\subsection{Designing A Complementary Network Architecture}
 
-\paragraph*{}Activation functions are a key parameter in the behavior of neural networks.
-As discussed in sec.
-(\ref{sec-Training}) a layer function, $f^{(l)}$ is generally composed of a linear transformation, as in eqn.
-(\ref{eqn-matVectEqn}), and then an element-wise activation function as in eqn.
-(\ref{eqn-elementActivation}).
-It is this second step that allows for neural networks to model the incredibly complex decision boundaries that are found in real-world problems \cite{Geron,Loy}.
-In this section, we detail the activation functions used in out classification neural network.
-
-\subsubsection{Rectified Linear Unit}
-
-\subsubsection{Softmax}
+\paragraph*{}With the appropriate set of features designed, and the number of output determined, we can organize the structure of the neural network function.
+We construct a multimodal neural network than processes two input arrays derived from the same audio sample that share a common label.
+This network is designed to handle and process each respective input independently, and concatenate the results to produce a single output.
 
@@
 
-\newpage
+\subsection{Testing and Evaluating Network Performance}
 
-\subsection{Training a Neural Network}
-\label{sec-Training}
-
-\paragraph*{}A neural network's purpose is to produce a function $F^*$ that approximates an unknown function $F$, using a set of parameters, $\Theta$.
-The model must have a procedure for updating the parameters in $\Theta$ to allow for a reasonably close approximation of $F$.
-To better understand this, we turn to Tom Mitchell's explanation of a learning algorithm \cite{Goodfellow,Mitchell}:
-\begin{quote}
-A computer program is said to learn from experience $E$ with respect to some class of tasks $T$ and performance measure $P$, if it's performance at tasks in $T$, as measured by $P$, improves with experience $E$.
-\end{quote}
-Without any human intervention, a model must update itself to improve it's performance at a give task a new information is presented to it.
-To do this, the model must be constructed with a training procedure in mind.
-
-\paragraph*{}We consider the set of parameters $\Theta$ as a concatenation of each applicable layer's weighting matrix and bias vector such that:
-\begin{equation}
-\label{eqn-Theta}
-\Theta = \big\{
-W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)}, W^{(L)}, b^{(L-1)},
-\big\}
-\end{equation}
-Each parameter is floating-point number, which is stored in a weight matrix $W^{(l)}$ or bias vector $b^{(l)}$.
-Each value for each parameter contributes to the output of the function.
-Note that $W^{(l)}$ or $b^{(l)}$, itself is a parameter to train, but rather the entries that make up those structures must be trained.
-In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow}.
-
-\subsubsection{The Cost Function}
-
-\paragraph*{}Suppose we pass a training sample, given by the feature-vector $x^{(0)}$, with an expected outcome given by the vector $y$, into the neural network.
-After the network finishes processing, it's output activations are given by the vector $x^{(L-1)}$, also noted at $y^*$.
-For a reasonably trained model, we expect the vector $y^*$ to be "similar" to $y$, indicating that with the provided data, the network has made a valid prediction.
-Conversely, for an untrained network, $y^*$ is not likely to be "similar" to $y$ at all, indicating that the network has made a poor prediction.
-
-\paragraph*{}To quantify the difference between the model's prediction,m $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $\mathbb{J}(y^*,y)$, to the network \cite{Goodfellow,James}.The cost function, also called a \textit{loss} or \textit{objective} function, compares the neural networks output, $y^*$ and the expected output $y$.
-It returns a single value, usually a floating-point number which measures the \textit{poorness} of the prediction.
-A high cost value indicates a \textit{poor} prediction, and a low cost indicates a reasonable prediction.
-
-\paragraph*{}$\mathbb{J}(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}.
-For this $k$-classes classification task, we choose to use a \textit{Categorical Crossentropy} (CXE) cost function.
-For a single predictions sample, it is defined \cite{Goodfellow}:
-\begin{equation}
-\label{eqn-CategoricalCrossentropy}
-\text{CXE}\big[ y^* , y \big] = - \sum_{i=0}^{k-1} y^*_i \log_{10}(y_i) 
-\end{equation}
-In practice, this operation is performed over a batch of samples and an average is computed and used a \textit{batch loss} \cite{Goodfellow}.
-
-\subsubsection{The Optimizer}
-
-\paragraph*{}We have developed a method for quantifying the difference between a given output $y^*$ and an expected output $y$ with the inclusion of a cost function.
-For a trained neural network, we expect that samples consistently produce a low cost value, particularly on previous unseen inputs, which indicates that the model has appropriately \textit{generalized}.
-The process of training the model is to choose the parameters in $\Theta$ that allows for this behavior of the cost function.
-We then treat the training process of a neural network as a higher dimensional \textit{optimization} problem.
-
-\paragraph*{}The general process of training
+\paragraph*{}We divide the raw data set up into a training and testing sets.
+We employ cross-validation and compute the results of performance metrics to ensure that out model is making reliable predictions, and generalize appropriately.
+In this stage, we also choose the value of hyper-parameters, activation functions and layer widths to best compliment the chosen features.
+This process is repeated and expanded upon until we have produced a model with a sufficient performance.
 
@@
 
-\newpage
+\subsection{Running Predictions of Chaotic Synthesizer Files}
 
-\subsection{Chosen Model Architecture}
-\label{sec-Architecture}
-
-\paragraph*{}The success of a neural network algorithm is enormously dependent of the strength of the chosen features, rather than the quantity of available data \cite{Geron,Kahn,Liu}.
-We have derived an appropriate set of inputs arrays \textit{[See Section on Features]}, and constructed a neural network architecture to compliment these features.
-
-\paragraph*{}The full classification neural network used for this project consists of two distinct entry points.
-This means that rather than presenting the network with one set of input data, $X$, we present the network with two different arrays, $X_1$ and $X_2$.
-Both arrays are a produce of the same audio file sound wave, and thus share a common training label.
-Each of the two entry points feed into their own, non-related set of layer functions.
-The second-to-last layer, the outputs from both neural networks are concatenated into a single dense layer, which is then passed into the output layer, which contains $k$ neurons, one of reach unique class \cite{Loy,Geron}.
-A visual representation of this architecture can be found in fig.
-(\ref{fig-NetworkArchitecture}).
-
-\begin{figure}[H]
-\label{fig-NetworkArchitecture}
-\begin{center}
-\includegraphics[scale=0.45]{../Figures/NeuralNetworkArchitecture}
-\end{center}
-\caption{The developed architecture of the audio file classification neural network.
-The Left branch process an image-like input, the right branch processes a vector-like input.
-The activations are then merged, and then a single output is produced}
-\end{figure}
-
-% ================
-
-\subsubsection{The Spectrogram Branch}
-
-\paragraph*{}The spectrogram branch is pictured on the right side of fig.
-(\ref{fig-NetworkArchitecture}).
-A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olsen,Kahn}.
-\textcolor{blue}{Details on the creating of the spectrogram can be found in the \textit{features} section of this document.}
-
-\paragraph*{}The input layer of the spectrogram accepts a 4-Dimensional array.
-The axes, in order of indexing, represents (i) the size of the \textit{mini-batch} of samples, (ii) the pixel width of each sample, (iii) the pixel height of each sample, and (iv) the number of channels in each sample.
-As a model hyper-parameter, we have chosen each batch to contain $64$ samples.
-We have also chosen to truncate time and frequency axes (ii \& iii) to contain $560$ frequency bins, and $256$ time-frames.
-Each image also contains a single channel, which make it gray-scale when visualized.
-We can denote the 4D shape of the input object into this branch as:
-\begin{equation}
-\label{eqn-shapeX1}
-X_1 \in \mathbb{R}^{(64 \times 560 \times 256 \times 1)}
-\end{equation}
-Any other shape will be rejected by the model, and an error is raised.
-
-\paragraph*{}After the input layer assert the appropriate shape, the array $X_1$, which is a collection of $64$ spectrograms, is passed into the first of three \textit{Convolution Layer Groups}.
-These layer groups are inspired from the \textit{VGG-16 Neural Network} architecture \textcolor{red}{[citation needed]}.
-Each convolution layer group in composed of three individual layers:
-\begin{enumerate}
-\item A 2-Dimensional Convolution layer, using $32$ filters, a $3 \times 3$ kernel, a $1 \times 1$ step size, and a ReLU activation function,
-\item A 2-Dimensional Convolution layer, using $32$ filters, a $3 \times 3$ kernel, a $1 \times 1$ step size, and a ReLU activation function,
-\item A 2-Dimensional Maximum Pooling layer using a $3 \times 3$ pooling size, and an Identity activation function
-\end{enumerate}  
-The Convolution layers convoluted over the middle two axes of the data (over space and time in the spectrogram).
-
-\paragraph*{}By grouping layers in this structure, each of the $32$ filters passes over a $3 \times 3$ area, and then again. The result is
-
-% ================
-
-\subsubsection{The Perceptron Branch}
-
-\paragraph*{} The Perceptron branch is picture on the right side of fig.
-(\ref{fig-NetworkArchitecture}), notice that it is considerably smaller in side and complexity than it's neighbor.
-Rather than accept an image-like input, the perception simply takes a vector-like input of properties of a larger data set - in this case, each waveform.
-We call these properties \textit{features} \cite{Geron,Kahn,Virtanen}.
-\textcolor{blue}{Details on the creating of these features can be found in the \textit{features} section of this document.}
-
-\paragraph*{}The input layer of the perceptron accepts a 2-Dimensional array.
-The axes, in order of indexing, represent (i) the size of the \textit{mini-batch} of samples, (ii) the number of features for each sample.
-We use the same model hyper-paramater of $64$ samples per batch, and have developed $23$ unique clssification features that have been derived from time-space and frequency-space representations of the audio file data.
-We can denote the 2D shape if the input object into this branch as:
-\begin{equation}
-\label{eqn-shapeX2}
-X_2 \in \mathbb{R}^{(64 \times 20)}
-\end{equation}
-Again, any other shape will be rejected by the model, and an error is raised.
-
-% ================
-
-\subsubsection{The Final Output Branch}
-
-\paragraph*{}
-
-% ================================================================
+\paragraph*{}Once we have established a suitable performance of the model, we allow the model to run predictions on the un-labeled chaotic synthesizer wave forms.
+We output the prediction results to a file, and compare the neural network predictions against human predictions.
+If further corrections are needed, we revert and re-deign the features, architecture, or hyper-parameters as needed.
 

### 2020-09-25 Thesis/Sections/EvaluatingPerformance.tex
Updates To Thesis
- Progress on Network Architecture
- Begun "Evaluating Performance Section
- Updated architecture figure

% ================================
% Landon Buell
% Kevin Short
% Physics 799%
% 24 Sept 2020 
% ================================

\documentclass[12pt,letterpaper]{article}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{algorithm}
\usepackage{algorithmic}

\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{xcolor}

\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}

\begin{document}

% ================================================================

\section{Evaluating Performance}
\label{sec-PerfEval}

\paragraph*{}Before making predictions on unlabeled data such as the Chaotic Synthesizers, we must determine that our model performs reasonably on data that it has never interacted with. The most common practice is to divide a full data set into a subset of \textit{training} samples, and \textit{testing} samples. The exact ratio of sample volume between these subsets varies depending on the task \cite{Goodfellow,Geron2,Mitchell}. We as the names imply, the training subset is used to fit the model, and we use the labeled testing data set to evaluate. Since the testing data is labeled, we can compare the classifiers predictions to the \textit{ground truth} labels.

% ================================================================

\subsection{Cross Validation}

\paragraph*{}Performance evaluations are most commonly implemented in the form of \textit{$K$-Fold Cross-Validation} (Also called X-val). This process involves taking a data set containing $N$ unique samples and dividing it into $K$ non-overlapping subsets. $1$ subset is reserved to evaluate the model, and $K-1$ are used to train the model. This belongs a larger family of statisical validations called \textit{Resampling methods} \cite{James}. Below, we detail pseudo-code for a $K$-Fold Cross Validation algorithm.

\begin{algorithm}[H]
\caption{A $K$-Fold Cross Validation program.}
\label{algFeedForward}

\begin{algorithmic}
\REQUIRE Untrained Network or related learning algorithm, $F^*$
\REQUIRE A full data set of $N$ samples. $X^{(i)}$, $i \in {0,1,2,...,N-1}$
\REQUIRE Number of splits in Cross validation, $K$
\REQUIRE Performance metric function(s), $P$

Divide Data into $K$ non-overlapping subsets $x_{i}$, each with roughly $K/N$ samples \\
$X \rightarrow \big\{ x_{0}, x_{1}, x_{2}, ..., x_{K-2},  x_{K-1} \big\}$ \\
Performance History $\leftarrow \{\}$

\FOR {$j = 0,1,2,3,...,K-2,K-1$}
	\item Reset all parameters in $F^*$ to a random "untrained" state
	\item Set aside testing data subset
	\item $X_{test} = x_{j}$
	\item Concatenate the remaining subsets into training data set
	\item $X_{train} = x_{j \neq k}$
	\item Train the model, $F^*$ with the $X_{train}$ data set
	\item Evaluate the trained model with metric function(s) $P$
	\item Store Performance $P$ in Performance History array
\ENDFOR

Compare performance results, and adjust model, parameters as needed, and repeat if desired.

\end{algorithmic}
\end{algorithm}

\paragraph*{}By using cross-validation, we gain a deeper understanding of the model to ensure that the model can be properly trained consistently. This also helps counteract the possibility that the model got very lucky or unlucky with a particular set of initial conditions \cite{Geron,James}.

% ================================================================

\subsection{Performance Metrics}

\paragraph*{}In the case of the multi-category classifier, it is also important that we choose the appropriate metrics to evaluate our performance. While the neural network itself uses the cost function as it's sole performance metric to optimize, we also require a set of more human-readable functions. We introduce a set of functions and metrics than enable a more tangible interpretation of model performance. 
To evaluate a performance metric, we require a set of samples with ground truth labels, $y$, and a model's prediction for those labels, $y^*$.

% ================================

\subsubsection{Confusion Matrix}

\paragraph*{}The confusion matrix (also called a confusion table) is a very quick, often graphical model that can be used to show how a model performs over a subset of predictions. The general idea of this object is count the number of times class $A$ is predicted to be in class $B$, and vice-versa \cite{Geron}. If we see that these classes are being repeatedly \textit{confused} in the model's prediction process, then we must modify the model or features to account for it.

\paragraph*{}For a $k$-classes classifier, a confusion matrix will have shape $k \times k$. Each row represents the actual labeled class and each column represents a predicted class. Thus for a confusion matrix, $C$, we can say that:
\begin{equation}
\label{eqn-ConfMat}
C_{i,j} = 
\text{Number of samples that belong to class $i$, and were predicted to be in class $j$}
\end{equation} 
Thus, $i = j$, represents a correct prediction, and $i \neq k$ indicates an incorrect prediction. A confusion matrix with a strong main diagonal indicates a model that consistently predicts correct labels \cite{Geron}.

\begin{figure}[H]
\label{fig-ConfMat}
\begin{center}
\textcolor{red}{Images of Confusion Matrices Go Here!} 
\end{center}
\caption{Example Confusion Matrices for $k$-classes tasks}
\end{figure}

\paragraph*{}We can also use a confusion matrix to define four useful quantities relating a prediction to it's label. Suppose a prediction, $y^* = p$ and a truth, $y = q$.
\begin{enumerate}
\item \textbf{True-Positive}\\
A sample is a true-positive if $p = q$
\item \textbf{True-Negative}\\

\item \textbf{False-Positive}\\

\item \textbf{False-Negative}\\
\end{enumerate}
\textcolor{red}{finish this!}

% ================================

\subsubsection{Precision Score}

\paragraph*{}Precision score (also called \textit{specificity}) offers a more concise performance metric than a confusion metric. For a classifier with $k = 2$ unique classes, we define the precision score of a model as:
\begin{equation}
\label{eqn-BinaryPrecision}
\text{Prec} = \frac{TP}{TP + FP}
\end{equation}
Where $TP$ is the number of \textit{true-positive}, and $FP$ is the number of false-positives predictions. For a $k$-classes confusion matrix, $C$, the precision score is given by the entry $C_{j,j}$ divided by the sum of column $j$:
\begin{equation}
\label{eqn-KPrecision}
\text{Prec}_j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{i,j}}
\end{equation}
For multi-class problems, the precision score is usually used as an average over all classes.

\paragraph*{}
\textcolor{red}{Physical Significance of Precision}

% ================================

\subsubsection{Recall Score}

\paragraph*{}Recall score (also called \textit{sensitivity}) also offers a more concise performance metric than a confusion metric. For a classifier with $k = 2$ unique classes, we define the recall score of a model as:
\begin{equation}
\label{eqn-BinaryRecall}
\text{Recall} = \frac{TP}{TP + FN}
\end{equation}
Where $TP$ is the number of \textit{true-positive}, and $FN$ is the number of false-negative predictions. For a $k$-classes confusion matrix, $C$, the precision score is given by the entry $C_{j,j}$ divided by the sum of row $j$:
\begin{equation}
\label{eqn-KRecall}
\text{Recall}j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{j,i}}
\end{equation}
For multi-class problems, the recall score is also used as an average over all classes.

\paragraph*{}
\textcolor{red}{Physical Significance of Recall}

% ================================

% ================================================================

% ================================================================

% ================================================================

% ================================================================

% ================================================================

% ================================================================

\newpage

\begin{thebibliography}{9}
\bibliographystyle{apalike}

\bibitem{Geron}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. O'Reilly, 2017.

\bibitem{Geron2}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. 2nd ed., O'Reilly, 2019.

\bibitem{Goodfellow}
Goodfellow, Ian, et al.\textit{Deep Learning}. MIT Press, 2017.

\bibitem{James}
James, Gareth, et al. \textit{An Introduction to Statistical Learning with Applications in R}. Springer, 2017.

\bibitem{Kahn}
Khan, M. Kashif Saeed, and Wasfi G. Al-Khatib. “Machine-Learning Based Classification of Speech and Music.” Multimedia Systems, vol. 12, no. 1, 2006, pp. 55–67., doi:10.1007/s00530-006-0034-0.

\bibitem{Levine}
Levine, Daniel S. \textit{Introduction to Neural and Cognitive Modeling}. 3rd ed., Routledge, 2019.

\bibitem{Liu}
Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classification." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.

\bibitem{Loy}
Loy, James , \textit{Neural Network Projects with Python}. Packt Publishing, 2019

\bibitem{McCulloch}
McCulloch, Warren S., and Walter Pitts. "A Logical Calculus of the Ideas Immanent in Nervous Activity." \textit{The Bulletin of Mathematical Biophysics}, vol. 5, no. 4, 1943, pp. 115–133.

\bibitem{Mierswa}
Mierswa, Ingo, and Katharina Morik. "Automatic Feature Extraction for Classifying Audio Data." \textit{Machine Learning}, vol. 58, no. 2-3, 2005, pp. 127–149., doi:10.1007/s10994-005-5824-7.

\bibitem{Mitchell}
Mitchell, Tom Michael. Machine Learning. 1st ed., McGraw-Hill, 1997.

\bibitem{Olsen}
Olson, Harry E. \textit{Music, Physics and Engineering}. 2nd ed., Dover Publications, 1967.

\bibitem{Peatross}
Peatross, Justin, and Michael Ware. \textit{Physics of Light and Optics.} Brigham Young University, Department of Physics, 2015.

\bibitem{Petrik}
Petrik, Marek. "Introduction to Deep Learning." Machine Learning. 20 April. 2020, Durham, New Hampshire.

\bibitem{Short}
Short, K. and Garcia R.A. 2006. "Signal Analysis Using the Complex Spectral Phase Evolution (CSPE) Method." AES: \textit{Audio Engineering Society Convention Paper}.

\bibitem{Virtanen}
Virtanen, Tuomas, et al. \textit{Computational Analysis of Sound Scenes and Events.} Springer, 2018.

\bibitem{White}
White, Harvey Elliott, and Donald H. White. \textit{Physics and Music: the Science of Musical Sound}. Dover Publications, Inc., 2019.

\bibitem{Zhang}
Zhang, Tong, and C.-C. Jay Kuo. “Content-Based Classification and Retrieval of Audio.” \textit{Advanced Signal Processing Algorithms, Architectures, and Implementations VIII}, 2 Oct. 1998, pp. 432–443., doi:10.1117/12.325703.

\end{thebibliography}

% ================================================================

\end{document}

### 2020-09-26 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Added Full Thesis Draft v0

--- 2020-09-23 Thesis/Sections/TheNerualNetwork.tex
@@
 % Physics 799%
-% 30 July 2020 
+% 26 September 2020
 % ================================
@@
 
+% ================================
+
+\DeclareMathOperator{\sign}{\text{sign}}
+
+% ================================
+
 \begin{document}
@@
 % ================================================================
-
+% ================================================================
+
+\begin{titlepage}
+	\begin{center}
+   		\vspace*{1cm}
+       	\begin{LARGE}
+       	\textbf{Classifying Chaotic Synthesizers with a Multimodal Neural Network} \\
+       	\end{LARGE}
+       	\vspace{1cm}
+       	\begin{Large}
+       	Thesis Subtitle 
+       	\end{Large}             
+       	\vspace{1.5cm}
+
+       	\textbf{By: \\ Landon Buell$^1$} \\       
+       	\vspace{0.5cm}
+       	\textbf{Advised By: \\ Dr. Kevin Short$^2$ , Dr. Maurik Holtrop$^1$} \\
+      	\vspace{1cm}
+      	A thesis presented for the degree of\\
+       	Bachelor of Science in Physics
+        \vspace{1cm}
+
+       \vfill
+
+       \vspace{1cm}              
+       $^1$Department of Physics and Astronomy\\           
+       $^2$Department of Mathematics and Statistics\\
+       \vspace{1cm}  
+       University of New Hampshire\\
+       Durham New Hampshire, USA\\
+       Dec 2020\\
+
+   \end{center}
+\end{titlepage}
+
+\tableofcontents
+
+% ================================================================
+% ================================================================
+\newpage
+\section{Introduction}
+\label{sec-Introduction}
+
+% ================================================================
+% ================================================================
+\newpage
+\section{Methodology}
+\label{sec-Methodology}
+
+\paragraph*{}We outline and detail the steps taken to execute this project from beginning to end.
+\textcolor{red}{Does this section need to be included? I'm not sure how to format or organize it}
+
+% ================================================================
+
+\subsection{Designing the Function}
+
+\paragraph*{}Consider the biological process of hearing a sound wave and matching it to a source.
+We can model this behavior by some unknown function $F$.
+We produce an approximation of that function $F^*$ that can map the contents of a sound file that have been generated by a chaotic synthesizer to a potential source.
+For a set of inputs $\vec{x} = \big\{ x_0 , x_1 , x_2 , ...
+, x_{p-1} \big\}$ and a set of classes $0$ through $k-1$, we denote this function as:
+\begin{equation}
+\label{eqn-MappingFunction}
+F^*: \vec{x} \rightarrow \big\{ 0 , 1 , 2 , ... , k-1 \big\}
+\end{equation}
+
+% ================================================================
+
+\subsection{Collecting and Pre-processing Raw Data}
+
+\paragraph*{}In order to train the Multimodal neural network to identify musical instrument sources, we need a suitable data set to present to the model.
+University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \textcolor{blue}{Citations!}.
+These contain short segments of musical instruments performing a single note or a collection of notes in succession.
+
+\paragraph*{}To ensure that these data sets are roughly homogeneous, we read each sample from it's original format, \textit{.aif}, \textit{.mp3}, or similar, and rewrite each sample as a new \textit{.wav} files, sampled at 44.1 kHz, with a 16 bit depth \textcolor{red}{check this!}.
+This ensures that all data will have a consistent format when features are extracted.
+We also use this stage to ensure that each audio file has a correct label, and to determine the number of unique output classes.
+
+% ================================================================
+
+\subsection{Designing Classification Features}
+
+\paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of classification features.
+These are properties of wave forms that can be represented by a numerical value or several numerical values and are used as the primary tool in classification.
+There are used in place of a full waveform to represent a file's contents We use tools from physics, mathematics, and signal processing to define and explore a comprehensive set of features that enables a high performance of the classifier.
+
+% ================================================================
+
+\subsection{Designing A Complementary Network Architecture}
+
+\paragraph*{}With the appropriate set of features designed, and the number of output determined, we can organize the structure of the neural network function.
+We construct a multimodal neural network than processes two input arrays derived from the same audio sample that share a common label.
+This network is designed to handle and process each respective input independently, and concatenate the results to produce a single output.
+
+% ================================================================
+
+\subsection{Testing and Evaluating Network Performance}
+
+\paragraph*{}We divide the raw data set up into a training and testing sets.
+We employ cross-validation and compute the results of performance metrics to ensure that out model is making reliable predictions, and generalize appropriately.
+In this stage, we also choose the value of hyper-parameters, activation functions and layer widths to best compliment the chosen features.
+This process is repeated and expanded upon until we have produced a model with a sufficient performance.
+
+% ================================================================
+
+\subsection{Running Predictions of Chaotic Synthesizer Files}
+
+\paragraph*{}Once we have established a suitable performance of the model, we allow the model to run predictions on the un-labeled chaotic synthesizer wave forms.
+We output the prediction results to a file, and compare the neural network predictions against human predictions.
+If further corrections are needed, we revert and re-deign the features, architecture, or hyper-parameters as needed.
+
+% ================================================================
+% ================================================================
+
+\newpage
 \section{The Neural Network}
@@
 \subsection{An Introduction to Neural Networks}
-\label{sec-NerualNetworkIntro}
+\label{subsec-NerualNetworkIntro}
 
@@
 
-\newpage
-
 \subsection{The Structure of a Neural Network}
-\label{sec-NetworkStructre}
+\label{subsec-NetworkStructre}
 
@@
 The exact nature of this operation can be very different depending on the layer type or where it sits within the network.
-It is this process of transforming inputs successively in a particular order until an output is attained \cite{Geron,Loy}.
+It is this process of transforming inputs successively in a particular order until an output is attained that makes up the core functionality of a neural network \cite{Geron,Loy}.
 This output encodes the models final "decision" given a unique input.
@@
 \end{equation}
-The array of activations, $x^{(0)}$, is the raw input given the neural network, most commonly called \textit{features}.
-Conversely, the activations $x^{(L-1)}$ are commonly called the network \textit{output} \cite{Geron,James,Loy}.
+The array of activations, $x^{(0)}$, is the raw input given the neural network, called \textit{input} activations.
+Conversely, $x^{(L-1)}$ is referred to as\textit{output} activations \cite{Geron,James,Loy}.
 
@@
 Each iteration in the main \textit{for-loop} represents the execution of a layer, and passing the result to the "next" layer function.
+We assume each layter to follow a two-step structure, being (i) a linear transformation as in eqn.
+(\ref{eqn-LinearTransform}) and (ii) an element-wise non-linear activation function as in eqn.
+(\ref{eqn-elementActivation}).
 A practical application of this algorithm should include batches of samples instead of a single sample.
-\textcolor{red}{I will put this some place better soon! It is here for future placement}}
+\textcolor{red}{I Want to include this algorithm for context - especially on the programming end, but am not sure where to put it. }}
 \label{algFeedForward}
@@
 \REQUIRE Network with $L$ layers - $0,1,2,....,L-2,L-1$
-\REQUIRE Set of weighting parameters - $W^{(i)}, i \in \{0,1,....,L-1\}$
-\REQUIRE Set of bias parameters - $b^{(i)}, i \in \{0,1,....,L-1\}$
-\REQUIRE Set of layer activation function - $a^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of layer functions $f^{(l)}, l \in 0,1,2,....,L-2,L-1$ made up of 
 \REQUIRE Input sample - $x^{(0)}$
@@
 $Z = \{\} \leftarrow$ array to hold pre-activations \\
-$X = \{\} \leftarrow$ array to hold final activations
+$X = \{\} \leftarrow$ array to hold final activations \\
 
 \FOR {$l = 1,2,...,L-2,L-1$}
-	\item Compute pre-nonlinear activation
-	\item $z^{(l)} \leftarrow W^{(l)}x^{(l-1)} + b^{(l)}$
-	\item Apply activation function
-	\item $x^{(l)} \leftarrow a^{(l)}[z^{(l)}]$
+
+	\item Break layer function into two linear transformation and non-linear activation
+
 	\item Store values for later use in optimizer
@@
 \item $y^* \leftarrow x^{(L-1)} = X[-1]$
-\item Return the pre-nonlinear activations and final-nonlinear activations
+\item Return the pre-nonlinear activations and final-nonlinear activations.\\
+\item The final index of $X$ represents the neural network's final prediction. \\
 \RETURN $Z , X$
@@
 
-\newpage
-
 \subsection{Layers Used in Classification Neural Network}
-\label{sec-Layers}
+\label{subsec-Layers}
 
@@
 \begin{equation}
-\label{eqn-matVectEqn}
+\label{eqn-LinearTransform}
 z^{(l)} = W^{(l)} x^{(l-1)} + b^{(l)}
@@
 \end{equation}
-Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-matVectEqn}).
+Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-LinearTransform}).
 $\sigma^{(l)}$ is some activation function, which is often use to enable the modeling of more complex-decision boundaries.
@@
 \paragraph*{}The combination of eqn.
-(\ref{eqn-matVectEqn}) and eqn.
+(\ref{eqn-LinearTransform}) and eqn.
 (\ref{eqn-elementActivation}), for a layer $l$ , make up the function represented by that layer, as in eqn.
@@
 
-% ================
+% ================================
 
 \subsubsection{Dense Layer}
-\label{subsec-DenseLayer}
+\label{subsubsec-DenseLayer}
 
@@
 \end{equation}
-The activation of each entry is given by a linear-combination of activations from the previous layer, as outlined in eqn.(\ref{eqn-matVectEqn}) and eqn.(\ref{eqn-elementActivation}).
+The activation of each entry is given by a linear-combination of activations from the previous layer, as outlined in eqn.(\ref{eqn-LinearTransform}) and eqn.(\ref{eqn-elementActivation}).
 
@@
 
-% ================
+% ================================
 
 \subsubsection{2-Dimensional Convolution Layer}
+\label{subsubsec-Conv2DLayer}
 
@@
 
-% ================
+% ================================
 
@@
 
-\paragraph*{}The 1-Dimensional Concatenation Layer, also called 1D-Concat layer takes separate vectors of activations
+\paragraph*{}The 1-Dimensional Concatenation Layer, also called 1D-Concat layer takes separate vectors of activations and combines them into a single 1D vector. Consider the layer activations
 
@@
 (\ref{sec-Training}) a layer function, $f^{(l)}$ is generally composed of a linear transformation, as in eqn.
-(\ref{eqn-matVectEqn}), and then an element-wise activation function as in eqn.
+(\ref{eqn-LinearTransform}), and then an element-wise activation function as in eqn.
 (\ref{eqn-elementActivation}).
@@
 \end{figure}
+For our chosen architecture, ReLU is applied to the activations in every single Convolution layer and Dense Layer, with the exception of the output dense layer.
+
+% ================================
 
@@
 
-% ================================================================
-
-\newpage
+\paragraph*{}The softmax activation function is commonly used in the output layer of a multi-class classification network, such as the one we implement.
+When softmax acts on a vector or activation, the result is a normalized,non-negative output vector.
+\cite{Geron,Goodfellow,Virtanen}.
+The $i$-th element in a softmax activation function is given by:
+\begin{equation}
+\label{eqn-Softmax}
+\text{Softmax}\big[ x \big]_{i} = \frac{1}{\sum_{j}e^{x_j}}e^{x_i}
+\end{equation}
+
+\paragraph*{}This function is only used in the output layer of a neural network, and encodes a discrete categorical probability.
+For example, if eqn.(\ref{eqn-Softmax}) returns a vector of the form: $[ 0.75 , 0.25]$, we interpret this as a sample having a $75\%$ chance of beloinging to class $0$ and a $25\%$ change of belonging to class $1$.
+
+% ================================================================
 
 \subsection{Training a Neural Network}
-\label{sec-Training}
+\label{subsec-Training}
 
@@
 
+% ================================
+
 \subsubsection{Gradient Based Learning}
@@
 \end{equation}
+
+% ================================
 
@@
 
-\newpage
-
 \subsection{Chosen Model Architecture}
@@
 
-\paragraph*{}The success of a neural network algorithm is enormously dependent of the strength of the chosen features, rather than the quantity of available data \cite{Geron,Kahn,Liu}.
-We have derived an appropriate set of inputs arrays \textcolor{blue}{See Section on Features}, and constructed a neural network architecture to compliment these features.
-From these two input arrays, one being a matrix and the other being a column-vector, we have produced a \textit{multimodal neural network}, that process the two inputs, and combines separate neural networks into a single model to produce a one prediction resulting from both inputs.
+\paragraph*{}The success of a neural network algorithm is enormously dependent of the strength of the chosen features, as well as a complementary architecture, rather than the quantity of available data \cite{Geron,Kahn,Liu}.
+We have derived an appropriate set of inputs arrays \textcolor{blue}{See Section on Features}, and constructed a neural network architecture to coincide with these features.
+From these two input arrays, one being a matrix and the other being a column-vector, we have produced a \textit{multimodal neural network}, that process the two inputs, and combines separate neural networks into a single model to produce a one prediction resulting from both inputs \textcolor{blue}{citation for multimodal networks}.
 
@@
 
-\paragraph*{}By grouping layers in this structure, each of the $32$ filters passes over a $3 \times 3$ area, and then again. The result is
+\paragraph*{}By grouping layers in this structure, we use the convolution  layers to reduce the number of features, and then the pooling layer to extract only the largest activations of the remianing features.
+This ensures that in the full spectrogram image, only the dominant features and feature shapes are preserved and passed into the next layer set for processing.
 
@@
 (\ref{fig-NetworkArchitecture}), notice that it is considerably smaller in side and complexity than it's neighbor.
-Rather than accept an image-like input, the perception simply takes a vector-like input of properties of a larger data set - in this case, each waveform.
+Rather than accept an image-like input, the perception simply takes a vector-like input of properties that are derived from the audio file.
 We call these properties \textit{features} \cite{Geron,Kahn,Virtanen}.
@@
 The axes, in order of indexing, represent (i) the size of the \textit{mini-batch} of samples, (ii) the number of features for each sample.
-We use the same model hyper-paramater of $64$ samples per batch, and have developed $23$ unique clssification features that have been derived from time-space and frequency-space representations of the audio file data.
+We use the same model hyper-paramater of $64$ samples per batch, and have developed $20$ unique classification features that have been derived from time-space and frequency-space representations of the audio file data.
 We can denote the 2D shape if the input object into this branch as:
@@
 \end{equation}
-Again, any other shape will be rejected by the model, and an error is raised.
+This 2D is referred to as a \textit{design matrix} \cite{James,Loy}. Any other shape will be rejected by the model, and an error is raised.
+
+\paragraph*{}In perceptron models, scaling the design matrix appropriately drastically improves the classification performance.
+A design matrix is scaled by taking all samples in a column (a particular feature from each class), subtracting the average, and then scaling it such that it has unit variance \cite{Geron,James}.
+This ensures that no one feature dominates the performance of the model and that layer activations to not get saturated as data progresses through the network.
 
@@
 
-\paragraph*{}The last layer in eachof the two branches is a ReLu-activated Dense layer containing 64 neurons. The activations are concatenated
-
-% ================================================================
+\paragraph*{}The last layer in each of the two branches is a ReLU-activated Dense layer containing 64 neurons, represented by a $64 \times 1$ column vectors.
+We combine these model layers by using a \textit{concatenation layer} to fuse the two column vectors together, "vertically", such that the result is a $128 \times 1$ column vector.
+This vector is then passed into the final dense layer, which used the softmax activation, and encodes the joint predictions based on both model branches.
+
+% ================================================================
+
+\section{Feature Selections}
+\label{sec-FeatureSelections}
+
+\paragraph*{}Even best minds in the world will perform poorly on test which they have studied the wrong material- neural networks are no different.
+In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}.
+It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier.
+Consider if you were tasked to identify cats and dogs from images, but instead were presented with only the top-most row of pixels- The task would be nearly impossible because of an inappropriate or in complete set of information.
+
+\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" \cite{Virtanen}:
+\begin{quote}
+For recognition algorithms, the necessary property of the acoustic features is low variability among features extracted from examples assigned to the same class, and at the same time high variability allowing distinction between features extracted from examples assigned to different classes.
+\end{quote}
+In constructing a neural network classifier, the development of appropriate features is of the utmost importance.
+To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency space representation of the waveform.
+It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely on these features.
+
+\paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}.
+In the training process, this object, along with the appropriate classification label, $y$ is presented to the neural network for processing.
+This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu}
+
+\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector.
+These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics.
+In the following sections, we outline the set of $21$ features used in the classification process
+
+\newpage
+
+% ================================
+
+\subsubsection{The Design Matrix}
+
+\paragraph*{}The $21$ features are from each file are organized into one of two array structures.
+each called a \textit{design matrix}.
+A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest.
+For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.
+each has shape given by:
+\begin{equation}
+\label{eqn-X1Shape}
+X_1 \in \mathbb{R}^{(b \times N' \times k' \times 1)}
+\end{equation}
+\begin{equation}
+\label{eqn-X2Shape}
+X_2 \in \mathbb{R}^{(b \times p)}
+\end{equation}
+Where $N' \times k' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
+(\ref{subsec-spectrogram}), The first axis, with length $b$ indicates that there are $b$ samples stored in that design matrix.
+Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec.
+(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).
+A row of $X_2$ has shape $1 \times p$ where there are $p$ features within the \textit{feature-vector} for each sample.
+Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.
+
+% ================================
+
+\subsubsection{Audio Preprocessing}
+
+\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}.
+In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
+\begin{enumerate}
+\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
+\item Audio encoded in a standard, and consistent format
+\item A consistent sample rate and bit depth between audio files
+\item A consistent number of channels
+\end{enumerate}
+Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
+\begin{enumerate}
+\item Roughly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
+\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
+\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
+\item All audio has been down-mixed into mono-channel waveforms.
+\end{enumerate}
+
+% ================================================================
+
+\newpage
+
+\subsection{Spectrogram Feature}
+\label{subsec-spectrogram}
+
+\paragraph*{}The field of neural classification is well studied in the application of image-processing.
+Many large-scale, and even introductory neural network projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
+As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior.
+Following this success, it make senses to provide an image-like representation of a sound wave as a feature.
+We do this in the form of a spectrogram matrix.
+
+\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both space and time.
+In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis.
+Thus each point in the 2-Dimensional space is an energy at a given time and frequency.
+Examples spectrograms from the wave form data set are shown in Fig.
+(\ref{fig-spectrograms}).
+
+\begin{figure}[H]
+\begin{center}
+\label{fig-spectrograms}
+\textcolor{red}{Insert spectrograms here}
+\caption{Spectrogram representations of various waveforms}
+\end{center}
+\end{figure}
+
+\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification.
+Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame.
+Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhang,Kahn,Virtanen}.
+For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
+At a sample rate of $f_s = 44100$ samples/second, each frame represents a slice of time that is about $0.1$ seconds long.
+
+\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
+\begin{equation}
+\label{eqn-FrameMatrix}
+A = \big\{ a_{0} , a_{1} , a_{2} , ... , a_{k-1} \big\} = 
+\begin{bmatrix}
+a_{0}[0] & a_{0}[1] & a_{0}[2] & \hdots & a_{0}[N-1] \\
+a_{1}[0] & a_{1}[1] & a_{1}[2] & \hdots & a_{1}[N-1] \\
+a_{2}[0] & a_{2}[1] & a_{2}[2] & \hdots & a_{2}[N-1] \\
+\vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
+a_{k-1}[0] & a_{k-1}[1] & a_{k-1}[2] & \hdots & a_{k-1}[N-1] \\
+\end{bmatrix}
+\end{equation}
+We use bracket notation, $[j]$ to indicate that each analysis frame $a_i$ is array-like. Many programming languages could also use the following indexing conventions for matrix $A$:
+\begin{equation}
+\label{eqn-IndexingA}
+A_{i,j} = A_i[j] = A[i][j] = A[i,j]
+\end{equation}
+These all represent equivalent entries.
+
+\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
+A standard \textit{Hann Window} of $N$ samples is generated and reshaped into a $N \times 1$ column-array, $H$.
+The $n$-th index in a Hann window with $N$ samples is defined:
+\begin{equation}
+\label{eqn-Hann}
+H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
+\end{equation}
+The window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
+Result is an $k \times N$ array, $\widetilde{A}$:
+\begin{equation}
+\label{eqn-WindowMatrix}
+\widetilde{A_i} = A_i \odot H
+\end{equation}
+
+\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross}.
+The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
+Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space containing $N$ samples
+\begin{equation}
+\label{eqn-DFTMatrix}
+\mathbb{W} = \frac{1}{\sqrt{N}}
+\begin{bmatrix}
+1 & 1 & 1 & 1 & \hdots & 1 \\
+1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
+1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
+1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
+\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
+1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
+\end{bmatrix}
+\end{equation}
+Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $\widetilde{A}^T$.
+The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
+
+\paragraph*{}Most standard implementations of neural network models require all activations, weights, and biases to be real floating-point numbers.
+Since the the DFT matrix introduces complex values, we compute the square of the element-wise $L2$-norm of the resultant array.
+\begin{equation}
+\label{eqn-Spectrogram}
+S_{i,j} = \big{\lVert} (\mathbb{W}\widetilde{A}^T)_{i,j} \big{\rVert}_{2}^{2}
+\end{equation}
+Where $\mathbb{W}$ is the DFT matrix from eqn.
+(\ref{eqn-DFTMatrix}) and $\widetilde{A}^T$ is the transpose of the analysis frames matrix from eqn.
+(\ref{eqn-WindowMatrix}).
+The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of real floating-point numbers.
+We can index matrix $S$ similarly to that of matrix $A$ in eqn.
+(\ref{eqn-IndexingA}):
+\begin{equation}
+\label{eqn-IndexingS}
+S_{i,j} = S[i][j] = S[i,j]
+\end{equation}
+
+\paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames.
+Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins.
+Since human hearing extends from $20$ Hz to $20$ kHz, audio files such as music and voice recordings are typically sampled around $44.1$ kHz, to ensure that the full range of audio is held by the recording \cite{Olson,Virtanen}.
+
+\paragraph*{}However, standard musical instruments seldom extend above $8$ kHz \cite{Olson,Virtanen,White}.
+This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
+As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $8000$ Hz.
+This makes the input array smaller, and eliminates redundant and non-useful information.
+The number rows in the $S$ matrix is reduced from $N$ down to $N'$.
+Since each raw audio file may contain a different number of samples to begin with, a different number of analysis frames are created.
+To ensure all samples are a homogeneous size, we assert that each matrix must have exactly $k'$ columns.
+If $k' < k$, columns of zeros are added to pad the input, and if $k' > k$, columns are removed.
+
+\paragraph*{}Each spectrogram is now $N' \times k' \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform a a function of both time and frequency.
+The spectrogram is the first feature used in this model.
+For this classifier, we have chosen $N' = 560$ and $k' = 256$.
+For training, a batch of $b$ samples are concatenated into a single array object.
+\textcolor{blue}{See Neural Network section for more details}.
+For a batch of $b$ samples of $N' \times k' \times 1$ spectrograms, we shape $X_1$ such that:
+\begin{equation}
+\label{eqn-X1 shape}
+X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k' \times 1)}
+\end{equation}
+Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}).
+This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
+\textcolor{blue}{See Neural Network section for more details}
+
+% ================================================================
+
+\newpage
+
+\subsection{Time-Space Features}
+\label{subsec-time}
+
+\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. Time space can be represented in one of three ways: 
+\begin{itemize}
+\item The raw waveform $s$\\
+Indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
+\item A single analysis frame $a_i$ \\
+Indexed by $a_i[j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
+\item The full analysis frame matrix $A$ \\
+Indexed by $A[i][j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
+\end{itemize}
+
+\paragraph*{}From time space, we use the following $7$ features:
+\begin{itemize}
+\item[•] Time Domain Envelope
+\item[•] Zero Crossing Rate
+\item[•] Temporal Center of Mass
+\item[•] Auto Correlation Coefficients ($\times 4$)
+\end{itemize}
+
+% ================================
+
+\subsubsection{Time Domain Envelope}
+
+\paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal Often, we compute the RMS-Energy of each frame - a larger energy of the frame, the larger the average amplitude of the waveform in that frame.
+For frames with smaller amplitude, we can assume that the signal has either not begun, or is decaying.
+
+\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olson,Virtanen}
+\begin{equation}
+\label{eqn-RMS}
+\text{RMS}\big[ s \big] = \sqrt{\frac{1}{N} \sum_{i=0}^{N-1} s[i]^2}
+\end{equation}
+By using the full waveform, we acquire a rough estimate for the energy in the entirety of the audio file \cite{Liu}.
+For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large waveform RMS when compared to those instruments without sustain such as plucked stings or dampened percussion
+
+\begin{figure}[H]
+\label{fig-FeatureTDE}
+\begin{center}
+\textcolor{red}{PLOT OF TDE FEATURES HERE}
+\end{center}
+\caption{Time domain envelope visualized in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Zero Crossing Rate}
+
+\paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses it's equilibrium point.
+This can be done per total sound wave, per unit time, or per analysis-frame.
+This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform.
+In some cases, the ZXR can be correlated to frequency as well \cite{Kahn,Zhang}.
+
+\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}. The ZXR for the full waveform $s$ is given by \cite{Virtanen,Liu}
+\begin{equation}
+\label{eqn-ZXR}
+\text{ZXR}\big[ s \big] = \frac{1}{2} \sum_{i=1}^{M-1} \big{|} \sign(s[i]) - \sign(s[i-1]) \big{|} 
+\end{equation}
+Where $\sign(x)$ returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$.
+This provides a rough estimate for the average frequency in the full waveform, and can help discern clean periodic signals (low ZXR) from those that may have more noise or volatile behavior (high ZXR)\cite{Virtanen}.
+
+\begin{figure}[H]
+\label{fig-FeatureZXR}
+\begin{center}
+\textcolor{red}{PLOT OF ZXR FEATURES HERE}
+\end{center}
+\caption{Zero crossing rate visualized in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Center of Mass}
+
+\paragraph*{}The temporal center of mass (TCM) of a signal is used to compute roughly where in time the amplitude of the waveform \textit{bunches up}.
+We treat the full waveform array, $s$, with $M$ samples as a 1-Dimensional discrete mass distribution.
+The TCM of that waveform is then given:
+\begin{equation}
+\label{eqn-FeatureTCM}
+\text{TCM}\big[ s \big] = \frac{\sum_{i=0}^{M-1}i s[i]}{\sum_{i=0}^{M-1}s[i]}
+\end{equation}
+This includes negative amplitude values acting as "negative masses".
+
+\paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance.
+For instruments with heavier attacks, we expect the TCM to be a very near the start of the waveform.
+For instruments with long sustain times, we expect a very centrally located center of mass, and for instruments with long release times, we expect a later TCM value.
+
+\begin{figure}[H]
+\label{fig-FeatureTCM}
+\begin{center}
+\textcolor{red}{PLOT OF TCM FEATURES HERE}
+\end{center}
+\caption{Temporal center-of-mass visualized in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Auto Correlation Coefficients}
+
+\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution .
+We can compute any number of ACC's and their value changed depending on the index chosen.
+It is common to only compute the first $K$ ACC's \cite{Virtanen}.
+For a full waveform signal $s$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
+\begin{equation}
+\label{eqn-FeatureACC}
+\text{ACC}_k\big[ s \big] = 
+\frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]} {\sqrt{\sum_{i=0}^{M-k-1}s^2[i]} \sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
+\end{equation}
+
+\begin{figure}[H]
+\label{fig-FeatureACC}
+\begin{center}
+\textcolor{red}{PLOT OF ACC FEATURES HERE}
+\end{center}
+\caption{First four auto correlation coefficients visualized in feature-space}
+\end{figure}
+
+% ================================================================
+
+\newpage
+
+\subsection{Frequency-Space Features}
+\label{subsec-frequency}
+
+\paragraph*{}The features described in this section are derived from the frequency-domain representations of each audio sample.
+Frequency space is represented by the transposed spectrogram matrix, $S^T$, described in sec.
+(\ref{subsec-spectrogram}).
+This is done to ensure that each  row is now an analysis frame, each column is a frequency bin.
+This gives a similar structure to the time-space analysis frames matrix, $A$, in eqn.
+(\ref{eqn-FrameMatrix}).
+For each feature, we detail the physical significance and provide a visualization in feature-space.
+
+\paragraph*{}From frequency space, we use the following $13$ features:
+\begin{itemize}
+\item[•] Mel Frequency Cepstral Coefficients ($\times 12$)
+\item[•] Frequency Center of Mass
+\end{itemize}
+
+% ================================
+
+\subsubsection{Mel Frequency Cepstral Coefficients}
+
+\paragraph*{}Mel Frequency Ceptstral Coefficients (MFCC's) are a very prolific feature used widly in audio classification tasks \cite{Liu,Virtanen,Zhang}.
+MFCC's are produced by converting a linear-frequency axis with units such as Hertz into units of Mels, which are design to account for the non-linear perception of frequency in humans.
+The Hertz to Mel and Mel to Hertz transforms are given \cite{Virtanen}:
+\begin{equation}
+\label{eqn-HztoMel}
+M_f[h] = 2595 \log_{10}\big(1+ \frac{h}{700}\big)
+\end{equation}
+\begin{equation}
+\label{eqn-MeltoHz}
+H_f[m] = 700 \big(10^{(\frac{m}{2595})}-1\big)
+\end{equation}
+Where $M_f$ is the frequency in units of Mels, given $[h]$, a frequency in Hertz, and $H_f$ is the frequency in Hertz given $[m]$ a frequency in Mels.
+
+\paragraph*{}Mel filters are produced by grouping frequency-space into $R$ overlapping bins called \textit{Mel Filter-banks}.
+In units of Mels, each filter bank, $R_i$ remains a constant width, but when shown in Hertz, the bins increase logarithmically.
+\begin{figure}[H]
+\label{fig-MelFilterBanks}
+\begin{center}
+\textcolor{red}{Figure of a few Mel Filter Banks goes here}
+\end{center}
+\caption{Mel Filter Banks shown in frequency space with units of Hertz}
+\end{figure}
+Each of the $R$ filters is created to be $N'$ samples long, and transformed back into units of Hertz.
+When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
+Thus, each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is a filter.
+We apply the Mel Filter banks to the spectrogram to create matrix $B$:
+\begin{equation}
+\label{eqn-FilterBanks}
+B = S^T M^T
+\end{equation}
+Matrix $B$ has shape $k' \times R$.
+
+\paragraph*{}Using $S^T$ ensure that each row of the matrix is an analysis frame in frequency space.
+Similarly, each column of the matrix $M$ is a appropriately scaled Mel filter-bank.
+This way, the matrix product in eqn.
+(\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
+Finally, we compute the average energy across all $k'$ frames.
+The resulting $R$ floating-point numbers are approximation of the signal's energy in those particular frequency bands.
+For this project, we have chosen to use $R = 12$ filter-banks, which are all used as features.
+
+\begin{figure}[H]
+\label{fig-FeatureMFCC}
+\begin{center}
+\textcolor{red}{PLOT OF MFCC FEATURES HERE}
+\end{center}
+\caption{Mel Frequency Ceptral Coefficients in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Center of Mass}
+
+\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a strong representation of how overtones and energy is distributed in the signal's frequency domain.
+As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
+This encodes the FCM for a single analysis frame (in frequency-space) in the waveform.
+For an frequency-analysis frame, $s^{(i)}$, the FCM is given by:
+\begin{equation}
+\label{eqn-FeatureFCM}
+\text{TCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
+\end{equation}
+We compute the FCM for each of the $k'$ frames, and then average the results. We use the average FCM across $k'$ frames to compute the FCM feature:
+\begin{equation}
+TCM = \sum_{i=0}^{k'} \text{TCM}_{i}\big[ s^{(i)} \big]
+\end{equation}
+
+\paragraph*{}The average FCM gives a strong approximation of the instrument or signal source's range.
+For example, a flute or violin will have a considerably high FCM value, even in their lower registers.
+Similarly, basses or tubas will have considerably low FCM values.
+Given that the standard frequency range of some musical instruments is fixed, it is guaranteed that for any particular instrument, the FCM will consistently remain within certain bounds \cite{Olson,White}.
+
+\begin{figure}[H]
+\label{fig-FeatureFCM}
+\begin{center}
+\textcolor{red}{PLOT OF FCM FEATURES HERE}
+\end{center}
+\caption{Frequency center-of-mass visualized in feature-space}
+\end{figure}
+
+% ================================================================
+
+% ================================================================
+
+\section{Evaluating Performance}
+\label{sec-PerfEval}
+
+\paragraph*{}Before making predictions on unlabeled data such as the Chaotic Synthesizers, we must determine that our model performs reasonably on data that it has never interacted with.
+The most common practice is to divide a full data set into a subset of \textit{training} samples, and \textit{testing} samples.
+The exact ratio of sample volume between these subsets varies depending on the task \cite{Goodfellow,Geron2,Mitchell}.
+We as the names imply, the training subset is used to fit the model, and we use the labeled testing data set to evaluate.
+Since the testing data is labeled, we can compare the classifiers predictions to the \textit{ground truth} labels.
+
+% ================================================================
+
+\subsection{Cross Validation}
+
+\paragraph*{}Performance evaluations are most commonly implemented in the form of \textit{$K$-Fold Cross-Validation} (Also called X-val).
+This process involves taking a data set containing $N$ unique samples and dividing it into $K$ non-overlapping subsets.
+$1$ subset is reserved to evaluate the model, and $K-1$ are used to train the model.
+This belongs a larger family of statisical validations called \textit{Resampling methods} \cite{James}.
+Below, we detail pseudo-code for a $K$-Fold Cross Validation algorithm.
+
+\begin{algorithm}[H]
+\caption{A $K$-Fold Cross Validation program.}
+\label{algFeedForward}
+
+\begin{algorithmic}
+\REQUIRE Untrained Network or related learning algorithm, $F^*$
+\REQUIRE A full data set of $N$ samples. $X^{(i)}$, $i \in {0,1,2,...,N-1}$
+\REQUIRE Number of splits in Cross validation, $K$
+\REQUIRE Performance metric function(s), $P$
+
+Divide Data into $K$ non-overlapping subsets $x_{i}$, each with roughly $K/N$ samples \\
+$X \rightarrow \big\{ x_{0}, x_{1}, x_{2}, ..., x_{K-2},  x_{K-1} \big\}$ \\
+Performance History $\leftarrow \{\}$
+
+\FOR {$j = 0,1,2,3,...,K-2,K-1$}
+	\item Reset all parameters in $F^*$ to a random "untrained" state
+	\item Set aside testing data subset
+	\item $X_{test} = x_{j}$
+	\item Concatenate the remaining subsets into training data set
+	\item $X_{train} = x_{j \neq k}$
+	\item Train the model, $F^*$ with the $X_{train}$ data set
+	\item Evaluate the trained model with metric function(s) $P$
+	\item Store Performance $P$ in Performance History array
+\ENDFOR
+
+Compare performance results, and adjust model, parameters as needed, and repeat if desired.
+
+\end{algorithmic}
+\end{algorithm}
+
+\paragraph*{}By using cross-validation, we gain a deeper understanding of the model to ensure that the model can be properly trained consistently.
+This also helps counteract the possibility that the model got very lucky or unlucky with a particular set of initial conditions \cite{Geron,James}.
+
+% ================================================================
+
+\subsection{Performance Metrics}
+
+\paragraph*{}In the case of the multi-category classifier, it is also important that we choose the appropriate metrics to evaluate our performance.
+While the neural network itself uses the cost function as it's sole performance metric to optimize, we also require a set of more human-readable functions.
+We introduce a set of functions and metrics than enable a more tangible interpretation of model performance.
+To evaluate a performance metric, we require a set of samples with ground truth labels, $y$, and a model's prediction for those labels, $y^*$.
+
+% ================================
+
+\subsubsection{Confusion Matrix}
+
+\paragraph*{}The confusion matrix (also called a confusion table) is a very quick, often graphical model that can be used to show how a model performs over a subset of predictions.
+The general idea of this object is count the number of times class $A$ is predicted to be in class $B$, and vice-versa \cite{Geron}.
+If we see that these classes are being repeatedly \textit{confused} in the model's prediction process, then we must modify the model or features to account for it.
+
+\paragraph*{}For a $k$-classes classifier, a confusion matrix will have shape $k \times k$.
+Each row represents the actual labeled class and each column represents a predicted class.
+Thus for a confusion matrix, $C$, we can say that:
+\begin{equation}
+\label{eqn-ConfMat}
+C_{i,j} = 
+\text{Number of samples that belong to class $i$, and were predicted to be in class $j$}
+\end{equation} 
+Thus, $i = j$, represents a correct prediction, and $i \neq k$ indicates an incorrect prediction.
+A confusion matrix with a strong main diagonal indicates a model that consistently predicts correct labels \cite{Geron}.
+
+\begin{figure}[H]
+\label{fig-ConfMat}
+\begin{center}
+\textcolor{red}{Images of Confusion Matrices Go Here!} 
+\end{center}
+\caption{Example Confusion Matrices for $k$-classes tasks}
+\end{figure}
+
+\paragraph*{}We can also use a confusion matrix to define four useful quantities relating a prediction to it's label. Suppose a prediction, $y^* = p$ and a truth, $y = q$.
+\begin{enumerate}
+\item \textbf{True-Positive}\\
+A sample is a true-positive if $p = q$
+\item \textbf{True-Negative}\\
+
+\item \textbf{False-Positive}\\
+
+\item \textbf{False-Negative}\\
+\end{enumerate}
+\textcolor{red}{finish this!}
+
+% ================================
+
+\subsubsection{Precision Score}
+
+\paragraph*{}Precision score (also called \textit{specificity}) offers a more concise performance metric than a confusion metric.
+For a classifier with $k = 2$ unique classes, we define the precision score of a model as:
+\begin{equation}
+\label{eqn-BinaryPrecision}
+\text{Prec} = \frac{TP}{TP + FP}
+\end{equation}
+Where $TP$ is the number of \textit{true-positive}, and $FP$ is the number of false-positives predictions.
+For a $k$-classes confusion matrix, $C$, the precision score is given by the entry $C_{j,j}$ divided by the sum of column $j$:
+\begin{equation}
+\label{eqn-KPrecision}
+\text{Prec}_j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{i,j}}
+\end{equation}
+For multi-class problems, the precision score is usually used as an average over all classes.
+
+\paragraph*{}
+\textcolor{red}{Physical Significance of Precision}
+
+% ================================
+
+\subsubsection{Recall Score}
+
+\paragraph*{}Recall score (also called \textit{sensitivity}) also offers a more concise performance metric than a confusion metric.
+For a classifier with $k = 2$ unique classes, we define the recall score of a model as:
+\begin{equation}
+\label{eqn-BinaryRecall}
+\text{Recall} = \frac{TP}{TP + FN}
+\end{equation}
+Where $TP$ is the number of \textit{true-positive}, and $FN$ is the number of false-negative predictions.
+For a $k$-classes confusion matrix, $C$, the precision score is given by the entry $C_{j,j}$ divided by the sum of row $j$:
+\begin{equation}
+\label{eqn-KRecall}
+\text{Recall}j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{j,i}}
+\end{equation}
+For multi-class problems, the recall score is also used as an average over all classes.
+
+\paragraph*{}
+\textcolor{red}{Physical Significance of Recall}
+
+% ================================
 

### 2020-09-29 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis Draft v0

@@
 % ================================================================
+
 \newpage
@@
 % ================================================================
+% ================================================================
 
@@
 % ================================================================
+% ================================================================
+
+\newpage
+\section{Experimental Results}
+\label{sec-Results}
+
+% ================================================================
+% ================================================================
+
+\newpage
+\section{Conclusion}
+\label{sec-Conclusion}
+
+% ================================================================
+% ================================================================
+
+\newpage
+\section{Acknowledgments}
+\label{sec-Acknowledge}
+
+\paragraph*{}The completion of this project would not have been possible without the various contributions from the following people:
+
+\begin{itemize}
+
+\item[•]Nathan Richard for consultation on physics, mathematics, and programming topics.
+
+\item[•]Morgan Saidel for consultation on physics, mathematics, and programming topics.
+
+\item[•]Madeline Edwards for differing me to this project, as well as constant support and consultation on mathematical topics.
+
+\item[•]John Parker for consultation on physics, mathematics, and programming topics.
+
+\item[•]Dakota Buell for consultation on physics, mathematics, and programming topics.
+
+\item[•]Dr. Kevin Short for various consultation and guidence throughout this project
+
+\item[•]Dr. Maurik Holtrop for various consultation and guidence throughout this project
+
+\end{itemize}
+
+% ================================================================
+% ================================================================
 

### 2020-09-30 Thesis/Sections/FeatureSelections.tex

@@
 
+% ================================
+
 \subsubsection{The Design Matrix}
@@
 Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.
+
+% ================================
 
@@
 \paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification.
-Frame-blocking creates a set of analysis frames, each labeled as $a^{(i)}$ and is $N$ samples in length, and has a fixed overlap with the next adjacent frame.
+Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame.
 Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhang,Kahn,Virtanen}.
@@
 
-\paragraph*{}We concatenate each analysis frame, $a^{(i)}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
+\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
 \begin{equation}
 \label{eqn-FrameMatrix}
-A = \big\{ a^{(0)} , a^{(1)} , a^{(2)} , ... , a^{(k-1)} \big\} = 
+A = \big\{ a_{0} , a_{1} , a_{2} , ... , a_{k-1} \big\} = 
 \begin{bmatrix}
-a^{(0)}[0] & a^{(0)}[1] & a^{(0)}[2] & \hdots & a^{(0)}[N-1] \\
-a^{(1)}[0] & a^{(1)}[1] & a^{(1)}[2] & \hdots & a^{(1)}[N-1] \\
-a^{(2)}[0] & a^{(2)}[1] & a^{(2)}[2] & \hdots & a^{(2)}[N-1] \\
+a_{0}[0] & a_{0}[1] & a_{0}[2] & \hdots & a_{0}[N-1] \\
+a_{1}[0] & a_{1}[1] & a_{1}[2] & \hdots & a_{1}[N-1] \\
+a_{2}[0] & a_{2}[1] & a_{2}[2] & \hdots & a_{2}[N-1] \\
 \vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
-a^{(k-1)}[0] & a^{(k-1)}[1] & a^{(k-1)}[2] & \hdots & a^{(k-1)}[N-1] \\
+a_{k-1}[0] & a_{k-1}[1] & a_{k-1}[2] & \hdots & a_{k-1}[N-1] \\
 \end{bmatrix}
 \end{equation}
-We use bracket notation, $[j]$ to indicate that each object is array-like. Many programming languages could also use the following indexing conventions for matrix 
-$A$:
+We use bracket notation, $[j]$ to indicate that each analysis frame $a_i$ is array-like. Many programming languages could also use the following indexing conventions for matrix $A$:
 \begin{equation}
 \label{eqn-IndexingA}
-A_{i,j} = a^{(i)}[j] = A[i][j] = A[i,j]
+A_{i,j} = A_i[j] = A[i][j] = A[i,j]
 \end{equation}
-Note that these all represent equivalent entries.
+These all represent equivalent entries.
 
@@
 \end{equation}
-The window function is applied to each analysis frame by computing the dot-product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
+The window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
 Result is an $k \times N$ array, $\widetilde{A}$:
@@
 \label{eqn-WindowMatrix}
-\widetilde{A} = A \cdot H^T
+\widetilde{A_i} = A_i \odot H
 \end{equation}
@@
 \label{eqn-Spectrogram}
-S = \big{\lVert} \mathbb{W}\widetilde{A}^T \big{\rVert}_{2}^{2}
+S_{i,j} = \big{\lVert} (\mathbb{W}\widetilde{A}^T)_{i,j} \big{\rVert}_{2}^{2}
 \end{equation}
@@
 \label{eqn-IndexingS}
-S_{i,j} = s^{(i)}[j] = S[i][j] = S[i,j]
+S_{i,j} = S[i][j] = S[i,j]
 \end{equation}
@@
 This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
-As a result of this, we can simply crop each matrix, to display frequencies that are only between $0$ Hz and $8000$ Hz.
+As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $8000$ Hz.
 This makes the input array smaller, and eliminates redundant and non-useful information.
 The number rows in the $S$ matrix is reduced from $N$ down to $N'$.
-lastly, each raw audio file may contain a different number of samples to begin with, thus a different number of analysis frames are created.
+Since each raw audio file may contain a different number of samples to begin with, a different number of analysis frames are created.
 To ensure all samples are a homogeneous size, we assert that each matrix must have exactly $k'$ columns.
@@
 
-\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample.
-In some cases, this can be from the waveform directly, or my manipulation of rows and columns in the analysis frames matrix $A$ from eqn.
-(\ref{eqn-FrameMatrix}).
-For each feature, we detail the physical significance and provide a visualization in feature-space.
+\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. Time space can be represented in one of three ways: 
+\begin{itemize}
+\item The raw waveform $s$\\
+Indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
+\item A single analysis frame $a_i$ \\
+Indexed by $a_i[j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
+\item The full analysis frame matrix $A$ \\
+Indexed by $A[i][j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
+\end{itemize}
 
 \paragraph*{}From time space, we use the following $7$ features:
+\begin{itemize}
+\item[•] Time Domain Envelope
+\item[•] Zero Crossing Rate
+\item[•] Temporal Center of Mass
+\item[•] Auto Correlation Coefficients ($\times 4$)
+\end{itemize}
 
-\begin{itemize}
-
-\item[•] Time Domain Envelope
-
-\item[•] Zero Crossing Rate
-
-\item[•] Temporal Center of Mass
-
-\item[•] Auto Correlation Coefficients ($\times 4$)
-
-\end{itemize}
+% ================================
 
@@
 
-\paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal.
-Generally, we start by computing the RMS-Energy of each frame.
-The larger the RMS energy of the frame, the larger the amplitude of the waveform in that frame.
-For frames with smaller amplitude, we conclude that the signal has either not begun, or is decaying.
-The RMS-Energy of a single analysis-frame $a^{(i)}$ is given by \cite{Olson,Virtanen}
+\paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal Often, we compute the RMS-Energy of each frame - a larger energy of the frame, the larger the average amplitude of the waveform in that frame.
+For frames with smaller amplitude, we can assume that the signal has either not begun, or is decaying.
+
+\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olson,Virtanen}
 \begin{equation}
 \label{eqn-RMS}
-\text{RMS}\big[ a^{(i)} \big] = \sqrt{\frac{1}{N} \sum_{j=0}^{N-1} \big( a^{(i)}[j]} \big)^2
+\text{RMS}\big[ s \big] = \sqrt{\frac{1}{N} \sum_{i=0}^{N-1} s[i]^2}
 \end{equation}
-
-\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}.
-By doing this, we acquire a rough estimate for the energy of a waveform in the entirety of the audio file \cite{Liu}.
-For instruments with long sustain or release times, such as strings or undampened mallet percussion, hold a comparably large waveform RMS when compared to those instruments without sustain such as brass or percussion.
+By using the full waveform, we acquire a rough estimate for the energy in the entirety of the audio file \cite{Liu}.
+For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large waveform RMS when compared to those instruments without sustain such as plucked stings or dampened percussion
 
@@
 
+% ================================
+
 \subsubsection{Zero Crossing Rate}
@@
 \paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses it's equilibrium point.
-This can be done per total sound wave, or per unit time, such an per analysis-frame.
-In differentiating speech and music, it is commonly to use the difference between the frame with the highest ZXR and the lowest ZXR.
+This can be done per total sound wave, per unit time, or per analysis-frame.
+This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform.
 In some cases, the ZXR can be correlated to frequency as well \cite{Kahn,Zhang}.
-The ZXR for a frame $a^{(i)}$ is given by \cite{Virtanen,Liu}
+
+\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}. The ZXR for the full waveform $s$ is given by \cite{Virtanen,Liu}
 \begin{equation}
 \label{eqn-ZXR}
-\text{ZXR}\big[ a^{(i)} \big] = \frac{1}{2} \sum_{j=1}^{N-1} \big{|} \sign(a^{(i)}[j]) - \sign(a^{(i)}[j-1]) \big{|} 
+\text{ZXR}\big[ s \big] = \frac{1}{2} \sum_{i=1}^{M-1} \big{|} \sign(s[i]) - \sign(s[i-1]) \big{|} 
 \end{equation}
 Where $\sign(x)$ returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$.
-
-\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}.
-This provides a rough estimate for the average frequency in the full waveform, and can help discern clean periodic signals (low ZXR) from those that may have more volatile behavior (high ZXR)\cite{Virtanen}.
+This provides a rough estimate for the average frequency in the full waveform, and can help discern clean periodic signals (low ZXR) from those that may have more noise or volatile behavior (high ZXR)\cite{Virtanen}.
 
@@
 
+% ================================
+
 \subsubsection{Center of Mass}
 
-\paragraph*{}The temporal center of mass (TCM) of a signal is used to compute where in time the amplitude sort of \textit{bunches up}.
-We treat the full waveform array, $a$, with $M$ samples as a 1-Dimensional discrete mass distribution.
+\paragraph*{}The temporal center of mass (TCM) of a signal is used to compute roughly where in time the amplitude of the waveform \textit{bunches up}.
+We treat the full waveform array, $s$, with $M$ samples as a 1-Dimensional discrete mass distribution.
 The TCM of that waveform is then given:
@@
 \label{eqn-FeatureTCM}
-\text{TCM}\big[ a \big] = \frac{\sum_{j=0}^{M-1}j a[j]}{\sum_{j=0}^{M-1}a[j]}
+\text{TCM}\big[ s \big] = \frac{\sum_{i=0}^{M-1}i s[i]}{\sum_{i=0}^{M-1}s[i]}
 \end{equation}
@@
 \paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance.
-For instruments with heavier attacks, we expect the TCM to be a very low value as most of the energy and amplitude is concentrated close to the start of the audio file.
-For instruments with long sustain times, we expect a very centrally located center of mass, and for instruments with long release times, we expect a very late TCM value.
+For instruments with heavier attacks, we expect the TCM to be a very near the start of the waveform.
+For instruments with long sustain times, we expect a very centrally located center of mass, and for instruments with long release times, we expect a later TCM value.
 
@@
 
+% ================================
+
 \subsubsection{Auto Correlation Coefficients}
 
-\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution \cite{Virtanen}.
+\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution .
 We can compute any number of ACC's and their value changed depending on the index chosen.
-It is common to only compute the first $k$ ACC's.
-For a full waveform signal $a$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
+It is common to only compute the first $K$ ACC's \cite{Virtanen}.
+For a full waveform signal $s$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
 \begin{equation}
 \label{eqn-FeatureACC}
-\text{ACC}_k\big[ a \big] = \frac{\sum_{j=0}^{M-k-1}a[j]a[j+k]} {\sqrt{\sum_{j=0}^{M-k-1}a^2[j]} \sqrt{\sum_{j=0}^{M-k-1}a^2[j+k]}}
+\text{ACC}_k\big[ s \big] = 
+\frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]} {\sqrt{\sum_{i=0}^{M-k-1}s^2[i]} \sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
 \end{equation}
@@
 \paragraph*{}The features described in this section are derived from the frequency-domain representations of each audio sample.
-Each of these features are exacted from the transpose spectrogram representation, $S^T$, where the creation of $S$ is outlined in sec.
-(\ref{subsec-spectrogram}) and computed in eqn.(\ref{eqn-Spectrogram}).
-This is done to return analysis frame into a row-like array, representing frequency space divided into $N'$ bins, with $k'$ analysis frames.
+Frequency space is represented by the transposed spectrogram matrix, $S^T$, described in sec.
+(\ref{subsec-spectrogram}).
+This is done to ensure that each  row is now an analysis frame, each column is a frequency bin.
+This gives a similar structure to the time-space analysis frames matrix, $A$, in eqn.
+(\ref{eqn-FrameMatrix}).
 For each feature, we detail the physical significance and provide a visualization in feature-space.
@@
 \begin{itemize}
+\item[•] Mel Frequency Cepstral Coefficients ($\times 12$)
+\item[•] Frequency Center of Mass
+\end{itemize}
 
-\item[•] Mel Frequency Cepstral Coefficients ($\times 12$)
-
-\item[•] Frequency Center of Mass
-
-\end{itemize}
+% ================================
 
@@
 MFCC's are produced by converting a linear-frequency axis with units such as Hertz into units of Mels, which are design to account for the non-linear perception of frequency in humans.
-The Hertz to Mel and Mel to Hertz transforms are provided \cite{Virtanen}:
+The Hertz to Mel and Mel to Hertz transforms are given \cite{Virtanen}:
 \begin{equation}
@@
 
+% ================================
+
 \subsubsection{Center of Mass}
@@
 \paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a strong representation of how overtones and energy is distributed in the signal's frequency domain.
-As with the temporal center-of-mass, we treat each row of the $S$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
+As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
 This encodes the FCM for a single analysis frame (in frequency-space) in the waveform.

### 2020-09-30 Thesis/Sections/TheNerualNetwork.tex

@@
 \end{figure}
+For our chosen architecture, ReLU is applied to the activations in every single Convolution layer and Dense Layer, with the exception of the output dense layer.
 
 \subsubsection{Softmax}
+
+\paragraph*{}The softmax activation function is commonly used in the output layer of a multi-class classification network, such as the one we implement.
+When softmax acts on a vector or activation, the result is a normalized,non-negative output vector.
+\cite{Geron,Goodfellow,Virtanen}.
+The $i$-th element in a softmax activation function is given by:
+\begin{equation}
+\label{eqn-Softmax}
+\text{Softmax}\big[ x \big]_{i} = \frac{1}{\sum_{j}e^{x_j}}e^{x_i}
+\end{equation}
+
+\paragraph*{}This function is only used in the output layer of a neural network, and encodes a discrete categorical probability.
+For example, if eqn.(\ref{eqn-Softmax}) returns a vector of the form: $[ 0.75 , 0.25]$, we interpret this as a sample having a $75\%$ chance of beloinging to class $0$ and a $25\%$ change of belonging to class $1$.
 
@@
 
-\paragraph*{}The last layer in eachof the two branches is a ReLu-activated Dense layer containing 64 neurons. The activations are concatenated
+\paragraph*{}The last layer in each of the two branches is a ReLU-activated Dense layer containing 64 neurons, represented by a $64 \times 1$ column vectors.
+We combine these model layers by using a \textit{concatenation layer} to fuse the two column vectors together, "vertically", such that the result is a $128 \times 1$ column vector.
+This vector is then passed into the final dense layer, which used the softmax activation, and encodes the joint predictions based on both model branches.
 

### 2020-09-30 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis Draft v0
- Reoranized Sections
- Relabeld important setions
- Appended acknowledgements

@@
 \DeclareMathOperator{\sign}{\text{sign}}
+
+\setcounter{tocdepth}{2}
 
@@
        	\begin{Large}
-       	Thesis Subtitle 
+       	\textcolor{red}{Thesis Subtitle}
        	\end{Large}             
@@
       	A thesis presented for the degree of\\
-       	Bachelor of Science in Physics
+       	Bachelor of Science in Physics \\
+       	\vspace{0.5cm}
+       	\textbf{December 2020}
         \vspace{1cm}
@@
        	$^2$Department of Mathematics and Statistics\\
-       \vspace{1cm}  
+       	\vspace{0.5cm}  
        	University of New Hampshire\\
        	Durham New Hampshire, USA\\            
-       Dec 2020\\
-
    \end{center}
@@
 
-\paragraph*{}In order to train the Multimodal neural network to identify musical instrument sources, we need a suitable data set to present to the model.
+\paragraph*{}In order to train the Multimodal neural network to identify musical instrument sources, we need a suitable data set to present to the model as training data.
 University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \textcolor{blue}{Citations!}.
 These contain short segments of musical instruments performing a single note or a collection of notes in succession.
-
-\paragraph*{}To ensure that these data sets are roughly homogeneous, we read each sample from it's original format, \textit{.aif}, \textit{.mp3}, or similar, and rewrite each sample as a new \textit{.wav} files, sampled at 44.1 kHz, with a 16 bit depth \textcolor{red}{check this!}.
+Each sound file is labeled according to the instrument that is producing that sound.
+
+\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 16 bit depth \textcolor{red}{check this!}.
 This ensures that all data will have a consistent format when features are extracted.
-We also use this stage to ensure that each audio file has a correct label, and to determine the number of unique output classes.
-
+This stage is detailed in sec.(\ref{subsubsec-Preprocessing}).
 % ================================================================
@@
 These are properties of wave forms that can be represented by a numerical value or several numerical values and are used as the primary tool in classification.
-There are used in place of a full waveform to represent a file's contents We use tools from physics, mathematics, and signal processing to define and explore a comprehensive set of features that enables a high performance of the classifier.
+We detail these features in sec.
+(\ref{sec-Features}).
+These are used in place of a full waveform to represent a file's contents in a low-dimensional array.
+We use tools from physics, mathematics, and signal processing to define and explore a comprehensive set of features that enables a high performance of the classifier.
 
@@
 \paragraph*{}With the appropriate set of features designed, and the number of output determined, we can organize the structure of the neural network function.
-We construct a multimodal neural network than processes two input arrays derived from the same audio sample that share a common label.
+We construct a multimodal neural network, explored in sec.
+(\ref{sec-Architecture}), that processes two input arrays derived from the same audio sample.
 This network is designed to handle and process each respective input independently, and concatenate the results to produce a single output.
@@
 If further corrections are needed, we revert and re-deign the features, architecture, or hyper-parameters as needed.
+
+% ================================================================
+% ================================================================
+
+\newpage
+\section{Feature Selections}
+\label{sec-Features}
+
+\paragraph*{}Audio and Machine learning researchers M.
+Kashif Saeed Khan and Wasfi G.
+Al-Khatib discuss the vitality of feature selection \cite{Khan}: \textcolor{red}{I'm not sure how to introduce the importance of feature extraction}
+\begin{quote}
+The data reduction stage which is also called feature extraction, consists of discovering a few important facts about each class.
+The choice of features is critical as it greatly affects the accuracy of audio classification.
+\end{quote}
+In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}.
+It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier.
+Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels.
+The inappropriate choice features does not reflect the significant characteristics of the signal.
+
+\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" \cite{Virtanen}:
+\begin{quote}
+For recognition algorithms, the necessary property of the acoustic features is low variability among features extracted from examples assigned to the same class, and at the same time high variability allowing distinction between features extracted from examples assigned to different classes.
+\end{quote}
+In constructing a neural network classifier, the development of appropriate features is of the utmost importance.
+To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency space representation of the waveform.
+It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely on these features.
+
+\paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}.
+In the training process, this object, along with the appropriate classification label, $y$ is presented to the neural network for processing.
+This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu}
+
+\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector.
+These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics.
+In the following sections, we outline the set of $21$ features used in the classification process
+
+\newpage
+
+% ================================
+
+\subsubsection{The Design Matrix}
+
+\paragraph*{}The $21$ features are from each file are organized into one of two array structures.
+each called a \textit{design matrix}.
+A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest.
+For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.
+each has shape given by:
+\begin{equation}
+\label{eqn-X1Shape}
+X_1 \in \mathbb{R}^{(b \times N' \times k' \times 1)}
+\end{equation}
+\begin{equation}
+\label{eqn-X2Shape}
+X_2 \in \mathbb{R}^{(b \times p)}
+\end{equation}
+Where $N' \times k' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
+(\ref{subsec-spectrogram}), The first axis, with length $b$ indicates that there are $b$ samples stored in that design matrix.
+Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec.
+(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).
+A row of $X_2$ has shape $1 \times p$ where there are $p$ features within the \textit{feature-vector} for each sample.
+Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.
+
+% ================================
+
+\subsubsection{Audio Preprocessing}
+\label{subsubsec-Preprocessing}
+
+\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}.
+In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
+\begin{enumerate}
+\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
+\item Audio encoded in a standard, and consistent format
+\item A consistent sample rate and bit depth between audio files
+\item A consistent number of channels
+\end{enumerate}
+Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
+\begin{enumerate}
+\item Roughly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
+\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
+\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
+\item All audio has been down-mixed into mono-channel waveforms.
+\end{enumerate}
+
+% ================================================================
+
+\newpage
+
+\subsection{Spectrogram Feature}
+\label{subsec-spectrogram}
+
+\paragraph*{}The field of neural classification is well studied in the application of image-processing.
+Many large-scale, and even introductory neural network projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
+As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior.
+Following this success, it make senses to provide an image-like representation of a sound wave as a feature.
+We do this in the form of a spectrogram matrix.
+
+\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both space and time.
+In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis.
+Thus each point in the 2-Dimensional space is an energy at a given time and frequency.
+Examples spectrograms from the wave form data set are shown in Fig.
+(\ref{fig-spectrograms}).
+
+\begin{figure}[H]
+\begin{center}
+\label{fig-spectrograms}
+\textcolor{red}{Insert spectrograms here}
+\caption{Spectrogram representations of various waveforms}
+\end{center}
+\end{figure}
+
+\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification.
+Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame.
+Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhang,Kahn,Virtanen}.
+For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
+At a sample rate of $f_s = 44100$ samples/second, each frame represents a slice of time that is about $0.1$ seconds long.
+
+\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
+\begin{equation}
+\label{eqn-FrameMatrix}
+A = \big\{ a_{0} , a_{1} , a_{2} , ... , a_{k-1} \big\} = 
+\begin{bmatrix}
+a_{0}[0] & a_{0}[1] & a_{0}[2] & \hdots & a_{0}[N-1] \\
+a_{1}[0] & a_{1}[1] & a_{1}[2] & \hdots & a_{1}[N-1] \\
+a_{2}[0] & a_{2}[1] & a_{2}[2] & \hdots & a_{2}[N-1] \\
+\vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
+a_{k-1}[0] & a_{k-1}[1] & a_{k-1}[2] & \hdots & a_{k-1}[N-1] \\
+\end{bmatrix}
+\end{equation}
+We use bracket notation, $[j]$ to indicate that each analysis frame $a_i$ is array-like. Many programming languages could also use the following indexing conventions for matrix $A$:
+\begin{equation}
+\label{eqn-IndexingA}
+A_{i,j} = A_i[j] = A[i][j] = A[i,j]
+\end{equation}
+These all represent equivalent entries.
+
+\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
+A standard \textit{Hann Window} of $N$ samples is generated and reshaped into a $N \times 1$ column-array, $H$.
+The $n$-th index in a Hann window with $N$ samples is defined:
+\begin{equation}
+\label{eqn-Hann}
+H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
+\end{equation}
+The window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
+Result is an $k \times N$ array, $\widetilde{A}$:
+\begin{equation}
+\label{eqn-WindowMatrix}
+\widetilde{A_i} = A_i \odot H
+\end{equation}
+
+\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross}.
+The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
+Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space containing $N$ samples
+\begin{equation}
+\label{eqn-DFTMatrix}
+\mathbb{W} = \frac{1}{\sqrt{N}}
+\begin{bmatrix}
+1 & 1 & 1 & 1 & \hdots & 1 \\
+1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
+1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
+1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
+\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
+1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
+\end{bmatrix}
+\end{equation}
+Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $\widetilde{A}^T$.
+The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
+
+\paragraph*{}Most standard implementations of neural network models require all activations, weights, and biases to be real floating-point numbers.
+Since the the DFT matrix introduces complex values, we compute the square of the element-wise $L2$-norm of the resultant array.
+\begin{equation}
+\label{eqn-Spectrogram}
+S_{i,j} = \big{\lVert} (\mathbb{W}\widetilde{A}^T)_{i,j} \big{\rVert}_{2}^{2}
+\end{equation}
+Where $\mathbb{W}$ is the DFT matrix from eqn.
+(\ref{eqn-DFTMatrix}) and $\widetilde{A}^T$ is the transpose of the analysis frames matrix from eqn.
+(\ref{eqn-WindowMatrix}).
+The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of real floating-point numbers.
+We can index matrix $S$ similarly to that of matrix $A$ in eqn.
+(\ref{eqn-IndexingA}):
+\begin{equation}
+\label{eqn-IndexingS}
+S_{i,j} = S[i][j] = S[i,j]
+\end{equation}
+
+\paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames.
+Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins.
+Since human hearing extends from $20$ Hz to $20$ kHz, audio files such as music and voice recordings are typically sampled around $44.1$ kHz, to ensure that the full range of audio is held by the recording \cite{Olson,Virtanen}.
+
+\paragraph*{}However, standard musical instruments seldom extend above $8$ kHz \cite{Olson,Virtanen,White}.
+This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
+As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $8000$ Hz.
+This makes the input array smaller, and eliminates redundant and non-useful information.
+The number rows in the $S$ matrix is reduced from $N$ down to $N'$.
+Since each raw audio file may contain a different number of samples to begin with, a different number of analysis frames are created.
+To ensure all samples are a homogeneous size, we assert that each matrix must have exactly $k'$ columns.
+If $k' < k$, columns of zeros are added to pad the input, and if $k' > k$, columns are removed.
+
+\paragraph*{}Each spectrogram is now $N' \times k' \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform a a function of both time and frequency.
+The spectrogram is the first feature used in this model.
+For this classifier, we have chosen $N' = 560$ and $k' = 256$.
+For training, a batch of $b$ samples are concatenated into a single array object.
+\textcolor{blue}{See Neural Network section for more details}.
+For a batch of $b$ samples of $N' \times k' \times 1$ spectrograms, we shape $X_1$ such that:
+\begin{equation}
+\label{eqn-X1 shape}
+X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k' \times 1)}
+\end{equation}
+Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}).
+This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
+\textcolor{blue}{See Neural Network section for more details}
+
+% ================================================================
+
+\newpage
+
+\subsection{Time-Space Features}
+\label{subsec-time}
+
+\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. Time space can be represented in one of three ways: 
+\begin{itemize}
+\item The raw waveform $s$\\
+Indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
+\item A single analysis frame $a_i$ \\
+Indexed by $a_i[j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
+\item The full analysis frame matrix $A$ \\
+Indexed by $A[i][j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
+\end{itemize}
+
+\paragraph*{}From time space, we use the following $7$ features:
+\begin{itemize}
+\item[•] Time Domain Envelope
+\item[•] Zero Crossing Rate
+\item[•] Temporal Center of Mass
+\item[•] Auto Correlation Coefficients ($\times 4$)
+\end{itemize}
+
+% ================================
+
+\subsubsection{Time Domain Envelope}
+
+\paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal Often, we compute the RMS-Energy of each frame - a larger energy of the frame, the larger the average amplitude of the waveform in that frame.
+For frames with smaller amplitude, we can assume that the signal has either not begun, or is decaying.
+
+\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olson,Virtanen}
+\begin{equation}
+\label{eqn-RMS}
+\text{RMS}\big[ s \big] = \sqrt{\frac{1}{N} \sum_{i=0}^{N-1} s[i]^2}
+\end{equation}
+By using the full waveform, we acquire a rough estimate for the energy in the entirety of the audio file \cite{Liu}.
+For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large waveform RMS when compared to those instruments without sustain such as plucked stings or dampened percussion
+
+\begin{figure}[H]
+\label{fig-FeatureTDE}
+\begin{center}
+\textcolor{red}{PLOT OF TDE FEATURES HERE}
+\end{center}
+\caption{Time domain envelope visualized in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Zero Crossing Rate}
+
+\paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses it's equilibrium point.
+This can be done per total sound wave, per unit time, or per analysis-frame.
+This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform.
+In some cases, the ZXR can be correlated to frequency as well \cite{Kahn,Zhang}.
+
+\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}. The ZXR for the full waveform $s$ is given by \cite{Virtanen,Liu}
+\begin{equation}
+\label{eqn-ZXR}
+\text{ZXR}\big[ s \big] = \frac{1}{2} \sum_{i=1}^{M-1} \big{|} \sign(s[i]) - \sign(s[i-1]) \big{|} 
+\end{equation}
+Where $\sign(x)$ returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$.
+This provides a rough estimate for the average frequency in the full waveform, and can help discern clean periodic signals (low ZXR) from those that may have more noise or volatile behavior (high ZXR)\cite{Virtanen}.
+
+\begin{figure}[H]
+\label{fig-FeatureZXR}
+\begin{center}
+\textcolor{red}{PLOT OF ZXR FEATURES HERE}
+\end{center}
+\caption{Zero crossing rate visualized in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Center of Mass}
+
+\paragraph*{}The temporal center of mass (TCM) of a signal is used to compute roughly where in time the amplitude of the waveform \textit{bunches up}.
+We treat the full waveform array, $s$, with $M$ samples as a 1-Dimensional discrete mass distribution.
+The TCM of that waveform is then given:
+\begin{equation}
+\label{eqn-FeatureTCM}
+\text{TCM}\big[ s \big] = \frac{\sum_{i=0}^{M-1}i s[i]}{\sum_{i=0}^{M-1}s[i]}
+\end{equation}
+This includes negative amplitude values acting as "negative masses".
+
+\paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance.
+For instruments with heavier attacks, we expect the TCM to be a very near the start of the waveform.
+For instruments with long sustain times, we expect a very centrally located center of mass, and for instruments with long release times, we expect a later TCM value.
+
+\begin{figure}[H]
+\label{fig-FeatureTCM}
+\begin{center}
+\textcolor{red}{PLOT OF TCM FEATURES HERE}
+\end{center}
+\caption{Temporal center-of-mass visualized in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Auto Correlation Coefficients}
+
+\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution .
+We can compute any number of ACC's and their value changed depending on the index chosen.
+It is common to only compute the first $K$ ACC's \cite{Virtanen}.
+For a full waveform signal $s$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
+\begin{equation}
+\label{eqn-FeatureACC}
+\text{ACC}_k\big[ s \big] = 
+\frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]} {\sqrt{\sum_{i=0}^{M-k-1}s^2[i]} \sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
+\end{equation}
+
+\begin{figure}[H]
+\label{fig-FeatureACC}
+\begin{center}
+\textcolor{red}{PLOT OF ACC FEATURES HERE}
+\end{center}
+\caption{First four auto correlation coefficients visualized in feature-space}
+\end{figure}
+
+% ================================================================
+
+\newpage
+
+\subsection{Frequency-Space Features}
+\label{subsec-frequency}
+
+\paragraph*{}The features described in this section are derived from the frequency-domain representations of each audio sample.
+Frequency space is represented by the transposed spectrogram matrix, $S^T$, described in sec.
+(\ref{subsec-spectrogram}).
+This is done to ensure that each  row is now an analysis frame, each column is a frequency bin.
+This gives a similar structure to the time-space analysis frames matrix, $A$, in eqn.
+(\ref{eqn-FrameMatrix}).
+For each feature, we detail the physical significance and provide a visualization in feature-space.
+
+\paragraph*{}From frequency space, we use the following $13$ features:
+\begin{itemize}
+\item[•] Mel Frequency Cepstral Coefficients ($\times 12$)
+\item[•] Frequency Center of Mass
+\end{itemize}
+
+% ================================
+
+\subsubsection{Mel Frequency Cepstral Coefficients}
+
+\paragraph*{}Mel Frequency Ceptstral Coefficients (MFCC's) are a very prolific feature used widly in audio classification tasks \cite{Liu,Virtanen,Zhang}.
+MFCC's are produced by converting a linear-frequency axis with units such as Hertz into units of Mels, which are design to account for the non-linear perception of frequency in humans.
+The Hertz to Mel and Mel to Hertz transforms are given \cite{Virtanen}:
+\begin{equation}
+\label{eqn-HztoMel}
+M_f[h] = 2595 \log_{10}\big(1+ \frac{h}{700}\big)
+\end{equation}
+\begin{equation}
+\label{eqn-MeltoHz}
+H_f[m] = 700 \big(10^{(\frac{m}{2595})}-1\big)
+\end{equation}
+Where $M_f$ is the frequency in units of Mels, given $[h]$, a frequency in Hertz, and $H_f$ is the frequency in Hertz given $[m]$ a frequency in Mels.
+
+\paragraph*{}Mel filters are produced by grouping frequency-space into $R$ overlapping bins called \textit{Mel Filter-banks}.
+In units of Mels, each filter bank, $R_i$ remains a constant width, but when shown in Hertz, the bins increase logarithmically.
+\begin{figure}[H]
+\label{fig-MelFilterBanks}
+\begin{center}
+\textcolor{red}{Figure of a few Mel Filter Banks goes here}
+\end{center}
+\caption{Mel Filter Banks shown in frequency space with units of Hertz}
+\end{figure}
+Each of the $R$ filters is created to be $N'$ samples long, and transformed back into units of Hertz.
+When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
+Thus, each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is a filter.
+We apply the Mel Filter banks to the spectrogram to create matrix $B$:
+\begin{equation}
+\label{eqn-FilterBanks}
+B = S^T M^T
+\end{equation}
+Matrix $B$ has shape $k' \times R$.
+
+\paragraph*{}Using $S^T$ ensure that each row of the matrix is an analysis frame in frequency space.
+Similarly, each column of the matrix $M$ is a appropriately scaled Mel filter-bank.
+This way, the matrix product in eqn.
+(\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
+Finally, we compute the average energy across all $k'$ frames.
+The resulting $R$ floating-point numbers are approximation of the signal's energy in those particular frequency bands.
+For this project, we have chosen to use $R = 12$ filter-banks, which are all used as features.
+
+\begin{figure}[H]
+\label{fig-FeatureMFCC}
+\begin{center}
+\textcolor{red}{PLOT OF MFCC FEATURES HERE}
+\end{center}
+\caption{Mel Frequency Ceptral Coefficients in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Center of Mass}
+
+\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a strong representation of how overtones and energy is distributed in the signal's frequency domain.
+As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
+This encodes the FCM for a single analysis frame (in frequency-space) in the waveform.
+For an frequency-analysis frame, $s^{(i)}$, the FCM is given by:
+\begin{equation}
+\label{eqn-FeatureFCM}
+\text{TCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
+\end{equation}
+We compute the FCM for each of the $k'$ frames, and then average the results. We use the average FCM across $k'$ frames to compute the FCM feature:
+\begin{equation}
+TCM = \sum_{i=0}^{k'} \text{TCM}_{i}\big[ s^{(i)} \big]
+\end{equation}
+
+\paragraph*{}The average FCM gives a strong approximation of the instrument or signal source's range.
+For example, a flute or violin will have a considerably high FCM value, even in their lower registers.
+Similarly, basses or tubas will have considerably low FCM values.
+Given that the standard frequency range of some musical instruments is fixed, it is guaranteed that for any particular instrument, the FCM will consistently remain within certain bounds \cite{Olson,White}.
+
+\begin{figure}[H]
+\label{fig-FeatureFCM}
+\begin{center}
+\textcolor{red}{PLOT OF FCM FEATURES HERE}
+\end{center}
+\caption{Frequency center-of-mass visualized in feature-space}
+\end{figure}
 
@@
 
-\section{Feature Selections}
-\label{sec-FeatureSelections}
-
-\paragraph*{}Even best minds in the world will perform poorly on test which they have studied the wrong material- neural networks are no different.
-In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}.
-It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier.
-Consider if you were tasked to identify cats and dogs from images, but instead were presented with only the top-most row of pixels- The task would be nearly impossible because of an inappropriate or in complete set of information.
-
-\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" \cite{Virtanen}:
-\begin{quote}
-For recognition algorithms, the necessary property of the acoustic features is low variability among features extracted from examples assigned to the same class, and at the same time high variability allowing distinction between features extracted from examples assigned to different classes.
-\end{quote}
-In constructing a neural network classifier, the development of appropriate features is of the utmost importance.
-To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency space representation of the waveform.
-It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely on these features.
-
-\paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}.
-In the training process, this object, along with the appropriate classification label, $y$ is presented to the neural network for processing.
-This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu}
-
-\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector.
-These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics.
-In the following sections, we outline the set of $21$ features used in the classification process
-
 \newpage
-
-% ================================
-
-\subsubsection{The Design Matrix}
-
-\paragraph*{}The $21$ features are from each file are organized into one of two array structures.
-each called a \textit{design matrix}.
-A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest.
-For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.
-each has shape given by:
-\begin{equation}
-\label{eqn-X1Shape}
-X_1 \in \mathbb{R}^{(b \times N' \times k' \times 1)}
-\end{equation}
-\begin{equation}
-\label{eqn-X2Shape}
-X_2 \in \mathbb{R}^{(b \times p)}
-\end{equation}
-Where $N' \times k' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
-(\ref{subsec-spectrogram}), The first axis, with length $b$ indicates that there are $b$ samples stored in that design matrix.
-Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec.
-(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).
-A row of $X_2$ has shape $1 \times p$ where there are $p$ features within the \textit{feature-vector} for each sample.
-Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.
-
-% ================================
-
-\subsubsection{Audio Preprocessing}
-
-\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}.
-In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
-\begin{enumerate}
-\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
-\item Audio encoded in a standard, and consistent format
-\item A consistent sample rate and bit depth between audio files
-\item A consistent number of channels
-\end{enumerate}
-Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
-\begin{enumerate}
-\item Roughly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
-\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
-\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
-\item All audio has been down-mixed into mono-channel waveforms.
-\end{enumerate}
-
-% ================================================================
-
-\newpage
-
-\subsection{Spectrogram Feature}
-\label{subsec-spectrogram}
-
-\paragraph*{}The field of neural classification is well studied in the application of image-processing.
-Many large-scale, and even introductory neural network projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
-As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior.
-Following this success, it make senses to provide an image-like representation of a sound wave as a feature.
-We do this in the form of a spectrogram matrix.
-
-\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both space and time.
-In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis.
-Thus each point in the 2-Dimensional space is an energy at a given time and frequency.
-Examples spectrograms from the wave form data set are shown in Fig.
-(\ref{fig-spectrograms}).
-
-\begin{figure}[H]
-\begin{center}
-\label{fig-spectrograms}
-\textcolor{red}{Insert spectrograms here}
-\caption{Spectrogram representations of various waveforms}
-\end{center}
-\end{figure}
-
-\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification.
-Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame.
-Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhang,Kahn,Virtanen}.
-For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
-At a sample rate of $f_s = 44100$ samples/second, each frame represents a slice of time that is about $0.1$ seconds long.
-
-\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
-\begin{equation}
-\label{eqn-FrameMatrix}
-A = \big\{ a_{0} , a_{1} , a_{2} , ... , a_{k-1} \big\} = 
-\begin{bmatrix}
-a_{0}[0] & a_{0}[1] & a_{0}[2] & \hdots & a_{0}[N-1] \\
-a_{1}[0] & a_{1}[1] & a_{1}[2] & \hdots & a_{1}[N-1] \\
-a_{2}[0] & a_{2}[1] & a_{2}[2] & \hdots & a_{2}[N-1] \\
-\vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
-a_{k-1}[0] & a_{k-1}[1] & a_{k-1}[2] & \hdots & a_{k-1}[N-1] \\
-\end{bmatrix}
-\end{equation}
-We use bracket notation, $[j]$ to indicate that each analysis frame $a_i$ is array-like. Many programming languages could also use the following indexing conventions for matrix $A$:
-\begin{equation}
-\label{eqn-IndexingA}
-A_{i,j} = A_i[j] = A[i][j] = A[i,j]
-\end{equation}
-These all represent equivalent entries.
-
-\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
-A standard \textit{Hann Window} of $N$ samples is generated and reshaped into a $N \times 1$ column-array, $H$.
-The $n$-th index in a Hann window with $N$ samples is defined:
-\begin{equation}
-\label{eqn-Hann}
-H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
-\end{equation}
-The window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
-Result is an $k \times N$ array, $\widetilde{A}$:
-\begin{equation}
-\label{eqn-WindowMatrix}
-\widetilde{A_i} = A_i \odot H
-\end{equation}
-
-\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross}.
-The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
-Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space containing $N$ samples
-\begin{equation}
-\label{eqn-DFTMatrix}
-\mathbb{W} = \frac{1}{\sqrt{N}}
-\begin{bmatrix}
-1 & 1 & 1 & 1 & \hdots & 1 \\
-1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
-1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
-1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
-\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
-1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
-\end{bmatrix}
-\end{equation}
-Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $\widetilde{A}^T$.
-The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
-
-\paragraph*{}Most standard implementations of neural network models require all activations, weights, and biases to be real floating-point numbers.
-Since the the DFT matrix introduces complex values, we compute the square of the element-wise $L2$-norm of the resultant array.
-\begin{equation}
-\label{eqn-Spectrogram}
-S_{i,j} = \big{\lVert} (\mathbb{W}\widetilde{A}^T)_{i,j} \big{\rVert}_{2}^{2}
-\end{equation}
-Where $\mathbb{W}$ is the DFT matrix from eqn.
-(\ref{eqn-DFTMatrix}) and $\widetilde{A}^T$ is the transpose of the analysis frames matrix from eqn.
-(\ref{eqn-WindowMatrix}).
-The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of real floating-point numbers.
-We can index matrix $S$ similarly to that of matrix $A$ in eqn.
-(\ref{eqn-IndexingA}):
-\begin{equation}
-\label{eqn-IndexingS}
-S_{i,j} = S[i][j] = S[i,j]
-\end{equation}
-
-\paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames.
-Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins.
-Since human hearing extends from $20$ Hz to $20$ kHz, audio files such as music and voice recordings are typically sampled around $44.1$ kHz, to ensure that the full range of audio is held by the recording \cite{Olson,Virtanen}.
-
-\paragraph*{}However, standard musical instruments seldom extend above $8$ kHz \cite{Olson,Virtanen,White}.
-This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
-As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $8000$ Hz.
-This makes the input array smaller, and eliminates redundant and non-useful information.
-The number rows in the $S$ matrix is reduced from $N$ down to $N'$.
-Since each raw audio file may contain a different number of samples to begin with, a different number of analysis frames are created.
-To ensure all samples are a homogeneous size, we assert that each matrix must have exactly $k'$ columns.
-If $k' < k$, columns of zeros are added to pad the input, and if $k' > k$, columns are removed.
-
-\paragraph*{}Each spectrogram is now $N' \times k' \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform a a function of both time and frequency.
-The spectrogram is the first feature used in this model.
-For this classifier, we have chosen $N' = 560$ and $k' = 256$.
-For training, a batch of $b$ samples are concatenated into a single array object.
-\textcolor{blue}{See Neural Network section for more details}.
-For a batch of $b$ samples of $N' \times k' \times 1$ spectrograms, we shape $X_1$ such that:
-\begin{equation}
-\label{eqn-X1 shape}
-X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k' \times 1)}
-\end{equation}
-Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}).
-This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
-\textcolor{blue}{See Neural Network section for more details}
-
-% ================================================================
-
-\newpage
-
-\subsection{Time-Space Features}
-\label{subsec-time}
-
-\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. Time space can be represented in one of three ways: 
-\begin{itemize}
-\item The raw waveform $s$\\
-Indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
-\item A single analysis frame $a_i$ \\
-Indexed by $a_i[j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
-\item The full analysis frame matrix $A$ \\
-Indexed by $A[i][j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
-\end{itemize}
-
-\paragraph*{}From time space, we use the following $7$ features:
-\begin{itemize}
-\item[•] Time Domain Envelope
-\item[•] Zero Crossing Rate
-\item[•] Temporal Center of Mass
-\item[•] Auto Correlation Coefficients ($\times 4$)
-\end{itemize}
-
-% ================================
-
-\subsubsection{Time Domain Envelope}
-
-\paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal Often, we compute the RMS-Energy of each frame - a larger energy of the frame, the larger the average amplitude of the waveform in that frame.
-For frames with smaller amplitude, we can assume that the signal has either not begun, or is decaying.
-
-\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olson,Virtanen}
-\begin{equation}
-\label{eqn-RMS}
-\text{RMS}\big[ s \big] = \sqrt{\frac{1}{N} \sum_{i=0}^{N-1} s[i]^2}
-\end{equation}
-By using the full waveform, we acquire a rough estimate for the energy in the entirety of the audio file \cite{Liu}.
-For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large waveform RMS when compared to those instruments without sustain such as plucked stings or dampened percussion
-
-\begin{figure}[H]
-\label{fig-FeatureTDE}
-\begin{center}
-\textcolor{red}{PLOT OF TDE FEATURES HERE}
-\end{center}
-\caption{Time domain envelope visualized in feature-space}
-\end{figure}
-
-% ================================
-
-\subsubsection{Zero Crossing Rate}
-
-\paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses it's equilibrium point.
-This can be done per total sound wave, per unit time, or per analysis-frame.
-This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform.
-In some cases, the ZXR can be correlated to frequency as well \cite{Kahn,Zhang}.
-
-\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}. The ZXR for the full waveform $s$ is given by \cite{Virtanen,Liu}
-\begin{equation}
-\label{eqn-ZXR}
-\text{ZXR}\big[ s \big] = \frac{1}{2} \sum_{i=1}^{M-1} \big{|} \sign(s[i]) - \sign(s[i-1]) \big{|} 
-\end{equation}
-Where $\sign(x)$ returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$.
-This provides a rough estimate for the average frequency in the full waveform, and can help discern clean periodic signals (low ZXR) from those that may have more noise or volatile behavior (high ZXR)\cite{Virtanen}.
-
-\begin{figure}[H]
-\label{fig-FeatureZXR}
-\begin{center}
-\textcolor{red}{PLOT OF ZXR FEATURES HERE}
-\end{center}
-\caption{Zero crossing rate visualized in feature-space}
-\end{figure}
-
-% ================================
-
-\subsubsection{Center of Mass}
-
-\paragraph*{}The temporal center of mass (TCM) of a signal is used to compute roughly where in time the amplitude of the waveform \textit{bunches up}.
-We treat the full waveform array, $s$, with $M$ samples as a 1-Dimensional discrete mass distribution.
-The TCM of that waveform is then given:
-\begin{equation}
-\label{eqn-FeatureTCM}
-\text{TCM}\big[ s \big] = \frac{\sum_{i=0}^{M-1}i s[i]}{\sum_{i=0}^{M-1}s[i]}
-\end{equation}
-This includes negative amplitude values acting as "negative masses".
-
-\paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance.
-For instruments with heavier attacks, we expect the TCM to be a very near the start of the waveform.
-For instruments with long sustain times, we expect a very centrally located center of mass, and for instruments with long release times, we expect a later TCM value.
-
-\begin{figure}[H]
-\label{fig-FeatureTCM}
-\begin{center}
-\textcolor{red}{PLOT OF TCM FEATURES HERE}
-\end{center}
-\caption{Temporal center-of-mass visualized in feature-space}
-\end{figure}
-
-% ================================
-
-\subsubsection{Auto Correlation Coefficients}
-
-\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution .
-We can compute any number of ACC's and their value changed depending on the index chosen.
-It is common to only compute the first $K$ ACC's \cite{Virtanen}.
-For a full waveform signal $s$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
-\begin{equation}
-\label{eqn-FeatureACC}
-\text{ACC}_k\big[ s \big] = 
-\frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]} {\sqrt{\sum_{i=0}^{M-k-1}s^2[i]} \sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
-\end{equation}
-
-\begin{figure}[H]
-\label{fig-FeatureACC}
-\begin{center}
-\textcolor{red}{PLOT OF ACC FEATURES HERE}
-\end{center}
-\caption{First four auto correlation coefficients visualized in feature-space}
-\end{figure}
-
-% ================================================================
-
-\newpage
-
-\subsection{Frequency-Space Features}
-\label{subsec-frequency}
-
-\paragraph*{}The features described in this section are derived from the frequency-domain representations of each audio sample.
-Frequency space is represented by the transposed spectrogram matrix, $S^T$, described in sec.
-(\ref{subsec-spectrogram}).
-This is done to ensure that each  row is now an analysis frame, each column is a frequency bin.
-This gives a similar structure to the time-space analysis frames matrix, $A$, in eqn.
-(\ref{eqn-FrameMatrix}).
-For each feature, we detail the physical significance and provide a visualization in feature-space.
-
-\paragraph*{}From frequency space, we use the following $13$ features:
-\begin{itemize}
-\item[•] Mel Frequency Cepstral Coefficients ($\times 12$)
-\item[•] Frequency Center of Mass
-\end{itemize}
-
-% ================================
-
-\subsubsection{Mel Frequency Cepstral Coefficients}
-
-\paragraph*{}Mel Frequency Ceptstral Coefficients (MFCC's) are a very prolific feature used widly in audio classification tasks \cite{Liu,Virtanen,Zhang}.
-MFCC's are produced by converting a linear-frequency axis with units such as Hertz into units of Mels, which are design to account for the non-linear perception of frequency in humans.
-The Hertz to Mel and Mel to Hertz transforms are given \cite{Virtanen}:
-\begin{equation}
-\label{eqn-HztoMel}
-M_f[h] = 2595 \log_{10}\big(1+ \frac{h}{700}\big)
-\end{equation}
-\begin{equation}
-\label{eqn-MeltoHz}
-H_f[m] = 700 \big(10^{(\frac{m}{2595})}-1\big)
-\end{equation}
-Where $M_f$ is the frequency in units of Mels, given $[h]$, a frequency in Hertz, and $H_f$ is the frequency in Hertz given $[m]$ a frequency in Mels.
-
-\paragraph*{}Mel filters are produced by grouping frequency-space into $R$ overlapping bins called \textit{Mel Filter-banks}.
-In units of Mels, each filter bank, $R_i$ remains a constant width, but when shown in Hertz, the bins increase logarithmically.
-\begin{figure}[H]
-\label{fig-MelFilterBanks}
-\begin{center}
-\textcolor{red}{Figure of a few Mel Filter Banks goes here}
-\end{center}
-\caption{Mel Filter Banks shown in frequency space with units of Hertz}
-\end{figure}
-Each of the $R$ filters is created to be $N'$ samples long, and transformed back into units of Hertz.
-When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
-Thus, each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is a filter.
-We apply the Mel Filter banks to the spectrogram to create matrix $B$:
-\begin{equation}
-\label{eqn-FilterBanks}
-B = S^T M^T
-\end{equation}
-Matrix $B$ has shape $k' \times R$.
-
-\paragraph*{}Using $S^T$ ensure that each row of the matrix is an analysis frame in frequency space.
-Similarly, each column of the matrix $M$ is a appropriately scaled Mel filter-bank.
-This way, the matrix product in eqn.
-(\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
-Finally, we compute the average energy across all $k'$ frames.
-The resulting $R$ floating-point numbers are approximation of the signal's energy in those particular frequency bands.
-For this project, we have chosen to use $R = 12$ filter-banks, which are all used as features.
-
-\begin{figure}[H]
-\label{fig-FeatureMFCC}
-\begin{center}
-\textcolor{red}{PLOT OF MFCC FEATURES HERE}
-\end{center}
-\caption{Mel Frequency Ceptral Coefficients in feature-space}
-\end{figure}
-
-% ================================
-
-\subsubsection{Center of Mass}
-
-\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a strong representation of how overtones and energy is distributed in the signal's frequency domain.
-As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
-This encodes the FCM for a single analysis frame (in frequency-space) in the waveform.
-For an frequency-analysis frame, $s^{(i)}$, the FCM is given by:
-\begin{equation}
-\label{eqn-FeatureFCM}
-\text{TCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
-\end{equation}
-We compute the FCM for each of the $k'$ frames, and then average the results. We use the average FCM across $k'$ frames to compute the FCM feature:
-\begin{equation}
-TCM = \sum_{i=0}^{k'} \text{TCM}_{i}\big[ s^{(i)} \big]
-\end{equation}
-
-\paragraph*{}The average FCM gives a strong approximation of the instrument or signal source's range.
-For example, a flute or violin will have a considerably high FCM value, even in their lower registers.
-Similarly, basses or tubas will have considerably low FCM values.
-Given that the standard frequency range of some musical instruments is fixed, it is guaranteed that for any particular instrument, the FCM will consistently remain within certain bounds \cite{Olson,White}.
-
-\begin{figure}[H]
-\label{fig-FeatureFCM}
-\begin{center}
-\textcolor{red}{PLOT OF FCM FEATURES HERE}
-\end{center}
-\caption{Frequency center-of-mass visualized in feature-space}
-\end{figure}
-
-% ================================================================
-
-% ================================================================
-
 \section{Evaluating Performance}
@@
 \paragraph*{}The confusion matrix (also called a confusion table) is a very quick, often graphical model that can be used to show how a model performs over a subset of predictions.
-The general idea of this object is count the number of times class $A$ is predicted to be in class $B$, and vice-versa \cite{Geron}.
+The general idea of this object is count the number of times class $i$ is predicted to be in class $j$, and vice-versa \cite{Geron}.
 If we see that these classes are being repeatedly \textit{confused} in the model's prediction process, then we must modify the model or features to account for it.
 
-\paragraph*{}For a $k$-classes classifier, a confusion matrix will have shape $k \times k$.
-Each row represents the actual labeled class and each column represents a predicted class.
+\paragraph*{}For a $k$-classes classifier, a confusion matrix will have shape $k \times k$, and every element is a non-negative integer.
+Each row represents the "ground truth" or  labeled class, and each column represents a predicted class.
 Thus for a confusion matrix, $C$, we can say that:
-\begin{equation}
+\begin{quote}
 \label{eqn-ConfMat}
-C_{i,j} = 
-\text{Number of samples that belong to class $i$, and were predicted to be in class $j$}
-\end{equation} 
-Thus, $i = j$, represents a correct prediction, and $i \neq k$ indicates an incorrect prediction.
-A confusion matrix with a strong main diagonal indicates a model that consistently predicts correct labels \cite{Geron}.
+\begin{center}
+$C_{i,j} =$ Number of samples that \\ 
+belong to class $i$, and were predicted to be in class $j$
+\end{center}
+
+\end{quote}
+Thus, indexes where $i = j$ represents a correct prediction, and $i \neq k$ indicates an incorrect prediction.
+A confusion matrix with relatively large values in main diagonal indicates a model that consistently predicts correct labels \cite{Geron}.
 
@@
 \label{fig-ConfMat}
+	\begin{subfigure}[h]{0.45\textwidth}
 	\begin{center}
@@
 	\end{center}
+	\end{subfigure}
+	\begin{subfigure}[h]{0.45\textwidth}
+	\begin{center}
+	\textcolor{red}{Images of Confusion Matrices Go Here!} 
+	\end{center}
+	\end{subfigure}
+	\begin{subfigure}[h]{0.45\textwidth}
+	\begin{center}
+	\textcolor{red}{Images of Confusion Matrices Go Here!} 
+	\end{center}
+	\end{subfigure}
+	\begin{subfigure}[h]{0.45\textwidth}
+	\begin{center}
+	\textcolor{red}{Images of Confusion Matrices Go Here!} 
+	\end{center}
+	\end{subfigure}
 \caption{Example Confusion Matrices for $k$-classes tasks}
@@
 
-\paragraph*{}We can also use a confusion matrix to define four useful quantities relating a prediction to it's label. Suppose a prediction, $y^* = p$ and a truth, $y = q$.
+\paragraph*{}We can also use a confusion matrix to define four useful quantities relating a prediction to it's label.
+Suppose a belongs to class $q$, with the prediction given by, $y^*$ and a label is given by, $y$:
 \begin{enumerate}
 \item \textbf{True-Positive}\\
-A sample is a true-positive if $p = q$
+A sample is \textit{TP} if $y^* = q$ and $y = q$
 \item \textbf{True-Negative}\\
-
+A sample is \textit{TN} if $y^* \neq q$ and $y \neq q$ 
 \item \textbf{False-Positive}\\
-
+A sample is \textit{FP} if $y^* = q$ and $y \neq q$ 
 \item \textbf{False-Negative}\\
+A sample is \textit{FN} if $y^* \neq q$ and $y = q$
 \end{enumerate}
-\textcolor{red}{finish this!}
+\textcolor{red}{Check this!}
 
@@
 % ================================
+
+\
+
+% ================================================================
+
+\subsection{Tracking Metrics over a Period of Training}
+\label{subsec-TrainingMetrics}
+
+% ================================================================
 
@@
 \item[•]Dr. Maurik Holtrop for various consultation and guidence throughout this project
+
+\item[•]University of Iowa, Electronic Music Studio for a digital sound library ued for training samples
+
+\item[•]Philharmonics Symphony Orchestra for a digital sound library used for training samples
 

### 2020-10-02 SignalClassifier/ClassifierMain/ClassifierMAIN.py
Rerunning Chaotic Synth training

@@ -57,6 +57,9 @@ if __name__ == '__main__':
     del(ProgramSetup)
     ProgramMode.__Call__(NeuralNetwork)      
 
+    dt_obj = sys_utils.datetime.datetime.now()
+    endtime = dt_obj.isoformat(sep='.',timespec='auto').replace(':','.').replace('-','.')
+    print("Time Stamp:",endtime)
     print("=)")
     
 

### 2020-10-02 SignalClassifier/ClassifierMain/ModeUtilities.py

@@ -158,9 +158,11 @@ class TrainMode (ProgramMode):
             X1 = matrixSXX.__Get_X__()
             X2 = matrixMLP.__Get_X__()
             Y = matrixSXX.__Get_Y__()
+
             modelHistory = Networks.MODEL.fit(x=[X1,X2],y=Y,
                                batch_size=32,epochs=self.n_epochs,verbose=1) 
             self.ExportHistory(modelHistory)
+
             del(matrixSXX,matrixMLP)    # delete Design Matrix Objs
             del(X1,X2,Y)                # delete Design Matrices
             self.groupCounter += 1      # incr coutner

### 2020-10-02 SignalClassifier/ClassifierMain/NeuralNetworkUtilities.py

@@ -22,7 +22,7 @@ NeuralNetworkModels.py - "Neural Network Models"
             #### VARIABLE DECLARATIONS ####
 
 inputShapeMLP = (20,)
-inputShapeCNN = (560,256,1)
+inputShapeCNN = (558,256,1)
 
             #### NEURAL NETWORK OBJECTS ####
 

### 2020-10-02 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis draft 0
- Cleaned up "Feature Selection" / "Spectrogram" Subsection

@@
 
-\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" \cite{Virtanen}:
+\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" about specifically how features must be chosen \cite{Virtanen}:
 \begin{quote}
@@
 In constructing a neural network classifier, the development of appropriate features is of the utmost importance.
-To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency space representation of the waveform.
-It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely on these features.
+To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency-space representation of the waveform.
+It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely solely these features.
 
 \paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}.
-In the training process, this object, along with the appropriate classification label, $y$ is presented to the neural network for processing.
+In the training process this object, along with the appropriate classification label, $y$ is presented to the neural network for processing.
 This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu}
@@
 \label{eqn-X1Shape}
-X_1 \in \mathbb{R}^{(b \times N' \times k' \times 1)}
+X_1 \in \mathbb{R}^{(b \times N' \times k \times 1)}
 \end{equation}
@@
 \label{eqn-X2Shape}
-X_2 \in \mathbb{R}^{(b \times p)}
-\end{equation}
-Where $N' \times k' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
-(\ref{subsec-spectrogram}), The first axis, with length $b$ indicates that there are $b$ samples stored in that design matrix.
-Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec.
-(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).
-A row of $X_2$ has shape $1 \times p$ where there are $p$ features within the \textit{feature-vector} for each sample.
+X_2 \in \mathbb{R}^{(b \times P)}
+\end{equation}
+Where $Q' \times R' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
+(\ref{subsec-spectrogram}).
+Similarly, $P$ is the number of features derived from the time and frequency-representation of features outlined in sec.
+(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ samples stored in that design matrix.
+A row of $X_2$ has shape $1 \times P$ where there are $P$ features within the \textit{feature-vector} for each sample.
 Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.
@@
 \paragraph*{}The field of neural classification is well studied in the application of image-processing.
-Many large-scale, and even introductory neural network projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
+Many large-scale, and even introductory projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
 As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior.
@@
 
-\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both space and time.
+\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time.
 In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis.
@@
 For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
-At a sample rate of $f_s = 44100$ samples/second, each frame represents a slice of time that is about $0.1$ seconds long.
+We also choose to use exactly $k = 256$ frames.
+Waveforms that are too short are padded with zeros, and waveforms that are too long are truncated.
+The audio has been sampled at $f_s = 44100$ samples/second, so ach frame represents a slice of time that is about $0.1$ seconds long.
 
@@
 \paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
-A standard \textit{Hann Window} of $N$ samples is generated and reshaped into a $N \times 1$ column-array, $H$.
+A standard \textit{Hann Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$.
 The $n$-th index in a Hann window with $N$ samples is defined:
@@
 \end{equation}
-The window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
+This window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
 Result is an $k \times N$ array, $\widetilde{A}$:
@@
 \end{equation}
+The window function allows for a cleaner transform into frequency space \cite{Virtanen}.
 
@@
 The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
+\begin{equation}
+\label{eqn-DFT}
+\text{DFT}\big[ \widetilde{A} \big] = \mathbb{W}\widetilde{A}^T
+\end{equation}
 
@@
 \paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames.
-Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins.
-Since human hearing extends from $20$ Hz to $20$ kHz, audio files such as music and voice recordings are typically sampled around $44.1$ kHz, to ensure that the full range of audio is held by the recording \cite{Olson,Virtanen}.
-
-\paragraph*{}However, standard musical instruments seldom extend above $8$ kHz \cite{Olson,Virtanen,White}.
+Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$.
+
+\paragraph*{}Standard western musical instruments seldom extend above $6$ kHz \cite{Olson,Virtanen,White}.
 This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
-As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $8000$ Hz.
+As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $6000$ Hz.
 This makes the input array smaller, and eliminates redundant and non-useful information.
 The number rows in the $S$ matrix is reduced from $N$ down to $N'$.
-Since each raw audio file may contain a different number of samples to begin with, a different number of analysis frames are created.
-To ensure all samples are a homogeneous size, we assert that each matrix must have exactly $k'$ columns.
-If $k' < k$, columns of zeros are added to pad the input, and if $k' > k$, columns are removed.
-
-\paragraph*{}Each spectrogram is now $N' \times k' \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform a a function of both time and frequency.
+
+\paragraph*{}Each spectrogram is now $N' \times k \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform as a function of both time and frequency.
 The spectrogram is the first feature used in this model.
-For this classifier, we have chosen $N' = 560$ and $k' = 256$.
+For this classifier, we have chosen $N' = 558$ and $k = 256$.
 For training, a batch of $b$ samples are concatenated into a single array object.
 \textcolor{blue}{See Neural Network section for more details}.
-For a batch of $b$ samples of $N' \times k' \times 1$ spectrograms, we shape $X_1$ such that:
+For a batch of $b$ samples of $N' \times k \times 1$ spectrograms, we shape $X_1$ such that:
 \begin{equation}
 \label{eqn-X1 shape}
-X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k' \times 1)}
+X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k \times 1)}
 \end{equation}

### 2020-10-03 SignalClassifier/ClassifierMain/ClassifierMAIN.py
Ran Predictions of Chaotic Synth 10/3

@@ -19,14 +19,14 @@ import NeuralNetworkUtilities as NN_utils
 if __name__ == '__main__':
        
     parent = 'C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\SignalClassifier'
-    read = os.path.join(parent,'Target-Data')
-    #read = os.path.join(parent,'ChaoticSynth-Data')
+    #read = os.path.join(parent,'Target-Data')
+    read = os.path.join(parent,'ChaoticSynth-Data')
     model = os.path.join(parent,'Model-Data')
     export = os.path.join(parent,'Output-Data')
     modelName = "ChaoticSynthClassifier"
 
     # PRE-PROCESSING FOR PROGRAM
-    ProgramSetup = sys_utils.ProgramInitializer([read,model,export],"train-predict",modelName,True)    
+    ProgramSetup = sys_utils.ProgramInitializer([read,model,export],"predict",modelName,False)    
     FILEOBJECTS = ProgramSetup.__Call__()
     (dataPath,exportPath,modelPath) = ProgramSetup.GetLocalPaths
     (modelName,newModel,N_classes,timeStart) = ProgramSetup.GetModelParams

### 2020-10-03 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Written Thesis

@@
 
+\paragraph*{}In secs.
+(\ref{subsec-NerualNetworkIntro}) and (\ref{subsec-NetworkStructure}), we introduce the nature and structure of a neural network and how it can use used in part to solve this problem.
+We show it's mathematical function analogue and how
+
 % ================================================================
@@
 \newpage
-\section{Feature Selections}
-\label{sec-Features}
-
-\paragraph*{}Audio and Machine learning researchers M.
-Kashif Saeed Khan and Wasfi G.
-Al-Khatib discuss the vitality of feature selection \cite{Khan}: \textcolor{red}{I'm not sure how to introduce the importance of feature extraction}
-\begin{quote}
-The data reduction stage which is also called feature extraction, consists of discovering a few important facts about each class.
-The choice of features is critical as it greatly affects the accuracy of audio classification.
-\end{quote}
-In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}.
-It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier.
-Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels.
-The inappropriate choice features does not reflect the significant characteristics of the signal.
-
-\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" about specifically how features must be chosen \cite{Virtanen}:
-\begin{quote}
-For recognition algorithms, the necessary property of the acoustic features is low variability among features extracted from examples assigned to the same class, and at the same time high variability allowing distinction between features extracted from examples assigned to different classes.
-\end{quote}
-In constructing a neural network classifier, the development of appropriate features is of the utmost importance.
-To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency-space representation of the waveform.
-It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely solely these features.
-
-\paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}.
-In the training process this object, along with the appropriate classification label, $y$ is presented to the neural network for processing.
-This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu}
-
-\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector.
-These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics.
-In the following sections, we outline the set of $21$ features used in the classification process
-
-\newpage
-
-% ================================
-
-\subsubsection{The Design Matrix}
-
-\paragraph*{}The $21$ features are from each file are organized into one of two array structures.
-each called a \textit{design matrix}.
-A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest.
-For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.
-each has shape given by:
-\begin{equation}
-\label{eqn-X1Shape}
-X_1 \in \mathbb{R}^{(b \times N' \times k \times 1)}
-\end{equation}
-\begin{equation}
-\label{eqn-X2Shape}
-X_2 \in \mathbb{R}^{(b \times P)}
-\end{equation}
-Where $Q' \times R' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
-(\ref{subsec-spectrogram}).
-Similarly, $P$ is the number of features derived from the time and frequency-representation of features outlined in sec.
-(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ samples stored in that design matrix.
-A row of $X_2$ has shape $1 \times P$ where there are $P$ features within the \textit{feature-vector} for each sample.
-Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.
-
-% ================================
-
-\subsubsection{Audio Preprocessing}
-\label{subsubsec-Preprocessing}
-
-\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}.
-In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
-\begin{enumerate}
-\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
-\item Audio encoded in a standard, and consistent format
-\item A consistent sample rate and bit depth between audio files
-\item A consistent number of channels
-\end{enumerate}
-Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
-\begin{enumerate}
-\item Roughly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
-\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
-\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
-\item All audio has been down-mixed into mono-channel waveforms.
-\end{enumerate}
-
-% ================================================================
-
-\newpage
-
-\subsection{Spectrogram Feature}
-\label{subsec-spectrogram}
-
-\paragraph*{}The field of neural classification is well studied in the application of image-processing.
-Many large-scale, and even introductory projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
-As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior.
-Following this success, it make senses to provide an image-like representation of a sound wave as a feature.
-We do this in the form of a spectrogram matrix.
-
-\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time.
-In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis.
-Thus each point in the 2-Dimensional space is an energy at a given time and frequency.
-Examples spectrograms from the wave form data set are shown in Fig.
-(\ref{fig-spectrograms}).
-
-\begin{figure}[H]
-\begin{center}
-\label{fig-spectrograms}
-\textcolor{red}{Insert spectrograms here}
-\caption{Spectrogram representations of various waveforms}
-\end{center}
-\end{figure}
-
-\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification.
-Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame.
-Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhang,Kahn,Virtanen}.
-For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
-We also choose to use exactly $k = 256$ frames.
-Waveforms that are too short are padded with zeros, and waveforms that are too long are truncated.
-The audio has been sampled at $f_s = 44100$ samples/second, so ach frame represents a slice of time that is about $0.1$ seconds long.
-
-\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
-\begin{equation}
-\label{eqn-FrameMatrix}
-A = \big\{ a_{0} , a_{1} , a_{2} , ... , a_{k-1} \big\} = 
-\begin{bmatrix}
-a_{0}[0] & a_{0}[1] & a_{0}[2] & \hdots & a_{0}[N-1] \\
-a_{1}[0] & a_{1}[1] & a_{1}[2] & \hdots & a_{1}[N-1] \\
-a_{2}[0] & a_{2}[1] & a_{2}[2] & \hdots & a_{2}[N-1] \\
-\vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
-a_{k-1}[0] & a_{k-1}[1] & a_{k-1}[2] & \hdots & a_{k-1}[N-1] \\
-\end{bmatrix}
-\end{equation}
-We use bracket notation, $[j]$ to indicate that each analysis frame $a_i$ is array-like. Many programming languages could also use the following indexing conventions for matrix $A$:
-\begin{equation}
-\label{eqn-IndexingA}
-A_{i,j} = A_i[j] = A[i][j] = A[i,j]
-\end{equation}
-These all represent equivalent entries.
-
-\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
-A standard \textit{Hann Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$.
-The $n$-th index in a Hann window with $N$ samples is defined:
-\begin{equation}
-\label{eqn-Hann}
-H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
-\end{equation}
-This window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
-Result is an $k \times N$ array, $\widetilde{A}$:
-\begin{equation}
-\label{eqn-WindowMatrix}
-\widetilde{A_i} = A_i \odot H
-\end{equation}
-The window function allows for a cleaner transform into frequency space \cite{Virtanen}.
-
-\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross}.
-The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
-Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space containing $N$ samples
-\begin{equation}
-\label{eqn-DFTMatrix}
-\mathbb{W} = \frac{1}{\sqrt{N}}
-\begin{bmatrix}
-1 & 1 & 1 & 1 & \hdots & 1 \\
-1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
-1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
-1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
-\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
-1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
-\end{bmatrix}
-\end{equation}
-Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $\widetilde{A}^T$.
-The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
-\begin{equation}
-\label{eqn-DFT}
-\text{DFT}\big[ \widetilde{A} \big] = \mathbb{W}\widetilde{A}^T
-\end{equation}
-
-\paragraph*{}Most standard implementations of neural network models require all activations, weights, and biases to be real floating-point numbers.
-Since the the DFT matrix introduces complex values, we compute the square of the element-wise $L2$-norm of the resultant array.
-\begin{equation}
-\label{eqn-Spectrogram}
-S_{i,j} = \big{\lVert} (\mathbb{W}\widetilde{A}^T)_{i,j} \big{\rVert}_{2}^{2}
-\end{equation}
-Where $\mathbb{W}$ is the DFT matrix from eqn.
-(\ref{eqn-DFTMatrix}) and $\widetilde{A}^T$ is the transpose of the analysis frames matrix from eqn.
-(\ref{eqn-WindowMatrix}).
-The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of real floating-point numbers.
-We can index matrix $S$ similarly to that of matrix $A$ in eqn.
-(\ref{eqn-IndexingA}):
-\begin{equation}
-\label{eqn-IndexingS}
-S_{i,j} = S[i][j] = S[i,j]
-\end{equation}
-
-\paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames.
-Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$.
-
-\paragraph*{}Standard western musical instruments seldom extend above $6$ kHz \cite{Olson,Virtanen,White}.
-This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
-As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $6000$ Hz.
-This makes the input array smaller, and eliminates redundant and non-useful information.
-The number rows in the $S$ matrix is reduced from $N$ down to $N'$.
-
-\paragraph*{}Each spectrogram is now $N' \times k \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform as a function of both time and frequency.
-The spectrogram is the first feature used in this model.
-For this classifier, we have chosen $N' = 558$ and $k = 256$.
-For training, a batch of $b$ samples are concatenated into a single array object.
-\textcolor{blue}{See Neural Network section for more details}.
-For a batch of $b$ samples of $N' \times k \times 1$ spectrograms, we shape $X_1$ such that:
-\begin{equation}
-\label{eqn-X1 shape}
-X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k \times 1)}
-\end{equation}
-Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}).
-This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
-\textcolor{blue}{See Neural Network section for more details}
-
-% ================================================================
-
-\newpage
-
-\subsection{Time-Space Features}
-\label{subsec-time}
-
-\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. Time space can be represented in one of three ways: 
-\begin{itemize}
-\item The raw waveform $s$\\
-Indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
-\item A single analysis frame $a_i$ \\
-Indexed by $a_i[j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
-\item The full analysis frame matrix $A$ \\
-Indexed by $A[i][j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
-\end{itemize}
-
-\paragraph*{}From time space, we use the following $7$ features:
-\begin{itemize}
-\item[•] Time Domain Envelope
-\item[•] Zero Crossing Rate
-\item[•] Temporal Center of Mass
-\item[•] Auto Correlation Coefficients ($\times 4$)
-\end{itemize}
-
-% ================================
-
-\subsubsection{Time Domain Envelope}
-
-\paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal Often, we compute the RMS-Energy of each frame - a larger energy of the frame, the larger the average amplitude of the waveform in that frame.
-For frames with smaller amplitude, we can assume that the signal has either not begun, or is decaying.
-
-\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olson,Virtanen}
-\begin{equation}
-\label{eqn-RMS}
-\text{RMS}\big[ s \big] = \sqrt{\frac{1}{N} \sum_{i=0}^{N-1} s[i]^2}
-\end{equation}
-By using the full waveform, we acquire a rough estimate for the energy in the entirety of the audio file \cite{Liu}.
-For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large waveform RMS when compared to those instruments without sustain such as plucked stings or dampened percussion
-
-\begin{figure}[H]
-\label{fig-FeatureTDE}
-\begin{center}
-\textcolor{red}{PLOT OF TDE FEATURES HERE}
-\end{center}
-\caption{Time domain envelope visualized in feature-space}
-\end{figure}
-
-% ================================
-
-\subsubsection{Zero Crossing Rate}
-
-\paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses it's equilibrium point.
-This can be done per total sound wave, per unit time, or per analysis-frame.
-This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform.
-In some cases, the ZXR can be correlated to frequency as well \cite{Kahn,Zhang}.
-
-\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}. The ZXR for the full waveform $s$ is given by \cite{Virtanen,Liu}
-\begin{equation}
-\label{eqn-ZXR}
-\text{ZXR}\big[ s \big] = \frac{1}{2} \sum_{i=1}^{M-1} \big{|} \sign(s[i]) - \sign(s[i-1]) \big{|} 
-\end{equation}
-Where $\sign(x)$ returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$.
-This provides a rough estimate for the average frequency in the full waveform, and can help discern clean periodic signals (low ZXR) from those that may have more noise or volatile behavior (high ZXR)\cite{Virtanen}.
-
-\begin{figure}[H]
-\label{fig-FeatureZXR}
-\begin{center}
-\textcolor{red}{PLOT OF ZXR FEATURES HERE}
-\end{center}
-\caption{Zero crossing rate visualized in feature-space}
-\end{figure}
-
-% ================================
-
-\subsubsection{Center of Mass}
-
-\paragraph*{}The temporal center of mass (TCM) of a signal is used to compute roughly where in time the amplitude of the waveform \textit{bunches up}.
-We treat the full waveform array, $s$, with $M$ samples as a 1-Dimensional discrete mass distribution.
-The TCM of that waveform is then given:
-\begin{equation}
-\label{eqn-FeatureTCM}
-\text{TCM}\big[ s \big] = \frac{\sum_{i=0}^{M-1}i s[i]}{\sum_{i=0}^{M-1}s[i]}
-\end{equation}
-This includes negative amplitude values acting as "negative masses".
-
-\paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance.
-For instruments with heavier attacks, we expect the TCM to be a very near the start of the waveform.
-For instruments with long sustain times, we expect a very centrally located center of mass, and for instruments with long release times, we expect a later TCM value.
-
-\begin{figure}[H]
-\label{fig-FeatureTCM}
-\begin{center}
-\textcolor{red}{PLOT OF TCM FEATURES HERE}
-\end{center}
-\caption{Temporal center-of-mass visualized in feature-space}
-\end{figure}
-
-% ================================
-
-\subsubsection{Auto Correlation Coefficients}
-
-\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution .
-We can compute any number of ACC's and their value changed depending on the index chosen.
-It is common to only compute the first $K$ ACC's \cite{Virtanen}.
-For a full waveform signal $s$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
-\begin{equation}
-\label{eqn-FeatureACC}
-\text{ACC}_k\big[ s \big] = 
-\frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]} {\sqrt{\sum_{i=0}^{M-k-1}s^2[i]} \sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
-\end{equation}
-
-\begin{figure}[H]
-\label{fig-FeatureACC}
-\begin{center}
-\textcolor{red}{PLOT OF ACC FEATURES HERE}
-\end{center}
-\caption{First four auto correlation coefficients visualized in feature-space}
-\end{figure}
-
-% ================================================================
-
-\newpage
-
-\subsection{Frequency-Space Features}
-\label{subsec-frequency}
-
-\paragraph*{}The features described in this section are derived from the frequency-domain representations of each audio sample.
-Frequency space is represented by the transposed spectrogram matrix, $S^T$, described in sec.
-(\ref{subsec-spectrogram}).
-This is done to ensure that each  row is now an analysis frame, each column is a frequency bin.
-This gives a similar structure to the time-space analysis frames matrix, $A$, in eqn.
-(\ref{eqn-FrameMatrix}).
-For each feature, we detail the physical significance and provide a visualization in feature-space.
-
-\paragraph*{}From frequency space, we use the following $13$ features:
-\begin{itemize}
-\item[•] Mel Frequency Cepstral Coefficients ($\times 12$)
-\item[•] Frequency Center of Mass
-\end{itemize}
-
-% ================================
-
-\subsubsection{Mel Frequency Cepstral Coefficients}
-
-\paragraph*{}Mel Frequency Ceptstral Coefficients (MFCC's) are a very prolific feature used widly in audio classification tasks \cite{Liu,Virtanen,Zhang}.
-MFCC's are produced by converting a linear-frequency axis with units such as Hertz into units of Mels, which are design to account for the non-linear perception of frequency in humans.
-The Hertz to Mel and Mel to Hertz transforms are given \cite{Virtanen}:
-\begin{equation}
-\label{eqn-HztoMel}
-M_f[h] = 2595 \log_{10}\big(1+ \frac{h}{700}\big)
-\end{equation}
-\begin{equation}
-\label{eqn-MeltoHz}
-H_f[m] = 700 \big(10^{(\frac{m}{2595})}-1\big)
-\end{equation}
-Where $M_f$ is the frequency in units of Mels, given $[h]$, a frequency in Hertz, and $H_f$ is the frequency in Hertz given $[m]$ a frequency in Mels.
-
-\paragraph*{}Mel filters are produced by grouping frequency-space into $R$ overlapping bins called \textit{Mel Filter-banks}.
-In units of Mels, each filter bank, $R_i$ remains a constant width, but when shown in Hertz, the bins increase logarithmically.
-\begin{figure}[H]
-\label{fig-MelFilterBanks}
-\begin{center}
-\textcolor{red}{Figure of a few Mel Filter Banks goes here}
-\end{center}
-\caption{Mel Filter Banks shown in frequency space with units of Hertz}
-\end{figure}
-Each of the $R$ filters is created to be $N'$ samples long, and transformed back into units of Hertz.
-When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
-Thus, each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is a filter.
-We apply the Mel Filter banks to the spectrogram to create matrix $B$:
-\begin{equation}
-\label{eqn-FilterBanks}
-B = S^T M^T
-\end{equation}
-Matrix $B$ has shape $k' \times R$.
-
-\paragraph*{}Using $S^T$ ensure that each row of the matrix is an analysis frame in frequency space.
-Similarly, each column of the matrix $M$ is a appropriately scaled Mel filter-bank.
-This way, the matrix product in eqn.
-(\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
-Finally, we compute the average energy across all $k'$ frames.
-The resulting $R$ floating-point numbers are approximation of the signal's energy in those particular frequency bands.
-For this project, we have chosen to use $R = 12$ filter-banks, which are all used as features.
-
-\begin{figure}[H]
-\label{fig-FeatureMFCC}
-\begin{center}
-\textcolor{red}{PLOT OF MFCC FEATURES HERE}
-\end{center}
-\caption{Mel Frequency Ceptral Coefficients in feature-space}
-\end{figure}
-
-% ================================
-
-\subsubsection{Center of Mass}
-
-\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a strong representation of how overtones and energy is distributed in the signal's frequency domain.
-As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
-This encodes the FCM for a single analysis frame (in frequency-space) in the waveform.
-For an frequency-analysis frame, $s^{(i)}$, the FCM is given by:
-\begin{equation}
-\label{eqn-FeatureFCM}
-\text{TCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
-\end{equation}
-We compute the FCM for each of the $k'$ frames, and then average the results. We use the average FCM across $k'$ frames to compute the FCM feature:
-\begin{equation}
-TCM = \sum_{i=0}^{k'} \text{TCM}_{i}\big[ s^{(i)} \big]
-\end{equation}
-
-\paragraph*{}The average FCM gives a strong approximation of the instrument or signal source's range.
-For example, a flute or violin will have a considerably high FCM value, even in their lower registers.
-Similarly, basses or tubas will have considerably low FCM values.
-Given that the standard frequency range of some musical instruments is fixed, it is guaranteed that for any particular instrument, the FCM will consistently remain within certain bounds \cite{Olson,White}.
-
-\begin{figure}[H]
-\label{fig-FeatureFCM}
-\begin{center}
-\textcolor{red}{PLOT OF FCM FEATURES HERE}
-\end{center}
-\caption{Frequency center-of-mass visualized in feature-space}
-\end{figure}
-
-% ================================================================
-% ================================================================
-
-\newpage
 \section{The Neural Network}
@@
 \subsection{The Structure of a Neural Network}
-\label{subsec-NetworkStructre}
+\label{subsec-NetworkStructure}
 
@@
 \REQUIRE Network with $L$ layers - $0,1,2,....,L-2,L-1$
-\REQUIRE Set of layer functions $f^{(l)}, l \in 0,1,2,....,L-2,L-1$ made up of 
+\REQUIRE Set of layer functions $f^{(l)}, l \in 0,1,2,....,L-2,L-1$ made up of a linear transformation and a non-linear transformation.
 \REQUIRE Input sample - $x^{(0)}$
 
+If training the network, the intermediate layer activations must be stored for back-propagation. Otherwise, they must be discarded.
 $Z = \{\} \leftarrow$ array to hold pre-activations \\
@@
 \FOR {$l = 1,2,...,L-2,L-1$}	
-
-	\item Break layer function into two linear transformation and non-linear activation
-
-	\item Store values for later use in optimizer
+	\item Evaluate Linear Transformation
+	\item $z^{(l)} \leftarrow$ 
+	\item Apply non-linear Activation Function
+	\item $x^{(l)} \leftarrow \sigma^{(l)} \big[ z^{(l)} \big]$ 
+	\item Store values for later use in optimizer, otherwise can be discarded.
 	\item $Z \leftarrow Z.add(z^{(l)})$
@@
 As shown in eqn.
-(\ref{eqn-altLayerFunction}), each function feeds directly into the next as to form a sort of computational graph \cite{Goodfellow}.
+(\ref{eqn-altLayerFunction}), each function feeds directly into the next as to form a sort of recursive computational graph \cite{Goodfellow}.
 
@@
 This activation function typically is a non-linear function which allows for the modeling of increasingly complex decision-boundaries.
-Step (i.) is usually in the form of a matrix-vector equation:
+The Linear transformation can be given by eqn (\ref{eqn-LinearTransform}) in the case of a 1D Dense layer (\ref{subsubsec-DenseLayer}) or eqn.
+(\ref{eqn-LinearTransform2}) in the case of a 2D Convolution layer.
 \begin{equation}
@@
 \end{equation}
-Where $W^{(l)}$ is the \textit{weighting-matrix} for layer $l$, $b^{(l)}$ is the \textit{bias-vector} for layer $l$, $z^{(l)}$ are the \textit{linear-activations} for layer $l$ and $x^{(l-1)}$ is the final activations for layer $l-1$.
-Step (ii.) is usually given by some \textit{activation function}:
+\begin{equation}
+\label{eqn-LinearTransform2}
+z^{(l)} = \big(W^{(l)} * x^{(l-1)}\big) + b^{(l)}
+\end{equation} 
+Where $W^{(l)} x^{(l-1)}$ denotes a matrix-vector product, and $\big(W^{(l)} * x^{(l-1)}\big)$ denotes a convolution product.
+In both cases, $W^{(l)}$ is the \textit{weighting-matrix} or \textit{weighting-kernel} for layer $l$, $b^{(l)}$ is the \textit{bias-vector} for layer $l$, $z^{(l)}$ are the \textit{linear-activations} for layer $l$ and $x^{(l-1)}$ is the final activations for layer $l-1$.
+
+\paragraph*{}Step (ii.) is usually given by some \textit{activation function}:
 \begin{equation}
@@
 The step size in each of the 2-dimension is known as the \textit{stride}.
-Each of the $K$ filters is used to generate a $m \times n$ feature map from the input activation.
+Each of the $K$ filters are used to generate a $m \times n$ feature map from the input activation.
 For an appropriately trained network, some filters may be dedicated to detecting vertical lines, horizontal lines, sharp edges, areas of mostly one color, etc.
-\cite{Loy,Geron}.
+\cite{Geron,Loy}.
 
@@
 \paragraph*{}The convolution layers allows for several advantages.
-Among these are (i) \textit{sparse-connectivity}: not every single activation (pixel) is connect to every single output pixel, so it is more computationally efficient, (ii) \textit{positional invariance}: key features can be identified regardless of where they are in the layer
+Among these are (i) \textit{sparse-connectivity}: not every single activation (pixel) is connect to every single output pixel, so it is more computationally efficient, (ii) \textit{positional invariance}: key features can be identified regardless of where they are in the layer, and (iii.) \textit{Automatic feature detection} as the training process will update the filters to identify dominant features in the data without human instruction \cite{Geron,Goodfellow,Loy}.
 
@@
 \paragraph*{}A Maximum Pooling layers simply returns the maximum neuron activation in a group of neurons.
-In the case of 2D Max Pooling, we choose a kernel size to be $m \times n$, just like in the 2D Convolution layer, and extract the maximum value in each window, and then step along accrdoing to the chosen stride size \cite{Loy,Goodfellow}.As an example, consider again figure (\ref{fig-2DConvExample}).
+In the case of 2D Max Pooling, we choose a kernel size to be $m \times n$, just like in the 2D Convolution layer, and extract the maximum value in each window, and then step along accrdoing to the chosen stride size \cite{Loy,Goodfellow}.As an example, consider again figure (\ref{fig-2DConvExample}a).
 Using the $2 \times 2$ kernel on the $3 \times 4$ input, each box would then contain the maximum value of the input activations.
@@
 
-\paragraph*{}The 1-Dimensional Concatenation Layer, also called 1D-Concat layer takes separate vectors of activations and combines them into a single 1D vector. Consider the layer activations
+\paragraph*{}The 1-Dimensional Concatenation Layer, also called 1D-Concat layer takes separate vectors of activations and combines them into a single 1D vector.
+Consider the layer activations $\vec{a}^{(l-1)}$ and $\vec{b}^{(l-1)}$ with shapes  $1 \times \alpha$ and $1 \times \beta$ respectively.
+They are the outputs of two different layers:
+\begin{equation}
+\vec{a}^{(l-1)} = \big[ a_{0},  a_{1}, ... ,  a_{\alpha-1} \big]
+\text{\hspace{1cm} and \hspace{1cm}}
+\vec{b}^{(l-1)} = \big[ b_{0},  b_{1}, ... ,  b_{\beta-1} \big]
+\end{equation}
+The result of the concatenation is a new 1D-array, $\vec{c}^{(l)}$ with size $1 \times \alpha\beta$:
+\begin{equation}
+\vec{c}^{(l)} = \big[ a_{0},  a_{1}, ... ,  a_{\alpha-1}, b_{0},  b_{1}, ... ,  b_{\beta-1} \big]
+\end{equation}
+
+\paragraph*{}We can denote this for $n$ arrays with function notation:
+\begin{equation}
+\label{eqn-ConcatenationFunction}
+f^{(l)} : x^{(l-1)}_{a} \in \mathbb{R}^{(1 \times \alpha)} , x^{(l-1)}_{b} \in \mathbb{R}^{(1 \times \beta)} , ....  \rightarrow
+x^{(l)}_{z} \in \mathbb{R}^{(1 \times \alpha\beta...)}
+\end{equation}
+The concatenation layer is used to combine activation non-adjacent, or non-related layers into a single new layer.
+In this case of the model used in the project, we use it to combine the activations that result from two distinct models into a single layer that is then transformed into a final output.
+This process is detailed further in sec.
+(\ref{sec-Architecture}).
 
@@
 \paragraph*{}The softmax activation function is commonly used in the output layer of a multi-class classification network, such as the one we implement.
-When softmax acts on a vector or activation, the result is a normalized,non-negative output vector.
-\cite{Geron,Goodfellow,Virtanen}.
+When softmax acts on a vector or activation, the result a non-negative output vector.
+with an $L_1$ norm of $1$ \cite{Geron,Goodfellow,Virtanen}.
 The $i$-th element in a softmax activation function is given by:
@@
 
-\paragraph*{}This function is only used in the output layer of a neural network, and encodes a discrete categorical probability.
+\paragraph*{}This function is almost only used in the output layer of a neural network, and encodes a discrete categorical probability.
 For example, if eqn.(\ref{eqn-Softmax}) returns a vector of the form: $[ 0.75 , 0.25]$, we interpret this as a sample having a $75\%$ chance of beloinging to class $0$ and a $25\%$ change of belonging to class $1$.
@@
 \REQUIRE Set of bias parameters - $b^{(i)}, i \in \{0,1,....,L-1\}$
-\REQUIRE Set of layer activation function - $a^{(i)}, i \in \{0,1,....,L-1\}$
-\REQUIRE Set of layer activation function derivatives - $\partial a^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of layer activation function - $\sigma^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Set of layer activation function derivatives - $\partial\sigma^{(i)}, i \in \{0,1,....,L-1\}$
 \REQUIRE Set of pre-nonlinear activation - $Z^{(i)}, i \in \{0,1,....,L-1\}$
@@
 	\item Compute gradient w.r.t pre-nonlinear activation portion of layer function
-	\item $dx^{(l)} \leftarrow \nabla_{Z^{(l)}}J = dx^{(l)} \odot \partial a^{(l)}[ Z^{(l)} ]$
+	\item $dx^{(l)} \leftarrow \nabla_{Z^{(l)}}J = dx^{(l)} \odot \partial\sigma^{(l)}[ Z^{(l)} ]$
 	\item Compute gradient w.r.t weighting and bias elements
@@
 This vector is then passed into the final dense layer, which used the softmax activation, and encodes the joint predictions based on both model branches.
+
+% ================================================================
+% ================================================================
+
+\newpage
+\section{Feature Selections}
+\label{sec-Features}
+
+\paragraph*{}Audio and Machine learning researchers M.
+Kashif Saeed Khan and Wasfi G.
+Al-Khatib discuss the vitality of feature selection \cite{Khan}: \textcolor{red}{I'm not sure how to introduce the importance of feature extraction}
+\begin{quote}
+The data reduction stage which is also called feature extraction, consists of discovering a few important facts about each class.
+The choice of features is critical as it greatly affects the accuracy of audio classification.
+\end{quote}
+In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}.
+It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier.
+Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels.
+The inappropriate choice features does not reflect the significant characteristics of the signal.
+
+\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" about specifically how features must be chosen \cite{Virtanen}:
+\begin{quote}
+For recognition algorithms, the necessary property of the acoustic features is low variability among features extracted from examples assigned to the same class, and at the same time high variability allowing distinction between features extracted from examples assigned to different classes.
+\end{quote}
+In constructing a neural network classifier, the development of appropriate features is of the utmost importance.
+To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency-space representation of the waveform.
+It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely solely these features.
+
+\paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}.
+In the training process this object, along with the appropriate classification label, $y$ is presented to the neural network for processing.
+This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu}
+
+\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector.
+These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics.
+In the following sections, we outline the set of $21$ features used in the classification process
+
+\newpage
+
+% ================================
+
+\subsubsection{The Design Matrix}
+
+\paragraph*{}The $21$ features are from each file are organized into one of two array structures.
+each called a \textit{design matrix}.
+A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest.
+For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.
+each has shape given by:
+\begin{equation}
+\label{eqn-X1Shape}
+X_1 \in \mathbb{R}^{(b \times N' \times k \times 1)}
+\end{equation}
+\begin{equation}
+\label{eqn-X2Shape}
+X_2 \in \mathbb{R}^{(b \times P)}
+\end{equation}
+Where $Q' \times R' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
+(\ref{subsec-spectrogram}).
+Similarly, $P$ is the number of features derived from the time and frequency-representation of features outlined in sec.
+(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ samples stored in that design matrix.
+A row of $X_2$ has shape $1 \times P$ where there are $P$ features within the \textit{feature-vector} for each sample.
+Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.
+
+% ================================
+
+\subsubsection{Audio Preprocessing}
+\label{subsubsec-Preprocessing}
+
+\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}.
+In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
+\begin{enumerate}
+\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
+\item Audio encoded in a standard, and consistent format
+\item A consistent sample rate and bit depth between audio files
+\item A consistent number of channels
+\end{enumerate}
+Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
+\begin{enumerate}
+\item Roughly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
+\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
+\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
+\item All audio has been down-mixed into mono-channel waveforms.
+\end{enumerate}
+
+% ================================================================
+
+\newpage
+
+\subsection{Spectrogram Feature}
+\label{subsec-spectrogram}
+
+\paragraph*{}The field of neural classification is well studied in the application of image-processing.
+Many large-scale, and even introductory projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
+As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior.
+Following this success, it make senses to provide an image-like representation of a sound wave as a feature.
+We do this in the form of a spectrogram matrix.
+
+\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time.
+In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis.
+Thus each point in the 2-Dimensional space is an energy at a given time and frequency.
+Examples spectrograms from the wave form data set are shown in Fig.
+(\ref{fig-spectrograms}).
+
+\begin{figure}[H]
+\begin{center}
+\label{fig-spectrograms}
+\textcolor{red}{Insert spectrograms here}
+\caption{Spectrogram representations of various waveforms}
+\end{center}
+\end{figure}
+
+\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification.
+Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame.
+Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhang,Kahn,Virtanen}.
+For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
+We also choose to use exactly $k = 256$ frames.
+Waveforms that are too short are padded with zeros, and waveforms that are too long are truncated.
+The audio has been sampled at $f_s = 44100$ samples/second, so ach frame represents a slice of time that is about $0.1$ seconds long.
+
+\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
+\begin{equation}
+\label{eqn-FrameMatrix}
+A = \big\{ a_{0} , a_{1} , a_{2} , ... , a_{k-1} \big\} = 
+\begin{bmatrix}
+a_{0}[0] & a_{0}[1] & a_{0}[2] & \hdots & a_{0}[N-1] \\
+a_{1}[0] & a_{1}[1] & a_{1}[2] & \hdots & a_{1}[N-1] \\
+a_{2}[0] & a_{2}[1] & a_{2}[2] & \hdots & a_{2}[N-1] \\
+\vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
+a_{k-1}[0] & a_{k-1}[1] & a_{k-1}[2] & \hdots & a_{k-1}[N-1] \\
+\end{bmatrix}
+\end{equation}
+We use bracket notation, $[j]$ to indicate that each analysis frame $a_i$ is array-like. Many programming languages could also use the following indexing conventions for matrix $A$:
+\begin{equation}
+\label{eqn-IndexingA}
+A_{i,j} = A_i[j] = A[i][j] = A[i,j]
+\end{equation}
+These all represent equivalent entries.
+
+\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
+A standard \textit{Hann Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$.
+The $n$-th index in a Hann window with $N$ samples is defined:
+\begin{equation}
+\label{eqn-Hann}
+H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
+\end{equation}
+This window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
+Result is an $k \times N$ array, $\widetilde{A}$:
+\begin{equation}
+\label{eqn-WindowMatrix}
+\widetilde{A_i} = A_i \odot H
+\end{equation}
+The window function allows for a cleaner transform into frequency space \cite{Virtanen}.
+
+\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross}.
+The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
+Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space containing $N$ samples
+\begin{equation}
+\label{eqn-DFTMatrix}
+\mathbb{W} = \frac{1}{\sqrt{N}}
+\begin{bmatrix}
+1 & 1 & 1 & 1 & \hdots & 1 \\
+1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
+1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
+1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
+\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
+1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
+\end{bmatrix}
+\end{equation}
+Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $\widetilde{A}^T$.
+The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
+\begin{equation}
+\label{eqn-DFT}
+\text{DFT}\big[ \widetilde{A} \big] = \mathbb{W}\widetilde{A}^T
+\end{equation}
+
+\paragraph*{}Most standard implementations of neural network models require all activations, weights, and biases to be real floating-point numbers.
+Since the the DFT matrix introduces complex values, we compute the square of the element-wise $L2$-norm of the resultant array.
+\begin{equation}
+\label{eqn-Spectrogram}
+S_{i,j} = \big{\lVert} (\mathbb{W}\widetilde{A}^T)_{i,j} \big{\rVert}_{2}^{2}
+\end{equation}
+Where $\mathbb{W}$ is the DFT matrix from eqn.
+(\ref{eqn-DFTMatrix}) and $\widetilde{A}^T$ is the transpose of the analysis frames matrix from eqn.
+(\ref{eqn-WindowMatrix}).
+The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of real floating-point numbers.
+We can index matrix $S$ similarly to that of matrix $A$ in eqn.
+(\ref{eqn-IndexingA}):
+\begin{equation}
+\label{eqn-IndexingS}
+S_{i,j} = S[i][j] = S[i,j]
+\end{equation}
+
+\paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames.
+Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$.
+
+\paragraph*{}Standard western musical instruments seldom extend above $6$ kHz \cite{Olson,Virtanen,White}.
+This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
+As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $6000$ Hz.
+This makes the input array smaller, and eliminates redundant and non-useful information.
+The number rows in the $S$ matrix is reduced from $N$ down to $N'$.
+
+\paragraph*{}Each spectrogram is now $N' \times k \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform as a function of both time and frequency.
+The spectrogram is the first feature used in this model.
+For this classifier, we have chosen $N' = 558$ and $k = 256$.
+For training, a batch of $b$ samples are concatenated into a single array object.
+\textcolor{blue}{See Neural Network section for more details}.
+For a batch of $b$ samples of $N' \times k \times 1$ spectrograms, we shape $X_1$ such that:
+\begin{equation}
+\label{eqn-X1 shape}
+X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k \times 1)}
+\end{equation}
+Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}).
+This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
+\textcolor{blue}{See Neural Network section for more details}
+
+% ================================================================
+
+\newpage
+
+\subsection{Time-Space Features}
+\label{subsec-time}
+
+\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. Time space can be represented in one of three ways: 
+\begin{itemize}
+\item The raw waveform $s$\\
+Indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
+\item A single analysis frame $a_i$ \\
+Indexed by $a_i[j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
+\item The full analysis frame matrix $A$ \\
+Indexed by $A[i][j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
+\end{itemize}
+
+\paragraph*{}From time space, we use the following $7$ features:
+\begin{itemize}
+\item[•] Time Domain Envelope
+\item[•] Zero Crossing Rate
+\item[•] Temporal Center of Mass
+\item[•] Auto Correlation Coefficients ($\times 4$)
+\end{itemize}
+
+% ================================
+
+\subsubsection{Time Domain Envelope}
+
+\paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal Often, we compute the RMS-Energy of each frame - a larger energy of the frame, the larger the average amplitude of the waveform in that frame.
+For frames with smaller amplitude, we can assume that the signal has either not begun, or is decaying.
+
+\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olson,Virtanen}
+\begin{equation}
+\label{eqn-RMS}
+\text{RMS}\big[ s \big] = \sqrt{\frac{1}{N} \sum_{i=0}^{N-1} s[i]^2}
+\end{equation}
+By using the full waveform, we acquire a rough estimate for the energy in the entirety of the audio file \cite{Liu}.
+For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large waveform RMS when compared to those instruments without sustain such as plucked stings or dampened percussion
+
+\begin{figure}[H]
+\label{fig-FeatureTDE}
+\begin{center}
+\textcolor{red}{PLOT OF TDE FEATURES HERE}
+\end{center}
+\caption{Time domain envelope visualized in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Zero Crossing Rate}
+
+\paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses it's equilibrium point.
+This can be done per total sound wave, per unit time, or per analysis-frame.
+This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform.
+In some cases, the ZXR can be correlated to frequency as well \cite{Kahn,Zhang}.
+
+\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}. The ZXR for the full waveform $s$ is given by \cite{Virtanen,Liu}
+\begin{equation}
+\label{eqn-ZXR}
+\text{ZXR}\big[ s \big] = \frac{1}{2} \sum_{i=1}^{M-1} \big{|} \sign(s[i]) - \sign(s[i-1]) \big{|} 
+\end{equation}
+Where $\sign(x)$ returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$.
+This provides a rough estimate for the average frequency in the full waveform, and can help discern clean periodic signals (low ZXR) from those that may have more noise or volatile behavior (high ZXR)\cite{Virtanen}.
+
+\begin{figure}[H]
+\label{fig-FeatureZXR}
+\begin{center}
+\textcolor{red}{PLOT OF ZXR FEATURES HERE}
+\end{center}
+\caption{Zero crossing rate visualized in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Center of Mass}
+
+\paragraph*{}The temporal center of mass (TCM) of a signal is used to compute roughly where in time the amplitude of the waveform \textit{bunches up}.
+We treat the full waveform array, $s$, with $M$ samples as a 1-Dimensional discrete mass distribution.
+The TCM of that waveform is then given:
+\begin{equation}
+\label{eqn-FeatureTCM}
+\text{TCM}\big[ s \big] = \frac{\sum_{i=0}^{M-1}i s[i]}{\sum_{i=0}^{M-1}s[i]}
+\end{equation}
+This includes negative amplitude values acting as "negative masses".
+
+\paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance.
+For instruments with heavier attacks, we expect the TCM to be a very near the start of the waveform.
+For instruments with long sustain times, we expect a very centrally located center of mass, and for instruments with long release times, we expect a later TCM value.
+
+\begin{figure}[H]
+\label{fig-FeatureTCM}
+\begin{center}
+\textcolor{red}{PLOT OF TCM FEATURES HERE}
+\end{center}
+\caption{Temporal center-of-mass visualized in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Auto Correlation Coefficients}
+
+\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution .
+We can compute any number of ACC's and their value changed depending on the index chosen.
+It is common to only compute the first $K$ ACC's \cite{Virtanen}.
+For a full waveform signal $s$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
+\begin{equation}
+\label{eqn-FeatureACC}
+\text{ACC}_k\big[ s \big] = 
+\frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]} {\sqrt{\sum_{i=0}^{M-k-1}s^2[i]} \sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
+\end{equation}
+
+\begin{figure}[H]
+\label{fig-FeatureACC}
+\begin{center}
+\textcolor{red}{PLOT OF ACC FEATURES HERE}
+\end{center}
+\caption{First four auto correlation coefficients visualized in feature-space}
+\end{figure}
+
+% ================================================================
+
+\newpage
+
+\subsection{Frequency-Space Features}
+\label{subsec-frequency}
+
+\paragraph*{}The features described in this section are derived from the frequency-domain representations of each audio sample.
+Frequency space is represented by the transposed spectrogram matrix, $S^T$, described in sec.
+(\ref{subsec-spectrogram}).
+This is done to ensure that each  row is now an analysis frame, each column is a frequency bin.
+This gives a similar structure to the time-space analysis frames matrix, $A$, in eqn.
+(\ref{eqn-FrameMatrix}).
+For each feature, we detail the physical significance and provide a visualization in feature-space.
+
+\paragraph*{}From frequency space, we use the following $13$ features:
+\begin{itemize}
+\item[•] Mel Frequency Cepstral Coefficients ($\times 12$)
+\item[•] Frequency Center of Mass
+\end{itemize}
+
+% ================================
+
+\subsubsection{Mel Frequency Cepstral Coefficients}
+
+\paragraph*{}Mel Frequency Ceptstral Coefficients (MFCC's) are a very prolific feature used widly in audio classification tasks \cite{Liu,Virtanen,Zhang}.
+MFCC's are produced by converting a linear-frequency axis with units such as Hertz into units of Mels, which are design to account for the non-linear perception of frequency in humans.
+The Hertz to Mel and Mel to Hertz transforms are given \cite{Virtanen}:
+\begin{equation}
+\label{eqn-HztoMel}
+M_f[h] = 2595 \log_{10}\big(1+ \frac{h}{700}\big)
+\end{equation}
+\begin{equation}
+\label{eqn-MeltoHz}
+H_f[m] = 700 \big(10^{(\frac{m}{2595})}-1\big)
+\end{equation}
+Where $M_f$ is the frequency in units of Mels, given $[h]$, a frequency in Hertz, and $H_f$ is the frequency in Hertz given $[m]$ a frequency in Mels.
+
+\paragraph*{}Mel filters are produced by grouping frequency-space into $R$ overlapping bins called \textit{Mel Filter-banks}.
+In units of Mels, each filter bank, $R_i$ remains a constant width, but when shown in Hertz, the bins increase logarithmically.
+\begin{figure}[H]
+\label{fig-MelFilterBanks}
+\begin{center}
+\textcolor{red}{Figure of a few Mel Filter Banks goes here}
+\end{center}
+\caption{Mel Filter Banks shown in frequency space with units of Hertz}
+\end{figure}
+Each of the $R$ filters is created to be $N'$ samples long, and transformed back into units of Hertz.
+When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
+Thus, each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is a filter.
+We apply the Mel Filter banks to the spectrogram to create matrix $B$:
+\begin{equation}
+\label{eqn-FilterBanks}
+B = S^T M^T
+\end{equation}
+Matrix $B$ has shape $k' \times R$.
+
+\paragraph*{}Using $S^T$ ensure that each row of the matrix is an analysis frame in frequency space.
+Similarly, each column of the matrix $M$ is a appropriately scaled Mel filter-bank.
+This way, the matrix product in eqn.
+(\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
+Finally, we compute the average energy across all $k'$ frames.
+The resulting $R$ floating-point numbers are approximation of the signal's energy in those particular frequency bands.
+For this project, we have chosen to use $R = 12$ filter-banks, which are all used as features.
+
+\begin{figure}[H]
+\label{fig-FeatureMFCC}
+\begin{center}
+\textcolor{red}{PLOT OF MFCC FEATURES HERE}
+\end{center}
+\caption{Mel Frequency Ceptral Coefficients in feature-space}
+\end{figure}
+
+% ================================
+
+\subsubsection{Center of Mass}
+
+\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a strong representation of how overtones and energy is distributed in the signal's frequency domain.
+As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
+This encodes the FCM for a single analysis frame (in frequency-space) in the waveform.
+For an frequency-analysis frame, $s^{(i)}$, the FCM is given by:
+\begin{equation}
+\label{eqn-FeatureFCM}
+\text{TCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
+\end{equation}
+We compute the FCM for each of the $k'$ frames, and then average the results. We use the average FCM across $k'$ frames to compute the FCM feature:
+\begin{equation}
+TCM = \sum_{i=0}^{k'} \text{TCM}_{i}\big[ s^{(i)} \big]
+\end{equation}
+
+\paragraph*{}The average FCM gives a strong approximation of the instrument or signal source's range.
+For example, a flute or violin will have a considerably high FCM value, even in their lower registers.
+Similarly, basses or tubas will have considerably low FCM values.
+Given that the standard frequency range of some musical instruments is fixed, it is guaranteed that for any particular instrument, the FCM will consistently remain within certain bounds \cite{Olson,White}.
+
+\begin{figure}[H]
+\label{fig-FeatureFCM}
+\begin{center}
+\textcolor{red}{PLOT OF FCM FEATURES HERE}
+\end{center}
+\caption{Frequency center-of-mass visualized in feature-space}
+\end{figure}
 
@@
 
-\item[•]Nathan Richard for consultation on physics, mathematics, and programming topics.
-
-\item[•]Morgan Saidel for consultation on physics, mathematics, and programming topics.
+\item[•]Dakota Buell, John Parker, Nathan Richard, Morgan Saidel for consultation on physics, mathematics, and programming topics.
 
@@
 
-\item[•]John Parker for consultation on physics, mathematics, and programming topics.
-
-\item[•]Dakota Buell for consultation on physics, mathematics, and programming topics.
-
-\item[•]Dr. Kevin Short for various consultation and guidence throughout this project
-
-\item[•]Dr. Maurik Holtrop for various consultation and guidence throughout this project
-
-\item[•]University of Iowa, Electronic Music Studio for a digital sound library ued for training samples
-
-\item[•]Philharmonics Symphony Orchestra for a digital sound library used for training samples
+\item[•]Dr. Kevin Short and Dr. Maurik Holtrop for various consultation and guidance throughout this project
+
+\item[•]University of Iowa, Electronic Music Studio and Philharmonica Symphony Orchestra for the digital sound library used for training data samples.
 
@@
 Short, K. and Garcia R.A. 2006. "Signal Analysis Using the Complex Spectral Phase Evolution (CSPE) Method." AES: \textit{Audio Engineering Society Convention Paper}.
+
+\bibitem{Tenorflow}
+TensorFlow: Large-scale machine learning on heterogeneous systems,
+2015. Software available from tensorflow.org.
 

### 2020-10-11 SignalClassifier/ClassifierMain/SystemUtilities.py
Updates to Cross Validation Program
- Exported Needed Splits
- Need to delete splits folder when done.
- Need to Run "ClassifierMAIN.py" from Xval code

@@ -248,7 +248,7 @@ class ArgumentValidator :
 
     @property
     def GetLocalPaths (self):
-        """ Return Necessaru Directory Paths """
+        """ Return Necessary Directory Paths """
         return (self.readPath,self.exportPath,self.modelPath)
 
     @property

### 2020-10-11 SignalClassifierTools/KFoldsCrossValidation/XValUtilities.py

@@ -7,46 +7,107 @@ X-Validation Utilities
 
             #### IMPORTS ####
 
-import numpy as np
 import os
 import sys
+import numpy as np
+import pandas as pd
 
             #### CLASS OBJECT DEFINITIONS ####
 
 class CrossValidationSplit:
     """ Apply Cross-Validation Split to Full data set """
     
-    def __init__(self,fileObjs,nSplits=10):
+    def __init__(self,fileObjs,filePath,nSplits=10):
         """ Initialize CrossValidationSplit Instance """
-        self.fileObjects = fileObjs
-        self.K = nSplits
-        self.ApplySplit()
+        self.fileObjects = fileObjs     # Add objects
+        self.filePath = filePath        # full data is stored
+        self.splitsPath = os.path.join(self.filePath,"ValidationSplits")
+        self.K = nSplits                # number of splits
+        self.ApplySplit()               # Dew it
 
     def ApplySplit(self):
         """ Split Data into 'K' equally sized groups """
         permuted = np.random.permutation(self.fileObjects)  # permute
-        self.folds = []                     # list to hold list of file objs
-        for i in range(self.K):             # each sample:
-            self.folds.append([])           # add an empty 'bin'
+        self.folds = [[] for i in range(self.K)]            # list to hold list of file objs
         for i in range(len(self.fileObjects)):      # each file
             _bin = i % self.K                       # get the bin for this sample
             self.folds[_bin].append(permuted[i])    # add sample to that bin
         return self         
 
-    def ExportFolds(self,splitNum):
-        """ Export the Splits based on the current iteration """
-        self.testSubset = self.folds[splitNum]  # build test data
-        self.trainSubset = []                   # init train data
-        for i in range(self.k):             # of the F-fold
-            if (i == splitNum):     # i = split, pass
-                continue
-            else:
-                self.trainSubset += self.folds[i]
+    def GetTrainTestData (self,i):  
+        """ Get Train / Test Data for i-th fold (i <= K) """
+        Xtest = self.folds[i]
+        Xtrain = []
+        for j in range(self.K):     # each subset
+            if i == j:              # this is test data
+                pass                # skip it
+            else:                   # otherwise
+                Xtrain += self.folds[j] # add to train data
+        return Xtrain,Xtest
+
+    def ExportSplits(self,sampleList,outPath):
[…]

### 2020-10-11 Thesis/SignalClassifierREADME/ClassifierREADME.tex
Started README for main Classifier

% ================================
% Landon Buell
% Kevin Short 
% PHYS 799.01
% 11 October 2020
% ================================

\documentclass[12pt,letterpaper]{article}

\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}
\usepackage{fancyhdr}

\begin{document}

% ================================================================

\title{Multi-Modal Signal Classifier - README}
\author{Landon Buell}
\date{October 2020}
\maketitle

\begin{abstract}
The \textit{Signal Classifier} program uses a hybrid neural network algorithm to attempt to classify time-series signals to a set of pre-determined classes. For the purpose of the algorithm's development, input samples were assumed to be .wav files of musical instruments performing one note, or several shorter notes in succession- totaling at around 100,000 - 200,000 samples each, sampled at 44.1 kHz.
\end{abstract}

% ================================================================

\subsection{Getting the Signal Classifier on Your Machine}

\paragraph*{}The \textit{Signal Classifier} program is stored in a GiHub Repository. As of Fall 2020, the repo can be found at
\begin{quote}
https://github.com/landonbuell/Buell-Senior-Thesis
\end{quote}
This repository can be pulled to your machine any number of ways, reccommended via github. (Git Clone, GitHub Desktop, etc.) Doing so will create new local directory on your machine. The "MAIN" python program itself is a standard \textit{.py} file located at:
\begin{quote}
../Buell-Senior-Thesis/SignalClassifier/ClassifierMain/ClassifierMAIN.py
\end{quote}

% ================================================================

\subsection{Command Line Arguments}

\paragraph*{}The Classifier requires 6 command-line arguments to function properly. These are:
\begin{itemize}

\item[•]\textbf{readPath} (str/path)\\
The local directory path where "read" data files are stored. Each file in this path is a a particularly formatted csv file. The csv/excel files are formatted as follows:
\begin{quote}
(Detail formatting here)
\end{quote}
The folder should otherwise be empty.

\item[•]\textbf{exportPath} (str/path)\\
The local directory path where progress data is exported to. When finished, this path will contain \textit{.csv} files detailing the training history of the model at each epoch or the label predictions of each sample.

\item[•]\textbf{modelPath} (str/path)\\
The local directory oath where the TensorFlow models are exported to. Each model will be saved in it's own sub-folder. This is where the program will look for the model to re-load it for future train/predict sessions.

\item[•]\textbf{ProgramMode} (str)\\
Indicates which mode the classifier program is executed as. Must be in ["train","predict","train-predict"]. \\
\paragraph*{}In \textit{train} mode, all collected samples will be used to train the classifier model. A "TRAININGHISTORY" file will be exported to "exportPath".  In \textit{predict} mode, all collected samples will be used to run predictions with the classifier model. A "PREDICTIONS" file will be exported to "exportPath". In \textit{train-predict} mode, a 90\% training, and 10\% testing split is made pseudo-randomly. The Classifier then runs \textit{train} mode and \textit{test} mode with the respective data subsets.

\item[•]\textbf{modelName} (str)\\
String representation used to name the classifier model in a human-readable format.

\item[•]\textbf{newModel} (bool)\\
Determines weather or not to create a NEW model of the given name. If \textit{true}, then any existing model of the same name is overwritten (cannot be recovered easily!). If \textit{False}, the program looks for an existing model of the name to resume training/predictions given last saved state.

\end{itemize}

% ================================================================

\subsection{When Running}

% ================================================================

\subsection{What to do with the Output}

% ================================================================

\end{document}

### 2020-10-20 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis Draft 0

@@
 \usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}
+
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyhf{}
+\lhead{Landon Buell}
+\rhead{B.S. Physics Thesis}
+\cfoot{\thepage}
 
@@
 \paragraph*{}Consider the biological process of hearing a sound wave and matching it to a source.
-We can model this behavior by some unknown function $F$.
-We produce an approximation of that function $F^*$ that can map the contents of a sound file that have been generated by a chaotic synthesizer to a potential source.
-For a set of inputs $\vec{x} = \big\{ x_0 , x_1 , x_2 , ...
+We can model this behavior by some unknown function $F$ and approximate it with the function $F^*$.
+This can map the contents of a sound file to a potential source as to mimic $F$.
+For a set of inputs (called features or predictors) $\vec{x} = \big\{ x_0 , x_1 , x_2 , ...
 , x_{p-1} \big\}$ and a set of classes $0$ through $k-1$, we denote this function as:
@@
 (\ref{subsec-NerualNetworkIntro}) and (\ref{subsec-NetworkStructure}), we introduce the nature and structure of a neural network and how it can use used in part to solve this problem.
-We show it's mathematical function analogue and how
 
@@
 \paragraph*{}The task of algorithmically matching sound files to musical instrument classes in exceedingly difficult through conventional computer programming techniques.
-Because of the complexity of sound waves, brain's interpretation them, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
-Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an architecture that allows for a computer to \textit{learn} and change and update itself as it is presented with more data.
+Because of the complexity of sound waves, and the brain's interpretation of them, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
+Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an solution that allows for a computer to \textit{learn} from past examples in order change and update itself.
 Such an algorithm exists in the form of a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine}.
-
-\paragraph*{}A neural network is a mathematical function that seeks to produce an approximation $F^*$, of some usually unknown function $F$ .
-For audio recognition, $F$ is some function, or series of functions, that occurs in the brain which allows for a listener to take the sensation of audio, and map it to a known musical instrument.
-For a neural network, a model must construct an approximate function $F^*$ using a set of parameters $\Theta$, which allows the model to map a series of inputs, $x$ (called \textit{features}) to a series of outputs, $y$ (called \textit{predictions}) \cite{Goodfellow,James,Virtanen}.
 
@@
 
-\paragraph*{}Over the course of their lives, humans will learn to map sounds to sources almost effortlessly.
+\paragraph*{}A neural network is a mathematical function that seeks to produce an approximation $F^*$, of some usually unknown function $F$ .
+For audio recognition, $F$ is some function or series of functions that occurs in the brain which allows for a listener to process the sensation of audio, and map it to a known source object.
+For a neural network, function $F^*$ uses a set of parameters $\Theta$, to map a series of inputs, $x$ (called \textit{features}) to a series of outputs, $y$ (called \textit{predictions}) \cite{Goodfellow,James,Virtanen}.
+
+\paragraph*{}Over the course of their lives, humans will learn to map sounds to sources almost effortlessly \cite{Virtanen}.
 Given an example, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olsen,White}.
@@
 \newpage
+\section{Properties of Musical Instruments}
+\label{sec-Instruments}
+
+\textcolor{red}{I have notes written out for this section, I just need to write it out here soon}
+
+% ================================================================
+% ================================================================
+
+\newpage
 \section{Feature Selections}
@@
 
-\paragraph*{}Audio and Machine learning researchers M.
+\paragraph*{}Audio machine learning researchers M.
 Kashif Saeed Khan and Wasfi G.
@@
 \end{quote}
-In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}.
-It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier.
+In the case of the biological process, the features of the audio is simply the raw time series waveform as processed by the brain.
+This information is then used into categorize the source.
+In the case of the neural network model, the time series waveform alone has shown to be unreliable in classification tasks \cite{Virtanen}.
+We must then develop a set of features or predictors that can describe important properties of the waveform in a far more efficient manner \cite{Goodfellow,James}.
+
+\paragraph*{}It becomes quickly apparent that the choice of features is extrodinarily important to the process of training and evaluation of the classifier model.
 Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels.
-The inappropriate choice features does not reflect the significant characteristics of the signal.
+The inappropriate choice features does not reflect the significant characteristics of the data.
 
@@
 \end{quote}
-In constructing a neural network classifier, the development of appropriate features is of the utmost importance.
-To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency-space representation of the waveform.
-It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely solely these features.
+To ensure the construction of a suitable model, we derive features based from three representations of the audio file: (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency-space representation of the waveform.
+It is important to note that although this algorithm will classify sound data to instruments, the model will never actually be presented with a waveform directly, instead it will rely solely on the features.
 
@@
 In the training process this object, along with the appropriate classification label, $y$ is presented to the neural network for processing.
-This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu}
+This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu,Kahn}.
 
 \paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector.
-These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics.
+These features are derived are principles of music, digital signal processing, previous work, and underlying physics that governs the behavior of instruments.
 In the following sections, we outline the set of $21$ features used in the classification process
@@
 \label{eqn-X2Shape}
-X_2 \in \mathbb{R}^{(b \times P)}
+X_2 \in \mathbb{R}^{(b \times p)}
 \end{equation}
@@
 (\ref{subsec-spectrogram}).
-Similarly, $P$ is the number of features derived from the time and frequency-representation of features outlined in sec.
-(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ samples stored in that design matrix.
-A row of $X_2$ has shape $1 \times P$ where there are $P$ features within the \textit{feature-vector} for each sample.
-Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.
+Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec.
+(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ audio samples stored in that design matrix.
 
@@
 \begin{enumerate}
-\item Roughly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
+\item Roughly $16,000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
 \item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
@@
 
-\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification.
+\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification \cite{Liu,Zhang}.
 Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame.
-Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhang,Kahn,Virtanen}.
-For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
-We also choose to use exactly $k = 256$ frames.
-Waveforms that are too short are padded with zeros, and waveforms that are too long are truncated.
-The audio has been sampled at $f_s = 44100$ samples/second, so ach frame represents a slice of time that is about $0.1$ seconds long.
+Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Kahn,Virtanen}.
+
+\paragraph*{}For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
+Since each audio file contains a different number of samples, we choose the number of frames, $k$ to be less than or equal to $256$.
+If $k > 256$, the waveform in truncated, if $k \leq 256$ the frames left as is.
+The audio has been sampled at $f_s = 44100$ samples/second, so each frame represents a slice of time that is about $0.1$ seconds long.
 
@@
 \end{equation}
-We use bracket notation, $[j]$ to indicate that each analysis frame $a_i$ is array-like. Many programming languages could also use the following indexing conventions for matrix $A$:
+We use bracket notation, $a[j]$ to indicate that each analysis frame $a_i$ is array-like. The following indexing conventions for matrix $A$ all represent the same entry:
 \begin{equation}
@@
 \end{equation}
-These all represent equivalent entries.
 
@@
 \end{equation}
-The window function allows for a cleaner transform into frequency space \cite{Virtanen}.
+The window function allows for a cleaner transform into frequency space \cite{Virtanen}. \textcolor{blue}{Expand on this. HOW? Why do we use a windowing function?}
 
@@
 \end{equation}
-Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $\widetilde{A}^T$.
+Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix - product of $\mathbb{W}$ and $\widetilde{A}^T$.
 The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
@@
 Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$.
+To ensure homogeneous input sizes between all samples, we zero-pad the matrix $S$ with additional columns until $k = 256$.
+Recall that wave forms were truncated to ensure that $k \leq 256$ analysis frames.
 
@@
 This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
-As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $6000$ Hz.
+To condense the size of the matrix, we select onlt the frequency bins that correspond to energies between $0$ Hz and $6000$ Hz.
 This makes the input array smaller, and eliminates redundant and non-useful information.
@@
 
-\paragraph*{}Each spectrogram is now $N' \times k \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform as a function of both time and frequency.
+\paragraph*{}Each spectrogram is now $N' \times k \times 1$ (The last axis represents a single pixel channel, as opposed to $3$ channels for RGB inputs, etc.) and effectively encodes the energy distribution of the waveform as a function of both time and frequency.
 The spectrogram is the first feature used in this model.
@@
 For training, a batch of $b$ samples are concatenated into a single array object.
-\textcolor{blue}{See Neural Network section for more details}.
 For a batch of $b$ samples of $N' \times k \times 1$ spectrograms, we shape $X_1$ such that:
@@
 \end{equation}
-Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}).
-This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
-\textcolor{blue}{See Neural Network section for more details}
+Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}). This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
 

### 2020-10-21 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Feature Selections Section

@@
 
+\textcolor{blue}{I need to clean this sub-subsection up as well. The optimizer needs a better introduction and justification}
+
 \paragraph*{}For this project, we employ an \textit{Adaptive-Moments} optimization algorithm, also called \textit{ADAM} for short.
@@
 \label{sec-Architecture}
+
+\textcolor{red}{I need to include a bit more detail \& citations on the "hybrid / multimodal" nature of this need works. Updates to follow}
 
@@
 
-\paragraph*{}The $21$ features are from each file are organized into one of two array structures.
-each called a \textit{design matrix}.
-A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest.
+\paragraph*{}The spectrogram and $20$ features from each sample are organized into one of two array structures, each called a \textit{design matrix}.
+A design matrix is an array of real floating-point numbers that stores the features in a convenient way for the neural network to digest.
 For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.
@@
 \end{equation}
-Where $Q' \times R' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
+Where $N' \times k \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
 (\ref{subsec-spectrogram}).
@@
 
-\subsection{Spectrogram Feature}
+\subsection{Spectrogram Features}
 \label{subsec-spectrogram}
@@
 
-\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. Time space can be represented in one of three ways: 
-\begin{itemize}
-\item The raw waveform $s$\\
-Indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
-\item A single analysis frame $a_i$ \\
-Indexed by $a_i[j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
-\item The full analysis frame matrix $A$ \\
-Indexed by $A[i][j]$ with $i \in [0,1,2,3,...,k-2,k-1]$ and $j \in [0,1,2,3,...,N-2,N-1]$
-\end{itemize}
+\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample.For consistency between smaples, each waveform is padded or truncated to contain exactly $M$ samples.
+Time space is indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
 
@@
 \paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal Often, we compute the RMS-Energy of each frame - a larger energy of the frame, the larger the average amplitude of the waveform in that frame.
-For frames with smaller amplitude, we can assume that the signal has either not begun, or is decaying.
-
-\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olson,Virtanen}
+For frames with smaller amplitude, it is likely that the signal has either not begun, or is decaying.
+
+\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olsen,Virtanen}
 \begin{equation}
 \label{eqn-RMS}
-\text{RMS}\big[ s \big] = \sqrt{\frac{1}{N} \sum_{i=0}^{N-1} s[i]^2}
+\text{RMS}\big[ s \big] = \sqrt{\frac{1}{M} \sum_{i=0}^{M-1} s[i]^2}
 \end{equation}
 By using the full waveform, we acquire a rough estimate for the energy in the entirety of the audio file \cite{Liu}.
-For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large waveform RMS when compared to those instruments without sustain such as plucked stings or dampened percussion
+For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large waveform RMS when compared to those instruments without sustain such as plucked stings or dampened percussion  \textcolor{red}{Citation?}
 
 \begin{figure}[H]
+\begin{center}
+\textcolor{red}{PLOT OF TDE FEATURES HERE}
+\end{center}
+\caption{Time domain envelope visualized in feature-space}
 \label{fig-FeatureTDE}
-\begin{center}
-\textcolor{red}{PLOT OF TDE FEATURES HERE}
-\end{center}
-\caption{Time domain envelope visualized in feature-space}
 \end{figure}
@@
 \label{eqn-ZXR}
-\text{ZXR}\big[ s \big] = \frac{1}{2} \sum_{i=1}^{M-1} \big{|} \sign(s[i]) - \sign(s[i-1]) \big{|} 
+\text{ZXR}\big[ s \big] = \frac{1}{2} \sum_{i=1}^{M-1} \Big{|} \sign(s[i]) - \sign(s[i-1]) \Big{|} 
 \end{equation}
@@
 \begin{figure}[H]
+\begin{center}
+\textcolor{red}{PLOT OF ZXR FEATURES HERE}
+\end{center}
+\caption{Zero crossing rate visualized in feature-space}
 \label{fig-FeatureZXR}
-\begin{center}
-\textcolor{red}{PLOT OF ZXR FEATURES HERE}
-\end{center}
-\caption{Zero crossing rate visualized in feature-space}
 \end{figure}
@@
 \paragraph*{}The temporal center of mass (TCM) of a signal is used to compute roughly where in time the amplitude of the waveform \textit{bunches up}.
-We treat the full waveform array, $s$, with $M$ samples as a 1-Dimensional discrete mass distribution.
+We treat the full waveform array, $s$, with $M$ samples as a discrete 1-Dimensional mass distribution.
 The TCM of that waveform is then given:
@@
 \end{equation}
-This includes negative amplitude values acting as "negative masses".
-
-\paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance.
+This includes negative amplitude values acting as "negative masses". \textcolor{blue}{Should I use the absolute value of the signal instead?}
+
+\paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance textcolor{red}{Citation needed}.
 For instruments with heavier attacks, we expect the TCM to be a very near the start of the waveform.
@@
 \begin{figure}[H]
+\begin{center}
+\textcolor{red}{PLOT OF TCM FEATURES HERE}
+\end{center}
+\caption{Temporal center-of-mass visualized in feature-space}
 \label{fig-FeatureTCM}
-\begin{center}
-\textcolor{red}{PLOT OF TCM FEATURES HERE}
-\end{center}
-\caption{Temporal center-of-mass visualized in feature-space}
 \end{figure}
@@
 \end{equation}
+
+\paragraph*{}An ACC can be thought of as convolving a signal with a time-delayed version of itself.
+This measures similarity between samples related to the time difference between them \textcolor{red}{Citation needed}.
+\textcolor{blue}{I may need to try a different set of ACC's for this}
 
@@
 
-\paragraph*{}Mel Frequency Ceptstral Coefficients (MFCC's) are a very prolific feature used widly in audio classification tasks \cite{Liu,Virtanen,Zhang}.
+\paragraph*{}Mel Frequency Ceptstral Coefficients (MFCC's) are a very prolific feature used widely in audio classification tasks \cite{Liu,Virtanen,Zhang}.
 MFCC's are produced by converting a linear-frequency axis with units such as Hertz into units of Mels, which are design to account for the non-linear perception of frequency in humans.
@@
 \end{figure}
-Each of the $R$ filters is created to be $N'$ samples long, and transformed back into units of Hertz.
+Each of the $R$ filters is created to be $N'$ samples long, to match the width of the cropped spectrogram, and transformed back into units of Hertz.
 When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
@@
 \end{equation}
-Matrix $B$ has shape $k' \times R$.
-
-\paragraph*{}Using $S^T$ ensure that each row of the matrix is an analysis frame in frequency space.
+Matrix $B$ has shape $k \times R$.
+
+\paragraph*{}Using $S^T$ ensures that each row of the matrix is an analysis frame in frequency space.
 Similarly, each column of the matrix $M$ is a appropriately scaled Mel filter-bank.
@@
 (\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
-Finally, we compute the average energy across all $k'$ frames.
+Finally, we compute the average energy across all $k$ frames.
 The resulting $R$ floating-point numbers are approximation of the signal's energy in those particular frequency bands.
@@
 \begin{figure}[H]
+\begin{center}
+\textcolor{red}{PLOT OF MFCC FEATURES HERE}
+\end{center}
+\caption{Mel Frequency Ceptral Coefficients in feature-space}
 \label{fig-FeatureMFCC}
-\begin{center}
-\textcolor{red}{PLOT OF MFCC FEATURES HERE}
-\end{center}
-\caption{Mel Frequency Ceptral Coefficients in feature-space}
 \end{figure}
@@
 % ================================================================
+
+\subsection{Assembling the Design Matrices}
+\label{subsec-AssembleXs}
+
+\textcolor{blue}{I would like to use some figures here to graphically represent how the feature vectors and spectrograms are concatenated into the design matrices.
+I may help with the geometry of the situation}
+
+% ================================================================
 % ================================================================
@@
 The most common practice is to divide a full data set into a subset of \textit{training} samples, and \textit{testing} samples.
+As the names imply, the training subset is used to fit the model, and we use the labeled testing data set to evaluate.
 The exact ratio of sample volume between these subsets varies depending on the task \cite{Goodfellow,Geron2,Mitchell}.
-We as the names imply, the training subset is used to fit the model, and we use the labeled testing data set to evaluate.
 Since the testing data is labeled, we can compare the classifiers predictions to the \textit{ground truth} labels.
@@
 \subsection{Cross Validation}
+\label{subsec-XValidation}
 
@@
 
-Divide Data into $K$ non-overlapping subsets $x_{i}$, each with roughly $K/N$ samples \\
+Divide Data into $K$ non-overlapping subsets $x_{i}$, each with roughly $N/K$ samples \\
 $X \rightarrow \big\{ x_{0}, x_{1}, x_{2}, ..., x_{K-2},  x_{K-1} \big\}$ \\
@@
 	\item Concatenate the remaining subsets into training data set
-	\item $X_{train} = x_{j \neq k}$
+	\item $X_{train} = x_{i \neq j}$
 	\item Train the model, $F^*$ with the $X_{train}$ data set
-	\item Evaluate the trained model with metric function(s) $P$
+	\item Evaluate the trained model with the $X_{train}$ dataset, and compute value of metric function(s) $P$
 	\item Store Performance $P$ in Performance History array
@@
 
-\paragraph*{}By using cross-validation, we gain a deeper understanding of the model to ensure that the model can be properly trained consistently.
+\paragraph*{}By using cross-validation, we gain a deeper understanding of the model to ensure that the model can be consistently trained.
 This also helps counteract the possibility that the model got very lucky or unlucky with a particular set of initial conditions \cite{Geron,James}.
@@
 
+\subsection{The Bagging Technique}
+\label{subsec-Bagging}
+
+\paragraph*{}Many learning models such as neural networks, or decision trees suffer from \textit{high variance} \cite{James}.
+This means that randomly splitting a full dataset into halves and fitting two a different model to each half has the potential to produce wildly different fit parameters.
+In the case of neural networks, high variance can be amplified by the nature of the randomization in multidimensional optimizer \cite{Geron}.
+To mitagate this effect, we can employ a variant of the \textit{bagging} algorithm.
+Bagging uses an average, or weighted average, of parameters in multiple models that have been trained on overlapping data sets.
+
+\paragraph*{}Consider if we have $k$ models, all trained on overlapping training/testing data sets:
+\begin{equation}
+\text{Models} = \Big\{ F^*_{0} , F^*_{1} , F^*_{2} , ... , F^*_{k-2} , F^*_{k-1} \Big\}
+\end{equation}
+Each model contains a corresponding set of paramaters, $\Theta_{i}$, $i \in [0,k-1]$.
+We could then aggregate the parameters according to a weighted average to create a new set of paramaters, $\Theta_{k}$ which can be used to construct a new model, $F^*_{k}$.
+
+\paragraph*{}This algorithm is often used after $K$-Folds Cross validation, as outlined in in subsec.
+(\ref{subsec-XValidation}).
+This grants the $k$ models and corresponding parameters that could be used in the bagging technique \cite{James}.
+\textcolor{blue}{This is very not finished yet}
+
 % ================================================================

### 2020-11-02 SignalClassifier-Postprocessing/FeatureProperties/PropertyUtilities.py
Added Feature Plots

@@ -40,7 +40,7 @@ class FeatureProcessor:
 
     def CreateDictionary(self,encdPath):
         """ Handle class dictionary """
-        modelName = "ChaoticXVal"
+        modelName = "FeaturesXVal"
         categories = CategoryDictionary(encdPath,modelName)
         self.classNames = categories.encoder.keys()          # get names of categories
             

### 2020-11-02 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex

@@
 Rather than accept an image-like input, the perception simply takes a vector-like input of properties that are derived from the audio file.
-We call these properties \textit{features} \cite{Geron,Kahn,Virtanen}.
+We call these properties \textit{features} \cite{Geron,Kahn,Serizel}.
 \textcolor{blue}{Details on the creating of these features can be found in the \textit{features} section of this document.}
@@
 This information is then used into categorize the source.
-In the case of the neural network model, the time series waveform alone has shown to be unreliable in classification tasks \cite{Virtanen}.
+In the case of the neural network model, the time series waveform alone has shown to be unreliable in classification tasks \cite{Serizel}.
 We must then develop a set of features or predictors that can describe important properties of the waveform in a far more efficient manner \cite{Goodfellow,James}.
@@
 Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame.
-Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Kahn,Virtanen}.
+Each of the $k$ frames then allows for a section of the signal in quazi-stationary state \cite{Kahn,Serizel}.
 
@@
 
-\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olsen,Virtanen}
+\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olsen,Serizel}
 \begin{equation}
@@
 
-\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}. The ZXR for the full waveform $s$ is given by \cite{Virtanen,Liu}
+\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}. The ZXR for the full waveform $s$ is given by \cite{Serizel,Liu}
 \begin{equation}
@@
 Where $\sign(x)$ returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$.
-This provides a rough estimate for the average frequency in the full waveform, and can help discern clean periodic signals (low ZXR) from those that may have more noise or volatile behavior (high ZXR)\cite{Virtanen}.
+This provides a rough estimate for the average frequency in the full waveform,n and can help discern clean periodic signals (low ZXR) from those that may have more noise or volatile behavior (high ZXR)\cite{Serizel}.
 
@@
 
-\subsubsection{Center of Mass}
+\subsubsection{Temporal Center of Mass}
 
@@
 We can compute any number of ACC's and their value changed depending on the index chosen.
-It is common to only compute the first $K$ ACC's \cite{Virtanen}.
+It is common to only compute the first $K$ ACC's \cite{Serizel}.
 For a full waveform signal $s$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
@@
 
-\subsubsection{Mel Frequency Cepstral Coefficients}
-
-\paragraph*{}Mel Frequency Ceptstral Coefficients (MFCC's) are a very prolific feature used widely in audio classification tasks \cite{Liu,Virtanen,Zhang}.
-MFCC's are produced by converting a linear-frequency axis with units such as Hertz into units of Mels, which are design to account for the non-linear perception of frequency in humans.
-The Hertz to Mel and Mel to Hertz transforms are given \cite{Virtanen}:
+\subsubsection{Mel Filter Bank Energies}
+
+\paragraph*{}Mel filter banks are divisions of the frequency spectrum of a signal into $R$ overlapping triangular bins \cite{Sahidullah}.
+These filter banks allows us to group sounds based on their energy distribution in frequency space.
+Each filter is triangularly shaped, over a certain band in frequency space, and zero elsewhere.
+This way, when computing the the dot product of any filter with frequency space, we get an approximation of energy in that filter bank \cite{Sahidullah,Serizel}.
+
+\paragraph*{}Rather than producing filter banks based on the linear Hertz scale, the frequency axis of the signal is transformed into units of \textit{Mels}, which is used to account for the non-linearity in human pitch perception \cite{Serizel,Kahn}.
+Filter banks are produced to be evenly spaced on the Mel scale, and then transformed back into the Hertz scale.
+This has the effect of producing triangular filter banks with grow in width as the frequency increases.
+The Hertz to Mel and Mel to Hertz transforms are given \cite{Serizel,Kahn}:
 \begin{equation}
@@
 \begin{figure}[H]
+\begin{center}
+\textcolor{red}{Figure of a few Mel Filter Banks goes here}
+\end{center}
+\caption{Mel Filter Banks shown in frequency space with units of Hertz}
 \label{fig-MelFilterBanks}
-\begin{center}
-\textcolor{red}{Figure of a few Mel Filter Banks goes here}
-\end{center}
-\caption{Mel Filter Banks shown in frequency space with units of Hertz}
 \end{figure}
-Each of the $R$ filters is created to be $N'$ samples long, to match the width of the cropped spectrogram, and transformed back into units of Hertz.
+Each of the $R$ filters is created to be $N'$ samples long, to match the width of the cropped frequency space in the spectrogram, and transformed back into units of Hertz.
 When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
-Thus, each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is a filter.
+Each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is a filter.
 We apply the Mel Filter banks to the spectrogram to create matrix $B$:
@@
 (\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
-Finally, we compute the average energy across all $k$ frames.
-The resulting $R$ floating-point numbers are approximation of the signal's energy in those particular frequency bands.
-For this project, we have chosen to use $R = 12$ filter-banks, which are all used as features.
+Finally, we compute the average energy across all $k$ frames, into array $\widetilde{B}$ with shape $1 \times R$.
+For this project, we have chosen to use $R = 12$ filter-banks, which are all appended to the feature vector.
 
@@
 \end{center}
-\caption{Mel Frequency Ceptral Coefficients in feature-space}
+\caption{Mel Frequency Cepstral Coefficients in feature-space}
+\label{fig-FeatureMFBE}
+\end{figure}
+
+% ================================
+
+\subsubsection{Mel Frequency Cepstral Coeffecients}
+
+\paragraph*{}Ceptstral coefficients are the result of computing the inverse discrete Fourier transform (IDFT) of the logarithm of the frequency Spectrum.
+Mel Frequency Cepstral Coefficients (MFCC's) are the most commonly used in digital signal processing.
+They are computed throught he inverse discrete cosine transform of the log energy in in each Mel frequency bank \cite{Serizel,Sahidullah}.
+The $c$-th coefficient is given by:
+\begin{equation}
+\label{feat-MFCC}
+\text{MFCC}[c] = \sqrt{\frac{2}{R}} \sum_{i=1}^{R} 
+\log\big(\widetilde{B[i]}\big) \cos\bigg(\frac{c(i-\frac{1}{2})\pi}{R[i]}\bigg)
+\end{equation}
+Where $\widetilde{B}$ are the column average of the Mel filter bank energies computed in eqn. (\ref{eqn-FilterBanks}), and $R$ is the number of filter banks used.
+
+\paragraph*{}Physically, MFCC's are a transform of a transform.
+This allows us to investigate the periodicity of the frequency spectrum, which highlights phenomena such as overtones or echoes \cite{Virtanen}.
+Ceptrum coefficients are commonly used to speech identification and are very prolific in sound recognition tasks \cite{Serizel,Sahidullah,Liu}.
+We provide a representation of MFCC properties below.
+
+\begin{figure}[H]
 \label{fig-FeatureMFCC}
+\begin{center}
+\textcolor{red}{PLOT OF MFCC FEATURES HERE}
+\end{center}
+\caption{Mel Frequency Cepstral Coefficients visualized in feature-space}
 \end{figure}
@@
 
-\subsubsection{Center of Mass}
-
-\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a strong representation of how overtones and energy is distributed in the signal's frequency domain.
+\subsubsection{Frequency Center of Mass}
+
+\paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a representation of how overtones and energy is distributed in the signal's frequency domain.
 As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
@@
 \label{eqn-FeatureFCM}
-\text{TCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
+\text{FCM}_{i}\big[ s^{(i)} \big] = \frac{\sum_{j=0}^{N'-1}j s^{(i)}[j]}{\sum_{j=0}^{N'-1}s^{(i)}[j]}
 \end{equation}
@@
 \begin{equation}
-TCM = \sum_{i=0}^{k'} \text{TCM}_{i}\big[ s^{(i)} \big]
+FCM = \sum_{i=0}^{k'} \frac{1}{k'}\text{FCM}_{i}\big[ s^{(i)} \big]
 \end{equation}
@@
 
+\bibitem{Sahidullah}
+Sahidullah, Goutam S. “Design, Analysis and Experimental Evaluation of Block Based Transformation in MFCC Computation for Speaker Recognition.” 18 Nov. 2011.
+
+\bibitem{Serizel}
+Serizel, Roman, et al. “Acoustic Features for Environmental Sound Analysis.” Computational Analysis of Sound Scenes and Events, by Tuomas Virtanen, Springer, 2018, pp. 71–101.
+
 \bibitem{Short}

### 2020-11-04 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex

@@
 \paragraph*{}Other than inspiration from the brain, Neural Networks are name \textit{networks} because of their nested composition nature.
-The model can be represented by a linear or acyclic computational graph which successively maps exactly how the repeated composition is structured.
-In a \textit{feed-forward network}, information is passes successively in one direction.
+The model can be represented by a linear computational graph which successively maps exactly how the repeated composition is structured.
+In a \textit{feed-forward network}, information is passed successively in one direction.
 For example functions could be chained together such as \cite{Goodfellow}
@@
 \paragraph*{}The model is recursive by nature, the activations from one layer, $l-1$, are used to directly produce the activations of the next successive layer $l$.
-Thus eqn.
+Thus Eq.
 (\ref{eqn-LayerFunction}) can be alternatively written as:
@@
 The array of activations, $x^{(0)}$, is the raw input given the neural network, called \textit{input} activations.
-Conversely, $x^{(L-1)}$ is referred to as\textit{output} activations \cite{Geron,James,Loy}.
+Conversely, $x^{(L-1)}$ is referred to as \textit{output} activations \cite{Geron,James,Loy}.
 
@@
 Each iteration in the main \textit{for-loop} represents the execution of a layer, and passing the result to the "next" layer function.
-We assume each layter to follow a two-step structure, being (i) a linear transformation as in eqn.
-(\ref{eqn-LinearTransform}) and (ii) an element-wise non-linear activation function as in eqn.
+We assume each layer to follow a two-step structure, being (i) a linear transformation as in Eq.
+(\ref{eqn-LinearTransform}) and (ii) an element-wise non-linear activation function as in Eq.
 (\ref{eqn-elementActivation}).
@@
 
-If training the network, the intermediate layer activations must be stored for back-propagation. Otherwise, they must be discarded.
+If training the network, the intermediate layer activations must be stored for back-propagation. Otherwise, they may be discarded. \\
 $Z = \{\} \leftarrow$ array to hold pre-activations \\
@@
 	\item Evaluate Linear Transformation
-	\item $z^{(l)} \leftarrow$ 
+	\item $z^{(l)} \leftarrow W^{(l)} x^{(l-1)} + b^{(l)}$ 
 	\item Apply non-linear Activation Function
@@
 
-\item Network final prediction is last object in 'act' array.
+\item Network final prediction is last object in $X$ array.
 \item $y^* \leftarrow x^{(L-1)} = X[-1]$
 \item Return the pre-nonlinear activations and final-nonlinear activations.\\
-\item The final index of $X$ represents the neural network's final prediction. \\
 \RETURN $Z , X$
@@
 
-\paragraph*{}As stated previously, a neural network is composed of a series of functions that are called successively to transform features (an input) into a prediction (an output).
-As shown in eqn.
+\paragraph*{}As stated previously, a neural network is composed of a series of functions that are called in succession to transform features (an input) into a prediction (an output).
+As shown in Eq.
 (\ref{eqn-altLayerFunction}), each function feeds directly into the next as to form a sort of recursive computational graph \cite{Goodfellow}.
@@
 This activation function typically is a non-linear function which allows for the modeling of increasingly complex decision-boundaries.
-The Linear transformation can be given by eqn (\ref{eqn-LinearTransform}) in the case of a 1D Dense layer (\ref{subsubsec-DenseLayer}) or eqn.
+The Linear transformation can be given by Eq.(\ref{eqn-LinearTransform}) in the case of a 1D Dense layer (\ref{subsubsec-DenseLayer}) or Eq.
 (\ref{eqn-LinearTransform2}) in the case of a 2D Convolution layer.
@@
 
-\paragraph*{}The combination of eqn.
-(\ref{eqn-LinearTransform}) and eqn.
-(\ref{eqn-elementActivation}), for a layer $l$ , make up the function represented by that layer, as in eqn.
+\paragraph*{}The combination of Eq.
+(\ref{eqn-LinearTransform}) and Eq.
+(\ref{eqn-elementActivation}), for a layer $l$ , make up the function represented by that layer, as in Eq.
 (\ref{eqn-altLayerFunction}).
@@
 
-\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer, or \textit{Fully-Connected} layer for short, was one of the earliest function types used in artificial neural network models \cite{Geron2,Loy}.
+\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer, or \textit{Fully-Connected} layer, was one of the earliest function types used in artificial neural network models \cite{Geron2,Loy,McCulloch}.
 They are among the most commonly used layer types.
 A dense layer is composed of a layer of \textit{artifical neurons}, each of which holds a numerical value within it, called the \textit{activation} of that neuron.
-This idea was developed back from McCulloch and Pitts' work \cite{McCulloch}, and was expanded upon by Frank Rosenblatt in  1957 \cite{Geron}.
+This idea was developed from McCulloch and Pitts' work \cite{McCulloch} in attempting to model cognitive processes as mathematical functions, and was expanded upon by Frank Rosenblatt in  1957 \cite{Geron}.
 
@@
 \end{equation}
-The activation of each entry is given by a linear-combination of activations from the previous layer, as outlined in eqn.(\ref{eqn-LinearTransform}) and eqn.(\ref{eqn-elementActivation}).
+The activation of each entry is given by a linear-combination of activations from the previous layer, Eq.(\ref{eqn-LinearTransform}) and the transformation in Eq.(\ref{eqn-elementActivation}).
 
@@
 Then the weighting-matrix, $W^{(l)}$ has shape $m \times n$, the bias-vector $b^{(l)}$ has shape $m \times 1$.
-We can denote the function in a similar manner to eqn.(\ref{eqn-altLayerFunction}) as:
+We can denote the function in a similar manner to Eq.(\ref{eqn-altLayerFunction}) as:
 \begin{equation}
@@
 \end{equation}
-Eqn. (\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}.
+Eq.
+(\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}.
+\textcolor{red}{How Do I finish this section?
+Uses of Dens layer, physical meaning?}
 
@@
 Note that convolution is commutative: $(A * B) = (B * A)$.
-We implement a convolutional layer $f^{(l)})$, by creating a series of $K$ weighting matrices, called \textit{filters}, each of size $m \times n$, where $m,n \in \mathbb{Z}$.
+We implement a convolutional layer $f^{(l)}$ by creating a series of $K$ weighting matrices, called \textit{filters}, each of size $m \times n$, where $m,n \in \mathbb{Z}$.
 Often we choose $m = n$ and call the shape the \textit{convolution kernel size} \cite{Loy, Goodfellow}.
 
-\paragraph*{}In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(N \times M)}$, the convolutions filters "step" through the input data and repeatedly compute the element-wise product of each $m \times n$ weighting kernel, and the local activation of the $x^{(l-1)}$ array.
+\paragraph*{}In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(N \times M)}$, the convolutions filters "step" through the input data and repeatedly compute the element-wise product of each $m \times n$ weighting kernel, and the local activations of the $x^{(l-1)}$ array.
 The step size in each of the 2-dimension is known as the \textit{stride}.
 Each of the $K$ filters are used to generate a $m \times n$ feature map from the input activation.
-For an appropriately trained network, some filters may be dedicated to detecting vertical lines, horizontal lines, sharp edges, areas of mostly one color, etc.
+For an appropriately trained network, some filters may result in detecting vertical lines, horizontal lines, sharp edges, areas of mostly one color, etc.
 \cite{Geron,Loy}.
@@
 \end{equation}
-As an example, consider a single filter map over input $x \in \mathbb{R}^{(4 \times 3)}$ and filter map $W \in \mathbb{R}^{(2 \times 2)}$ as shown in fig. (\ref{fig-2DConvExample}):
+As an example, consider a single filter map over input $x \in \mathbb{R}^{(4 \times 3)}$ and filter map $W \in \mathbb{R}^{(2 \times 2)}$ as shown in Fig. (\ref{fig-2DConvExample}):
 \begin{figure}[H]
-\label{fig-2DConvExample}
 \begin{center}
@@
 \caption{The result of convolving an input (a) with an filter map (b) is a new set of activations (c). This Image was adapted from Goodfellow, pg. 325 \cite{Goodfellow}}
+\label{fig-2DConvExample}
 \end{figure}
@@
 \subsubsection{2-Dimensional Maximum Pooling Layer}
+\label{subsubsec-2DPool}
 
@@
 Using the $2 \times 2$ kernel on the $3 \times 4$ input, each box would then contain the maximum value of the input activations.
-We detail this in fig.
+We detail this in Fig.
 (\ref{fig-2DMaxPool}):
@@
 \subsubsection{1-Dimensional Flattening Layer}
+\label{subsubsec-1DFlatten}
 
 \paragraph*{}A flattening layer is used to compress an array with two or more dimensions down into a single dimension.
-For a flattening layer $l$, multidimensional activations in layer $l-1$ are compressed down into a single dimensional array.
+For a flattening layer $l$, multidimensional activations in layer $l-1$ are rearranged down into a single dimensional array.
+Note that this is not like projecting the data into a lower dimension, but rather is simple the reorganization of values into an array of a single axis.
 We can use function notation to express this as:
@@
 The numerical value of each activation is left unchanged.
-For a layer with activation shape$N \times M$, the resulting activations are reshaped into $NM \times 1$ as shown in eqn (\ref{eqn-FlattenFunction}).
+For a layer with activation shape$N \times M$, the resulting activations are reshaped into $NM \times 1$ as shown in Eq.(\ref{eqn-FlattenFunction}).
 
@@
 \subsubsection{1-Dimensional Concatenation Layer}
+\label{subsubsec-1DConcat}
 
@@
 \end{equation}
-The result of the concatenation is a new 1D-array, $\vec{c}^{(l)}$ with size $1 \times \alpha\beta$:
+The result of the concatenation is a new 1D-array, $\vec{c}^{(l)}$ with size $1 \times \alpha + \beta$:
 \begin{equation}
@@
 f^{(l)} : x^{(l-1)}_{a} \in \mathbb{R}^{(1 \times \alpha)} , x^{(l-1)}_{b} \in \mathbb{R}^{(1 \times \beta)} , ....  \rightarrow
-x^{(l)}_{z} \in \mathbb{R}^{(1 \times \alpha\beta...)}
+x^{(l)}_{z} \in \mathbb{R}^{(1 \times \alpha + \beta + ...)}
 \end{equation}
@@
 As discussed in sec.
-(\ref{sec-Training}) a layer function, $f^{(l)}$ is generally composed of a linear transformation, as in eqn.
-(\ref{eqn-LinearTransform}), and then an element-wise activation function as in eqn.
+(\ref{sec-Training}) a layer function, $f^{(l)}$ is generally composed of a linear transformation, as in Eq.
+(\ref{eqn-LinearTransform}), and then an element-wise activation function as in Eq.
 (\ref{eqn-elementActivation}).
@@
 \end{equation}
-ReLU is only defined on a real domain. We provide a visualization of the function in fig. (\ref{fig-ReLU}).
+ReLU is only defined on a real domain. We provide a visualization of the function in Fig. (\ref{fig-ReLU}).
 \begin{figure}[H]
+\begin{center}
+\includegraphics[scale=0.2]{../Figures/RectifiedLinearUnit}
+\end{center}
+\caption{Rectifed Linear Unit (ReLU) activation function}
 \label{fig-ReLU}
-\begin{center}
-\includegraphics[scale=0.2]{../Figures/RectifiedLinearUnit}
-\end{center}
-\caption{Rectifed Linear Unit (ReLU) activation function}
 \end{figure}
@@
 \subsubsection{Softmax}
+\label{subsubsec-Softmax}
 
@@
 \label{eqn-Softmax}
-\text{Softmax}\big[ x \big]_{i} = \frac{1}{\sum_{j}e^{x_j}}e^{x_i}
+\text{Softmax}\big[ x \big]_{i} = \frac{e^{x_i}}{\sum_{j}e^{x_j}}
 \end{equation}
@@
 \paragraph*{}This function is almost only used in the output layer of a neural network, and encodes a discrete categorical probability.
-For example, if eqn.(\ref{eqn-Softmax}) returns a vector of the form: $[ 0.75 , 0.25]$, we interpret this as a sample having a $75\%$ chance of beloinging to class $0$ and a $25\%$ change of belonging to class $1$.
+For example, if Eq.(\ref{eqn-Softmax}) returns a vector of the form: $[ 0.75 , 0.25]$, we interpret this as a sample having a $75\%$ chance of beloinging to class $0$ and a $25\%$ change of belonging to class $1$.
 
@@
 Note that $W^{(l)}$ or $b^{(l)}$, itself is a parameter to train, but rather the entries that make up those structures must be trained.
-In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow}.
+Certain layers, such as pooling layers (\ref{subsubsec-2DPooling}), concatenation layers (\ref{subsubsec-1DConcat}), or flattening layers (\ref{subsubsec-1DFlatten}) do not contain any trainable parameters.
+Similarly, activation functions themselves are static and are not included in the list of parameters.
+
+\paragraph*{}In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow,Levine}.
 
@@
 \paragraph*{}$J(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}.
-For this $k$-classes classification task, we choose to use a \textit{Categorical Crossentropy} (CXE) cost function.
-For a single predictions sample, it is defined \cite{Goodfellow}:
-\begin{equation}
-\label{eqn-CategoricalCrossentropy}
-\text{CXE}\big[ y^* , y \big] = - \sum_{i=0}^{k-1} y^*_i \log_{10}(y_i) 
-\end{equation}
+For this $k$-classes classification task, we choose to use the \textit{Categorical Crossentropy} (CXE) cost function.
+For a sample labeled by the one-hot-encoded vector $y$ and corresponding prediction vector $y^*$, the CXE cost is given by \cite{Goodfellow,Virtanen}:
+\begin{equation}
+\label{eqn-CXELoss}
+\text{CXE}\big[ y^* , y \big] = - \sum_{i=0}^{k-1} y_i \log_{10}(y^*_i) 
+\end{equation}
+
+\paragraph*{}Suppose that a given sample belongs to class $j$ in a $k$-classes classifier.
+Since the label vector, $y$ is one-hot-encoded, all entries are zero except $y_{j} = 1$.
+Thus the sum in Eq.
+(\ref{eqn-CXELoss}) contains mostly zero terms.
+Similarly, the network output $y^*$ has only values between $0$ and $1$, due to the softmax activation function (\ref{subsubsec-Softmax}) in the output layer.
+Taking the logarithm results a negative quantity.
+The smaller the value for $y^*_j$, the larger the difference between corresponding indicies and the larger the mangitude of the cost.
+We multiply the sum by $-1$ to make all values positive.
+
+\begin{figure}[h]
+\begin{center}
+\textcolor{red}{Plot of CXE goes here}
+%\includegraphics[scale=0.2]{•}
+\end{center}
+\caption{Plot of how $y^*_{j}$ affects the output values of the CXE cost function}
+\label{fig-CXELoss}
+\end{figure}
+
+\paragraph*{}When $y^*_j \approx y_j$, we compute a small cost value, and when $y^*_j << y_j$ we find a large cost value.
+We visualize this relationship in Fig.
+(\ref{fig-CXELoss}).
 In practice, this operation is performed over a batch of samples and an average is computed and used a \textit{batch loss} \cite{Goodfellow}.
@@
 \begin{quote}
-In most learning scenarios, we care about some performance measure $P$,... We reduce a different cost function, $J(\theta)$ in the hope that doing so will also imprvce $P$.
+In most learning scenarios, we care about some performance measure $P$,... We reduce a different cost function, $J(\theta)$ in the hope that doing so will also improve $P$.
 \end{quote}
-By choosing an appropriate cost function, and selecting the parameters $\Theta$ that minimize the average cost over a data set, we also assume that doing so minimized the error in the performance $P$.
+By choosing an appropriate cost function, and selecting the parameters $\Theta$ that minimize the average cost over a data set, we also assume that doing so minimizes classification error and maximizes the performance $P$.
 
 \paragraph*{}The cost of a sample is dependent on training labels $y$ and the network output $y^*$.
-The output is given by the final layer activation $x^{(L-1)}$, which in turn are produced by the previous layer and so forth, as demonstrated in eqn.
+The output is given by the final layer activation $x^{(L-1)}$, which in turn are produced by the previous layer and so forth, as demonstrated in Eq.
 (\ref{eqn-altLayerFunction}), This recursive nature combined with the dimensionality of the parameter object $\Theta$ makes an analytical solution to the optimization impractical \cite{Geron,Goodfellow,James}.
-We instead optimize with a gradient-based method.
-
-\paragraph*{}We can reduce the cost given a set of paramaters, $J(\Theta)$, by moving each element in $\Theta$ with small steps in the direction of the negative partial derivative of each parameter.
+We instead optimize the cost function with a gradient-based method.
+
+\paragraph*{}We can reduce the cost given a set of parameters, $J(\Theta)$, by moving each element in $\Theta$ with small steps in the direction of the negative partial derivative of each parameter.
 In the case of the high-dimensional $\Theta$ object, we compute the partial derivative with respect to each weight and bias in the form of the \textit{gradient vector}.
@@
 
-\paragraph*{}Due to the nested composition of the network output in eqn.
-(\ref{eqn-FunctionChain}), and subsequently the cost itself, we must use the chain rule of calculus to work backwards through the neural network to compute the partial derivative with respect to each parameter in $\Theta$.
+\paragraph*{}Due to the nested composition of the network output in Eq.
+(\ref{eqn-FunctionChain}), and subsequently the cost itself, we must use the chain rule of calculus to work backwards through computational graph of the neural network to compute the partial derivative with respect to each parameter in $\Theta$.
 The process of working backwards to compute each element in the gradient vector is called \textit{back-propagation} \cite{Geron}.
-Below we detail an algorithm in pseudo-code to back-propagate through a fully-connected nueral network, such as the multilayer perceptron outlines in sec.(\ref{sec-NetworkStructre})
+Below we detail an algorithm in pseudo-code to back-propagate through a fully-connected neural network, such as the multilayer perceptron outlines in sec.(\ref{sec-NetworkStructre})
 
@@
 $dx \leftarrow \nabla_{(y^*)}J(y,y^*)$ \\
-Intialize $\nabla J$ as output object, should have same shape as $\Theta$
+Initialize $\nabla J$ as output object, should have same shape as $\Theta$
 
@@
 
-\paragraph*{}After (i) computing the gradient, we can scale is by a desired learning rate, $\alpha$ and (ii) add it element-wise to the exisitint elements in $\Theta$.
-By repeating steps (i) and (ii) in sucession, we gradually drive the cost function to produces consistently lower and lower values.
+\paragraph*{}After (i) computing the gradient, we can scale is by a desired learning rate, $\alpha$ and (ii) add it element-wise to the existing elements in $\Theta$.
+By repeating steps (i) and (ii) in succession, we gradually drive the cost function to produces consistently lower and lower values.
 This is called \textit{gradient descent} and is the basis for many optimization algorithms.
-We show the general update rule on iteration $(i)$ for gradient based learning over a batch of $m$ samples in eqn.
+We show the general update rule on iteration $(i)$ for gradient based learning over a batch of $m$ samples in Eq.
 (\ref{eqn-GradientLearning}).
@@
 \textcolor{blue}{I need to clean this sub-subsection up as well. The optimizer needs a better introduction and justification}
+
+\paragraph*{}Standard gradient-based learning, as given by the parameter update rule in Eq.
+(\ref{eqn-GradientLearning}) is cumbersome and often prone to numerical error.
+This includes phenomena where very small changes can compound and produce undesired effects such as \textit{vanishing} or \textit{exploding} gradients \cite{Geron,Goodfellow,Loy}.
+To combat this, many gradient-based optimizers have been developed over the years to mitigate some f these vulnerabilities.
 
@@
 These two activation vectors are concatenated into a single new dense layer, and then passed through one final layer to generate the model's final output.
-A visual representation of this architecture can be found in fig.
+A visual representation of this architecture can be found in Fig.
 (\ref{fig-NetworkArchitecture}).
@@
 
-\paragraph*{}The spectrogram branch is pictured on the left side of fig.
+\paragraph*{}The spectrogram branch is pictured on the left side of Fig.
 (\ref{fig-NetworkArchitecture}).
@@
 
-\paragraph*{} The Perceptron branch is picture on the right side of fig.
+\paragraph*{} The Perceptron branch is picture on the right side of Fig.
 (\ref{fig-NetworkArchitecture}), notice that it is considerably smaller in side and complexity than it's neighbor.
@@
 \end{equation}
-Where $\mathbb{W}$ is the DFT matrix from eqn.
-(\ref{eqn-DFTMatrix}) and $\widetilde{A}^T$ is the transpose of the analysis frames matrix from eqn.
+Where $\mathbb{W}$ is the DFT matrix from Eq.
+(\ref{eqn-DFTMatrix}) and $\widetilde{A}^T$ is the transpose of the analysis frames matrix from Eq.
 (\ref{eqn-WindowMatrix}).
 The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of real floating-point numbers.
-We can index matrix $S$ similarly to that of matrix $A$ in eqn.
+We can index matrix $S$ similarly to that of matrix $A$ in Eq.
 (\ref{eqn-IndexingA}):
@@
 This is done to ensure that each  row is now an analysis frame, each column is a frequency bin.
-This gives a similar structure to the time-space analysis frames matrix, $A$, in eqn.
+This gives a similar structure to the time-space analysis frames matrix, $A$, in Eq.
 (\ref{eqn-FrameMatrix}).
@@
 Similarly, each column of the matrix $M$ is a appropriately scaled Mel filter-bank.
-This way, the matrix product in eqn.
+This way, the matrix product in Eq.
 (\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
@@
 \end{equation}
-Where $\widetilde{B}$ are the column average of the Mel filter bank energies computed in eqn. (\ref{eqn-FilterBanks}), and $R$ is the number of filter banks used.
+Where $\widetilde{B}$ are the column average of the Mel filter bank energies computed in Eq. (\ref{eqn-FilterBanks}), and $R$ is the number of filter banks used.
 

### 2020-11-07 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Update to Instrument Properties

@@
 The axes, in order of indexing, represent (i) the size of the \textit{mini-batch} of samples, (ii) the number of features for each sample.
-We use the same model hyper-paramater of $64$ samples per batch, and have developed $20$ unique classification features that have been derived from time-space and frequency-space representations of the audio file data.
+We use the same model hyper-parameter of $64$ samples per batch, and have developed $20$ unique classification features that have been derived from time-space and frequency-space representations of the audio file data.
 We can denote the 2D shape if the input object into this branch as:
@@
 \textcolor{red}{I have notes written out for this section, I just need to write it out here soon}
+
+\paragraph*{}As discussed in Sec.
+(\ref{sec-TheNeuralNetwork}), performance quality of a neural network is greatly dependent on the properties of the chosen features \cite{Virtanen,Liu}.
+To ensure that a the classifier model performs adequately and consistently, we must choose these features to have high variance between classes, and low variance within each class.
+This enables a neural network to development clear decision boundaries between each unique class \cite{James,Serizel}.
+To develop this set of features, we explore the physical and mechanical properties of musical instruments and the sounds that they create.
+
+\paragraph*{}Rather than explore each class individually,
 

### 2020-11-08 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Instrument Properties Section

@@
 \usepackage{xcolor}
+
+\usepackage{multicol}
 
@@
 
-\textcolor{red}{I have notes written out for this section, I just need to write it out here soon}
-
 \paragraph*{}As discussed in Sec.
@@
 
-\paragraph*{}Rather than explore each class individually,
+\paragraph*{}We have assembled training data samples than can be grouping in 38 classes of unique sources listed below:
+\begin{multicols}{2}
+\begin{enumerate}
+	\item Alto Flute
+	\item Alto Saxophone
+	\item Banjo
+	\item Bass
+	\item Bass Clairnet
+	\item Bass Flute
+	\item Bassoon
+	\item Bass Tromobe
+	\item B$\flat$ Clarinet
+	\item Bells
+
+	\item Cello
+	\item Clarinet \textcolor{blue}{Check this!}
+	\item Contrabassoon
+	\item Crotale
+	\item E$\flat$ Clarinet
+	\item English Horn
+	\item Flute
+	\item Guitar
+	\item Hi-Hat
+	\item Horn
+		\columnbreak
+	\item Mandolin
+	\item Marimba
+	\item Oboe
+	\item Sawtooth Wave
+	\item Saxophone (Tenor)
+	\item Sine Wave
+	\item Soprano Saxophone
+	\item Square Wave
+	\item Tenor Trombone
+	\item Triangle Wave
+
+	\item Trombone
+	\item Trumpet (B$\flat$)
+	\item Tuba
+	\item Vibraphone
+	\item Violin
+	\item Viola
+	\item White Nosie
+	\item Xylophone
+	\item
+	\item
+\end{enumerate}
+\end{multicols}
+
+\paragraph*{}Rather than explore each class individually, we can examine the properties of groupings of musical instrumentsby using the \textit{Hornbostel-Sachs} system \textit{red}{Citation needed!}.
+In this syetem, musical instruments or sound sources can be divided up into four broad categories based on the nature of the sound-producing material.
+These categories are (i) Idiophones, (ii) membranophones, (iii) Chordophones, and (iv) aerophones.
+In this section, we explore the mechanical properties of each group and show how the physics of the source instrument influences our feature choice.
+
+% ================================================================
+
+\subsection*{Idiophones}
+\label{subsec-Idiophone}
+
+\paragraph*{}An idiophone is an instrument that produces sound through the vibration of the full body of the object.
+This generally includes most percussive instruments excluding drums \textcolor{red}{citation needed}.
+From the set of classes that we use, bells, crotales, Hi-hats, vibraphones, and xylophones are all examples of idiophones.
 

### 2020-11-08 SignalClassifier-Postprocessing/FeatureProperties/FeaturePropertiesMain.py
Added BoxPlots of Features

@@ -19,9 +19,9 @@ if __name__ == '__main__':
 
     # Initialize Directories
     parentPath = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis"
-    mtrxPath = os.path.join(parentPath,"FeatureData\\Features1\\Matrix1.csv")
-    exptPath = os.path.join(parentPath,"FeatureData\\Features1")
-    encdPath = os.path.join(parentPath,"SignalClassifier-CrossValidation\\XVal-Output-Data\\FeaturesXVal")
+    mtrxPath = os.path.join(parentPath,"FeatureData\\Features2\\Matrix2.csv")
+    exptPath = os.path.join(parentPath,"FeatureData\\Features2")
+    encdPath = os.path.join(parentPath,"SignalClassifier-CrossValidation\\XValCLFB-Output-Data")
 
     # Get Raw Datas
     inputFrame = pd.read_csv(mtrxPath,header=0).to_numpy()
@@ -29,7 +29,7 @@ if __name__ == '__main__':
     y = inputFrame[1:,1].astype(np.int16)
 
     # Organize Data
-    n_classes,n_features = 33,40
+    n_classes,n_features = 38,20
     Processor = utils.FeatureProcessor(X,y,n_classes,n_features)
     Processor.CreateDictionary(encdPath)
     Processor.__Call__(exptPath)

### 2020-11-08 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisMAIN.py
Updated Classifier Analysis to Work for X-Validation

@@ -19,32 +19,16 @@ import AnalysisUtilities as utils
         
 if __name__ == '__main__':
 
+    # Establish local Directory Paths
     parent = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\SignalClassifier-CrossValidation"
-    dataPath = os.path.join(parent,"XVal-Output-Data")
+    dataPath = os.path.join(parent,"XValCLFB-Output-Data")
+    exptPath = os.path.join(parent,"XValCLFB-Analysis")
+    modelName = "XValCLFB"
+    n_classes = 38
 
-    models = ["ChaoticXVal","FeaturesXVal"]
-    n_classes = 33
-
-
-    infiles = ["ChaoticXVal1@PREDICTIONS@2020.10.19.22.03.30.032221.csv",
-               "FeaturesXVal1@PREDICTIONS@2020.11.01.01.31.42.020625.csv"]
-
-    infiles = [file for file in os.listdir(dataPath) if ("@PREDICTIONS@" in file)]
-
-    export = os.path.join(parent,"Confusions")
-
-    for file in infiles:
-        modelName = file.split("@")[0]
-        Program = utils.AnalyzeModels(modelName,dataPath,file,n_classes)
-        Program.__Call__()
-
-        """
-        os.chdir(export)
-        utils.ClassifierMetrics.ExportConfusion(Program.weightedConfusion,modelName+" Weighted Confusion",export)
-        utils.ClassifierMetrics.ExportConfusion(Program.standardConfusion,modelName+" Standard Confusion",export)
-
-        utils.ClassifierMetrics.PlotConfusion(Program.weightedConfusion,33,modelName+" Weighted Confusion")
-        utils.ClassifierMetrics.PlotConfusion(Program.standardConfusion,33,modelName+" Standard Confusion")
-        """
-
+    # Run Main program
+    Program = utils.AnalyzeModels(modelName,dataPath,n_classes)
+    Program.__Call__()
+    Program.ExportMetrics(exptPath)
+    
     print("=)")

### 2020-11-09 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Properties of Musical instruments

@@
 	\item Viola
-	\item White Nosie
+	\item White Noise
 	\item Xylophone
@@
 In this syetem, musical instruments or sound sources can be divided up into four broad categories based on the nature of the sound-producing material.
-These categories are (i) Idiophones, (ii) membranophones, (iii) Chordophones, and (iv) aerophones.
+These categories are (i) idiophones, (ii) membranophones, (iii) chordophones, and (iv) aerophones.
 In this section, we explore the mechanical properties of each group and show how the physics of the source instrument influences our feature choice.
@@
 
-\subsection*{Idiophones}
+\subsection{Idiophones}
 \label{subsec-Idiophone}
@@
 % ================================================================
+
+\subsection{Membranophones}
+\label{subsec-membranophones}
+
+% ================================================================
+
+\subsection{Chordophones}
+\label{subsec-chordophones}
+
+\paragraph*{}A chordophone is a musical instrument that produces sound through the vibration of strings that are stretched between two fixed points \textcolor{red}{citation needed}.
+From our data set, banjos, basses, cellos, guitars, mandolins, violins, and violas are all examples of chordophones.
+
+\paragraph*{}We can model a chordophone simply as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$.
+The string is flexible, and free to vibrate in a single dimension.
+We describe the state of string over space and time with a function $U(x,t)$.
+The behavior of the string can be  modeled by D'Alembert's 1-dimensional wave equation \cite{Haberman,Taylor}:
+\begin{equation}
+\label{eqn-1DWaveEqn}
+\frac{\partial^2 U}{\partial t^2} = v^2 \frac{\partial^2 U}{\partial x^2}
+\end{equation}
+Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$. Additionally, the string is fixed in place at both ends, which can be modeled by the boundary conditions:
+\begin{equation}
+U(0,t) = 0 
+	\text{\hspace*{2cm} and \hspace*{2cm}}
+U(L,t) = 0 
+\end{equation}
+
+\paragraph*{}In order to specify a solution, we must also specificy two intitial conditions. We described the initial state of the string at time $t = 0$  by the two conditions:
+\begin{equation}
+U(x,0) = f(x) 
+	\text{\hspace*{2cm} and \hspace*{2cm}}
+\frac{\partial U}{\partial t}(x,0) = g(x)
+\end{equation}
+Depending on the exact nature of the source instrument, $f(x)$ and $g(x)$ can take on different forms.
+For example, for plucked stringed instruments, $f(x)$ may appear to be as triangle-like function, with a peak at some position $0 < x_0 < L$ where then string was struck.
+$g(x)$
+
+\paragraph*{}We explore solutions that take the form \cite{Haberman}:
+\begin{equation}
+U(x,t) = \psi(x)h(t)
+\end{equation}
+Because of the linear nature of the wave equation, Eq. (\ref{eqn-1DWaveEqn}), a linear combination of solutions is also a solution, so we can express $U(x,t)$ as \cite{Haberman}:
+\begin{equation}
+U(x,t) = 
+\sum_{n=1}^{\infty} \bigg( A_n \sin\big(\frac{n\pi x}{L}\big)\cos\big(\frac{n\pi vt}{L}\big)
++ B_n \sin\big(\frac{n\pi x}{L}\big)\sin\big(\frac{n\pi vt}{L}\big) \bigg)
+\end{equation}
+The initial conditions are satisfied if:
+\begin{equation}
+\begin{array}{ll}
+    f(x) = \sum_{n=1}^{\infty} A_n \sin\big(\frac{n\pi x}{L}\big) \\
+    g(x) = \sum_{n=1}^{\infty} B_n\big(\frac{n\pi v}{L}\big)
+    			\sin\big(\frac{n\pi x}{L}\big)
+\end{array} 
+\end{equation}
+Where $A_n$ and $B_n$ are given by:
+\begin{equation}
+\begin{array}{ll}
+    A_n = \frac{2}{L} \int_{0}^{L} f(x) \sin\big(\frac{n\pi x}{L}\big) dx \\
+    B_n = \frac{2}{n\pi v} \int_{0}^{L} g(x) \sin\big(\frac{n\pi x}{L}\big) dx \\
+\end{array} 
+\end{equation}
+
+\paragraph*{}Examining the solutions for $U(x,t)$ indicates that under the right initial conditions, chordophones vibrate with all harmonics present.
+
+% ================================================================
+
+\subsection{Aerophones}
+\label{subsec-Aerophones}
+
+% ================================================================
+
+\subsection{Other Generated Sounds}
+\label{subsec-Generated}
+
+\paragraph*{}We group sounds produced from non-physical musical instruments in this final category.
+Form our data set, this category includes the four simplest waveforms, (i) sine waves, (ii) sawtooth waves, (iii) square waves, and (iv) triangle waves, as well as any color noises \cite{White}.
+Since these sounds are only produced synthetically through a MATLAB program, we choose not to include them in the Hornbostel-Sachs grouping above.
+We explore the properties of each of these generated sounds.
+
+% ================
+
+\subsubsection{Sine Wave}
+
+\paragraph*{}A sine wave is the simplest of sound waves, and makes up the foundation for all periodic wave forms \cite{White,Virtanen}.
+It consists of a single oscillatory term with a fixed fundamental frequency $f_0$.
+A sine wave's amplitude as a function of time is given by
+\begin{equation}
+\label{eqn-SineWave}
+x(t) = A_0 \sin(2\pi f_0 t + \phi)
+\end{equation}
+Where $A_0$ gives an amplitude, $f_0$ is the fundamental frequency, and $\phi$ is a phase shift. We show a simple sine wave in the time and frequency domain in Fig. (\ref{fig-SineWave}).
+
+\begin{figure}[h]
+\begin{center}
+	\textit{[Image of Sine Wave Waveform]}
+	\textit{[Image of Sine Wave Freq. Spect]}
+\end{center}
+\caption{A sine wave in the (a) time-domian and (b) frequency domain}
+\label{fig-SineWave}
+\end{figure}
+
+\paragraph*{}A pure sine wave contains no overtones, only a time-independent fundamental frequency, which can take on any value due to synthetic generation.
+
+% ================
+
+\subsubsection{Sawtooth Wave}
+
+\paragraph*{}
+
+% ================
+
+\subsubsection{Square Wave}
+
+\paragraph*{}A square wave is a piece-wise defined waveform whose value alternatively alternates between $+1$ and $-1$ \cite{White,Olsen}.
+A square wave with period $f_0$ has a waveform defined over a single period as:
+\begin{equation}
+\label{eqn-SquareWave}
+x(t) =  \left\{
+\begin{array}{ll}
+    +1 & \text{\hspace{0.5cm}} 0 < x \leq T_0 / 2 \\
+    -1 & \text{\hspace{0.5cm}} T_0/2 < x < T_0
+\end{array} 
+\right.
+\end{equation}
+where $T_0 \equiv 1/f_0$.
+
+\paragraph*{}We can use Fourier decomposition to examine the constituent sinusoidal wave that make up a square wave.
+The frequency space representation of a square wave indicates that is can be approximated as a sum of higher odd-numbered harmonics, with the amplitude of each decreasing by the reciprocal of the harmonic number \cite{White}.
+Thus a square wave in the time domain can be approximated as:
+\begin{equation}
+x(t) \approx \sum_{n = 1}^{\infty} \frac{1}{2n-1} \sin \bigg( 2 \pi (2n - 1)f_0 t \bigg)
+\end{equation}
+
+\begin{figure}[h]
+\begin{center}
+	\textit{[Image of Square Wave Waveform]}
+	\textit{[Image of Sqaure Wave Freq. Spect]}
+\end{center}
+\caption{A square wave in the (a) time-domain and (b) frequency domain}
+\label{fig-SquareWave}
+\end{figure}
+
+% ================
+
+\subsubsection{Triangle Wave}
+
+% ================
+
+\subsubsection{White Noise}
+
+% ================================================================
 % ================================================================
@@
 
-\paragraph*{}Audio machine learning researchers M.
-Kashif Saeed Khan and Wasfi G.
-Al-Khatib discuss the vitality of feature selection \cite{Khan}: \textcolor{red}{I'm not sure how to introduce the importance of feature extraction}
+\paragraph*{}Classification tasks require a set of inputs that are used to make the decision as to which class the sample belongs to.
+These inputs are called \textit{predictors} or \textit{features} \cite{James,Loy,Serizel}.
+Features are quantitative, low-dimensional representations of each sample that convey key characteristics of the sample.
+Audio machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib discusses the vitality of feature selection \cite{Khan}:
 \begin{quote}
@@
 
-\paragraph*{}It becomes quickly apparent that the choice of features is extrodinarily important to the process of training and evaluation of the classifier model.
+\paragraph*{}It becomes quickly apparent that the choice of features is extraordinarily important to the process of training and evaluation of the classifier model.
 Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels.
@@
 These features are derived are principles of music, digital signal processing, previous work, and underlying physics that governs the behavior of instruments.
-In the following sections, we outline the set of $21$ features used in the classification process
+In the following sections, we outline the set of $21$ features used in the classification process.
+For each feature, we visualize the distribution in across each class in the form as box-plots.
+Each feature has been normalize to have a zero mean, and unit-variance acorss all classes.
 
@@
 
-\subsection{The Bagging Technique}
+\subsection{Boosted Aggregation}
 \label{subsec-Bagging}
@@
 \paragraph*{}Many learning models such as neural networks, or decision trees suffer from \textit{high variance} \cite{James}.
-This means that randomly splitting a full dataset into halves and fitting two a different model to each half has the potential to produce wildly different fit parameters.
+This means that randomly splitting a full dataset into halves and fitting two different model to each half has the potential to produce wildly different fit parameters.
 In the case of neural networks, high variance can be amplified by the nature of the randomization in multidimensional optimizer \cite{Geron}.
-To mitagate this effect, we can employ a variant of the \textit{bagging} algorithm.
+To mitigate this effect, we can employ a variant of the \textit{bagging} algorithm.
 Bagging uses an average, or weighted average, of parameters in multiple models that have been trained on overlapping data sets.
 
-\paragraph*{}Consider if we have $k$ models, all trained on overlapping training/testing data sets:
-\begin{equation}
-\text{Models} = \Big\{ F^*_{0} , F^*_{1} , F^*_{2} , ... , F^*_{k-2} , F^*_{k-1} \Big\}
-\end{equation}
-Each model contains a corresponding set of paramaters, $\Theta_{i}$, $i \in [0,k-1]$.
-We could then aggregate the parameters according to a weighted average to create a new set of paramaters, $\Theta_{k}$ which can be used to construct a new model, $F^*_{k}$.
+\paragraph*{}Consider if we have $K$ models, all trained on overlapping training/testing data sets:
+\begin{equation}
+\text{Models} = \Big\{ F^*_{0} , F^*_{1} , F^*_{2} , ... , F^*_{K-2} , F^*_{K-1} \Big\}
+\end{equation}
+Each model contains a corresponding set of parameters, $\Theta^{i}$, $i \in [0,K-1]$.
+We could then aggregate the parameters according to a weighted average to create a new set of paramaters, $\Theta '$ which can be used to construct a new model, $F'$.
 
@@
 (\ref{subsec-XValidation}).
-This grants the $k$ models and corresponding parameters that could be used in the bagging technique \cite{James}.
-\textcolor{blue}{This is very not finished yet}
+This grants the $K$ models and corresponding parameters that could be used in the bagging technique \cite{James}.
+\textcolor{blue}{This is very not finished yet!}
 
@@
 
+\bibitem{Haberman}
+“Wave Equation: Vibrating Strings and Membranes.” \textit{Applied Partial Differential Equations with Fourier Series and Boundary Value Problems}, by Richard Haberman, Pearson, 2019, pp. 130–150.
+
 \bibitem{James}
@@
 Short, K. and Garcia R.A. 2006. "Signal Analysis Using the Complex Spectral Phase Evolution (CSPE) Method." AES: \textit{Audio Engineering Society Convention Paper}.
+
+\bibitem{Taylor}
+“Continuum Mechanics.” \textit{Classical Mechanics}, by John Robert Taylor, University Science Books, 2005, pp. 681–738.
 

### 2020-11-11 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex

@@
 
-\paragraph*{}We can model a chordophone simply as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$.
+\subsubsection{The 1-Dimension Vibrating String}
+
+\paragraph*{}We can model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$.
 The string is flexible, and free to vibrate in a single dimension.
@@
 \end{equation}
-Because of the linear nature of the wave equation, Eq. (\ref{eqn-1DWaveEqn}), a linear combination of solutions is also a solution, so we can express $U(x,t)$ as \cite{Haberman}:
+From this separation, we find that $\psi(x)$ and $h(t)$ each are composed of a linear combination of orthogonal trigonometric functions.
+Applying the boundary and initial conditions to the system allows for a linear combination of solutions \cite{Haberman}:
 \begin{equation}
@@
 
-\paragraph*{}Examining the solutions for $U(x,t)$ indicates that under the right initial conditions, chordophones vibrate with all harmonics present.
+\subsubsection{Consequences of the Wave Equation}
+
+\paragraph*{}The solution that we have derived from the wave equation shows that the behavior of $U(x,t)$ is greatly dependent on the nature of the string's initial shape, $f(x)$, when struck.
+In the case of picked or plucked instruments, the initial shape of $f(x)$ would be something like a "ramp function":
+\begin{equation}
+\label{eqn-RampFunc}
+f(x) = 
+\end{equation}
 
@@
 
-\paragraph*{}Before making predictions on unlabeled data such as the Chaotic Synthesizers, we must determine that our model performs reasonably on data that it has never interacted with.
+\paragraph*{}Before making predictions on unlabeled data such as the Chaotic Synthesizers, we must confirm that our model performs reasonably well on data that it has never interacted with.
 The most common practice is to divide a full data set into a subset of \textit{training} samples, and \textit{testing} samples.
@@
 
-\paragraph*{}Performance evaluations are most commonly implemented in the form of \textit{$K$-Fold Cross-Validation} (Also called X-val).
+\paragraph*{}Performance evaluations are commonly implemented in the form of \textit{$K$-Fold Cross-Validation} (Also called X-val) \cite{Geron,Goodfellow}.
 This process involves taking a data set containing $N$ unique samples and dividing it into $K$ non-overlapping subsets.
-$1$ subset is reserved to evaluate the model, and $K-1$ are used to train the model.
-This belongs a larger family of statisical validations called \textit{Resampling methods} \cite{James}.
+$1$ subset is reserved to evaluate the model, and $K-1$ remaining subsets are used to train the model.
+This belongs a larger family of statistical validations called \textit{Resampling methods} \cite{James}.
 Below, we detail pseudo-code for a $K$-Fold Cross Validation algorithm.
@@
 \REQUIRE Untrained Network or related learning algorithm, $F^*$
-\REQUIRE A full data set of $N$ samples. $X^{(i)}$, $i \in {0,1,2,...,N-1}$
+\REQUIRE A full labeled data set of $N$ samples. $X^{(i)}$, $i \in {0,1,2,...,N-1}$
 \REQUIRE Number of splits in Cross validation, $K$
@@
 	\item Set aside testing data subset
-	\item $X_{test} = x_{j}$
+	\item $X_{test} \leftarrow x_{j}$
 	\item Concatenate the remaining subsets into training data set
-	\item $X_{train} = x_{i \neq j}$
+	\item $X_{train} =\leftarrow x_{i \neq j}$
 	\item Train the model, $F^*$ with the $X_{train}$ data set
@@
 
-\paragraph*{}By using cross-validation, we gain a deeper understanding of the model to ensure that the model can be consistently trained.
-This also helps counteract the possibility that the model got very lucky or unlucky with a particular set of initial conditions \cite{Geron,James}.
+\paragraph*{}The output of cross validation is $K$ models that are all trained and evaluated on overlapping subsets of the full data.
+Each model $F^*$, shows one possible outcome of training the network.
+It has a corresponding set of learned parameters $\Theta^*$, as defined in Eq.
+(\ref{eqn-Theta}) that it uses to make any predictions.
 
@@
 
-\paragraph*{}In the case of the multi-category classifier, it is also important that we choose the appropriate metrics to evaluate our performance.
-While the neural network itself uses the cost function as it's sole performance metric to optimize, we also require a set of more human-readable functions.
-We introduce a set of functions and metrics than enable a more tangible interpretation of model performance.
-To evaluate a performance metric, we require a set of samples with ground truth labels, $y$, and a model's prediction for those labels, $y^*$.
+\paragraph*{}In the case of the multi-category classifier, it is important that we choose the appropriate performance metrics to confirm that the network is completeing it's assigned as as expected \cite{Geron}.
+While the neural network itself uses the cost function as it's sole objective to optimize, we also require a set of more human-readable functions.
+For example, a loss score of $1.075$ over a given subset of previously unseen samples provides us with no real information as to how well the network is performing at it's designed task.
+In this section, we introduce a set of functions and metrics than enable a more tangible interpretation of the model's performance.
+To evaluate any performance metric, we require a set of samples with ground truth labels, $y$, and a model's prediction for those labels, $y^*$ \cite{Goodfellow,James}.
 
@@
 
-\paragraph*{}The confusion matrix (also called a confusion table) is a very quick, often graphical model that can be used to show how a model performs over a subset of predictions.
+\paragraph*{}The confusion matrix (also called a confusion table) is a very quick, often graphical model that can be used to show how a classifier model performs over a subset of predictions.
 The general idea of this object is count the number of times class $i$ is predicted to be in class $j$, and vice-versa \cite{Geron}.
-If we see that these classes are being repeatedly \textit{confused} in the model's prediction process, then we must modify the model or features to account for it.
+If we see that these classes are being repeatedly \textit{confused} in the model's prediction process, then we can modify the model or features to account for it.
 
@@
 \begin{figure}[H]
-\label{fig-ConfMat}
+
 	\begin{subfigure}[h]{0.45\textwidth}
@@
 \caption{Example Confusion Matrices for $k$-classes tasks}
+\label{fig-ConfMat}
 \end{figure}
 
-\paragraph*{}We can also use a confusion matrix to define four useful quantities relating a prediction to it's label.
-Suppose a belongs to class $q$, with the prediction given by, $y^*$ and a label is given by, $y$:
-\begin{enumerate}
-\item \textbf{True-Positive}\\
-A sample is \textit{TP} if $y^* = q$ and $y = q$
-\item \textbf{True-Negative}\\
-A sample is \textit{TN} if $y^* \neq q$ and $y \neq q$ 
-\item \textbf{False-Positive}\\
-A sample is \textit{FP} if $y^* = q$ and $y \neq q$ 
-\item \textbf{False-Negative}\\
-A sample is \textit{FN} if $y^* \neq q$ and $y = q$
-\end{enumerate}
-\textcolor{red}{Check this!}
+\paragraph*{}The confusion matrix can be a cumbersome, so often it is useful to express the performance in terms of more concise quantities.
+For this we use \textit{accuracy score}, \textit{precision score}, and \textit{recall score}.
 
@@
 
-\paragraph*{}Precision score (also called \textit{specificity}) offers a more concise performance metric than a confusion metric.
+\paragraph*{}Precision score (also called \textit{specificity} or \textit{positive predictive value}) is the ratio of chosen elements to all relevant elements.
+This bounds precision to the range $(0,1)$, with a higher value more desirable.
 For a classifier with $k = 2$ unique classes, we define the precision score of a model as:
@@
 \end{equation}
-Where $TP$ is the number of \textit{true-positive}, and $FP$ is the number of false-positives predictions.
-For a $k$-classes confusion matrix, $C$, the precision score is given by the entry $C_{j,j}$ divided by the sum of column $j$:
+Where $TP$ is the number of \textit{true-positive}, and $FP$ is the number of false-positive predictions.
+For a $k$-classes confusion matrix, $C$, the precision score of a class $j$, is given by the entry $C_{j,j}$ divided by the sum of row $j$:
 \begin{equation}
 \label{eqn-KPrecision}
-\text{Prec}_j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{i,j}}
-\end{equation}
-For multi-class problems, the precision score is usually used as an average over all classes.
-
-\paragraph*{}
-\textcolor{red}{Physical Significance of Precision}
+\text{Prec}_j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{j,i}}
+\end{equation}
+For multi-class problems, we report the precision score as averaged over all $k$ classes.
+
+\paragraph*{}The quantity $TP + FP$ is a measurement of the total number chosen items in that class.
+Thus, the quantity precision gives the ratio of correct selections to all selections that were made.
+More intuitively, we can describe precision as the fraction of selected items that are relevant to the problem at hand \cite{Geron}.
 
@@
 
-\paragraph*{}Recall score (also called \textit{sensitivity}) also offers a more concise performance metric than a confusion metric.
+\paragraph*{}Recall score (also called \textit{sensitivity} or \textit{true positive rate}) also offers a more concise performance metric than a confusion metric.
 For a classifier with $k = 2$ unique classes, we define the recall score of a model as:
@@
 \end{equation}
-Where $TP$ is the number of \textit{true-positive}, and $FN$ is the number of false-negative predictions.
-For a $k$-classes confusion matrix, $C$, the precision score is given by the entry $C_{j,j}$ divided by the sum of row $j$:
+Where $TP$ is the number of \textit{true-positive}, and $FN$ is the number of \textit{false-negative} predictions.
+For a $k$-classes confusion matrix, $C$, the precision score of a class $j$ is given by the entry $C_{j,j}$ divided by the sum of column $j$:
 \begin{equation}
 \label{eqn-KRecall}
-\text{Recall}j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{j,i}}
-\end{equation}
-For multi-class problems, the recall score is also used as an average over all classes.
-
-\paragraph*{}
-\textcolor{red}{Physical Significance of Recall}
-
-% ================================
-
-\
+\text{Recall}_j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{i,j}}
+\end{equation}
+For multi-class problems, we report the precision score as averaged over all $k$ classes.
+
+\paragraph*{}The quantity $TP + FN$ is a measurement of the total number items in that class, independent of selection.
+Thus, the quantity recall gives the ratio of correct selections to all selectes that were made.
+More intuitively, we can describe recall as the fraction of relevant items that were selected \cite{Geron}.
+
+% ================================
+
+\subsubsection{Accuracy Score}
+
+\paragraph*{}Accuracy score, while not commonly used is the most intuitive of all of the performance metrics. It is the ratio of
 
@@
 \label{subsec-TrainingMetrics}
+
+\paragraph*{}A period of training is characterized by fitting the parameters $\Theta$ of a model $F^*$ to a set of data $X$ and corresponding labels $Y$ \cite{Goodfellow,Virtanen}.
+This is done by passing subsets of data, called \textit{mini-batches}, into the neural network for training.
+The average cost for the mini-batch is then used to compute the gradient vector $\nabla_{\Theta}J$, and subsequently update the model according to the optimizer chosen \cite{Geron,Goodfellow}.
+
+\paragraph{}We execute computation in batches to reduce the amount of memory required for the operation.
+Pushing a full data set through a model at one time would require more RAM than is usually available , thus repeated subset of data tend to avoid memory exhaustion errors.
+Additionally, every mini-batch used equates to one step in the optimizer update rule \cite{Goodfellow}.
+Thus, a single pass over a full data set allows for multiple iterations of the optimizer to reduce the value of the cost function.
+This can be combined with multiple passes over the full data set, called \textit{epochs} \cite{James,Loy}.
+
+\paragraph*{}Large mini-batches require lots of RAM, but prevent the model from being over-fit to to any one sample, or class of samples.
+Small mini-batches require less RAM, but often may bias the optimizer to over-fit the given samples, and make optimization unstable \cite{Geron,James}.
+To ensure that the model is optimizing properly, we can track how the metrics behave over a training period.
+This allows us to monitor the \textit{rate of convergence} of the model.
+If the cost function is dropping to quickly or slowly, this may indicate that the optimizer learning rate is too high or too low.
+This may lead to an over-fit or under-fit model, or indicate an inappropriate set of feature is being used \cite{Geron,Goodfellow}.
+In Some cases, it can be used to initiate \textit{early-stopping}, which halts training when a set of parameters are met.
+
+\paragraph*{}Given the high dimensionality of this model's parameter space,the large volume of sound files, and the large amount of RAM required to store the spectrogram matrix and the feature vector for each sample, we do not directly load the full data set into memory at once.
+Instead, we produce a large subset of the full data set of $256$ samples which we dub a \textit{mega-batch}.
+From this mega-batch, we produce the two deign matrices required for input, and load the corresponding labels.
+We then use a subset of this group as the \textit{mini-batches} for training.
+Each mini-batch contains $32$ samples.
+Once all mini-batches are fit, we discard the design matrices in the mega batch ans repeat for the next $256$ samples.
+
+\paragraph*{}Along each training step, we record the precision, recall, and loss scores.
+Our program stores these values locally in a \textit{training-history} file, which we can examine after the program completes.
+Below, we visualize the value of each metric score at each training epoch.
+
+\begin{figure}[h]
+\begin{center}
+%\includegraphics[scale=0.2]{•}
+\textcolor{red}{Loss Score Goes Here}
+\end{center}
+\caption{The loss function score decreases with each training step, indicating that optimization is performing correctly}
+\label{fig-LossScore}
+\end{figure}
+
+similarly, we can visualize the precision score and recall score at each training step.
+
+\begin{figure}[h]
+\begin{center}
+%\includegraphics[scale=0.2]{•}
+\textcolor{red}{Precision Score Goes Here}
+\textcolor{red}{Recall Score Goes Here}
+\end{center}
+\caption{The precision score (a) and recall score (b) increases with each training step}
+\label{fig-PrecisionRecallScores}
+\end{figure}
 

### 2020-11-12 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex

@@
 \end{quote}
-Without any human intervention, a model must update itself to improve it's performance at a give task a new information is presented to it.
+Without any direct human intervention, a model must update itself to improve it's performance at a give task a new information is presented to it.
 To do this, the model must be constructed with a training procedure in mind.
@@
 Each parameter is floating-point number, which is stored in a weight matrix $W^{(l)}$ or bias vector $b^{(l)}$.
-Each value for each parameter contributes to the output of the function.
-Note that $W^{(l)}$ or $b^{(l)}$, itself is a parameter to train, but rather the entries that make up those structures must be trained.
+Each value for each parameter contributes to the output of the function, thus indirectly influences the final layer activations.
+Note that $W^{(l)}$ or $b^{(l)}$, themselves are not parameters, but arrays of parameters to be trained.
 Certain layers, such as pooling layers (\ref{subsubsec-2DPooling}), concatenation layers (\ref{subsubsec-1DConcat}), or flattening layers (\ref{subsubsec-1DFlatten}) do not contain any trainable parameters.
@@
 
-\paragraph*{}In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow,Levine}.
+\paragraph*{}In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\Theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow,Levine}.
+For the network that we have designed in this project, there are roughly $33,000$ parameters across $20$ layers.
 
@@
 
-\paragraph*{}Suppose we pass a training sample, given by the feature-vector $x^{(0)}$, with an expected outcome given by the vector $y$, into the neural network.
-After the network finishes processing, it's output activations are given by the vector $x^{(L-1)}$, also noted at $y^*$.
+\paragraph*{}Suppose we pass a training sample, given by the feature-vector $x^{(0)}$, with an expected outcome given by the one-hot-encoded vector $y$, into the neural network.
+After the network finishes processing, it's output activations are given by the vector $x^{(L-1)}$, also noted as $y^*$.
 For a reasonably trained model, we expect the vector $y^*$ to be "similar" to $y$, indicating that with the provided data, the network has made a valid prediction.
@@
 
-\paragraph*{}To quantify the difference between the model's prediction, $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $J(y^*,y)$, to the network \cite{Goodfellow,James}.
+\paragraph*{}To quantify the difference between the model's prediction, $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $J(y^*,y)$, to the model \cite{Goodfellow,James}.
 The cost function, also called a \textit{loss} or \textit{objective} function, compares the neural networks output, $y^*$ and the expected output $y$.
-It returns a single value, usually a floating-point number which measures the \textit{poorness} of the prediction.
+It returns a single floating-point number which measures the \textit{poorness} of the prediction.
 A high cost value indicates a \textit{poor} prediction, and a low cost indicates a reasonable prediction.
@@
 For this $k$-classes classification task, we choose to use the \textit{Categorical Crossentropy} (CXE) cost function.
-For a sample labeled by the one-hot-encoded vector $y$ and corresponding prediction vector $y^*$, the CXE cost is given by \cite{Goodfellow,Virtanen}:
+For a sample labeled by the one-hot-encoded vector $y$ and corresponding prediction vector $y^*$, the CXE cost for a single sample is given by \cite{Goodfellow,Virtanen}:
 \begin{equation}
 \label{eqn-CXELoss}
-\text{CXE}\big[ y^* , y \big] = - \sum_{i=0}^{k-1} y_i \log_{10}(y^*_i) 
-\end{equation}
-
-\paragraph*{}Suppose that a given sample belongs to class $j$ in a $k$-classes classifier.
-Since the label vector, $y$ is one-hot-encoded, all entries are zero except $y_{j} = 1$.
+\text{CXE}\big[ y , y^* \big] = - \sum_{i=0}^{k-1} y_i \log_{10}(y^*_i) 
+\end{equation}
+Thus, the average loss over a mini-batch of $b$ samples is given:
+\begin{equation}
+\label{eqn-CXELossAvg}
+\big\langle \text{CXE}\big[ y , y^* \big]\big\rangle = 
+- \frac{1}{b}\sum_{n=0}^{b-1}\sum_{i=0}^{k-1} y_i^{(n)} \log_{10}(y^{*(n)}_i) 
+\end{equation}
+
+\paragraph*{}Suppose that a given sample belongs to class $j$ in a $k$-classes classifier. Since the label vector, $y$ is one-hot-encoded, all entries are zero except $y_{j} = 1$.
+\begin{equation}
+y = \big[y_0,y_1, ... , y_{j} , ..., y_{k-1} \big]^T  = 
+\big[0,0, ... , 1 , ...,0 \big]^T
+\end{equation}
 Thus the sum in Eq.
 (\ref{eqn-CXELoss}) contains mostly zero terms.
-Similarly, the network output $y^*$ has only values between $0$ and $1$, due to the softmax activation function (\ref{subsubsec-Softmax}) in the output layer.
-Taking the logarithm results a negative quantity.
-The smaller the value for $y^*_j$, the larger the difference between corresponding indicies and the larger the mangitude of the cost.
-We multiply the sum by $-1$ to make all values positive.
+The only non-zero term is the produce of $y_j$ and $\log_{10}(y^*_j)$.
+Since the vector $y^*$ has been subject to the softmax activation function, we must have $y^*_j \in [0,1]$.
+This means that taking the log of this value returns a negative number.
+Multiplying by negative number returns a high loss when the activation of $y^*_j$ is low and a low cost when $y^*_j \approx 1$.
+We visualize this relationship in Fig.
+(\ref{fig-CXELoss}):
 
@@
 \begin{center}
-\textcolor{red}{Plot of CXE goes here}
-%\includegraphics[scale=0.2]{•}
+\includegraphics[scale=0.25]{../Figures/CXELoss}
 \end{center}
@@
 
-\paragraph*{}When $y^*_j \approx y_j$, we compute a small cost value, and when $y^*_j << y_j$ we find a large cost value.
-We visualize this relationship in Fig.
-(\ref{fig-CXELoss}).
-In practice, this operation is performed over a batch of samples and an average is computed and used a \textit{batch loss} \cite{Goodfellow}.
+\paragraph*{}By optimizing the parameters $\Theta$ in the network model, we allow for the output of a consistently low cost function to be produced across all samples in the data set.
 
@@
 \paragraph*{}We have developed a method for quantifying the difference between a given output $y^*$ and an expected output $y$ with the inclusion of a cost function.
-For a trained neural network, we expect that samples consistently produce a low cost value, particularly on previous unseen inputs, which indicates that the model has appropriately \textit{generalized}.
+For a trained neural network, we expect that samples consistently produce a low cost value, particularly on previous unseen inputs, which indicates that the model has appropriately \textit{generalized} \cite{James,Loy}.
 The process of training the model is to choose the parameters in $\Theta$ that allows for this behavior of the cost function.
-We then treat the training process of a neural network as a higher dimensional \textit{optimization} problem.
+We then treat the training process of a neural network as a higher dimensional \textit{optimization} problem \cite{Goodfellow}.
 
@@
 
-\paragraph*{}After (i) computing the gradient, we can scale is by a desired learning rate, $\alpha$ and (ii) add it element-wise to the existing elements in $\Theta$.
-By repeating steps (i) and (ii) in succession, we gradually drive the cost function to produces consistently lower and lower values.
+\paragraph*{}After (i) computing the gradient, we can scale it by a desired learning rate, $\alpha$ and (ii) add the gradient vector element-wise to the existing elements in $\Theta$ object.
+By repeating steps (i) and (ii) in succession, we gradually drive the cost function to produces consistently lower and lower values across a data set \cite{Geron}.
 This is called \textit{gradient descent} and is the basis for many optimization algorithms.
@@
 
-\textcolor{blue}{I need to clean this sub-subsection up as well. The optimizer needs a better introduction and justification}
-
 \paragraph*{}Standard gradient-based learning, as given by the parameter update rule in Eq.
 (\ref{eqn-GradientLearning}) is cumbersome and often prone to numerical error.
-This includes phenomena where very small changes can compound and produce undesired effects such as \textit{vanishing} or \textit{exploding} gradients \cite{Geron,Goodfellow,Loy}.
-To combat this, many gradient-based optimizers have been developed over the years to mitigate some f these vulnerabilities.
+This can include phenomena such as \textit{vanishing gradients}, \textit{exploding gradients}, \textit{poor conditioning}, or unstable solution-spaces.
+\cite{Geron,Goodfellow,Loy}.
+To combat this, we require a more stable and robust optimizer than the bare gradient descent method.
+Many gradient-based optimizers have been developed over the years to mitigate some f these vulnerabilities.
 
 \paragraph*{}For this project, we employ an \textit{Adaptive-Moments} optimization algorithm, also called \textit{ADAM} for short.
-It is a powerful variant of algorithms with an adaptive learning rate.
-It tracks an exponentially decaying average of past gradients, as well as exponentially decaying average of past squared gradients \cite{Geron}.
+It is a powerful optimizer with uses adaptive learning rate and momentum parameter.
+ADAM tracks an exponentially decaying average of past gradients, as well as exponentially decaying average of past squared gradients \cite{Geron}.
 This produces a far more aggressive optimizer at a higher computational cost.
-For a given iteration $(i)$, The ADAM update is given:
+
+\paragraph*{}This means that as the cost function iterates through each step, the effect will tend to "snowball".
+If the previous step was found to reduce the cost function by a large or small amount, the step size for the previous step will update accordingly.
+Note that the upper index $(i)$ or $(i-1)$F gives an iteration index, while the upper iteration $i$ means to raise a value to the power of the iteration.
+For a given step $(i)$, The ADAM update is given:
 \begin{equation}
@@
 							\frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]  \\
-s'^{(i)} &= \frac{s^{(i)}}{1-\rho_1^t} \\
-r'^{(i)} &= \frac{r^{(i)}}{1-\rho_2^t} \\
+s'^{(i)} &= \frac{s^{(i)}}{1-\rho_1^i} \\
+r'^{(i)} &= \frac{r^{(i)}}{1-\rho_2^i} \\
 \Theta^{(i)} &= \Theta^{(i-1)} + (-\alpha)\frac{s'^{(i)}}{\sqrt{r'^{(i)}}+\delta} \\
@@
 
-\textcolor{red}{I need to include a bit more detail \& citations on the "hybrid / multimodal" nature of this need works. Updates to follow}
-
 \paragraph*{}The success of a neural network algorithm is enormously dependent of the strength of the chosen features, as well as a complementary architecture, rather than the quantity of available data \cite{Geron,Kahn,Liu}.
-We have derived an appropriate set of inputs arrays \textcolor{blue}{See Section on Features}, and constructed a neural network architecture to coincide with these features.
-From these two input arrays, one being a matrix and the other being a column-vector, we have produced a \textit{multimodal neural network}, that process the two inputs, and combines separate neural networks into a single model to produce a one prediction resulting from both inputs \textcolor{blue}{citation for multimodal networks}.
+We have derived an appropriate set of inputs arrays, explore in sec.
+(\ref{sec-Features}) and constructed a neural network architecture to coincide with these features.
+From each sample, we produce two input arrays, one being a matrix and the other being a column-vector, and present those to a  \textit{multimodal neural network} \cite{Virtanen}.
+This type of hybrid network accepts one array at each of two input layers, passes them through a series of non-overlapping layers, and combines separate neural networks into a single model to produce a one prediction resulting from both inputs \textcolor{blue}{citation for multimodal networks}.
 

### 2020-11-13 SignalClassifier/ClassifierMain/ModeUtilities.py
Updates to SignalClassifier
- Added class counter
- Added scaler handler

@@ -52,7 +52,14 @@ class ProgramMode:
         self.n_files = len(self.FILEOBJS)   # number of file objects
         self.groupCounter = 0
 
+        self.useNewScaler = True            # create new scaler & fit
         self.Scaler = StandardScaler()      # design matrix scaler
+
+    def SetScaler(self,scalerInstance):
+        """ Set Pre-existing Instance of a Sklearn Scaler to this Instance """
+        self.Scaler = scalerInstance()
+        self.useNewScaler = False           # we have an exisitng scaler obj, use it
+        return self.Scaler()
     
     def LoopCounter (self,cntr,max,text):
         """ Print Loop Counter for User """
@@ -62,10 +69,11 @@ class ProgramMode:
         del(text)
         return None
 
-    def ScaleData (self,matrixObj):
+    def ScaleData (self,matrixObj,fit=True):
         """ Scale Design Matrix 'X' for processing """
         X = matrixObj.__GetX__()            # get raw data
-        self.Scaler.partial_fit(X,y=None)   # fit the matrix
+        if fit == True:
+            self.Scaler.partial_fit(X,y=None)   # fit the matrix
         X_new = self.Scaler.transform(X)    # scale & return
         matrixObj.SetMatrixData(X_new)      # set as attrb
         return matrixObj                    # retuen updaed inst.
@@ -106,7 +114,10 @@ class ProgramMode:
             X2.AddSample(x2,i)          # add to MLP matrix
        
         # Format Design Matricies for Input
-        X2 = self.ScaleData(X2)     # scale design matrix
+        if self.useNewScaler == True:
+            X2 = self.ScaleData(X2,True)    # Fit & Scale
+        else:
+            X2 = self.ScaleData(X1,False)   # Scale, but don't fit
 
         return (X1,X2)      # return 2 Design matricies & target matrix
 
@@ -137,6 +148,7 @@ class TrainMode (ProgramMode):
         self.InitOutputStructure()
         self.n_iters = n_iters
         self.n_epochs = 2
+        
 
     def InitOutputStructure (self):
         """ Create Output Structure for Testing/Prediction Mode """
@@ -163,9 +175,11 @@ class TrainMode (ProgramMode):
             (matrixSXX,matrixMLP) = self.ConstructDesignMatrices(FILES,shapes)
             
             # Execute training
-            modelHistory = Networks.MODEL.fit(x=[matrixSXX.__GetX__(),matrixMLP.__GetX__()],
-                                              y=matrixSXX.__GetY__(),
[…]

### 2020-11-13 Thesis/MakeFigures/ThesisFigures/SpectrogramFigures/FeatureUtilities.py
Added Some Figures for the thesis

@@ -1,0 +1,374 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+12 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+
+import scipy.fftpack as fftpack
+import scipy.integrate as integ
+import scipy.signal as signal
+import scipy.sparse as sparse
+
+import MathUtilities as math_utils
+import PlottingUtilities as plot_utils
+
+"""
+FeaturesUtilities.py - "Feature Extraction Utils"
+    Contains Definitions to extract features and data from
+    time-domain representations of a signal
+"""
+
+        #### CLASS DEFINITIONS ####
+
+class BaseFeatures:
+    """
+    Basic Feature Extraction Class
+        'TimeSeriesFeatures' and 'FrequencySeriesFeatures' inherit from here
+    Assigns waveform attribute, sample rate, number of samples,
+    --------------------------------
+    waveform (arr) : 1 x N array of FP64 values representing a time-series waveform
+    rate (int) : Signal sample rate in Hz (samples/sec)
+    npts (int) : Number of samples used in each analysis frame
+    overlap (float) : Percent overlap between frames (must be in (0,1))
+    n_frames (int) : Number of desired analysis frames
+    presetFrame (arr) : Array of analysis frames already made
+    --------------------------------
+    divides into time-frames
+    """
+
+    def __init__(self,waveform,rate=44100,npts=4096,overlap=0.75,n_frames=256,presetFrames=None):
+        """ Initialize Class Object """
+        self.signal = waveform              # set waveform to self
+        self.n_samples = self.signal.shape[-1]  # samples in waveform
+        self.rate = rate                    # sample rate
+        self.npts = npts                    # points per frame
+        self.overlap = overlap              # overlap between frames
+        self.n_frames = n_frames            # number of desired frames     
+        self.frameStep = int(self.npts*(1-self.overlap))  # steps between frames
+
+    def ResizeWaveform(self):
+        """ Truncate or Zero-Pad Waveform Depending on Length """
+        currentSamples = self.signal.shape[-1]  # samples in waveform
+        self.oldSamples = currentSamples        # number of sample before padding
+        neededSamples = self.frameStep * (self.n_frames - 1) + self.npts
+        if currentSamples > neededSamples:              # too many samples
+            self.signal = self.signal[:neededSamples]   # take first needed samples
+        elif currentSamples < neededSamples:            # not enough samples
+            deficit = neededSamples - currentSamples    # sample deficit
[…]

### 2020-11-13 Thesis/MakeFigures/ThesisFigures/SpectrogramFigures/MathUtilities.py

@@ -1,0 +1,65 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+17 June 2020
+"""
+
+            #### IMPORTS ####
+              
+import numpy as np
+
+"""
+MathUtilities.py - "Math Utilities"
+    Contains Definitions for general mathematical functions
+"""
+
+            #### FUNCTION DEFINITIONS ####
+
+class MathematicalUtilities :
+    """
+    Mathematical Utilites for feature processing
+    --------------------------------
+    * no args
+    --------------------------------
+    All methods are static
+    """
+
+    @staticmethod
+    def DistributionData (X):
+        """
+        Analyze properties of an array of FP values
+        --------------------------------
+        X (arr) : (1 x N) Array of FP numbers to analyze as distribution
+        --------------------------------
+        Return array of [mean,median,mode,variance]
+        """
+        mean = np.mean(X,axis=-1)           # avg        
+        median = np.median(X,axis=-1)       # median
+        var = np.var(X,axis=-1)             # variance
+        return np.array([mean,median,var])  # return data
+
+    @staticmethod
+    def ReimannSum (X,dx):
+        """
+        Compute Reimann Sum of 1D array X with sample spacing dx
+        --------------------------------
+        X (arr) : (1 x N) Array of FP numbers to compute Reimann Sum of
+        dx (float) : Spacing between samples, 1 by default
+        --------------------------------
+        Return Reimann Sum approximation of array
+        """
+        return np.sum(X)*dx
+
+    @staticmethod
+    def PadZeros(X,outCols=256):
+        """ Zero-pad 2D Array w/ columns """
+        Xshape = X.shape                       # current array shape
+        colDeficit = outCols - Xshape[-1]      # number of missing columns
+        if colDeficit >= 1:                          # need to add cols
+            zeroPad = np.zeros(shape=(Xshape[0],colDeficit),dtype=float)
+            X = np.concatenate((X,zeroPad),axis=-1) # pad w/ zeroes
+        else:                                       # otherwise
+            X = X[:,:outCols]                       # remove cols
+        return X                                    # return new Array
+

### 2020-11-13 Thesis/MakeFigures/ThesisFigures/SpectrogramFigures/PlottingUtilities.py

@@ -1,0 +1,177 @@
+"""
+Landon Buell
+PHYS 799
+Instrument Classifier v0
+10 June 2020
+"""
+
+            #### IMPORTS ####
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+"""
+PlottingUtilities.py - "Plotting Utilities"
+    Contains Definitions to visualize spectral data in
+    time-space, frequency-space, and feature-space
+"""
+
+            #### PLOTTING FUNCTIONS ####
+
+def Plot_Features_2D (X1,X2,classes,labels,title='',
+                      save=False,show=True):
+    """
+    Create 2D visualization Comparing features
+    --------------------------------
+    X1 (arr) : (1 x N) array of data to plot on x-axis
+    X2 (arr) : (1 x N) array of data to plot on y-axis
+    classes (arr) : (1 x N) array of labels use to color-code by class
+    labels (iter) : (2 x 1) iterable containing labels for x & y axes
+    title (str) : Title for plot
+    save (bool) : If true, save MPL figure to cwd (False by Default)
+    show (bool) : If true, shows current figure to User (True by Default)
+    --------------------------------
+    return None
+    """
+    plt.figure(figsize=(16,12))
+    plt.title(title,size=40,weight='bold')
+    plt.xlabel(str(labels[0]),size=20,weight='bold')
+    plt.ylabel(str(labels[1]),size=20,weight='bold')
+
+    for X in [X1/X2]:           # Normalize Each Feature
+        X = X/np.max(np.abs(X))
+
+    plt.scatter(X1,X2,c=classes)
+
+    plt.yticks(np.arange(0,1.1,0.1))
+    plt.hlines(0,0,1,color='black')
+    plt.vlines(0,0,1,color='black')
+
+    plt.grid()
+    plt.tight_layout()
+    if save == True:
+        plt.savefig(title+'.png')
+    if show == True:
+        plt.show()
+
+def Plot_History (History,modelName,save=False,show=True):
+    """
+    Visualize Data from Keras History Object Instance
+    --------------------------------
+    History (Obj) : Keras history object
+    modelName (Obj) : Keras Sequential model w/ name attrb
+    save (bool) : If true, save MPL figure to cwd (False by Default)
+    show (bool) : If true, shows current figure to User (True by Default)
+    --------------------------------
+    Return None
+    """
+    # Initialize Figure
+    eps = np.array(History.epoch)          # arr of epochs
[…]

### 2020-11-13 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to thesis paper

@@
 
-\paragraph*{}We outline and detail the steps taken to execute this project from beginning to end.
-\textcolor{red}{Does this section need to be included? I'm not sure how to format or organize it}
+\paragraph*{}This multi-faceted project includes a great number of steps to ensure it's completion. Here we show a high-level outline of the pieces of this project.
 
@@
 
-\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 16 bit depth \textcolor{red}{check this!}.
+\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 16 bit depth.
 This ensures that all data will have a consistent format when features are extracted.

### 2020-11-13 SignalClassifier/ClassifierMain/ClassifierMAIN.py
Preparing for Cross Validation

@@ -34,11 +34,11 @@ if __name__ == '__main__':
     if ProgramSetup.programMode == 'train':
         ProgramMode = mode_utils.TrainMode(FILEOBJS=FILEOBJECTS,modelName=modelName,
                                             n_classes=N_classes,timestamp=timeStart,exportpath=exportPath,
-                                            groupSize=256,n_iters=4)
+                                            groupSize=256,n_iters=2)
     elif ProgramSetup.programMode == 'train-predict':     
         ProgramMode =  mode_utils.TrainPredictMode(FILEOBJS=FILEOBJECTS,modelName=modelName,
                                             n_classes=N_classes,timestamp=timeStart,exportpath=exportPath,
-                                            groupSize=256,n_iters=4,testSize=0.1)
+                                            groupSize=256,n_iters=2,testSize=0.1)
     elif ProgramSetup.programMode == 'predict':
         ProgramMode = mode_utils.PredictMode(FILEOBJS=FILEOBJECTS,modelName=modelName,
                                             n_classes=N_classes,timestamp=timeStart,exportpath=exportPath,

### 2020-11-13 SignalClassifier/ClassifierMain/FeatureUtilities.py

@@ -221,9 +221,15 @@ class FrequencySeriesFeatures (BaseFeatures):
         self.MelToHertz = lambda m : 700*(10**(m/2595)-1)
 
         # Time Axis, Frequency Axis
-        self.hertz,self.frequencyPoints = self.FrequencyAxis(low=0,high=6000)
+        self.SetFrequencyRange(0,12000)
+        self.hertz,self.frequencyPoints = self.FrequencyAxis()
         self.mels = self.HertzToMel(self.hertz)
         self.t = np.arange(0,self.n_frames,1)   
+
+    def SetFrequencyRange(self,low=0,high=6000):
+        """ Set Frequency Axis Bounds """
+        self.lowHz,self.highHz = low,high
+        return self
 
     def __Call__(self):
         """
@@ -239,27 +245,24 @@ class FrequencySeriesFeatures (BaseFeatures):
 
         # Add Elements to Feature vector
         featureVector = np.array([])
-        MFBEs = self.MelFilterBankEnergies()
-        #featureVector = np.append(featureVector,MFBEs)     # don't use filter bank energies?
+        MFBEs = self.MelFilterBankEnergies(n_filters=16)
         MFCCs = self.MelFrequencyCeptralCoefficients(MFBEs)
 
         featureVector = np.append(featureVector,MFCCs)
         featureVector = np.append(featureVector,self.CenterOfMass())
         return featureVector
 
-    def FrequencyAxis (self,low=0,high=6000):
+    def FrequencyAxis (self):
         """
         Compute Frequenxy Axis
         --------------------------------
-        low (float) : Low value for frequency slice
-        high (float) : High value for frequency bound
+        * no args
         --------------------------------
         Return frequency axis array between bounds, f
             and appropriate index, pts
         """
-        self.lowHz,self.highHz = low,high                   # set low/high bnds in Hz
         f_space = fftpack.fftfreq(n=self.npts,d=1/self.rate)# comput freq space
-        pts = np.where((f_space>=low)&(f_space<=high))[0]   # get slices
+        pts = np.where((f_space>=self.lowHz)&(f_space<=self.highHz))[0]   # get slices
         f_space = f_space[pts]                              # truncate space        
         return f_space,pts                                  # return space & pts
 

### 2020-11-13 SignalClassifier/ClassifierMain/ModeUtilities.py

@@ -57,9 +57,9 @@ class ProgramMode:
 
     def SetScaler(self,scalerInstance):
         """ Set Pre-existing Instance of a Sklearn Scaler to this Instance """
-        self.Scaler = scalerInstance()
+        self.Scaler = scalerInstance
         self.useNewScaler = False           # we have an exisitng scaler obj, use it
-        return self.Scaler()
+        return self.Scaler
     
     def LoopCounter (self,cntr,max,text):
         """ Print Loop Counter for User """
@@ -86,7 +86,7 @@ class ProgramMode:
         # Create Feature vector for MLP Branch
         timeFeatures = feat_utils.TimeSeriesFeatures(fileobj.waveform)  # collect time-domain features  
         featureVector.AddFeatures(timeFeatures.__Call__())              # and time-domain features
-        freqFeatures = feat_utils.FrequencySeriesFeatures(timeFeatures.signal)
+        freqFeatures = feat_utils.FrequencySeriesFeatures(timeFeatures.signal,n_frames=128)
         featureVector.AddFeatures(freqFeatures.__Call__())              # add frequency-domain features
             
         # Create Spectrogram Matrix for CNN Branch
@@ -117,7 +117,7 @@ class ProgramMode:
         if self.useNewScaler == True:
             X2 = self.ScaleData(X2,True)    # Fit & Scale
         else:
-            X2 = self.ScaleData(X1,False)   # Scale, but don't fit
+            X2 = self.ScaleData(X2,False)   # Scale, but don't fit
 
         return (X1,X2)      # return 2 Design matricies & target matrix
 

### 2020-11-13 SignalClassifier/ClassifierMain/SystemUtilities.py

@@ -163,7 +163,7 @@ class CategoryDictionary :
         decodeList = sorted(self.decoder.items())
         cols = ["Target Int","Target Str"]
         decodeFrame = pd.DataFrame(data=decodeList,columns=cols)
-        decodeFrame["Counts"] = self.classCounter
+        #decodeFrame["Counts"] = self.classCounter
         decodeFrame.to_csv(self.filePath,index=False)
         return self
 

### 2020-11-13 SignalClassifier-CrossValidation/KFoldsCrossValidation/CrossValidationMain.py
Preparing for X-Validation

@@ -21,7 +21,7 @@ if __name__ == "__main__":
     # HARD-CODE VARIABLES FOR DEVELOPMENT
     parent = 'C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis'
     read = os.path.join(parent,'SignalClassifier','Target-Data')   
-    modelName = "XValCLFC"
+    modelName = "XValCLFBeta"
     export = os.path.join(parent,'SignalClassifier-CrossValidation',modelName+'-Output-Data')
     model = os.path.join(parent,'SignalClassifier-CrossValidation',modelName+'-Model-Data')
     

### 2020-11-13 SignalClassifier/ClassifierMain/ModeUtilities.py
Preparing (again)
- Things went wrong

@@ -143,7 +143,7 @@ class TrainMode (ProgramMode):
         super().__init__(FILEOBJS=FILEOBJS,modelName=modelName,n_classes=n_classes,
                          timestamp=timestamp,exportpath=exportpath,groupSize=groupSize)
 
-        outfile = self.modelName+"@"+self.timestamp+"@TRAINING-HISTORY.csv"
+        self.outfile = self.modelName+"@"+self.timestamp+"@TRAINING-HISTORY.csv"
         self.exportpath = os.path.join(self.exportpath,self.outfile)
         self.InitOutputStructure()
         self.n_iters = n_iters
@@ -221,8 +221,8 @@ class PredictMode (ProgramMode):
                          n_classes=n_classes,timestamp=timestamp,exportpath=exportpath,
                          groupSize=groupSize)
 
-        outfile = self.modelName+"@"+self.timestamp+"@PREDICTIONS.csv"
-        self.exportpath = os.path.join(self.exportpath,outfile)
+        self.outfile = self.modelName+"@"+self.timestamp+"@PREDICTIONS.csv"
+        self.exportpath = os.path.join(self.exportpath,self.outfile)
         self.InitOutputStructure()
         self.predictionThreshold = prediction_threshold
         self.useNewScaler = True

### 2020-11-13 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to introduction

@@
 \paragraph*{}The task of algorithmically matching sound files to musical instrument classes in exceedingly difficult through conventional computer programming techniques.
-Because of the complexity of sound waves, and the brain's interpretation of them, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
-Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an solution that allows for a computer to \textit{learn} from past examples in order change and update itself.
-Such an algorithm exists in the form of a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine}.
-
-\paragraph*{}Former YouTube video classification team lead, and current machine learning consultant, Aurelien Geron writes about the relationship between biological brains and mathematical neural networks \cite{Geron}:
+Because of the complexity of sound recognition, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
+Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an solution that allows for a computer to \textit{learn} from labeled training examples in order \textit{teach} itself.
+One such an algorithm that has been used for this type of task is a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine,Virtanen}.
+
+\paragraph*{}As the name implies, Early neural networks were inspired from from the human brain.
+Former YouTube video classification team lead, and current machine learning consultant, Aurelien Geron writes about the relationship between biological brains and mathematical neural networks \cite{Geron}:
 \begin{quote}
@@
 \end{quote}
-The result of such an analogy is a computer program that is reminiscent of the brain.
-
-\paragraph*{}A neural network is a mathematical function that seeks to produce an approximation $F^*$, of some usually unknown function $F$ .
+The result of such an analogy is a computer program that is reminiscent of the structure of the a brain.
+Where a biological brain uses these chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Geron,Levine}.
+
+\paragraph*{}A neural network can then be considered as mathematical function that seeks to produce an approximation $F^*$, of some usually unknown function $F$ .
 For audio recognition, $F$ is some function or series of functions that occurs in the brain which allows for a listener to process the sensation of audio, and map it to a known source object.
@@
 A classification task involves mapping the input data, $x$ to one of $k$ possible \textit{classes}, each represented by an integer, $0$ through $k-1$.
-Each of the $k$ classes represents a particular musical instrument that could have produced the sound-wave in the audio file.
+Each of the $k$ classes represents a particular musical instrument that could have produced the sound-wave in the audio file \cite{Goodfellow,Loy,Virtanen}.
 
@@
 \paragraph*{}Other than inspiration from the brain, Neural Networks are name \textit{networks} because of their nested composition nature.
-The model can be represented by a linear computational graph which successively maps exactly how the repeated composition is structured.
-In a \textit{feed-forward network}, information is passed successively in one direction.
-For example functions could be chained together such as \cite{Goodfellow}
+The model can be represented by a linked computational graph which successively maps exactly how the repeated composition is structured.
+Each node in the graph represents a \textit{layer}, which executes a particular prescribed mathematical function \cite{Goodfellow}.
+In the case of a \textit{linear, feed-forward} network, information passes in a single direction, to produce an output.
+We can represent this as a graph:
+\begin{equation}
+\label{eqn-FunctionGraph}
+F(x) = x \rightarrow f^{(0)}(x) \rightarrow f^{(1)}(x) \rightarrow ..... \rightarrow
+f^{(L-2)}(x) \rightarrow f^{(L-1)}(x) \rightarrow y
+\end{equation}
+or as a nested function:
 \begin{equation}
@@
 \end{equation}
-Where each function $f^{(l)}$ represents a layer of the network model.
+Each function $f^{(l)}$ represents a layer of the network model.
 The number of layers in a neural network is referred to as the network \textit{depth}.
@@
 
-\paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}.
-In the training process this object, along with the appropriate classification label, $y$ is presented to the neural network for processing.
-This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu,Kahn}.
-
 \paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector.
@@
 \paragraph*{}The spectrogram and $20$ features from each sample are organized into one of two array structures, each called a \textit{design matrix}.
-A design matrix is an array of real floating-point numbers that stores the features in a convenient way for the neural network to digest.
+A design matrix contains real floating-point numbers that stores the features in a convenient way for the neural network to digest.
 For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.

### 2020-11-14 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex

@@
 
-\paragraph*{}Standard gradient-based learning, as given by the parameter update rule in Eq.
-(\ref{eqn-GradientLearning}) is cumbersome and often prone to numerical error.
-This can include phenomena such as \textit{vanishing gradients}, \textit{exploding gradients}, \textit{poor conditioning}, or unstable solution-spaces.
+\paragraph*{}An optimizer is the algorithm or procedure that is used by a machine learning model to achieve the lowest possible value of the cost function over a data set \cite{Geron}.
+Some models such as minimizing a \textit{mean-squared error} for linear regression model can be solve analytically, while high dimensional neural networks
+Standard gradient-based learning, as given by the parameter update rule in Eq.
+(\ref{eqn-GradientLearning}) is cumbersome and often prone errors such as vanishing or exploding gradients.
 \cite{Geron,Goodfellow,Loy}.
-To combat this, we require a more stable and robust optimizer than the bare gradient descent method.
-Many gradient-based optimizers have been developed over the years to mitigate some f these vulnerabilities.
+To combat this, model must often implement an algorithm that is more stable, and aggressive in it's ability to
 
@@
 If the previous step was found to reduce the cost function by a large or small amount, the step size for the previous step will update accordingly.
-Note that the upper index $(i)$ or $(i-1)$F gives an iteration index, while the upper iteration $i$ means to raise a value to the power of the iteration.
-For a given step $(i)$, The ADAM update is given:
+Note that a superscript $(i)$ or $(i-1)$ gives an iteration index, while the superscript $i$ means to raise a value to the power of $i$. For a given step $(i)$, The ADAM update is given:
 \begin{equation}

### 2020-11-14 SignalClassifier/ClassifierMain/NeuralNetworkUtilities.py
Preparing for Final Cross Validation

@@ -21,8 +21,11 @@ NeuralNetworkModels.py - "Neural Network Models"
 
             #### VARIABLE DECLARATIONS ####
 
-inputShapeMLP = (24,)
-inputShapeCNN = (1115,128,1)
+#inputShapeMLP = (24,)
+#inputShapeCNN = (1115,128,1)
+
+inputShapeMLP = (20,)
+inputShapeCNN = (558,256,1)
 
             #### NEURAL NETWORK OBJECTS ####
 

### 2020-11-15 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Proof-Reading Thesis Sections

@@
 
-\paragraph*{}Typically, a layer function can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation.
-This activation function typically is a non-linear function which allows for the modeling of increasingly complex decision-boundaries.
+\paragraph*{}Many layer functions can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation.
+This activation function typically is a non-linear function which allows for the modeling of increasingly complex decision-boundaries \cite{Geron,Loy}.
 The Linear transformation can be given by Eq.(\ref{eqn-LinearTransform}) in the case of a 1D Dense layer (\ref{subsubsec-DenseLayer}) or Eq.
@@
 They are among the most commonly used layer types.
-A dense layer is composed of a layer of \textit{artifical neurons}, each of which holds a numerical value within it, called the \textit{activation} of that neuron.
-This idea was developed from McCulloch and Pitts' work \cite{McCulloch} in attempting to model cognitive processes as mathematical functions, and was expanded upon by Frank Rosenblatt in  1957 \cite{Geron}.
+A dense layer is composed of a layer of \textit{artificial neurons}, each of which holds a numerical value within it, (usual a double-precision floating point number) called the \textit{activation} of that neuron.
+This idea was developed from McCulloch and Pitts' work \cite{McCulloch} in attempting to model cognitive processes as mathematical functions, and was expanded upon by Frank Rosenblatt in  1957 by combining many dense layers together to form a multilayer perceptron (MLP) \cite{Geron,Loy,Levine}.
 
 \paragraph*{}We model a layer of neurons as a vector of floating-point numbers.
-Typically, it is required that the array be one-dimensional.
-Suppose a layer $(l)$ contains $n$ artificial neurons.
-We denote the array that hold those activations as $x^{(l)}$ and is given by:
+By convention, the array is an $n$-dimensional column vector, where $n$ is number of nodes in that layer.
+Suppose a layer $(l)$ contains $n$ artificial neurons- we denote the array that hold those activations as $x^{(l)}$ and is given by:
 \begin{equation}
@@
 
-\paragraph*{}Suppose the layer $l-1$ contains $m$ neurons.
-Then the weighting-matrix, $W^{(l)}$ has shape $m \times n$, the bias-vector $b^{(l)}$ has shape $m \times 1$.
+\paragraph*{}Suppose the layer $(l-1)$ contains $m$ neurons.
+Then the weighting-matrix, $W^{(l)}$ has shape $m \times n$, the bias-vector $b^{(l)}$ has shape $n \times 1$.
 We can denote the function in a similar manner to Eq.(\ref{eqn-altLayerFunction}) as:
 \begin{equation}
-\label{eqn-FunctionDense}
+\label{eqn-FunctionDense}s
 f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(m \times 1)} \rightarrow x^{(l)} \in \mathbb{R}^{(n \times 1)}
@@
 \begin{algorithm}[H]
-\caption{Adaptive-Moments (ADAM) optimizer for a neural network}
+\caption{Adaptive-Moments (ADAM) optimizer for a neural network. This algorithm is adapted from Goodfellow, \cite{Goodfellow}}
 \label{algAdaGrad}
@@
 
-\paragraph*{}The success of a neural network algorithm is enormously dependent of the strength of the chosen features, as well as a complementary architecture, rather than the quantity of available data \cite{Geron,Kahn,Liu}.
-We have derived an appropriate set of inputs arrays, explore in sec.
-(\ref{sec-Features}) and constructed a neural network architecture to coincide with these features.
-From each sample, we produce two input arrays, one being a matrix and the other being a column-vector, and present those to a  \textit{multimodal neural network} \cite{Virtanen}.
-This type of hybrid network accepts one array at each of two input layers, passes them through a series of non-overlapping layers, and combines separate neural networks into a single model to produce a one prediction resulting from both inputs \textcolor{blue}{citation for multimodal networks}.
-
-\paragraph*{}The full classification neural network used for this project consists of two distinct entry points.
-Rather than presenting the network with one set of input data, $X$, we present the network with two different arrays, $X_1$ and $X_2$.
-Both arrays are a product of the same audio file sound wave, and thus share a common training label, $y$.
-Each of the two entry layers leads to it's own branch and the given information is process roughly in parallel.
-Once a certain number of layer functions have been applied, each arm of the neural network is left with a single dense layer of activations.
-These two activation vectors are concatenated into a single new dense layer, and then passed through one final layer to generate the model's final output.
-A visual representation of this architecture can be found in Fig.
-(\ref{fig-NetworkArchitecture}).
+\paragraph*{}In addition to choosing a strong set of features for a classification task, it is also important to combine the predictors with a complementary architecture.
+Since a neural network is a computational graph with each layer represented by a node, it can take on a nearly infinite number of different shapes and structures \cite{Goodfellow,Virtanen}.
+The structure of the network defines the composition of it's function, $F^*$ as in Eq.(\ref{eqn-FunctionGraph}), and thus it's performance in completing any given task \cite{Geron}.
+The layer structure of the neural network it's \textit{architecture} \ref{Goodfellow}.
+Most standard implementations of networks utilize a \textit{unimodal architecture} where the model is created with a single input layer \cite{N}
 
@@
 \begin{center}
-\includegraphics[scale=0.45]{../Figures/NeuralNetworkArchitecture}
-\end{center}
-\caption{The developed architecture of the audio file classification neural network.
+\includegraphics[scale=0.5]{../Figures/NeuralNetworkArchitecture}
+\end{center}
+\caption{The implemented miltimodal architecture of the audio file classification neural network.
 The Left branch process an image-like input, the right branch processes a vector-like input.
-The activations are then merged, and then a single output is produced}
+The activations are then merged, and then a single output vector is produced}
 \end{figure}
@@
 \begin{enumerate}
-\item A 2-Dimensional Convolution layer, using $32$ filters, a $3 \times 3$ kernel, a $1 \times 1$ step size, and a ReLU activation function,
-\item A 2-Dimensional Convolution layer, using $32$ filters, a $3 \times 3$ kernel, a $1 \times 1$ step size, and a ReLU activation function,
-\item A 2-Dimensional Maximum Pooling layer using a $3 \times 3$ pooling size, and an Identity activation function
+\item A 2-Dimensional Convolution layer, $32$ filters, $3 \times 3$ kernel, $1 \times 1$ step size, ReLU activation function,
+\item A 2-Dimensional Convolution layer, $32$ filters, $3 \times 3$ kernel, $1 \times 1$ step size, ReLU activation function,
+\item A 2-Dimensional Maximum Pooling layer, $3 \times 3$ pooling size, Identity activation function
 \end{enumerate}  
@@
 
-\paragraph*{}By grouping layers in this structure, we use the convolution  layers to reduce the number of features, and then the pooling layer to extract only the largest activations of the remianing features.
+\paragraph*{}By grouping layers in this structure, we use convolution to reduce the number of features, and then the pooling layer to extract only the largest activations of the remaining values.
 This ensures that in the full spectrogram image, only the dominant features and feature shapes are preserved and passed into the next layer set for processing.
+This also allows for positional invariance in features.
+Regardless of where in space or time a feature is detected, the moving kernel will still allow it to be found \cite{Goodfellow,Loy}.
 
@@
 \newpage
-\section{Evaluating Performance}
+\section{Evaluating Model Performance}
 \label{sec-PerfEval}
@@
 \paragraph*{}Before making predictions on unlabeled data such as the Chaotic Synthesizers, we must confirm that our model performs reasonably well on data that it has never interacted with.
-The most common practice is to divide a full data set into a subset of \textit{training} samples, and \textit{testing} samples.
-As the names imply, the training subset is used to fit the model, and we use the labeled testing data set to evaluate.
-The exact ratio of sample volume between these subsets varies depending on the task \cite{Goodfellow,Geron2,Mitchell}.
-Since the testing data is labeled, we can compare the classifiers predictions to the \textit{ground truth} labels.
+The most common practice is to divide a full data set into a subset of \textit{training} samples, and \textit{testing} samples \cite{Geron}.
+As the names imply, the training subset is used to fit the model, and we use the labeled testing data set to evaluate how well the model has trained.
+The exact ratio of sizes between these subsets varies depending on the task \cite{Goodfellow,Geron2,Mitchell}, however we choose to generally use around $90\%$ training samples and $10\%$ testing samples.
 
@@
 
-\paragraph*{}Performance evaluations are commonly implemented in the form of \textit{$K$-Fold Cross-Validation} (Also called X-val) \cite{Geron,Goodfellow}.
+\paragraph*{}The optimization of neural networks are heavily dependent on initial conditions of parameters and the data sets.
+We consider models that suffer from this phenomenon to be \textit{high-variance} models \cite{James}.
+To eliminate any concerns of possible out-liers, or abnormalities that arise, it is commont implement a resampling method called \textit{cross validation} (Also called X-val) \cite{Geron,Goodfellow}.
 This process involves taking a data set containing $N$ unique samples and dividing it into $K$ non-overlapping subsets.
 $1$ subset is reserved to evaluate the model, and $K-1$ remaining subsets are used to train the model.
-This belongs a larger family of statistical validations called \textit{Resampling methods} \cite{James}.
-Below, we detail pseudo-code for a $K$-Fold Cross Validation algorithm.
+For each of the $K$ models, we can evaluate a series of performance metrics, and store any model parameters.
+We can compare any one model to the other $K-1$ models to ensure that each network is performing consistently, despite small changes in the initial data set.
+We detail pseudo-code for a $K$-Fold Cross Validation algorithm.
 
@@
 	\item Train the model, $F^*$ with the $X_{train}$ data set
-	\item Evaluate the trained model with the $X_{train}$ dataset, and compute value of metric function(s) $P$
+	\item Evaluate the trained model with the $X_{train}$ data set, and compute value of metric function(s) $P$
 	\item Store Performance $P$ in Performance History array
@@
 \bibitem{Levine}
-Levine, Daniel S. \textit{Introduction to Neural and Cognitive Modeling}. 3rd ed., Routledge, 2019.
+Levine, Daniel S. \textit{Introduction to Neural and Cognitive Modeling}. 2nd ed., Routledge, 2000.
+
+\bibitem{Li}
+Li, Yingming, and Ming Yang. “A Survey of Multi-View Representation Learning.” Journal of LateX Class Files, vol. 14, no. 8, Aug. 2015.
 
@@
 Mitchell, Tom Michael. Machine Learning. 1st ed., McGraw-Hill, 1997.
+
+\bibitem{Ngiam}
+Ngiam, Jiquan, et al. "Multimodal Deep Learning." 2011.
 

### 2020-11-15 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to thesis

@@
 \end{equation}
-Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$. Additionally, the string is fixed in place at both ends, which can be modeled by the boundary conditions:
+Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$.
+Additionally, the string is fixed in place at both ends, with the nut at $x = 0$ and the bridge at $x = L$, which can be modeled by the boundary conditions:
 \begin{equation}
@@
 
-\paragraph*{}In order to specify a solution, we must also specificy two intitial conditions. We described the initial state of the string at time $t = 0$  by the two conditions:
+\paragraph*{}In order to specify a solution, we must also specify two initial conditions. We described the initial state of the string at time $t = 0$  by the two conditions:
 \begin{equation}
@@
 \label{subsec-Aerophones}
+
+\paragraph*{}An aerophone is a musical instrument that produces sounds through the vibration of an air molecules in a column-like structure.
 
@@
 \begin{equation}
-FCM = \sum_{i=0}^{k'} \frac{1}{k'}\text{FCM}_{i}\big[ s^{(i)} \big]
+FCM = \frac{1}{k'}\sum_{i=0}^{k'}\text{FCM}_{i}\big[ s^{(i)} \big]
 \end{equation}
@@
 We consider models that suffer from this phenomenon to be \textit{high-variance} models \cite{James}.
-To eliminate any concerns of possible out-liers, or abnormalities that arise, it is commont implement a resampling method called \textit{cross validation} (Also called X-val) \cite{Geron,Goodfellow}.
+To eliminate any concerns of possible out-liers, or abnormalities that arise, it is common to implement a resampling method called \textit{cross validation} (Also called X-validation) \cite{Geron,Goodfellow}.
 This process involves taking a data set containing $N$ unique samples and dividing it into $K$ non-overlapping subsets.
@@
 \paragraph*{}The output of cross validation is $K$ models that are all trained and evaluated on overlapping subsets of the full data.
-Each model $F^*$, shows one possible outcome of training the network.
+Each model $F^*$, shows a possible outcome of training the network given a subset of data samples, and a particular set of initial parameters..
 It has a corresponding set of learned parameters $\Theta^*$, as defined in Eq.

### 2020-11-15 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisUtilities.py
Ran Model Evaluations from Cross Validations

@@ -42,7 +42,7 @@ class AnalyzeModels:
         self.modelName = modelName
         self.dataPath = datapath  
         self.n_classes = n_classes
-        self.outputFile = self.modelName+"@ANALYSIS@"+self.startTime+".csv"
+        self.outputFile = self.modelName+"@"+self.startTime+"@ANALYSIS"+".csv"
 
     def GetKeywordFiles(self,keyword):
         """ Find files in path w/ Keyword in name """
@@ -76,6 +76,7 @@ class AnalyzeModels:
         nCols = 4
         self.metricsArray = np.empty(shape=(nRows,nCols))
 
+        # Initialize 3 Average Confusion matrices
         avgStandardConfMat = np.zeros(shape=(self.n_classes,self.n_classes))
         avgHitsWeightedConfMat = np.zeros(shape=(self.n_classes,self.n_classes))
         avgScrsWeightedConfMat = np.zeros(shape=(self.n_classes,self.n_classes))
@@ -101,29 +102,43 @@ class AnalyzeModels:
             # Create the matricies
             standardConfMat = ComputeMetrics.StandardConfusion()
             hitsWghtConfMat = ComputeMetrics.HitsWeightedConfusion()
-            scrsWghtConfMat = ComputeMetrics.ScoreWeightedConfusionn()
+            scrsWghtConfMat = ComputeMetrics.ScoreWeightedConfusion()
 
             os.chdir(exptPath)
+            # Export the Confusion matrices Arrays
+            ClassifierMetrics.ExportConfusion(standardConfMat,stdMatName,exptPath)
+            ClassifierMetrics.ExportConfusion(hitsWghtConfMat,hitsMatName,exptPath)
+            ClassifierMetrics.ExportConfusion(scrsWghtConfMat,scrsMatName,exptPath)
+
+            # Export the Confusin matrices Plots
             ClassifierMetrics.PlotConfusion(standardConfMat,self.n_classes,stdMatName,False)
             ClassifierMetrics.PlotConfusion(hitsWghtConfMat,self.n_classes,hitsMatName,False)
-            ClassifierMetrics.PlotConfusion(weightedConfMat,self.n_classes,scrsMatName,False)
+            ClassifierMetrics.PlotConfusion(scrsWghtConfMat,self.n_classes,scrsMatName,False)
             os.chdir(homePath)
 
             # Add To average Conf Mats
             avgStandardConfMat += standardConfMat
-            avgWeightedConfMat += weightedConfMat
[…]

### 2020-11-16 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Ran Model Evaluations from Cross Validations
Updates to Written Thesis
- Added analysis frames figure

@@
 
+\paragraph*{}\textcolor{red}{How do I write an introduction???}
+
 % ================================================================
@@
 \paragraph*{}Over the course of their lives, humans will learn to map sounds to sources almost effortlessly \cite{Virtanen}.
-Given an example, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olsen,White}.
+Given an example, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olson,White}.
 We can simplify the idea of humans recognizing sound as some function or operation that occurs within the brain, accepting an input sound, and produces an output label.
@@
 (\ref{fig-NetworkArchitecture}).
-A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olsen,Kahn}.
+A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olson,Kahn}.
 \textcolor{blue}{Details on the creating of the spectrogram can be found in the \textit{features} section of this document.}
@@
 
-\paragraph*{}A square wave is a piece-wise defined waveform whose value alternatively alternates between $+1$ and $-1$ \cite{White,Olsen}.
+\paragraph*{}A square wave is a piece-wise defined waveform whose value alternatively alternates between $+1$ and $-1$ \cite{White,Olson}.
 A square wave with period $f_0$ has a waveform defined over a single period as:
@@
 \end{quote}
-In the case of the biological process, the features of the audio is simply the raw time series waveform as processed by the brain.
-This information is then used into categorize the source.
-In the case of the neural network model, the time series waveform alone has shown to be unreliable in classification tasks \cite{Serizel}.
-We must then develop a set of features or predictors that can describe important properties of the waveform in a far more efficient manner \cite{Goodfellow,James}.
-
-\paragraph*{}It becomes quickly apparent that the choice of features is extraordinarily important to the process of training and evaluation of the classifier model.
+In the biological process of categorizing sound sources, the time-domain waveform is usually enough to match the sound to a source \cite{Olson}.
+However, a computer representation of a waveform is an array-like structure of values sampled discretely in time and volume \cite{Virtanen,Liu}.
+Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks \cite{Serizel}.
+We must develop a set of features or predictors that can describe important properties of the waveform in an efficient manner \cite{Goodfellow,James}.
+
+\paragraph*{}It becomes quickly apparent that the choice of features is extraordinarily important to the process of training and evaluation of the classifier model \cite{Mierswa}.
 Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels.
@@
 \paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector.
+We have developed a set of predictors that describe each sample in a compact manner, with reasonable separation boundaries between samples from different classes.
 These features are derived are principles of music, digital signal processing, previous work, and underlying physics that governs the behavior of instruments.
@@
 For each feature, we visualize the distribution in across each class in the form as box-plots.
-Each feature has been normalize to have a zero mean, and unit-variance acorss all classes.
+Each feature has been normalize to have a zero mean, and unit-variance across all classes.
 
@@
 
-\paragraph*{}The spectrogram and $20$ features from each sample are organized into one of two array structures, each called a \textit{design matrix}.
-A design matrix contains real floating-point numbers that stores the features in a convenient way for the neural network to digest.
+\paragraph*{}From each audio file, we produce a spectrogram matrix and a feature vector, as well as a target label for training purpose.
+From a collection of multiple samples, the spectrograms are concatenated into a single object $X_1$, and the feature vectors are concatenated into an object, $X_2$.
+Each objects is a multidimensional array called a \textit{design matrix} \cite{Geron,Goodfellow,Loy,Zerizel}.
+For any machine learning task, a  design matrix is an object that contains real floating-point numbers that store the features in a convenient way for the neural network to digest.
 For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.
-each has shape given by:
+Each has shape given by:
 \begin{equation}
@@
 \end{equation}
-Where $N' \times k \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect.
+Where $N' \times k \times 1$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sect.
 (\ref{subsec-spectrogram}).
-Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec.
-(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ audio samples stored in that design matrix.
+Similarly, $p$ is the number of predictors extracted from each sample, outlined in sec.
+(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ audio file samples stored in that design matrix.
+
+\paragraph*{}A design matrix is typically accompanied by a \textit{target matrix},$Y$, which indicates the class that the particular sample belongs to.
+For a classifier with $\kappa$ classes, each sample labeled by a one-hot-encoded vector for shape $1 \times \kappa$ \cite{Tensorflow}.
+Thus, for the design matrices $X_1$ and $X_2$, we have a corresponding target matrix given by:
+\begin{equation}
+\label{eqn-YShape}
+Y \in \mathbb{R}^{(b \times \kappa)}
+\end{equation}
 
@@
 \paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification \cite{Liu,Zhang}.
-Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame.
-Each of the $k$ frames then allows for a section of the signal in quazi-stationary state \cite{Kahn,Serizel}.
+Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the previous frame.
+Each of the $k$ frames then allows for a section of the signal to be analyzed in a \textit{quazi-stationary state} \cite{Kahn,Serizel}.
+Below we visualize how analysis frames are related to the full time-series waveform.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=0.45]{../Figures/AnalysisFrames}
+\end{center}
+\caption{A visualization of how frame-blocking is used to create each analysis frames.
+This image has been adapted and modified from Liu, et.
+al.
+"Audio Feature Extraction and Analysis", Fig.
+(1).
+See ref.
+\cite{Liu}.}
+\label{fig-AnalysisFrames}
+\end{figure}
 
@@
 Since each audio file contains a different number of samples, we choose the number of frames, $k$ to be less than or equal to $256$.
-If $k > 256$, the waveform in truncated, if $k \leq 256$ the frames left as is.
+If $k > 256$, the waveform in truncated, if $k \leq 256$ the frames left as is, and missing frames are accounted for later (to improve computation time).
 The audio has been sampled at $f_s = 44100$ samples/second, so each frame represents a slice of time that is about $0.1$ seconds long.
 
-\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
+\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is a sample in each frame
 \begin{equation}
@@
 \end{equation}
-We use bracket notation, $a[j]$ to indicate that each analysis frame $a_i$ is array-like. The following indexing conventions for matrix $A$ all represent the same entry:
+We use bracket notation, $a[i]$ to indicate that each analysis frame $a_i$ is array-like. The following indexing conventions for matrix $A$ all represent the same entry:
 \begin{equation}
@@
 This window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
-Result is an $k \times N$ array, $\widetilde{A}$:
+The result is another $k \times N$ array, $\widetilde{A}$:
 \begin{equation}
@@
 \end{equation}
-The window function allows for a cleaner transform into frequency space \cite{Virtanen}. \textcolor{blue}{Expand on this. HOW? Why do we use a windowing function?}
-
-\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross}.
+
+\paragraph*{}Window functions are use to account for discontinuities that may arise in the waveform at the edges of each analysis frame.
+The Fourier Transform assumes that an integer number of signal periods fit within each analysis frame, however this is rarely the case.
+A transform of this kind of signal can lead to \textit{spectral leakage} where energy appears to "leak" into adjacent frequency bins \textcolor{red}{Citation needed}.
+This result is a frequency domain that is not an accurate representation of the equivalent time domain.
+The Hann window uses the raised cosine function to taper the signal off to zero at the end-points, thus eliminate discontinuities at the edges while weighting the samples at the center much more heavily.
+
+\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross,Virtanen}.
 The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
-Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space containing $N$ samples
+Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space signal containing $N$ samples
 \begin{equation}
@@
 
-\paragraph*{}Most standard implementations of neural network models require all activations, weights, and biases to be real floating-point numbers.
-Since the the DFT matrix introduces complex values, we compute the square of the element-wise $L2$-norm of the resultant array.
+\paragraph*{}Most standard implementations of neural network models have all activations, weights, and biases to be real floating-point numbers cite{Levine,Loy,Tensorflow}.
+Since the elements of the DFT matrix lie on the complex unit circle, each real-valued analysis frame will be moved into complex space.
+This means we compute the element-wise product of the transformed signal matrix and it's complex-conjugate matrix.
+This is the $N \times k$
+spectrogram matrix, where each element is a real-values number. Matrix $S$ is defined:
 \begin{equation}
 \label{eqn-Spectrogram}
-S_{i,j} = \big{\lVert} (\mathbb{W}\widetilde{A}^T)_{i,j} \big{\rVert}_{2}^{2}
+S = (\mathbb{W}\widetilde{A}^T) \odot (\mathbb{W}\widetilde{A}^T)^*
 \end{equation}
@@
 (\ref{eqn-WindowMatrix}).
+The asterisks indicate the element-wise complex conjugation.
+In practice, the matrix product $\mathbb{W}\widetilde{A}^T$ is computed once, and the conjugate is applied to a copy of the array.
+
 The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of real floating-point numbers.
@@
 
-\paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames.
-Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$.
+\paragraph*{}Each column of the $S$ matrix is now a single analysis frame that has been moved into a frequency-space representation of itself.
+There are $k$ columns, just as there were $k$ time-series frames, and $N$ rows since there were $N$ samples per row.
+Given the discrete nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$.
 To ensure homogeneous input sizes between all samples, we zero-pad the matrix $S$ with additional columns until $k = 256$.
@@
 
-\paragraph*{}Standard western musical instruments seldom extend above $6$ kHz \cite{Olson,Virtanen,White}.
-This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
-To condense the size of the matrix, we select onlt the frequency bins that correspond to energies between $0$ Hz and $6000$ Hz.
+\paragraph*{}Standard western musical instruments seldom have fundamental frequencies that extend above $6$ kHz \cite{Olson,Virtanen,White}.
+This means that when constructing the spectrogram, we will rarely see significant energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
+To condense the size of the matrix, we select only the frequency bins (rows) that correspond to energies between $0$ Hz and $6000$ Hz.
 This makes the input array smaller, and eliminates redundant and non-useful information.
@@
 \paragraph*{}Each spectrogram is now $N' \times k \times 1$ (The last axis represents a single pixel channel, as opposed to $3$ channels for RGB inputs, etc.) and effectively encodes the energy distribution of the waveform as a function of both time and frequency.
-The spectrogram is the first feature used in this model.
+The spectrogram makes up each sample in the first design matrix $X_1$, Eq.(\ref{eqn-ShapeX1}) used in this model.
 For this classifier, we have chosen $N' = 558$ and $k = 256$.
@@
 \begin{equation}
-\label{eqn-X1 shape}
+\label{eqn-X1}
 X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k \times 1)}
@@
 
-\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample.For consistency between smaples, each waveform is padded or truncated to contain exactly $M$ samples.
+\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample.
+Each feature is one element in the feature vector for the particular sample.
+For consistency between samples, each waveform is padded or truncated to contain the same number of samples $M$.
 Time space is indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
@@
 
-\paragraph*{}The time domain envelope (TDE) is a method of determining which parts of the sound wave contains most of the energy of the signal Often, we compute the RMS-Energy of each frame - a larger energy of the frame, the larger the average amplitude of the waveform in that frame.
-For frames with smaller amplitude, it is likely that the signal has either not begun, or is decaying.
-
-\paragraph*{}We adapt this feature to \textbf{compute the RMS-Energy of the full waveform}. The RMS-Energy of the full waveform, $s$ is given by \cite{Olsen,Serizel}
+\paragraph*{}The time domain envelope (TDE) is a rough measurement of the energy containined in the time domain.
+If we divide the signal into analysis frames, as in Fig.
+(\ref{fig-AnalysisFrames}), then the TDE approximates the energy in that frame.
+A frame with a TDE indicates a generally large amplitude, and a frame with a low TDE indicates a generally small ampliute.
+(i.e.
+the signal has not started or is decaying)
+
+\paragraph*{}We adapt this TDE to \textbf{compute the RMS-Energy of the full waveform}.
+Since the maximum amplitude of each waveform array has been normalized to $\pm 1$, the TDE presents a consistent measurement of energy in the full time-domain signal \cite{Liu}.
+The TDE is computed as RMS-Energy of the full waveform, $s$ and is given by \cite{Olson,Serizel}
 \begin{equation}
@@
 \end{equation}
-By using the full waveform, we acquire a rough estimate for the energy in the entirety of the audio file \cite{Liu}.
-For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large waveform RMS when compared to those instruments without sustain such as plucked stings or dampened percussion  \textcolor{red}{Citation?}
+For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large TDE value.
+For instruments with short sustain times, such as plucked stings or dampened percussion we expect a comparably small TDE value \cite{Olson,White}.
+The difference allows for considerable separation between many percussion and woodwind classes.
 
@@
 \end{center}
-\caption{Time domain envelope visualized in feature-space}
+\caption{A comparison of the Time Domain Envelope across each class}
 \label{fig-FeatureTDE}
@@
 \paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses it's equilibrium point.
-This can be done per total sound wave, per unit time, or per analysis-frame.
-This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform.
+This can be computed per total sound wave, per analysis-frame, or per unit time.
+This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform \cite{Liu}.
 In some cases, the ZXR can be correlated to frequency as well \cite{Kahn,Zhang}.
@@
 Petrik, Marek. "Introduction to Deep Learning." Machine Learning. 20 April. 2020, Durham, New Hampshire.
+
+\bibitem{Powers}
+Powers, David. (2008). \textit{Evaluation: From Precision, Recall and F-Factor to ROC, Informedness, Markedness \& Correlation}. Mach. Learn. Technol. 2.
 

### 2020-11-16 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Progress on paper
- reorganized some figures

@@
 
-\paragraph*{}The time domain envelope (TDE) is a rough measurement of the energy containined in the time domain.
+\paragraph*{}The time domain envelope (TDE) is a rough measurement of the energy contained in the time domain.
 If we divide the signal into analysis frames, as in Fig.
 (\ref{fig-AnalysisFrames}), then the TDE approximates the energy in that frame.
-A frame with a TDE indicates a generally large amplitude, and a frame with a low TDE indicates a generally small ampliute.
+A frame with a high TDE indicates a generally large amplitude, and a frame with a low TDE indicates a generally small amplitude.
 (i.e.
@@
 
-\paragraph*{}We adapt this TDE to \textbf{compute the RMS-Energy of the full waveform}.
-Since the maximum amplitude of each waveform array has been normalized to $\pm 1$, the TDE presents a consistent measurement of energy in the full time-domain signal \cite{Liu}.
-The TDE is computed as RMS-Energy of the full waveform, $s$ and is given by \cite{Olson,Serizel}
+\paragraph*{}We adapt this TDE to \textbf{compute the time domain envelope of the full waveform}.
+Since the maximum amplitude of each waveform array has been normalized to $\pm 1$, the TDE represents a consistent measurement of energy in the full time-domain signal \cite{Liu}.
+The TDE is computed as the RMS-Energy of the waveform, $s$ and is given by \cite{Olson,Serizel}:
 \begin{equation}
@@
 \begin{center}
-\textcolor{red}{PLOT OF TDE FEATURES HERE}
-\end{center}
-\caption{A comparison of the Time Domain Envelope across each class}
+\textcolor{red}{Plot of TDE Feature Here}
+%\includegraphics[scale=0.3]{../FiguresFeatures/Time_Domain_Env}
+\end{center}
+\caption{A comparison of the Time Domain Envelope across each class using a box-and-whisker plot}
 \label{fig-FeatureTDE}
@@
 This can be computed per total sound wave, per analysis-frame, or per unit time.
-This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform \cite{Liu}.
-In some cases, the ZXR can be correlated to frequency as well \cite{Kahn,Zhang}.
-
-\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}. The ZXR for the full waveform $s$ is given by \cite{Serizel,Liu}
+This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform \cite{Kahn,Liu,Zhang}.
+
+\paragraph*{}We adapt this feature to \textbf{compute the zero crossing rate for the full waveform}.
+Signals with a high ZXR can be representative of classes that often have additional noise and signals with a low ZXR, can indicate signals with more stable, periodic behavior.
+The ZXR for the full waveform $s$ is given by \cite{Serizel,Liu}
 \begin{equation}
@@
 Where $\sign(x)$ returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$.
-This provides a rough estimate for the average frequency in the full waveform,n and can help discern clean periodic signals (low ZXR) from those that may have more noise or volatile behavior (high ZXR)\cite{Serizel}.
+ZXR also provides a very rough estimate for the average frequency of the waveform.
+This allows it to alos be useful in discerning classes with generllay hgher frequencies, such as upper woodwinds, against classes with generaly lower frequencies, such as low brass \cite{White}.
 
@@
 \end{center}
-\caption{Zero crossing rate visualized in feature-space}
+\caption{A comparison of the Zero-Crossing Rate for each class using a box-and-whisker plot}
 \label{fig-FeatureZXR}
@@
 \paragraph*{}The temporal center of mass (TCM) of a signal is used to compute roughly where in time the amplitude of the waveform \textit{bunches up}.
-We treat the full waveform array, $s$, with $M$ samples as a discrete 1-Dimensional mass distribution.
+We compute the element-wise absolute value of the waveform and treat it as a 1-dimensional discrete mass distribution of $M$ samples.
 The TCM of that waveform is then given:
@@
 \label{eqn-FeatureTCM}
-\text{TCM}\big[ s \big] = \frac{\sum_{i=0}^{M-1}i s[i]}{\sum_{i=0}^{M-1}s[i]}
-\end{equation}
-This includes negative amplitude values acting as "negative masses". \textcolor{blue}{Should I use the absolute value of the signal instead?}
-
-\paragraph*{}The TCM turns out to be a very unique feature, and very powerful in classification due to it's variance textcolor{red}{Citation needed}.
-For instruments with heavier attacks, we expect the TCM to be a very near the start of the waveform.
-For instruments with long sustain times, we expect a very centrally located center of mass, and for instruments with long release times, we expect a later TCM value.
+\text{TCM}\big[ s \big] = \frac{\sum_{i=0}^{M-1}i \big|s[i]\big|}
+{\sum_{i=0}^{M-1}\big|s[i]\big|}
+\end{equation}
+
+\paragraph*{}TCM condenses the idea of the amplitude envelope into a single value.
+It allows for the quick measurement of where in the time most of the energy of the signal lies.
+For percussive instruments with short attack and release times, such as bells or xylophones, we expect a very low TCM.
+Instruments with plucked strings, but longer release times such as mandolins and guitars should have similarly low values.
+Instruments in the woodwind and brass family generally have longer sustain and release times, giving them a slightly higher center of mass.
+Strings and undampened percussion have notoriously long sustain and release times giving them much higher TCM values \cite{Olson,White}.
+Finally, the synthetic wave forms have no characteristic  envelope shape (due to their synthetic nature).
+This gives a centrally located TCM, very close to $M/2$.
 
@@
 \end{center}
-\caption{Temporal center-of-mass visualized in feature-space}
+\caption{A comparison of the temporal center mass for each class using a box-and-whisker plot}
 \label{fig-FeatureTCM}
@@
 
-\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution .
+\paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution.
+They are computed by summing a signal with a time-delayed variant of itself, and then normalized depending on the contect.
 We can compute any number of ACC's and their value changed depending on the index chosen.
-It is common to only compute the first $K$ ACC's \cite{Serizel}.
+It is common to use the first $K$ ACC's \cite{Serizel}.
 For a full waveform signal $s$, with $M$ samples, the $k$-th ACC (indexed from $1$ to $K$) is given by:
@@
 \text{ACC}_k\big[ s \big] = 
-\frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]} {\sqrt{\sum_{i=0}^{M-k-1}s^2[i]} \sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
-\end{equation}
-
-\paragraph*{}An ACC can be thought of as convolving a signal with a time-delayed version of itself.
-This measures similarity between samples related to the time difference between them \textcolor{red}{Citation needed}.
-\textcolor{blue}{I may need to try a different set of ACC's for this}
+\frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]} {\sqrt{\sum_{i=0}^{M-k-1}s^2[i]} 
+\sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
+\end{equation}
+
+\paragraph*{}\textcolor{red}{I need to complete my discussion of ACC's here!}
 
 \begin{figure}[H]
+\begin{center}
+\textcolor{red}{PLOT OF ACC FEATURES HERE}
+\end{center}
+\caption{A comparison of the the first four auto correlation coefficents in each class using a box-and-whisker plot}
 \label{fig-FeatureACC}
-\begin{center}
-\textcolor{red}{PLOT OF ACC FEATURES HERE}
-\end{center}
-\caption{First four auto correlation coefficients visualized in feature-space}
 \end{figure}
@@
 
-\paragraph*{}Mel filter banks are divisions of the frequency spectrum of a signal into $R$ overlapping triangular bins \cite{Sahidullah}.
+\paragraph*{}MEl Filter Bank Energies are not used directly as features, but are used in computing Mel Frequency Cepstrum Coefficient (MFCC's) so we describe them here.
+Mel filter banks are divisions of the frequency spectrum of a signal into $R$ overlapping bins \cite{Sahidullah,Serizel}.
 These filter banks allows us to group sounds based on their energy distribution in frequency space.
-Each filter is triangularly shaped, over a certain band in frequency space, and zero elsewhere.
+Each filter is triangularly shaped, covering a certain band in frequency space, and zero elsewhere.
 This way, when computing the the dot product of any filter with frequency space, we get an approximation of energy in that filter bank \cite{Sahidullah,Serizel}.
@@
 
-\paragraph*{}Mel filters are produced by grouping frequency-space into $R$ overlapping bins called \textit{Mel Filter-banks}.
-In units of Mels, each filter bank, $R_i$ remains a constant width, but when shown in Hertz, the bins increase logarithmically.
 \begin{figure}[H]
@@
 \end{center}
-\caption{Mel Filter Banks shown in frequency space with units of Hertz}
+\caption{Mel Filter Banks shown in frequency space with units of (a) Mels and (b)Hertz}
 \label{fig-MelFilterBanks}
 \end{figure}
-Each of the $R$ filters is created to be $N'$ samples long, to match the width of the cropped frequency space in the spectrogram, and transformed back into units of Hertz.
+
+\paragraph*{}Each of the $R$ filters is created to be $N'$ samples long, to match the width of the cropped frequency space in the spectrogram, Eq.
+(\ref{eqn-Spectrogram}).
 When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
@@
 \label{eqn-FilterBanks}
-B = S^T M^T
+B = (MS)^T
 \end{equation}
@@
 
-\paragraph*{}Using $S^T$ ensures that each row of the matrix is an analysis frame in frequency space.
-Similarly, each column of the matrix $M$ is a appropriately scaled Mel filter-bank.
-This way, the matrix product in Eq.
+\paragraph*{}Tis matrix product in Eq.
 (\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
 Finally, we compute the average energy across all $k$ frames, into array $\widetilde{B}$ with shape $1 \times R$.
-For this project, we have chosen to use $R = 12$ filter-banks, which are all appended to the feature vector.
-
-\begin{figure}[H]
-\begin{center}
-\textcolor{red}{PLOT OF MFCC FEATURES HERE}
-\end{center}
-\caption{Mel Frequency Cepstral Coefficients in feature-space}
-\label{fig-FeatureMFBE}
-\end{figure}
+For this project, we have chosen to use $R = 12$ filter-banks, which are all are used to compute the MFCC's in the next section.
 
@@
 
-\paragraph*{}Ceptstral coefficients are the result of computing the inverse discrete Fourier transform (IDFT) of the logarithm of the frequency Spectrum.
-Mel Frequency Cepstral Coefficients (MFCC's) are the most commonly used in digital signal processing.
-They are computed throught he inverse discrete cosine transform of the log energy in in each Mel frequency bank \cite{Serizel,Sahidullah}.
+\paragraph*{}Ceptstral coefficients are the result of computing the inverse discrete Fourier transform (IDFT) of the logarithm of the frequency Spectrum \cite{Serizel,Sahidullah}.
+Mel Frequency Cepstral Coefficients (MFCC's) are the most commonly used ceptral coefficients and appear commonly in digital signal processing.
 The $c$-th coefficient is given by:
@@
 \end{equation}
-Where $\widetilde{B}$ are the column average of the Mel filter bank energies computed in Eq. (\ref{eqn-FilterBanks}), and $R$ is the number of filter banks used.
+Where $\widetilde{B}$ is the column average of the Mel filter bank energies computed in Eq. (\ref{eqn-FilterBanks}), and $R$ is the number of filter banks used.
 
 \paragraph*{}Physically, MFCC's are a transform of a transform.
-This allows us to investigate the periodicity of the frequency spectrum, which highlights phenomena such as overtones or echoes \cite{Virtanen}.
+This allows us to investigate the periodicity of the frequency spectrum, which highlights phenomena such as overtones or echoes in the signal\cite{Virtanen}.
 Ceptrum coefficients are commonly used to speech identification and are very prolific in sound recognition tasks \cite{Serizel,Sahidullah,Liu}.
-We provide a representation of MFCC properties below.
+
+\paragraph*{}As the frequency bin index increases, the width of the bin in frequency space increases.
+For instruments with higher fundamental frequencies, we expect very little energy in the lower frequency bins, and also a lower MFCC value.
+For instruments with lower fundamental frequencies, we expected
 
 \begin{figure}[H]
-\label{fig-FeatureMFCC}
 \begin{center}
@@
 \end{center}
-\caption{Mel Frequency Cepstral Coefficients visualized in feature-space}
+\caption{A comparison of the $12$ Mel Frequency Cepstral Coefficients for each class using box-and-whisker plots}
+\label{fig-FeatureMFCCs}
 \end{figure}
@@
 
-\paragraph*{}Accuracy score, while not commonly used is the most intuitive of all of the performance metrics. It is the ratio of
+\paragraph*{}Accuracy score, while not commonly used is the most intuitive of all of the performance metrics.
+It is the ratio of correct predictions of he total number of predictions.
+While immediately useful for equally sampled binary classification problems, it looses meaning as the number of classes increases, and epecially if the number of samples per class is not consistent \cite{Geron,James}.
+
+\paragraph*{}For example, we could develop a model that uses a few predictors from every human currently alive and determine which of them has walked on the moon.
+There are roughly 7 billion humans alive, four of which have been on out moon.
+Simply guess \textit{no} for every human, our model would have more than a $99.9999\%$ accuracy.
+However, we would argue that this model does not perform well seeing as it has a $0 \%$ recall score, and and a $0 \%$ precision score.
+
+\paragraph*{}Despite this we can still sue accuracy score to provide a rough approximation for how the model is performing. \textcolor{red}{finish this!}
 

### 2020-11-16 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to thesis & figures

@@
 
+\textcolor{red}{Describe nature of features w/ separation boundaries}
+
 \newpage
@@
 \paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}.
-In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
+In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following steps and requirements:
 \begin{enumerate}
-\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
+\item A suitably sized number of files of reasonable audio quality with normalized amplitudes
 \item Audio encoded in a standard, and consistent format
@@
 \begin{enumerate}
-\item Roughly $16,000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
+\item Roughly $18,000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
 \item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
@@
 
-\newpage
-
 \subsection{Time-Space Features}
@@
 
+\newpage
+
 \subsubsection{Time Domain Envelope}
@@
 \begin{center}
-\textcolor{red}{Plot of TDE Feature Here}
-%\includegraphics[scale=0.3]{../FiguresFeatures/Time_Domain_Env}
+%textcolor{red}{Plot of TDE Feature Here}
+\includegraphics[scale=0.3]{../FiguresFeatures/Time_Domain_Env}
 \end{center}
@@
 \begin{center}
-\textcolor{red}{PLOT OF ZXR FEATURES HERE}
+%\textcolor{red}{PLOT OF ZXR FEATURES HERE}
+\includegraphics[scale=0.3]{../FiguresFeatures/Zero_X-Rate}
 \end{center}
@@
 \begin{center}
-\textcolor{red}{PLOT OF TCM FEATURES HERE}
+%\textcolor{red}{PLOT OF TCM FEATURES HERE}
+\includegraphics[scale=0.3]{../FiguresFeatures/Time_Center_of_Mass}
 \end{center}
@@
 \begin{center}
-\textcolor{red}{PLOT OF ACC FEATURES HERE}
+%\textcolor{red}{PLOT OF ACC FEATURES HERE}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/Auto_Correlation_1}
+	\caption{ACC $k=1$}
+	\end{subfigure}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/Auto_Correlation_2}
+	\caption{ACC $k=2$}
+	\end{subfigure}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/Auto_Correlation_3}
+	\caption{ACC $k=3$}
+	\end{subfigure}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/Auto_Correlation_4}
+	\caption{ACC $k=4$}
+	\end{subfigure}
+
 \end{center}
@@
 
-\paragraph*{}As the frequency bin index increases, the width of the bin in frequency space increases.
-For instruments with higher fundamental frequencies, we expect very little energy in the lower frequency bins, and also a lower MFCC value.
-For instruments with lower fundamental frequencies, we expected
+\paragraph*{}As the frequency bin index increases, the width of the bin in frequency space increases. \textcolor{red}{Finish this! What does a MFCC tell us with words!}
 
@@
 \begin{center}
-\textcolor{red}{PLOT OF MFCC FEATURES HERE}
-\end{center}
-\caption{A comparison of the $12$ Mel Frequency Cepstral Coefficients for each class using box-and-whisker plots}
+%\textcolor{red}{PLOT OF MFCC FEATURES HERE}
+
+\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/MFCC_1}
+	\caption{MFCC $R[1]$}
+	\end{subfigure}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/MFCC_4}
+	\caption{MFCC $R[4]$}
+	\end{subfigure}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/MFCC_8}
+	\caption{MFCC $R[8]$}
+	\end{subfigure}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/MFCC_12}
+	\caption{MFCC $R[12]$}
+	\end{subfigure}
+
+\end{center}
+\caption{A comparison of 4 Mel Frequency Cepstral Coefficients, $1$, $4$, $8$ and $12$ for each class using box-and-whisker plots}
 \label{fig-FeatureMFCCs}
@@
 \begin{center}
-\textcolor{red}{PLOT OF FCM FEATURES HERE}
-\end{center}
-\caption{Frequency center-of-mass visualized in feature-space}
+%\textcolor{red}{PLOT OF FCM FEATURES HERE}
+\includegraphics[scale=0.3]{../FiguresFeatures/Frequency_Center_of_Mass}
+\end{center}
+\caption{A comparison of the frequency center-of-mass for each class using box-and-whisker plots}
 \end{figure}

### 2020-11-16 SignalClassifier-Postprocessing/FeatureProperties/PropertyUtilities.py

@@ -31,7 +31,7 @@ class FeatureProcessor:
     @property
     def GetFeatureNames(self):
         """ Get Names of all features as list of strs """
-        names = ["Time Domain Env.","Zero X-Rate","Time Center of Mass"]                         
+        names = ["Time Domain Env","Zero X-Rate","Time Center of Mass"]                         
         names += ["Auto Correlation "+str(i+1) for i in range(4)]        
         names += ["MFCC "+str(i+1) for i in range (12)]      
         names += ["Frequency Center of Mass"]                                    
@@ -39,14 +39,15 @@ class FeatureProcessor:
 
     def CreateDictionary(self,encdPath):
         """ Handle class dictionary """
-        modelName = "XValCLFB"
+        modelName = "XValCLFAlpha"
         categories = CategoryDictionary(encdPath,modelName)
         self.classNames = categories.encoder.keys()          # get names of categories
             
     def __Call__(self,exptPath):
         """ Execute Feature Processor Instance """   
         homePath = os.getcwd()
-        xTickNames = ["Full Data"] + [x for x in self.classNames] # make ticks for boxplot
+        #xTickNames = ["Full Data"] + [x for x in self.classNames] # make ticks for boxplot
+        xTickNames = [x for x in self.classNames] # make ticks for boxplot
         
         # Make BoxPlot Data for the Full matrix
         for i in range(self.nFeatures):   # Each feature:
@@ -54,7 +55,7 @@ class FeatureProcessor:
             featureData = self.X[:,i]            # get full col of matrix
             featureName = self.GetFeatureNames[i]
 
-            self.boxPlotArrays = [BoxPlotData(featureData,"Full Feature")]
+            self.boxPlotArrays = []
 
             for j in range(self.nClasses):          # each class
                 # Get data for this class
@@ -126,17 +127,19 @@ class BoxPlotFigure:
         --------------------------------
         Return None
         """
-        plt.figure(figsize=(20,10))
+        plt.figure(figsize=(20,8))
         #plt.title(title,size=60,weight='bold',pad=2.0)
         
         boxPlots = [x.data for x in data]
         plt.boxplot(boxPlots,showfliers=False)
 
         plt.grid()
-        plt.subplots_adjust(left=0.02, right=0.98, top=0.95, bottom=0.15)
+        plt.subplots_adjust(left=0.02, right=0.98, top=0.95, bottom=0.18)
 
+        plt.yticks(weight='bold')
[…]

### 2020-11-17 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updated Architecture figure & draft

@@
 
-\paragraph*{}This function is almost only used in the output layer of a neural network, and encodes a discrete categorical probability.
+\paragraph*{}This function is almost only used in the output layer of a neural network, and encodes a normalized discrete categorical probability \cite{Loy,Virtanen}.
 For example, if Eq.(\ref{eqn-Softmax}) returns a vector of the form: $[ 0.75 , 0.25]$, we interpret this as a sample having a $75\%$ chance of beloinging to class $0$ and a $25\%$ change of belonging to class $1$.
@@
 \paragraph*{}A neural network's purpose is to produce a function $F^*$ that approximates an unknown function $F$, using a set of parameters, $\Theta$.
-The model must have a procedure for updating the parameters in $\Theta$ to allow for a reasonably close approximation of $F$.
-To better understand this, we turn to Tom Mitchell's explanation of a learning algorithm \cite{Goodfellow,Mitchell}:
+The model must have a procedure for updating the parameters in $\Theta$ to allow for a reasonably close approximation of $F$ \cite{Goodfellow}.
+To better understand this, we turn to Tom Mitchell's explanation of a learning algorithm \cite{Mitchell}:
 \begin{quote}
@@
 \end{quote}
-Without any direct human intervention, a model must update itself to improve it's performance at a give task a new information is presented to it.
+Without any direct human intervention, a model must update itself to improve it's performance at a give task as new information is presented to it.
 To do this, the model must be constructed with a training procedure in mind.
 
-\paragraph*{}We consider the set of parameters $\Theta$ as a concatenation of each applicable layer's weighting matrix and bias vector such that:
+\paragraph*{}We consider the set of parameters $\Theta$ as the set of values within each trainable layer's weighting matrix and bias vector such that:
 \begin{equation}
@@
 \Theta = \big\{
-W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)}, W^{(L)}, b^{(L-1)},
+W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)}, W^{(L)}, b^{(L-1)}
 \big\}
 \end{equation}
-Each parameter is floating-point number, which is stored in a weight matrix $W^{(l)}$ or bias vector $b^{(l)}$.
-Each value for each parameter contributes to the output of the function, thus indirectly influences the final layer activations.
-Note that $W^{(l)}$ or $b^{(l)}$, themselves are not parameters, but arrays of parameters to be trained.
-Certain layers, such as pooling layers (\ref{subsubsec-2DPooling}), concatenation layers (\ref{subsubsec-1DConcat}), or flattening layers (\ref{subsubsec-1DFlatten}) do not contain any trainable parameters.
-Similarly, activation functions themselves are static and are not included in the list of parameters.
-
-\paragraph*{}In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\Theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow,Levine}.
+The arrays $W^{(l)}$and bias vectors $b^{(l)}$ are not trainable parameters, themselves.
+Instead, the floating-point entries within these arrays are the values that can be adjusted.
+Each element in this set may contain hundreds or thousands of parameters, so we represent these indirectly as elements of their respective matricies or vectors.
+We choose this notation for $\Theta$ for notation simplicity.
+Note that not all layers have trainable parameters, and activations functions themselves are not trainable, but fixed functions.
+
+\paragraph*{}Modern neural networks can contain upwards of hundreds of thousands,or even millions of elements in $\Theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow,Levine}.
 For the network that we have designed in this project, there are roughly $33,000$ parameters across $20$ layers.
+In this sections we motivate and explore how the we can update the parameters in $\Theta$ as to train the neural network.
+
+% ================================
 
@@
 
-\paragraph*{}A neural network uses \textit{indirect optimization}, which contrasts from pure optimization. Deep Learning expert Ian Goodfellow described this \cite{Goodfellow}:
+\paragraph*{}A neural network uses \textit{indirect optimization}, which contrasts from pure optimization. Deep Learning expert Ian Goodfellow describes the difference \cite{Goodfellow}:
 \begin{quote}
@@
 
-\paragraph*{}We can reduce the cost given a set of parameters, $J(\Theta)$, by moving each element in $\Theta$ with small steps in the direction of the negative partial derivative of each parameter.
+\paragraph*{}We can reduce the cost given a set of parameters, $J(\Theta)$, by moving each element in $\Theta$ with small steps in the direction of the negative partial derivative with respect to each parameter.
 In the case of the high-dimensional $\Theta$ object, we compute the partial derivative with respect to each weight and bias in the form of the \textit{gradient vector}.
@@
 \end{equation}
-Where $\frac{\partial J}{\partial W^{(l)}}$ is taking the partial derivative of each element in the $W^{(l)}$ matrix, and preserves the shape.
+Where $\frac{\partial J}{\partial W^{(l)}}$ is taking the partial derivative of each element $W_{i,j}$ in the $W^{(l)}$ matrix, and preserves the shape.
+While there may only be $20$ or so layers, the gradient vector actually has one element for every trainable parameter in all of the layers.
+This means that for our network, the gradient vector contains upwards of $33,000$ elements.
+We again choose to group these elements by their parent structure for ease of notation.
 
 \paragraph*{}Due to the nested composition of the network output in Eq.
-(\ref{eqn-FunctionChain}), and subsequently the cost itself, we must use the chain rule of calculus to work backwards through computational graph of the neural network to compute the partial derivative with respect to each parameter in $\Theta$.
-The process of working backwards to compute each element in the gradient vector is called \textit{back-propagation} \cite{Geron}.
-Below we detail an algorithm in pseudo-code to back-propagate through a fully-connected neural network, such as the multilayer perceptron outlines in sec.(\ref{sec-NetworkStructre})
+(\ref{eqn-FunctionChain}), and subsequently the cost itself, we must use the chain rule of calculus to work backwards through computational graph of the neural network to compute the partial derivative of $J$ with respect to each parameter in $\Theta$.
+The process of working backwards to compute each element in the gradient vector is called \textit{back-propagation} \cite{Geron,Goodfellow,Loy}.
+
+% ================================
+
+\subsubsection{Back-Propagation}
+\label{subsubsec-BackProp}
+
+\paragraph*{}Recall our model of a neural network as a computational graph as in Eq.
+(\ref{eqn-FunctionGraph}).
+Each node of the graph is a layer that represents a mathematical function which takes the activation from the previous layer $x^{(l-1)}$ and transforms them into the activations of the current layer, as in Eq.
+(\ref{eqn-LayerFunction}) We can visualize this chain of operations as such:
+\begin{figure}
+\begin{center}
+
+\end{center}
+\end{figure}
 
@@
 \begin{figure}[H]
-\label{fig-NetworkArchitecture}
-\begin{center}
-\includegraphics[scale=0.5]{../Figures/NeuralNetworkArchitecture}
+\begin{center}
+\includegraphics[scale=0.75]{../Figures/NeuralNetworkArchitecture}
 \end{center}
@@
 The activations are then merged, and then a single output vector is produced}
+\label{fig-NetworkArchitecture}
 \end{figure}

### 2020-11-18 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to paper

@@
 Each node of the graph is a layer that represents a mathematical function which takes the activation from the previous layer $x^{(l-1)}$ and transforms them into the activations of the current layer, as in Eq.
-(\ref{eqn-LayerFunction}) We can visualize this chain of operations as such:
-\begin{figure}
-\begin{center}
-
-\end{center}
+(\ref{eqn-LayerFunction}).
+Additionally, we recall that each layer itself is made up two steps which produce linear activations such as in Eq.
+(\ref{eqn-LinearTransform}) and non-linear activations, as in Eq.
+(\ref{eqn-elementActivation}).
+Therefore, to understand back propagation, it is necessary to examine the internal functions of each layer.
+We can use this idea to visualize this chain of operations as in Fig.
+(\ref{fig-ComputationalGraph})
+\begin{figure}[H]
+\begin{center}
+\textcolor{red}{Graph goes here}
+\end{center}
+\caption{A visual representation of a computational graph}
+\label{fig-ComputationalGraph}
 \end{figure}
+
+\paragraph*{}Given this graph chain and it's numerical nature, we cannot compute each element in the gradient vector by conventional symbolic calculus.
+We must instead use the chain rule for partial derivatives to begin at the final output of the network and successively work our way forward to the entry layer to compute the numerical derivative with respect to each parameter.
+This process is called \textit{back-propagation} \cite{Geron,Goodfellow,Loy}.
+
+\paragraph*{}We begin by
 

### 2020-11-18 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Proof-read sections

@@
 
-\paragraph*{}This multi-faceted project includes a great number of steps to ensure it's completion. Here we show a high-level outline of the pieces of this project.
+\paragraph*{}This project includes a great number of steps to ensure it's completion. Here we show a high-level outline of the pieces involved.
 
@@
 \item $y^* \leftarrow x^{(L-1)} = X[-1]$
-\item Return the pre-nonlinear activations and final-nonlinear activations.\\
+\item Return the pre-nonlinear activations and final-nonlinear activations:\\
 \RETURN $Z , X$
@@
 
-\paragraph*{}As stated previously, a neural network is composed of a series of functions that are called in succession to transform features (an input) into a prediction (an output).
+\paragraph*{}As stated previously, a neural network is composed of a series of functions that are called in succession to transform features (an input) into a predictions (an output).
 As shown in Eq.
-(\ref{eqn-altLayerFunction}), each function feeds directly into the next as to form a sort of recursive computational graph \cite{Goodfellow}.
-
-\paragraph*{}Many layer functions can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation.
+(\ref{eqn-altLayerFunction}), each function feeds directly into the next as to form a chain-like computational graph \cite{Goodfellow}.
+Many layer functions can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation.
 This activation function typically is a non-linear function which allows for the modeling of increasingly complex decision-boundaries \cite{Geron,Loy}.
@@
 Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-LinearTransform}).
-$\sigma^{(l)}$ is some activation function, which is often use to enable the modeling of more complex-decision boundaries.
+$\sigma^{(l)}$ is some activation function which introduces the ability to account for non-linearity in the
 

### 2020-11-18 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisUtilities.py

@@ -104,18 +104,6 @@ class AnalyzeModels:
             hitsWghtConfMat = ComputeMetrics.HitsWeightedConfusion()
             scrsWghtConfMat = ComputeMetrics.ScoreWeightedConfusion()
 
-            os.chdir(exptPath)
-            # Export the Confusion matrices Arrays
-            ClassifierMetrics.ExportConfusion(standardConfMat,stdMatName,exptPath)
-            ClassifierMetrics.ExportConfusion(hitsWghtConfMat,hitsMatName,exptPath)
-            ClassifierMetrics.ExportConfusion(scrsWghtConfMat,scrsMatName,exptPath)
-
-            # Export the Confusin matrices Plots
-            ClassifierMetrics.PlotConfusion(standardConfMat,self.n_classes,stdMatName,False)
-            ClassifierMetrics.PlotConfusion(hitsWghtConfMat,self.n_classes,hitsMatName,False)
-            ClassifierMetrics.PlotConfusion(scrsWghtConfMat,self.n_classes,scrsMatName,False)
-            os.chdir(homePath)
-
             # Add To average Conf Mats
             avgStandardConfMat += standardConfMat
             avgHitsWeightedConfMat += hitsWghtConfMat

### 2020-11-21 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Progress on Back-Propagation section

@@
 \begin{center}
-\includegraphics[scale=0.2]{../Figures/RectifiedLinearUnit}
+\includegraphics[scale=0.25]{../Figures/RectifiedLinearUnit}
 \end{center}
@@
 \paragraph*{}By optimizing the parameters $\Theta$ in the network model, we allow for the output of a consistently low cost function to be produced across all samples in the data set.
+When a model produces consistently low cost values across new unseen samples, we consider this to be a \textit{trained} or \textit{fit} model \cite{Goodfellow}.
 
@@
 (\ref{eqn-elementActivation}).
-Therefore, to understand back propagation, it is necessary to examine the internal functions of each layer.
-We can use this idea to visualize this chain of operations as in Fig.
+Therefore, to understand back propagation, it is helpful to examine the flow of information within each layer.
+Consider a simplified neural network model visualized in Fig.
 (\ref{fig-ComputationalGraph})
@@
 \begin{center}
-\textcolor{red}{Graph goes here}
-\end{center}
-\caption{A visual representation of a computational graph}
+\includegraphics[scale=0.8]{../Figures/LayerGraph}
+\end{center}
+\caption{A visual representation of a simplified neural network as a computational graph}
 \label{fig-ComputationalGraph}
 \end{figure}
-
-\paragraph*{}Given this graph chain and it's numerical nature, we cannot compute each element in the gradient vector by conventional symbolic calculus.
+Note that we indicate the cost as $J(\Theta)$.
+This is an allusion to the fact that $J$ depends of both the labels $y$, and the predictions $y^*$.
+Where $y^*$ is a function of all of the previous layer activation, which are in turn functions of each weight bias element, i.e.
+the contents of the $\Theta$ object, in Eq.
+(\ref{eqn-Theta}).
+This is why we are able to compute the gradient with respect to $\Theta$ as in Eq.
+(\ref{eqn-CostGradient}).
+
+\paragraph*{}Raw information is presented as $x^{(0)}$ at the top of the figure, and and output is returned as $x^{(L-1)}$ at the bottom.
+Arrows represent the flow of information.
+As expressed in Eq.
+(\ref{eqn-CXELoss}), we compute the cost of a sample, or batch of samples by comparing the difference between $y^*$ (which is $x^{(L-1)}$) and $y$.
+Given this graph chain and it's numerical nature, we cannot compute each element in the gradient vector through conventional symbolic calculus \cite{Loy}.
 We must instead use the chain rule for partial derivatives to begin at the final output of the network and successively work our way forward to the entry layer to compute the numerical derivative with respect to each parameter.
-This process is called \textit{back-propagation} \cite{Geron,Goodfellow,Loy}.
-
-\paragraph*{}We begin by
+This process is called \textit{back-propagation} \cite{Geron,Goodfellow}.
+
+\paragraph*{}Suppose we wish to compute the elements of $\frac{\partial J}{\partial W^{(L-1)}}$ and $\frac{\partial J}{\partial b^{(L-1)}}$ for the gradient vector.
+The flow of information in Fig.
+(\ref{fig-ComputationalGraph}) indicates that we cannot directly evaluate the derivative because the cost $J$, is a function $x^{(L-1)}$, which is a function of $z^{(L-1)}$, which is a function of elements in $W^{(L-1)}$.
+Thus, we have:
+\begin{equation}
+\frac{\partial J}{\partial W^{(L-1)}} = \frac{\partial}{\partial W^{(L-1)}}
+\Bigg[ J \bigg\{ x^{(L-1)} \Big[ z^{(L-1)}  \big\{ W^{(L-1)} 
+\big\} \Big] \bigg\} \Bigg]
+\end{equation}
+The evaluation of the derivative of a composite function requires use of the chain rule of multivariate calculus. We represent this symbolically as:
+\begin{equation}
+\label{eqn-dWL1}
+\frac{\partial J}{\partial W^{(L-1)}} = 
+\frac{\partial J}{\partial x^{(L-1)}}\frac{\partial x^{(L-1)}}{\partial z^{(L-1)}}\frac{\partial z^{(L-1)}}{\partial W^{(L-1)}}
+\end{equation}
+Similarly, the partial derivative of the cost with respect to the bias array can be formulated as:
+\begin{equation}
+\label{eqn-dbL1}
+\frac{\partial J}{\partial b^{(L-1)}} = 
+\frac{\partial J}{\partial x^{(L-1)}}\frac{\partial x^{(L-1)}}{\partial z^{(L-1)}}\frac{\partial z^{(L-1)}}{\partial b^{(L-1)}}
+\end{equation}
+
+\paragraph*{}For the categorical cross entropy cost function, we can evaluate $\partial J / \partial x^{(L-1)}$ over a single sample as:
+\begin{equation}
+\label{eqn-CXELossDeriv}
+\frac{\partial J}{\partial x^{(L-1)}} = \frac{\partial J}{\partial y^*} =
+\frac{\partial}{\partial x^{(L-1)}}\big[ -y \log_{10} (y^*) \big] = -\frac{1}{\ln(10)}\sum_{i}\frac{y_{i}}{y^*_i}
+\end{equation}
+The value $\partial x^{(L-1)} / \partial z^{(L-1)}$ can be found by differentiating Eq. (\ref{eqn-elementActivation}) with respect to the input activations.
+\begin{equation}
+\frac{\partial x^{(L-1)}}{\partial z^{(L-1)}} = \sigma^{'(l)} \big[ z^{(L-1)} \big]
+\end{equation}
+
+\paragraph*{}Suppose we then wish to compute the elements of $\frac{\partial J}{\partial W^{(l)}}$ and $\frac{\partial J}{\partial b^{(l)}}$.
+Using the same graph from Fig.
+(\ref{fig-ComputationalGraph}), we can follow the chain of information to derive an expression for the similar to Eq.
+(\ref{eqn-dWL1}) and Eq.
+(\ref{eqn-dbL1}) for each layer $(l)$ in the nueral network.
+In general, we can state that:
+\begin{equation}
+\label{eqn-dWGeneral}
+\end{equation}
+And
+\begin{equation}
+\label{eqn-dbGeneral}
+\end{equation}
 
@@
 
-\subsubsection{The 1-Dimension Vibrating String}
+\subsubsection{The 1-Dimensional Vibrating String}
 
@@
 Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$.
-Additionally, the string is fixed in place at both ends, with the nut at $x = 0$ and the bridge at $x = L$, which can be modeled by the boundary conditions:
+Additionally, the string is fixed in place at both ends, with a nut at $x = 0$ and a bridge at $x = L$, which can be modeled by the boundary conditions \cite{Olson,White,Haberman}:
 \begin{equation}
@@
 \label{eqn-X1Shape}
-X_1 \in \mathbb{R}^{(b \times N' \times k \times 1)}
+X_1 \in \mathbb{R}^{(b \times N' \times k)}
 \end{equation}
@@
 \end{equation}
-Where $N' \times k \times 1$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sect.
+Where $N' \times k$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sect.
 (\ref{subsec-spectrogram}).
 Similarly, $p$ is the number of predictors extracted from each sample, outlined in sec.
-(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ audio file samples stored in that design matrix.
-
-\paragraph*{}A design matrix is typically accompanied by a \textit{target matrix},$Y$, which indicates the class that the particular sample belongs to.
-For a classifier with $\kappa$ classes, each sample labeled by a one-hot-encoded vector for shape $1 \times \kappa$ \cite{Tensorflow}.
+(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).
+The first axis, with size $b$ indicates that there are $b$ audio file samples stored in that design matrix.
+
+\paragraph*{}A design matrix is typically accompanied by a \textit{target matrix} $Y$, which indicates the class that the particular sample belongs to.
+For a classifier with $\kappa$ classes, each sample labeled by a one-hot-encoded vector for shape $1 \times \kappa$ \cite{Tensorflow,Loy}.
 Thus, for the design matrices $X_1$ and $X_2$, we have a corresponding target matrix given by:
@@
 
-\paragraph*{}The field of neural classification is well studied in the application of image-processing.
-Many large-scale, and even introductory projects find themselves under the umbrella of image classification \cite{Geron,Goodfellow,Loy,Mierswa}.
+\paragraph*{}The application of neural networks to image-processing and recognition has been well studied and developed in the last few decades \cite{Geron,Goodfellow,Loy,Mierswa}.
 As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior.
 Following this success, it make senses to provide an image-like representation of a sound wave as a feature.
-We do this in the form of a spectrogram matrix.
-
-\paragraph*{}A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time.
+We do this in the form of a \textit{spectrogram} matrix.
+A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time.
 In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis.
@@
 (\ref{fig-spectrograms}).
-
 \begin{figure}[H]
 \begin{center}
-\label{fig-spectrograms}
 \textcolor{red}{Insert spectrograms here}
 \caption{Spectrogram representations of various waveforms}
+\label{fig-spectrograms}
 \end{center}
@@
 
-\paragraph*{}For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap.
+\paragraph*{}For this project, we have chosen to use frames of size $N = 1024$ with a $75\%$ or $768$ sample overlap.
 Since each audio file contains a different number of samples, we choose the number of frames, $k$ to be less than or equal to $256$.
 If $k > 256$, the waveform in truncated, if $k \leq 256$ the frames left as is, and missing frames are accounted for later (to improve computation time).
-The audio has been sampled at $f_s = 44100$ samples/second, so each frame represents a slice of time that is about $0.1$ seconds long.
+The audio has been sampled at $f_s = 44100$ samples/second, so each frame represents a slice of time that is about $0.0232$ seconds long.
 
@@
 \paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
-A standard \textit{Hann Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$.
-The $n$-th index in a Hann window with $N$ samples is defined:
-\begin{equation}
-\label{eqn-Hann}
+A standard \textit{Hanning Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$.
+The $n$-th index in a Hanning window with $N$ samples is defined:
+\begin{equation}
+\label{eqn-Hanning}
 H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
 \end{equation}
-This window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
+This window function is applied to each analysis frame by computing the element-wise product of the Hanning window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
 The result is another $k \times N$ array, $\widetilde{A}$:
@@
 \end{equation}
+We show the effect of a Hanning window on a wae 
+\begin{figure}[H]
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	%\includegraphics[width=\textwidth , height=0.2\textheight]{../FiguresFeatures/Auto_Correlation_4}
+	\caption{A section of a waveform, $1024$ samples long}
+	\end{subfigure}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	%\includegraphics[width=\textwidth , height=0.2\textheight]{../FiguresFeatures/Auto_Correlation_4}
+	\caption{The Same waveform with a Hanning Window Applied}
+	\end{subfigure}
+
+\end{figure}
 
@@
 This result is a frequency domain that is not an accurate representation of the equivalent time domain.
-The Hann window uses the raised cosine function to taper the signal off to zero at the end-points, thus eliminate discontinuities at the edges while weighting the samples at the center much more heavily.
-
-\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross,Virtanen}.
+The Hanning window uses the raised cosine function to taper the signal off to zero at the end-points, thus eliminate discontinuities at the edges while weighting the samples at the center much more heavily.
+
+\paragraph*{}Before we compute the Fourier Transform to move each analysis frame into frequency-space, we choose to tail-pad each analysis frame with an additional $1024$ samples of all zeros.
+This means that each frame has gone from being $1024$ samples, to $2048$ samples.
+Matrix $\widehat{A}$ has a shape of $k \times 2048$.
+Doubling the size of each analysis frame allows us the synthetically double the resolution in frequency-space, while retaining the resolution in time-space \cite{Virtanen}.
+
+\paragraph*{}With this final change, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross,Virtanen}.
 The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
@@
 \end{equation}
-Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix - product of $\mathbb{W}$ and $\widetilde{A}^T$.
+Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.
+The DFT is applied by a taking the matrix - product of $\mathbb{W}$ and $\widetilde{A}^T$.
 The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
@@
 
-\paragraph*{}Each spectrogram is now $N' \times k \times 1$ (The last axis represents a single pixel channel, as opposed to $3$ channels for RGB inputs, etc.) and effectively encodes the energy distribution of the waveform as a function of both time and frequency.
+\paragraph*{}Each spectrogram is now $N' \times k$ and effectively encodes the energy distribution of the waveform as a function of both time and frequency.
 The spectrogram makes up each sample in the first design matrix $X_1$, Eq.(\ref{eqn-ShapeX1}) used in this model.
@@
 \label{eqn-X1}
-X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k \times 1)}
+X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k)}
 \end{equation}
@@
 \paragraph*{}The quantity $TP + FN$ is a measurement of the total number items in that class, independent of selection.
-Thus, the quantity recall gives the ratio of correct selections to all selectes that were made.
+Thus, the quantity recall gives the ratio of correct selections to all selections that were made.
 More intuitively, we can describe recall as the fraction of relevant items that were selected \cite{Geron}.
@@
 
-\item[•]Dr. Kevin Short and Dr. Maurik Holtrop for various consultation and guidance throughout this project
+\item[•]Dr. Kevin Short and Dr. Maurik Holtrop for various consultation and guidance throughout this project.
+
+\item[•]Dr. Kourosh Zarringhalam and Dr. Marek Petrik for additional consultation on machine learning topics.
 

### 2020-11-22 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
General Updates, Cleaned Figures

@@
 \begin{equation}
-\label{eqn-FunctionDense}s
+\label{eqn-FunctionDense}
 f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(m \times 1)} \rightarrow x^{(l)} \in \mathbb{R}^{(n \times 1)}
@@
 \label{eqn-CXELoss}
-\text{CXE}\big[ y , y^* \big] = - \sum_{i=0}^{k-1} y_i \log_{10}(y^*_i) 
+\text{CXE}\big[ y , y^* \big] = - \sum_{i=0}^{k-1} y_i \ln(y^*_i) 
 \end{equation}
@@
 \big\langle \text{CXE}\big[ y , y^* \big]\big\rangle = 
-- \frac{1}{b}\sum_{n=0}^{b-1}\sum_{i=0}^{k-1} y_i^{(n)} \log_{10}(y^{*(n)}_i) 
+- \frac{1}{b}\sum_{n=0}^{b-1}\sum_{i=0}^{k-1} y_i^{(n)} \ln(y^{*(n)}_i) 
 \end{equation}
@@
 Thus the sum in Eq.
-(\ref{eqn-CXELoss}) contains mostly zero terms.
-The only non-zero term is the produce of $y_j$ and $\log_{10}(y^*_j)$.
+(\ref{eqn-CXELoss}) contains mostly zero terms, with the only exception at index $j$, where we have $y_j\ln(y^*_j) = \ln(y^*_j)$.
 Since the vector $y^*$ has been subject to the softmax activation function, we must have $y^*_j \in [0,1]$.
-This means that taking the log of this value returns a negative number.
-Multiplying by negative number returns a high loss when the activation of $y^*_j$ is low and a low cost when $y^*_j \approx 1$.
-We visualize this relationship in Fig.
+This means that taking the natural log of this value returns a negative number.
+Multiplying that by negative 1 returns a high loss when the activation of $y^*_j$ is low and a low cost when $y^*_j \approx 1$.
+We visualize this relationship for a single sample in Fig.
 (\ref{fig-CXELoss}):
@@
 (\ref{eqn-altLayerFunction}), This recursive nature combined with the dimensionality of the parameter object $\Theta$ makes an analytical solution to the optimization impractical \cite{Geron,Goodfellow,James}.
-We instead optimize the cost function with a gradient-based method.
-
-\paragraph*{}We can reduce the cost given a set of parameters, $J(\Theta)$, by moving each element in $\Theta$ with small steps in the direction of the negative partial derivative with respect to each parameter.
+We instead optimize the cost function with a numerical \textit{iterative} method \cite{Loy}.
+
+\paragraph*{}We can reduce the cost given a set of parameters, $J(\Theta)$, by repeatedly moving each element in $\Theta$ with small steps in the direction of the negative partial derivative with respect to each parameter.
 In the case of the high-dimensional $\Theta$ object, we compute the partial derivative with respect to each weight and bias in the form of the \textit{gradient vector}.
@@
 
-\paragraph*{}For the categorical cross entropy cost function, we can evaluate $\partial J / \partial x^{(L-1)}$ over a single sample as:
+\paragraph*{}For the categorical cross entropy cost function, we can evaluate $\partial J / \partial x^{(L-1)}$ over a single sample that belongs to class $i$ as:
 \begin{equation}
@@
 \frac{\partial J}{\partial x^{(L-1)}} = \frac{\partial J}{\partial y^*} =
-\frac{\partial}{\partial x^{(L-1)}}\big[ -y \log_{10} (y^*) \big] = -\frac{1}{\ln(10)}\sum_{i}\frac{y_{i}}{y^*_i}
-\end{equation}
-The value $\partial x^{(L-1)} / \partial z^{(L-1)}$ can be found by differentiating Eq. (\ref{eqn-elementActivation}) with respect to the input activations.
+\frac{\partial}{\partial y^*}\Big[ -y \ln (y^*) \Big] = -\frac{1}{y^*_i + \delta}
+\end{equation}
+We often introduce $\delta \approx 10^{-8}$ to prevent possible division by $0$ errors.
+The value $\partial x^{(L-1)} / \partial z^{(L-1)}$ can be found by differentiating Eq.
+(\ref{eqn-elementActivation}) with respect to the input activations.
 \begin{equation}
 \frac{\partial x^{(L-1)}}{\partial z^{(L-1)}} = \sigma^{'(l)} \big[ z^{(L-1)} \big]
+\end{equation}
+For a dense layer as in sec.
+(\ref{subsubsec-DenseLayer}) or a 2D-convolution layer as in sec.
+(\ref{subsubsec-Conv2DLayer}) $\partial z^{(L-1)} / \partial W^{(L-1)}$ is given by the derivative of Eq.
+(\ref{eqn-LinearTransform}) or Eq.
+(\ref{eqn-LinearTransform2}) with respect to $W^{(l)}$:
+\begin{equation}
+\frac{\partial z^{(L-1)}}{\partial W^{(L-1)}} = 
+\frac{\partial}{W^{(L-1)}}\Big[ W^{(L-1)}x^{(L-2)} + b^{(L-1)}\Big] = x^{(L-2)}
+\end{equation}
+\begin{equation}
+\frac{\partial z^{(L-1)}}{\partial W^{(L-1)}} = 
+\frac{\partial}{W^{(L-1)}}\Big[ \big( W^{(L-1)} * x^{(L-2)} \big) + b^{(L-1)}\Big] = x^{(L-2)}
+\end{equation}
+Finally, differentiating with respect to the bias array: $\partial z^{(L-1)} / \partial b^{(L-1)}$, we have:
+\begin{equation}
+\frac{\partial z^{(L-1)}}{\partial b^{(L-1)}} = \frac{\partial}{W^{(L-1)}}\Big[ W^{(L-1)}x^{(L-2)} + b^{(L-1)}\Big] = 1
 \end{equation}
@@
 \label{eqn-dWGeneral}
+\nabla_{W^{(l)}}J = \frac{\partial J}{\partial W^{(l)}} = 
+\frac{\partial J}{\partial x^{(l)}}\odot \partial\sigma^{(l)}[ z^{(l)} ] \cdot x^{(l-1)}
 \end{equation}
@@
 \label{eqn-dbGeneral}
-\end{equation}
+\nabla_{b^{(l)}}J = \frac{\partial J}{\partial b^{(l)}} = 
+\frac{\partial J}{\partial x^{(l)}}\odot \partial\sigma^{(l)}[ z^{(l)} ]
+\end{equation}
+Where $z^{(l)}$ are the linear activations defined in Eq.
+(\ref{eqn-LinearTransform}) and Eq.
+(\ref{eqn-LinearTransform2}).
+Note that each $z^{(l)}$ and $x^{(l)}$ are typically stored in memory during the forward pass in Alg.
+(\ref{algFeedForward}) to prevent the need to recompute them \cite{Geron2,Goodfellow}.
 
@@
 Each iteration in the \textit{for-loop} computes the gradient of the cost function $J$ with respect to the weight and bias arrays.
-Each element in those arrays is then the discrete gradient of that parameter.
-A practical application of this algorithm should include batches of samples instead of a single sample}
+Each element in those arrays $dW$ and $db$ is the discrete gradient of the cost due to that parameter.
+A practical application of this algorithm should include batches of samples instead of a single sample and a regularizing function at each step.}
 \label{algBackProp}
@@
 \begin{algorithmic}
-\REQUIRE Cost/Objective function $J$ and learning rate $\alpha$
-\REQUIRE Set of weighting parameters - $W^{(i)}, i \in \{0,1,....,L-1\}$
-\REQUIRE Set of bias parameters - $b^{(i)}, i \in \{0,1,....,L-1\}$
-\REQUIRE Set of layer activation function - $\sigma^{(i)}, i \in \{0,1,....,L-1\}$
-\REQUIRE Set of layer activation function derivatives - $\partial\sigma^{(i)}, i \in \{0,1,....,L-1\}$
-\REQUIRE Set of pre-nonlinear activation - $Z^{(i)}, i \in \{0,1,....,L-1\}$
-\REQUIRE Set of post-nonlinear activation - $X^{(i)}, i \in \{0,1,....,L-1\}$
+\REQUIRE Cost/Objective function $J$.
+\REQUIRE Set of Layer functions $f^{(i)}$.
+Each one contains a weighting array $W^{(i)}$, a bias array $b^{(i)}$, and activation function $\sigma^{(i)}$, the activation function derivative, $\sigma^{'(i)}$.
+In all cases, $i \in \{0,1,....,L-1\}$
+\REQUIRE Set of linear and non-linear activation arrays $z^{(i)}$ and $x^{(i)}$.
 
@@
 
-\paragraph*{}After (i) computing the gradient, we can scale it by a desired learning rate, $\alpha$ and (ii) add the gradient vector element-wise to the existing elements in $\Theta$ object.
+\paragraph*{}After (i) computing the gradient, we can scale it by a desired learning rate $\alpha$, and (ii) add the gradient vector element-wise to the existing elements in $\Theta$ object.
 By repeating steps (i) and (ii) in succession, we gradually drive the cost function to produces consistently lower and lower values across a data set \cite{Geron}.
 This is called \textit{gradient descent} and is the basis for many optimization algorithms.
-We show the general update rule on iteration $(i)$ for gradient based learning over a batch of $m$ samples in Eq.
+Let $\bar{J}$ be the avergae cost over a batch of $b$ samples.
+We show the general update rule on iteration $(i)$ for gradient based learning in Eq.
 (\ref{eqn-GradientLearning}).
@@
 \label{eqn-GradientLearning}
-\Theta^{(i)} = \Theta^{(i-1)} + (-\alpha)\frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big] \\
-\end{equation}
+\Theta^{(i)} = \Theta^{(i-1)} + (-\alpha) \nabla_{\Theta} \bar{J}
+\end{equation}
+Where $\Theta^{(i)}$ will give the set of new, updated parameters of the network.
 
@@
 \paragraph*{}An optimizer is the algorithm or procedure that is used by a machine learning model to achieve the lowest possible value of the cost function over a data set \cite{Geron}.
-Some models such as minimizing a \textit{mean-squared error} for linear regression model can be solve analytically, while high dimensional neural networks
-Standard gradient-based learning, as given by the parameter update rule in Eq.
-(\ref{eqn-GradientLearning}) is cumbersome and often prone errors such as vanishing or exploding gradients.
+Some models such as minimizing a \textit{mean-squared error} for linear regression model can be solve analytically, while high dimensional neural networks, such as the one used in this project, outlined in sec.
+(\ref{subsec-Architecture}), cannot be solved symbolically.
+Thus, we then employ an iterative gradient method, much like the one in Eq.
+(\ref{eqn-GradientLearning}).
+These standard gradient-based learning algorithms are cumbersome and often prone errors such as vanishing or exploding gradients.
 \cite{Geron,Goodfellow,Loy}.
-To combat this, model must often implement an algorithm that is more stable, and aggressive in it's ability to
+To combat this, model must often implement an algorithm that is more stable, and robust in it's ability to drive the cost function to a successively lower value.
 
@@
 It is a powerful optimizer with uses adaptive learning rate and momentum parameter.
-ADAM tracks an exponentially decaying average of past gradients, as well as exponentially decaying average of past squared gradients \cite{Geron}.
+ADAM tracks an exponentially decaying average of past gradients (see $s^{(i})$ in Eq.
+(\ref{eqn-ADAMupdate})), as well as exponentially decaying average of past squared gradients (see $r^{(i})$ in Eq.
+(\ref{eqn-ADAMupdate}))\cite{Geron}.
 This produces a far more aggressive optimizer at a higher computational cost.
@@
 \begin{split}
-s^{(i)} &= \rho_1 s^{(i-1)} + (1 - \rho_1) \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]  \\
-r^{(i)} &= \rho_2 r^{(i-1)} + (1 - \rho_2) \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big] \odot
-							\frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]  \\
+s^{(i)} &= \rho_1 s^{(i-1)} + (1 - \rho_1) \nabla_{\Theta} \bar{J}  \\
+r^{(i)} &= \rho_2 r^{(i-1)} + (1 - \rho_2) \Big[ \nabla_{\Theta} \bar{J} \odot \nabla_{\Theta} \bar{J} \Big]  \\
 s'^{(i)} &= \frac{s^{(i)}}{1-\rho_1^i} \\
@@
 \caption{Adaptive-Moments (ADAM) optimizer for a neural network. This algorithm is adapted from Goodfellow, \cite{Goodfellow}}
-\label{algAdaGrad}
+\label{alg-ADAM}
 
@@
 	\item Compute numerical gradient estimate of each sample in batch. This can be done with standard back-propagation in algorithm (\ref{algBackProp}) and 			 	normalize by batch size $m$:
-	\item $\nabla J \leftarrow \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]$
-
-	\item Compute first bias moment: $s \leftarrow \rho_1 s + (1 - \rho_1) \nabla J$
-	\item Compute second bias moment: $r \leftarrow \rho_2 s + (1 - \rho_2) \nabla J \odot \nabla J$
+	\item $\nabla \bar{J} \leftarrow \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]$
+
+	\item Compute first bias moment: $s \leftarrow \rho_1 s + (1 - \rho_1) \nabla \bar{J}$
+	\item Compute second bias moment: $r \leftarrow \rho_2 s + (1 - \rho_2) \nabla \bar{J} \odot \nabla \bar{J}$
 	\item First bias correction: $s' \leftarrow \frac{s}{1 - \rho_1^i}$
@@
 \subsection{Chosen Model Architecture}
-\label{sec-Architecture}
+\label{subsec-Architecture}
 
@@
 The layer structure of the neural network it's \textit{architecture} \ref{Goodfellow}.
-Most standard implementations of networks utilize a \textit{unimodal architecture} where the model is created with a single input layer \cite{N}
+Most standard implementations of networks utilize a \textit{unimodal architecture} where the model is created with a single input layer .
 

### 2020-11-22 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Progress on draft, Added new figures, removed old figures

@@
 \textcolor{red}{Insert spectrograms here}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=0.45\textwidth , height=0.2\textheight]{../Figures/AnalysisFrame}
+	\caption{A section of a violin bowing an $A4$ note, $1024$ samples long}
+	\end{subfigure}
 \caption{Spectrogram representations of various waveforms}
@@
 \end{equation}
-We show the effect of a Hanning window on a wae 
+We show the effect of a Hanning window on an analysis frame:
 \begin{figure}[H]
@@
 	\centering
-	%\includegraphics[width=\textwidth , height=0.2\textheight]{../FiguresFeatures/Auto_Correlation_4}
-	\caption{A section of a waveform, $1024$ samples long}
+	\includegraphics[width=\textwidth , height=0.2\textheight]{../Figures/AnalysisFrame}
+	\caption{A section of a violin bowing an $A4$ note, $1024$ samples long}
 	\end{subfigure}
@@
 	\centering
-	%\includegraphics[width=\textwidth , height=0.2\textheight]{../FiguresFeatures/Auto_Correlation_4}
-	\caption{The Same waveform with a Hanning Window Applied}
+	\includegraphics[width=\textwidth , height=0.2\textheight]{../Figures/WindowedFrame}
+	\caption{The same waveform with a Hanning Window Applied}
 	\end{subfigure}

### 2020-11-22 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisUtilities.py
Update ClassifierAnalysis

@@ -117,7 +117,6 @@ class AnalyzeModels:
         avgStdMatName =  self.modelName + " Avg Standard Confusion"
         avgHitMatName =  self.modelName + " Avg Hits Weighted Confusion"
         avgScrMatName =  self.modelName + " Avg Score Weighted Confusion"
-
         
         ClassifierMetrics.ExportConfusion(avgStandardConfMat,avgStdMatName,exptPath)
         ClassifierMetrics.ExportConfusion(avgHitsWeightedConfMat,avgHitMatName,exptPath)
@@ -183,6 +182,11 @@ class ClassifierMetrics :
             standardMatrix[x,y] += 1.                   # add counter
         return standardMatrix
 
+    def __Call__(self,confMat):
+        """ Compute a Series of Metrics From the confusion matrix per each class """
+        precisions = self.PrecisionScore(confMat)       # precision scores over all classes
+        recall = self.RecallScore(confMat)       # recall scores over all classes
+
     def AccuracyScore (self):
         """ Compute Recall Score of Data """    
         acc = 0
@@ -191,31 +195,29 @@ class ClassifierMetrics :
                 acc += 1
         return acc/ len(self.x)
 
-    def PrecisionScore(self):
+    def PrecisionScore(self,confMat):
         """ Compute Precision Score of Data """
-        confMat = self.StandardConfusion()
-        sumRow = np.sum(confMat,axis=1)     # sum across rows
-        prec = 0
-        for i in range(self.n_classes):     # each class
-            if sumRow[i] != 0:
-                p = confMat[i,i]/sumRow[i]  # precision of class i
-            else: 
-                p = 0
-            prec += p                       # add to total
-        return prec / self.n_classes        # avg over classes
+        sumRow = np.sum(confMat,axis=1)         # sum across rows
+        prec = np.zeros(shape=self.n_classes)   # store precision scores
+        for i in range(self.n_classes):         # each class
+            if sumRow[i] != 0:                  # if not zero
+                p = confMat[i,i]/sumRow[i]      # precision of class i
+            else:                               # div by zero
+                p = 0                           # zero
+            prec[i] += p                        # add to total
+        return prec                             # return precision
        
-    def RecallScore (self):
+    def RecallScore (self,confMat):
         """ Compute Recall Score of Data """
-        confMat = self.StandardConfusion()
-        sumCol = np.sum(confMat,axis=0)     # sum across cols
-        recl = 0
-        for i in range(self.n_classes):     # each class
-            if sumCol[i] != 0:
[…]

### 2020-11-23 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Main Thesis Draft

@@
 \end{quote}
-The result of such an analogy is a computer program that is reminiscent of the structure of the a brain.
-Where a biological brain uses these chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Geron,Levine}.
-
-\paragraph*{}A neural network can then be considered as mathematical function that seeks to produce an approximation $F^*$, of some usually unknown function $F$ .
-For audio recognition, $F$ is some function or series of functions that occurs in the brain which allows for a listener to process the sensation of audio, and map it to a known source object.
-For a neural network, function $F^*$ uses a set of parameters $\Theta$, to map a series of inputs, $x$ (called \textit{features}) to a series of outputs, $y$ (called \textit{predictions}) \cite{Goodfellow,James,Virtanen}.
-
-\paragraph*{}Over the course of their lives, humans will learn to map sounds to sources almost effortlessly \cite{Virtanen}.
-Given an example, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olson,White}.
-We can simplify the idea of humans recognizing sound as some function or operation that occurs within the brain, accepting an input sound, and produces an output label.
-Similarly, a neural network can be constructed, presented with \textit{features} of multiple, labeled sound waves and learns a set of parameters $\Theta$ that allows for the mapping to a source.
+The result of such an analogy is a computer program that is reminiscent of the a brain in that the program can \textit{learn} in a sense.
+Where a biological brain uses connections of chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Geron,Levine}.
+
+\paragraph*{}When a listener hears a sound, millions of neurons in their brain exchanges those chemical and electrical signals in such a way as to be able to identify the source of that sound \cite{Geron,Virtanen}.
+More conceptually, we can say that a listener is presented with a set of information $x$, which is air molecules vibrating near their tympanic membrane \cite{White}.
+That information is then passed into the brain where some function $F$ is used to model the incredibly complex set of neural connections.
+The output of that function is some label $y$, which the listener associates with a particular source \cite{Olson}.
+Similarly, we construct a neural network to accept a set of predictors $x$, which is passed into a function $F^*$ that is use to approximate $F$, and produce an output $y^*$, which predicts the source of the audio sample.
+
+\paragraph*{}A neural network can then be considered as mathematical function that seeks to produce an approximation $F^*$, of some the usually unknown function $F$.
+The function $F^*$ uses a set of parameters $\Theta$, to map a series of inputs, $x$ (called \textit{features}) to a series of outputs, $y$ (called \textit{predictions}) \cite{Goodfellow,James,Virtanen}.
+Over the course of their development, humans will be able to learn to match sounds to sources with relative ease, given the appropriate labels.
+In a similar manner, out neural network is present a collection of sound files and predictors and a complementary set of labels indicating the source of each sound.
 
@@
 A classification task involves mapping the input data, $x$ to one of $k$ possible \textit{classes}, each represented by an integer, $0$ through $k-1$.
-Each of the $k$ classes represents a particular musical instrument that could have produced the sound-wave in the audio file \cite{Goodfellow,Loy,Virtanen}.
+Each of the $k$ classes represents a particular musical instrument or sound source that could have produced the sound-wave in the audio file \cite{Goodfellow,Loy,Virtanen}.
+In this section we detail the nature of a general neural network.
 
@@
 
-\paragraph*{}A Neural Network is simply a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Goodfellow,Loy}.
+\paragraph*{}A Neural Network is a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Goodfellow,Loy}.
 Each layer represents an operation that takes some real input, typically an array of real double-precision floating-point numbers, and returns a modified array of new double-precision floating-point numbers.
 The exact nature of this operation can be very different depending on the layer type or where it sits within the network.
+The output of one layer is passed forward and use as the input for the next layer.
 It is this process of transforming inputs successively in a particular order until an output is attained that makes up the core functionality of a neural network \cite{Geron,Loy}.
-This output encodes the models final "decision" given a unique input.
-
-\paragraph*{}Other than inspiration from the brain, Neural Networks are name \textit{networks} because of their nested composition nature.
-The model can be represented by a linked computational graph which successively maps exactly how the repeated composition is structured.
-Each node in the graph represents a \textit{layer}, which executes a particular prescribed mathematical function \cite{Goodfellow}.
+The output of the final layer encodes the "decision" of the model given a particular input.
+
+\paragraph*{}Other than inspiration from the brain, Neural Networks are named \textit{networks} due to their successive chained or nested composition nature.
+A standard representation of a neural network is often a linked list or computational graph structure.
+This maps out exactly how the repeated compositions are structured and organizes the flow of information in more complicated networks.
+Each node in the computational graph represents a \textit{layer}, which executes a particular prescribed mathematical function \cite{Goodfellow}.
 In the case of a \textit{linear, feed-forward} network, information passes in a single direction, to produce an output.
@@
 \label{eqn-FunctionGraph}
-F(x) = x \rightarrow f^{(0)}(x) \rightarrow f^{(1)}(x) \rightarrow ..... \rightarrow
-f^{(L-2)}(x) \rightarrow f^{(L-1)}(x) \rightarrow y
+F^*(x) = x \rightarrow f^{(0)} \rightarrow f^{(1)} \rightarrow ..... \rightarrow
+f^{(L-2)} \rightarrow f^{(L-1)} \rightarrow y
 \end{equation}
@@
 \end{equation}
-Each function $f^{(l)}$ represents a layer of the network model.
-The number of layers in a neural network is referred to as the network \textit{depth}.
-The dimensionality of each layer is referred to as the network \textit{width} \cite{Geron,Loy}.
-
-\paragraph*{}A network model that contains $L$ unique layers is said to be an $L$-Layer Neural Network, with each layer usually indexed by a superscipt, $0$ through $L-1$.
-Layer $0$ is said to be the \textit{input layer} and layer $L-1$ is said to be the \textit{output layer}.
-The function that represents a layer $(l)$ is given by
-\begin{equation}
-\label{eqn-LayerFunction}
-f^{(l)} : x \in \mathbb{R} \rightarrow y \in \mathbb{R}
-\end{equation}
-The value of $x$ can also be index by layer, we call the array $x^{(l)}$ the \textit{activations} of layer $l$ \cite{Goodfellow,Loy}.
-
-\paragraph*{}The model is recursive by nature, the activations from one layer, $l-1$, are used to directly produce the activations of the next successive layer $l$.
-Thus Eq.
-(\ref{eqn-LayerFunction}) can be alternatively written as:
+The number of layers in a neural network is referred to as the network \textit{depth}. The dimensionality of each layer is referred to as the network \textit{width} \cite{Geron,Loy}.
+A network model that contains $L$ unique layers is said to be an $L$-Layer Neural Network, with each layer indexed by a superscipt, $(0)$ through $(L-1)$.
+Layer $(0)$ is said to be the \textit{input layer} and layer $L-1$ is said to be the \textit{output layer} \cite{Geron,Loy}.
+
+\paragraph*{}Due to the chained nature of the model, the activations from some layer, $(l-1)$, are used to directly produce the activations for the next successive layer $(l)$.
+The function that represents a layer $(l)$ is given by:
 \begin{equation}
@@
 
+\paragraph*{}Below we outline a standard "forward pass" algorithm for a general feed-forward deep neural network.
+We presume each layer to be a node in a computational graph that contains a method "\textit{call}" which executes the layer's main function as in Eq.
+(\ref{eqn-altLayerFunction}).
+Each call method is presumed to be composed of two steps: a (i) linear transformation, and a (ii) non-linear activation function.
+See sec.
+(\ref{subsec-Layers}) for more detials.
+Additionally, each node contains a pointer "\textit{next}" which gives the next layer in the network chain.
+Each layer should also store it's linear activations, $z^{(l)}$ and it's output activations $x^{(l)}$ for training purposes.
+This algorithm is adapted from Goodfellow, \cite{Goodfellow}.
+
 \begin{algorithm}[H]
 \caption{Forward propagation system in a standard deep neural network.
-Each iteration in the main \textit{for-loop} represents the execution of a layer, and passing the result to the "next" layer function.
-We assume each layer to follow a two-step structure, being (i) a linear transformation as in Eq.
-(\ref{eqn-LinearTransform}) and (ii) an element-wise non-linear activation function as in Eq.
-(\ref{eqn-elementActivation}).
-A practical application of this algorithm should include batches of samples instead of a single sample.
-\textcolor{red}{I Want to include this algorithm for context - especially on the programming end, but am not sure where to put it. }}
-\label{algFeedForward}
+Each layer is presumed to be a node in a linked computational graph.
+This example has been setup to assume one input layer, and one output layer.
+Practical implementations should include mini-batches of data as opposed to a single sample.}
+\label{alg-FeedForward}
 
 \begin{algorithmic}
-\REQUIRE Network with $L$ layers - $0,1,2,....,L-2,L-1$
-\REQUIRE Set of layer functions $f^{(l)}, l \in 0,1,2,....,L-2,L-1$ made up of a linear transformation and a non-linear transformation.
+\REQUIRE Set of Layer functions $f^{(i)}$, $i \in [0,1,2,3,...,L-1]$.
 \REQUIRE Input sample - $x^{(0)}$
 
-If training the network, the intermediate layer activations must be stored for back-propagation. Otherwise, they may be discarded. \\
-$Z = \{\} \leftarrow$ array to hold pre-activations \\
-$X = \{\} \leftarrow$ array to hold final activations \\
-
-\FOR {$l = 1,2,...,L-2,L-1$}	
-	\item Evaluate Linear Transformation
-	\item $z^{(l)} \leftarrow W^{(l)} x^{(l-1)} + b^{(l)}$ 
-	\item Apply non-linear Activation Function
-	\item $x^{(l)} \leftarrow \sigma^{(l)} \big[ z^{(l)} \big]$ 
-	\item Store values for later use in optimizer, otherwise can be discarded.
-	\item $Z \leftarrow Z.add(z^{(l)})$
-	\item $X \leftarrow X.add(x^{(l)})$
+Set the current layer to be the input layer: \\
+$f^{(i)} \leftarrow f^{(0)}$
+\FOR {Layer $i \in [1,2,3,...,L-1]$}
+	\item Run "Call" Method with current activations, transform activations:
+	\item $x^{(i)}$ = $f^{(i)}$.call($x^{(i-1)}$)
+	\item Move to the next layer in the network:
+	\item $f^{(i)} \leftarrow f^{(i)}$.next()
 \ENDFOR
-
-\item Network final prediction is last object in $X$ array.
-\item $y^* \leftarrow x^{(L-1)} = X[-1]$
-\item Return the pre-nonlinear activations and final-nonlinear activations:\\
-\RETURN $Z , X$
-
+\item Return the network's output, which are the output activation of the final layer \\
+\RETURN $x^{(L-1}$
 \end{algorithmic}
@@
 
-\subsection{Layers Used in Classification Neural Network}
+\subsection{Layers Used in this Classification Neural Network}
 \label{subsec-Layers}

### 2020-11-23 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisUtilities.py

@@ -89,10 +89,7 @@ class AnalyzeModels:
             labels = data["Int Label"].to_numpy()
             predns = data["Int Prediction"].to_numpy()
             scores = data["Confidence"].to_numpy()
-
             ComputeMetrics = ClassifierMetrics(self.n_classes,labels,predns,scores) 
-            metrics = ComputeMetrics.MetricScores()
-            self.metricsArray[i] = metrics
 
             # Create & Names for Confusion matrices
             stdMatName =  self.modelName + str(i) + " Standard Confusion"
@@ -103,6 +100,11 @@ class AnalyzeModels:
             standardConfMat = ComputeMetrics.StandardConfusion()
             hitsWghtConfMat = ComputeMetrics.HitsWeightedConfusion()
             scrsWghtConfMat = ComputeMetrics.ScoreWeightedConfusion()
+
+            # Compute Metrics for this split
+            
+            metrics = ComputeMetrics.MetricScores(standardConfMat)
+            self.metricsArray[i] = metrics
 
             # Add To average Conf Mats
             avgStandardConfMat += standardConfMat
@@ -130,7 +132,11 @@ class AnalyzeModels:
         os.chdir(homePath)
         """
 
+        # Compute metrics avg. across all classes
         self.ConfusionMatrix = avgStandardConfMat
+
+
+
         return self
 
 class ClassifierMetrics :
@@ -185,14 +191,14 @@ class ClassifierMetrics :
             standardMatrix[x,y] += 1.                   # add counter
         return standardMatrix
 
-    def __Call__(self,confMat):
-        """ Compute a Series of Metrics From the confusion matrix per each class """
-        precisions = self.PrecisionScore(confMat)       # precision scores over all classes
-        recall = self.RecallScore(confMat)       # recall scores over all classes
-
-    def AccuracyScore (self):
+    def AccuracyScore (self,confMat):
         """ Compute Recall Score of Data """    
         accy = np.zeros(shape=self.n_classes)   # store accuracy scores
+        for i in range(self.n_classes):         # number of classes
+            accy[i] = confMat[i,i]              # True pos.
+        _sum = np.sum(confMat)
+        accy /= _sum                            # divide by all predictions
+        return accy                             # return accuracy
 
     def PrecisionScore(self,confMat):
         """ Compute Precision Score of Data """
@@ -218,17 +224,13 @@ class ClassifierMetrics :
[…]

### 2020-11-23 SignalClassifier/ClassifierHybrid/ModeUtilities.py

@@ -9,7 +9,6 @@ Instrument Classifier v0
 
 import numpy as np
 import os
-from sklearn.model_selection import train_test_split
 from sklearn.preprocessing import StandardScaler
 
 import SystemUtilities as sys_utils

### 2020-11-23 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisMAIN.py
Added Metrics figures, Updated Post-Processing script

@@ -28,8 +28,20 @@ if __name__ == '__main__':
 
     # Run Main program
     Program = utils.AnalyzeModels(modelName,dataPath,n_classes)
-    Program.__Call__(exptPath)
+    encode,decode = Program.MakeDecodeDictionary()
 
+    Program.__Call__(exptPath)
     Program.ExportMetrics(exptPath)
+
+
+    # Compute & Plots Avg. metrics per class
+    _ = np.arange(10)
+    ComputeMetrics = utils.ClassifierMetrics(n_classes,_,_,_)
+    scores = ComputeMetrics.MetricScores(Program.ConfusionMatrix)
+    os.chdir("C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\Thesis\\FiguresMetrics")
+    for i in range(n_classes):         # each class
+        className = decode[i]
+        print(className,Program.counts[i])
+        utils.ClassifierMetrics.PlotMetricsForClass(scores[:,i],className,False,True)
     
     print("=)")

### 2020-11-23 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisUtilities.py

@@ -44,6 +44,20 @@ class AnalyzeModels:
         self.n_classes = n_classes
         self.outputFile = self.modelName+"@"+self.startTime+"@ANALYSIS"+".csv"
 
+    def MakeDecodeDictionary(self):
+        """ Make Decoder Dictionary From Local Path """
+        decodeFileName = self.modelName + "Categories.csv"
+        decodeFullPath = os.path.join(self.dataPath,decodeFileName)
+        decoder = {}
+        encoder = {}
+        rawData = pd.read_csv(decodeFullPath)
+        Ints,Strs = rawData.iloc[:,0],rawData.iloc[:,1]   
+        self.counts = rawData.iloc[:,2]
+        for Int,Str in zip(Ints,Strs):          # iterate by each
+            encoder.update({str(Str):int(Int)})
+            decoder.update({int(Int):str(Str)})
+        return encoder,decoder
+
     def GetKeywordFiles(self,keyword):
         """ Find files in path w/ Keyword in name """
         pathList = []
@@ -56,7 +70,7 @@ class AnalyzeModels:
 
     def ExportMetrics(self,outputPath):
         """ Export Metrics Array to Local path """
-        colNames = ["Accuracy","Precision","Recall","Loss"]
+        colNames = ["Accuracy","Precision","Recall"]
         outputFrame = pd.DataFrame(data=None,index=None)
         outputFrame["CLF"] = [x.split("\\")[-1] for x in self.predictionFiles]
         for i in range(len(colNames)):
@@ -73,7 +87,7 @@ class AnalyzeModels:
         homePath = os.getcwd()
 
         nRows = len(self.predictionFiles)
-        nCols = 4
+        nCols = 3
         self.metricsArray = np.empty(shape=(nRows,nCols))
 
         # Initialize 3 Average Confusion matrices
@@ -104,6 +118,7 @@ class AnalyzeModels:
             # Compute Metrics for this split
             
             metrics = ComputeMetrics.MetricScores(standardConfMat)
+            metrics = np.mean(metrics,axis=1)
             self.metricsArray[i] = metrics
 
             # Add To average Conf Mats
@@ -134,9 +149,7 @@ class AnalyzeModels:
 
         # Compute metrics avg. across all classes
         self.ConfusionMatrix = avgStandardConfMat
-
-
-
+       
         return self
 
 class ClassifierMetrics :
@@ -232,7 +245,7 @@ class ClassifierMetrics :
         scoreMatrix[2] = self.RecallScore(confMat)
[…]

### 2020-11-23 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis

@@
 \paragraph*{}We have assembled training data samples than can be grouping in 38 classes of unique sources listed below:
-\begin{multicols}{2}
-\begin{enumerate}
-	\item Alto Flute
-	\item Alto Saxophone
-	\item Banjo
-	\item Bass
-	\item Bass Clairnet
-	\item Bass Flute
-	\item Bassoon
-	\item Bass Tromobe
-	\item B$\flat$ Clarinet
-	\item Bells
-
-	\item Cello
-	\item Clarinet \textcolor{blue}{Check this!}
-	\item Contrabassoon
-	\item Crotale
-	\item E$\flat$ Clarinet
-	\item English Horn
-	\item Flute
-	\item Guitar
-	\item Hi-Hat
-	\item Horn
-		\columnbreak
-	\item Mandolin
-	\item Marimba
-	\item Oboe
-	\item Sawtooth Wave
-	\item Saxophone (Tenor)
-	\item Sine Wave
-	\item Soprano Saxophone
-	\item Square Wave
-	\item Tenor Trombone
-	\item Triangle Wave
-
-	\item Trombone
-	\item Trumpet (B$\flat$)
-	\item Tuba
-	\item Vibraphone
-	\item Violin
-	\item Viola
-	\item White Noise
-	\item Xylophone
-	\item
-	\item
-\end{enumerate}
-\end{multicols}
-
-\paragraph*{}Rather than explore each class individually, we can examine the properties of groupings of musical instrumentsby using the \textit{Hornbostel-Sachs} system \textit{red}{Citation needed!}.
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{||c|c|c||c|c|c||}
+\hline
+\textbf{Class Index} & \textbf{Class Name} & \textbf{Count} & \textbf{Class Index} & \textbf{Class Name} & \textbf{Count} \\
+\hline \hline
+$0$ & Alto Flute & $72$ & & \\ \hline
+$1$ & Alto Saxophone & 128&  \\ \hline
+$2$ & Banjo &
+$3$
+$4$
+$5$
+
+\end{tabular}
+\end{center}
+\caption{Instruments categories used in the classification task. Note that the network uses only integers to indentify sources while the }
+\end{figure}
+
+\paragraph*{}Rather than explore each class individually, we can examine the properties of groupings of musical instruments by using the \textit{Hornbostel-Sachs} system \textit{red}{Citation needed!}.
 In this syetem, musical instruments or sound sources can be divided up into four broad categories based on the nature of the sound-producing material.

### 2020-11-23 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Performance on Thesis Draft

@@
 The exact ratio of sizes between these subsets varies depending on the task \cite{Goodfellow,Geron2,Mitchell}, however we choose to generally use around $90\%$ training samples and $10\%$ testing samples.
-
-% ================================================================
-
-\subsection{Cross Validation}
+By doing this train-test split scheme, we are confirming or disproving the predictive power of the model.
+If the model score high within it's training subset, but low within the testing subset, this can indicate a model that is \textit{overfitted}, and will not perform well on other unseen samples \cite{Geron}.
+
+% ================================================================
+
+\subsection{K-Folds Cross Validation}
 \label{subsec-XValidation}
 
-\paragraph*{}The optimization of neural networks are heavily dependent on initial conditions of parameters and the data sets.
-We consider models that suffer from this phenomenon to be \textit{high-variance} models \cite{James}.
-To eliminate any concerns of possible out-liers, or abnormalities that arise, it is common to implement a resampling method called \textit{cross validation} (Also called X-validation) \cite{Geron,Goodfellow}.
-This process involves taking a data set containing $N$ unique samples and dividing it into $K$ non-overlapping subsets.
-$1$ subset is reserved to evaluate the model, and $K-1$ remaining subsets are used to train the model.
-For each of the $K$ models, we can evaluate a series of performance metrics, and store any model parameters.
-We can compare any one model to the other $K-1$ models to ensure that each network is performing consistently, despite small changes in the initial data set.
-We detail pseudo-code for a $K$-Fold Cross Validation algorithm.
+\paragraph*{}We can expand on the idea of a train/test split with a resampling method called \textit{K-Folds Cross Validation} (Also called X-validation) \cite{Geron,James}.
+Suppose we have machine learning model $F^*$, with a set of trainable parameters $\Theta$.
+We also have a data set $X$ and a set of appropriately labeled targets, $Y$, each of which contain $N$ samples.
+For $K$-folds X-val, we divide the full data set into $K$ subsets (called \textit{folds}), each with size $K/N$:
+\begin{equation}
+\label{eqn-XValSplit}
+X,Y \rightarrow \Big\{ \big(X^{(0)},Y^{(0)}\big) , \big(X^{(1)},Y^{(1)}\big) , ... , \big(X^{(K-1)},Y^{(K-1)}\big) \Big\}
+\end{equation}
+For each iteration, $k \in [0,1,2,...,K-1]$ we reserve a single subset of data $\big(X^{(k)},Y^{(k)}\big)$ to use as a testing subset.
+We use the remaining $K-1$ subsets as training data.
+We fit the model with the data and labels to produce a model $F^{*(k)}$ which as set of parameters $\Theta^{k}$.
+We return the the test set, and run predictions on this unseen data subset.
+We compare those predictions to the corresponding set of labels $Y^{(k)}$ and evaluate the result of any selected performance metrics.
+
+\paragraph*{}The output of cross validation is $K$ models that are all trained and evaluated on overlapping subsets of the full data.
+Each model $F^*$, shows a possible outcome of training the network given a subset of data samples, and a particular set of initial parameters.
+It has a corresponding set of learned parameters $\Theta^*$, as defined in Eq.
+(\ref{eqn-Theta}) that it uses to make any predictions.
+We can compare the performance of each model and test if they produce similar outcomes, which indicates that the model will be able to consistently generalize to new, unseen samples.
 
@@
 \caption{A $K$-Fold Cross Validation program.}
-\label{algFeedForward}
-
+\label{alg-CrossValidation}
 \begin{algorithmic}
 \REQUIRE Untrained Network or related learning algorithm, $F^*$
-\REQUIRE A full labeled data set of $N$ samples. $X^{(i)}$, $i \in {0,1,2,...,N-1}$
+\REQUIRE A full labeled data set $(X,Y)$ of $N$ samples
 \REQUIRE Number of splits in Cross validation, $K$
@@
 Divide Data into $K$ non-overlapping subsets $x_{i}$, each with roughly $N/K$ samples \\
-$X \rightarrow \big\{ x_{0}, x_{1}, x_{2}, ..., x_{K-2},  x_{K-1} \big\}$ \\
+$X,Y \rightarrow \Big\{ \big(X^{(0)},Y^{(0)}\big) , \big(X^{(1)},Y^{(1)}\big) , ... , \big(X^{(K-1)},Y^{(K-1)}\big) \Big\}$ \\
 Performance History $\leftarrow \{\}$
 
-\FOR {$j = 0,1,2,3,...,K-2,K-1$}
+\FOR {$k = 0,1,2,3,...,K-2,K-1$}
 	\item Reset all parameters in $F^*$ to a random "untrained" state
 	\item Set aside testing data subset
-	\item $X_{test} \leftarrow x_{j}$
+	\item $X_{test} \leftarrow X^{(k)}$
+	\item $Y_{test} \leftarrow Y^{(k)}$
 	\item Concatenate the remaining subsets into training data set
-	\item $X_{train} =\leftarrow x_{i \neq j}$
-	\item Train the model, $F^*$ with the $X_{train}$ data set
-	\item Evaluate the trained model with the $X_{train}$ data set, and compute value of metric function(s) $P$
+	\item $X_{train} \leftarrow X^{(i \neq j)}$
+	\item $Y_{train} \leftarrow Y^{(i \neq j)}$
+	\item Train the model, $F^*$ with the $X_{train}$ and $Y_{train}$ subset.
+	\item Evaluate the trained model with the $X_{test}$ and $Y_{test}$ data set, and compute value of metric function(s) $P$
 	\item Store Performance $P$ in Performance History array
-\ENDFOR
-
-Compare performance results, and adjust model, parameters as needed, and repeat if desired.
-
+\ENDFOR \\
+Compare performance results, and adjust model or parameters as needed, and repeat if desired. \\
+Run additional analysis on performance metrics.
 \end{algorithmic}
@@
 
-\paragraph*{}The output of cross validation is $K$ models that are all trained and evaluated on overlapping subsets of the full data.
-Each model $F^*$, shows a possible outcome of training the network given a subset of data samples, and a particular set of initial parameters..
-It has a corresponding set of learned parameters $\Theta^*$, as defined in Eq.
-(\ref{eqn-Theta}) that it uses to make any predictions.
+\paragraph*{}Cross Validation is particularly useful in models such as neural networks because they suffer from the phenomenon of \textit{high-variance}, which means that small changes in initial conditions can drastically change the outcome of the model \cite{James}.
+Cross validation allows us to control these initial conditions by training the model on similar, but non-identical subsets of data, along with a slightly different set of initial parameters.
+This repetition allows us to explore the model's behavior over a range of possible initial conditions and validation sets, to ensure that the network is functions as expected over multiple trials.
+This also eliminates the fear of "unique" cases where the model happens to perform exceptionally well or exceptionally poorly given a random set of initial parameters \cite{Geron}.
 
@@
 While the neural network itself uses the cost function as it's sole objective to optimize, we also require a set of more human-readable functions.
-For example, a loss score of $1.075$ over a given subset of previously unseen samples provides us with no real information as to how well the network is performing at it's designed task.
+For example, an average loss score of $1.075$ over a given subset of previously unseen samples provides us with no real information as to how well the network is performing at it's designed task.
 In this section, we introduce a set of functions and metrics than enable a more tangible interpretation of the model's performance.
@@
 
-\paragraph*{}The confusion matrix (also called a confusion table) is a very quick, often graphical model that can be used to show how a classifier model performs over a subset of predictions.
+\paragraph*{}The \textit{standard confusion matrix} (also called a confusion table) is a very quick, often graphical model that can be used to show how a classifier model performs over a subset of predictions.
 The general idea of this object is count the number of times class $i$ is predicted to be in class $j$, and vice-versa \cite{Geron}.
@@
 A confusion matrix with relatively large values in main diagonal indicates a model that consistently predicts correct labels \cite{Geron}.
+Below we present some "dummy" confusion matrices as numerical arrays, and a corresponding heat-map equivalent.
 
@@
 
-	\begin{subfigure}[h]{0.45\textwidth}
+	\begin{subfigure}[h]{\textwidth , 0.8\textheight}
 	\begin{center}
@@
 	\end{subfigure}
-	\begin{subfigure}[h]{0.45\textwidth}
+	\begin{subfigure}[h]{\textwidth , 0.8\textheight}
 	\begin{center}
@@
 	\end{subfigure}
-	\begin{subfigure}[h]{0.45\textwidth}
-	\begin{center}
-	\textcolor{red}{Images of Confusion Matrices Go Here!} 
-	\end{center}
-	\end{subfigure}
-	\begin{subfigure}[h]{0.45\textwidth}
-	\begin{center}
-	\textcolor{red}{Images of Confusion Matrices Go Here!} 
-	\end{center}
-	\end{subfigure}
+
 \caption{Example Confusion Matrices for $k$-classes tasks}
-\label{fig-ConfMat}
+\label{fig-DummyConfMat}
 \end{figure}
+
+\paragraph*{}In addition to the standard confusion matrix, we can also weight entries by prediction score.
+Rather than adding $+1$ to each entry $C_{i,j}$ where appropriate, we instead add the \textit{probability} value, which is bounded $[0,1]$ (See softmax activation function in sec.
+\ref{subsubsec-Softmax})).
+This allows us to bake in the predictive \textit{confidence} into the confusion matrix.
+For example, two correct predictions with a score $0.2$ are weighted equally to a single incorrect prediction of $0.4$.
+This is useful for identifying a classifier that makes correct predictions, but only by smaller threshold.
+This can almost be through of as assigning "partial credit" to each prediction.
 
@@
 
+\paragraph*{}
+
 % ================================================================

### 2020-11-25 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Added New TDE features, updated Figures

@@
 \begin{center}
+
 	\begin{subfigure}{0.45\textwidth}
@@
 	\end{subfigure}
+
 	\begin{subfigure}{0.45\textwidth}
@@
 	\end{subfigure}
+
 	\begin{subfigure}{0.9\textwidth}
@@
 	\end{subfigure}
+
 \end{center}
@@
 
-\paragraph*{}Classification tasks require a set of inputs that are used to make the decision as to which class the sample belongs to.
+\paragraph*{}Classification tasks require a set of inputs  .
 These inputs are called \textit{predictors} or \textit{features} \cite{James,Loy,Serizel}.
@@
 However, a computer representation of a waveform is an array-like structure of values sampled discretely in time and volume \cite{Virtanen,Liu}.
-Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks \cite{Serizel}.
-We must develop a set of features or predictors that can describe important properties of the waveform in an efficient manner \cite{Goodfellow,James}.
+Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks so we must develop a set of features or predictors that can describe important properties of the waveform in an efficient manner \cite{Goodfellow,James,Serizel}.
 
@@
 For each feature, we visualize the distribution in across each class in the form as box-plots.
-Each feature has been normalize to have a zero mean, and unit-variance across all classes.
-
-\textcolor{red}{Describe nature of features w/ separation boundaries}
-
-\newpage
+Each feature has been normalized to have a zero mean, and unit-variance across all classes.
+
+% ================================
+
+\subsubsection{Decision Boundaries}
+
+\paragraph*{}A trained classifier makes a prediction in the form of a statistical likelihood of a sample belonging to a particular class \cite{Goodfellow,James}.
+A $k$- categories classifier contains $k$ output neurons, each one representing a class.
+When a set of features is presented to the classifier, the value contained within each neuron is the "confidence" on the interval $[0,1]$ that a sample belongs to that class.
+For example, if neuron $q$ has an activation value of $0.25$, we say that there is a $25\%$ chance that the sample belongs to class $q$.
+Most commonly, we take the neuron with the highest activation value to be the chosen class, even if the next highest activation is a close second \cite{Loy}.
+
+\paragraph*{}This concept stems from the idea that a trained neural network classifier is basing its predictions by generating \textit{decision boundaries} in feature space \cite{Loy,James,Serizel}.
 
@@
 \textcolor{red}{Insert spectrograms here}
-
-	\begin{subfigure}{1.0\textwidth}
-	\centering
-	\includegraphics[width=0.45\textwidth , height=0.2\textheight]{../Figures/AnalysisFrame}
-	\caption{A section of a violin bowing an $A4$ note, $1024$ samples long}
-	\end{subfigure}
 \caption{Spectrogram representations of various waveforms}
@@
 \end{figure}
+
+% ================================
+
+\subsubsection{Frame Blocking}
+\label{subsubsec-FrameBlocking}
 
@@
 
+% ================================
+
+\subsubsection{Windowing}
+\label{subsubsec-Windowing}
+
 \paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame.
@@
 The Fourier Transform assumes that an integer number of signal periods fit within each analysis frame, however this is rarely the case.
-A transform of this kind of signal can lead to \textit{spectral leakage} where energy appears to "leak" into adjacent frequency bins \textcolor{red}{Citation needed}.
+Transforming a signal with to \textit{spectral leakage} where energy appears to "leak" into adjacent frequency bins \textcolor{red}{Citation needed}.
 This result is a frequency domain that is not an accurate representation of the equivalent time domain.
@@
 Doubling the size of each analysis frame allows us the synthetically double the resolution in frequency-space, while retaining the resolution in time-space \cite{Virtanen}.
+
+% ================================
+
+\subsubsection{Discrete Fourier Transform}
+\label{subsubsec-DFT}
 
@@
 For consistency between samples, each waveform is padded or truncated to contain the same number of samples $M$.
+The number of samples $M$ is chosen to correspond the number of sample needed to make the $N \times k$ spectrogram matrix.
+This way,t he spectrogram and time-series features are representative of the same time interval in the file sample.
 Time space is indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
@@
 (\ref{fig-AnalysisFrames}), then the TDE approximates the energy in that frame.
-A frame with a high TDE indicates a generally large amplitude, and a frame with a low TDE indicates a generally small amplitude.
-(i.e.
-the signal has not started or is decaying)
-
-\paragraph*{}We adapt this TDE to \textbf{compute the time domain envelope of the full waveform}.
-Since the maximum amplitude of each waveform array has been normalized to $\pm 1$, the TDE represents a consistent measurement of energy in the full time-domain signal \cite{Liu}.
-The TDE is computed as the RMS-Energy of the waveform, $s$ and is given by \cite{Olson,Serizel}:
+A frame with a high TDE indicates a generally large amplitude, and a frame with a low TDE indicates a generally small amplitude, i.e.
+the signal has not started or is decaying.
+The small size of each analysis frame makes computing a TDE for each impractical, and create a very high-dimensional feature vector.
+This would also cause problems as some waveforms may have an initial attack that differs in time by a few analysis frames.
+Computing TDE for each frame would therefore introduce temporal bias, as the same waveform delayed by a few milliseconds would generate a wildly different set of predictor values \cite{Serizel}.
+
+\paragraph*{}One way to mitigate this is to group analysis frames together and compute the TDE of a collection of frames.
+This way, small most waveforms will produce an identical set of features to a time-delayed version of itself.
+By choosing a sufficiently large number of TDE values, we can also generate n approximation of than amplitude envelope of the time-series waveform.
+This comes at a higher computational cost, and a previously mentioned higher dimensional feature vector
+
+\paragraph*{}We adapt this TDE to \textbf{compute the time domain envelope over $5$ non-overlapping analysis frames}.
+Since the maximum amplitude of each waveform array has been normalized to $\pm 1$, the TDE represents a consistent measurement of energy in each waveform subset.
+\cite{Liu}.
+The TDE is computed as the RMS-Energy of the waveform, $s$ and the $j$-th TDE value is given by \cite{Olson,Serizel}:
 \begin{equation}
 \label{eqn-RMS}
-\text{RMS}\big[ s \big] = \sqrt{\frac{1}{M} \sum_{i=0}^{M-1} s[i]^2}
+\text{TDE}_j\big[ s \big] = \sqrt{\frac{1}{Q} \sum_{i=n}^{n+Q} s[i]^2}
 \end{equation}
@@
 %textcolor{red}{Plot of TDE Feature Here}
-\includegraphics[scale=0.3]{../FiguresFeatures/Time_Domain_Env}
+\includegraphics[scale=0.3]{../FiguresFeatures/TDE}
 \end{center}
@@
 %\textcolor{red}{PLOT OF ZXR FEATURES HERE}
-\includegraphics[scale=0.3]{../FiguresFeatures/Zero_X-Rate}
+\includegraphics[scale=0.3]{../FiguresFeatures/ZXR}
 \end{center}
@@
 %\textcolor{red}{PLOT OF TCM FEATURES HERE}
-\includegraphics[scale=0.3]{../FiguresFeatures/Time_Center_of_Mass}
+\includegraphics[scale=0.3]{../FiguresFeatures/TCM}
 \end{center}
@@
 	\includegraphics[width=\textwidth , height=0.2\textheight]
-		{../FiguresFeatures/Auto_Correlation_1}
+		{../FiguresFeatures/ACC_1}
 	\caption{ACC $k=1$}
@@
 	\includegraphics[width=\textwidth , height=0.2\textheight]
-		{../FiguresFeatures/Auto_Correlation_2}
+		{../FiguresFeatures/ACC_2}
 	\caption{ACC $k=2$}
@@
 	\includegraphics[width=\textwidth , height=0.2\textheight]
-		{../FiguresFeatures/Auto_Correlation_3}
+		{../FiguresFeatures/ACC_3}
 	\caption{ACC $k=3$}
@@
 	\includegraphics[width=\textwidth , height=0.2\textheight]
-		{../FiguresFeatures/Auto_Correlation_4}
+		{../FiguresFeatures/ACC_4}
 	\caption{ACC $k=4$}
@@
 This allows us to investigate the periodicity of the frequency spectrum, which highlights phenomena such as overtones or echoes in the signal\cite{Virtanen}.
-Ceptrum coefficients are commonly used to speech identification and are very prolific in sound recognition tasks \cite{Serizel,Sahidullah,Liu}.
+Cepstrum coefficients are commonly used to speech identification and are very prolific in sound recognition tasks \cite{Serizel,Sahidullah,Liu}.
 
@@
 %\textcolor{red}{PLOT OF FCM FEATURES HERE}
-\includegraphics[scale=0.3]{../FiguresFeatures/Frequency_Center_of_Mass}
+\includegraphics[scale=0.3]{../FiguresFeatures/FCM}
 \end{center}
@@
 	\item Concatenate the remaining subsets into training data set
-	\item $X_{train} \leftarrow X^{(i \neq j)}$
-	\item $Y_{train} \leftarrow Y^{(i \neq j)}$
+	\item $X_{train} \leftarrow X^{(i \neq k)}$
+	\item $Y_{train} \leftarrow Y^{(i \neq k)}$
 	\item Train the model, $F^*$ with the $X_{train}$ and $Y_{train}$ subset.
@@
 Thus, indexes where $i = j$ represents a correct prediction, and $i \neq k$ indicates an incorrect prediction.
-A confusion matrix with relatively large values in main diagonal indicates a model that consistently predicts correct labels \cite{Geron}.
-Below we present some "dummy" confusion matrices as numerical arrays, and a corresponding heat-map equivalent.
+A confusion matrix with relatively large values in main diagonal indicates a model that predicts correct labels \cite{Geron}.
+Below we present some synthetic confusion matrices, which combine the counts in each index and a corresponding color map.
 
@@
 
-	\begin{subfigure}[h]{\textwidth , 0.8\textheight}
-	\begin{center}
-	\textcolor{red}{Images of Confusion Matrices Go Here!} 
-	\end{center}
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresMetrics/StdConfA}
+	\caption{Diagonal dominance indicates a stronger classifier}
 	\end{subfigure}
-	\begin{subfigure}[h]{\textwidth , 0.8\textheight}
-	\begin{center}
-	\textcolor{red}{Images of Confusion Matrices Go Here!} 
-	\end{center}
+	\hfill	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresMetrics/StdConfB}
+	\caption{No diagonal dominance indicates a weaker classifier}
 	\end{subfigure}
 
-\caption{Example Confusion Matrices for $k$-classes tasks}
+\caption{Example Confusion Matrices for $4$-categories classifier}
 \label{fig-DummyConfMat}
@@
 
+\paragraph*{}However, it is more useful to weight the confusion matrix according to class occurrence.
+For example, if we had a $2 \times 2$ matrix with entries $100$ and $20$ in the main diagonal, it seems that class $A$ has a much higher prediction success than class $B$.
+However, if there are $200$ elements in class $A$, and only $21$ in class $B$, then we see that class $A$ has a $50\%$ classification rate, while class $B$ has a $95\%$ classification rate, To Combat this, we typically normalize each confusion matrix by the number of samples in each "actual" class.
+Put simply, we all elements in a given row by the sum of that row.
+
 \paragraph*{}The confusion matrix can be a cumbersome, so often it is useful to express the performance in terms of more concise quantities.
-For this we use \textit{accuracy score}, \textit{precision score}, and \textit{recall score}.
+For this we use \textit{accuracy score}, \textit{precision score}, \textit{F1-score}, and \textit{recall score}.
+These metrics are standard in the field of machine-learning classification and are often useful for identifying different strengths and weaknesses in each model \cite{Geron,James}.
 
@@
 \end{equation}
-For multi-class problems, we report the precision score as averaged over all $k$ classes.
-
-\paragraph*{}The quantity $TP + FP$ is a measurement of the total number chosen items in that class.
-Thus, the quantity precision gives the ratio of correct selections to all selections that were made.
-More intuitively, we can describe precision as the fraction of selected items that are relevant to the problem at hand \cite{Geron}.
+In the case of a multi-class classifier, the precision score represents an\textit{one-vs-all} measurement.
+This means that for any class $j$, the sample belongs to class $j$ or it does not.
+All other classes, $i \neq j$ are temporarily considered to be a single aggregated class.
+The quantity $TP + FP$, or the sum over the confusion matrix row is a measurement of the total number of items that are predicted to be in the given class.
+Therefore the precision metric answers the question: \textit{"How many selected items are relevant to the problem?"} \cite{Geron,James}.
 
@@
 \end{equation}
-For multi-class problems, we report the precision score as averaged over all $k$ classes.
-
-\paragraph*{}The quantity $TP + FN$ is a measurement of the total number items in that class, independent of selection.
-Thus, the quantity recall gives the ratio of correct selections to all selections that were made.
-More intuitively, we can describe recall as the fraction of relevant items that were selected \cite{Geron}.
-
-% ================================
-
-\subsubsection{Accuracy Score}
+In the case of a multi-class classifier, the recall score also represents an\textit{one-vs-all} measurement.
+This means that for any class $j$, the sample belongs to class $j$ or it does not.
+All other classes, $i \neq j$ are again temporarily considered to be a single aggregated class.
+The quantity $TP + FN$, or the sum over the confusion matrix coumn is a measurement of the total number of items that are actually in the given class.
+Therefore the recall metric answers the question: \textit{"How many relevant items to the problem are selected?"} \cite{Geron,James}.
+
+% ================================================================
+
+\subsection{Micro F1-Score}
+
+% ================================
+
+\subsubsection{Accuracy Score \&}
 
@@
 It is the ratio of correct predictions of he total number of predictions.
-While immediately useful for equally sampled binary classification problems, it looses meaning as the number of classes increases, and epecially if the number of samples per class is not consistent \cite{Geron,James}.
+While immediately useful for equally sampled binary classification problems, it looses meaning as the number of classes increases, and epecially if the number of samples per class is not consistent \cite{Geron}.
 
@@
 
-\paragraph*{}Despite this we can still sue accuracy score to provide a rough approximation for how the model is performing. \textcolor{red}{finish this!}
+\paragraph*{}Accuracy score of model is defined:
+\begin{equation}
+\label{eqn-BinaryAccuracy}
+\text{Accuracy} = \frac{TP + FN}{TP + FP + FN + FP}
+\end{equation}
+
+\paragraph*{}For a multi-class problem, we present accuracy over \textit{all} classes simultaneously. It is the ratio of the sum of the main diagonal to the sum or all entries in the matrix:
+\begin{equation}
+\label{eqn-AvgAccuracy}
+\text{Accuracy} = \frac{\sum_{i}C_{i,i}}{\sum_{i}\sum_{j}C_{i,j}}
+\end{equation}
+Where all sum indexes goes from $0$ to $k-1$.
 
@@
 
-\paragraph*{}
+\paragraph*{}To formally produce classification predictions on the chaotic synthesizer wave forms, we must use all of the principles outlined in the previous sections.
+Using the described features in sec.
+(\ref{sec-Features}) and appropriate architecture sec.
+(\ref{subsec-Architecture}), We run a
+
+we produce a neural network \textit{ChaoticSynthClassifier} and train it on the roughly $18,000$ audio files that serve as the training set.
 

### 2020-11-25 SignalClassifier-Postprocessing/ClassifierFeatures/FeatureUtilities.py

@@ -112,7 +112,6 @@ class TimeSeriesFeatures (BaseFeatures):
         """ Initialize Class Object Instance """
         super().__init__(waveform=waveform,rate=rate,npts=npts,overlap=overlap,
                          n_frames=n_frames,presetFrames=presetFrames)
-        self.frames = None          # no analysis frames? (temp???)
 
     def __Call__(self):
         """
@@ -129,25 +128,31 @@ class TimeSeriesFeatures (BaseFeatures):
         featureVector = np.append(featureVector,self.ZeroCrossingRate())
         featureVector = np.append(featureVector,self.CenterOfMass())       
         featureVector = np.append(featureVector,self.AutoCorrelationCoefficients())
+
         # Crop Waveform if previously Shorter
         if self.oldSamples < self.n_samples:
             self.signal = self.signal[:self.oldSamples]
-
         return featureVector
     
-    def TimeDomainEnvelope(self,attrb='signal'):
+    def TimeDomainEnvelope(self,nSplits=5):
         """ 
         Compute Time-Envelope by waveform or by frame (Virtanen) 
         --------------------------------
-        attrb (str) : Attribute to operate with. Must be in ['signal','frames']
+        nSplits (int) : Number of sections to split waveform into.
         --------------------------------
         Return Time-Domain-Envelope of waveform or frames
         """
-        assert attrb in ['signal','frames']
-        X = self.__getattribute__(attrb)    # isolate signal or frames
-        TDE = np.sum(X*X,axis=-1)/self.n_samples
-        TDE = np.sqrt(TDE)
-        return TDE
+        # Change this in main classifier!
+        X = self.signal
+        TDEs = np.zeros(shape=nSplits)
+        samplesPerSplit = int(self.n_samples/nSplits)
+        for i in range(0,nSplits):
+            startIdx = i*samplesPerSplit            # where frame starts
+            frame = X[startIdx:startIdx+samplesPerSplit]   # make temporary frame
+            RMS = np.sqrt(np.sum(frame**2)/samplesPerSplit)  
+            TDEs[i] = RMS                           # set to frame        
+        del(X)
+        return TDEs
 
     def ZeroCrossingRate (self,attrb='signal'):
         """ 

### 2020-11-25 SignalClassifier-Postprocessing/ClassifierFeatures/FeaturesMAIN.py

@@ -23,10 +23,10 @@ if __name__ == '__main__':
     # Initialize Directories
     dataPath = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\SignalClassifier\\Target-Data"
     exptPath = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\Thesis\\FiguresFeatures"
-    mtrxPath = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\FeatureData\\Matrix1.csv"
+    mtrxPath = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\FeatureData\\Matrix2.csv"
 
     # Preprocessing
-    n_features = 20
+    n_features = 24
     ProgramSetup = sys_utils.ProgramInitializer([dataPath,exptPath])
     ProgramSetup.InitOutputMatrix(mtrxPath,n_features)
     groupedFiles = ProgramSetup.__Call__()

### 2020-11-25 SignalClassifier-Postprocessing/FeatureProperties/FeaturePropertiesMain.py

@@ -19,7 +19,7 @@ if __name__ == '__main__':
 
     # Initialize Directories
     parentPath = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis"
-    mtrxPath = os.path.join(parentPath,"FeatureData\\Matrix1.csv")
+    mtrxPath = os.path.join(parentPath,"FeatureData\\Matrix2.csv")
     exptPath = os.path.join(parentPath,"Thesis\\FiguresFeatures")
     encdPath = os.path.join(parentPath,"SignalClassifier-CrossValidation\\XValGammaCLF-Output-Data")
 
@@ -29,7 +29,7 @@ if __name__ == '__main__':
     y = inputFrame[1:,1].astype(np.int16)
 
     # Organize Data
-    n_classes,n_features = 37,20
+    n_classes,n_features = 37,24
     Processor = utils.FeatureProcessor(X,y,n_classes,n_features)
     Processor.CreateDictionary(encdPath)
     Processor.__Call__(exptPath)

### 2020-11-25 SignalClassifier-Postprocessing/FeatureProperties/PropertyUtilities.py

@@ -31,7 +31,8 @@ class FeatureProcessor:
     @property
     def GetFeatureNames(self):
         """ Get Names of all features as list of strs """
-        names = ["TDE","ZXR","TCM"]                         
+        names = ["TDE "+str(i+1) for i in range(5)]
+        names += ["ZXR","TCM"]                         
         names += ["ACC "+str(i+1) for i in range(4)]        
         names += ["MFCC "+str(i+1) for i in range (12)]      
         names += ["FCM"]                                    

### 2020-11-25 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis Draft

@@
 
-\paragraph*{}From time space, we use the following $7$ features:
+\paragraph*{}From time space, we use the following $11$ features:
 \begin{itemize}
-\item[•] Time Domain Envelope
+\item[•] Time Domain Envelope ($\times 5$)
 \item[•] Zero Crossing Rate
@@
 \end{equation}
-For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large TDE value.
-For instruments with short sustain times, such as plucked stings or dampened percussion we expect a comparably small TDE value \cite{Olson,White}.
-The difference allows for considerable separation between many percussion and woodwind classes.
+Where $Q$ gives the number of sample sin each analysis frame (number of sample sin waveform divided by number of frames), and $n$ gives the index where the $j$-th frame begins.
+
+\paragraph*{}These uniformly size analysis frames let us create an naive envelope of the waveform, but will allow it to generalize between classes.
+For example, this allows for a crude approximation of the energy in the attack, decay, sustain, and release energies in a waveform \cite{Virtanen,Olson}.
+For instruments with heavier attacks, we expect the TDE in the $1$-st frame to be comparably large, see Fig.
+(\ref{fig-FeatureTDE}a).
+Instruments with a heavy decay will likely have little energy in the $2$-nd or higher frames, indicating that the amplitude has substantially died off as in Fig.
+(\ref{fig-FeatureTDE}b).
+Conversely, instruments with longer sustain such as upper woodwinds, vibraphones or strings will container relatively higher TDE values for the later analysis frames as seen in Fig.
+(\ref{fig-FeatureTDE}c).
+Instruments with little or no waveform envelope, such as the synthesized waveforms and the whitenoise show constant TDE values across each frame as expected.
 
 \begin{figure}[H]
-\begin{center}
-%textcolor{red}{Plot of TDE Feature Here}
-\includegraphics[scale=0.3]{../FiguresFeatures/TDE}
-\end{center}
-\caption{A comparison of the Time Domain Envelope across each class using a box-and-whisker plot}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/TDE_1}
+	\caption{TDE $1$}
+	\end{subfigure}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/TDE_2}
+	\caption{TDE $2$}
+	\end{subfigure}
+
+	\begin{subfigure}{1.0\textwidth}
+	\centering
+	\includegraphics[width=\textwidth , height=0.2\textheight]
+		{../FiguresFeatures/TDE_3}
+	\caption{TDE $3$}
+	\end{subfigure}
+
+\caption{A comparison of the first $3$ of $5$ Time Domain Envelope across each class using a box-and-whisker plot}
 \label{fig-FeatureTDE}
@@
 This can be computed per total sound wave, per analysis-frame, or per unit time.
-This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform \cite{Kahn,Liu,Zhang}.
+This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform \cite{Kahn,Liu,Zhang} that musical instruments do.
 
@@
 ZXR also provides a very rough estimate for the average frequency of the waveform.
-This allows it to alos be useful in discerning classes with generllay hgher frequencies, such as upper woodwinds, against classes with generaly lower frequencies, such as low brass \cite{White}.
+This allows it to allows be useful in discerning classes with generally higher fundamental frequencies, such as upper woodwinds, against classes with generally lower frequencies, such as low brass \cite{Liu,White}.
+
+\paragraph*{}This behavior becomes apparent when comparing sets of classes in Fig.
+(\ref{fig-FeatureZXR}).
+For example, consider the ZXR value of a a bass and cellos against that of bells or a soprano saxophone.
+The bass and cellos have on average much lower fundamental frequencies than that of bellos of soprano saxophones.
+In the case of this data set, the ZXR provides a predictor which contains clear separations between classes such as crotales and $E\flat$ clarinets.
+The large separation gives rise to a distinction decision boundary which means that this classes are not likely to be mistake when predictions are run \cite{Loy,James}.
 
@@
 
-\subsection{Micro F1-Score}
+\subsubsection{Micro F1-Score}
 

### 2020-11-25 SignalClassifier/ClassifierHybrid/FeatureUtilities.py
Preparing Repo for Cross-Validation

@@ -135,19 +135,25 @@ class TimeSeriesFeatures (BaseFeatures):
 
         return featureVector
     
-    def TimeDomainEnvelope(self,attrb='signal'):
+    def TimeDomainEnvelope(self,nSplits=5):
         """ 
         Compute Time-Envelope by waveform or by frame (Virtanen) 
         --------------------------------
-        attrb (str) : Attribute to operate with. Must be in ['signal','frames']
+        nSplits (int) : Number of sections to split waveform into.
         --------------------------------
         Return Time-Domain-Envelope of waveform or frames
         """
-        assert attrb in ['signal','frames']
-        X = self.__getattribute__(attrb)    # isolate signal or frames
-        TDE = np.sum(X*X,axis=-1)/self.n_samples
-        TDE = np.sqrt(TDE)
-        return TDE
+        # Change this in main classifier!
+        X = self.signal
+        TDEs = np.zeros(shape=nSplits)
+        samplesPerSplit = int(self.n_samples/nSplits)
+        for i in range(0,nSplits):
+            startIdx = i*samplesPerSplit            # where frame starts
+            frame = X[startIdx:startIdx+samplesPerSplit]   # make temporary frame
+            RMS = np.sqrt(np.sum(frame**2)/samplesPerSplit)  
+            TDEs[i] = RMS                           # set to frame        
+        del(X)
+        return TDEs
 
     def ZeroCrossingRate (self,attrb='signal'):
         """ 

### 2020-11-25 SignalClassifier/ClassifierHybrid/NeuralNetworkUtilities.py

@@ -24,7 +24,7 @@ NeuralNetworkModels.py - "Neural Network Models"
 #inputShapeMLP = (24,)
 #inputShapeCNN = (1115,128,1)
 
-inputShapeMLP = (20,)
+inputShapeMLP = (24,)
 inputShapeCNN = (558,256,1)
 
             #### NEURAL NETWORK OBJECTS ####

### 2020-11-25 SignalClassifier-CrossValidation/KFoldsCrossValidation/CrossValidationMain.py
Organizing Repo, Removing Redundant Files

@@ -21,12 +21,11 @@ if __name__ == "__main__":
     # HARD-CODE VARIABLES FOR DEVELOPMENT
     parent = 'C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis'
     read = os.path.join(parent,'SignalClassifier','Target-Data')   
-    modelName = "XValGammaCLF"
+    modelName = "XValAlphaCLF"
     nSplits = 10
     export = os.path.join(parent,'SignalClassifier-CrossValidation',modelName+'-Output-Data')
     model = os.path.join(parent,'SignalClassifier-CrossValidation',modelName+'-Model-Data')
-    
-
+   
     scriptPath = os.path.join(parent,'SignalClassifier','ClassifierMain')
     scriptName = "ClassifierMAIN.py"
 

### 2020-11-25 SignalClassifier/ClassifierHybrid/ModeUtilities.py
Prepared Repo for X-Validation

@@ -9,6 +9,8 @@ Instrument Classifier v0
 
 import numpy as np
 import os
+
+from sklearn.model_selection import train_test_split
 from sklearn.preprocessing import StandardScaler
 
 import SystemUtilities as sys_utils

### 2020-11-25 SignalClassifier/ClassifierHybrid/SystemUtilities.py

@@ -55,7 +55,14 @@ class FileObject:
             self.targetStr = str(datarow[2])    # target as str
         except:
             self.targetStr = None    # unknown str
-        
+
+    def __repr__(self):
+        """ Return Low-Level String description of Instance """
+        try:
+            return self.filename + " , " + str(self.targetInt) + " , " + str(self.targetStr)
+        except:
+            return self.filename + " , None , None"
+
     def ReadFileWAV (self):
         """ Read raw .wav file data from local path """
         rate,data = sciowav.read(self.fullpath)    
@@ -94,6 +101,7 @@ class OutputStructure :
             print("\n\tERROR! - File mode not recognized!")
             self.cols = []
             raise BaseException()
+        self.mode = programMode
         self.exportPath = exportPath
         self.InitData()
     
@@ -205,7 +213,7 @@ class ArgumentValidator :
             self.HardCodedVars()
 
         # make Sure Args are in acceptable values
-        assert self.modelName not in [None," "]
+        assert self.modelName not in [None,""," "]
         assert self.programMode in ['train','train-predict','predict']
         assert self.newModel in [True,False]
 

### 2020-11-25 SignalClassifier-CrossValidation/KFoldsCrossValidation/CrossValidationMain.py
Ran Cross Validation!

@@ -26,8 +26,8 @@ if __name__ == "__main__":
     export = os.path.join(parent,'SignalClassifier-CrossValidation',modelName+'-Output-Data')
     model = os.path.join(parent,'SignalClassifier-CrossValidation',modelName+'-Model-Data')
    
-    scriptPath = os.path.join(parent,'SignalClassifier','ClassifierMain')
-    scriptName = "ClassifierMAIN.py"
+    scriptPath = os.path.join(parent,'SignalClassifier','ClassifierHybrid')
+    scriptName = "ClassifierHybridMain.py"
 
     # HANDLE LOCAL DIRECTORIES
     homePath = os.getcwd()

### 2020-11-25 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis Paper

@@
 % ================================================================
+
+\begin{abstract}
+
+\end{abstract}
+
+% ================================================================
+% ================================================================
 \newpage
@@
 
-\paragraph*{}\textcolor{red}{How do I write an introduction???}
+\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}.
+These signals can take the form of day-to-day topics such as weather measurements, financial reports, or audio-visual media, and extend into disciplines of medicine, physics, and digital signal processing.
+In all cases, we explore a problem where the task to categorize the sample, or subset of the sample into one of $k$ \textit{bins} called classes \cite{Mierswa,Virtanen,Geron}.
+
+\paragraph*{}For this classification task, we have developed an automated model (called a \textit{classifier}) which can process information from a time-series audio file, and group the file based on it's prediction of what produced the sound in that file.
+For example, classifying an audio file which contains the waveform of a clarinet sustaining a single note should return the classification prediction of "clarinet" and so forth.
+This non-trivial task requires developing a model
+
+ Developments in computational efficiency and the age of \textit{Big Data} has lead to a staggering increase in the utilization
 
@@
 
-% ================================
+% ================================================================
+
+\subsection{Feature Space}
+
+\paragraph*{}From each audio file sample, we derive an identical set of $p$ predictors that will be
 
@@
 
-\paragraph*{}This concept stems from the idea that a trained neural network classifier is basing its predictions by generating \textit{decision boundaries} in feature space \cite{Loy,James,Serizel}.
+\paragraph*{}This concept stems from the idea that when a trained neural network classifier makes a prediction, it is doing so based on a set of generated \textit{decision boundaries} \cite{Geron,James}.
 
@@
 
-\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}.
+\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James,Serizel}.
 In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following steps and requirements:

### 2020-11-25 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisMAIN.py

@@ -21,10 +21,10 @@ if __name__ == '__main__':
 
     # Establish local Directory Paths
     parent = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\SignalClassifier-CrossValidation"
-    modelName = "XValGammaCLF"
+    modelName = "XValAlphaCLF"
     dataPath = os.path.join(parent,modelName+"-Output-Data")
     exptPath = os.path.join(parent,modelName+"-Analysis")    
-    n_classes = 38
+    n_classes = 37
 
     # Run Main program
     Program = utils.AnalyzeModels(modelName,dataPath,n_classes)

### 2020-11-25 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisUtilities.py

@@ -135,7 +135,7 @@ class AnalyzeModels:
         avgHitMatName =  self.modelName + " Avg Hits Weighted Confusion"
         avgScrMatName =  self.modelName + " Avg Score Weighted Confusion"
         
-        """
+        
         ClassifierMetrics.ExportConfusion(avgStandardConfMat,avgStdMatName,exptPath)
         ClassifierMetrics.ExportConfusion(avgHitsWeightedConfMat,avgHitMatName,exptPath)
         ClassifierMetrics.ExportConfusion(avgScrsWeightedConfMat,avgScrMatName,exptPath)
@@ -145,7 +145,7 @@ class AnalyzeModels:
         ClassifierMetrics.PlotConfusion(avgHitsWeightedConfMat,self.n_classes,avgHitMatName)
         ClassifierMetrics.PlotConfusion(avgScrsWeightedConfMat,self.n_classes,avgScrMatName)
         os.chdir(homePath)
-        """
+        
 
         # Compute metrics avg. across all classes
         self.ConfusionMatrix = avgStandardConfMat

### 2020-11-26 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesise, added new paper

@@
 
-\subsection{Layers Used in this Classification Neural Network}
+\subsection{Layers Used in this Classification Model}
 \label{subsec-Layers}
@@
 
-\subsection{Training a Neural Network}
+\subsection{Training The Model}
 \label{subsec-Training}
@@
 	\item Compute first bias moment: $s \leftarrow \rho_1 s + (1 - \rho_1) \nabla \bar{J}$
-	\item Compute second bias moment: $r \leftarrow \rho_2 s + (1 - \rho_2) \nabla \bar{J} \odot \nabla \bar{J}$
+	\item Compute second bias moment: $r \leftarrow \rho_2 r + (1 - \rho_2) \big( \nabla \bar{J} \odot \nabla \bar{J} \big)$
 	\item First bias correction: $s' \leftarrow \frac{s}{1 - \rho_1^i}$
@@
 
-\subsection{Chosen Model Architecture}
+\subsection{Multimodal Architecture}
 \label{subsec-Architecture}
@@
 The structure of the network defines the composition of it's function, $F^*$ as in Eq.(\ref{eqn-FunctionGraph}), and thus it's performance in completing any given task \cite{Geron}.
-The layer structure of the neural network it's \textit{architecture} \ref{Goodfellow}.
-Most standard implementations of networks utilize a \textit{unimodal architecture} where the model is created with a single input layer .
+The layer structure of the neural network is referred to as it's \textit{architecture} \cite{Goodfellow}.
+
+\paragraph*{}For this project, we have derived features that describe that audio file using two different \textit{modalities}.
+A modality is a method of describing and interpreting a sample of data \cite{Ngiam}.
+For example.
+Humans can be said to experience the world through five modalities - those being our cardinal senses of sight, hearing, taste, smell and touch.
+The sight and sound of a guitar are two very different ways of experiencing the same thing.
+One or the other is often enough to identify the guitar - but both together yield an ever higher predictive confidence.
 
@@
 
+\paragraph*{}We can carry this idea over by producing a \textit{multimodal} neural network that accepts two different forms of input for each sample.
+One input is an $N \times k$ spectrogram matrix, explored in sec.
+(\ref{subsec-Spectrogram}) and the other input is a $1 \times p$ feature vector explored in sec.
+(\ref{subsec-TimeFeatures}) and sec.
+(\ref{subsec-FreqFeatures}).
+The spectrogram acts to provide an energy distribution of a signal as a function of frequency and time, while the feature vector provides qualities in a more list-like fashion.
+This type of supervised learning is referred to as \textit{multi-view} learning, and we detail a conceptual diagram of the architecture in Fig.
+(\ref{fig-NetworkArchitecture}) \cite{Li,Ngiam}.
+
 % ================================
@@
 (\ref{fig-NetworkArchitecture}).
-A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olson,Kahn}.
-\textcolor{blue}{Details on the creating of the spectrogram can be found in the \textit{features} section of this document.}
+A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olson,Khan}
 
 \paragraph*{}The input layer of the spectrogram accepts a 4-Dimensional array.
-The axes, in order of indexing, represents (i) the size of the \textit{mini-batch} of samples, (ii) the pixel width of each sample, (iii) the pixel height of each sample, and (iv) the number of channels in each sample.
-As a model hyper-parameter, we have chosen each batch to contain $64$ samples.
-We have also chosen to truncate time and frequency axes (ii \& iii) to contain $560$ frequency bins, and $256$ time-frames.
-Each image also contains a single channel, which make it gray-scale when visualized.
-We can denote the 4D shape of the input object into this branch as:
+The axes, in order of indexing, represents (i) the size of the \textit{mini-batch} of samples, (ii) the pixel width of each sample, (iii) the pixel height of each sample, and (iv) the number of channels in the image.
+For this model, we have selected to use $64$ samples per batch, $558$ pixels in width, $256$ pixels in length, and $1$ gray-scale channel.
+We denote the 4D shape of the design matrix for this branch as:
 \begin{equation}
 \label{eqn-shapeX1}
-X_1 \in \mathbb{R}^{(64 \times 560 \times 256 \times 1)}
-\end{equation}
-Any other shape will be rejected by the model, and an error is raised.
-
-\paragraph*{}After the input layer assert the appropriate shape, the array $X_1$, which is a collection of $64$ spectrograms, is passed into the first of three \textit{Convolution Layer Groups}.
+X_1 \in \mathbb{R}^{(64 \times 558 \times 256 \times 1)}
+\end{equation}
+Any other shape will be rejected, and an error is raised.
+
+\paragraph*{}After the input layer holds store the input activations, $X_1$ and tests for the appropriate shape, the array which is a collection of $64$ spectrograms, is passed into the first of three \textit{Convolution Layer Groups}.
 These layer groups are inspired from the \textit{VGG-16 Neural Network} architecture \textcolor{red}{[citation needed]}.
@@
 
-\paragraph*{}Classification tasks require a set of inputs  .
-These inputs are called \textit{predictors} or \textit{features} \cite{James,Loy,Serizel}.
-Features are quantitative, low-dimensional representations of each sample that convey key characteristics of the sample.
+\paragraph*{}Classification tasks require a set of inputs called \textit{predictors} or \textit{features} \cite{James,Loy,Serizel}.
+A features is a quantitative, low-dimensional representation of a sample that conveys key characteristics of it.
+For example, in classifying types of animals, a feature could be the mass, mass volume or number of teeth on the animal.
+Typically, we produce a set of features $p$ for each sample and assemble them into a $1 \times p$ vector called a \textit{feature vector} which acts as a list of descriptive qualities of the sample \cite{Geron,James}.
 Audio machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib discusses the vitality of feature selection \cite{Khan}:
@@
 \end{quote}
-In the biological process of categorizing sound sources, the time-domain waveform is usually enough to match the sound to a source \cite{Olson}.
+An adequate selection features is vital to the process of training and evaluation of the classifier model \cite{Mierswa,Serizel,Liu}.
+Consider the task of identifying cats and dogs from images, given only the top-most row of pixels or the number of eyes.
+While the data represents \textit{correct} properties, it is not enough information to distinguish the two categories.
+
+\paragraph*{}In the biological process of categorizing sound sources, the time-domain waveform is usually enough to match the sound to a source \cite{Olson}.
 However, a computer representation of a waveform is an array-like structure of values sampled discretely in time and volume \cite{Virtanen,Liu}.
-Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks so we must develop a set of features or predictors that can describe important properties of the waveform in an efficient manner \cite{Goodfellow,James,Serizel}.
-
-\paragraph*{}It becomes quickly apparent that the choice of features is extraordinarily important to the process of training and evaluation of the classifier model \cite{Mierswa}.
-Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels.
-The inappropriate choice features does not reflect the significant characteristics of the data.
+Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks so we must develop a set of features or predictors that can describe important properties of the waveform in a far more efficient manner \cite{Goodfellow,James,Serizel}.
+
+\paragraph*{}To ensure the construction of a suitable model, we derive features based from three representations of the audio file: (i) a spectrogram matrix representation, (ii) the time-space representation, and (iii) the frequency-space representation.
+It is important to note that although this algorithm will map audio files to source instruments, the model will never actually be presented with a waveform directly, instead it will rely solely on the features to make predictions.
+
+% ================================================================
+
+\subsection{Feature Space}
+
+\paragraph*{}From each audio file sample, we derive an identical set of $p$ predictors that will be use for classification.
+For this multi-modal neural network, the $p$ predictors are arranged into two separated structures, each called a \textit{design matrix}, described in sec.
+(\ref{subsubsec-DesignMatrix}) \cite{Goodfellow,Geron}.
 
@@
 \end{quote}
-To ensure the construction of a suitable model, we derive features based from three representations of the audio file: (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency-space representation of the waveform.
-It is important to note that although this algorithm will classify sound data to instruments, the model will never actually be presented with a waveform directly, instead it will rely solely on the features.
-
-\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector.
-We have developed a set of predictors that describe each sample in a compact manner, with reasonable separation boundaries between samples from different classes.
-These features are derived are principles of music, digital signal processing, previous work, and underlying physics that governs the behavior of instruments.
-In the following sections, we outline the set of $21$ features used in the classification process.
-For each feature, we visualize the distribution in across each class in the form as box-plots.
-Each feature has been normalized to have a zero mean, and unit-variance across all classes.
-
-% ================================================================
-
-\subsection{Feature Space}
-
-\paragraph*{}From each audio file sample, we derive an identical set of $p$ predictors that will be
 
@@
 \subsubsection{The Design Matrix}
-
-\paragraph*{}From each audio file, we produce a spectrogram matrix and a feature vector, as well as a target label for training purpose.
+\label{subsubsec-DesignMatrix}
+
+\paragraph*{}From each training audio file, we produce a spectrogram matrix explored in sec.
+(\ref{subsec-Spectrogram}) and a feature vector, as well as a target label for training purpose.
 From a collection of multiple samples, the spectrograms are concatenated into a single object $X_1$, and the feature vectors are concatenated into an object, $X_2$.
@@
 \subsection{Spectrogram Features}
-\label{subsec-spectrogram}
+\label{subsec-Spectrogram}
 
@@
 \subsection{Time-Space Features}
-\label{subsec-time}
+\label{subsec-TimeFeatures}
 
@@
 \subsection{Frequency-Space Features}
-\label{subsec-frequency}
+\label{subsec-FreqFeatures}
 
@@
 
-\bibitem{Kahn}
+\bibitem{Khan}
 Khan, M. Kashif Saeed, and Wasfi G. Al-Khatib. “Machine-Learning Based Classification of Speech and Music.” Multimedia Systems, vol. 12, no. 1, 2006, pp. 55–67., doi:10.1007/s00530-006-0034-0.

### 2020-11-27 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Major revisions

@@
 \end{equation}
-The concatenation layer is used to combine activation non-adjacent, or non-related layers into a single new layer.
-In this case of the model used in the project, we use it to combine the activations that result from two distinct models into a single layer that is then transformed into a final output.
+The concatenation layer is used to combine activations from two different layers into a single new layer.
+In this case of the model used in the project, we use it to combine the outputs that result from the convolution branch and the perceptron branch tp produce an single aggregated output.
 This process is detailed further in sec.
@@
 It is this second step that allows for neural networks to model the incredibly complex decision boundaries that are found in real-world problems \cite{Geron,Loy}.
-In this section, we detail the activation functions used in out classification neural network.
+In this section, we detail the activation functions used in this classification neural network.
 
@@
 \paragraph*{}The Rectified Linear Unit (ReLU) activation function acts element-wise on the activations in a given layer.
-If the activation of a neurons is non-zero or non-negative, the value is untouched, otherwise a $0$ is returned.
-For an input activation $x$, ReLU is defined by:
+If the activation of a neurons is non-negative, the value is untouched, otherwise a $0$ is returned.
+For an input activation array $x$, ReLU is defined by:
 \begin{equation}
@@
 \Theta = \big\{
-W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)}, W^{(L)}, b^{(L-1)}
+W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)}, W^{(L-1)}, b^{(L-1)}
 \big\}
 \end{equation}
-The arrays $W^{(l)}$and bias vectors $b^{(l)}$ are not trainable parameters, themselves.
-Instead, the floating-point entries within these arrays are the values that can be adjusted.
-Each element in this set may contain hundreds or thousands of parameters, so we represent these indirectly as elements of their respective matricies or vectors.
+The arrays $W^{(l)}$and bias vectors $b^{(l)}$ are not trainable parameters themselves, but the the floating-point entries within them are the values that can be adjusted.
+Each element in this set may contain hundreds or thousands of parameters, so we represent these indirectly as parameters within their respective layers.
 We choose this notation for $\Theta$ for notation simplicity.
 Note that not all layers have trainable parameters, and activations functions themselves are not trainable, but fixed functions.
-
-\paragraph*{}Modern neural networks can contain upwards of hundreds of thousands,or even millions of elements in $\Theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow,Levine}.
+Modern neural networks can contain upwards of hundreds of thousands,or even millions of elements in $\Theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow,Levine}.
 For the network that we have designed in this project, there are roughly $33,000$ parameters across $20$ layers.
@@
 
-\paragraph*{}Suppose we pass a training sample, given by the feature-vector $x^{(0)}$, with an expected outcome given by the one-hot-encoded vector $y$, into the neural network.
-After the network finishes processing, it's output activations are given by the vector $x^{(L-1)}$, also noted as $y^*$.
-For a reasonably trained model, we expect the vector $y^*$ to be "similar" to $y$, indicating that with the provided data, the network has made a valid prediction.
+\paragraph*{}Suppose we pass a training sample into the neural network.
+This sample is represented by the feature-vector $x^{(0)}$, with an expected outcome given by the one-hot-encoded vector $y$.
+After the network finishes processing, it's output activations, given by the vector $x^{(L-1)}$, also noted as $y^*$ represents the prediction for the class label.
+For a reasonably trained model, we expect the vector $y^*$ to be "similar" to $y$, indicating that with the provided data, the network has made a reasonably valid prediction.
 Conversely, for an untrained network, $y^*$ is not likely to be "similar" to $y$ at all, indicating that the network has made a poor prediction.
@@
 (\ref{fig-ComputationalGraph})
+
+\paragraph*{}Note that we indicate the cost as $J(\Theta)$.
+This is an allusion to the fact that $J$ depends of both the labels $y$, and the predictions $y^*$.
+Where $y^*$ is a function of all of the previous layer activation, which are in turn functions of each weight bias element, i.e.
+the contents of the $\Theta$ object, in Eq.
+(\ref{eqn-Theta}).
+This is why we are able to compute the gradient with respect to $\Theta$ as in Eq.
+(\ref{eqn-CostGradient}).
+
+\paragraph*{}Raw information is presented as $x^{(0)}$ at the top of the figure, and and output is returned as $x^{(L-1)}$ at the bottom.
+Arrows represent the flow of information.
+As expressed in Eq.
+(\ref{eqn-CXELoss}), we compute the cost of a sample, or batch of samples by comparing the difference between $y^*$ (which is $x^{(L-1)}$) and $y$.
+Given this graph chain and it's numerical nature, we cannot compute each element in the gradient vector through conventional symbolic calculus \cite{Loy}.
+We must instead use the chain rule for partial derivatives to begin at the final output of the network and successively work our way forward to the entry layer to compute the numerical derivative with respect to each parameter.
+This process is called \textit{back-propagation} \cite{Geron,Goodfellow}.
+
 \begin{figure}[H]
@@
 \end{figure}
-Note that we indicate the cost as $J(\Theta)$.
-This is an allusion to the fact that $J$ depends of both the labels $y$, and the predictions $y^*$.
-Where $y^*$ is a function of all of the previous layer activation, which are in turn functions of each weight bias element, i.e.
-the contents of the $\Theta$ object, in Eq.
-(\ref{eqn-Theta}).
-This is why we are able to compute the gradient with respect to $\Theta$ as in Eq.
-(\ref{eqn-CostGradient}).
-
-\paragraph*{}Raw information is presented as $x^{(0)}$ at the top of the figure, and and output is returned as $x^{(L-1)}$ at the bottom.
-Arrows represent the flow of information.
-As expressed in Eq.
-(\ref{eqn-CXELoss}), we compute the cost of a sample, or batch of samples by comparing the difference between $y^*$ (which is $x^{(L-1)}$) and $y$.
-Given this graph chain and it's numerical nature, we cannot compute each element in the gradient vector through conventional symbolic calculus \cite{Loy}.
-We must instead use the chain rule for partial derivatives to begin at the final output of the network and successively work our way forward to the entry layer to compute the numerical derivative with respect to each parameter.
-This process is called \textit{back-propagation} \cite{Geron,Goodfellow}.
 
@@
 \frac{\partial J}{\partial x^{(L-1)}} = \frac{\partial J}{\partial y^*} =
-\frac{\partial}{\partial y^*}\Big[ -y \ln (y^*) \Big] = -\frac{1}{y^*_i + \delta}
+\frac{\partial}{\partial y^*}\Big[ -y \ln (y^*) \Big] = -\frac{y}{y^*_i + \delta} = -\frac{1}{y^*_i + \delta}
 \end{equation}
@@
 Note that each $z^{(l)}$ and $x^{(l)}$ are typically stored in memory during the forward pass in Alg.
-(\ref{algFeedForward}) to prevent the need to recompute them \cite{Geron2,Goodfellow}.
+(\ref{alg-FeedForward}) to prevent the need to recompute them \cite{Geron2,Goodfellow}.
 
@@
 
-Execute forward pass in algorithm (\ref{algFeedForward}) and compute the gradient of the cost with respect to the final layer activations \\
+Execute forward pass in algorithm (\ref{alg-FeedForward}) and compute the gradient of the cost with respect to the final layer activations \\
 $dx \leftarrow \nabla_{(y^*)}J(y,y^*)$ \\
@@
 This is called \textit{gradient descent} and is the basis for many optimization algorithms.
-Let $\bar{J}$ be the avergae cost over a batch of $b$ samples.
+Let $\bar{J}$ be the average cost over a batch of $b$ samples.
 We show the general update rule on iteration $(i)$ for gradient based learning in Eq.
@@
 \end{equation}
-Where $\Theta^{(i)}$ will give the set of new, updated parameters of the network.
+Where $\Theta^{(i)}$ will give the set of new, updated parameters of the network. Note that for Eq. (\ref{eqn-GradientLearning}), all operations are applied element-wise.
 
@@
 It is a powerful optimizer with uses adaptive learning rate and momentum parameter.
-ADAM tracks an exponentially decaying average of past gradients (see $s^{(i})$ in Eq.
-(\ref{eqn-ADAMupdate})), as well as exponentially decaying average of past squared gradients (see $r^{(i})$ in Eq.
+ADAM tracks an exponentially decaying average of past gradients, $s^{(i)}$, and an exponentially decaying average of past squared gradients, $r^{(i)}$ in Eq.
 (\ref{eqn-ADAMupdate}))\cite{Geron}.
-This produces a far more aggressive optimizer at a higher computational cost.
-
-\paragraph*{}This means that as the cost function iterates through each step, the effect will tend to "snowball".
+This produces a far more aggressive optimizer at a higher computational cost than standard gradient descent.
+
+\paragraph*{}As the cost function iterates through each step, the effect will tend to "snowball".
 If the previous step was found to reduce the cost function by a large or small amount, the step size for the previous step will update accordingly.
-Note that a superscript $(i)$ or $(i-1)$ gives an iteration index, while the superscript $i$ means to raise a value to the power of $i$. For a given step $(i)$, The ADAM update is given:
+This enables to ADAm to overcome smaller discontunities that may arise in the solution space \cite{Goodfellow}.
+Note that a superscript $(i)$ or $(i-1)$ gives an iteration index, while the superscript $i$ means to raise a value to the power of $i$.
+For a given step $(i)$, The ADAM update is given:
 \begin{equation}
@@
 A modality is a method of describing and interpreting a sample of data \cite{Ngiam}.
-For example.
-Humans can be said to experience the world through five modalities - those being our cardinal senses of sight, hearing, taste, smell and touch.
+For example humans can be said to experience the world through five modalities - those being our cardinal senses of sight, hearing, taste, smell and touch.
 The sight and sound of a guitar are two very different ways of experiencing the same thing.
-One or the other is often enough to identify the guitar - but both together yield an ever higher predictive confidence.
+One or the other is often enough to identify the guitar - but both together yield an even higher predictive confidence.
+Since modalities are \textit{different} by nature, we cannot simply combine them into a single object and present the neural network with it.
+We must account for the difference by provide two distinct input layers.
+Consider again the act of seeing any hearing a guitar.
+Both modalities are captured by two different senses but ultimately processed by the same brain to produce a single prediction.
+
+\paragraph*{}We can carry this idea over by producing a \textit{multimodal} neural network that accepts two different forms of input for each sample.
+One input is an $N \times k$ spectrogram matrix, explored in sec.
+(\ref{subsec-Spectrogram}) and the other input is a $1 \times p$ feature vector explored in sec.
+(\ref{subsec-TimeFeatures}) and sec.
+(\ref{subsec-FreqFeatures}).
+The spectrogram acts to provide an energy distribution of a signal as a function of frequency and time, while the feature vector provides qualities in a more list-like fashion.
+This type of supervised learning is referred to as \textit{multi-view} learning, and we detail a conceptual diagram of the architecture in Fig.
+(\ref{fig-NetworkArchitecture}) \cite{Li,Ngiam}.
 
@@
 
-\paragraph*{}We can carry this idea over by producing a \textit{multimodal} neural network that accepts two different forms of input for each sample.
-One input is an $N \times k$ spectrogram matrix, explored in sec.
-(\ref{subsec-Spectrogram}) and the other input is a $1 \times p$ feature vector explored in sec.
-(\ref{subsec-TimeFeatures}) and sec.
-(\ref{subsec-FreqFeatures}).
-The spectrogram acts to provide an energy distribution of a signal as a function of frequency and time, while the feature vector provides qualities in a more list-like fashion.
-This type of supervised learning is referred to as \textit{multi-view} learning, and we detail a conceptual diagram of the architecture in Fig.
-(\ref{fig-NetworkArchitecture}) \cite{Li,Ngiam}.
-
 % ================================
@@
 (\ref{fig-NetworkArchitecture}).
-A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olson,Khan}
-
-\paragraph*{}The input layer of the spectrogram accepts a 4-Dimensional array.
+A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olson,Khan}.
+The input layer of the spectrogram accepts a 4-Dimensional array.
 The axes, in order of indexing, represents (i) the size of the \textit{mini-batch} of samples, (ii) the pixel width of each sample, (iii) the pixel height of each sample, and (iv) the number of channels in the image.
@@
 \paragraph*{}After the input layer holds store the input activations, $X_1$ and tests for the appropriate shape, the array which is a collection of $64$ spectrograms, is passed into the first of three \textit{Convolution Layer Groups}.
-These layer groups are inspired from the \textit{VGG-16 Neural Network} architecture \textcolor{red}{[citation needed]}.
-Each convolution layer group in composed of three individual layers:
+These layer groups are inspired from the \textit{Visual Geometry Group-16 Neural Network} architecture \cite{Goodfellow,Loy}.
+Each convolution layer group is composed of three individual layers:
 \begin{enumerate}
@@
 \end{enumerate}  
-The Convolution layers convoluted over the middle two axes of the data (over space and time in the spectrogram).
+The Convolution layers convolve over the middle two axes of the data. This corresponds to convolving as weighting kernel over the time and frequency axes.
 
 \paragraph*{}By grouping layers in this structure, we use convolution to reduce the number of features, and then the pooling layer to extract only the largest activations of the remaining values.
-This ensures that in the full spectrogram image, only the dominant features and feature shapes are preserved and passed into the next layer set for processing.
+This drastically reduces the width of each layer before passing the activations down, and ensures that only the dominant features and characteristic shapes are preserved and passed into the next layer set for processing.
 This also allows for positional invariance in features.
-Regardless of where in space or time a feature is detected, the moving kernel will still allow it to be found \cite{Goodfellow,Loy}.
+Regardless of where in frequency or time a feature is detected, the moving kernel will still allow it to be found \cite{Goodfellow,Loy}.
 
@@
 
-\paragraph*{} The Perceptron branch is picture on the right side of Fig.
-(\ref{fig-NetworkArchitecture}), notice that it is considerably smaller in side and complexity than it's neighbor.
-Rather than accept an image-like input, the perception simply takes a vector-like input of properties that are derived from the audio file.
-We call these properties \textit{features} \cite{Geron,Kahn,Serizel}.
-\textcolor{blue}{Details on the creating of these features can be found in the \textit{features} section of this document.}
+\paragraph*{} The Perceptron branch is pictured on the right side of Fig.
+(\ref{fig-NetworkArchitecture}), notice that it is considerably smaller in depths and complexity than it's neighbor.
+Rather than accept an image-like input, the perception simply takes a $1 \times p$ vector-like input of properties that are derived from the audio file.
+We call these properties \textit{features} \cite{Geron,Khan,Serizel}.
+Details on the natures and selectiosn of these $p$ elements are found in sec.
+(\ref{subsec-TimeFeatures}) and sec.
+(\ref{subsec-FreqFeatures}).
 
@@
 The axes, in order of indexing, represent (i) the size of the \textit{mini-batch} of samples, (ii) the number of features for each sample.
-We use the same model hyper-parameter of $64$ samples per batch, and have developed $20$ unique classification features that have been derived from time-space and frequency-space representations of the audio file data.
+We use the same model hyper-parameter of $b = 64$ samples per batch, and have developed $p = 24$ unique classification features that have been derived from time-space and frequency-space representations of the audio file data.
 We can denote the 2D shape if the input object into this branch as:
@@
 \end{equation}
-This 2D is referred to as a \textit{design matrix} \cite{James,Loy}. Any other shape will be rejected by the model, and an error is raised.
-
-\paragraph*{}In perceptron models, scaling the design matrix appropriately drastically improves the classification performance.
+This 2D array is referred to as a \textit{design matrix} \cite{James,Loy}. Any other shape will be rejected by the model, and an error is raised.
+
+\paragraph*{}In perceptron models, the scaling of the design matrix is vital to classification performance.
 A design matrix is scaled by taking all samples in a column (a particular feature from each class), subtracting the average, and then scaling it such that it has unit variance \cite{Geron,James}.
@@
 
-\paragraph*{}The last layer in each of the two branches is a ReLU-activated Dense layer containing 64 neurons, represented by a $64 \times 1$ column vectors.
-We combine these model layers by using a \textit{concatenation layer} to fuse the two column vectors together, "vertically", such that the result is a $128 \times 1$ column vector.
-This vector is then passed into the final dense layer, which used the softmax activation, and encodes the joint predictions based on both model branches.
+\paragraph*{}The last layer in each of the two branches is a ReLU-activated Dense layer containing 64 neurons, represented by a $1 \times 64$ vectors.
+We combine these model layers by using a \textit{concatenation layer} to fuse the two column vectors together, "vertically", such that the result is a $1 \times 128$ vector.
+This vector is then transformed into the final dense layer, which uses the softmax activation, and encodes the joint predictions based on contributions of both model branches.
+Again, compare this the the concept of two different bodily senses detecting the same object or environment.
+Information is produced from a single sources, received through multiple senses, but ultimately those experiences are combined in a such a way to produce a single prediction label.
 
@@
 \begin{center}
-\begin{tabular}{||c|c|c||c|c|c||}
+\begin{tabular}{||c|c|c| |c|c|c||}
 \hline
-\textbf{Class Index} & \textbf{Class Name} & \textbf{Count} & \textbf{Class Index} & \textbf{Class Name} & \textbf{Count} \\
+\textbf{Class Index} & \textbf{Class Name} & \textbf{Counts} & \textbf{Class Index} & \textbf{Class Name} & \textbf{Counts} \\
 \hline \hline
-$0$ & Alto Flute & $72$ & & \\ \hline
-$1$ & Alto Saxophone & 128&  \\ \hline
-$2$ & Banjo &
-$3$
-$4$
-$5$
+$0$ & Alto Flute & $72$ 			& $20$ & Marimba & $364$ \\ \hline
+$1$ & Alto Saxophone & $128$ 		& $21$ & Oboe & $666$  \\ \hline
+$2$ & Banjo & $74$ 					& $22$ & Sawtooth Wave & $200$ \\ \hline
+$3$ & Bass & $1060$ 				& $23$ & Tenor Saxophone & $732$ \\ \hline
+$4$ & Bass Clarinet & $1036$ 		& $24$ & Sine Wave & $200$ \\ \hline
+
+$5$ & Bass Flute & $76$ 			& $25$ & Soprano Saxophone & $128$\\ \hline
+$6$ & Bassoon & $800$ 				& $26$ & Square Wave & $200$ \\ \hline
+$7$ & Bass Trombone & $54$ 			& $27$ & Tenor Trombone & $66$ \\ \hline
+$8$ & $B\flat$ Clarinet & $938$ 	& $28$ & Triangle Wave & $200$ \\ \hline
+$9$ & Bells & $164$ 				& $29$ & Trombone & $831$ \\ \hline
+
+$10$ & Violoncello & $1079$ 		& $30$ & $B\flat$ Trumpet & $627$ \\ \hline
+$11$ & Contrabassoon & $710$ 		& $31$ & Tuba & $1046$ \\ \hline
+$12$ & Crotale & $50$ 				& $32$ & Vibraphone & $334$ \\ \hline
+$13$ & $E\flat$ Clarinet & $78$ 	& $33$ & Viola & $1173$ \\ \hline
+$14$ & English Horn & $1382$ 		& $34$ & Violin & $787$ \\ \hline
+
+$15$ & Flute & $1032$ 				& $35$ & Whitenoise & $200$ \\ \hline
+$16$ & Guitar & $106$ 				& $36$ & Xylophone & $176$ \\ \hline
+$17$ & Hihat & $10$ 				& $37$ & & \\ \hline
+$18$ & French Horn & $740$ 			& $38$ & & \\ \hline
+$19$ & Mandolin & $364$ 			& $39$ & & \\ \hline
 
@@
 \end{center}
-\caption{Instruments categories used in the classification task. Note that the network uses only integers to indentify sources while the }
+\caption{Instruments categories used in the classification task.
+Note that the network uses only integers given by "Class index" to indentify sources.
+The string "Class Name" is keep for human readability}
 \end{figure}
 
-\paragraph*{}Rather than explore each class individually, we can examine the properties of groupings of musical instruments by using the \textit{Hornbostel-Sachs} system \textit{red}{Citation needed!}.
+\paragraph*{}Rather than explore each class individually, we can examine the properties of groupings of musical instruments by using the \textit{Hornbostel-Sachs} organization system.
 In this syetem, musical instruments or sound sources can be divided up into four broad categories based on the nature of the sound-producing material.
@@
 A features is a quantitative, low-dimensional representation of a sample that conveys key characteristics of it.
-For example, in classifying types of animals, a feature could be the mass, mass volume or number of teeth on the animal.
+For example, in classifying types of animals, a feature could be the mass, volume or number of teeth on the animal.
 Typically, we produce a set of features $p$ for each sample and assemble them into a $1 \times p$ vector called a \textit{feature vector} which acts as a list of descriptive qualities of the sample \cite{Geron,James}.
@@
 
-\paragraph*{}From each audio file sample, we derive an identical set of $p$ predictors that will be use for classification.
-For this multi-modal neural network, the $p$ predictors are arranged into two separated structures, each called a \textit{design matrix}, described in sec.
+\paragraph*{}From each audio file sample, we calculate the same predictors that will be use for classification.
+The predictors are arranged into two separated structures, each called a \textit{design matrix}, described in sec.
 (\ref{subsubsec-DesignMatrix}) \cite{Goodfellow,Geron}.
-
-\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" about specifically how features must be chosen \cite{Virtanen}:
+Each sample in the design matrix $X_1$ contains $N \times k$ predictors, and the matrix $X_2$ contains $1 \times p$ predictors.
+For the purposes of exploring the properties of feature space, we consider the $p$ predictors for each sample in $X_2$.
+
+\paragraph*{}Feature space is a $p$ dimensional vector space where each basis vector represents a predictor \cite{Goodfellow,James}.
+The value that we compute for each predictor is the the value of that component in the space.
+This means that each sample can be described by this $p$-dimensional vector, given by each row of the design matrix $X_2$.
+For samples $x^{(a)}$ and $x^{(b)}$ that belong to the same class, we expect the quantity $||x^{(a)} - x^{(b)}||_{2}$ to be reasonably small, indicating that the two sample lie "close together" in space.
+Similarly, for samples $x^{(c)}$ and $x^{(d)}$ that belong to different classes, we expect the quantity $||x^{(c)} - x^{(d)}||_{2}$ to be comparably large, indicating that the two sample lie "far apart" in space.
+
+\paragraph*{}We can expand this idea by considering by how features should behave within each class, and between each class.
+Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" about specifically how features must be chosen \cite{Virtanen}:
 \begin{quote}
@@
 \end{quote}
+This is to say, features should \textit{ideally} form non-overlapping groups or bubbles that allows classifiers to effectively differentiate categories.
+Given the complexity of real-world problems, this is an often unrealistic goal \cite{Goodfellow,James}.
+However under the right circumstances, classifiers can still produce parameters that allow for reasonable performance \cite{Geron,Loy}.
+In practice, a neural network does not rely on comparing the norms of different samples in feature space, but rather uses something called a \textit{decision boundary}.
 
@@
 \paragraph*{}This concept stems from the idea that when a trained neural network classifier makes a prediction, it is doing so based on a set of generated \textit{decision boundaries} \cite{Geron,James}.
+To explore decision boundaries, consider a simplified 2D feature space.
 
@@
 % ================================================================
-
-\subsection{Assembling the Design Matrices}
-\label{subsec-AssembleXs}
-
-\textcolor{blue}{I would like to use some figures here to graphically represent how the feature vectors and spectrograms are concatenated into the design matrices.
-I may help with the geometry of the situation}
-
-% ================================================================
 % ================================================================

### 2020-11-28 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Minor updates to thesis draft

@@
 \paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}.
-These signals can take the form of day-to-day topics such as weather measurements, financial reports, or audio-visual media, and extend into disciplines of medicine, physics, and digital signal processing.
-In all cases, we explore a problem where the task to categorize the sample, or subset of the sample into one of $k$ \textit{bins} called classes \cite{Mierswa,Virtanen,Geron}.
-
-\paragraph*{}For this classification task, we have developed an automated model (called a \textit{classifier}) which can process information from a time-series audio file, and group the file based on it's prediction of what produced the sound in that file.
-For example, classifying an audio file which contains the waveform of a clarinet sustaining a single note should return the classification prediction of "clarinet" and so forth.
-This non-trivial task requires developing a model
-
- Developments in computational efficiency and the age of \textit{Big Data} has lead to a staggering increase in the utilization
+These signals can take the form of day-to-day topics such as weather measurements, financial reports, or audio-visual media, and extend into more niche disciplines of medicine, physics, and digital signal processing.
+
+\paragraph*{}Recent progress in high performance computing and computational efficiency have given rise to another burst
 
@@
 This stage is detailed in sec.(\ref{subsubsec-Preprocessing}).
+
 % ================================================================
@@
 Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-LinearTransform}).
-$\sigma^{(l)}$ is some activation function which introduces the ability to account for non-linearity in the
-
-\paragraph*{}The combination of Eq.
+$\sigma^{(l)}$ is some activation function which introduces the ability to account for non-linearity in the decision boundaries.
+The combination of Eq.
 (\ref{eqn-LinearTransform}) and Eq.
@@
 (\ref{eqn-altLayerFunction}).
-Below, we discuss and describe the types of layer functions that are used to produce the classification model in this project.
+In this, we discuss and describe the types of layer functions that are used to produce the classification model in this project.
 
@@
 
-\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer, or \textit{Fully-Connected} layer, was one of the earliest function types used in artificial neural network models \cite{Geron2,Loy,McCulloch}.
-They are among the most commonly used layer types.
-A dense layer is composed of a layer of \textit{artificial neurons}, each of which holds a numerical value within it, (usual a double-precision floating point number) called the \textit{activation} of that neuron.
+\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer, or \textit{Fully-Connected} layer, was one of the earliest and most common function types used in artificial neural network models \cite{Geron2,Loy,McCulloch}.
+A dense layer is composed of a layer of \textit{artificial neurons}, each of which holds a numerical value within it, (usually a double-precision floating point number) called the \textit{activation} of that neuron.
 This idea was developed from McCulloch and Pitts' work \cite{McCulloch} in attempting to model cognitive processes as mathematical functions, and was expanded upon by Frank Rosenblatt in  1957 by combining many dense layers together to form a multilayer perceptron (MLP) \cite{Geron,Loy,Levine}.
@@
 \end{equation}
-Eq.
-(\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}.
-\textcolor{red}{How Do I finish this section?
-Uses of Dens layer, physical meaning?}
+Eq. (\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}.
+
+\paragraph*{}The dense layer acts as an
 

### 2020-11-29 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Major updates to Thesis
- Addednew figures as well!

@@
 Because of the complexity of sound recognition, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
-Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an solution that allows for a computer to \textit{learn} from labeled training examples in order \textit{teach} itself.
-One such an algorithm that has been used for this type of task is a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine,Virtanen}.
+Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an solution that allows for a computer to \textit{learn} from labeled training examples in order \textit{teach} itself \cite{Bishop,Mitchell}.
+One such an algorithm that has been used for this type of task is a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine}.
 
@@
 The result of such an analogy is a computer program that is reminiscent of the a brain in that the program can \textit{learn} in a sense.
-Where a biological brain uses connections of chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Geron,Levine}.
+Where a biological brain uses connections of chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Geron,Levine,Bishop}.
 
 \paragraph*{}When a listener hears a sound, millions of neurons in their brain exchanges those chemical and electrical signals in such a way as to be able to identify the source of that sound \cite{Geron,Virtanen}.
-More conceptually, we can say that a listener is presented with a set of information $x$, which is air molecules vibrating near their tympanic membrane \cite{White}.
+More conceptually, we can say that a listener is presented with a set of information $x$, which is air molecules vibrating near their tympanic membrane \cite{White,Olson}.
 That information is then passed into the brain where some function $F$ is used to model the incredibly complex set of neural connections.
@@
 \end{equation}
-Eq. (\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}.
-
-\paragraph*{}The dense layer acts as an
+Eq.
+(\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}.
+Below, we detail pseudo-code for what a "Call" method for a dense layer node in a computational graph may look like \cite{Geron,Tensorflow} Compare this process with Eq.
+(\ref{eqn-DenseFeedForward}).
+
+\begin{algorithm}[H]
+\caption{Typical "Call" method for a dense layer in a neural network that contains $n$ neurons/nodes.
+This example shows the computation over a single input $x^{(l-1)}$ but a practical implementation should include mini-batches of samples.}
+\label{alg-CallDense}
+
+\begin{algorithmic}
+\REQUIRE $x^{(l-1)} \leftarrow$ Input activations shaped into $(m \times 1)$ column vector
+\REQUIRE $n \leftarrow$ Number of nodes in this dense layer
+\REQUIRE $\sigma^{(l)} \leftarrow$ Activation function for this layer
+\REQUIRE $W \leftarrow$ a $(n \times m)$ matrix of weights
+\REQUIRE $b \leftarrow$ a $(m \times 1)$ vector of bias values
+
+Evaluate linear activation values by computing the standard matrix-vector produce of $W^{(l)}$ and $x^{(l-1)}$:\\
+$z[i] \leftarrow b[i] + \sum_{j=0}^{n-1} W[i,j] x^{(l-1)}[j]$ \\
+Evaluate output activation values by applying the activation function to each element in the linear activation column vector $z$:\\
+$x^{(l)}[i] \leftarrow \sigma^{(l)}\big[ z[i] \big]$ \\
+
+Store both activation arrays for back-propagation. Return the output activations:\\
+\RETURN $x^{(l)}$
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 \label{eqn-ConvFeedForward}
-x^{(l)}_k = \sigma^{(l)}\bigg[ \Big( \sum_{u=0}^{m-1} \sum_{v=0}^{n-1} x^{(l-1)}(i,j) W^{(l)}_k(i - u,j - v) \Big) + b^{(l)}_k \bigg]
-\end{equation}
-\textcolor{red}{Please check my math here!}
+x^{(l)}_k(i,j) = \sigma^{(l)}\bigg[ \Big( \sum_{u=0}^{m-1} \sum_{v=0}^{n-1} W^{(l)}(i,j) x^{(l-1)}_k(i - u,j - v) \Big) + b^{(l)}_k \bigg]
+\end{equation}
 This operation repeats for each of the $K$ feature maps. Each maps has it's own $n \times m$ weighting matrix and appropriately shaped bias .
@@
 Among these are (i) \textit{sparse-connectivity}: not every single activation (pixel) is connect to every single output pixel, so it is more computationally efficient, (ii) \textit{positional invariance}: key features can be identified regardless of where they are in the layer, and (iii.) \textit{Automatic feature detection} as the training process will update the filters to identify dominant features in the data without human instruction \cite{Geron,Goodfellow,Loy}.
+Below we detail what the "Call" method for a 2-dimensional convolutional neural network may look like.
+Compare this procedure with Eq.
+(\ref{eqn-ConvFeedForward}).
+
+\begin{algorithm}[H]
+\caption{Typical "Call" method for a 2-Dimensional Convolutional layer in a neural network that uses $K$ filters, of $n \times m$ kernels, with an assumed stride size of $1 \times 1$.
+This example shows the computation over a single input $x^{(l-1)}$ but a practical implementation should include mini-batches of samples.}
+\label{alg-CallConv2D}
+
+\begin{algorithmic}
+\REQUIRE $x^{(l-1)} \leftarrow$ Input activations shaped into $(N \times M)$ matrix
+\REQUIRE $K \leftarrow$ The number of filters (feature maps) to be used.
+\REQUIRE $\sigma \leftarrow$ Activation function for this layer
+\REQUIRE $W_{k} \leftarrow$ a $(n \times m)$ matrix of weights 
+(called a weighting kernel in this case), $k \in [0,...,k-1]$
+\REQUIRE $b_{k} \leftarrow$ a $(m \times 1)$ vector of bias values, $k \in [0,...,k-1]$ \\
+
+\FOR {Each feature map, $k \in [0,1,2,...,k-2,k-1]$}
+	\item Evaluate linear activation values by computing the 2D convolution-product of 
+	$W_{k}$ and $x^{(l-1)}_{k}$:\\
+	\item $z_{k}[i,j] \leftarrow b_{k} + 
+	\sum_{i=0}^{N-1}\sum_{j=0}^{M-1} W_{k}[u,v] x^{(l-1)}_{k}[u-i,v-j]$ \\
+	\item Evaluate output activation values by applying the activation function to each element in the linear activation 			matrix $z$:\\
+	$x^{(l)}_{k}[i,j] \leftarrow \sigma\big[ z_{k}[i,j] \big]$ \\
+\ENDFOR
+
+Store both activation arrays for back-propagation. Return the output activations from each of the $K$ filters:\\
+\RETURN $x^{(l)}$
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 \begin{figure}[h]
-\label{fig-2DMaxPool}
+
 \begin{center}
@@
 \caption{The result of 2D maximum-pooling an input array. This image was adapted from Loy, pg. 126 \cite{Loy}}
+\label{fig-2DMaxPool}
 \end{figure}
@@
 For this $k$-classes classification task, we choose to use the \textit{Categorical Crossentropy} (CXE) cost function.
-For a sample labeled by the one-hot-encoded vector $y$ and corresponding prediction vector $y^*$, the CXE cost for a single sample is given by \cite{Goodfellow,Virtanen}:
+For a sample labeled by the one-hot-encoded vector $y$ and corresponding prediction vector $y^*$, the CXE cost for a single sample is given by \cite{Goodfellow,Virtanen,Bishop}:
 \begin{equation}
@@
 \paragraph*{}By optimizing the parameters $\Theta$ in the network model, we allow for the output of a consistently low cost function to be produced across all samples in the data set.
-When a model produces consistently low cost values across new unseen samples, we consider this to be a \textit{trained} or \textit{fit} model \cite{Goodfellow}.
+When a model produces consistently low cost values across new unseen samples, we consider this to be a \textit{trained} or \textit{fitted} model \cite{Goodfellow,Loy,Mitchell}.
 
@@
 \paragraph*{}Feature space is a $p$ dimensional vector space where each basis vector represents a predictor \cite{Goodfellow,James}.
-The value that we compute for each predictor is the the value of that component in the space.
-This means that each sample can be described by this $p$-dimensional vector, given by each row of the design matrix $X_2$.
+Each sample can be described by this $p$-dimensional vector, given by each row of the design matrix $X_2$.
 For samples $x^{(a)}$ and $x^{(b)}$ that belong to the same class, we expect the quantity $||x^{(a)} - x^{(b)}||_{2}$ to be reasonably small, indicating that the two sample lie "close together" in space.
 Similarly, for samples $x^{(c)}$ and $x^{(d)}$ that belong to different classes, we expect the quantity $||x^{(c)} - x^{(d)}||_{2}$ to be comparably large, indicating that the two sample lie "far apart" in space.
+Not that this is an idealization, and not always the defining case for the decision behavior.
 
@@
 \subsubsection{Decision Boundaries}
+\label{subsubsec-Decision}
 
@@
 \paragraph*{}This concept stems from the idea that when a trained neural network classifier makes a prediction, it is doing so based on a set of generated \textit{decision boundaries} \cite{Geron,James}.
-To explore decision boundaries, consider a simplified 2D feature space.
+To explore decision boundaries, consider a simplified \textit{toy data set} with a 2D feature space for a classifier that must only discern between \textit{Class A} and \textit{Class B}.
+We can visualize each sample in this 2D space, and color-code (and shape-code) each sample according according to it's class label as in Fig.
+(\ref{fig-LinSep1}).
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=0.35]{../MakeFigures/LinearSeparable1}
+\end{center}
+\caption{Feature Space with Linear separability between two classes}
+\label{fig-LinSep1}
+\end{figure}
+
+\paragraph*{}In the case of these chosen, features, we can see a clear, well-defined separation between samples in each class.
+In practice, this is rarely the case, but shows graphically an example where a linear decision boundary arises \cite{James}.
+Notice how we can also use "box-and-whisker plots" to neatly summarize how each feature (each component) behaves by dividing the samples for each class based into quartiles.
+Notice how on the right of Fig.(\ref{fig-LinSep1}) the box plots for feature 2 show no overlap, but the box plots for feature 1, at the top show very similar behavior between classes.
+Despite this, a classifier can produce a clean boundary to separate the two classes.
+Note that this may not be the exact boundary used by a model, but it represents an ideal case.
+
+\paragraph*{}We can also explore an example where both features have mutual overlap between classes, but we can still form a reasonable decision boundary in the space.
+Consider Fig.
+(\ref{fig-LinSep2}) and Fig.
+(\ref{fig-LinNonSep}).
+In both cases, we see the box plot for each feature overlap considerably, and we also see sample that appear to "cross" the decision boundary.
+This crossing the boundary is why it is so useful that we choose an activation function that encode the output of the neural network as a probability of being in either class as opposed to a hard prediction \cite{Loy,Geron}.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=0.35]{../MakeFigures/LinearSeparable2}
+\end{center}
+\caption{Feature Space with near linear separability between two classes}
+\label{fig-LinSep2}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=0.35]{../MakeFigures/LinearNonSeparable}
+\end{center}
+\caption{Feature Space with near linear non-separability between two classes}
+\label{fig-LinNonSep}
+\end{figure}
+
+\paragraph*{}Samples that appear very near to decision boundary will likely have almost equal probability of occurring in either class, and samples that appear very far from the decision boundary will likely have very much larger probability of occurring in one class or the other \cite{Bishop,James}.
+
+\paragraph*{}Note that these are over-idealized cases, constrained to two classes in two dimensions.
+The classifier implemented in this project uses $24$ classes in a single branch and outlines a probabilty estimate over $37$ classes.
+Given the related nature of many of the categories, (i.e.
+belonging to similar Hornbostel-Sachs groups), such well-defined decision boundaries are unlikely to be produced.
+Note also that the examples provided showed only \textit{linear} boundaries, where the inclusion of non-linear activation functions will create far more complex systems in a far higher-dimensional space.
+
+\paragraph*{}From these examples, we conclude the mathematical nature of features allow each sample to be characterized by a vector in $p$-dimensional feature-space\cite{Goodfellow}.
+We expect feature of the same class to exhibit similar behaviors as to allow a trained classifier to develop multiple decision boundaries in the higher-dimensional space \cite{James,Bishop}.
+As a consequence, we derive the predictors from the physical mechanical nature of each instrument or sound-source.
 
@@
 
-\paragraph*{}From each training audio file, we produce a spectrogram matrix explored in sec.
-(\ref{subsec-Spectrogram}) and a feature vector, as well as a target label for training purpose.
-From a collection of multiple samples, the spectrograms are concatenated into a single object $X_1$, and the feature vectors are concatenated into an object, $X_2$.
-Each objects is a multidimensional array called a \textit{design matrix} \cite{Geron,Goodfellow,Loy,Zerizel}.
-For any machine learning task, a  design matrix is an object that contains real floating-point numbers that store the features in a convenient way for the neural network to digest.
-For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples.
+\paragraph*{}Each audio sample is given by an $N \times k$ spectrogram matrix explored in sec.
+(\ref{subsec-Spectrogram}), a $1 \times p$ feature vector, and a target label, $y$ for training purpose.
+As explored in sec.
+(\ref{subsubsec-Decision}), each sample can be associated with a vector in feature-space.
+In order to efficiently present the information to the model for training or predicting, we extract a batch of $b$ samples and produce the two arrays form each.
+
+\paragraph*{}Since the spectrogram and feature vector represent different \textit{modalities}, we construct two separate \textit{design matrices}, $X_1$ and $X_2$ \cite{Geron,Li,Ngiam}.
 Each has shape given by:
@@
 \label{eqn-X1Shape}
-X_1 \in \mathbb{R}^{(b \times N' \times k)}
+X_1 \in \mathbb{R}^{(b \times N \times k)}
 \end{equation}
@@
 \end{equation}
-Where $N' \times k$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sect.
+Where $N \times k$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sect.
 (\ref{subsec-spectrogram}).
@@
 The first axis, with size $b$ indicates that there are $b$ audio file samples stored in that design matrix.
+Organizing the samples in this fashion allows for both easy machine and human interpretation of each axis or index.
 
@@
 \end{enumerate}
+
+\paragraph*{}Given these standardization methods, we can exact the predictors for each sample and explore how they behave mathematically, and what they represent physically.
 
@@
 The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
-Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space signal containing $N$ samples
+Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space signal containing $N$ samples is given by \cite{Taylor,Virtanen}
 \begin{equation}
@@
 
+\bibitem{Bishop}
+Bishop, Christopher M. \textit{Pattern Recognition and Machine Learning}. Springer New York, 2016.
+
 \bibitem{Geron}
@@
 
-\bibitem{Tenorflow}
+\bibitem{Tensorflow}
 TensorFlow: Large-scale machine learning on heterogeneous systems,

### 2020-11-30 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Added new figures, Updates to Thesis

@@
 \caption{Backwards propagation system, in a standard densely connected deep neural network.
-Each iteration in the \textit{for-loop} computes the gradient of the cost function $J$ with respect to the weight and bias arrays.
+Each iteration in the \textit{for-loop} computes the gradient of the cost function $J$ with respect to the weight and bias arrays in a given layer $(l)$.
 Each element in those arrays $dW$ and $db$ is the discrete gradient of the cost due to that parameter.
 A practical application of this algorithm should include batches of samples instead of a single sample and a regularizing function at each step.}
-\label{algBackProp}
+\label{alg-BackProp}
 
@@
 
-\FOR {$L-1,L-2,...,2,1$}
+\FOR {$l \in [L-1,L-2,...,2,1]$}
 	\item Compute gradient w.r.t pre-nonlinear activation portion of layer function
@@
 \REQUIRE Small constant $\delta$ for numerical stabilization, usually about $10^{-7}$.
-\REQUIRE constants $\rho_1$, $\rho_2$ used got exponential decay rates, usually $0.9$ and $0.999$ respectively.
-\REQUIRE Subroutine/function to compute gradient of cost function.
+\REQUIRE Constants $\rho_1$, $\rho_2$ used track exponential decay rates, usually $0.9$ and $0.999$ respectively.
+\REQUIRE Subroutine/function to compute gradient of cost function See Alg. (\ref{alg-BackProp})
 \REQUIRE Mini-batch size, $m$
@@
 \label{eqn-shapeX2}
-X_2 \in \mathbb{R}^{(64 \times 20)}
+X_2 \in \mathbb{R}^{(64 \times 24)}
 \end{equation}
@@
 The string "Class Name" is keep for human readability}
+\label{fig-ClassList}
 \end{figure}
@@
 This can be computed per total sound wave, per analysis-frame, or per unit time.
-This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform \cite{Kahn,Liu,Zhang} that musical instruments do.
+This feature is most commonly associated with differentiating speech from music, because speech presents a more jagged and often less periodic waveform that musical instruments do \cite{Khan,Liu,Zhang} .
 
@@
 
-\paragraph*{}Rather than producing filter banks based on the linear Hertz scale, the frequency axis of the signal is transformed into units of \textit{Mels}, which is used to account for the non-linearity in human pitch perception \cite{Serizel,Kahn}.
+\paragraph*{}Rather than producing filter banks based on the linear Hertz scale, the frequency axis of the signal is transformed into units of \textit{Mels}, which is used to account for the non-linearity in human pitch perception \cite{Serizel,Khan}.
 Filter banks are produced to be evenly spaced on the Mel scale, and then transformed back into the Hertz scale.
@@
 For example, if we had a $2 \times 2$ matrix with entries $100$ and $20$ in the main diagonal, it seems that class $A$ has a much higher prediction success than class $B$.
-However, if there are $200$ elements in class $A$, and only $21$ in class $B$, then we see that class $A$ has a $50\%$ classification rate, while class $B$ has a $95\%$ classification rate, To Combat this, we typically normalize each confusion matrix by the number of samples in each "actual" class.
-Put simply, we all elements in a given row by the sum of that row.
+However, if there are $200$ elements in class $A$, and only $21$ in class $B$, then we see that class $A$ has a $50\%$ classification rate, while class $B$ has a $95\%$ classification rate.
+Consider the list of instrument classes in Fig.(\ref{fig-ClassList}) and notice how all instruments are not equally represented.
+This creates a training bias such that the model is more heavily trained on a particular class compared to others.
+This may also show when making predictions, where the classifier is more likely to predict samples that it has been trained on more \cite{James,Loy}.
+To Combat this, we typically normalize each confusion matrix by the number of samples in each "actual" class.
+Put simply, we divide each element in a given row by the \textit{sum} of that row.
 
@@
 
-\subsubsection{Micro F1-Score}
-
-% ================================
-
-\subsubsection{Accuracy Score \&}
+\subsubsection{F1-Score}
+
+\paragraph*{}F1-score (also called F-score) is the harmonic mean of precision and recall scores and it also bounded on $[0,1]$ with a higher score being favorable \cite{Geron}.
+Often, the two metrics can be through of as somewhat \textit{exclusive} to each other - the higher one, the lower the other.
+Compare this with the idea that the more \textit{sensitive} the model is, the less \textit{specific} it is, and vice-versa.
+This phenomenon is called the \textit{precision-recall tradeoff} \cite{Geron,James}.
+We compute the $F1$ score for a class $k$ as:
+\begin{equation}
+\label{eqn-F1Score}
+\text{F1}_{j} = 2 \times \frac{\text{Prec}_j + \text{Recall}_j}{\text{Prec}_j \times \text{Recall}_j}
+\end{equation}
+
+\paragraph*{}The $F1$ favors models with both a high precision and high recall score.
+Some models allow for the ability to adjust the threshold of the decision function.
+This means that by changing a few parameters that are external to the classifier itself, we can change how sensitive or specific a model is when making it's class decision.
+In the case of this multi-category classifier, this is somewhat like modifying the generated decision boundaries as to change the outputted probability distribution.
+In case cases, it is useful to use the $F1$ score to find the set of hyper-parameters that allow for the classifier to produce both the highest possible precision \textit{and} recall score.
+
+% ================================
+
+\subsubsection{Accuracy Score}
 
@@
 
-\paragraph*{}For a multi-class problem, we present accuracy over \textit{all} classes simultaneously. It is the ratio of the sum of the main diagonal to the sum or all entries in the matrix:
-\begin{equation}
-\label{eqn-AvgAccuracy}
+\paragraph*{}For a multi-class problem, present accuracy over each individual class, called \textit{micro-accuracy} \cite{James}.
+The accuracy for a class $j$ is the correct predictions related to the class divided by the total predictions and total counts of the class.
+We express this mathematically by using sums over each row, each column, and the main diagonal as such:
+\begin{equation}
+\label{eqn-Accuracy}
+\text{Accuracy}_j = \frac{\sum_{i}C_{i,i}}{\sum_{i}C_{i,i} + \sum_{i \neq j}C_{i,j} + \sum_{i \neq j}C_{j,i}}
+\end{equation}
+Where all sum indexes goes from $0$ to $k-1$.
+
+\paragraph*{}We can also present \textit{global accuracy} or \textit{macro accuracy} by computing the acurracy over the full confusion matrix.
+This would then by the ratio of all correct predictions (the main diagonal) to all predictions (the sum of the matrix).
+We can express this as:
+\begin{equation}
 \text{Accuracy} = \frac{\sum_{i}C_{i,i}}{\sum_{i}\sum_{j}C_{i,j}}
 \end{equation}
-Where all sum indexes goes from $0$ to $k-1$.
 
@@
 \begin{center}
-%\includegraphics[scale=0.2]{•}
-\textcolor{red}{Precision Score Goes Here}
-\textcolor{red}{Recall Score Goes Here}
+
 \end{center}
@@
 
+\subsection{Executing Cross Validation}
+
 \paragraph*{}To formally produce classification predictions on the chaotic synthesizer wave forms, we must use all of the principles outlined in the previous sections.
@@
 (\ref{sec-Features}) and appropriate architecture sec.
-(\ref{subsec-Architecture}), We run a
-
-we produce a neural network \textit{ChaoticSynthClassifier} and train it on the roughly $18,000$ audio files that serve as the training set.
+(\ref{subsec-Architecture}), We run a $K=10$ folds cross validation program as in Alg.(\ref{alg-CrossValidation}).
+For each of the $10$ models, we produce a standard confusion matrix, an compute the (i) accuracy score, (ii) precision score, (iii) recall score, and (iv) F1 score.
+For each of the $37$ classes, we compute the arithmetic mean of the metrics across the $10$ folds.
+We show the results of this in Figs.
+(\ref{fig-HighWindsScores}), (\ref{fig-LowWindsScores}), (\ref{fig-BrassScores})
+
+\paragraph*{}Additionally, we report the average of each four metrics across all classes for each of the $10$ splits in Fig.
+(\ref{fig-ValidationTable}).
+We also present a more condensed version of the data by showing the average, minimum, maximum, and variance of each score in Fig.
+(\ref{fig-ValidationStats}).
+Each value is on the interval $[0,1]$, with higher values being more favorable.
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\textbf{Split Index} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} \\ \hline
+$0$ & 0.992969341 & 0.849762613	& 0.853483643 & 0.838007935 \\ \hline
+$1$ & 0.993086645 & 0.857063114	& 0.865737308 & 0.854069688 \\ \hline
+$2$ & 0.994175444 & 0.858936065	& 0.854231756 & 0.851319866 \\ \hline
+$3$ & 0.993883291 & 0.887070101	& 0.901606142 & 0.882074022 \\ \hline
+$4$ & 0.992941956 & 0.884115922	& 0.902609597 & 0.884775112 \\ \hline
+$5$ & 0.992941956 & 0.884115922	& 0.902609597 & 0.884775112 \\ \hline
+$6$ & 0.994315799 & 0.856425689	& 0.842680234 & 0.834139910 \\ \hline
+$7$ & 0.993057475 & 0.869049669	& 0.867171387 & 0.856152544 \\ \hline
+$8$ & 0.992979711 & 0.843322939	& 0.866599329 & 0.846637817 \\ \hline
+$9$ & 0.992799981 & 0.842635691	& 0.877821096 & 0.832496007 \\ \hline
+\end{tabular}
+\end{center}
+\caption{Metrics averaged over all classes for $K=10$ validation splits}
+\label{fig-ValidationTable}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\textbf{Measure} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} \\ \hline
+\textbf{Average} & 0.993385794 & 0.860133646 & 0.872055273 & 0.853799365 \\ \hline
+\textbf{Minimum} & 0.992799981 & 0.842635691 & 0.842680234 & 0.832496007 \\ \hline
+\textbf{Maximum} & 0.994315799 & 0.887070101 & 0.902609597 & 0.884775112 \\ \hline
+\textbf{Variance}& 2.88066E-07 & 0.000215270 & 0.000373321 & 0.000293214 \\ \hline
+\end{tabular}
+\end{center}
+\caption{Metric statisitcs over all classes  and all validation splits}
+\label{fig-ValidationStats}
+\end{figure}
+
+\begin{figure}[H]
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/AltoFlute}
+	\caption{Alto Flute}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/AltoSax}
+	\caption{Alto Saxophone}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/BbClarinet}
+	\caption{$B\flat$ Clarinet}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/EbClarinet}
+	\caption{$E\flat$ Clarinet}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/EnglishHorn}
+	\caption{English Horn}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Flute}
+	\caption{Flute}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Oboe}
+	\caption{Oboe}
+	\end{subfigure}		
+	\begin{subfigure}[b]{0.45 \textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/SopSax}
+	\caption{Soprano Saxophone}
+	\end{subfigure}
+
+\caption{Performance Metrics Across all High Ranged Woodwind Instruments}
+\label{fig-HighWindsScores}
+\end{figure}
+
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/BassClarinet}
+	\caption{Bass Clarinet}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/BassFlute}
+	\caption{Bass Flute}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Bassoon}
+	\caption{Bassoon}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/ContraBassoon}
+	\caption{Contra Bassoon}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Saxophone}
+	\caption{Tenor Saxophone}
+	\end{subfigure}
+\caption{Performance Metrics Across all Mid and Low Ranged Woodwind Instruments}
+\label{fig-LowWindsScores}
+\end{figure}
+
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/BassTrombone}
+	\caption{Bass Trombone}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Horn}
+	\caption{French Horn}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/TenorTrombone}
+	\caption{Tenor Trombone}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Trombone}
+	\caption{Trombone}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Trumpet}
+	\caption{$B\flat$ Trumpet}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Tuba}
+	\caption{Tuba}
+	\end{subfigure}
+\caption{Performance Metrics Across all Brass Instruments}
+\label{fig-BrassScores}
+\end{figure}
+
+\paragraph*{}With cross validation completed and the results
+
+% ================================================================
+
+\subsection{•}
 

### 2020-11-30 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisFigs.py

@@ -1,0 +1,91 @@
+"""
+Landon Buell
+PHYS 799.32
+Classifier Analysis Main
+28 July 2020
+"""
+
+        #### IMPORTS ####
+
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+import os
+import datetime
+
+import tensorflow as tf
+import tensorflow.keras as keras
+
+        #### OBJECT DEFINITIONS ####
+
+class MetricFigures :
+    """ Create Figures for Metrics of Each Class """
+
+    def __init__(self,classInts,classStrs,metricsArray):
+        """ Contstructor for MakeFigures Instance """
+        self.classInts = classInts
+        self.classStrs = classStrs
+        self.totalMetricsArray = metricsArray                       # shape = (nFiles,nMetrics,n_classes)
+        self.fileMetricsArray = np.mean(metricsArray,axis=0)        # shape = (nMetrics,n_classes)
+        self.avgMetricsArray = np.mean(self.fileMetricsArray,axis=-1)# shape = (nMetrics)
+
+    def __Call__(self,exportPath):
+        """ Call this Class """
+        print(self.avgMetricsArray)
+        metricsErr = np.array([ np.min(self.totalMetricsArray,axis=0),
+                                np.max(self.totalMetricsArray,axis=0)])
+        homePath = os.getcwd()
+        for (_int,_str) in zip(self.classInts,self.classStrs):          # class
+            print("Class:",_str)
+            #perClassMetrics = self.totalMetricsArray[:,:,_int]          # all metrics for this class
+            #self.BoxPlotMetricsForClass(perClassMetrics,_str,save=False)
+            perClassMetrics = self.fileMetricsArray[:,_int]
+            os.chdir(exportPath)
+            self.BarChartMetricsForClass(perClassMetrics,_str,show=False)
+            os.chdir(homePath)
+        return self
+
+    def BoxPlotMetricsForClass(self,X,namesave="",show=True,save=True):
+        """ Plot Accuracy, Precision, Recall for A Given Class """
+
+        boxprops = dict(linestyle='-',linewidth=4,color='black')
+        capprops = dict(linestyle='-',linewidth=3,color='green')
+        whiskprops = dict(linestyle='-',linewidth=4,color='black')
+        mednprops = dict(linestyle=':',linewidth=3,color='red')
+        meanprops = dict(linestyle='--',linewidth=3,color='blue')
+
+        plt.figure(figsize=(8,6))
[…]

### 2020-11-30 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisMAIN.py

@@ -14,34 +14,34 @@ os.environ['TF_CPP_MIN_LOG_LEVEL'] = '2'
 import tensorflow.keras as keras
 
 import AnalysisUtilities as utils
+import AnalysisFigs as Figs
 
         #### MAIN EXECUTABLE ####
         
 if __name__ == '__main__':
 
     # Establish local Directory Paths
-    parent = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\SignalClassifier-CrossValidation"
+    parent = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis"
     modelName = "XValAlphaCLF"
-    dataPath = os.path.join(parent,modelName+"-Output-Data")
-    exptPath = os.path.join(parent,modelName+"-Analysis")    
+    dataPath = os.path.join(parent,"SignalClassifier-CrossValidation",modelName+"-Output-Data")
+    metricsPath = os.path.join(parent,"Thesis\\FiguresMetrics")    
+    figuresPath = os.path.join(parent,"Thesis\\FiguresClasses")    
     n_classes = 37
 
     # Run Main program
     Program = utils.AnalyzeModels(modelName,dataPath,n_classes)
     encode,decode = Program.MakeDecodeDictionary()
 
-    Program.__Call__(exptPath)
-    Program.ExportMetrics(exptPath)
+    Program.__Call__(metricsPath)
+    Program.ExportMetricsBySplit(metricsPath)
+    Program.ExportMetricsByClass(metricsPath)
 
 
-    # Compute & Plots Avg. metrics per class
-    _ = np.arange(10)
-    ComputeMetrics = utils.ClassifierMetrics(n_classes,_,_,_)
-    scores = ComputeMetrics.MetricScores(Program.ConfusionMatrix)
-    os.chdir("C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis\\Thesis\\FiguresMetrics")
-    for i in range(n_classes):         # each class
-        className = decode[i]
-        print(className,Program.counts[i])
-        utils.ClassifierMetrics.PlotMetricsForClass(scores[:,i],className,False,True)
-    
+    # Prepare Figures
+    classIntegerNames = [x for x in range(n_classes)]
+    classStringNames = [decode[x] for x in range(n_classes)]
+
+    Figures = Figs.MetricFigures(classIntegerNames,classStringNames,Program.metricsArray)
+    Figures.__Call__(figuresPath)
+
     print("=)")

### 2020-11-30 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisUtilities.py

@@ -68,14 +68,26 @@ class AnalyzeModels:
                 pathList.append(fullPath)
         return pathList
 
-    def ExportMetrics(self,outputPath):
+    def ExportMetricsBySplit(self,outputPath):
         """ Export Metrics Array to Local path """
-        colNames = ["Accuracy","Precision","Recall"]
+        colNames = ["Accuracy","Precision","Recall","F1"]
         outputFrame = pd.DataFrame(data=None,index=None)
         outputFrame["CLF"] = [x.split("\\")[-1] for x in self.predictionFiles]
+        outputArray = np.average(self.metricsArray,axis=-1)
         for i in range(len(colNames)):
-            outputFrame[colNames[i]] = self.metricsArray[:,i]
-        outputPath = os.path.join(outputPath,self.outputFile)
+            outputFrame[colNames[i]] = outputArray[:,i]
+        outputPath = os.path.join(outputPath,"BySplit"+self.outputFile)
+        outputFrame.to_csv(outputPath,index=False)
+
+    def ExportMetricsByClass(self,outputPath):
+        """ Export Metrics Array to Local path """
+        colNames = ["Accuracy","Precision","Recall","F1"]
+        outputFrame = pd.DataFrame(data=None,index=None)
+        outputFrame["Class"] = [x for x in range(self.n_classes)]
+        outputArray = np.average(self.metricsArray,axis=0)
+        for i in range(len(colNames)):
+            outputFrame[colNames[i]] = outputArray[i]
+        outputPath = os.path.join(outputPath,"ByClass"+self.outputFile)
         outputFrame.to_csv(outputPath,index=False)
 
     def __Call__(self,exptPath):
@@ -86,16 +98,16 @@ class AnalyzeModels:
         self.classDictionary = self.GetKeywordFiles("Categories")[-1]
         homePath = os.getcwd()
 
-        nRows = len(self.predictionFiles)
-        nCols = 3
-        self.metricsArray = np.empty(shape=(nRows,nCols))
+        nFiles = len(self.predictionFiles)
+        nMetrics = 4
+        self.metricsArray = np.empty(shape=(nFiles,nMetrics,self.n_classes))
 
         # Initialize 3 Average Confusion matrices
         avgStandardConfMat = np.zeros(shape=(self.n_classes,self.n_classes))
         avgHitsWeightedConfMat = np.zeros(shape=(self.n_classes,self.n_classes))
[…]

### 2020-12-03 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Properties of musical instruments

@@
        	\begin{LARGE}
-       	\textbf{Classifying Chaotic Synthesizers with a Multimodal Neural Network} \\
+       	\textbf{Mapping Chaotically Generated Synthesizers to Real World Instruments with Machine Learning and Harmonic Analysis} \\
        	\end{LARGE}
@@
 
-\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}.
-These signals can take the form of day-to-day topics such as weather measurements, financial reports, or audio-visual media, and extend into more niche disciplines of medicine, physics, and digital signal processing.
-
-\paragraph*{}Recent progress in high performance computing and computational efficiency have given rise to another burst
+\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}.Whether its climate measurements, financial reports, audio-visual media, or medicine complex signal surround the modern world at every corner.
+
+\paragraph*{}Recent progress in high performance computing and computational efficiency have given rise to another burst in the
 
@@
 
-\paragraph*{}We have assembled training data samples than can be grouping in 38 classes of unique sources listed below:
+\paragraph*{}We have assembled training data samples than can be grouping into $37$ classes of unique sources listed below:
 
@@
 We describe the state of string over space and time with a function $U(x,t)$.
-The behavior of the string can be modeled by D'Alembert's 1-dimensional wave equation \cite{Haberman,Taylor}:
+The behavior of the string can be modeled by D'Alembert's 1-dimensional wave equation \cite{Haberman,Hunter,Taylor}:
 \begin{equation}
@@
 Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$.
+D'Alembert's equation indicates that the acceleration of any point on a string is directly proportional to the rate of change of the slope of the string at that point.
 Additionally, the string is fixed in place at both ends, with a nut at $x = 0$ and a bridge at $x = L$, which can be modeled by the boundary conditions \cite{Olson,White,Haberman}:
@@
 For example, for plucked stringed instruments, $f(x)$ may appear to be as triangle-like function, with a peak at some position $0 < x_0 < L$ where then string was struck.
-$g(x)$
-
-\paragraph*{}We explore solutions that take the form \cite{Haberman}:
-\begin{equation}
-U(x,t) = \psi(x)h(t)
-\end{equation}
-From this separation, we find that $\psi(x)$ and $h(t)$ each are composed of a linear combination of orthogonal trigonometric functions.
-Applying the boundary and initial conditions to the system allows for a linear combination of solutions \cite{Haberman}:
-\begin{equation}
-U(x,t) = 
-\sum_{n=1}^{\infty} \bigg( A_n \sin\big(\frac{n\pi x}{L}\big)\cos\big(\frac{n\pi vt}{L}\big)
-+ B_n \sin\big(\frac{n\pi x}{L}\big)\sin\big(\frac{n\pi vt}{L}\big) \bigg)
-\end{equation}
-The initial conditions are satisfied if:
-\begin{equation}
-\begin{array}{ll}
-    f(x) = \sum_{n=1}^{\infty} A_n \sin\big(\frac{n\pi x}{L}\big) \\
-    g(x) = \sum_{n=1}^{\infty} B_n\big(\frac{n\pi v}{L}\big)
-    			\sin\big(\frac{n\pi x}{L}\big)
-\end{array} 
-\end{equation}
-Where $A_n$ and $B_n$ are given by:
-\begin{equation}
-\begin{array}{ll}
-    A_n = \frac{2}{L} \int_{0}^{L} f(x) \sin\big(\frac{n\pi x}{L}\big) dx \\
-    B_n = \frac{2}{n\pi v} \int_{0}^{L} g(x) \sin\big(\frac{n\pi x}{L}\big) dx \\
-\end{array} 
-\end{equation}
-
-\subsubsection{Consequences of the Wave Equation}
-
-\paragraph*{}The solution that we have derived from the wave equation shows that the behavior of $U(x,t)$ is greatly dependent on the nature of the string's initial shape, $f(x)$, when struck.
-In the case of picked or plucked instruments, the initial shape of $f(x)$ would be something like a "ramp function":
-\begin{equation}
-\label{eqn-RampFunc}
-f(x) =
-\end{equation}
+It is these initial conditions that allow for the drastically different timbres that arise in the wave forms.
+
+\paragraph*{}Despite these differences, the wave equation is a \textit{linear} partial differential equation which allows for the fact that a linear combination of solutions is also a valid solution.
+In the case of the taught finite string that is fixed at both ends, such a guitar, viola or cello, the a solution tends to take the form of a sinusoidal function such a sine or cosine \cite{Hunter, Taylor, White}.
+
+\paragraph*{}The boundary continuations, and most forms of standard initial conditions allow for the each sinusoidal to fit exactly an integer wavelengths into the region $[0,L]$ \cite{Haberman,Hunter}.
+Physically, this corresponds to having the string vibrate with some fundamental frequency $f_0$, which represents it's lowest possible note,and a linear combination of higher harmonics, $n \times f_0$, where $n \in \mathbb{Z}$ \cite{Olson,Taylor,White}.
+
+\begin{figure}[H]
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/CELLO-F4}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Guitar-B2}
+	\end{subfigure}
+\end{figure}
 
@@
 
+\bibitem{Hunter}
+Hunter, Joseph L. \textit{Acoutics}. Prentice Hall, 1957.
+
 \bibitem{James}

### 2020-12-05 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Modified Figures, Modified Thesis

@@
 % Kevin Short
-% Physics 799%
+% Physics 799
 % 26 September 2020
@@
        	\begin{Large}
-       	\textcolor{red}{Thesis Subtitle}
+       	Multimodal Classification of Digital Signal
        	\end{Large}             
@@
 
+% ================================================================
+
+\subsection{Introduction}
+
 \paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}.Whether its climate measurements, financial reports, audio-visual media, or medicine complex signal surround the modern world at every corner.
 
+\paragraph*{}Consider the task of identifying the source of a sound.
+
 \paragraph*{}Recent progress in high performance computing and computational efficiency have given rise to another burst in the
@@
 \newpage
-\section{Methodology}
+\subsection{Methodology}
 \label{sec-Methodology}
@@
 
-\subsection{Designing the Function}
+\subsubsection{Designing the Function}
 
@@
 
-\subsection{Collecting and Pre-processing Raw Data}
+\subsubsection{Collecting and Pre-processing Raw Data}
 
@@
 
-\subsection{Designing Classification Features}
+\subsubsection{Designing Classification Features}
 
@@
 
-\subsection{Designing A Complementary Network Architecture}
+\subsubsection{Designing A Complementary Network Architecture}
 
@@
 
-\subsection{Testing and Evaluating Network Performance}
+\subsubsection{Testing and Evaluating Network Performance}
 
@@
 
-\subsection{Running Predictions of Chaotic Synthesizer Files}
+\subsubsection{Running Predictions of Chaotic Synthesizer Files}
 
@@
 \label{eqn-DFTMatrix}
-\mathbb{W} = \frac{1}{\sqrt{N}}
+\mathbb{W} = \frac{1}{N}
 \begin{bmatrix}
@@
 
-\paragraph*{}Most standard implementations of neural network models have all activations, weights, and biases to be real floating-point numbers cite{Levine,Loy,Tensorflow}.
+\paragraph*{}Most standard implementations of neural network models have all activations, weights, and biases to be real floating-point numbers \cite{Levine,Loy,Tensorflow}.
 Since the elements of the DFT matrix lie on the complex unit circle, each real-valued analysis frame will be moved into complex space.
@@
 This means that when constructing the spectrogram, we will rarely see significant energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
-To condense the size of the matrix, we select only the frequency bins (rows) that correspond to energies between $0$ Hz and $6000$ Hz.
+To condense the size of the matrix, we select only the frequency bins (rows) that correspond to energies between $0$ Hz and $12,000$ Hz.
 This makes the input array smaller, and eliminates redundant and non-useful information.
@@
 \paragraph*{}Each spectrogram is now $N' \times k$ and effectively encodes the energy distribution of the waveform as a function of both time and frequency.
-The spectrogram makes up each sample in the first design matrix $X_1$, Eq.(\ref{eqn-ShapeX1}) used in this model.
+The spectrogram makes up each sample in the first design matrix $X_1$, Eq.(\ref{eqn-X1Shape}) used in this model.
 For this classifier, we have chosen $N' = 558$ and $k = 256$.
@@
 \end{equation}
-Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}). This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
+Which is consistent with the shape of the $X_1$ matrix outlined in Eq. (\ref{eqn-X1Shape}). This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
 
@@
 The number of samples $M$ is chosen to correspond the number of sample needed to make the $N \times k$ spectrogram matrix.
-This way,t he spectrogram and time-series features are representative of the same time interval in the file sample.
+This way, the spectrogram and time-series features are representative of the same time interval in the file sample.
 Time space is indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
@@
 \paragraph*{}One way to mitigate this is to group analysis frames together and compute the TDE of a collection of frames.
-This way, small most waveforms will produce an identical set of features to a time-delayed version of itself.
-By choosing a sufficiently large number of TDE values, we can also generate n approximation of than amplitude envelope of the time-series waveform.
+This way,  almost all waveforms will produce an identical set of features to a short time-delayed version of itself.
+By choosing a sufficiently large number of TDE values, we can also generate an approximation of than amplitude envelope of the time-series waveform.
 This comes at a higher computational cost, and a previously mentioned higher dimensional feature vector
@@
 \paragraph*{}We adapt this TDE to \textbf{compute the time domain envelope over $5$ non-overlapping analysis frames}.
-Since the maximum amplitude of each waveform array has been normalized to $\pm 1$, the TDE represents a consistent measurement of energy in each waveform subset.
-\cite{Liu}.
+Since the maximum amplitude of each waveform array has been normalized to $\pm 1$, the TDE represents a consistent measurement of energy in each waveform subset \cite{Liu}.
 The TDE is computed as the RMS-Energy of the waveform, $s$ and the $j$-th TDE value is given by \cite{Olson,Serizel}:
@@
 Where $Q$ gives the number of sample sin each analysis frame (number of sample sin waveform divided by number of frames), and $n$ gives the index where the $j$-th frame begins.
-
-\paragraph*{}These uniformly size analysis frames let us create an naive envelope of the waveform, but will allow it to generalize between classes.
-For example, this allows for a crude approximation of the energy in the attack, decay, sustain, and release energies in a waveform \cite{Virtanen,Olson}.
+We provide a graphic representation of how the TDE compares to the amplitude of sections of a waveform in Fig.
+(\ref{fig-ExampleTDE}).
+
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{center}
+	\includegraphics[width=1.0\linewidth]{../FiguresSpectrogram/GUITAR-B2_TDE}
+	\caption{Guitar - B2}
+	\end{center}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{center}
+	\includegraphics[width=1.0\linewidth]{../FiguresSpectrogram/Tuba-A2_TDE}
+	\caption{Tuba - A2}
+	\end{center}
+	\end{subfigure}
+	\caption{TDE Envelope values for musical instruments}
+	\label{fig-ExampleTDE}
+\end{figure}
+
+\paragraph*{}The uniformly sized analysis frames let us create an naive envelope of the waveform, but will allow it to generalize between classes.
+For example, this allows for a crude approximation of the energy in the attack, decay, sustain, and release portion of the signal \cite{Virtanen,Olson}.
 For instruments with heavier attacks, we expect the TDE in the $1$-st frame to be comparably large, see Fig.
@@
 \begin{center}
-%\textcolor{red}{PLOT OF ZXR FEATURES HERE}
 \includegraphics[scale=0.3]{../FiguresFeatures/ZXR}
@@
 
-\paragraph*{}TCM condenses the idea of the amplitude envelope into a single value.
+\paragraph*{}TCM condenses the idea of the amplitude envelope into a single scalar value.
 It allows for the quick measurement of where in the time most of the energy of the signal lies.
@@
 Instruments with plucked strings, but longer release times such as mandolins and guitars should have similarly low values.
+See Fig.
+(\ref{fig-ExampleTCM}) for examples.
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{center}
+	\includegraphics[width=1.0\linewidth]{../FiguresSpectrogram/Vibraphone-sustain-A5-R_TCM}
+	\caption{Vibraphone - A5}
+	\end{center}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\begin{center}
+	\includegraphics[width=1.0\linewidth]{../FiguresSpectrogram/CELLO-F4_TCM}
+	\caption{Cello - F4}
+	\end{center}
+	\end{subfigure}
+	\caption{TCM values for musical instruments}
+	\label{fig-ExampleTCM}
+\end{figure}
 Instruments in the woodwind and brass family generally have longer sustain and release times, giving them a slightly higher center of mass.
@@
 
-\paragraph*{}\textcolor{red}{I need to complete my discussion of ACC's here!}
+\paragraph*{}Physically, the numerator of the ACC representing computing the dot product of the signal, $s[i]$ with a time-delayed version of itself $s[i+k]$, and  the denominator provides a normalization for the value.
+Dotting the signal and the time delay allows us to introduce a synthetic phase shift and compare the resulting relationship.
+If we chose $k$ to be equal, or similar to the number of samples that make-up a period or half-period of the waveform, then $s[i] \approx s[i+k]$ and then $\text{ACC}_k \rightarrow 1$.
+Alternatively, for many other values of $k$, frequent multiplication and summation of samples that are approximately zero result in $\text{ACC}_k << 1$.
+This make auto-correlation coefficients extremely useful for detecting periodicity in time-space \cite{Serizel}.
 
@@
 \begin{center}
-%\textcolor{red}{PLOT OF ACC FEATURES HERE}
 
@@
 \end{center}
-\caption{A comparison of the the first four auto correlation coefficents in each class using a box-and-whisker plot}
+\caption{A comparison of the the first four auto correlation coefficients in each class using a box-and-whisker plot}
 \label{fig-FeatureACC}
@@
 \begin{center}
-\textcolor{red}{Figure of a few Mel Filter Banks goes here}
-\end{center}
-\caption{Mel Filter Banks shown in frequency space with units of (a) Mels and (b)Hertz}
+\includegraphics[scale=0.28]{../FiguresSpectrogram/MelFilterBanks}
+\end{center}
+\caption{Mel Filter Banks shown in frequency space with units of Hertz}
 \label{fig-MelFilterBanks}
@@
 \paragraph*{}Physically, MFCC's are a transform of a transform.
-This allows us to investigate the periodicity of the frequency spectrum, which highlights phenomena such as overtones or echoes in the signal\cite{Virtanen}.
+This allows us to investigate the periodicity of the frequency spectrum, which highlights phenomena such as overtones or echoes in the signal \cite{Virtanen}.
 Cepstrum coefficients are commonly used to speech identification and are very prolific in sound recognition tasks \cite{Serizel,Sahidullah,Liu}.
-
-\paragraph*{}As the frequency bin index increases, the width of the bin in frequency space increases. \textcolor{red}{Finish this! What does a MFCC tell us with words!}
+We show a feature-space representation of MFCC's for a selection of coefficients in Fig.
+(\ref{fig-FeatureMFCCs}).
 
@@
 \begin{center}
-%\textcolor{red}{PLOT OF MFCC FEATURES HERE}
 

### 2020-12-06 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
New Figures, Major Thesis Updates

@@
 This process is detailed further in sec.
-(\ref{sec-Architecture}).
+(\ref{sec-NetworkArchitecture}).
 
@@
 
+\subsubsection{Accuracy Score}
+
+\paragraph*{}Accuracy score, while not commonly used is the most intuitive of all of the performance metrics.
+It is the ratio of correct predictions of he total number of predictions.
+While immediately useful for equally sampled binary classification problems, it looses meaning as the number of classes increases, and epecially if the number of samples per class is not consistent \cite{Geron}.
+
+\paragraph*{}For example, we could develop a model that uses a few predictors from every human currently alive and determine which of them has walked on the moon.
+There are roughly 7 billion humans alive, four of which have been on out moon.
+Simply guess \textit{no} for every human, our model would have more than a $99.9999\%$ accuracy.
+However, we would argue that this model does not perform well seeing as it has a $0 \%$ recall score, and and a $0 \%$ precision score.
+
+\paragraph*{}Accuracy score of model is defined:
+\begin{equation}
+\label{eqn-BinaryAccuracy}
+\text{Accuracy} = \frac{TP + FN}{TP + FP + FN + FP}
+\end{equation}
+
+\paragraph*{}For a multi-class problem, present accuracy over each individual class, called \textit{micro-accuracy} \cite{James}.
+The accuracy for a class $j$ is the correct predictions related to the class divided by the total predictions and total counts of the class.
+We express this mathematically by using sums over each row, each column, and the main diagonal as such:
+\begin{equation}
+\label{eqn-Accuracy}
+\text{Accuracy}_j = \frac{\sum_{i}C_{i,i}}{\sum_{i}C_{i,i} + \sum_{i \neq j}C_{i,j} + \sum_{i \neq j}C_{j,i}}
+\end{equation}
+Where all sum indexes goes from $0$ to $k-1$.
+
+\paragraph*{}We can also present \textit{global accuracy} or \textit{macro accuracy} by computing the acurracy over the full confusion matrix.
+This would then by the ratio of all correct predictions (the main diagonal) to all predictions (the sum of the matrix).
+We can express this as:
+\begin{equation}
+\text{Accuracy} = \frac{\sum_{i}C_{i,i}}{\sum_{i}\sum_{j}C_{i,j}}
+\end{equation}
+
+% ================================
+
 \subsubsection{Precision Score}
@@
 In case cases, it is useful to use the $F1$ score to find the set of hyper-parameters that allow for the classifier to produce both the highest possible precision \textit{and} recall score.
-
-% ================================
-
-\subsubsection{Accuracy Score}
-
-\paragraph*{}Accuracy score, while not commonly used is the most intuitive of all of the performance metrics.
-It is the ratio of correct predictions of he total number of predictions.
-While immediately useful for equally sampled binary classification problems, it looses meaning as the number of classes increases, and epecially if the number of samples per class is not consistent \cite{Geron}.
-
-\paragraph*{}For example, we could develop a model that uses a few predictors from every human currently alive and determine which of them has walked on the moon.
-There are roughly 7 billion humans alive, four of which have been on out moon.
-Simply guess \textit{no} for every human, our model would have more than a $99.9999\%$ accuracy.
-However, we would argue that this model does not perform well seeing as it has a $0 \%$ recall score, and and a $0 \%$ precision score.
-
-\paragraph*{}Accuracy score of model is defined:
-\begin{equation}
-\label{eqn-BinaryAccuracy}
-\text{Accuracy} = \frac{TP + FN}{TP + FP + FN + FP}
-\end{equation}
-
-\paragraph*{}For a multi-class problem, present accuracy over each individual class, called \textit{micro-accuracy} \cite{James}.
-The accuracy for a class $j$ is the correct predictions related to the class divided by the total predictions and total counts of the class.
-We express this mathematically by using sums over each row, each column, and the main diagonal as such:
-\begin{equation}
-\label{eqn-Accuracy}
-\text{Accuracy}_j = \frac{\sum_{i}C_{i,i}}{\sum_{i}C_{i,i} + \sum_{i \neq j}C_{i,j} + \sum_{i \neq j}C_{j,i}}
-\end{equation}
-Where all sum indexes goes from $0$ to $k-1$.
-
-\paragraph*{}We can also present \textit{global accuracy} or \textit{macro accuracy} by computing the acurracy over the full confusion matrix.
-This would then by the ratio of all correct predictions (the main diagonal) to all predictions (the sum of the matrix).
-We can express this as:
-\begin{equation}
-\text{Accuracy} = \frac{\sum_{i}C_{i,i}}{\sum_{i}\sum_{j}C_{i,j}}
-\end{equation}
 
@@
 \end{center}
-\caption{The precision score (a) and recall score (b) increases with each training step}
+\caption{The precision score (a) and recall score (b) generally increase with each training step}
 \label{fig-PrecisionRecallScores}
 \end{figure}
-
-% ================================================================
-
-\subsection{Boosted Aggregation}
-\label{subsec-Bagging}
-
-\paragraph*{}Many learning models such as neural networks, or decision trees suffer from \textit{high variance} \cite{James}.
-This means that randomly splitting a full dataset into halves and fitting two different model to each half has the potential to produce wildly different fit parameters.
-In the case of neural networks, high variance can be amplified by the nature of the randomization in multidimensional optimizer \cite{Geron}.
-To mitigate this effect, we can employ a variant of the \textit{bagging} algorithm.
-Bagging uses an average, or weighted average, of parameters in multiple models that have been trained on overlapping data sets.
-
-\paragraph*{}Consider if we have $K$ models, all trained on overlapping training/testing data sets:
-\begin{equation}
-\text{Models} = \Big\{ F^*_{0} , F^*_{1} , F^*_{2} , ... , F^*_{K-2} , F^*_{K-1} \Big\}
-\end{equation}
-Each model contains a corresponding set of parameters, $\Theta^{i}$, $i \in [0,K-1]$.
-We could then aggregate the parameters according to a weighted average to create a new set of paramaters, $\Theta '$ which can be used to construct a new model, $F'$.
-
-\paragraph*{}This algorithm is often used after $K$-Folds Cross validation, as outlined in in subsec.
-(\ref{subsec-XValidation}).
-This grants the $K$ models and corresponding parameters that could be used in the bagging technique \cite{James}.
-\textcolor{blue}{This is very not finished yet!}
 
@@
 
-\paragraph*{}To formally produce classification predictions on the chaotic synthesizer wave forms, we must use all of the principles outlined in the previous sections.
+\paragraph*{}To formally produce classification predictions on the chaotic synthesizer waveforms, we must use all of the neural network, physics, and statistical principles outlined in the previous sections.
 Using the described features in sec.
@@
 (\ref{subsec-Architecture}), We run a $K=10$ folds cross validation program as in Alg.(\ref{alg-CrossValidation}).
-For each of the $10$ models, we produce a standard confusion matrix, an compute the (i) accuracy score, (ii) precision score, (iii) recall score, and (iv) F1 score.
-For each of the $37$ classes, we compute the arithmetic mean of the metrics across the $10$ folds.
-We show the results of this in Figs.
-(\ref{fig-HighWindsScores}), (\ref{fig-LowWindsScores}), (\ref{fig-BrassScores})
-
-\paragraph*{}Additionally, we report the average of each four metrics across all classes for each of the $10$ splits in Fig.
-(\ref{fig-ValidationTable}).
-We also present a more condensed version of the data by showing the average, minimum, maximum, and variance of each score in Fig.
-(\ref{fig-ValidationStats}).
-Each value is on the interval $[0,1]$, with higher values being more favorable.
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\textbf{Split Index} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} \\ \hline
-$0$ & 0.992969341 & 0.849762613	& 0.853483643 & 0.838007935 \\ \hline
-$1$ & 0.993086645 & 0.857063114	& 0.865737308 & 0.854069688 \\ \hline
-$2$ & 0.994175444 & 0.858936065	& 0.854231756 & 0.851319866 \\ \hline
-$3$ & 0.993883291 & 0.887070101	& 0.901606142 & 0.882074022 \\ \hline
-$4$ & 0.992941956 & 0.884115922	& 0.902609597 & 0.884775112 \\ \hline
-$5$ & 0.992941956 & 0.884115922	& 0.902609597 & 0.884775112 \\ \hline
-$6$ & 0.994315799 & 0.856425689	& 0.842680234 & 0.834139910 \\ \hline
-$7$ & 0.993057475 & 0.869049669	& 0.867171387 & 0.856152544 \\ \hline
-$8$ & 0.992979711 & 0.843322939	& 0.866599329 & 0.846637817 \\ \hline
-$9$ & 0.992799981 & 0.842635691	& 0.877821096 & 0.832496007 \\ \hline
-\end{tabular}
-\end{center}
-\caption{Metrics averaged over all classes for $K=10$ validation splits}
-\label{fig-ValidationTable}
-\end{figure}
-
-\begin{figure}[H]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\textbf{Measure} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} & \textbf{F1} \\ \hline
-\textbf{Average} & 0.993385794 & 0.860133646 & 0.872055273 & 0.853799365 \\ \hline
-\textbf{Minimum} & 0.992799981 & 0.842635691 & 0.842680234 & 0.832496007 \\ \hline
-\textbf{Maximum} & 0.994315799 & 0.887070101 & 0.902609597 & 0.884775112 \\ \hline
-\textbf{Variance}& 2.88066E-07 & 0.000215270 & 0.000373321 & 0.000293214 \\ \hline
-\end{tabular}
-\end{center}
-\caption{Metric statisitcs over all classes  and all validation splits}
-\label{fig-ValidationStats}
-\end{figure}
+For each of the $10$ models, we produce a standard confusion matrix, and compute the (i) accuracy score, (ii) precision score, (iii) recall score, and (iv) F1 score.
+In Fig.
+(\ref{fig-MultimodalXval}) we show how the metrics compare in each the $10$ models by averaging the scores across the $37$ classes.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[scale=0.3]{../FiguresMetrics/AvgXval-Multimodal}
+\caption{Performance metrics across $10$ models and $37$ classes}
+\label{fig-MultimodalXval}
+\end{center}
+\end{figure}
+Additionally, we present the average standard confusion matrix, and the hits-weighted confusion matrix in Fig. (\ref{fig-MultimodalConfs}).
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresMetrics/XValAlphaCLF_Avg_Standard_Confusion}
+	\caption{Standard Confusion Matrix}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresMetrics/XValAlphaCLF_Avg_Hits_Weighted_Confusion}
+	\caption{Occurance Weighted Confusion Matrix}
+	\end{subfigure}
+
+	\caption{}
+	\label{fig-MultimodalConfs}
+\end{figure}
+
+\paragraph*{}We show the metric values of all splits to show the consistency in performance across all subsets.
+Notice how the models each perform reasonably well (precision and recall score consistently above 80\%).
+This indicates that for this data set, architecture, and feature selection, our model can performance reasonably and generalize appropriately.
+This step is critical in ensuring that there are no major out-liers in the classification results, and that any set of initial conditions can still allow the model to reach an acceptable set of parameters and decision boundaries.
+The results of cross validation indicate a strong classier that can be implemented to make predictions on other waveforms.
+
+% ================================================================
+
+\subsection{Comparing Results between Architectures}
+
+\paragraph*{}In addition to considering our multimodal network architecture performance, we have also run the identical $K = 10$ folds cross validation program on two uni-modal variants of the model.
+The first variant contains only the Convolutional branch of the network in Fig.
+(\ref{fig-NetworkArchitecture}), meaning that we feed the activations from the last dense layer in the left column directly to the output layer.
+Similarly, the second variant contains only the perceptron branch of the network in Fig.
+(\ref{fig-NetworkArchitecture}), meaning that we feed the activations from the last dense later in the right column directly to the output layer.
+For consistency, the same full data set (around $18,000$ samples) was using in the cross validation program.
+Comparing the performance of the each model gives us an insight as to the predictive contribution of each input branch
+
+\begin{figure}[H]
+
+	\begin{subfigure}[b]{0.9\textwidth}
+	\centering
+	\includegraphics[scale=0.3]{../FiguresMetrics/AvgXval-Convolution}
+	\caption{Unimodal Architecture, See left side of Fig. (\ref{fig-NetworkArchitecture})}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.9\textwidth}
+	\centering
+	\includegraphics[scale=0.3]{../FiguresMetrics/AvgXval-Perceptron}
+	\caption{Unimodal Architecture, See right side of Fig. (\ref{fig-NetworkArchitecture})}
+	\end{subfigure}
+
+	\caption{}
+	\label{fig-UnimodalXVal}
+\end{figure}
+
+\paragraph*{}Compare these unimodal model performances with that of the multimodal network results in Fig.
+(\ref{fig-MultimodalXval}).
+Notice how the multimodal network consistently produce superior classification results.
+Similarly, we present the standard and weighted confusion matrices for both unimodal networks.
+Compare the results with Fig.
+(\ref{fig-MultimodalConfs}) and see how the confusion matrix indicates a stronger classifier.
+
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresMetrics/XValGammaCNN_Avg_Standard_Confusion}
+	\caption{Standard Confusion Matrix for Convolution Branch}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresMetrics/XValGammaCNN_Avg_Hits_Weighted_Confusion}
+	\caption{Occurance Weighted Confusion Matrix for Convolution Branch}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresMetrics/XValBetaMLP_Avg_Standard_Confusion}
+	\caption{Standard Confusion Matrix for Perceptron Branch}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresMetrics/XValBetaMLP_Avg_Hits_Weighted_Confusion}
+	\caption{Occurance Weighted Confusion Matrix for Perceptron Branch}
+	\end{subfigure}	
+	\label{fig-MultimodalConfs}
+\end{figure}
+
+% ================================================================
+
+\subsection{Comparing Classification Scores within Each Class}
+
+\paragraph*{}Below we present the average accuracy, precision, recall and F1 score for each class, as averaged across $10$-folds cross validation, comparing the three architectures.
+These plots represent a more "micro" representation of classification by showing the response and scores within each specific class.
 
@@
 \end{figure}
-
-\paragraph*{}With cross validation completed and the results
-
-% ================================================================
-
-\subsection{•}
 

### 2020-12-06 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisMAIN.py

@@ -22,7 +22,7 @@ if __name__ == '__main__':
 
     # Establish local Directory Paths
     parent = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis"
-    modelName = "XValAlphaCLF"
+    modelName = "XValGammaCNN"
     dataPath = os.path.join(parent,"SignalClassifier-CrossValidation",modelName+"-Output-Data")
     metricsPath = os.path.join(parent,"Thesis\\FiguresMetrics")    
     figuresPath = os.path.join(parent,"Thesis\\FiguresClasses")    
@@ -33,15 +33,15 @@ if __name__ == '__main__':
     encode,decode = Program.MakeDecodeDictionary()
 
     Program.__Call__(metricsPath)
-    Program.ExportMetricsBySplit(metricsPath)
-    Program.ExportMetricsByClass(metricsPath)
+    #Program.ExportMetricsBySplit(metricsPath)
+    #Program.ExportMetricsByClass(metricsPath)
 
 
     # Prepare Figures
-    classIntegerNames = [x for x in range(n_classes)]
-    classStringNames = [decode[x] for x in range(n_classes)]
+    #classIntegerNames = [x for x in range(n_classes)]
+    #classStringNames = [decode[x] for x in range(n_classes)]
 
-    Figures = Figs.MetricFigures(classIntegerNames,classStringNames,Program.metricsArray)
-    Figures.__Call__(figuresPath)
+    #Figures = Figs.MetricFigures(classIntegerNames,classStringNames,Program.metricsArray)
+    #Figures.__Call__(figuresPath)
 
     print("=)")

### 2020-12-06 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisUtilities.py

@@ -142,9 +142,9 @@ class AnalyzeModels:
         avgScrMatName =  self.modelName + " Avg Score Weighted Confusion"
         
 
-        ExportAndPlot.ExportConfusion(avgStandardConfMat,avgStdMatName,exptPath)
-        ExportAndPlot.ExportConfusion(avgHitsWeightedConfMat,avgHitMatName,exptPath)
-        ExportAndPlot.ExportConfusion(avgScrsWeightedConfMat,avgScrMatName,exptPath)
+        #ExportAndPlot.ExportConfusion(avgStandardConfMat,avgStdMatName,exptPath)
+        #ExportAndPlot.ExportConfusion(avgHitsWeightedConfMat,avgHitMatName,exptPath)
+        #ExportAndPlot.ExportConfusion(avgScrsWeightedConfMat,avgScrMatName,exptPath)
 
         os.chdir(exptPath)
         ExportAndPlot.PlotConfusion(avgStandardConfMat,self.n_classes,avgStdMatName,False)
@@ -265,10 +265,10 @@ class ExportAndPlot :
     def PlotConfusion(X,n_classes,title="",show=True,save=True):
         """ Visualize Confusion with ColorMap """
         plt.figure(figsize=(16,16))
-        plt.title(title,fontsize=20,weight='bold')
+        #plt.title(title,fontsize=20,weight='bold')
         plt.imshow(X,cmap=plt.cm.jet)
-        plt.xticks(np.arange(0,n_classes,1),weight='bold')
-        plt.yticks(np.arange(0,n_classes,1),weight='bold')
+        plt.xticks(np.arange(0,n_classes,1),size=15,weight='bold')
+        plt.yticks(np.arange(0,n_classes,1),size=15,weight='bold')
         plt.tight_layout()
         if save == True:
             plt.savefig(title.replace(" ","_")+".png")

### 2020-12-07 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
New Figures, Thesis Updates

@@
 (\ref{subsec-NerualNetworkIntro}) and (\ref{subsec-NetworkStructure}), we introduce the nature and structure of a neural network and how it can use used in part to solve this problem.
+We discuss it's inspiration from a biological brain, and show how different layers of the neural network compare to functions or processes in the brain.
 
@@
 University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \textcolor{blue}{Citations!}.
-These contain short segments of musical instruments performing a single note or a collection of notes in succession.
-Each sound file is labeled according to the instrument that is producing that sound.
+These files contain short segments of musical instruments performing a single note, and is labeled according to the instrument that produced the sound.
+The files and labels make up the core of the data set that we use to train the model.
 
@@
 This ensures that all data will have a consistent format when features are extracted.
-This stage is detailed in sec.(\ref{subsubsec-Preprocessing}).
+This stage is detailed in sec.
+(\ref{subsubsec-Preprocessing}).
 
@@
 
-\paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of classification features.
+\paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of classification features which represent the input given to the neural network.
 These are properties of wave forms that can be represented by a numerical value or several numerical values and are used as the primary tool in classification.
@@
 
-\paragraph*{}With the appropriate set of features designed, and the number of output determined, we can organize the structure of the neural network function.
+\paragraph*{}With the appropriate set of features designed, and the number of outputs determined, we can organize the structure of the neural network function.
+The shape of the network defines the hypothesis space, and a subset of the possible solutions that the trained model could arrive at.
 We construct a multimodal neural network, explored in sec.
-(\ref{sec-Architecture}), that processes two input arrays derived from the same audio sample.
-This network is designed to handle and process each respective input independently, and concatenate the results to produce a single output.
+(\ref{subsec-Architecture}), that processes two distinct entry points derived from the same audio sample.
+This network is designed to handle and process each respective input independently, and concatenate the results to produce a single outputted prediction.
 
@@
 \paragraph*{}We divide the raw data set up into a training and testing sets.
-We employ cross-validation and compute the results of performance metrics to ensure that out model is making reliable predictions, and generalize appropriately.
+We employ a resampling method called cross-validation and compute the results of various performance metrics to ensure that our model is making reliable predictions, and can generalize appropriately.
 In this stage, we also choose the value of hyper-parameters, activation functions and layer widths to best compliment the chosen features.
 This process is repeated and expanded upon until we have produced a model with a sufficient performance.
+We explore the explore this is sec.
+(\ref{sec-PerfEval}).
 
@@
 If further corrections are needed, we revert and re-deign the features, architecture, or hyper-parameters as needed.
+We explore thisas part of our conclusions in sec.
+(\ref{sec-Conclusion}).
 
@@
 
-\paragraph*{}As the name implies, Early neural networks were inspired from from the human brain.
+\paragraph*{}As the name implies, early neural networks were inspired from from the human brain.
 Former YouTube video classification team lead, and current machine learning consultant, Aurelien Geron writes about the relationship between biological brains and mathematical neural networks \cite{Geron}:
@@
 The exact nature of this operation can be very different depending on the layer type or where it sits within the network.
-The output of one layer is passed forward and use as the input for the next layer.
+The output of one layer is passed forward and used as the input for the next layer.
 It is this process of transforming inputs successively in a particular order until an output is attained that makes up the core functionality of a neural network \cite{Geron,Loy}.
@@
 A network model that contains $L$ unique layers is said to be an $L$-Layer Neural Network, with each layer indexed by a superscipt, $(0)$ through $(L-1)$.
-Layer $(0)$ is said to be the \textit{input layer} and layer $L-1$ is said to be the \textit{output layer} \cite{Geron,Loy}.
+Layer $(0)$ is said to be the \textit{input layer} and layer $(L-1)$ is said to be the \textit{output layer} \cite{Geron,Loy}.
 
@@
 (\ref{eqn-altLayerFunction}).
-Each call method is presumed to be composed of two steps: a (i) linear transformation, and a (ii) non-linear activation function.
-See sec.
-(\ref{subsec-Layers}) for more detials.
 Additionally, each node contains a pointer "\textit{next}" which gives the next layer in the network chain.
@@
 \item Return the network's output, which are the output activation of the final layer \\
-\RETURN $x^{(L-1}$
+\RETURN $x^{(L-1)}$
 \end{algorithmic}
@@
 
-\paragraph*{}As stated previously, a neural network is composed of a series of functions that are called in succession to transform features (an input) into a predictions (an output).
+\paragraph*{}As stated previously, a neural network is composed of a series of functions that are called in succession to transform features (an input) into predictions (an output).
 As shown in Eq.
@@
 \REQUIRE $W \leftarrow$ a $(n \times m)$ matrix of weights
-\REQUIRE $b \leftarrow$ a $(m \times 1)$ vector of bias values
-
-Evaluate linear activation values by computing the standard matrix-vector produce of $W^{(l)}$ and $x^{(l-1)}$:\\
+\REQUIRE $b \leftarrow$ a $(n \times 1)$ vector of bias values
+
+Evaluate linear activation values by computing the standard matrix-vector product of $W^{(l)}$ and $x^{(l-1)}$, and adding the bias neuron value:\\
 $z[i] \leftarrow b[i] + \sum_{j=0}^{n-1} W[i,j] x^{(l-1)}[j]$ \\
 Evaluate output activation values by applying the activation function to each element in the linear activation column vector $z$:\\
-$x^{(l)}[i] \leftarrow \sigma^{(l)}\big[ z[i] \big]$ \\
+$x^{(l)}[i] \leftarrow \sigma^{(l)}\big( z[i] \big)$ \\
 
@@
 \paragraph*{}Convolution layers emerged from studying the brain's visual cortex, and have been used from image recognition related tasks for around 40 years.
-\cite{Geron,Loy}).
-This layer get's it's name from it's implementation of the mathematical \textit{convolution} function.
+\cite{Geron,Loy}.
+The layer function get's it's name from it's implementation of the mathematical \textit{convolution} operation.
 The 2D discrete-convolution of function or 2D array $A[i,j]$ and $B[i,j]$ is given by \cite{Goodfellow}:
@@
 
-\paragraph*{}In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(N \times M)}$, the convolutions filters "step" through the input data and repeatedly compute the element-wise product of each $m \times n$ weighting kernel, and the local activations of the $x^{(l-1)}$ array.
+\paragraph*{}In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(M \times N)}$, the convolutions filters "step" through the input data and repeatedly compute the element-wise product of each $m \times n$ weighting kernel, and the local activations of the $x^{(l-1)}$ array.
 The step size in each of the 2-dimension is known as the \textit{stride}.
@@
 \begin{equation}
-f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(N \times M)} \rightarrow
-x^{(l)} \in \mathbb{R}^{([N-n+1] \times [M-m+1] \times K)}
-\end{equation}
-As an example, consider a single filter map over input $x \in \mathbb{R}^{(4 \times 3)}$ and filter map $W \in \mathbb{R}^{(2 \times 2)}$ as shown in Fig. (\ref{fig-2DConvExample}):
+f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(M \times N)} \rightarrow
+x^{(l)} \in \mathbb{R}^{([M-m+1] \times [N-n+1] \times K)}
+\end{equation}
+As an example, consider a single filter map over input $x \in \mathbb{R}^{(3 \times 4)}$ and filter map $W \in \mathbb{R}^{(2 \times 2)}$ as shown in Fig. (\ref{fig-2DConvExample}):
 \begin{figure}[H]
@@
 	\includegraphics[scale=0.6]{../figures/2DConvExample(a)}
-	\caption{Input Activations}
+	\caption{Input Activations, $x^{(l-1)}$}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.6]{../figures/2DConvExample(b)}
-	\caption{Convolution Filter}
+	\caption{Convolution Filter, $W^{(l)}_k$}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.6]{../figures/2DConvExample(c)}
-	\caption{Convolution Result}
+	\caption{Convolution Result, $x^{(l)}_k$}
 	\end{subfigure}
@@
 \label{eqn-ConvFeedForward}
-x^{(l)}_k(i,j) = \sigma^{(l)}\bigg[ \Big( \sum_{u=0}^{m-1} \sum_{v=0}^{n-1} W^{(l)}(i,j) x^{(l-1)}_k(i - u,j - v) \Big) + b^{(l)}_k \bigg]
+x^{(l)}_k(i,j) = \sigma^{(l)}\bigg[ \Big( \sum_{u=0}^{m-1} \sum_{v=0}^{n-1} W^{(l)}_k(i,j) x^{(l-1)}_k(i - u,j - v) \Big) + b^{(l)}_k \bigg]
 \end{equation}
@@
 \begin{algorithm}[H]
-\caption{Typical "Call" method for a 2-Dimensional Convolutional layer in a neural network that uses $K$ filters, of $n \times m$ kernels, with an assumed stride size of $1 \times 1$.
+\caption{Typical "Call" method for a 2-Dimensional Convolutional layer in a neural network that uses $K$ filters, of $m \times n$ kernels, with an assumed stride size of $1 \times 1$.
 This example shows the computation over a single input $x^{(l-1)}$ but a practical implementation should include mini-batches of samples.}
@@
 \begin{algorithmic}
-\REQUIRE $x^{(l-1)} \leftarrow$ Input activations shaped into $(N \times M)$ matrix
+\REQUIRE $x^{(l-1)} \leftarrow$ Input activations shaped into $(M \times N)$ matrix
 \REQUIRE $K \leftarrow$ The number of filters (feature maps) to be used.
 \REQUIRE $\sigma \leftarrow$ Activation function for this layer
-\REQUIRE $W_{k} \leftarrow$ a $(n \times m)$ matrix of weights 
-(called a weighting kernel in this case), $k \in [0,...,k-1]$
-\REQUIRE $b_{k} \leftarrow$ a $(m \times 1)$ vector of bias values, $k \in [0,...,k-1]$ \\
+\REQUIRE $W \leftarrow$ array of weight kernels containing $W_k, k \in [0,1,...,K-1]$ each shaped $m \times n$ \\
+\REQUIRE $b \leftarrow$ a $(1 \times K)$ vector of bias values, $b_k, k \in [0,...,k-1]$ \\
 
@@
 The purpose of this arrangement is to reduce the number of weights, thereby dropping the complexity of the model and ensuring only features with large activation values are preserved \cite{Geron,Loy,Goodfellow}.
+This layer "non-trainable" because it does no use any weights or transformations, only a fixed procedure.
+Below, we detail what the "Call" method for a 2D maximum pooling layer might look like.
+
+\begin{algorithm}[H]
+\caption{Typical "Call" method for a 2-Dimensional Maximum Pooling layer in a neural network.
+We assume 2D input, but a practical implementation may include the need to loop over a high dimensional structure.
+For simplicity, we assume a stride size of $1 \times 1$.
+This example shows the computation over a single input $x^{(l-1)}$ but a practical implementation should include mini-batches of samples.}
+\label{alg-CallPool2D}
+
+\begin{algorithmic}
+\REQUIRE $x^{(l-1)} \leftarrow$ Input activations shaped into $(M \times N)$ matrix
+\REQUIRE $m \times n \leftarrow$ Pool height and width
+\REQUIRE $P \leftarrow$ A temporary pool array of shape $m \times n $ to hold local activationbs
+
+\FOR {$i \in [0,1,...,M-2,M-1$}
+	\FOR {$j \in [0,1,...,N-2,N-1$}
+		\item Collect local activations in $P$, zero pad if necessary
+		\item $P = x^{(l-1)}[i:i+m,j:j+n]$
+		\item Find maximum valie in $P$, and add to output
+		\item $x^{(l)}[i,j] = \max\big( P \big)$
+	\ENDFOR
+\ENDFOR
+
+Store the activation array for back-propagation, and return it
+\RETURN $x^{(l)}$
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 Those values are then flattened to 1 dimensions, which can then be passed into dense layers for further processing.
+This layer also is "non-trainable" because it does no use any weights or transformations, only a fixed procedure.
 
@@
 This process is detailed further in sec.
-(\ref{sec-NetworkArchitecture}).
+(\ref{subsec-Architecture}).
+This layer also "non-trainable" because it does no use any weights or transformations, only a fixed procedure.
 
@@
 As discussed in sec.
-(\ref{sec-Training}) a layer function, $f^{(l)}$ is generally composed of a linear transformation, as in Eq.
+(\ref{subsec-Training}) a layer function, $f^{(l)}$ is generally composed of a linear transformation, as in Eq.
 (\ref{eqn-LinearTransform}), and then an element-wise activation function as in Eq.
@@
 Each node of the graph is a layer that represents a mathematical function which takes the activation from the previous layer $x^{(l-1)}$ and transforms them into the activations of the current layer, as in Eq.
-(\ref{eqn-LayerFunction}).
-Additionally, we recall that each layer itself is made up two steps which produce linear activations such as in Eq.
+(\ref{eqn-altLayerFunction}).
+Additionally, we recall that each layer with trainable parameters is made up two steps which produce linear activations such as in Eq.
 (\ref{eqn-LinearTransform}) and non-linear activations, as in Eq.
@@
 
-\paragraph*{}An optimizer is the algorithm or procedure that is used by a machine learning model to achieve the lowest possible value of the cost function over a data set \cite{Geron}.
-Some models such as minimizing a \textit{mean-squared error} for linear regression model can be solve analytically, while high dimensional neural networks, such as the one used in this project, outlined in sec.
-(\ref{subsec-Architecture}), cannot be solved symbolically.
-Thus, we then employ an iterative gradient method, much like the one in Eq.
+\paragraph*{}An optimizer is the algorithm or procedure that is used by a machine learning model to perform the optimization task and seeks to achieve the lowest possible value of the cost function over a data set \cite{Geron}.
+Regression models my often used a \textit{mean-squared error} cost function which can often be solved analytically, while high dimensional neural networks, such as the one used in this project, outlined in sec.
+(\ref{subsec-Architecture}), can only up updated iterativly \cite{Goodfellow,James,Loy}.
+We employ an iterative gradient-based method, much like the one in Eq.
 (\ref{eqn-GradientLearning}).
-These standard gradient-based learning algorithms are cumbersome and often prone errors such as vanishing or exploding gradients.
-\cite{Geron,Goodfellow,Loy}.
+These standard gradient-based learning algorithms are cumbersome and often prone errors such as vanishing or exploding gradients \cite{Geron,Goodfellow,Loy}.
 To combat this, model must often implement an algorithm that is more stable, and robust in it's ability to drive the cost function to a successively lower value.
@@
 \paragraph*{}For this project, we employ an \textit{Adaptive-Moments} optimization algorithm, also called \textit{ADAM} for short.
-It is a powerful optimizer with uses adaptive learning rate and momentum parameter.
+It is a powerful optimizer that uses an adaptive learning rate and momentum parameter.
 ADAM tracks an exponentially decaying average of past gradients, $s^{(i)}$, and an exponentially decaying average of past squared gradients, $r^{(i)}$ in Eq.
@@
 If the previous step was found to reduce the cost function by a large or small amount, the step size for the previous step will update accordingly.
-This enables to ADAm to overcome smaller discontunities that may arise in the solution space \cite{Goodfellow}.
+This enables to ADAM to overcome smaller discontunities that may arise in the solution space \cite{Goodfellow}.
 Note that a superscript $(i)$ or $(i-1)$ gives an iteration index, while the superscript $i$ means to raise a value to the power of $i$.
@@
 
-\paragraph*{}ADAM has experimentally shown to be a very powerful and robust optimizer useful for a wide range of tasks.
-Because of the two decay constants $\rho_1$ and $\rho_2$, we an compound and accumulate the values of past gradients to continue to push the cost to lower and lower values, even if the magnitude of the gradient becomes very small \cite{Geron}.
+\paragraph*{}ADAM has experimentally shown to be a very powerful and robust optimizer useful for a wide range of tasks \cite{Goodfellow}.
+Because of the two decay constants $\rho_1$ and $\rho_2$, we can compound and accumulate the values of past gradients to continue to push the cost to lower and lower values, even if the magnitude of the gradient becomes very small \cite{Geron}.
 
@@
 	$[y^{(0)},y^{(1)},...,y^{(m-1)}]$.
-	\item Compute numerical gradient estimate of each sample in batch. This can be done with standard back-propagation in algorithm (\ref{algBackProp}) and 			 	normalize by batch size $m$:
+	\item Compute numerical gradient estimate of each sample in batch. This can be done with standard back-propagation in algorithm (\ref{alg-BackProp}) and 			 	normalize by batch size $m$:
 	\item $\nabla \bar{J} \leftarrow \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]$
@@
 
-\paragraph*{}In addition to choosing a strong set of features for a classification task, it is also important to combine the predictors with a complementary architecture.
+\paragraph*{}In addition to choosing a strong set of features, and an appropriate optimizer for a classification task, it is also important to combine the predictors with a complementary network architecture.
 Since a neural network is a computational graph with each layer represented by a node, it can take on a nearly infinite number of different shapes and structures \cite{Goodfellow,Virtanen}.
-The structure of the network defines the composition of it's function, $F^*$ as in Eq.(\ref{eqn-FunctionGraph}), and thus it's performance in completing any given task \cite{Geron}.
-The layer structure of the neural network is referred to as it's \textit{architecture} \cite{Goodfellow}.
+The structure of the network defines the composition of it's function, $F^*$ as in Eq.(\ref{eqn-FunctionGraph}), and thus affects it's performance in completing any given task \cite{Geron}.
+The layer structure of the neural network is referred to as it's \textit{architecture}, and define it's \textit{hypothesis - space} \cite{Goodfellow}.
 
@@
 We must account for the difference by provide two distinct input layers.
-Consider again the act of seeing any hearing a guitar.
-Both modalities are captured by two different senses but ultimately processed by the same brain to produce a single prediction.
+Modalities of seeing and hearing are captured by two different senses but ultimately processed by the same brain to produce a single prediction.
 
 \paragraph*{}We can carry this idea over by producing a \textit{multimodal} neural network that accepts two different forms of input for each sample.
-One input is an $N \times k$ spectrogram matrix, explored in sec.
+One input is an $N' \times k$ spectrogram matrix, explored in sec.
 (\ref{subsec-Spectrogram}) and the other input is a $1 \times p$ feature vector explored in sec.
@@
 \caption{Instruments categories used in the classification task.
-Note that the network uses only integers given by "Class index" to indentify sources.
-The string "Class Name" is keep for human readability}
+Note that the network uses only integers given by "Class index" to identify sources.
+The string "Class Name" is kept for human readability}
 \label{fig-ClassList}
@@
 Where $N \times k$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sect.
-(\ref{subsec-spectrogram}).
+(\ref{subsec-Spectrogram}).
 Similarly, $p$ is the number of predictors extracted from each sample, outlined in sec.
-(\ref{subsec-time}) and sec.(\ref{subsec-frequency}).
+(\ref{subsec-TimeFeatures}) and sec.(\ref{subsec-FreqFeatures}).
 The first axis, with size $b$ indicates that there are $b$ audio file samples stored in that design matrix.
@@
 Examples spectrograms from the wave form data set are shown in Fig.
-(\ref{fig-spectrograms}).
-\begin{figure}[H]
-\begin{center}
-\textcolor{red}{Insert spectrograms here}
+(\ref{fig-Spectrograms}).
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Clarinet-Gs5}
+	\caption{$B\flat$ Clarinet playing $G\sharp 5$}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/GUITAR-B2}
+	\caption{Guitar playing $B2$}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/SquareWave-220}
+	\caption{Square Wave at $220$ Hz}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Tuba-A2}
+	\caption{Tuba playing $A2$}
+	\end{subfigure}
+
 \caption{Spectrogram representations of various waveforms}
-\label{fig-spectrograms}
-\end{center}
+\label{fig-Spectrograms}
 \end{figure}
@@
 Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the previous frame.
-Each of the $k$ frames then allows for a section of the signal to be analyzed in a \textit{quazi-stationary state} \cite{Kahn,Serizel}.
+Each of the $k$ frames then allows for a section of the signal to be analyzed in a \textit{quazi-stationary state} \cite{Khan,Serizel}.
 Below we visualize how analysis frames are related to the full time-series waveform.
@@
 
-\newpage
-
 \subsubsection{Time Domain Envelope}
@@
 In the case of this data set, the ZXR provides a predictor which contains clear separations between classes such as crotales and $E\flat$ clarinets.
-The large separation gives rise to a distinction decision boundary which means that this classes are not likely to be mistake when predictions are run \cite{Loy,James}.
-
 \begin{figure}[H]
@@
 Frequency space is represented by the transposed spectrogram matrix, $S^T$, described in sec.
-(\ref{subsec-spectrogram}).
+(\ref{subsec-Spectrogram}).
 This is done to ensure that each  row is now an analysis frame, each column is a frequency bin.
@@
 
-\paragraph*{}MEl Filter Bank Energies are not used directly as features, but are used in computing Mel Frequency Cepstrum Coefficient (MFCC's) so we describe them here.
+\paragraph*{}Mel Filter Bank Energies (MFBE's) are not used directly as features, but are used in computing Mel Frequency Cepstrum Coefficient (MFCC's) so we describe them here.
 Mel filter banks are divisions of the frequency spectrum of a signal into $R$ overlapping bins \cite{Sahidullah,Serizel}.
@@
 
-\paragraph*{}Rather than producing filter banks based on the linear Hertz scale, the frequency axis of the signal is transformed into units of \textit{Mels}, which is used to account for the non-linearity in human pitch perception \cite{Serizel,Khan}.
+\paragraph*{}Rather than producing filter banks based on the linear Hertz scale, the frequency axis of the signal is transformed into units of \textit{Mels}, which is used to account for the non-linearity in human pitch perception \cite{Serizel,Khan,Olson}.
 Filter banks are produced to be evenly spaced on the Mel scale, and then transformed back into the Hertz scale.
 This has the effect of producing triangular filter banks with grow in width as the frequency increases.
-The Hertz to Mel and Mel to Hertz transforms are given \cite{Serizel,Kahn}:
+The Hertz to Mel and Mel to Hertz transforms are given \cite{Serizel,Khan}:
 \begin{equation}
@@
 When applied to an analysis frame in the frequency spectrum, the dot-product between the filter and the spectrum gives an approximation of the energy in that filter bank.
-Each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is a filter.
+Each filter is concatenated into a matrix $M$ of shape $R \times N'$, where each row is one filter.
 We apply the Mel Filter banks to the spectrogram to create matrix $B$:
@@
 
-\paragraph*{}Tis matrix product in Eq.
+\paragraph*{}The matrix product in Eq.
 (\ref{eqn-FilterBanks}) allows that $B_{i,j}$ is the dot product between the $i$-th analysis frame and the $j$-th filter-bank.
@@
 	\includegraphics[scale=0.3]{../FiguresMetrics/AvgXval-Convolution}
-	\caption{Unimodal Architecture, See left side of Fig. (\ref{fig-NetworkArchitecture})}
+	\caption{Convolutional Unimodal Architecture, See left side of Fig. (\ref{fig-NetworkArchitecture})}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.3]{../FiguresMetrics/AvgXval-Perceptron}
-	\caption{Unimodal Architecture, See right side of Fig. (\ref{fig-NetworkArchitecture})}
+	\caption{Perceptron Unimodal Architecture, See right side of Fig. (\ref{fig-NetworkArchitecture})}
 	\end{subfigure}
@@
 	\end{subfigure}	
-	\label{fig-MultimodalConfs}
+	\caption{}
+	\label{fig-UnimodalConfs}
 \end{figure}
@@
 \subsection{Comparing Classification Scores within Each Class}
+\label{subsec-ClassScores}
 
@@
 
+% ================================================================
+
+\subsubsection{High Woodwind Scores}
+
 \begin{figure}[H]
@@
 	\end{subfigure}
+	\hfill
 	\begin{subfigure}[b]{0.45\textwidth}
@@
 	\end{subfigure}
+
 	\begin{subfigure}[b]{0.45\textwidth}
@@
 	\end{subfigure}	
+	\hfill
 	\begin{subfigure}[b]{0.45\textwidth}
@@
 	\end{subfigure}
+	\hfill	
 	\begin{subfigure}[b]{0.45 \textwidth}
@@
 
-\caption{Performance Metrics Across all High Ranged Woodwind Instruments}
+\caption{}
 \label{fig-HighWindsScores}
 \end{figure}
+
+% ================================================================
+
+\subsubsection{Middle and Low Woodwind Scores}
 
@@
 	\end{subfigure}
-\caption{Performance Metrics Across all Mid and Low Ranged Woodwind Instruments}
+
+\caption{}
 \label{fig-LowWindsScores}
 \end{figure}
+
+% ================================================================
+
+\subsubsection{Brass Scores}
 
@@
 	\end{subfigure}
-\caption{Performance Metrics Across all Brass Instruments}
+
+\caption{}
 \label{fig-BrassScores}
 \end{figure}
+
+% ================================================================
+
+\subsubsection{String Scores}
+
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Banjo}
+	\caption{Banjo}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Bass}
+	\caption{Double Bass}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Cello}
+	\caption{Violoncello}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Guitar}
+	\caption{Guitar}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Mandolin}
+	\caption{Mandolin}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Viola}
+	\caption{Viola}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Violin}
+	\caption{Violin}
+	\end{subfigure}
+
+\caption{}
+\label{fig-StringScores}
+\end{figure}
+
+% ================================================================
+
+\subsubsection{Percussion Scores}
+
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Bells}
+	\caption{Bells}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Crotale}
+	\caption{Crotales}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Hihat}
+	\caption{HiHat}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Marimba}
+	\caption{Marimba}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Vibraphone}
+	\caption{Vibraphone}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/Xylophone}
+	\caption{Xylophone}
+	\end{subfigure}
+
+\caption{}
+\label{fig-PercussionScores}
+\end{figure}
+
+% ================================================================
+
+\subsubsection{Synthetic Waveform Scores}
+
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/SawtoothWave}
+	\caption{Sawtooth Wave}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/SineWave}
+	\caption{Sine Wave}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/SquareWave}
+	\caption{Square Wave}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/TriangleWave}
+	\caption{Triangle Wave}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{../FiguresClasses/WhiteNoise}
+	\caption{White Noise}
+	\end{subfigure}
+
+\caption{}
+\label{fig-SynthScores}
+\end{figure}
+
+% ================================================================
+
+\subsection{Discussion of Results}
+
+\paragraph*{}Comparing the results within each class, as averaged over $10$ folds of cross validation indicate that our model performs very well at the ability to a match sound waves to their sources.
+We see this behavior in the plots in sec.
+(\ref{subsec-ClassScores}) as well as the confusion matrices in Fig.
+(\ref{fig-MultimodalConfs}).
+For the chosen set of classes, features and architecture, the model can generalize to new information allowing it to distinguish between different type of musical instruments reasonably well.
+Additionally, we show that predictive power of the model improves through our development of the multimodal architecture.
+By choosing to express the waveform in two different modalities in the form of the spectrogram matrix and the feature vector, the hybrid model demonstrates consistently higher classification performance across the same number of samples and splits.
+
+% ================================================================
+
+\subsection{Predictions on Chaotic Synthesizers}
 
@@
 
+\item[•]Dr. Kevin Short and Dr. Maurik Holtrop for various consultation and guidance throughout this project.
+
 \item[•]Dakota Buell, John Parker, Nathan Richard, Morgan Saidel for consultation on physics, mathematics, and programming topics.
@@
 \item[•]Madeline Edwards for differing me to this project, as well as constant support and consultation on mathematical topics.
-
-\item[•]Dr. Kevin Short and Dr. Maurik Holtrop for various consultation and guidance throughout this project.
 

### 2020-12-07 SignalClassifier-Postprocessing/ClassifierAnalysis/AnalysisMAIN.py

@@ -22,7 +22,7 @@ if __name__ == '__main__':
 
     # Establish local Directory Paths
     parent = "C:\\Users\\Landon\\Documents\\GitHub\\Buell-Senior-Thesis"
-    modelName = "XValGammaCNN"
+    modelName = "XValAlphaCLF"
     dataPath = os.path.join(parent,"SignalClassifier-CrossValidation",modelName+"-Output-Data")
     metricsPath = os.path.join(parent,"Thesis\\FiguresMetrics")    
     figuresPath = os.path.join(parent,"Thesis\\FiguresClasses")    
@@ -34,7 +34,7 @@ if __name__ == '__main__':
 
     Program.__Call__(metricsPath)
     #Program.ExportMetricsBySplit(metricsPath)
-    #Program.ExportMetricsByClass(metricsPath)
+    Program.ExportMetricsByClass(metricsPath)
 
 
     # Prepare Figures

### 2020-12-09 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis paper

@@
        	\begin{LARGE}
-       	\textbf{Mapping Chaotically Generated Synthesizers to Real World Instruments with Machine Learning and Harmonic Analysis} \\
+       	\textbf{Mapping Chaotically Generated Synthesizers to Musical Instruments with Machine Learning and Harmonic Analysis} \\
        	\end{LARGE}
@@
 
+The task of recognizing the source of a sound wave is trivial and almost effortless to a human being.
+
 \end{abstract}
@@
 
-\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}.Whether its climate measurements, financial reports, audio-visual media, or medicine complex signal surround the modern world at every corner.
-
-\paragraph*{}Consider the task of identifying the source of a sound.
-
-\paragraph*{}Recent progress in high performance computing and computational efficiency have given rise to another burst in the
+\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan,Mierswa}.
+From climate measurements, to financial reports, to audio-visual media, or to medicine, time-domain signals surround the modern world at every corner \cite{Liu,Zhang}.
+In each context, the general idea is to place the data or a subset of the data into distinct categories called \textit{classes} based on it's properties.
+For example, doctors may wish to classify a patient as having a heart condition based on properties of their heartbeat or banks may wish to detect fraudulent transactions based on a history of spending habits.
+Often, the volume  of information or complexity of the task makes it unreasonable for a human to do unaided by some form of automation.
+
+\paragraph*{}It has long been a goal of computer scientists and engineers alike to develop a program, algorithm, or machine that could perform a certain task to the level of human-being \cite{Bishop,Geron,Loy}.
+While humans are intricate organisms capable of recognition or classification in many contexts, we are not notorious for the ability to process millions of raw numerical values in the course of a few seconds.
+Similarly, modern computers are also complex systems that can filter through exabytes of information on a daily basis, but are not generally known for being able to distinguish cats from dogs \cite{Geron}.
+The compromise between is an algorithm called a \textit{neural network} that combines the computation speed of a computer with the decision-making power of a human \cite{Goodfellow,Levine,Loy}.
+
+\paragraph*{}In this work, we have developed an automated neural network program that can classify digital sound waves based on the musical instrument that produced them.
+The general use of machine learning algorithms for audio information classification or identification is well explored, and a topic of much modern research \cite{Khan,Liu,Mierswa,Serizel,Zhang}.
+
+\paragraph*{}
 
@@
 We also have a data set $X$ and a set of appropriately labeled targets, $Y$, each of which contain $N$ samples.
-For $K$-folds X-val, we divide the full data set into $K$ subsets (called \textit{folds}), each with size $K/N$:
+For $K$-folds X-val, we divide the full data set into $K$ subsets (called \textit{folds}), each with size $N/K$:
 \begin{equation}
@@
 Each mini-batch contains $32$ samples.
-Once all mini-batches are fit, we discard the design matrices in the mega batch ans repeat for the next $256$ samples.
-
-\paragraph*{}Along each training step, we record the precision, recall, and loss scores.
-Our program stores these values locally in a \textit{training-history} file, which we can examine after the program completes.
-Below, we visualize the value of each metric score at each training epoch.
-
-\begin{figure}[h]
+Once all mini-batches are fit, we discard the design matrices in the mega batch and repeat for the next $256$ samples.
+
+\paragraph*{}With each training step, we have recorded the precision, recall, and loss scores.
+These scores are computed from the forward pass of the training data before the gradient is computed, and parameters updated, i.e.
+the program has not seen Our program stores these values locally in a \textit{training-history} file, which we can examine after the program completes.
+Below, we visualize the evolution of each score as training progresses.
+These plots are from a model that was trained separately on the full data set after cross validation was performed.
+
+\begin{figure}[H]
 \begin{center}
-%\includegraphics[scale=0.2]{•}
-\textcolor{red}{Loss Score Goes Here}
+\includegraphics[scale=0.3]{../Figures/LossHistory}
 \end{center}
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 \begin{center}
-
+\includegraphics[scale=0.3]{../Figures/MetricHistory}
 \end{center}
-\caption{The precision score (a) and recall score (b) generally increase with each training step}
+\caption{The precision score and recall score generally increase with each training step}
 \label{fig-PrecisionRecallScores}
 \end{figure}
+
+\paragraph*{}Notice how loss, precision and recall show a pattern of increasing and decreasing every two steps.
+This is because we extract a mega-batch of $256$ samples, and perform two epochs of training on the batch.
+The first step represents the first time the model has seen the data, thus produces a higher cost function value.
+In the second step, the model has already seen the samples in the batch, and it produces a slightly lower cost value that the first step.
+The batch is discarded and a new subset of samples is drawn so that the process repeats.
+With two epochs per mega-batch, and two passes over the full data set (permuted in the middle), the model is effectively trained on the full data set a total of $4$ times.
 
@@
 \includegraphics[scale=0.3]{../FiguresMetrics/AvgXval-Multimodal}
-\caption{Performance metrics across $10$ models and $37$ classes}
+\caption{Performance metrics for the multimodal networks across $10$ models, scores are averaged over $37$ classes}
 \label{fig-MultimodalXval}
@@
 	\includegraphics[scale=0.18]{../FiguresMetrics/XValAlphaCLF_Avg_Standard_Confusion}
-	\caption{Standard Confusion Matrix}
+	\caption{Standard confusion matrix for hybrid network}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.18]{../FiguresMetrics/XValAlphaCLF_Avg_Hits_Weighted_Confusion}
-	\caption{Occurance Weighted Confusion Matrix}
-	\end{subfigure}
-
-	\caption{}
+	\caption{Occurrence weighted confusion matrix for hybrid network}
+	\end{subfigure}	
+	\caption{Confusion matrices, each is averaged over 10 folds of cross validation}
 	\label{fig-MultimodalConfs}
@@
 \paragraph*{}We show the metric values of all splits to show the consistency in performance across all subsets.
-Notice how the models each perform reasonably well (precision and recall score consistently above 80\%).
-This indicates that for this data set, architecture, and feature selection, our model can performance reasonably and generalize appropriately.
+Notice how each split shows reasonable performance as given by the precision and recall score consistently above 80\%.
+This indicates that for this data set, architecture, and feature selection, our model can accurately classify waveforms and generalize appropriately.
 This step is critical in ensuring that there are no major out-liers in the classification results, and that any set of initial conditions can still allow the model to reach an acceptable set of parameters and decision boundaries.
@@
 	\includegraphics[scale=0.18]{../FiguresMetrics/XValGammaCNN_Avg_Standard_Confusion}
-	\caption{Standard Confusion Matrix for Convolution Branch}
+	\caption{Standard confusion Matrix for the convolution branch}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.18]{../FiguresMetrics/XValGammaCNN_Avg_Hits_Weighted_Confusion}
-	\caption{Occurance Weighted Confusion Matrix for Convolution Branch}
+	\caption{Occurrence Weighted confusion matrix for the convolution branch}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.18]{../FiguresMetrics/XValBetaMLP_Avg_Standard_Confusion}
-	\caption{Standard Confusion Matrix for Perceptron Branch}
+	\caption{Standard confusion matrix for the perceptron Branch}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.18]{../FiguresMetrics/XValBetaMLP_Avg_Hits_Weighted_Confusion}
-	\caption{Occurance Weighted Confusion Matrix for Perceptron Branch}
-	\end{subfigure}	
-	\caption{}
+	\caption{Occurrence weighted confusion matrix the for perceptron branch}
+	\end{subfigure}	
+	\caption{Performance metrics for the unimodal networks across $10$ models, scores are averaged over $37$ classes}
 	\label{fig-UnimodalConfs}
@@
 Additionally, we show that predictive power of the model improves through our development of the multimodal architecture.
-By choosing to express the waveform in two different modalities in the form of the spectrogram matrix and the feature vector, the hybrid model demonstrates consistently higher classification performance across the same number of samples and splits.
+By choosing to express the waveform in two different modalities in the form of the spectrogram matrix and the feature vector, the hybrid model demonstrates a generally higher classification performance across the same number of samples and splits.
+
+\paragraph*{}Despite the higher average scores in the hybrid network, see Fig.
+(\ref{fig-MultimodalXval}) compared to each unimodal network, Fig.
+(\ref{fig-UnimodalXVal}), some exceptions do arise at a micro-level (within each class).
+Consider the Hi-hat instrument in Fig.
+(\ref{fig-PercussionScores}c).
 

### 2020-12-09 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to properties section

@@
 (\ref{sec-TheNeuralNetwork}), performance quality of a neural network is greatly dependent on the properties of the chosen features \cite{Virtanen,Liu}.
-To ensure that a the classifier model performs adequately and consistently, we must choose these features to have high variance between classes, and low variance within each class.
+To ensure that the classifier model performs adequately and consistently, we must choose these features to have high variance between classes, and low variance within each class.
 This enables a neural network to development clear decision boundaries between each unique class \cite{James,Serizel}.
@@
 
-\paragraph*{}We have assembled training data samples than can be grouping into $37$ classes of unique sources listed below:
+\paragraph*{}Computer algorithms such are neural networks are build to handle exclusively quantitative information \cite{Geron}.
+Where a human would use qualitative adjectives such as \textit{bright} or \textit{harsh} or \textit{percussive} to describe sound, computers require a numerical descriptor instead.
+The goal of this section is to develop the attributes of sound that enable us to describe a sound wave in a quantitative and compact way.
+Thus we use values that can be expressed as numbers such as \textit{amplitude envelopes}, \textit{frequency spectra}, or \textit{formant structure}.
+For this section, we represent waveforms as \textit{spectrograms} to capture the time-space and frequency-space development of energy simultaneously.
+We motivate and describe the production of a spectrogram in sec.
+(\ref{subsec-Spectrogram}).
+
+\paragraph*{}We have assembled training data samples than can be grouped into $37$ classes of unique sources listed below:
 
@@
 
-\paragraph*{}Rather than explore each class individually, we can examine the properties of groupings of musical instruments by using the \textit{Hornbostel-Sachs} organization system.
-In this syetem, musical instruments or sound sources can be divided up into four broad categories based on the nature of the sound-producing material.
+\paragraph*{}Rather than explore each class individually, we can examine the properties of groupings of musical instruments by using the \textit{Hornbostel-Sachs} organization system developed by  Erich M.
+von Hornbostel and Curt Sachs, and published in 1961 \cite{Hornbostel}.
+In this system, musical instruments or sound sources can be divided up into four broad categories based on the nature of the sound-producing material.
 These categories are (i) idiophones, (ii) membranophones, (iii) chordophones, and (iv) aerophones.
@@
 \paragraph*{}An idiophone is an instrument that produces sound through the vibration of the full body of the object.
-This generally includes most percussive instruments excluding drums \textcolor{red}{citation needed}.
-From the set of classes that we use, bells, crotales, Hi-hats, vibraphones, and xylophones are all examples of idiophones.
+This generally includes most percussive instruments excluding drums \cite{Hornbostel}.
+From the set of classes that we use, bells, crotales, Hi-hats, marimbas, vibraphones, and xylophones are all examples of idiophones.
+In each case, sound comes from the vibration of the object itself or some subset of the body.
+In the case of mallet percussion, the wood or metal keys vibrate when struck with a felt or yarn mallet.
+Sometimes the vibration is amplified by nearby air columns, but it is the vibration of the key itself where the sound originates from \cite{Olson}.
+
+\paragraph*{}Idiophones in particular can be characterized by their \textit{transient response} \cite{White}.
+The transient response is the time-evolution response of the waveform in time, which we normally break into \textit{attack}, \textit{decay}, \textit{sustain}, and \textit{release}.
+For most idiophones, the system is struck once and left to a free or dampened vibration; which we can mathematically model as a rigid body reacting to an impulse \cite{Hunter,Olsen}.
+
+\begin{figure}
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\textcolor{red}{Idiophone}
+	\caption{•}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\textcolor{red}{Idiophone}
+	\caption{•}
+	\end{subfigure}
+\caption{Spectrogram representation of idiophone waveforms}
+\label{fig-PropertiesIdiophones}
+\end{figure}
+
+\paragraph*{}From the spectrogram representation of idophone waveforms , we can see the majority of energy in the time domain is right at the start of the waveform.
+This is shown by the vertical bright yellow line at on the left side of each image in Fig.
+(\ref{fig-PropertiesIdiophones}).
+When an idiophone is struck, all of the energy for the vibration is delivered up front, and this the amplitude of the waveform can only decay.
+This gives the resulting transient a very short attack time, followed by a short decay, sustain, and often long release as the last of the energy dies out \cite{White}.
+While other instruments sch as plucked strings like guitars show similar response, this is a very important property
+
+\paragraph*{}This property allows for us to distinguish idiophones from other instruments by an approximation of their amplitude envelope.
+For example, if we divide the time series waveform into $q$ distinct sections, and compute the RMS energy in each section, we should see a gradual decay of energy with time.
+More specifically, the energy in some section $q_i$ should be greater than the energy in any subsequent section $q_{i + n}, n \in \mathbb{Z}$.
+Having this property does not guarantee the source is an idiophone but can we can reasonable state that most idiophones follow this behavior.
+In addition to the amplitude envelope, we can consider the distribution of time-space energy in the form of a single scalar quantity as the center of mass.
+If we treat the waveform as a 1D mass distribution, and compute the center of mass, we should see consistently low values because the largest values of amplitudes happen early on in the time-domain.
 
@@
 
+\paragraph*{}A membranophone is an instrument that produces sound through the vibration of a tight membrane \cite{Hornbostel}.
+This includes most drum-like instruments While none of the instruments that we classify are membranophones, they do exhibit some noteworthy properties that influence our feature for other instruments.
+Common examples include the tympani, the bass drum, or the kettle drum.
+Each of these instruments is composed of a large cylinder or bowl-like structure that serves as an amplifying cavity \cite{Olson,White}.
+Given that most membranophone instruments are played by striking the membrane with the hand or mallet, the amplitude envelope properties
+
+\paragraph*{}Additionally, we model the tight elastic membrane very similarly as that of a tight elastic string, except in two dimensions \cite{White}.
+However, the partials for the membrane are not related by integer multiples like that or strings are.
+This lack of harmonic structure leaves most membranophones to have a sort of "muddled" frequency spectrum where we see a continuous distribution of constituent frequencies arise as opposed to clean overtones arising as in stringed or wind instruments \cite{White,Olson}.
+This is in part why many membranophones have a much more "percussive" sound as opposed to performing any distinct note.
+
 % ================================================================
@@
 
-\paragraph*{}A chordophone is a musical instrument that produces sound through the vibration of strings that are stretched between two fixed points \textcolor{red}{citation needed}.
+\paragraph*{}A chordophone is a musical instrument that produces sound through the vibration of strings that are stretched between two fixed points \cite{Hornbostel}.
 From our data set, banjos, basses, cellos, guitars, mandolins, violins, and violas are all examples of chordophones.
-
-\subsubsection{The 1-Dimensional Vibrating String}
-
-\paragraph*{}We can model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$.
+We commonly model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$.
 The string is flexible, and free to vibrate in a single dimension.
@@
 D'Alembert's equation indicates that the acceleration of any point on a string is directly proportional to the rate of change of the slope of the string at that point.
-Additionally, the string is fixed in place at both ends, with a nut at $x = 0$ and a bridge at $x = L$, which can be modeled by the boundary conditions \cite{Olson,White,Haberman}:
+
+\paragraph*{}Since the PDE is second order in time, we must also specify two initial conditions being the shape and the derivative of the shape at time $t = 0$.  \cite{Olson,White,Haberman}:
+\begin{equation}
+U(x,0) = f(x) 
+	\text{\hspace*{2cm} and \hspace*{2cm}}
+\frac{\partial U}{\partial t}(x,0) = g(x)
+\end{equation}
+Additionally, the string is fixed in place at both ends, with a nut at $x = 0$ and a bridge at $x = L$, which can be modeled by the boundary conditions
 \begin{equation}
@@
 \end{equation}
-
-\paragraph*{}In order to specify a solution, we must also specify two initial conditions. We described the initial state of the string at time $t = 0$  by the two conditions:
-\begin{equation}
-U(x,0) = f(x) 
-	\text{\hspace*{2cm} and \hspace*{2cm}}
-\frac{\partial U}{\partial t}(x,0) = g(x)
-\end{equation}
 Depending on the exact nature of the source instrument, $f(x)$ and $g(x)$ can take on different forms.
@@
 It is these initial conditions that allow for the drastically different timbres that arise in the wave forms.
-
-\paragraph*{}Despite these differences, the wave equation is a \textit{linear} partial differential equation which allows for the fact that a linear combination of solutions is also a valid solution.
+Compare the spectrogram representation of a few stringed instruments in Fig.
+(\ref{fig-PropertiesChordophones}).
+\begin{figure}[H]
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/CELLO-F4}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Guitar-B2}
+	\end{subfigure}
+\caption{Spectrograms for a few Stringed instruments}	
+\label{fig-PropertiesChordophones}
+\end{figure}
+
+\paragraph*{}Despite these differences, the wave equation is still a \textit{linear} partial differential equation which allows for the fact that a linear combination of solutions is also a valid solution.
 In the case of the taught finite string that is fixed at both ends, such a guitar, viola or cello, the a solution tends to take the form of a sinusoidal function such a sine or cosine \cite{Hunter, Taylor, White}.
-
-\paragraph*{}The boundary continuations, and most forms of standard initial conditions allow for the each sinusoidal to fit exactly an integer wavelengths into the region $[0,L]$ \cite{Haberman,Hunter}.
+The boundary continuations, and most forms of standard initial conditions allow for the each sinusoidal to fit exactly an integer wavelengths into the region $0 \leq x \leq L$ \cite{Haberman,Hunter}.
 Physically, this corresponds to having the string vibrate with some fundamental frequency $f_0$, which represents it's lowest possible note,and a linear combination of higher harmonics, $n \times f_0$, where $n \in \mathbb{Z}$ \cite{Olson,Taylor,White}.
-
-\begin{figure}[H]
-	\begin{subfigure}{0.45\textwidth}
-	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/CELLO-F4}
-	\end{subfigure}
-	\begin{subfigure}{0.45\textwidth}
-	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Guitar-B2}
-	\end{subfigure}
-\end{figure}
+In the case of bowed stringed instruments such as cellos or violins, we often see a formant structure marked by fairly uniform amplitude of each harmonic in the frequency spectrum.
+Observe this behavior in Fig.
+(\ref{fig-PropertiesChordophones}).
+
+\paragraph*{}Additionally, It is worth noting at each string instrument produces a slightly different frequency spectrum, hence each provides a slightly different timbre to the listener, so differentiating between them is difficult, but possible.
+Because of this, we find that the spectrogram representation of the waveform is so critical to classification success because the convolution layers allow for the detection of small variations in the frequency-time domain where humans would otherwise be unable to \cite{Loy,Virtanen}.
+However, the size of the instrument limits the length of the string that vibrates which leads to limitations in the range of the overtones the instruments will produce.
+For example, a cello playing a low $C1$ will have overtones extenting up into the $12$ kHz range, but the energy will be very low there, thus have a very low frequency center of mass.
+Compare this with a violin playing a $C6$, will have overtones into the $20$ kHz range, and will produce a very high frequency center of mass.
+While the ranges of the musical instruments overlap a great deal, the energy distribution in frequency space can be treated as a 1D mass distribution, and the frequency center of masses of instruments with similar timbres can still differ greatly \cite{Serizel}.
+
+\paragraph*{}Notice as well in the spectrograms of Fig.
+({fig-PropertiesChordophones}), how the transient response (the time domain) of chordophones differs wildly from idiophones and membranophones.
+In the case of bowed instruments, the attack of the stringed instrument is much longer, with a much more gradual sustain decay, and release.
+Where an idiophone or plucked string has all of the time-domain energy up front, the bowed string waveform continues to build energy as the instrument is bowed, and only loses energy once the bowing stops, and the string is left to vibrate by itself \cite{Hunter}.
+This causes a bowed stringed instruemnt to present a very different amplitude envelope compared to the other categories of instruments, and a much more centrally located temporal center of mass.
 
@@
 \paragraph*{}An aerophone is a musical instrument that produces sounds through the vibration of an air molecules in a column-like structure.
+This is the largest category of instruemnts that we have, and is commonly broken down into smaller subcategories such as \textit{woodwind} and \textit{bass} instruments.
+From out data set- alto flutes, alto saxophones, bass clarinets, bass flutes, bassoons, $B\flat$ clarinets, contrabassoons, $E\flat$ clarinets, English horns, flutes, oboes, tenor saxophones, and soprano saxophones are all examples of woodwind aerophones.
+Additionally, bass trombones, french horns, tenor trombones, trombones, $B\flat$ trumpets, and tubas are all examples of brass aerophones \cite{Hornbostel,Olson,White}.
 
@@
 \paragraph*{}We group sounds produced from non-physical musical instruments in this final category.
-Form our data set, this category includes the four simplest waveforms, (i) sine waves, (ii) sawtooth waves, (iii) square waves, and (iv) triangle waves, as well as any color noises \cite{White}.
+Form our data set, this category includes the four simplest waveforms,sine waves, (ii) sawtooth waves, square waves, and triangle waves, as well as any color noises \cite{White}.
 Since these sounds are only produced synthetically through a MATLAB program, we choose not to include them in the Hornbostel-Sachs grouping above.
-We explore the properties of each of these generated sounds.
-
-% ================
-
-\subsubsection{Sine Wave}
-
-\paragraph*{}A sine wave is the simplest of sound waves, and makes up the foundation for all periodic wave forms \cite{White,Virtanen}.
-It consists of a single oscillatory term with a fixed fundamental frequency $f_0$.
-A sine wave's amplitude as a function of time is given by
-\begin{equation}
-\label{eqn-SineWave}
-x(t) = A_0 \sin(2\pi f_0 t + \phi)
-\end{equation}
-Where $A_0$ gives an amplitude, $f_0$ is the fundamental frequency, and $\phi$ is a phase shift. We show a simple sine wave in the time and frequency domain in Fig. (\ref{fig-SineWave}).
-
-\begin{figure}[h]
-\begin{center}
-	\textit{[Image of Sine Wave Waveform]}
-	\textit{[Image of Sine Wave Freq. Spect]}
-\end{center}
-\caption{A sine wave in the (a) time-domian and (b) frequency domain}
-\label{fig-SineWave}
-\end{figure}
-
-\paragraph*{}A pure sine wave contains no overtones, only a time-independent fundamental frequency, which can take on any value due to synthetic generation.
-
-% ================
-
-\subsubsection{Sawtooth Wave}
-
-\paragraph*{}
-
-% ================
-
-\subsubsection{Square Wave}
-
-\paragraph*{}A square wave is a piece-wise defined waveform whose value alternatively alternates between $+1$ and $-1$ \cite{White,Olson}.
-A square wave with period $f_0$ has a waveform defined over a single period as:
-\begin{equation}
-\label{eqn-SquareWave}
-x(t) =  \left\{
-\begin{array}{ll}
-    +1 & \text{\hspace{0.5cm}} 0 < x \leq T_0 / 2 \\
-    -1 & \text{\hspace{0.5cm}} T_0/2 < x < T_0
-\end{array} 
-\right.
-\end{equation}
-where $T_0 \equiv 1/f_0$.
-
-\paragraph*{}We can use Fourier decomposition to examine the constituent sinusoidal wave that make up a square wave.
-The frequency space representation of a square wave indicates that is can be approximated as a sum of higher odd-numbered harmonics, with the amplitude of each decreasing by the reciprocal of the harmonic number \cite{White}.
-Thus a square wave in the time domain can be approximated as:
-\begin{equation}
-x(t) \approx \sum_{n = 1}^{\infty} \frac{1}{2n-1} \sin \bigg( 2 \pi (2n - 1)f_0 t \bigg)
-\end{equation}
-
-\begin{figure}[h]
-\begin{center}
-	\textit{[Image of Square Wave Waveform]}
-	\textit{[Image of Sqaure Wave Freq. Spect]}
-\end{center}
-\caption{A square wave in the (a) time-domain and (b) frequency domain}
-\label{fig-SquareWave}
-\end{figure}
-
-% ================
-
-\subsubsection{Triangle Wave}
-
-% ================
-
-\subsubsection{White Noise}
+We explore the properties of each of these generated sounds and how they relate to physical instruments.
 
@@
 
+\bibitem{Hornbostel}
+Von Hornbostel, Erich, and Curt Sachs. “Classification of Musical Instruments.” \textit{The Galpin Society Journal}, Translated by Anthony Baines and Klaus Wachsmann, vol. 14, Mar. 1961, pp. 3–29.
+
 \bibitem{Hunter}

### 2020-12-10 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
New Figures, updates to Thesis

@@
 The transient response is the time-evolution response of the waveform in time, which we normally break into \textit{attack}, \textit{decay}, \textit{sustain}, and \textit{release}.
-For most idiophones, the system is struck once and left to a free or dampened vibration; which we can mathematically model as a rigid body reacting to an impulse \cite{Hunter,Olsen}.
-
-\begin{figure}
-	\begin{subfigure}[b]{0.45\textwidth}
-	\centering
-	\textcolor{red}{Idiophone}
-	\caption{•}
+For most idiophones, the system is struck once and left to a free or dampened vibration; which we can mathematically model as a rigid body reacting to an impulse \cite{Hunter,Olson}.
+
+\begin{figure}[H]
+	\begin{subfigure}[b]{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Vibraphone-A5}
+	\caption{Vibraphone playing $A5$}
 	\end{subfigure}
@@
 	\centering
-	\textcolor{red}{Idiophone}
-	\caption{•}
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Marimba-C2}
+	\caption{Marimba playing $C2$}
 	\end{subfigure}
@@
 This gives the resulting transient a very short attack time, followed by a short decay, sustain, and often long release as the last of the energy dies out \cite{White}.
-While other instruments sch as plucked strings like guitars show similar response, this is a very important property
+While other instruments sch as plucked strings like guitars show similar response, this is a very important property of many idiophones.
+Notice additionally, that the energy of the higher overtones die out very quickly in each spectrogram, and only the lowest pitch - the fundamental is preserved for much of the duration.
 
@@
 	\includegraphics[scale=0.18]{../FiguresSpectrogram/CELLO-F4}
+	\caption{Violoncello playing $F4$}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.18]{../FiguresSpectrogram/Guitar-B2}
+	\caption{Guitar playing $B2$}
+	\end{subfigure}
+
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Violin-G4}
+	\caption{Violin playing $G4$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Viola-G4}
+	\caption{Viola playing $G4$}
 	\end{subfigure}
@@
 
-\paragraph*{}Despite these differences, the wave equation is still a \textit{linear} partial differential equation which allows for the fact that a linear combination of solutions is also a valid solution.
-In the case of the taught finite string that is fixed at both ends, such a guitar, viola or cello, the a solution tends to take the form of a sinusoidal function such a sine or cosine \cite{Hunter, Taylor, White}.
-The boundary continuations, and most forms of standard initial conditions allow for the each sinusoidal to fit exactly an integer wavelengths into the region $0 \leq x \leq L$ \cite{Haberman,Hunter}.
-Physically, this corresponds to having the string vibrate with some fundamental frequency $f_0$, which represents it's lowest possible note,and a linear combination of higher harmonics, $n \times f_0$, where $n \in \mathbb{Z}$ \cite{Olson,Taylor,White}.
-In the case of bowed stringed instruments such as cellos or violins, we often see a formant structure marked by fairly uniform amplitude of each harmonic in the frequency spectrum.
-Observe this behavior in Fig.
-(\ref{fig-PropertiesChordophones}).
-
-\paragraph*{}Additionally, It is worth noting at each string instrument produces a slightly different frequency spectrum, hence each provides a slightly different timbre to the listener, so differentiating between them is difficult, but possible.
+\paragraph*{}Despite these differences, the wave equation is still a \textit{linear} partial differential equation which allows for a linear combination of solutions to form a sound wave.
+In the case of the taught finite string that is fixed at both ends, such a guitar, viola or cello, the a solution tends to take the form of a sine or cosine function \cite{Hunter, Taylor, White}.
+The boundary conditions, and most forms of standard initial conditions allow for the each sinusoidal to fit exactly an integer or half-integer number wavelengths into the region $0 \leq x \leq L$ \cite{Haberman,Hunter}.
+Players of chordophones change pitch by shortening the length of the vibrating string or applying additional tension to the string.
+This changes the length of portion of the string that vibrates, and causes the production of a new pitch.
+
+\paragraph*{}It is worth noting at each string instrument do produce a slightly different frequency spectrum, hence each provides a slightly different timbre to the listener, so differentiating between them is difficult, but possible.
 Because of this, we find that the spectrogram representation of the waveform is so critical to classification success because the convolution layers allow for the detection of small variations in the frequency-time domain where humans would otherwise be unable to \cite{Loy,Virtanen}.
 However, the size of the instrument limits the length of the string that vibrates which leads to limitations in the range of the overtones the instruments will produce.
-For example, a cello playing a low $C1$ will have overtones extenting up into the $12$ kHz range, but the energy will be very low there, thus have a very low frequency center of mass.
+For example, a cello playing a low $C1$ will have overtones extending up into the $12$ kHz range, but the energy will be very low there, thus have a very low frequency center of mass.
 Compare this with a violin playing a $C6$, will have overtones into the $20$ kHz range, and will produce a very high frequency center of mass.
@@
 \paragraph*{}An aerophone is a musical instrument that produces sounds through the vibration of an air molecules in a column-like structure.
-This is the largest category of instruemnts that we have, and is commonly broken down into smaller subcategories such as \textit{woodwind} and \textit{bass} instruments.
-From out data set- alto flutes, alto saxophones, bass clarinets, bass flutes, bassoons, $B\flat$ clarinets, contrabassoons, $E\flat$ clarinets, English horns, flutes, oboes, tenor saxophones, and soprano saxophones are all examples of woodwind aerophones.
+This is the largest category of instruemnts that we have, and is commonly broken down into smaller subcategories such as \textit{woodwind} and \textit{brass} instruments.
+From our data set - alto flutes, alto saxophones, bass clarinets, bass flutes, bassoons, $B\flat$ clarinets, contrabassoons, $E\flat$ clarinets, English horns, flutes, oboes, tenor saxophones, and soprano saxophones are all examples of woodwind aerophones.
 Additionally, bass trombones, french horns, tenor trombones, trombones, $B\flat$ trumpets, and tubas are all examples of brass aerophones \cite{Hornbostel,Olson,White}.
+
+\paragraph*{}Aerophones all produce sound by exciting molecules of air within a column that vibrate in different patterns called \textit{modes} \cite{White}.
+The nature of modes are determine by the structure of the instruments.
+Most aerophones such a flutes, clarinets, and saxophones are more much more reminiscent of air columns that are closed at one end and open at the other.
+The is marked by the presence of a mouth piece at one end where a played blows air fro their lungs to add energy, and a bell at the other end to serve as an amplification structure \cite{Olson}.
+For a column of length $L$, that is open at one end, the fundamental frequency is given by \cite{Olson}:
+\begin{equation}
+f_0 = \frac{v}{4L} = \frac{v}{\lambda}
+\end{equation}
+where $v$ is the velocity of sound in the medium, and $\lambda$ is the wavelength of the sound wave.
+This is the lowest pitch that such an instrument can play.
+Lower woodwinds such as bass clarinets, have a much longer vibrating air column that that of the short piccolo.
+
+\paragraph*{}To change the pitch, the performer of an aerophone must change the length of the vibrating air column by pressing keys with their fingers.
+This causes a different number of wavelengths to fit within the column, and thus change the note being played.
+Shortening the column (reducing $L$) also causes a reduction in the wavelength, and an increase in frequnecy and vice-versa.
+In Fig.
+(\ref{fig-PropertiesAerophonesWind}) we show the spectrogram waveforms for a few different woodwind instruments.
+
+\begin{figure}[H]
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/AltoSax-A4}
+	\caption{Alto Saxophone playing $A4$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Clarinet-Gs5}
+	\caption{$B\flat$ Clarinet playing $G\sharp 5$}
+	\end{subfigure}
+
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Oboe-Bb4}
+	\caption{Oboe playing $B\flat 4$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Bassoon-D4}
+	\caption{Bassoon playing $D4$}
+	\end{subfigure}
+\caption{Spectrograms for a few Stringed instruments}	
+\label{fig-PropertiesAerophonesWind}
+\end{figure}
+
+\paragraph*{}In addition to the woodwind instruments described above , we also consider the properties of brass aerophones.
+As the name implies, brass instruments are usually made of interconnected hollow tubes of brass.
+as opposed to linear columns of mostly wood.
+brass instruments are also modeled as open-closes columns that vibrate which are again shortened and lengthened by pressing keys.
+Brass instruments are generally much longer than woodwinds, and produce sounds at a generally greater volume \cite{Olson}.
+Despite these differences, brass instruments do generally display a great deal of similarities with wood winds, as we can see in Fig.
+(\ref{fig-PropertiesAerophonesBrass})
+
+\begin{figure}[H]
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/FRENCHHORN-Cs4}
+	\caption{French horn playing $c\sharp 4$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/TenorTrombone-F4}
+	\caption{Tenor Trombone playing $F4$}
+	\end{subfigure}
+
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Trumpet-B3}
+	\caption{$B\flat$ Trumpet playing $B3$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/Tuba-A2}
+	\caption{Tuba playing $A2$}
+	\end{subfigure}
+\caption{Spectrograms for a few Stringed instruments}	
+\label{fig-PropertiesAerophonesBrass}
+\end{figure}
+
+\paragraph*{}Just like with idiophones and chordophones, the amplitude envelop of a brass instrument is very characteristic.
+Aerophones require a user to vibrate air with their lungs which gradually adds energy to the waveform.
+This transfer of energy can take comparably long time, giving aerophones particularity long attack times.
+The note is sustained as long as a player is vibrating the air, allowing for any length of decay and sustain, but the energy does out very suddenly when the player stops, giving a characteristically short release time \cite{White}.
 
@@
 \paragraph*{}We group sounds produced from non-physical musical instruments in this final category.
-Form our data set, this category includes the four simplest waveforms,sine waves, (ii) sawtooth waves, square waves, and triangle waves, as well as any color noises \cite{White}.
+Form our data set, this category includes the four simplest waveforms, sine waves, sawtooth waves, square waves, and triangle waves, as well as any color noises \cite{White}.
 Since these sounds are only produced synthetically through a MATLAB program, we choose not to include them in the Hornbostel-Sachs grouping above.
 We explore the properties of each of these generated sounds and how they relate to physical instruments.
+
+\paragraph*{}Each of the five synthetically generated waveforms were produce to be constant with all time.
+This means that each waveform has no characteristic amplitude envelope and the spectrogram shows no time-evolution of energy in the waveform.
+Each of the the signals can be composed od a linear combinations of oscillating sinusoidal at various different frequencies and energies.
+For example, a sine wave conists only of a single oscillating term, while a square wave consists of repeated odd harmonics.
+These behaviors can be observed in Fig.
+(\ref{fig-PropertiesSynths}).
+
+\begin{figure}[H]
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/SquareWave-880Hz}
+	\caption{Square Wave at $880$ Hz}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/SawtoothWave-880Hz}
+	\caption{Sawtooth Wave at $880$ Hz}
+	\end{subfigure}
+
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/SineWave-880Hz}
+	\caption{Sine Wave at $880$ Hz}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
+	\centering
+	\includegraphics[scale=0.18]{../FiguresSpectrogram/WhiteNoise-190}
+	\caption{White Noise}
+	\end{subfigure}
+\caption{Spectrograms for a few Stringed instruments}	
+\label{fig-PropertiesSynths}
+\end{figure}
+
+These waveform were included to our data set to serve primilarly as a control to understand how the chosen features respond to simple waveforms.
+Additionally, the elementary composition of each waveform allows for it to potentially resemble a wide variety of frequency spectra \cite{White}.
 
@@
 	\centering
-	\includegraphics[scale=0.2]{../FiguresSpectrogram/SquareWave-220}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/SquareWave-880Hz}
 	\caption{Square Wave at $220$ Hz}

### 2020-12-14 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis

@@
 \paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan,Mierswa}.
-From climate measurements, to financial reports, to audio-visual media, or to medicine, time-domain signals surround the modern world at every corner \cite{Liu,Zhang}.
+From climate measurements, to financial reports, to audio-visual media, or to medicine, time-domain signals surround the modern world at every corner \cite{Virtanen}.
 In each context, the general idea is to place the data or a subset of the data into distinct categories called \textit{classes} based on it's properties.
@@
 
-\paragraph*{}In this work, we have developed an automated neural network program that can classify digital sound waves based on the musical instrument that produced them.
+\paragraph*{}In this work, we have developed an automated neural network program that can classify digital sound waves as one of $37$ musical instrument that it most closely resembles.
 The general use of machine learning algorithms for audio information classification or identification is well explored, and a topic of much modern research \cite{Khan,Liu,Mierswa,Serizel,Zhang}.
-
-\paragraph*{}
+From previous work, it has been found that various types of audio classification are possible, and are still being expanded upon.
+Some papers details features and performances of attempting to classify speech against music or organize audio-visual media based on content.
+
+\paragraph*{}It is well know that the choice of inputs, called features is critically important to classification success \cite{Khan,Serizel}.
+In many cases, we can develop and explore a set of features that allows for the particular classification task to be executed considerably well.
+In our case, the choice of features is motivated by the physics of each musical instrument class.
+By exploring the nature of the vibration part of each instrument according to the Hornbostel-Sachs classification system, we can describe some of the mechanical properties and see how they differ between instruments of different types.
+These differences are key to providing a set of features which allow a neural network to differentiate between classes of instruments \cite{Liu,Zhang}.
+
+\paragraph*{}The design of the neural function that we have constructed combines two architecture types by using two distinct entry arrays which are processed, and a single output is formed.
+Thus type of neural network is referred to as a \textit{multimodal} nueral network \cite{Li,Ngiam}.
+
+\paragraph*{}\textcolor{red}{This is not my best into to date}
 
@@
 We can model this behavior by some unknown function $F$ and approximate it with the function $F^*$.
-This can map the contents of a sound file to a potential source as to mimic $F$.
+This can map the contents of a sound file to a potential source as to mimic the behavior of $F$.
 For a set of inputs (called features or predictors) $\vec{x} = \big\{ x_0 , x_1 , x_2 , ...
@@
 (\ref{subsec-NerualNetworkIntro}) and (\ref{subsec-NetworkStructure}), we introduce the nature and structure of a neural network and how it can use used in part to solve this problem.
-We discuss it's inspiration from a biological brain, and show how different layers of the neural network compare to functions or processes in the brain.
+We discuss it's inspiration from a biological brain,and show how different layer types are influenced from the brain's functions as well as how they are used in this problem.
 
@@
 
-\paragraph*{}In order to train the Multimodal neural network to identify musical instrument sources, we need a suitable data set to present to the model as training data.
-University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \textcolor{blue}{Citations!}.
+\paragraph*{}In order to train the neural network to be able to identify musical instrument sources, we need a suitable data set to present to the model as training data.
+University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files (See acknowledgments).
 These files contain short segments of musical instruments performing a single note, and is labeled according to the instrument that produced the sound.
@@
 
-\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 16 bit depth.
+\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 24-bit depth.
 This ensures that all data will have a consistent format when features are extracted.
@@
 
-\paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of classification features which represent the input given to the neural network.
-These are properties of wave forms that can be represented by a numerical value or several numerical values and are used as the primary tool in classification.
+\paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of predictors or features which represent the raw input given to the model.
+These inputs are designed to represent properties of wave forms that can be expressed by a single or multiple numerical values.
 We detail these features in sec.
@@
 
-\paragraph*{}With the appropriate set of features designed, and the number of outputs determined, we can organize the structure of the neural network function.
-The shape of the network defines the hypothesis space, and a subset of the possible solutions that the trained model could arrive at.
+\paragraph*{}With the appropriate set of features designed, and the number of output categories determined, we can organize the structure of the neural network function.
+The shape of the network defines the flow of information, and the hypothesis space.
+The nature of all possible solutions that the trained model could arrive at is subject to the architecture \cite{Goodfellow,Loy}.
 We construct a multimodal neural network, explored in sec.
 (\ref{subsec-Architecture}), that processes two distinct entry points derived from the same audio sample.
-This network is designed to handle and process each respective input independently, and concatenate the results to produce a single outputted prediction.
+This network is designed to evaluate each input independently, and concatenate the results to produce a single outputted prediction.
 
@@
 
-\paragraph*{}We divide the raw data set up into a training and testing sets.
-We employ a resampling method called cross-validation and compute the results of various performance metrics to ensure that our model is making reliable predictions, and can generalize appropriately.
+\paragraph*{}We execute a K-Folds cross validation algorithm to evaluate the performance of the neural network across overlapping subsets of data.
+This ensures that the model can perform consistently and reliably given small changes in initial conditions.
 In this stage, we also choose the value of hyper-parameters, activation functions and layer widths to best compliment the chosen features.
@@
 
-\paragraph*{}The task of algorithmically matching sound files to musical instrument classes in exceedingly difficult through conventional computer programming techniques.
+\paragraph*{}The task of automatically matching sound files to musical instrument classes is exceedingly challenging through conventional computer programming techniques.
 Because of the complexity of sound recognition, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
 Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an solution that allows for a computer to \textit{learn} from labeled training examples in order \textit{teach} itself \cite{Bishop,Mitchell}.
-One such an algorithm that has been used for this type of task is a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine}.
+We choose to employ a neural network, which a computer algorithm that is designed to update itself to perform a task with increasing proficiency as it is presented with new information \cite{Geron2,Goodfellow,Levine,Mitchell}.
 
@@
 \begin{quote}
-Birds inspired us to fly, burdock plants inspired velcro and nature has inspired many other inventions.
-It seems only logical, then, to look to the brain's architecture for inspiration on how to build an intelligent machine.
+Birds inspired us to fly, burdock plants inspired velcro, and nature has inspired many other inventions.
+It seems only logical then, to look to the brain's architecture for inspiration on how to build an intelligent machine.
 \end{quote}
-The result of such an analogy is a computer program that is reminiscent of the a brain in that the program can \textit{learn} in a sense.
-Where a biological brain uses connections of chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Geron,Levine,Bishop}.
+The result is a computer program that is reminiscent of the a brain in that it structured much like the brain, and can\textit{learn} from new data.
+Where a biological brain uses connections of chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Levine,Bishop}.
+Where a brain uses physical connection of neurons through axons, the nueral network uses mathematical connections of neurons through mathematical operations \cite{Geron,Levine}.
 
@@
 
-\paragraph*{}A neural network can then be considered as mathematical function that seeks to produce an approximation $F^*$, of some the usually unknown function $F$.
-The function $F^*$ uses a set of parameters $\Theta$, to map a series of inputs, $x$ (called \textit{features}) to a series of outputs, $y$ (called \textit{predictions}) \cite{Goodfellow,James,Virtanen}.
-Over the course of their development, humans will be able to learn to match sounds to sources with relative ease, given the appropriate labels.
-In a similar manner, out neural network is present a collection of sound files and predictors and a complementary set of labels indicating the source of each sound.
-
-\paragraph*{}For this particular project, a neural network has been constructed to perform a \textit{classification} task.
-A classification task involves mapping the input data, $x$ to one of $k$ possible \textit{classes}, each represented by an integer, $0$ through $k-1$.
+\paragraph*{}The neural network function $F^*$ uses a set of parameters $\Theta$, to map those inputs, $x$ to outputs, $y$ \cite{Goodfellow,James,Virtanen}.
+It is the process of updating the elements in the object $\Theta$ which allow us to train a neural network to perform the desired task.
+Similarly, it is the process of organizing and connecting neurons in the brain that allow humans to perform any specific task \cite{Geron,Levine}.
+Over the course of their lives, humans will be able to learn to match sounds to sources with relative ease, given the appropriate labels.
+In a similar manner, our neural network is presented a collection of predictors from sound files and a complementary set of labels indicating the source of each sound.
+This type of task is called \textit{classification}, which involves mapping the input data, $x$ to one of $k$ possible \textit{classes}, each represented by an integer, $0$ through $k-1$.
 Each of the $k$ classes represents a particular musical instrument or sound source that could have produced the sound-wave in the audio file \cite{Goodfellow,Loy,Virtanen}.
-In this section we detail the nature of a general neural network.
+In this section, we explore the motivation, structure, and training process of a neural network.
 
@@
 \paragraph*{}A Neural Network is a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Goodfellow,Loy}.
-Each layer represents an operation that takes some real input, typically an array of real double-precision floating-point numbers, and returns a modified array of new double-precision floating-point numbers.
+Each layer represents an operation that takes an input, typically an array of real double-precision floating-point numbers, and returns an output which is a modified array of new double-precision floating-point numbers.
 The exact nature of this operation can be very different depending on the layer type or where it sits within the network.
-The output of one layer is passed forward and used as the input for the next layer.
+Typically, a neural network is characterized by a chain-like structure where the output of one layer is fed directly into the input of the next layer \cite{Geron,Goodfellow}.
 It is this process of transforming inputs successively in a particular order until an output is attained that makes up the core functionality of a neural network \cite{Geron,Loy}.
@@
 \paragraph*{}Other than inspiration from the brain, Neural Networks are named \textit{networks} due to their successive chained or nested composition nature.
-A standard representation of a neural network is often a linked list or computational graph structure.
+A standard representation of a neural network is often a linked list or computational graph structure \cite{Goodfellow}.
 This maps out exactly how the repeated compositions are structured and organizes the flow of information in more complicated networks.
 Each node in the computational graph represents a \textit{layer}, which executes a particular prescribed mathematical function \cite{Goodfellow}.
-In the case of a \textit{linear, feed-forward} network, information passes in a single direction, to produce an output.
+In the case of a \textit{linear, feed-forward} network, such as the one that we implement, information passes in a single direction to produce an output.
 We can represent this as a graph:
@@
 F^*(x) = x \rightarrow f^{(0)} \rightarrow f^{(1)} \rightarrow ..... \rightarrow
-f^{(L-2)} \rightarrow f^{(L-1)} \rightarrow y
+f^{(L-2)} \rightarrow f^{(L-1)} \rightarrow y^*
 \end{equation}
@@
 \label{eqn-FunctionChain}
-F(x) = f^{(L-1)}\big[f^{(L-2)}\big[...f^{(1)}\big[f^{(0)}\big[x]\big]\big]...\big]\big]
+F^*(x) = f^{(L-1)}\big[f^{(L-2)}\big[...f^{(1)}\big[f^{(0)}\big[x\big]\big]\big]...\big]\big] = y^*
 \end{equation}
@@
 (\ref{eqn-altLayerFunction}), each function feeds directly into the next as to form a chain-like computational graph \cite{Goodfellow}.
-Many layer functions can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation.
-This activation function typically is a non-linear function which allows for the modeling of increasingly complex decision-boundaries \cite{Geron,Loy}.
+There are multiple type of layers that we use to construct the network in this project, but the two most important are called a \textit{dense} layer and a \textit{convoltuion} layer.
+These layers each contain a set of parameters which makeupa  subset of the trainable elements in $\Theta$.
+These two layer functions can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation.
 The Linear transformation can be given by Eq.(\ref{eqn-LinearTransform}) in the case of a 1D Dense layer (\ref{subsubsec-DenseLayer}) or Eq.
@@
 Where $W^{(l)} x^{(l-1)}$ denotes a matrix-vector product, and $\big(W^{(l)} * x^{(l-1)}\big)$ denotes a convolution product.
-In both cases, $W^{(l)}$ is the \textit{weighting-matrix} or \textit{weighting-kernel} for layer $l$, $b^{(l)}$ is the \textit{bias-vector} for layer $l$, $z^{(l)}$ are the \textit{linear-activations} for layer $l$ and $x^{(l-1)}$ is the final activations for layer $l-1$.
+In both cases, $W^{(l)}$ is a \textit{weighting-matrix} or \textit{weighting-kernel} for layer $(l)$, $b^{(l)}$ is the \textit{bias-vector} for layer $(l)$, $z^{(l)}$ are the \textit{linear-activations} for layer $(l)$ and $x^{(l-1)}$ is the final activations for layer $(l-1)$.
 
@@
 Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-LinearTransform}).
-$\sigma^{(l)}$ is some activation function which introduces the ability to account for non-linearity in the decision boundaries.
+$\sigma^{(l)}$ is some activation function which introduces the ability to account for complicated non-linear decision boundaries which the neural network uses to make predictions.
 The combination of Eq.
@@
 (\ref{eqn-altLayerFunction}).
-In this, we discuss and describe the types of layer functions that are used to produce the classification model in this project.
+In this section, we detail the types of layer functions that are used to produce the classification model in this project.
 
@@
 A dense layer is composed of a layer of \textit{artificial neurons}, each of which holds a numerical value within it, (usually a double-precision floating point number) called the \textit{activation} of that neuron.
-This idea was developed from McCulloch and Pitts' work \cite{McCulloch} in attempting to model cognitive processes as mathematical functions, and was expanded upon by Frank Rosenblatt in  1957 by combining many dense layers together to form a multilayer perceptron (MLP) \cite{Geron,Loy,Levine}.
-
-\paragraph*{}We model a layer of neurons as a vector of floating-point numbers.
-By convention, the array is an $n$-dimensional column vector, where $n$ is number of nodes in that layer.
-Suppose a layer $(l)$ contains $n$ artificial neurons- we denote the array that hold those activations as $x^{(l)}$ and is given by:
+The activation of a dense layer are given by a linear combination of the layers inputs.
+This idea was developed from McCulloch and Pitts' work \cite{McCulloch} in attempting to model cognitive processes as mathematical functions by connecting neurons through a series of weighting values.
+The idea was expanded upon by Frank Rosenblatt in  1957 by combining many dense layers together to form a multilayer perceptron (MLP), which will make up a portion of the network that we have implemented.
+\cite{Geron,Loy,Levine}.
+
+\paragraph*{}We model a layer of neurons as an array or vector of floating-point numbers.
+Suppose a layer $(l)$ contains $n$ artificial neurons- we denote the $n$-dimensional array that holds those activations as $x^{(l)}$ and is given by:
 \begin{equation}
@@
 We implement a convolutional layer $f^{(l)}$ by creating a series of $K$ weighting matrices, called \textit{filters}, each of size $m \times n$, where $m,n \in \mathbb{Z}$.
-Often we choose $m = n$ and call the shape the \textit{convolution kernel size} \cite{Loy, Goodfellow}.
+Often we choose $m = n$ and we call the shape the \textit{convolution kernel size} \cite{Loy, Goodfellow}.
+The step size in each of the two dimensions is known as the \textit{stride size}, which we choose to be $1$ in both dimensions.
 
 \paragraph*{}In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(M \times N)}$, the convolutions filters "step" through the input data and repeatedly compute the element-wise product of each $m \times n$ weighting kernel, and the local activations of the $x^{(l-1)}$ array.
-The step size in each of the 2-dimension is known as the \textit{stride}.
-Each of the $K$ filters are used to generate a $m \times n$ feature map from the input activation.
+Each of the $K$ filters are used to generate a $m \times n$ feature map from the input activations.
 For an appropriately trained network, some filters may result in detecting vertical lines, horizontal lines, sharp edges, areas of mostly one color, etc.
@@
 
-\paragraph*{}In general, for an $N \times M$ input, with kernel size $m \times n$, with stride size $1 \times 1$, and $K$ feature maps.
+\paragraph*{}In general, for an $M \times N$ input, with kernel size $m \times n$, with stride size $1 \times 1$, and $K$ feature maps.
 \begin{equation}
@@
 \begin{center}
-
 	\begin{subfigure}{0.45\textwidth}
@@
 	\end{subfigure}	
-
 	\begin{subfigure}{0.45\textwidth}
@@
 	\end{subfigure}	
-
 	\begin{subfigure}{0.9\textwidth}
@@
 	\end{subfigure}	
-
 \end{center}
@@
 
-\paragraph*{}For 2D convolution over input $x^{(l-1)}$ with feature map $W^{(l)}_k$, producing activations $x^{(l)}$, we compute the activations $x^{(l)}_{k}$ as \cite{Goodfellow}
+\paragraph*{}For 2D convolution layer $(l)$, given input $x^{(l-1)}$, we compute the activations of the $k$-th filter $x^{(l)}_{k}$ using feature map $W^{(l)}_k$ and bias neuron $b^{(l)}_k$ as \cite{Goodfellow}:
 \begin{equation}
 \label{eqn-ConvFeedForward}
-x^{(l)}_k(i,j) = \sigma^{(l)}\bigg[ \Big( \sum_{u=0}^{m-1} \sum_{v=0}^{n-1} W^{(l)}_k(i,j) x^{(l-1)}_k(i - u,j - v) \Big) + b^{(l)}_k \bigg]
+x^{(l)}_k(i,j) = \sigma^{(l)}\bigg[ b^{(l)}_k +  \sum_{u=0}^{m-1} \sum_{v=0}^{n-1} W^{(l)}_k(i,j) x^{(l-1)}_k(i - u,j - v) \bigg]
 \end{equation}
@@
 
-\paragraph*{}The convolution layers allows for several advantages.
+\paragraph*{}The convolution layers allows for several advantages over the dense layer.
 Among these are (i) \textit{sparse-connectivity}: not every single activation (pixel) is connect to every single output pixel, so it is more computationally efficient, (ii) \textit{positional invariance}: key features can be identified regardless of where they are in the layer, and (iii.) \textit{Automatic feature detection} as the training process will update the filters to identify dominant features in the data without human instruction \cite{Geron,Goodfellow,Loy}.
@@
 
-\FOR {Each feature map, $k \in [0,1,2,...,k-2,k-1]$}
+\FOR {Each feature map, $k \in [0,1,2,...,K-2,K-1]$}
 	\item Evaluate linear activation values by computing the 2D convolution-product of 
@@
 
-\paragraph*{}A Maximum Pooling layers simply returns the maximum neuron activation in a group of neurons.
-In the case of 2D Max Pooling, we choose a kernel size to be $m \times n$, just like in the 2D Convolution layer, and extract the maximum value in each window, and then step along accrdoing to the chosen stride size \cite{Loy,Goodfellow}.As an example, consider again figure (\ref{fig-2DConvExample}a).
+\paragraph*{}A Maximum Pooling layers returns the maximum neuron activation in a two-dimensional group of neurons.
+In the case of 2D Max Pooling, we choose a kernel size to be $m \times n$, similar to the convolution layer, and extract the maximum value in each window, while stepping along according to a chosen stride size \cite{Loy,Goodfellow}.
+Consider an input like in Fig.
+(\ref{fig-2DConvExample}a).
 Using the $2 \times 2$ kernel on the $3 \times 4$ input, each box would then contain the maximum value of the input activations.
@@
 (\ref{fig-2DMaxPool}):
-\begin{figure}[h]
-
-\begin{center}
+\begin{figure}[H]
+	\begin{subfigure}{0.45\textwidth}
+	\includegraphics[scale=0.6]{../figures/2DConvExample(a)}
+	\caption{Input Activations, $x^{(l-1)}$}
+	\end{subfigure}
+	\begin{subfigure}{0.45\textwidth}
 	\includegraphics[scale=0.6]{../figures/2DConvExample(d)}
-\end{center}
+	\caption{Input Activations, $x^{(l-1)}$}
+	\end{subfigure}
 \caption{The result of 2D maximum-pooling an input array. This image was adapted from Loy, pg. 126 \cite{Loy}}
@@
 
-\paragraph*{}Pooling layers, such as maximum pooling, average pooling, or similar are typically placed after a layer or a set of layers of convolution.
-The purpose of this arrangement is to reduce the number of weights, thereby dropping the complexity of the model and ensuring only features with large activation values are preserved \cite{Geron,Loy,Goodfellow}.
-This layer "non-trainable" because it does no use any weights or transformations, only a fixed procedure.
+\paragraph*{}Pooling layers, such as maximum pooling, average pooling, or similar are typically placed after a layer or a set of layers of convolution \cite{Loy}.
+The purpose of this arrangement is to reduce the number of activations by selecting only the largest valus, thereby dropping the width of the model and ensuring only features with large activation values are preserved \cite{Geron,Loy,Goodfellow}.
+This layer "non-trainable" because it does not use any weights or transformations, only a fixed procedure that cannot be updated.
 Below, we detail what the "Call" method for a 2D maximum pooling layer might look like.
@@
 \REQUIRE $m \times n \leftarrow$ Pool height and width
-\REQUIRE $P \leftarrow$ A temporary pool array of shape $m \times n $ to hold local activationbs
+\REQUIRE $P \leftarrow$ A temporary pool array of shape $m \times n $ to hold local activations
 
@@
 		\item $P = x^{(l-1)}[i:i+m,j:j+n]$
-		\item Find maximum valie in $P$, and add to output
+		\item Find maximum value in $P$, and add to output
 		\item $x^{(l)}[i,j] = \max\big( P \big)$
@@
 \paragraph*{}A flattening layer is used to compress an array with two or more dimensions down into a single dimension.
-For a flattening layer $l$, multidimensional activations in layer $l-1$ are rearranged down into a single dimensional array.
-Note that this is not like projecting the data into a lower dimension, but rather is simple the reorganization of values into an array of a single axis.
-We can use function notation to express this as:
+For a flattening layer $(l)$, multidimensional activations in layer $(l-1)$ are rearranged down into an array such that each sample contains only one axis.
+Note that a batch of samples will still be two-dimensional.
+This is not like projecting the data into a lower dimension, but rather is the reorganization of values into an array of a row of column array.
+We can use function notation to express this for a single sample as:
 \begin{equation}
@@
 The numerical value of each activation is left unchanged.
-For a layer with activation shape$N \times M$, the resulting activations are reshaped into $NM \times 1$ as shown in Eq.(\ref{eqn-FlattenFunction}).
+For a layer with activation shape$M \times N$, the resulting activations are reshaped into $MN \times 1$ as shown in Eq.(\ref{eqn-FlattenFunction}).
 
 \paragraph*{}Flattening Layer are most commonly used to prepare activations for entry into dense layer or series of dense layers.
-For example, 2D or 3D images are typically processed with 2D convolution, which may output a 2D or 3D array of activations.
-Those values are then flattened to 1 dimensions, which can then be passed into dense layers for further processing.
+For example, an image may contain two or three dimension, and convolution over it will return two or three dimensional activations per sample.
+Each sample must be compressed into one dimensions so that it can be processed by dense layers.
 This layer also is "non-trainable" because it does no use any weights or transformations, only a fixed procedure.
@@
 
-\paragraph*{}The 1-Dimensional Concatenation Layer, also called 1D-Concat layer takes separate vectors of activations and combines them into a single 1D vector.
+\paragraph*{}The 1-Dimensional Concatenation Layer, also called 1D-Concat layer takes separate arrays of activations and combines them into a single array, while preserving the dimensionality of the sample.
 Consider the layer activations $\vec{a}^{(l-1)}$ and $\vec{b}^{(l-1)}$ with shapes  $1 \times \alpha$ and $1 \times \beta$ respectively.
@@
 The concatenation layer is used to combine activations from two different layers into a single new layer.
-In this case of the model used in the project, we use it to combine the outputs that result from the convolution branch and the perceptron branch tp produce an single aggregated output.
+In this case of the model used in the project, we combine the outputs that result from the convolution branch and the perceptron branch to produce an single aggregated output.
 This process is detailed further in sec.
@@
 
-\paragraph*{}Activation functions are a key parameter in the behavior of neural networks.
-As discussed in sec.
-(\ref{subsec-Training}) a layer function, $f^{(l)}$ is generally composed of a linear transformation, as in Eq.
-(\ref{eqn-LinearTransform}), and then an element-wise activation function as in Eq.
-(\ref{eqn-elementActivation}).
-It is this second step that allows for neural networks to model the incredibly complex decision boundaries that are found in real-world problems \cite{Geron,Loy}.
-In this section, we detail the activation functions used in this classification neural network.
+\paragraph*{}Activation functions are an important factor in the behavior of neural networks \cite{Geron}.
+For the convolution or dense layer, activation functions make up the second transformation step as in Eq.
+(\ref{eqn-elementActivation}) which allows for the neural network to produce non-linear decisions.
+In this section, we detail the activation functions used in this classification model.
 
@@
 \end{equation}
-ReLU is only defined on a real domain. We provide a visualization of the function in Fig. (\ref{fig-ReLU}).
+We provide a visualization of the function in Fig. (\ref{fig-ReLU}).
 \begin{figure}[H]
@@
 
-\paragraph*{}The softmax activation function is commonly used in the output layer of a multi-class classification network, such as the one we implement.
-When softmax acts on a vector or activation, the result a non-negative output vector.
-with an $L_1$ norm of $1$ \cite{Geron,Goodfellow,Virtanen}.
+\paragraph*{}The softmax activation function is commonly used in the output layer of a multi-class classification network, such as the one we implement \cite{Geron,Loy}.
+When softmax acts on a vector of activations, the result a non-negative output vector with an $L_1$ norm of $1$ \cite{Geron,Goodfellow,Virtanen}.
 The $i$-th element in a softmax activation function is given by:
@@
 
-\paragraph*{}This function is almost only used in the output layer of a neural network, and encodes a normalized discrete categorical probability \cite{Loy,Virtanen}.
-For example, if Eq.(\ref{eqn-Softmax}) returns a vector of the form: $[ 0.75 , 0.25]$, we interpret this as a sample having a $75\%$ chance of beloinging to class $0$ and a $25\%$ change of belonging to class $1$.
+\paragraph*{}If Eq.(\ref{eqn-Softmax}) returns a vector of the form: $[ 0.75 , 0.25]$, we interpret this as a sample having a $75\%$ chance of belonging to class $0$ and a $25\%$ change of belonging to class $1$.
+This tool is particularly useful is we are interested in determining the predictive confidence of a network.
+For example, if some if the two largest values in the output vector are very similar in magnitude, then the classifier is likely having a hard time differentiating between those two classes.
 
@@
 Each element in this set may contain hundreds or thousands of parameters, so we represent these indirectly as parameters within their respective layers.
-We choose this notation for $\Theta$ for notation simplicity.
+We choose this representation of $\Theta$ for notation simplicity.
 Note that not all layers have trainable parameters, and activations functions themselves are not trainable, but fixed functions.
@@
 This sample is represented by the feature-vector $x^{(0)}$, with an expected outcome given by the one-hot-encoded vector $y$.
-After the network finishes processing, it's output activations, given by the vector $x^{(L-1)}$, also noted as $y^*$ represents the prediction for the class label.
-For a reasonably trained model, we expect the vector $y^*$ to be "similar" to $y$, indicating that with the provided data, the network has made a reasonably valid prediction.
-Conversely, for an untrained network, $y^*$ is not likely to be "similar" to $y$ at all, indicating that the network has made a poor prediction.
-
-\paragraph*{}To quantify the difference between the model's prediction, $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $J(y^*,y)$, to the model \cite{Goodfellow,James}.
-The cost function, also called a \textit{loss} or \textit{objective} function, compares the neural networks output, $y^*$ and the expected output $y$.
-It returns a single floating-point number which measures the \textit{poorness} of the prediction.
+After the network finishes processing, it's output activations, given by the vector $x^{(L-1)}$, also noted as $y^*$, represents the prediction for the class label.
+For a reasonably trained model, we expect the vector $y^*$ to be "similar" to $y$, indicating that model has made a a reasonable prediction with the given input values.
+Alternatively, for an untrained network, $y^*$ is not likely to be "similar" to $y$ at all, indicating that the model has made a poor prediction with the given input.
+
+\paragraph*{}To quantify the difference between the model's prediction, $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $J(y^*,y)$ \cite{Goodfellow,James}.
+The cost function, also called a \textit{loss} or \textit{objective} function, compares $y^*$ and $y$ to return a single scalar value which measures the quality of the prediction.
 A high cost value indicates a \textit{poor} prediction, and a low cost indicates a reasonable prediction.
-
-\paragraph*{}$J(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}.
+We can generalize this idea to consider that we want a trained neural network to produce a consistently low cost function value across samples in a data set.
+
+\paragraph*{}The cost function itself, $J(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}.
 For this $k$-classes classification task, we choose to use the \textit{Categorical Crossentropy} (CXE) cost function.
-For a sample labeled by the one-hot-encoded vector $y$ and corresponding prediction vector $y^*$, the CXE cost for a single sample is given by \cite{Goodfellow,Virtanen,Bishop}:
+For a sample labeled by the one-hot-encoded vector $y$ and corresponding prediction vector $y^*$, the CXE objective value for a single sample is given by \cite{Bishop,Goodfellow,Virtanen}:
 \begin{equation}
@@
 This means that taking the natural log of this value returns a negative number.
-Multiplying that by negative 1 returns a high loss when the activation of $y^*_j$ is low and a low cost when $y^*_j \approx 1$.
+Multiplying that by $-1$ returns a high loss when the activation of $y^*_j << 1$ and a low cost when $y^*_j \approx 1$.
 We visualize this relationship for a single sample in Fig.
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
 \begin{center}
@@
 \end{center}
-\caption{Plot of how $y^*_{j}$ affects the output values of the CXE cost function}
+\caption{Plot of how $y^*_{j} \in [0,1]$ affects the output values of the CXE cost function}
 \label{fig-CXELoss}
@@
 \paragraph*{}By optimizing the parameters $\Theta$ in the network model, we allow for the output of a consistently low cost function to be produced across all samples in the data set.
-When a model produces consistently low cost values across new unseen samples, we consider this to be a \textit{trained} or \textit{fitted} model \cite{Goodfellow,Loy,Mitchell}.
+When a model produces consistently low cost values across new unseen samples, this means that $y^* \approx y$ and we consider this to be a \textit{trained} or \textit{fitted} neural network \cite{Goodfellow,Loy,Mitchell}.
 
@@
 \paragraph*{}We have developed a method for quantifying the difference between a given output $y^*$ and an expected output $y$ with the inclusion of a cost function.
-For a trained neural network, we expect that samples consistently produce a low cost value, particularly on previous unseen inputs, which indicates that the model has appropriately \textit{generalized} \cite{James,Loy}.
-The process of training the model is to choose the parameters in $\Theta$ that allows for this behavior of the cost function.
-We then treat the training process of a neural network as a higher dimensional \textit{optimization} problem \cite{Goodfellow}.
-
-\paragraph*{}A neural network uses \textit{indirect optimization}, which contrasts from pure optimization. Deep Learning expert Ian Goodfellow describes the difference \cite{Goodfellow}:
+The process of training the model is to choose the parameters in $\Theta$ that allows for consistently low values of the cost function.
+We then treat the training process of training a neural network as a high dimensional \textit{optimization} problem.
+A neural network uses \textit{indirect optimization}, which contrasts from pure optimization.
+Deep Learning expert Ian Goodfellow describes the difference \cite{Goodfellow}:
 \begin{quote}
@@
 \end{quote}
-By choosing an appropriate cost function, and selecting the parameters $\Theta$ that minimize the average cost over a data set, we also assume that doing so minimizes classification error and maximizes the performance $P$.
-
-\paragraph*{}The cost of a sample is dependent on training labels $y$ and the network output $y^*$.
+By choosing an appropriate cost function, and selecting the parameters $\Theta$ that minimize the average cost over a data set, we assert that $y^* \approx y$, but can only assume that doing so minimizes classification error and improves the performance metrics.
+
+\paragraph*{}The cost value of a sample is dependent on the relationship between training labels $y$ and the network output $y^*$.
 The output is given by the final layer activation $x^{(L-1)}$, which in turn are produced by the previous layer and so forth, as demonstrated in Eq.
 (\ref{eqn-altLayerFunction}), This recursive nature combined with the dimensionality of the parameter object $\Theta$ makes an analytical solution to the optimization impractical \cite{Geron,Goodfellow,James}.
-We instead optimize the cost function with a numerical \textit{iterative} method \cite{Loy}.
-
-\paragraph*{}We can reduce the cost given a set of parameters, $J(\Theta)$, by repeatedly moving each element in $\Theta$ with small steps in the direction of the negative partial derivative with respect to each parameter.
-In the case of the high-dimensional $\Theta$ object, we compute the partial derivative with respect to each weight and bias in the form of the \textit{gradient vector}.
-We denote the gradient of $J$ with respect to the parameters in $\Theta$ as:
+We instead optimize the cost function with a numerical iterative method called \textit{gradient descent} \cite{Loy}.
+
+\paragraph*{}We can reduce the cost given a set of parameters, $J(\Theta)$, by repeatedly stepping each element in $\Theta$.
+We step each element acording to the direction and manitude of each element in a gradient vector, $\nabla_\Theta J$, which is the gradient of the cost function with respect to each parameter in $\Theta$.
+We express the gradient of $J$ with respect to the parameters in $\Theta$ as:
 \begin{equation}
@@
 Where $\frac{\partial J}{\partial W^{(l)}}$ is taking the partial derivative of each element $W_{i,j}$ in the $W^{(l)}$ matrix, and preserves the shape.
-While there may only be $20$ or so layers, the gradient vector actually has one element for every trainable parameter in all of the layers.
+While there may only be $20$ or so layers, the gradient vector actually has one element for every trainable parameter in the $\Theta$ object.
 This means that for our network, the gradient vector contains upwards of $33,000$ elements.
@@
 (\ref{eqn-altLayerFunction}).
-Additionally, we recall that each layer with trainable parameters is made up two steps which produce linear activations such as in Eq.
+Additionally, we recall that each layer with trainable parameters is made up of two steps which produce linear activations such as in Eq.
 (\ref{eqn-LinearTransform}) and non-linear activations, as in Eq.
@@
 Consider a simplified neural network model visualized in Fig.
-(\ref{fig-ComputationalGraph})
-
-\paragraph*{}Note that we indicate the cost as $J(\Theta)$.
-This is an allusion to the fact that $J$ depends of both the labels $y$, and the predictions $y^*$.
-Where $y^*$ is a function of all of the previous layer activation, which are in turn functions of each weight bias element, i.e.
-the contents of the $\Theta$ object, in Eq.
-(\ref{eqn-Theta}).
-This is why we are able to compute the gradient with respect to $\Theta$ as in Eq.
-(\ref{eqn-CostGradient}).
+(\ref{fig-ComputationalGraph}).
+Note that we indicate the cost as $J(\Theta)$.
+This is alluding to the fact that $y^*$ is ultimately a function of the parameters in $\Theta$.
 
 \paragraph*{}Raw information is presented as $x^{(0)}$ at the top of the figure, and and output is returned as $x^{(L-1)}$ at the bottom.
-Arrows represent the flow of information.
-As expressed in Eq.
-(\ref{eqn-CXELoss}), we compute the cost of a sample, or batch of samples by comparing the difference between $y^*$ (which is $x^{(L-1)}$) and $y$.
-Given this graph chain and it's numerical nature, we cannot compute each element in the gradient vector through conventional symbolic calculus \cite{Loy}.
-We must instead use the chain rule for partial derivatives to begin at the final output of the network and successively work our way forward to the entry layer to compute the numerical derivative with respect to each parameter.
+(Recall $y^* = x^{(L-1)}$) Arrows represent the flow of information in the network.
+Because of the nested computation nature of the graph, we use the chain rule for partial derivatives to begin at the final output of the network and successively work our way forward to the entry layer.
+At each step, we compute the numerical derivative with respect to the parameters in each layer.
 This process is called \textit{back-propagation} \cite{Geron,Goodfellow}.
@@
 
-\paragraph*{}Suppose we then wish to compute the elements of $\frac{\partial J}{\partial W^{(l)}}$ and $\frac{\partial J}{\partial b^{(l)}}$.
+\paragraph*{}Suppose we then wish to compute the elements of $\frac{\partial J}{\partial W^{(l)}}$ and $\frac{\partial J}{\partial b^{(l)}}$ for any layer $(l)$.
 Using the same graph from Fig.
@@
 
-\paragraph*{}After (i) computing the gradient, we can scale it by a desired learning rate $\alpha$, and (ii) add the gradient vector element-wise to the existing elements in $\Theta$ object.
+\paragraph*{}After (i) computing the gradient, we can scale it by a desired learning rate $\alpha$ wich controls the size of the gradient step in each component, and (ii) add the gradient vector element-wise to the existing elements in $\Theta$ object.
 By repeating steps (i) and (ii) in succession, we gradually drive the cost function to produces consistently lower and lower values across a data set \cite{Geron}.
@@
 We show the general update rule on iteration $(i)$ for gradient based learning in Eq.
-(\ref{eqn-GradientLearning}).
+(\ref{eqn-GradientLearning}) \cite{Geron,Goodfellow}.
 \begin{equation}
@@
 \subsubsection{The Optimizer}
-
-\paragraph*{}An optimizer is the algorithm or procedure that is used by a machine learning model to perform the optimization task and seeks to achieve the lowest possible value of the cost function over a data set \cite{Geron}.
-Regression models my often used a \textit{mean-squared error} cost function which can often be solved analytically, while high dimensional neural networks, such as the one used in this project, outlined in sec.
+\label{subsubsec-Optimizer}
+
+\paragraph*{}An optimizer is the algorithm or procedure that is used by a machine learning model to perform the optimization task to reduce the cost value after reciveing each new training sample.
+Regression models may often used a \textit{mean-squared error} cost function which can often be solved analytically, while high dimensional neural networks, such as the one used in this project, outlined in sec.
 (\ref{subsec-Architecture}), can only up updated iterativly \cite{Goodfellow,James,Loy}.
-We employ an iterative gradient-based method, much like the one in Eq.
+We use a variation of gradient descent much like the one in Eq.
 (\ref{eqn-GradientLearning}).
-These standard gradient-based learning algorithms are cumbersome and often prone errors such as vanishing or exploding gradients \cite{Geron,Goodfellow,Loy}.
-To combat this, model must often implement an algorithm that is more stable, and robust in it's ability to drive the cost function to a successively lower value.
-
-\paragraph*{}For this project, we employ an \textit{Adaptive-Moments} optimization algorithm, also called \textit{ADAM} for short.
-It is a powerful optimizer that uses an adaptive learning rate and momentum parameter.
-ADAM tracks an exponentially decaying average of past gradients, $s^{(i)}$, and an exponentially decaying average of past squared gradients, $r^{(i)}$ in Eq.
-(\ref{eqn-ADAMupdate}))\cite{Geron}.
-This produces a far more aggressive optimizer at a higher computational cost than standard gradient descent.
-
-\paragraph*{}As the cost function iterates through each step, the effect will tend to "snowball".
+A standard stochastic gradient-based or batch gradient descent learning algorithm can be fast, but are often prone errors such as vanishing or exploding gradients \cite{Geron,Goodfellow,Loy}.
+To combat this, model must often implement an optimizer that is more stable, and robust in it's ability to drive the cost function to a successively lower value.
+
+\paragraph*{}For this project, we employ an \textit{Adaptive-Moments} optimizer, also called \textit{ADAM} for short.
+This is a powerful algorithm that uses an adaptive learning rate and built-in momentum parameter.
+ADAM records and updates an exponentially decaying average of past gradients, $s^{(i)}$, and an exponentially decaying average of past squared gradients, $r^{(i)}$ in Eq.
+(\ref{eqn-ADAMupdate}) \cite{Geron}.
+This produces a far more aggressive optimizer at a higher computational cost than standard gradient descent \cite{Goodfellow}.
+
+\paragraph*{}As the optimizer iterates through each step, the effect of past iterations will tend to "snowball".
 If the previous step was found to reduce the cost function by a large or small amount, the step size for the previous step will update accordingly.
 This enables to ADAM to overcome smaller discontunities that may arise in the solution space \cite{Goodfellow}.
-Note that a superscript $(i)$ or $(i-1)$ gives an iteration index, while the superscript $i$ means to raise a value to the power of $i$.
 For a given step $(i)$, The ADAM update is given:
@@
 \end{equation}
-
-\paragraph*{}ADAM has experimentally shown to be a very powerful and robust optimizer useful for a wide range of tasks \cite{Goodfellow}.
+Note that a superscript $(i)$ or $(i-1)$ gives an iteration index, while the superscript $i$ means to raise a value to the power of $i$.
+ADAM has experimentally shown to be a very powerful and robust optimizer useful for a wide range of tasks \cite{Goodfellow}.
 Because of the two decay constants $\rho_1$ and $\rho_2$, we can compound and accumulate the values of past gradients to continue to push the cost to lower and lower values, even if the magnitude of the gradient becomes very small \cite{Geron}.
@@
 \begin{algorithm}[H]
-\caption{Adaptive-Moments (ADAM) optimizer for a neural network. This algorithm is adapted from Goodfellow, \cite{Goodfellow}}
+\caption{Adaptive-Moments (ADAM) optimizer for a neural network. This algorithm is adapted from Goodfellow \cite{Goodfellow}}
 \label{alg-ADAM}
@@
 
-	\item Compute And Apply update:	$\Delta \Theta = (-\alpha) \frac{s'}{\sqrt{r'} + \delta}$
-	\item $\Theta = \Theta + \Delta \Theta$	
+	\item Compute And Apply update:	$\Delta \Theta \leftarrow (-\alpha) \frac{s'}{\sqrt{r'} + \delta}$
+	\item $\Theta \leftarrow \Theta + \Delta \Theta$	
 	\item Update Iteration number: $i \leftarrow i + 1$
@@
 Since modalities are \textit{different} by nature, we cannot simply combine them into a single object and present the neural network with it.
-We must account for the difference by provide two distinct input layers.
+We must account for the difference by providing two distinct input layers.
 Modalities of seeing and hearing are captured by two different senses but ultimately processed by the same brain to produce a single prediction.
@@
 \paragraph*{}The spectrogram branch is pictured on the left side of Fig.
-(\ref{fig-NetworkArchitecture}).
+(\ref{fig-NetworkArchitecture}), and is an implementation of a \textit{convolutional neural networl} (CNN).
 A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olson,Khan}.
 The input layer of the spectrogram accepts a 4-Dimensional array.
-The axes, in order of indexing, represents (i) the size of the \textit{mini-batch} of samples, (ii) the pixel width of each sample, (iii) the pixel height of each sample, and (iv) the number of channels in the image.
-For this model, we have selected to use $64$ samples per batch, $558$ pixels in width, $256$ pixels in length, and $1$ gray-scale channel.
+The axes, in order of indexing, represents (i) the size of the \textit{mini-batch} of samples, (ii) the pixel height of each sample, (iii) the pixel wifth of each sample, and (iv) the number of channels in the image.
+For this model, we have selected to use $64$ samples per batch, $558$ pixels in height, $256$ pixels in width, and $1$ gray-scale channel.
 We denote the 4D shape of the design matrix for this branch as:
@@
 
-\paragraph*{}After the input layer holds store the input activations, $X_1$ and tests for the appropriate shape, the array which is a collection of $64$ spectrograms, is passed into the first of three \textit{Convolution Layer Groups}.
+\paragraph*{}The input layer holds the input activations, $X_1$, which is a collection of $64$ spectrograms.
+The output of the the input layer is passed into the first of three \textit{Convolution Layer Groups}.
 These layer groups are inspired from the \textit{Visual Geometry Group-16 Neural Network} architecture \cite{Goodfellow,Loy}.
@@
 \end{enumerate}  
-The Convolution layers convolve over the middle two axes of the data. This corresponds to convolving as weighting kernel over the time and frequency axes.
+The convolution layers iterate over the middle two axes of the data, see sec.
+(\ref{subsubsec-Conv2DLayer}).
+Physically, this allows us to search through the frequency and time axes to detect dominant features or shapes.
 
 \paragraph*{}By grouping layers in this structure, we use convolution to reduce the number of features, and then the pooling layer to extract only the largest activations of the remaining values.
-This drastically reduces the width of each layer before passing the activations down, and ensures that only the dominant features and characteristic shapes are preserved and passed into the next layer set for processing.
+This drastically reduces the width of each layer before passing the activations down, and ensures that only the pertinent characteristic shapes are preserved and passed into the next layer set for processing.
 This also allows for positional invariance in features.
@@
 
-\paragraph*{} The Perceptron branch is pictured on the right side of Fig.
-(\ref{fig-NetworkArchitecture}), notice that it is considerably smaller in depths and complexity than it's neighbor.
-Rather than accept an image-like input, the perception simply takes a $1 \times p$ vector-like input of properties that are derived from the audio file.
-We call these properties \textit{features} \cite{Geron,Khan,Serizel}.
-Details on the natures and selectiosn of these $p$ elements are found in sec.
+\paragraph*{}The perceptron branch is pictured on the right side of Fig.
+(\ref{fig-NetworkArchitecture}) and is an implementation of a \textit{multilayer percepton neural network} (MLP).
+Rather than accept an image-like input, the perception simply takes a $p$-dimensional vector-like input of properties that are derived from the audio file.
+We call these properties \textit{features} or \textit{predictors} \cite{Geron,Khan,Serizel}.
+Details on the natures and selections of these $p$ elements are found in sec.
 (\ref{subsec-TimeFeatures}) and sec.
@@
 A design matrix is scaled by taking all samples in a column (a particular feature from each class), subtracting the average, and then scaling it such that it has unit variance \cite{Geron,James}.
-This ensures that no one feature dominates the performance of the model and that layer activations to not get saturated as data progresses through the network.
+This ensures that no one feature dominates the performance of the model and that layer activations do not get saturated to extremes as data progresses through the network.
 
@@
 
-\paragraph*{}The last layer in each of the two branches is a ReLU-activated Dense layer containing 64 neurons, represented by a $1 \times 64$ vectors.
-We combine these model layers by using a \textit{concatenation layer} to fuse the two column vectors together, "vertically", such that the result is a $1 \times 128$ vector.
+\paragraph*{}The last layer in each of the two branches is a ReLU-activated Dense layer containing 64 neurons, represented by a $64$ - dimensional vector.
+We combine these model layers by using a \textit{concatenation layer} to fuse the arrays together, such that each sample is given by a $128$-dimensional vector.
 This vector is then transformed into the final dense layer, which uses the softmax activation, and encodes the joint predictions based on contributions of both model branches.
-Again, compare this the the concept of two different bodily senses detecting the same object or environment.
-Information is produced from a single sources, received through multiple senses, but ultimately those experiences are combined in a such a way to produce a single prediction label.
+In sec.
+(\ref{sec-Results}) we explore how the predictive power of the network changes when examining the performance of each individual branch compared to the hybrid model.
 
@@
 
-\paragraph*{}Computer algorithms such are neural networks are build to handle exclusively quantitative information \cite{Geron}.
+\paragraph*{}Since computer algorithms such are neural networks are built to handle exclusively quantitative information, we must ensure that each property can be represented by a numerical quantity \cite{Geron,Levine}.
 Where a human would use qualitative adjectives such as \textit{bright} or \textit{harsh} or \textit{percussive} to describe sound, computers require a numerical descriptor instead.
@@
 These categories are (i) idiophones, (ii) membranophones, (iii) chordophones, and (iv) aerophones.
-In this section, we explore the mechanical properties of each group and show how the physics of the source instrument influences our feature choice.
+In this section, we show how the physics of the source instrument influences some of our feature choices.
 
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Vibraphone-A5}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Vibraphone-A5}
 	\caption{Vibraphone playing $A5$}
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Marimba-C2}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Marimba-C2}
 	\caption{Marimba playing $C2$}
 	\end{subfigure}
-\caption{Spectrogram representation of idiophone waveforms}
+\caption{Spectrograms from idiophone waveforms}
 \label{fig-PropertiesIdiophones}
@@
 (\ref{fig-PropertiesIdiophones}).
-When an idiophone is struck, all of the energy for the vibration is delivered up front, and this the amplitude of the waveform can only decay.
+When an idiophone is struck, all of the energy for the vibration is delivered up front, and the amplitude can only decay.
 This gives the resulting transient a very short attack time, followed by a short decay, sustain, and often long release as the last of the energy dies out \cite{White}.
-While other instruments sch as plucked strings like guitars show similar response, this is a very important property of many idiophones.
-Notice additionally, that the energy of the higher overtones die out very quickly in each spectrogram, and only the lowest pitch - the fundamental is preserved for much of the duration.
+While other instruments such as plucked strings like guitars show similar response, this is a very important property of many idiophones.
+Notice that the energy of the higher overtones die out very quickly in each spectrogram, and only the lowest pitch - the fundamental is preserved for much of the duration.
 
@@
 More specifically, the energy in some section $q_i$ should be greater than the energy in any subsequent section $q_{i + n}, n \in \mathbb{Z}$.
-Having this property does not guarantee the source is an idiophone but can we can reasonable state that most idiophones follow this behavior.
+Having this property does not guarantee the source is an idiophone but can we can state within reason that most idiophones obey this behavior.
 In addition to the amplitude envelope, we can consider the distribution of time-space energy in the form of a single scalar quantity as the center of mass.
@@
 
-\paragraph*{}Additionally, we model the tight elastic membrane very similarly as that of a tight elastic string, except in two dimensions \cite{White}.
-However, the partials for the membrane are not related by integer multiples like that or strings are.
-This lack of harmonic structure leaves most membranophones to have a sort of "muddled" frequency spectrum where we see a continuous distribution of constituent frequencies arise as opposed to clean overtones arising as in stringed or wind instruments \cite{White,Olson}.
-This is in part why many membranophones have a much more "percussive" sound as opposed to performing any distinct note.
+\paragraph*{}We model the tight elastic membrane very similarly as that of a tight elastic string, except in two dimensions \cite{White}.
+Unlike the chordophone sec.
+(\ref{subsec-chordophones}), the partials for the membrane are not related by integer multiples.
+This lack of harmonic structure leaves most membranophones to have a sort of "muddled" frequency spectrum where we see a more continuous distribution of constituent frequencies arise as opposed to clean integer related overtones \cite{White,Olson}.
+This partly why many membranophones have a much more "percussive" sound as opposed to performing any distinct note.
 
@@
 We commonly model a chordophone as having a string of length $L$, with a constant linear mass density, $\mu$, subject to a tension force $F_T$.
-The string is flexible, and free to vibrate in a single dimension.
+The string is flexible, and free to vibrate in a spatial single dimension, $x$.
 We describe the state of string over space and time with a function $U(x,t)$.
@@
 Where $v$ is the wave propagation velocity, given by $\sqrt{\frac{F_T}{\mu}}$.
-D'Alembert's equation indicates that the acceleration of any point on a string is directly proportional to the rate of change of the slope of the string at that point.
+D'Alembert's equation indicates that the acceleration of any point on a string is directly proportional to the rate of change of the slope of the string at that point \cite{Taylor}.
 
@@
 For example, for plucked stringed instruments, $f(x)$ may appear to be as triangle-like function, with a peak at some position $0 < x_0 < L$ where then string was struck.
-It is these initial conditions that allow for the drastically different timbres that arise in the wave forms.
+It is these initial conditions that allow for the drastically different timbres that arise in the wave forms \cite{Hunter}.
 Compare the spectrogram representation of a few stringed instruments in Fig.
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/CELLO-F4}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/CELLO-F4}
 	\caption{Violoncello playing $F4$}
 	\end{subfigure}
+	\hfill
 	\begin{subfigure}{0.45\textwidth}
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Guitar-B2}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Guitar-B2}
 	\caption{Guitar playing $B2$}
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Violin-G4}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Violin-G4}
 	\caption{Violin playing $G4$}
 	\end{subfigure}
+	\hfill
 	\begin{subfigure}{0.45\textwidth}
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Viola-G4}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Viola-G4}
 	\caption{Viola playing $G4$}
 	\end{subfigure}
-\caption{Spectrograms for a few Stringed instruments}	
+\caption{Spectrograms from chordophone waveforms}	
 \label{fig-PropertiesChordophones}
@@
 
-\paragraph*{}Despite these differences, the wave equation is still a \textit{linear} partial differential equation which allows for a linear combination of solutions to form a sound wave.
+\paragraph*{}The wave equation is a \textit{linear} partial differential equation which allows for a linear combination of solutions to form a sound wave.
 In the case of the taught finite string that is fixed at both ends, such a guitar, viola or cello, the a solution tends to take the form of a sine or cosine function \cite{Hunter, Taylor, White}.
+Notice the terms arise by the many a parallel yellow and orange lines in each spectrogram in Fig.
+(\ref{fig-PropertiesChordophone}).
+The verical position of any line is given by the linear frequency of the sinusoid, and the brightness is proportional to the coefficient of the combination.
 The boundary conditions, and most forms of standard initial conditions allow for the each sinusoidal to fit exactly an integer or half-integer number wavelengths into the region $0 \leq x \leq L$ \cite{Haberman,Hunter}.
@@
 
-\paragraph*{}It is worth noting at each string instrument do produce a slightly different frequency spectrum, hence each provides a slightly different timbre to the listener, so differentiating between them is difficult, but possible.
+\paragraph*{}Each chordophone instrument does produce a slightly different frequency spectrum, hence each provides a slightly different timbre to the listener, so differentiating between them is possible.
 Because of this, we find that the spectrogram representation of the waveform is so critical to classification success because the convolution layers allow for the detection of small variations in the frequency-time domain where humans would otherwise be unable to \cite{Loy,Virtanen}.
@@
 \paragraph*{}Notice as well in the spectrograms of Fig.
-({fig-PropertiesChordophones}), how the transient response (the time domain) of chordophones differs wildly from idiophones and membranophones.
+(\ref{fig-PropertiesChordophones}), how the transient response (the time domain) of chordophones differs wildly from idiophones and membranophones.
 In the case of bowed instruments, the attack of the stringed instrument is much longer, with a much more gradual sustain decay, and release.
 Where an idiophone or plucked string has all of the time-domain energy up front, the bowed string waveform continues to build energy as the instrument is bowed, and only loses energy once the bowing stops, and the string is left to vibrate by itself \cite{Hunter}.
-This causes a bowed stringed instruemnt to present a very different amplitude envelope compared to the other categories of instruments, and a much more centrally located temporal center of mass.
+This causes a bowed stringed instruments to present a very different amplitude envelope compared to the other categories of instruments, and a much more centrally located temporal center of mass.
 
@@
 \paragraph*{}An aerophone is a musical instrument that produces sounds through the vibration of an air molecules in a column-like structure.
-This is the largest category of instruemnts that we have, and is commonly broken down into smaller subcategories such as \textit{woodwind} and \textit{brass} instruments.
+This is the largest category of instruments that we have, and is commonly broken down into smaller subcategories such as \textit{woodwind} and \textit{brass} instruments.
 From our data set - alto flutes, alto saxophones, bass clarinets, bass flutes, bassoons, $B\flat$ clarinets, contrabassoons, $E\flat$ clarinets, English horns, flutes, oboes, tenor saxophones, and soprano saxophones are all examples of woodwind aerophones.
@@
 
-\paragraph*{}Aerophones all produce sound by exciting molecules of air within a column that vibrate in different patterns called \textit{modes} \cite{White}.
-The nature of modes are determine by the structure of the instruments.
+\paragraph*{}Aerophones all produce sound by exciting molecules of air within a column that vibrates in different patterns called \textit{modes} \cite{White}.
+the wavelength and energy of each mode is  determined by the structure of the instruments, and the actions of the player.
 Most aerophones such a flutes, clarinets, and saxophones are more much more reminiscent of air columns that are closed at one end and open at the other.
-The is marked by the presence of a mouth piece at one end where a played blows air fro their lungs to add energy, and a bell at the other end to serve as an amplification structure \cite{Olson}.
-For a column of length $L$, that is open at one end, the fundamental frequency is given by \cite{Olson}:
-\begin{equation}
+This is marked by the presence of a mouth piece at one end where a played blows air from their lungs to add energy, and a bell at the other end to serve as an amplification structure \cite{Olson}.
+For a column of length $L$, that is open at one end, the fundamental frequency of the vibration is given by \cite{Olson}:
+\begin{equation}
+\label{eqn-OpenClosedCol}
 f_0 = \frac{v}{4L} = \frac{v}{\lambda}
@@
 where $v$ is the velocity of sound in the medium, and $\lambda$ is the wavelength of the sound wave.
-This is the lowest pitch that such an instrument can play.
-Lower woodwinds such as bass clarinets, have a much longer vibrating air column that that of the short piccolo.
+Eq.
+(\cite{eqn-OpenClosedCol}) gives the lowest pitch that such an instrument with a length $L$ can play.
+Lower woodwinds such as bass clarinets, have a much longer vibrating air column that that of the much shorter piccolo, thus can produce considerably lower notes.
 
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/AltoSax-A4}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/AltoSax-A4}
 	\caption{Alto Saxophone playing $A4$}
 	\end{subfigure}
+	\hfill
 	\begin{subfigure}{0.45\textwidth}
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Clarinet-Gs5}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Clarinet-Gs5}
 	\caption{$B\flat$ Clarinet playing $G\sharp 5$}
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Oboe-Bb4}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Oboe-Bb4}
 	\caption{Oboe playing $B\flat 4$}
 	\end{subfigure}
+	\hfill
 	\begin{subfigure}{0.45\textwidth}
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Bassoon-D4}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Bassoon-D4}
 	\caption{Bassoon playing $D4$}
 	\end{subfigure}
-\caption{Spectrograms for a few Stringed instruments}	
+\caption{Spectrograms from woodwind aerophone waveforms}	
 \label{fig-PropertiesAerophonesWind}
@@
 \paragraph*{}In addition to the woodwind instruments described above , we also consider the properties of brass aerophones.
-As the name implies, brass instruments are usually made of interconnected hollow tubes of brass.
-as opposed to linear columns of mostly wood.
-brass instruments are also modeled as open-closes columns that vibrate which are again shortened and lengthened by pressing keys.
+As the name implies, brass instruments are usually made of interconnected hollow tubes of brass as opposed to linear columns of mostly wood.
+Brass aerophones are also modeled as open-closed columns that vibrate and are also shortened and lengthened by pressing keys.
 Brass instruments are generally much longer than woodwinds, and produce sounds at a generally greater volume \cite{Olson}.
-Despite these differences, brass instruments do generally display a great deal of similarities with wood winds, as we can see in Fig.
+Despite these differences, brass instruments do generally display a great deal of similarities with wood winds, as shown in Fig.
 (\ref{fig-PropertiesAerophonesBrass})
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/FRENCHHORN-Cs4}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/FRENCHHORN-Cs4}
 	\caption{French horn playing $c\sharp 4$}
 	\end{subfigure}
+	\hfill
 	\begin{subfigure}{0.45\textwidth}
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/TenorTrombone-F4}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/TenorTrombone-F4}
 	\caption{Tenor Trombone playing $F4$}
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Trumpet-B3}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Trumpet-B3}
 	\caption{$B\flat$ Trumpet playing $B3$}
 	\end{subfigure}
+	\hfill
 	\begin{subfigure}{0.45\textwidth}
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/Tuba-A2}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/Tuba-A2}
 	\caption{Tuba playing $A2$}
 	\end{subfigure}
-\caption{Spectrograms for a few Stringed instruments}	
+\caption{Spectrograms from brass aerophone waveforms}	
 \label{fig-PropertiesAerophonesBrass}
@@
 Aerophones require a user to vibrate air with their lungs which gradually adds energy to the waveform.
-This transfer of energy can take comparably long time, giving aerophones particularity long attack times.
+This transfer of energy can take comparably long time, giving aerophones particularity long attack times when compared to idiophones or membranophones.
 The note is sustained as long as a player is vibrating the air, allowing for any length of decay and sustain, but the energy does out very suddenly when the player stops, giving a characteristically short release time \cite{White}.
@@
 
-\paragraph*{}We group sounds produced from non-physical musical instruments in this final category.
-Form our data set, this category includes the four simplest waveforms, sine waves, sawtooth waves, square waves, and triangle waves, as well as any color noises \cite{White}.
-Since these sounds are only produced synthetically through a MATLAB program, we choose not to include them in the Hornbostel-Sachs grouping above.
-We explore the properties of each of these generated sounds and how they relate to physical instruments.
-
-\paragraph*{}Each of the five synthetically generated waveforms were produce to be constant with all time.
-This means that each waveform has no characteristic amplitude envelope and the spectrogram shows no time-evolution of energy in the waveform.
-Each of the the signals can be composed od a linear combinations of oscillating sinusoidal at various different frequencies and energies.
-For example, a sine wave conists only of a single oscillating term, while a square wave consists of repeated odd harmonics.
+\paragraph*{}We group sounds produced from non-physical musical instruments in this final category because they are not considered in the original Hornbostel-Sachs system.
+From our data set, this category includes the four simplest waveforms begin, sine waves, sawtooth waves, square waves, and triangle waves, as well as white colored noise \cite{White}.
+These sounds have been produced synthetically through a MATLAB program specifically for this project.
+Because of their synthetic nature, they do not display many of the physical or mechanical properties of the previous sections.
+
+\paragraph*{}Each of the five synthetically generated waveform types were produce to have a constant envelope with all time.
+This means that each waveform has no characteristic amplitude shape and the spectrogram shows no time-evolution of energy as expected.
+Each of the the signals can be composed of a linear combinations of oscillating sinusoidal at various different frequencies and energies.
+For example, a sine wave consists only of a single oscillating term, while a square wave consists of repeated odd harmonics.
+White noise consists of a roughly uniform distribution of energy, thus shows no energy evolution in time or frequency space.
 These behaviors can be observed in Fig.
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/SquareWave-880Hz}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/SquareWave-880Hz}
 	\caption{Square Wave at $880$ Hz}
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/SawtoothWave-880Hz}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/SawtoothWave-880Hz}
 	\caption{Sawtooth Wave at $880$ Hz}
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/SineWave-880Hz}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/SineWave-880Hz}
 	\caption{Sine Wave at $880$ Hz}
@@
 	\centering
-	\includegraphics[scale=0.18]{../FiguresSpectrogram/WhiteNoise-190}
+	\includegraphics[scale=0.2]{../FiguresSpectrogram/WhiteNoise-190}
 	\caption{White Noise}
 	\end{subfigure}
-\caption{Spectrograms for a few Stringed instruments}	
+\caption{Spectrograms from synethetically generated waveforms}	
 \label{fig-PropertiesSynths}
@@
 
-These waveform were included to our data set to serve primilarly as a control to understand how the chosen features respond to simple waveforms.
-Additionally, the elementary composition of each waveform allows for it to potentially resemble a wide variety of frequency spectra \cite{White}.
+These waveforms were included to our data set to serve as a control to understand how the chosen features respond to simple waveforms.
+Additionally, the elementary composition of each waveform allows for it to potentially resemble a wide variety of instrument frequency spectra \cite{White}.
 
@@
 \paragraph*{}Classification tasks require a set of inputs called \textit{predictors} or \textit{features} \cite{James,Loy,Serizel}.
-A features is a quantitative, low-dimensional representation of a sample that conveys key characteristics of it.
+A feature is a quantitative, low-dimensional representation of a sample that conveys its important characteristics.
 For example, in classifying types of animals, a feature could be the mass, volume or number of teeth on the animal.
-Typically, we produce a set of features $p$ for each sample and assemble them into a $1 \times p$ vector called a \textit{feature vector} which acts as a list of descriptive qualities of the sample \cite{Geron,James}.
-Audio machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib discusses the vitality of feature selection \cite{Khan}:
+Typically, we produce a set of features $p$ for each sample and assemble them into a $p$-dimensional vector called a \textit{feature vector} which acts as a list of descriptive qualities of the sample \cite{Geron,James}.
+Audio machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib describe the vitality of feature selection \cite{Khan}:
 \begin{quote}
@@
 \end{quote}
-An adequate selection features is vital to the process of training and evaluation of the classifier model \cite{Mierswa,Serizel,Liu}.
-Consider the task of identifying cats and dogs from images, given only the top-most row of pixels or the number of eyes.
-While the data represents \textit{correct} properties, it is not enough information to distinguish the two categories.
+An adequate selection of features is vital to the process of training and evaluation of the classifier model \cite{Mierswa,Serizel,Liu}.
+Consider the task of identifying fish from sharks using only the presence of gills.
+Since both sharks and fish have gills, the features are correct representations, but not useful for discerning them.
+A more appropriate choice would be compare the number of gills that fish or sharks have, which would provide a correct representation and allows for differentiation.
 
@@
 However, a computer representation of a waveform is an array-like structure of values sampled discretely in time and volume \cite{Virtanen,Liu}.
-Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks so we must develop a set of features or predictors that can describe important properties of the waveform in a far more efficient manner \cite{Goodfellow,James,Serizel}.
-
-\paragraph*{}To ensure the construction of a suitable model, we derive features based from three representations of the audio file: (i) a spectrogram matrix representation, (ii) the time-space representation, and (iii) the frequency-space representation.
-It is important to note that although this algorithm will map audio files to source instruments, the model will never actually be presented with a waveform directly, instead it will rely solely on the features to make predictions.
+Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks so we must develop a set of features that can describe important properties of the waveform in a far more efficient manner \cite{Goodfellow,James,Serizel}.
+To ensure the construction of a suitable model, we derive features based from three representations of the audio file: (i) a spectrogram matrix, (ii) the time-space, and (iii) the frequency-space.
+It is important to note that although this algorithm will map audio files to source instruments, it will never actually be presented with a waveform directly, and instead will rely solely on the features to make predictions.
 
@@
 
-\paragraph*{}From each audio file sample, we calculate the same predictors that will be use for classification.
+\paragraph*{}From each audio file sample, we calculate the values for the same predictors.
 The predictors are arranged into two separated structures, each called a \textit{design matrix}, described in sec.
 (\ref{subsubsec-DesignMatrix}) \cite{Goodfellow,Geron}.
-Each sample in the design matrix $X_1$ contains $N \times k$ predictors, and the matrix $X_2$ contains $1 \times p$ predictors.
-For the purposes of exploring the properties of feature space, we consider the $p$ predictors for each sample in $X_2$.
-
-\paragraph*{}Feature space is a $p$ dimensional vector space where each basis vector represents a predictor \cite{Goodfellow,James}.
-Each sample can be described by this $p$-dimensional vector, given by each row of the design matrix $X_2$.
-For samples $x^{(a)}$ and $x^{(b)}$ that belong to the same class, we expect the quantity $||x^{(a)} - x^{(b)}||_{2}$ to be reasonably small, indicating that the two sample lie "close together" in space.
-Similarly, for samples $x^{(c)}$ and $x^{(d)}$ that belong to different classes, we expect the quantity $||x^{(c)} - x^{(d)}||_{2}$ to be comparably large, indicating that the two sample lie "far apart" in space.
-Not that this is an idealization, and not always the defining case for the decision behavior.
+For a model with $p$ predictors, feature space is a $p$-dimensional vector space where each basis vector represents a predictor \cite{Goodfellow,James}.
+Each sample can be described by a $p$-dimensional vector, given by each row of the design matrix $X_2$.
+For samples $x^{(a)}$ and $x^{(b)}$ that belong to the same class, we expect the vector to be similar, $x^{(a)} \approx x^{(b)}$ in some way.
+This indicates that the two samples lie "close together" in space.
+Similarly, for samples $x^{(c)}$ and $x^{(d)}$ that belong to different classes, we expect the vectors to be very different, indicating that the two sample lie "far apart" in space.
+Note that this is an idealization, and not always the defining case for the decision function behavior.
 
 \paragraph*{}We can expand this idea by considering by how features should behave within each class, and between each class.
-Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" about specifically how features must be chosen \cite{Virtanen}:
+Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" about specifically how features should be selected \cite{Virtanen}:
 \begin{quote}
@@
 This is to say, features should \textit{ideally} form non-overlapping groups or bubbles that allows classifiers to effectively differentiate categories.
-Given the complexity of real-world problems, this is an often unrealistic goal \cite{Goodfellow,James}.
-However under the right circumstances, classifiers can still produce parameters that allow for reasonable performance \cite{Geron,Loy}.
+Given the complexity of real-world problems, this is an often unobtainable \cite{Goodfellow,James}.
+Under the right circumstances, classifiers can still produce parameters that allow for reasonable performance \cite{Geron,Loy}.
 In practice, a neural network does not rely on comparing the norms of different samples in feature space, but rather uses something called a \textit{decision boundary}.
@@
 \paragraph*{}A trained classifier makes a prediction in the form of a statistical likelihood of a sample belonging to a particular class \cite{Goodfellow,James}.
-A $k$- categories classifier contains $k$ output neurons, each one representing a class.
+A $k$- categories classifier contains $k$ output neurons, each one representing a different class.
 When a set of features is presented to the classifier, the value contained within each neuron is the "confidence" on the interval $[0,1]$ that a sample belongs to that class.
@@
 Most commonly, we take the neuron with the highest activation value to be the chosen class, even if the next highest activation is a close second \cite{Loy}.
-
-\paragraph*{}This concept stems from the idea that when a trained neural network classifier makes a prediction, it is doing so based on a set of generated \textit{decision boundaries} \cite{Geron,James}.
-To explore decision boundaries, consider a simplified \textit{toy data set} with a 2D feature space for a classifier that must only discern between \textit{Class A} and \textit{Class B}.
-We can visualize each sample in this 2D space, and color-code (and shape-code) each sample according according to it's class label as in Fig.
+Thus the formal prediction function is the index of the maximum value in the output vector.
+
+\paragraph*{}This concept stems from the idea that when a trained neural network classifier makes a prediction, it is basing class probabilities on a set of generated \textit{decision boundaries} \cite{Geron,James}.
+To explore decision boundaries, consider a simplified toy data set with a 2D feature space for a classifier that must only discern between \textit{Class A} and \textit{Class B}.
+We can visualize each sample in this 2D space, and color-code each sample according according to it's class label as in Fig.
 (\ref{fig-LinSep1}).
@@
 belonging to similar Hornbostel-Sachs groups), such well-defined decision boundaries are unlikely to be produced.
-Note also that the examples provided showed only \textit{linear} boundaries, where the inclusion of non-linear activation functions will create far more complex systems in a far higher-dimensional space.
-
-\paragraph*{}From these examples, we conclude the mathematical nature of features allow each sample to be characterized by a vector in $p$-dimensional feature-space\cite{Goodfellow}.
-We expect feature of the same class to exhibit similar behaviors as to allow a trained classifier to develop multiple decision boundaries in the higher-dimensional space \cite{James,Bishop}.
-As a consequence, we derive the predictors from the physical mechanical nature of each instrument or sound-source.
+Note also that the examples provided showed only \textit{linear} boundaries, where the inclusion of non-linear activation functions will create far more complex systems in a far higher-dimensional space \cite{Goodfellow}.
+
+\paragraph*{}From these examples, we conclude the mathematical nature of features allow each sample to be characterized by a vector in $p$-dimensional feature-space \cite{Goodfellow,James}.
+We expect feature of the same class to exhibit similar characteristics, and features of differing classes to exhibit different characteristics.
+This enables a trained classifier to develop multiple decision boundaries in the higher-dimensional space \cite{James,Bishop}.
 
@@
 
-\paragraph*{}Each audio sample is given by an $N \times k$ spectrogram matrix explored in sec.
-(\ref{subsec-Spectrogram}), a $1 \times p$ feature vector, and a target label, $y$ for training purpose.
-As explored in sec.
-(\ref{subsubsec-Decision}), each sample can be associated with a vector in feature-space.
+\paragraph*{}Each audio sample is represented by an $N' \times k$ spectrogram matrix explored in sec.
+(\ref{subsec-Spectrogram}), a $1 \times p$ feature vector, and a  one-hot-encoded target label, $y$.
 In order to efficiently present the information to the model for training or predicting, we extract a batch of $b$ samples and produce the two arrays form each.
-
-\paragraph*{}Since the spectrogram and feature vector represent different \textit{modalities}, we construct two separate \textit{design matrices}, $X_1$ and $X_2$ \cite{Geron,Li,Ngiam}.
+Since the spectrogram and feature vector represent different \textit{modalities}, we construct two separate \textit{design matrices}, $X_1$ and $X_2$ \cite{Geron,Li,Ngiam}.
 Each has shape given by:
@@
 \label{eqn-X1Shape}
-X_1 \in \mathbb{R}^{(b \times N \times k)}
+X_1 \in \mathbb{R}^{(b \times N' \times k)}
 \end{equation}
@@
 \end{equation}
-Where $N \times k$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sect.
+Where $N' \times k$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sec.
 (\ref{subsec-Spectrogram}).
@@
 The first axis, with size $b$ indicates that there are $b$ audio file samples stored in that design matrix.
-Organizing the samples in this fashion allows for both easy machine and human interpretation of each axis or index.
+Organizing the samples in this fashion allows for easy machine and human interpretation of each axis and index.
 
@@
 \begin{enumerate}
-\item Roughly $18,000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
+\item Roughly $18,000$ audio files Professionally or semi-professionally recorded in a studio(see acknowldgements) All ampltiudes have been normalized to $\pm 1$ unit.
 \item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
-\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
+\item All audio is sampled at $44,100$ Hz and $24$-bit depth.
 \item All audio has been down-mixed into mono-channel waveforms.
@@
 As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior.
-Following this success, it make senses to provide an image-like representation of a sound wave as a feature.
+Following this success, it is reasonable to provide an image-like representation of a sound wave as a feature.
 We do this in the form of a \textit{spectrogram} matrix.
@@
 	\includegraphics[scale=0.2]{../FiguresSpectrogram/SquareWave-880Hz}
-	\caption{Square Wave at $220$ Hz}
+	\caption{Square Wave at $880$ Hz}
 	\end{subfigure}
@@
 
-\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification \cite{Liu,Zhang}.
-Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the previous frame.
+\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal processing \cite{Liu,Zhang}.
+Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being a fixed $N$ samples in length, and has a fixed overlap with the previous frame.
 Each of the $k$ frames then allows for a section of the signal to be analyzed in a \textit{quazi-stationary state} \cite{Khan,Serizel}.
@@
 \end{equation}
-We use bracket notation, $a[i]$ to indicate that each analysis frame $a_i$ is array-like. The following indexing conventions for matrix $A$ all represent the same entry:
+We use bracket notation, $a_i[j]$ to indicate that each analysis frame $a_i$ is array-like. The following indexing conventions for matrix $A$ all represent the same entry:
 \begin{equation}
 \label{eqn-IndexingA}
-A_{i,j} = A_i[j] = A[i][j] = A[i,j]
+A_{i,j} = A_i[j] = A[i,j]
 \end{equation}
@@
 \end{equation}
-This window function is applied to each analysis frame by computing the element-wise product of the Hanning window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$.
-The result is another $k \times N$ array, $\widetilde{A}$:
+This window function is applied to each analysis frame by computing the element-wise product of the Hanning window array, $H$ and each row of the analysis frames matrix, $A[i,:]$.
+The result is another $k \times N$ array, which is denoted as $\widetilde{A}$, and is given by:
 \begin{equation}
@@
 \end{equation}
-We show the effect of a Hanning window on an analysis frame:
+We show the effect of a Hanning window applied to an analysis frame:
 \begin{figure}[H]
@@
 The Fourier Transform assumes that an integer number of signal periods fit within each analysis frame, however this is rarely the case.
-Transforming a signal with to \textit{spectral leakage} where energy appears to "leak" into adjacent frequency bins \textcolor{red}{Citation needed}.
+Transforming a signal with to \textit{spectral leakage} where energy appears to "leak" into adjacent frequency bins.
 This result is a frequency domain that is not an accurate representation of the equivalent time domain.
 The Hanning window uses the raised cosine function to taper the signal off to zero at the end-points, thus eliminate discontinuities at the edges while weighting the samples at the center much more heavily.
+This allows for a much cleaner transform array.
 
@@
 This means that each frame has gone from being $1024$ samples, to $2048$ samples.
-Matrix $\widehat{A}$ has a shape of $k \times 2048$.
+Matrix $\widetilde{A}$ has a shape of $k \times 2048$.
 Doubling the size of each analysis frame allows us the synthetically double the resolution in frequency-space, while retaining the resolution in time-space \cite{Virtanen}.
@@
 \paragraph*{}With this final change, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross,Virtanen}.
-The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$.
-Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space signal containing $N$ samples is given by \cite{Taylor,Virtanen}
+The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted as $\mathbb{W}$.
+Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space signal containing $N$ samples is given by \cite{Taylor,Peatross,Virtanen}:
 \begin{equation}
@@
 The DFT is applied by a taking the matrix - product of $\mathbb{W}$ and $\widetilde{A}^T$.
-The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
+The transpose of $\widetilde{A}$ makes each analysis frame into a column vector, which gives the appropriate format for transformation.
 \begin{equation}
@@
 
-\paragraph*{}Most standard implementations of neural network models have all activations, weights, and biases to be real floating-point numbers \cite{Levine,Loy,Tensorflow}.
+\paragraph*{}Most standard implementations of neural network models use activations, weights, and biases to all be real floating-point numbers \cite{Levine,Loy,Tensorflow}.
 Since the elements of the DFT matrix lie on the complex unit circle, each real-valued analysis frame will be moved into complex space.
@@
 
-The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of real floating-point numbers.
+\paragraph*{}The matrix $S$, is the spectrogram representation of the initial waveform, and has shape $N \times k$ of all real floating-point numbers.
 We can index matrix $S$ similarly to that of matrix $A$ in Eq.
@@
 \label{eqn-IndexingS}
-S_{i,j} = S[i][j] = S[i,j]
+S_{i,j} = S_i[j] = S[i,j]
 \end{equation}
@@
 There are $k$ columns, just as there were $k$ time-series frames, and $N$ rows since there were $N$ samples per row.
-Given the discrete nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$.
-To ensure homogeneous input sizes between all samples, we zero-pad the matrix $S$ with additional columns until $k = 256$.
+Given the discrete nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$ \cite{Short,Peatross}.
+To ensure homogeneous input sizes between all samples, we zero-pad the matrix $S$ with additional columns until $k = 256$, which mimics tail-padding the original signal with zeros.
 Recall that wave forms were truncated to ensure that $k \leq 256$ analysis frames.
@@
 \paragraph*{}Standard western musical instruments seldom have fundamental frequencies that extend above $6$ kHz \cite{Olson,Virtanen,White}.
-This means that when constructing the spectrogram, we will rarely see significant energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
+This means that when constructing the spectrogram, we will rarely see significant energy present above $12$ kHz at any time, and the $S$ matrix will contain mostly zero, or zero-like entries.
 To condense the size of the matrix, we select only the frequency bins (rows) that correspond to energies between $0$ Hz and $12,000$ Hz.
-This makes the input array smaller, and eliminates redundant and non-useful information.
+This makes the input array smaller, (less than 1/4 the size) and eliminates redundant and non-useful information.
 The number rows in the $S$ matrix is reduced from $N$ down to $N'$.
@@
 \label{eqn-X1}
-X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k)}
+X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k \times 1)}
 \end{equation}
@@
 \paragraph*{}The features described in this section are derived from time-domain representations of each audio sample.
-Each feature is one element in the feature vector for the particular sample.
 For consistency between samples, each waveform is padded or truncated to contain the same number of samples $M$.
-The number of samples $M$ is chosen to correspond the number of sample needed to make the $N \times k$ spectrogram matrix.
-This way, the spectrogram and time-series features are representative of the same time interval in the file sample.
+The number of samples $M$ is chosen to correspond the same number of samples as needed to make the $N \times k$ spectrogram matrix.
+In doing this, the spectrogram and time-series features are representative of the same time interval in the file sample.
 Time space is indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$
@@
 
-\paragraph*{}The time domain envelope (TDE) is a rough measurement of the energy contained in the time domain.
+\paragraph*{}The time domain envelope (TDE) is a rough measurement of the energy contained in the time-space of the waveform.
 If we divide the signal into analysis frames, as in Fig.
@@
 the signal has not started or is decaying.
-The small size of each analysis frame makes computing a TDE for each impractical, and create a very high-dimensional feature vector.
+The small size of each analysis frame makes computing a TDE for each impractical, and creates a very high-dimensional feature vector.
 This would also cause problems as some waveforms may have an initial attack that differs in time by a few analysis frames.
-Computing TDE for each frame would therefore introduce temporal bias, as the same waveform delayed by a few milliseconds would generate a wildly different set of predictor values \cite{Serizel}.
+Computing TDE for each frame would therefore introduce temporal bias, as the same waveform delayed by a few milliseconds would generate a slightly different set of predictor values \cite{Serizel}.
 
@@
 \end{equation}
-Where $Q$ gives the number of sample sin each analysis frame (number of sample sin waveform divided by number of frames), and $n$ gives the index where the $j$-th frame begins.
+Where $Q$ gives the number of samples in each analysis frame (number of sample sin waveform divided by number of frames), and $n$ gives the index where the $j$-th frame begins.
 We provide a graphic representation of how the TDE compares to the amplitude of sections of a waveform in Fig.
@@
 For example, this allows for a crude approximation of the energy in the attack, decay, sustain, and release portion of the signal \cite{Virtanen,Olson}.
-For instruments with heavier attacks, we expect the TDE in the $1$-st frame to be comparably large, see Fig.
+For instruments with heavier attacks, we expect the TDE in the first frame to be comparably large, see Fig.
 (\ref{fig-FeatureTDE}a).
-Instruments with a heavy decay will likely have little energy in the $2$-nd or higher frames, indicating that the amplitude has substantially died off as in Fig.
+Instruments with a heavy decay will likely have little energy in the second or higher frames, indicating that the amplitude has substantially died off as in Fig.
 (\ref{fig-FeatureTDE}b).
-Conversely, instruments with longer sustain such as upper woodwinds, vibraphones or strings will container relatively higher TDE values for the later analysis frames as seen in Fig.
+Conversely, instruments with longer sustain such as upper woodwinds, vibraphones or strings will contain relatively higher TDE values for the later analysis frames as seen in Fig.
 (\ref{fig-FeatureTDE}c).
@@
 
-\caption{A comparison of the first $3$ of $5$ Time Domain Envelope across each class using a box-and-whisker plot}
+\caption{A comparison of the first three of five time domain envelope values across each class using a box-and-whisker plot}
 \label{fig-FeatureTDE}
@@
 For example, consider the ZXR value of a a bass and cellos against that of bells or a soprano saxophone.
-The bass and cellos have on average much lower fundamental frequencies than that of bellos of soprano saxophones.
+The bass and cellos have on average much lower fundamental frequencies than that of cellos of soprano saxophones.
 In the case of this data set, the ZXR provides a predictor which contains clear separations between classes such as crotales and $E\flat$ clarinets.
@@
 \end{center}
-\caption{A comparison of the Zero-Crossing Rate for each class using a box-and-whisker plot}
+\caption{A comparison of the zero-crossing rate for each class using a box-and-whisker plot}
 \label{fig-FeatureZXR}
@@
 	\includegraphics[width=1.0\linewidth]{../FiguresSpectrogram/Vibraphone-sustain-A5-R_TCM}
-	\caption{Vibraphone - A5}
+	\caption{Vibraphone at $A5$ shows a lower TCM}
 	\end{center}
@@
 	\includegraphics[width=1.0\linewidth]{../FiguresSpectrogram/CELLO-F4_TCM}
-	\caption{Cello - F4}
+	\caption{Cello at $F4$ shows a central TCM}
 	\end{center}
@@
 Strings and undampened percussion have notoriously long sustain and release times giving them much higher TCM values \cite{Olson,White}.
-Finally, the synthetic wave forms have no characteristic  envelope shape (due to their synthetic nature).
-This gives a centrally located TCM, very close to $M/2$.
+Finally, the synthetic wave forms have no characteristic envelope shape which gives a centrally located TCM.
 
@@
 \begin{center}
-%\textcolor{red}{PLOT OF TCM FEATURES HERE}
 \includegraphics[scale=0.3]{../FiguresFeatures/TCM}
@@
 \paragraph*{}Auto correlation coefficients (ACC) are rough estimates of the signal spectral distribution.
-They are computed by summing a signal with a time-delayed variant of itself, and then normalized depending on the contect.
-We can compute any number of ACC's and their value changed depending on the index chosen.
+They are computed by multiplying a signal with a time-expedited variant of itself, and then normalized to be between $0$ and $1$ We can compute any number of ACC's and their value changed depending on the index chosen.
 It is common to use the first $K$ ACC's \cite{Serizel}.
@@
 
-\paragraph*{}Physically, the numerator of the ACC representing computing the dot product of the signal, $s[i]$ with a time-delayed version of itself $s[i+k]$, and  the denominator provides a normalization for the value.
+\paragraph*{}Physically, the numerator of the ACC representing computing the dot product of the signal, $s[i]$ with a time-hastened version of itself $s[i+k]$, and the denominator provides a normalization for the value.
 Dotting the signal and the time delay allows us to introduce a synthetic phase shift and compare the resulting relationship.
@@
 \end{center}
-\caption{A comparison of the the first four auto correlation coefficients in each class using a box-and-whisker plot}
+\caption{A comparison of the first four auto correlation coefficients in each class using box-and-whisker plots}
 \label{fig-FeatureACC}
@@
 \paragraph*{}The features described in this section are derived from the frequency-domain representations of each audio sample.
-Frequency space is represented by the transposed spectrogram matrix, $S^T$, described in sec.
-(\ref{subsec-Spectrogram}).
-This is done to ensure that each  row is now an analysis frame, each column is a frequency bin.
-This gives a similar structure to the time-space analysis frames matrix, $A$, in Eq.
-(\ref{eqn-FrameMatrix}).
 For each feature, we detail the physical significance and provide a visualization in feature-space.
@@
 \paragraph*{}Ceptstral coefficients are the result of computing the inverse discrete Fourier transform (IDFT) of the logarithm of the frequency Spectrum \cite{Serizel,Sahidullah}.
-Mel Frequency Cepstral Coefficients (MFCC's) are the most commonly used ceptral coefficients and appear commonly in digital signal processing.
+Mel Frequency Cepstral Coefficients (MFCC's) are the most commonly used ceptral coefficients and appear often in digital signal processing.
 The $c$-th coefficient is given by:
@@
 
-\paragraph*{}Physically, MFCC's are a transform of a transform.
+\paragraph*{}Physically, MFCC's are a b inverse transform of a transform.
 This allows us to investigate the periodicity of the frequency spectrum, which highlights phenomena such as overtones or echoes in the signal \cite{Virtanen}.
-Cepstrum coefficients are commonly used to speech identification and are very prolific in sound recognition tasks \cite{Serizel,Sahidullah,Liu}.
+Cepstrum coefficients are commonly used for speech identification and are very prolific in sound recognition tasks \cite{Serizel,Sahidullah,Liu}.
 We show a feature-space representation of MFCC's for a selection of coefficients in Fig.
@@
 \paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a representation of how overtones and energy is distributed in the signal's frequency domain.
-As with the temporal center-of-mass, we treat each row of the $S^T$ matrix as it's own 1-Dimensional mass distribution, and compute the center of mass of that row.
+As with the temporal center-of-mass, we treat each column of the $S$ matrix as it's own one-dimensional mass distribution, and compute the center of mass of each column.
 This encodes the FCM for a single analysis frame (in frequency-space) in the waveform.
-For an frequency-analysis frame, $s^{(i)}$, the FCM is given by:
+For an frequency-space analysis frame, $s^{(i)}$, the FCM is given by:
 \begin{equation}
@@
 Similarly, basses or tubas will have considerably low FCM values.
-Given that the standard frequency range of some musical instruments is fixed, it is guaranteed that for any particular instrument, the FCM will consistently remain within certain bounds \cite{Olson,White}.
+Given that the standard frequency range of some musical instruments is fixed, it is expected that for any particular instrument, the FCM will consistently have low variability \cite{Olson,White}.
 
@@
 \begin{center}
-%\textcolor{red}{PLOT OF FCM FEATURES HERE}
 \includegraphics[scale=0.3]{../FiguresFeatures/FCM}
 \end{center}
-\caption{A comparison of the frequency center-of-mass for each class using box-and-whisker plots}
+\caption{A comparison of the frequency center of mass for each class using box-and-whisker plots}
 \end{figure}
@@
 The exact ratio of sizes between these subsets varies depending on the task \cite{Goodfellow,Geron2,Mitchell}, however we choose to generally use around $90\%$ training samples and $10\%$ testing samples.
-By doing this train-test split scheme, we are confirming or disproving the predictive power of the model.
-If the model score high within it's training subset, but low within the testing subset, this can indicate a model that is \textit{overfitted}, and will not perform well on other unseen samples \cite{Geron}.
+If the model performs well within it's training subset, but poorly within the testing subset, this can indicate a model that is \textit{overfitted}, and will not perform well on other unseen samples \cite{Geron}.
 
@@
 Each model $F^*$, shows a possible outcome of training the network given a subset of data samples, and a particular set of initial parameters.
-It has a corresponding set of learned parameters $\Theta^*$, as defined in Eq.
-(\ref{eqn-Theta}) that it uses to make any predictions.
 We can compare the performance of each model and test if they produce similar outcomes, which indicates that the model will be able to consistently generalize to new, unseen samples.
@@
 
-\paragraph*{}In the case of the multi-category classifier, it is important that we choose the appropriate performance metrics to confirm that the network is completeing it's assigned as as expected \cite{Geron}.
+\paragraph*{}In the case of the multi-category classifier, it is important that we choose the appropriate performance metrics to confirm that the network is completing it's assigned as as expected \cite{Geron}.
 While the neural network itself uses the cost function as it's sole objective to optimize, we also require a set of more human-readable functions.
 For example, an average loss score of $1.075$ over a given subset of previously unseen samples provides us with no real information as to how well the network is performing at it's designed task.
-In this section, we introduce a set of functions and metrics than enable a more tangible interpretation of the model's performance.
+In this section, we introduce a set of functions and metrics that allow for a more tangible interpretation of the model's performance.
 To evaluate any performance metric, we require a set of samples with ground truth labels, $y$, and a model's prediction for those labels, $y^*$ \cite{Goodfellow,James}.
@@
 The general idea of this object is count the number of times class $i$ is predicted to be in class $j$, and vice-versa \cite{Geron}.
-If we see that these classes are being repeatedly \textit{confused} in the model's prediction process, then we can modify the model or features to account for it.
+If we see that these classes are being repeatedly \textit{confused} in the model's prediction process, then we can modify the model or features to account for it, or explore why this happens.
 
@@
 
-\paragraph*{}For a multi-class problem, present accuracy over each individual class, called \textit{micro-accuracy} \cite{James}.
+\paragraph*{}For a multi-class problem, present an accuracy for each individual class, called \textit{micro-accuracy} \cite{James}.
 The accuracy for a class $j$ is the correct predictions related to the class divided by the total predictions and total counts of the class.
@@
 \end{equation}
-In the case of a multi-class classifier, the precision score represents an\textit{one-vs-all} measurement.
+In the case of a multi-class classifier, the precision score represents a \textit{one-vs-all} measurement.
 This means that for any class $j$, the sample belongs to class $j$ or it does not.
@@
 \end{equation}
-In the case of a multi-class classifier, the recall score also represents an\textit{one-vs-all} measurement.
+In the case of a multi-class classifier, the recall score also represents a \textit{one-vs-all} measurement.
 This means that for any class $j$, the sample belongs to class $j$ or it does not.
@@
 
-\paragraph*{}F1-score (also called F-score) is the harmonic mean of precision and recall scores and it also bounded on $[0,1]$ with a higher score being favorable \cite{Geron}.
+\paragraph*{}F1-score (also called F-score) is the harmonic mean of the precision and recall scores and it also bounded on $[0,1]$ with a higher score being favorable \cite{Geron}.
 Often, the two metrics can be through of as somewhat \textit{exclusive} to each other - the higher one, the lower the other.
@@
 This phenomenon is called the \textit{precision-recall tradeoff} \cite{Geron,James}.
-We compute the $F1$ score for a class $k$ as:
+We compute the $F1$ score for a class $j$ as:
 \begin{equation}
@@
 In the case of this multi-category classifier, this is somewhat like modifying the generated decision boundaries as to change the outputted probability distribution.
-In case cases, it is useful to use the $F1$ score to find the set of hyper-parameters that allow for the classifier to produce both the highest possible precision \textit{and} recall score.
+The $F1$ score to find the set of hyper-parameters that allow for the classifier to produce both a high precision \textit{and} recall score.
 
@@
 The average cost for the mini-batch is then used to compute the gradient vector $\nabla_{\Theta}J$, and subsequently update the model according to the optimizer chosen \cite{Geron,Goodfellow}.
-
-\paragraph{}We execute computation in batches to reduce the amount of memory required for the operation.
-Pushing a full data set through a model at one time would require more RAM than is usually available , thus repeated subset of data tend to avoid memory exhaustion errors.
-Additionally, every mini-batch used equates to one step in the optimizer update rule \cite{Goodfellow}.
+Recall we implement an ADAM optimizer as outlined in sec.
+(\ref{subsubsec-Optimizer}).
+
+\paragraph{}We execute training computations in batches to reduce the amount of memory required for the operation.
+Pushing a full data set through a model at one time would require more RAM than is usually available so we use repeating, non-overlapping subsets of data called mini-batches to avoid memory exhaustion errors.
+Each mini-batch used equates to one step in the optimizer update rule in Eq.
+(\ref{eqn-ADAMupdate}) \cite{Goodfellow}.
 Thus, a single pass over a full data set allows for multiple iterations of the optimizer to reduce the value of the cost function.
@@
 If the cost function is dropping to quickly or slowly, this may indicate that the optimizer learning rate is too high or too low.
-This may lead to an over-fit or under-fit model, or indicate an inappropriate set of feature is being used \cite{Geron,Goodfellow}.
-In Some cases, it can be used to initiate \textit{early-stopping}, which halts training when a set of parameters are met.
+This may lead to an over-fit or under-fit model, or indicate an inappropriate set of features are being used \cite{Geron,Goodfellow}.
+In Some cases, it can be used to initiate \textit{early-stopping}, which halts training when a set of conditions are met.
 
@@
 Instead, we produce a large subset of the full data set of $256$ samples which we dub a \textit{mega-batch}.
-From this mega-batch, we produce the two deign matrices required for input, and load the corresponding labels.
-We then use a subset of this group as the \textit{mini-batches} for training.
+From this mega-batch, we produce the two design matrices required for input, and load the corresponding labels.
+We then use a subset of \textit{this} group as the \textit{mini-batches} for training.
 Each mini-batch contains $32$ samples.
-Once all mini-batches are fit, we discard the design matrices in the mega batch and repeat for the next $256$ samples.
+Once all mini-batches are fit, we discard the mega-batch design matrices and repeat for the next $256$ samples.
 
 \paragraph*{}With each training step, we have recorded the precision, recall, and loss scores.
-These scores are computed from the forward pass of the training data before the gradient is computed, and parameters updated, i.e.
-the program has not seen Our program stores these values locally in a \textit{training-history} file, which we can examine after the program completes.
+These values are computed from the forward pass of the training data before the gradient is computed, and parameters updated, i.e.
+the program has not seen these particular sample system.
+Our program stores past metric and loss score histories locally in a \textit{training-history} file, which we can examine after the program completes.
 Below, we visualize the evolution of each score as training progresses.
@@
 \end{figure}
-
 similarly, we can visualize the precision score and recall score at each training step.
-
 \begin{figure}[H]
@@
 \end{center}
-\caption{The precision score and recall score generally increase with each training step}
+\caption{The precision score and recall score generally increase with each training step, indicating that the model gis getting both more sensistive and more specific with each step}
 \label{fig-PrecisionRecallScores}
@@
 The batch is discarded and a new subset of samples is drawn so that the process repeats.
-With two epochs per mega-batch, and two passes over the full data set (permuted in the middle), the model is effectively trained on the full data set a total of $4$ times.
+With two epochs per mega-batch, and two passes over the full data set (permuted in the middle), the model is effectively trained on the full data set a total of four times.
 
@@
 	\end{subfigure}	
-	\caption{Confusion matrices, each is averaged over 10 folds of cross validation}
+	\caption{Confusion matrices, each is averaged over 10 folds of cross validation. Recall that each integer represents a class labeled, as given in Tab. (\ref{fig-ClassList})}
 	\label{fig-MultimodalConfs}
@@
 (\ref{fig-PercussionScores}c).
+over the cross validations, it was found that the multilayer perceptron architecture produced a better precision, recall, and F1 score than either the convolution or the hybrid network architecture.
+This can be contrasted with most other classes showing hat the hyrbidg model performed better than either individual mode, with the convolution architecture as a close second.
+
+\paragraph*{}We can also observe a loose correlation to the number of samples in each class compared to the classification metric scores.
+When a model is trained on one class more than another we are more likely to generate predictions in that class too.
+This can be seen in the scores and occurrences of alto flutes (\ref{fig-HighWindsScores}a) with $72$ samples compared to that of English horns (\ref{fig-HighWindsScores}e) with $1382$ samples.
+In both confusion matrices of Fig.
+(\ref{fig-MultimodalConfs}), we see a realty small entry in $C_{0,0}$ (alto flutes) compared to $C_{14,14}$ ( English horn).
+This indicates that fewer correction predictions were made, and the normalized matrix shows that fewer predictions were made at all.
+Contrast this with the english horn having a dark red square in both matrices shows many predictions, and many correction predictions.
+
+\paragraph*{}
+\textcolor{red}{Also not done here}
 
@@
 \subsection{Predictions on Chaotic Synthesizers}
+
+\textcolor{red}{Help}
 
@@
 
+\paragraph*{}The experimental results show that we have successfully constructed a multimodal neural network that can classify sound waves into one of $37$ categories that it most resembles.
+Each category is representative of a particular musical instrument, and collectively the categories cover many stringed, woodwind, brass, mallet percussion, and synthetic instruments.
+From performing a $10$-folds cross validation, we find that given slightly different initial conditions and overlapping subsets of training data, the model produces consistency reasonable classification scores as shown in Fig.
+(\ref{fig-MultimodalXval}).
+This behavior indicates a neural network architecture and features that can generalize to unseen data.
+
+\paragraph*{}Examining the two diagonally dominant confusion matrices in Fig.
+(\ref{fig-MultimodalConfs}) indicates that the neural network is consistently making correct categorical predictions.
+The presence of off-diagonal entries in the confusion matrices indicates that misclassifications are a possibility due to an imperfect set features.
+Averaged across $37$ classes, we see in Fig.
+(\ref{fig-MultimodalXval}) that the classification accuracy score averages around $0.98$ and precision and recall scores around $0.83$ and $0.82$ respectively.
+On average, examining each class in an \textit{one-versus-all} context, the model selects $83\%$ of relevant samples, and $82\%$ of relevant samples are selected.
+This indicates a neural network that can reasonably differentiate between $37$ classes of musical instruments.
+
+\paragraph*{}Additionally, we conclude that on average, the hybrid neural network architecture in Fig.
+(\ref{fig-NetworkArchitecture}) exhibits superior classification performance over either of it's unimodal counterpart architectures.
+In examining confusion matrices from both unimodal models in Fig.
+(\ref{fig-UnimodalConfs}), we see the presence of diagonal dominance.
+However, in comparing this to the multimodal network confusion matrix from Fig.
+(\ref{fig-MultimodalConfs}), we see that the multimodal network has a much stronger main diagonal entry.
+This indicates that my aggregating to the output of each modal branch with a concatenation layer, we can benefit from the predictive power of both branches together.
+This indicates that both a multilayer perceptron and convolutional network are producing generally appropriate classification labels, but an aggregation of two architectures yields and even higher classification performance.
+
+\text{red}{Also plz help here}
+
 % ================================================================
@@
 
-\item[•]Dr. Kevin Short and Dr. Maurik Holtrop for various consultation and guidance throughout this project.
-
-\item[•]Dakota Buell, John Parker, Nathan Richard, Morgan Saidel for consultation on physics, mathematics, and programming topics.
+\item[•]Dr. Kevin Short and Dr. Maurik Holtrop for advising this project.
+
+\item[•]Dakota Buell, Tan Dao, John Parker, Nathan Richard, Morgan Saidel for consultation on physics, mathematics, and programming topics.
 
@@
 
-\item[•]University of Iowa, Electronic Music Studio and Philharmonica Symphony Orchestra for the digital sound library used for training data samples.
+\item[•]University of Iowa, Electronic Music Studio and Philharmonia Symphony Orchestra for the digital sound library used for training data samples.
 

### 2020-12-14 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Added v3, Finished abstract & intro

@@
 
+\newpage
+
 \begin{abstract}
 
-The task of recognizing the source of a sound wave is trivial and almost effortless to a human being.
+The task of recognizing the source of a sound wave in a digital audio file is trivial and almost effortless to a human being, but far more difficult for a computer to do.
+To execute this task, we have designed and constructed a multimodal neural network, that utilizes two different input branches, one being a convolutional neural network (CNN), and the other, a multilayer perceptron (MLP).
+The CNN branch accepts input in the form of a two-dimensional spectrogram matrix, which encodes the energy distribution of an audio signal over frequency and time, and the MLP branch accepts input as a one-dimensional array of features derived from the physical nature of the sound wave.
+The spectrogram is produced by using a concatenation of multiple short-time discrete Fourier transformations (STDFT) of overlapping windowed time-space analysis frames.
+The feature vector implements techniques from digital signal processing to combine properties of the time-space and frequency-space information.
+To classify the audio files based on predicted sources, we aggregate the of the activations from the final layers of each branch, and produce a single prediction label.
+We find that this architecture allows for reasonable classification performance, and demonstrates an average superior classification performance when compared to either of it's constituent unimodal architectures.
 
@@
 From climate measurements, to financial reports, to audio-visual media, or to medicine, time-domain signals surround the modern world at every corner \cite{Virtanen}.
-In each context, the general idea is to place the data or a subset of the data into distinct categories called \textit{classes} based on it's properties.
-For example, doctors may wish to classify a patient as having a heart condition based on properties of their heartbeat or banks may wish to detect fraudulent transactions based on a history of spending habits.
+In each context, the general idea is to place data or a subset of data into distinct categories called \textit{classes} based on it's properties.
+For example, doctors may wish to classify a patient as having a heart condition based on properties of their heartbeat or banks may wish to classify a purchase as fraudulent based on a history of spending habits.
 Often, the volume  of information or complexity of the task makes it unreasonable for a human to do unaided by some form of automation.
@@
 Some papers details features and performances of attempting to classify speech against music or organize audio-visual media based on content.
+
+\paragraph*{}As the name implies, a neural network is a computation a model or graph that is loosely structured off of the human \cite{Geron,Loy}.
+Where a biological brain uses physical connects to exchanges chemicals to communicate information, a neural network uses a chain of mathematical operations to communicate information \cite{Goodfellow}.
+The earliest work on attempting to model cognitive processes goes back to 1943, where Warren McCulloch and Walter Pitts began to develop a mathematical model of the human brain using principles of mathematics \cite{McCulloch,Loy}.
+Nearly ten years, later, one of the earliest computation neural networks called the \textit{perceptron} was developed by Frank Rosenblatt in 1953, which modeled connections of neurons through principles of linear algebra \cite{Geron}.
+Another decade after that, inspiration from the visual cortex gave rise to the convolution operation to be applied to digital image processing.
+
+\paragraph*{}Modern developments in high-performance computing and
 
@@
 
-\paragraph*{}The design of the neural function that we have constructed combines two architecture types by using two distinct entry arrays which are processed, and a single output is formed.
+\paragraph*{}The design of our neural function combines two architecture types by using two distinct entry arrays which are processed, and a single output is formed.
 Thus type of neural network is referred to as a \textit{multimodal} nueral network \cite{Li,Ngiam}.
-
-\paragraph*{}\textcolor{red}{This is not my best into to date}
+Our multimodal network contains a convolutional neural network (CNN) that processes an image-like representation of an audio waveform, and a multilayer perceptron (MLP) that processes a list-like representation of an audio wave form.
+Each arm of the network is it's own computuational graph that is designed to process it's respective inputs types and
 
@@
 
-\item[•]Dakota Buell, Tan Dao, John Parker, Nathan Richard, Morgan Saidel for consultation on physics, mathematics, and programming topics.
+\item[•]Dakota Buell, Tan Dao, John Parker, Nathan Richard, and Morgan Saidel for consultation on physics, mathematics, and programming topics.
 

### 2020-12-14 Thesis/Drafts/Buell-PHYS799-ThesisDraft3.tex
Added v3, Finished abstract & intro

--- 2020-12-14 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
@@
        	\begin{LARGE}
-       	\textbf{Mapping Chaotically Generated Synthesizers to Musical Instruments with Machine Learning and Harmonic Analysis} \\
+       	\textbf{Audio Classification of Musical Instruments with a Multimodal Neural Network} \\
        	\end{LARGE}
-       	\vspace{1cm}
-       	\begin{Large}
-       	Multimodal Classification of Digital Signal
-       	\end{Large}             
-       	\vspace{1.5cm}
+       	\vspace{6cm}
 
@@
 
-\tableofcontents
-
 % ================================================================
@@
 The CNN branch accepts input in the form of a two-dimensional spectrogram matrix, which encodes the energy distribution of an audio signal over frequency and time, and the MLP branch accepts input as a one-dimensional array of features derived from the physical nature of the sound wave.
-The spectrogram is produced by using a concatenation of multiple short-time discrete Fourier transformations (STDFT) of overlapping windowed time-space analysis frames.
-The feature vector implements techniques from digital signal processing to combine properties of the time-space and frequency-space information.
+The spectrogram is produced by using a concatenation of multiple short-time Fourier transformations (STFT) of overlapping windowed time-space analysis frames.
+The feature vector implements techniques from digital signal processing to combine more explicit properties of the time-space and frequency-space information.
 To classify the audio files based on predicted sources, we aggregate the of the activations from the final layers of each branch, and produce a single prediction label.
-We find that this architecture allows for reasonable classification performance, and demonstrates an average superior classification performance when compared to either of it's constituent unimodal architectures.
+We find that this architecture allows for reasonable classification performance, and demonstrates superior classification performance on average, when compared to either of it's constituent unimodal architectures.
+Training data for this experiment is from studio recordings of the Philharmonia Symphony Orchestra and University of Iowa's Electronic Music Studios.
 
 \end{abstract}
+
+% ================================================================
+% ================================================================
+
+\newpage
+
+\tableofcontents
 
@@
 Similarly, modern computers are also complex systems that can filter through exabytes of information on a daily basis, but are not generally known for being able to distinguish cats from dogs \cite{Geron}.
-The compromise between is an algorithm called a \textit{neural network} that combines the computation speed of a computer with the decision-making power of a human \cite{Goodfellow,Levine,Loy}.
-
-\paragraph*{}In this work, we have developed an automated neural network program that can classify digital sound waves as one of $37$ musical instrument that it most closely resembles.
+The compromise between humans and machines an algorithm called a \textit{neural network} that combines the computation speed of a computer with the decision-making power modeled from human brain \cite{Goodfellow,Levine,Loy}.
+
+\paragraph*{}In this work, we have developed an automated neural network program that can classify digital sound waves as one of $37$ musical instruments that it most closely resembles.
 The general use of machine learning algorithms for audio information classification or identification is well explored, and a topic of much modern research \cite{Khan,Liu,Mierswa,Serizel,Zhang}.
 From previous work, it has been found that various types of audio classification are possible, and are still being expanded upon.
-Some papers details features and performances of attempting to classify speech against music or organize audio-visual media based on content.
-
-\paragraph*{}As the name implies, a neural network is a computation a model or graph that is loosely structured off of the human \cite{Geron,Loy}.
-Where a biological brain uses physical connects to exchanges chemicals to communicate information, a neural network uses a chain of mathematical operations to communicate information \cite{Goodfellow}.
-The earliest work on attempting to model cognitive processes goes back to 1943, where Warren McCulloch and Walter Pitts began to develop a mathematical model of the human brain using principles of mathematics \cite{McCulloch,Loy}.
-Nearly ten years, later, one of the earliest computation neural networks called the \textit{perceptron} was developed by Frank Rosenblatt in 1953, which modeled connections of neurons through principles of linear algebra \cite{Geron}.
+Many papers details predictors for classifying speech against music or features for organizing audio-visual media based on content.
+In each case, features are often tailored to meet the specific task at hand \cite{Virtan,Liu}.
+
+\paragraph*{}It has been experimentally determined that the choice of features is critically important to classification success \cite{Khan,Serizel}.
+In our case, the nature of these features is motivated by the physics and mechanical properties of each musical instrument class.
+By exploring the physics of the vibrating parts of each instrument according to the Hornbostel-Sachs classification system, we gain a more through understanding of each instrument group.
+This allows us to develop properties within each class that are consistent with a low variability, and what properties differ between classes and show a higher variability.
+These differences are key to providing a set of features which allow a neural network to differentiate between classes of musical instruments \cite{Liu,Zhang}.
+
+\paragraph*{}As the name implies, a neural network is a computation a model or graph that is loosely structured off of the biological brain \cite{Geron,Loy}.
+Where a biological brain uses physical connects through axons to exchanges chemicals to communicate information, a neural network uses a chain of mathematical operations to communicate information \cite{Goodfellow}.
+The earliest work on attempting to model cognitive processes goes back to 1943, where Warren McCulloch and Walter Pitts began to develop a model of the human brain using principles of mathematics \cite{McCulloch,Loy}.
+Nearly ten years later, a simple neural networks called the \textit{perceptron} was developed by Frank Rosenblatt, which modeled connections of neurons through principles of linear algebra \cite{Geron}.
 Another decade after that, inspiration from the visual cortex gave rise to the convolution operation to be applied to digital image processing.
 
-\paragraph*{}Modern developments in high-performance computing and
-
-\paragraph*{}It is well know that the choice of inputs, called features is critically important to classification success \cite{Khan,Serizel}.
-In many cases, we can develop and explore a set of features that allows for the particular classification task to be executed considerably well.
-In our case, the choice of features is motivated by the physics of each musical instrument class.
-By exploring the nature of the vibration part of each instrument according to the Hornbostel-Sachs classification system, we can describe some of the mechanical properties and see how they differ between instruments of different types.
-These differences are key to providing a set of features which allow a neural network to differentiate between classes of instruments \cite{Liu,Zhang}.
-
-\paragraph*{}The design of our neural function combines two architecture types by using two distinct entry arrays which are processed, and a single output is formed.
-Thus type of neural network is referred to as a \textit{multimodal} nueral network \cite{Li,Ngiam}.
-Our multimodal network contains a convolutional neural network (CNN) that processes an image-like representation of an audio waveform, and a multilayer perceptron (MLP) that processes a list-like representation of an audio wave form.
-Each arm of the network is it's own computuational graph that is designed to process it's respective inputs types and
+\paragraph*{}The design of our neural network function combines two architecture types by using two distinct entry arrays which are processed, and a single output is formed.
+This type of neural network is referred to as a \textit{multimodal} neural network \cite{Li,Ngiam}.
+Our model contains a convolutional neural network (CNN) that processes an image-like representation of an audio waveform, and a multilayer perceptron (MLP) that processes a list-like representation of an audio wave form.
+Each arm of the network is it's own computational graph that is designed to process it's respective inputs types.
+The activations at the end of each layer are concatenated into a new layer, which is further processed and then used to generate a single prediction.
+This prediction aggregated from two features on average shows superior classification when compared to the performance either of either of it's constituent unimodal architectures alone.
 
@@
 	\includegraphics[scale=0.6]{../figures/2DConvExample(d)}
-	\caption{Input Activations, $x^{(l-1)}$}
+	\caption{Output Activations, $x^{(l)}$}
 	\end{subfigure}
@@
 The spectrogram acts to provide an energy distribution of a signal as a function of frequency and time, while the feature vector provides qualities in a more list-like fashion.
-This type of supervised learning is referred to as \textit{multi-view} learning, and we detail a conceptual diagram of the architecture in Fig.
+This type of supervised learning is referred to as \textit{multi-representation learning}, and we detail a conceptual diagram of the architecture in Fig.
 (\ref{fig-NetworkArchitecture}) \cite{Li,Ngiam}.
@@
 \end{center}
-\caption{The implemented miltimodal architecture of the audio file classification neural network.
-The Left branch process an image-like input, the right branch processes a vector-like input.
+\caption{The implemented multimodal architecture of the audio file classification neural network.
+The left branch process an image-like input, and the right branch processes a vector-like input.
 The activations are then merged, and then a single output vector is produced}
@@
 
-\subsubsection{The Spectrogram Branch}
-
-\paragraph*{}The spectrogram branch is pictured on the left side of Fig.
-(\ref{fig-NetworkArchitecture}), and is an implementation of a \textit{convolutional neural networl} (CNN).
-A spectrogram is a representation of a sound wave, or signal by representing energy distributions as a function of \textit{time} and \textit{frequency} \cite{White,Olson,Khan}.
-The input layer of the spectrogram accepts a 4-Dimensional array.
+\subsubsection{The Convolution Branch}
+
+\paragraph*{}The convolution branch is pictured on the left side of Fig.
+(\ref{fig-NetworkArchitecture}), and is an implementation of a \textit{convolutional neural network} (CNN).
+It processes a spectrogram, which is a representation of a waveform, or signal as an energy distributions over \textit{time} and \textit{frequency} \cite{White,Olson,Khan}.
+The input layer of this branch accepts a 4-Dimensional array.
 The axes, in order of indexing, represents (i) the size of the \textit{mini-batch} of samples, (ii) the pixel height of each sample, (iii) the pixel wifth of each sample, and (iv) the number of channels in the image.
@@
 \end{equation}
+Note that the spectrogram provided to the neural network is representing the power spectrum of the audio file as defined in Eq.
+(\ref{eqn-Spectrogram}).
+All spectrogram figures in this report are from taking the element-wise \textit{natural log} of the power spectrum.
+This has been done solely for visualization purposes.
 
@@
 \end{center}
-\caption{The precision score and recall score generally increase with each training step, indicating that the model gis getting both more sensistive and more specific with each step}
+\caption{The precision score and recall score generally increase with each training step, indicating that the model is getting both more sensitive and more specific as training progresses}
 \label{fig-PrecisionRecallScores}
@@
 % ================================================================
-
-\subsection{Predictions on Chaotic Synthesizers}
-
-\textcolor{red}{Help}
 

### 2020-12-14 Thesis/Drafts/Buell-PHYS799-ThesisDraft3.tex
Minor updates to Thesis, New Citation

@@
 We find that this architecture allows for reasonable classification performance, and demonstrates superior classification performance on average, when compared to either of it's constituent unimodal architectures.
-Training data for this experiment is from studio recordings of the Philharmonia Symphony Orchestra and University of Iowa's Electronic Music Studios.
+Training data for this experiment is from studio recordings of the Philharmonia Symphony Orchestra and the University of Iowa's Electronic Music Studios.
 
@@
 
-\paragraph*{}This project includes a great number of steps to ensure it's completion. Here we show a high-level outline of the pieces involved.
+\paragraph*{}This project includes a number of steps to ensure it's completion. Here we show a high-level outline of the pieces involved.
 
@@
 This ensures that all data will have a consistent format when features are extracted.
-This stage is detailed in sec.
-(\ref{subsubsec-Preprocessing}).
+This stage is detailed in section (\ref{subsubsec-Preprocessing}).
 
@@
 These inputs are designed to represent properties of wave forms that can be expressed by a single or multiple numerical values.
-We detail these features in sec.
-(\ref{sec-Features}).
+We detail these features in section (\ref{sec-Features}).
 These are used in place of a full waveform to represent a file's contents in a low-dimensional array.
@@
 The nature of all possible solutions that the trained model could arrive at is subject to the architecture \cite{Goodfellow,Loy}.
-We construct a multimodal neural network, explored in sec.
-(\ref{subsec-Architecture}), that processes two distinct entry points derived from the same audio sample.
+We construct a multimodal neural network, explored in section (\ref{subsec-Architecture}), that processes two distinct entry points derived from the same audio sample.
 This network is designed to evaluate each input independently, and concatenate the results to produce a single outputted prediction.
@@
 This process is repeated and expanded upon until we have produced a model with a sufficient performance.
-We explore the explore this is sec.
-(\ref{sec-PerfEval}).
+We explore the explore this is section (\ref{sec-PerfEval}).
 
@@
 If further corrections are needed, we revert and re-deign the features, architecture, or hyper-parameters as needed.
-We explore thisas part of our conclusions in sec.
-(\ref{sec-Conclusion}).
+We explore thisas part of our conclusions in section (\ref{sec-Conclusion}).
 
@@
 Birds inspired us to fly, burdock plants inspired velcro, and nature has inspired many other inventions.
-It seems only logical then, to look to the brain's architecture for inspiration on how to build an intelligent machine.
+It seems only logical, then, to look to the brain's architecture for inspiration on how to build an intelligent machine.
 \end{quote}
@@
 Where a biological brain uses connections of chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Levine,Bishop}.
-Where a brain uses physical connection of neurons through axons, the nueral network uses mathematical connections of neurons through mathematical operations \cite{Geron,Levine}.
+Where a brain uses physical connection of neurons through axons, the neural network uses mathematical connections of neurons through mathematical operations \cite{Geron,Levine}.
 
@@
 In this section, we explore the motivation, structure, and training process of a neural network.
+We implement our neural network with the \textit{Tensorflow} Python package \cite{Tensorflow}.
 
@@
 In this case of the model used in the project, we combine the outputs that result from the convolution branch and the perceptron branch to produce an single aggregated output.
-This process is detailed further in sec.
-(\ref{subsec-Architecture}).
+This process is detailed further in section (\ref{subsec-Architecture}).
 This layer also "non-trainable" because it does no use any weights or transformations, only a fixed procedure.
@@
 \end{equation}
-For a dense layer as in sec.
-(\ref{subsubsec-DenseLayer}) or a 2D-convolution layer as in sec.
-(\ref{subsubsec-Conv2DLayer}) $\partial z^{(L-1)} / \partial W^{(L-1)}$ is given by the derivative of Eq.
+For a dense layer as in section (\ref{subsubsec-DenseLayer}) or a 2D-convolution layer as in section (\ref{subsubsec-Conv2DLayer}) $\partial z^{(L-1)} / \partial W^{(L-1)}$ is given by the derivative of Eq.
 (\ref{eqn-LinearTransform}) or Eq.
@@
 \paragraph*{}An optimizer is the algorithm or procedure that is used by a machine learning model to perform the optimization task to reduce the cost value after reciveing each new training sample.
-Regression models may often used a \textit{mean-squared error} cost function which can often be solved analytically, while high dimensional neural networks, such as the one used in this project, outlined in sec.
-(\ref{subsec-Architecture}), can only up updated iterativly \cite{Goodfellow,James,Loy}.
+Regression models may often used a \textit{mean-squared error} cost function which can often be solved analytically, while high dimensional neural networks, such as the one used in this project, outlined in section (\ref{subsec-Architecture}), can only up updated iteratively \cite{Goodfellow,James,Loy}.
 We use a variation of gradient descent much like the one in Eq.
@@
 If the previous step was found to reduce the cost function by a large or small amount, the step size for the previous step will update accordingly.
-This enables to ADAM to overcome smaller discontunities that may arise in the solution space \cite{Goodfellow}.
+This enables to ADAM to overcome smaller discontinuities that may arise in the model's solution space \cite{Goodfellow}.
 For a given step $(i)$, The ADAM update is given:
@@
 \paragraph*{}We can carry this idea over by producing a \textit{multimodal} neural network that accepts two different forms of input for each sample.
-One input is an $N' \times k$ spectrogram matrix, explored in sec.
-(\ref{subsec-Spectrogram}) and the other input is a $1 \times p$ feature vector explored in sec.
-(\ref{subsec-TimeFeatures}) and sec.
-(\ref{subsec-FreqFeatures}).
+One input is an $N' \times k$ spectrogram matrix, explored in section (\ref{subsec-Spectrogram}) and the other input is a $1 \times p$ feature vector explored in section (\ref{subsec-TimeFeatures}) and section (\ref{subsec-FreqFeatures}).
 The spectrogram acts to provide an energy distribution of a signal as a function of frequency and time, while the feature vector provides qualities in a more list-like fashion.
@@
 \end{enumerate}  
-The convolution layers iterate over the middle two axes of the data, see sec.
-(\ref{subsubsec-Conv2DLayer}).
+The convolution layers iterate over the middle two axes of the data, see section (\ref{subsubsec-Conv2DLayer}).
 Physically, this allows us to search through the frequency and time axes to detect dominant features or shapes.
@@
 We call these properties \textit{features} or \textit{predictors} \cite{Geron,Khan,Serizel}.
-Details on the natures and selections of these $p$ elements are found in sec.
-(\ref{subsec-TimeFeatures}) and sec.
-(\ref{subsec-FreqFeatures}).
+Details on the natures and selections of these $p$ elements are found in section (\ref{subsec-TimeFeatures}) and section (\ref{subsec-FreqFeatures}).
 
@@
 This ensures that no one feature dominates the performance of the model and that layer activations do not get saturated to extremes as data progresses through the network.
+This operation was implemented through the \textit{scikit-learn} Python package \cite{Sklearn}.
 
@@
 This vector is then transformed into the final dense layer, which uses the softmax activation, and encodes the joint predictions based on contributions of both model branches.
-In sec.
-(\ref{sec-Results}) we explore how the predictive power of the network changes when examining the performance of each individual branch compared to the hybrid model.
+In section (\ref{sec-Results}) we explore how the predictive power of the network changes when examining the performance of each individual branch compared to the hybrid model.
 
@@
 
-\paragraph*{}As discussed in Sec.
-(\ref{sec-TheNeuralNetwork}), performance quality of a neural network is greatly dependent on the properties of the chosen features \cite{Virtanen,Liu}.
+\paragraph*{}As discussed in section (\ref{sec-TheNeuralNetwork}), performance quality of a neural network is greatly dependent on the properties of the chosen features \cite{Virtanen,Liu}.
 To ensure that the classifier model performs adequately and consistently, we must choose these features to have high variance between classes, and low variance within each class.
@@
 For this section, we represent waveforms as \textit{spectrograms} to capture the time-space and frequency-space development of energy simultaneously.
-We motivate and describe the production of a spectrogram in sec.
-(\ref{subsec-Spectrogram}).
+We motivate and describe the production of a spectrogram in section (\ref{subsec-Spectrogram}).
 
@@
 \paragraph*{}We model the tight elastic membrane very similarly as that of a tight elastic string, except in two dimensions \cite{White}.
-Unlike the chordophone sec.
-(\ref{subsec-chordophones}), the partials for the membrane are not related by integer multiples.
+Unlike the chordophone section (\ref{subsec-chordophones}), the partials for the membrane are not related by integer multiples.
 This lack of harmonic structure leaves most membranophones to have a sort of "muddled" frequency spectrum where we see a more continuous distribution of constituent frequencies arise as opposed to clean integer related overtones \cite{White,Olson}.
@@
 \paragraph*{}From each audio file sample, we calculate the values for the same predictors.
-The predictors are arranged into two separated structures, each called a \textit{design matrix}, described in sec.
-(\ref{subsubsec-DesignMatrix}) \cite{Goodfellow,Geron}.
+The predictors are arranged into two separated structures, each called a \textit{design matrix}, described in section (\ref{subsubsec-DesignMatrix}) \cite{Goodfellow,Geron}.
 For a model with $p$ predictors, feature space is a $p$-dimensional vector space where each basis vector represents a predictor \cite{Goodfellow,James}.
@@
 
-\paragraph*{}Each audio sample is represented by an $N' \times k$ spectrogram matrix explored in sec.
-(\ref{subsec-Spectrogram}), a $1 \times p$ feature vector, and a  one-hot-encoded target label, $y$.
+\paragraph*{}Each audio sample is represented by an $N' \times k$ spectrogram matrix explored in section (\ref{subsec-Spectrogram}), a $1 \times p$ feature vector, and a  one-hot-encoded target label, $y$.
 In order to efficiently present the information to the model for training or predicting, we extract a batch of $b$ samples and produce the two arrays form each.
@@
 \end{equation}
-Where $N' \times k$ gives the shape of the spectrogram matrix $S$ from a single sample, described in sec.
-(\ref{subsec-Spectrogram}).
-Similarly, $p$ is the number of predictors extracted from each sample, outlined in sec.
-(\ref{subsec-TimeFeatures}) and sec.(\ref{subsec-FreqFeatures}).
+Where $N' \times k$ gives the shape of the spectrogram matrix $S$ from a single sample, described in section (\ref{subsec-Spectrogram}).
+Similarly, $p$ is the number of predictors extracted from each sample, outlined in section (\ref{subsec-TimeFeatures}) and section(\ref{subsec-FreqFeatures}).
 The first axis, with size $b$ indicates that there are $b$ audio file samples stored in that design matrix.
@@
 \label{eqn-DFTMatrix}
-\mathbb{W} = \frac{1}{N}
+\mathbb{W} = 
 \begin{bmatrix}
@@
 \paragraph*{}In addition to the standard confusion matrix, we can also weight entries by prediction score.
-Rather than adding $+1$ to each entry $C_{i,j}$ where appropriate, we instead add the \textit{probability} value, which is bounded $[0,1]$ (See softmax activation function in sec.
-\ref{subsubsec-Softmax})).
+Rather than adding $+1$ to each entry $C_{i,j}$ where appropriate, we instead add the \textit{probability} value, which is bounded $[0,1]$ (See softmax activation function in section \ref{subsubsec-Softmax})).
 This allows us to bake in the predictive \textit{confidence} into the confusion matrix.
@@
 The average cost for the mini-batch is then used to compute the gradient vector $\nabla_{\Theta}J$, and subsequently update the model according to the optimizer chosen \cite{Geron,Goodfellow}.
-Recall we implement an ADAM optimizer as outlined in sec.
-(\ref{subsubsec-Optimizer}).
+Recall we implement an ADAM optimizer as outlined in section (\ref{subsubsec-Optimizer}).
 
@@
 \paragraph*{}To formally produce classification predictions on the chaotic synthesizer waveforms, we must use all of the neural network, physics, and statistical principles outlined in the previous sections.
-Using the described features in sec.
-(\ref{sec-Features}) and appropriate architecture sec.
-(\ref{subsec-Architecture}), We run a $K=10$ folds cross validation program as in Alg.(\ref{alg-CrossValidation}).
+Using the described features in section (\ref{sec-Features}) and appropriate architecture section (\ref{subsec-Architecture}), We run a $K=10$ folds cross validation program as in Alg.(\ref{alg-CrossValidation}).
 For each of the $10$ models, we produce a standard confusion matrix, and compute the (i) accuracy score, (ii) precision score, (iii) recall score, and (iv) F1 score.
@@
 \paragraph*{}Comparing the results within each class, as averaged over $10$ folds of cross validation indicate that our model performs very well at the ability to a match sound waves to their sources.
-We see this behavior in the plots in sec.
-(\ref{subsec-ClassScores}) as well as the confusion matrices in Fig.
+We see this behavior in the plots in section (\ref{subsec-ClassScores}) as well as the confusion matrices in Fig.
 (\ref{fig-MultimodalConfs}).
@@
 
+\bibitme{Matplotlib}
+John D. Hunter. Matplotlib: A 2D Graphics Environment, Computing in Science & Engineering, 9, 90-95 (2007), DOI:10.1109/MCSE.2007.55
+
 \bibitem{McCulloch}
@@
 
+\bibitem{Numpy}
+Harris, C.R., Millman, K.J., van der Walt, S.J. et al. Array programming with NumPy. Nature 585, 357–362 (2020). DOI: 0.1038/s41586-020-2649-2.
+
 \bibitem{Olson}
@@
 
+\bibitem{Scipy}
+Pauli Virtanen, et. al. SciPy 1.0: Fundamental Algorithms for Scientific Computing in Python. Nature Methods, 17(3), 261-272.
+
 \bibitem{Short}
 Short, K. and Garcia R.A. 2006. "Signal Analysis Using the Complex Spectral Phase Evolution (CSPE) Method." AES: \textit{Audio Engineering Society Convention Paper}.
+
+\bibitem{Sklearn}
+Fabian Pedregosa, et. al. Scikit-learn: Machine Learning in Python, Journal of Machine Learning Research, 12, 2825-2830 (2011)
 

### 2020-12-16 Thesis/Drafts/Buell-PHYS799-ThesisDraft3.tex
Major Updates to Thesis & Figures

@@
 
-The task of recognizing the source of a sound wave in a digital audio file is trivial and almost effortless to a human being, but far more difficult for a computer to do.
-To execute this task, we have designed and constructed a multimodal neural network, that utilizes two different input branches, one being a convolutional neural network (CNN), and the other, a multilayer perceptron (MLP).
+The task of recognizing the source of a sound wave in a digital audio file is trivial and almost effortless to a human being in many cases, but is far more difficult for a computer to do.
+In order to automate source source identification, we have designed and constructed a multimodal neural network that can classify audio files by what musical instrument the sound most resembles.
+The network uses two different input branches, one being a convolutional neural network (CNN), and the other, a multilayer perceptron (MLP).
 The CNN branch accepts input in the form of a two-dimensional spectrogram matrix, which encodes the energy distribution of an audio signal over frequency and time, and the MLP branch accepts input as a one-dimensional array of features derived from the physical nature of the sound wave.
@@
 The feature vector implements techniques from digital signal processing to combine more explicit properties of the time-space and frequency-space information.
-To classify the audio files based on predicted sources, we aggregate the of the activations from the final layers of each branch, and produce a single prediction label.
+To classify the audio files based on predicted sources, we aggregate and transform the activations from the final layers of each branch, and produce a single prediction label.
 We find that this architecture allows for reasonable classification performance, and demonstrates superior classification performance on average, when compared to either of it's constituent unimodal architectures.
@@
 \end{abstract}
+
+\vspace{8cm}
+
+\begin{center}
+All source code and documentation for this project can be found at  \\
+\textit{https://github.com/landonbuell/Buell-Senior-Thesis}
+\end{center}
 
@@
 From climate measurements, to financial reports, to audio-visual media, or to medicine, time-domain signals surround the modern world at every corner \cite{Virtanen}.
-In each context, the general idea is to place data or a subset of data into distinct categories called \textit{classes} based on it's properties.
+In each context, the general idea is to place information into distinct categories called \textit{classes} based on inherent properties of the data.
 For example, doctors may wish to classify a patient as having a heart condition based on properties of their heartbeat or banks may wish to classify a purchase as fraudulent based on a history of spending habits.
-Often, the volume  of information or complexity of the task makes it unreasonable for a human to do unaided by some form of automation.
+Often, the volume  of information or complexity of the task makes it unreasonable for a human to do without the aide of some form of automation.
 
 \paragraph*{}It has long been a goal of computer scientists and engineers alike to develop a program, algorithm, or machine that could perform a certain task to the level of human-being \cite{Bishop,Geron,Loy}.
-While humans are intricate organisms capable of recognition or classification in many contexts, we are not notorious for the ability to process millions of raw numerical values in the course of a few seconds.
+While humans are intricate organisms capable of recognition or classification in many contexts, we do not have the ability to process millions of raw numerical values in the course of a few seconds.
 Similarly, modern computers are also complex systems that can filter through exabytes of information on a daily basis, but are not generally known for being able to distinguish cats from dogs \cite{Geron}.
@@
 From previous work, it has been found that various types of audio classification are possible, and are still being expanded upon.
-Many papers details predictors for classifying speech against music or features for organizing audio-visual media based on content.
-In each case, features are often tailored to meet the specific task at hand \cite{Virtan,Liu}.
-
-\paragraph*{}It has been experimentally determined that the choice of features is critically important to classification success \cite{Khan,Serizel}.
+Many papers detail possible sets of inputs for classifying speech against music or inputs for organizing audio-visual media based on content.
+In each case these inputs, called features, must often be tailored to meet the specific task at hand \cite{Virtanen,Liu}.
+
+\paragraph*{}It has been experimentally determined that the choice of features is critically important to classification success \cite{Khan,Mierswa,Serizel}.
 In our case, the nature of these features is motivated by the physics and mechanical properties of each musical instrument class.
-By exploring the physics of the vibrating parts of each instrument according to the Hornbostel-Sachs classification system, we gain a more through understanding of each instrument group.
-This allows us to develop properties within each class that are consistent with a low variability, and what properties differ between classes and show a higher variability.
+By exploring the physics of the vibrating parts of each instrument according to the Hornbostel-Sachs classification system, we gain a more thorough understanding of each instrument group.
+This allows us to develop properties within each class that are consistent and have low variability, and what properties differ between classes and show a higher variability.
 These differences are key to providing a set of features which allow a neural network to differentiate between classes of musical instruments \cite{Liu,Zhang}.
+For our classifier model, we have developed $24$ features from the time-series and frequency-series representation of the audio file data.
+These quantities are assembled into a single axis array for processing.
+Additionally, we construct an image-like representation of the waveform and the 2D array is also used for proceessing.
+Both of these input modes represent a set of features that convey the nature of the waveform in two different modalities.
 
@@
 The earliest work on attempting to model cognitive processes goes back to 1943, where Warren McCulloch and Walter Pitts began to develop a model of the human brain using principles of mathematics \cite{McCulloch,Loy}.
-Nearly ten years later, a simple neural networks called the \textit{perceptron} was developed by Frank Rosenblatt, which modeled connections of neurons through principles of linear algebra \cite{Geron}.
+Nearly ten years later, a simple neural networks called the \textit{perceptron} was developed by Frank Rosenblatt, which modeled connections of neurons through principles of linear algebra \cite{Geron,Petrik}.
 Another decade after that, inspiration from the visual cortex gave rise to the convolution operation to be applied to digital image processing.
 
-\paragraph*{}The design of our neural network function combines two architecture types by using two distinct entry arrays which are processed, and a single output is formed.
+\paragraph*{}The design of our neural network function combines two distinct architecture types by using two distinct entry arrays which are processed, and a single output is formed.
 This type of neural network is referred to as a \textit{multimodal} neural network \cite{Li,Ngiam}.
@@
 The activations at the end of each layer are concatenated into a new layer, which is further processed and then used to generate a single prediction.
-This prediction aggregated from two features on average shows superior classification when compared to the performance either of either of it's constituent unimodal architectures alone.
+This output that is aggregated from two inputs shows on average, superior classification performance when compared to either of it's constituent unimodal architectures alone.
 
@@
 
-\paragraph*{}This project includes a number of steps to ensure it's completion. Here we show a high-level outline of the pieces involved.
+\paragraph*{}This project includes a number of steps from taking raw input data to the final classification task.
+In this section, we provide a very high level outline of the parts of this projects and show how each one influence the final product.
+Additionally, we indicate the sections in this thesis where the particular material is introduced and developed much more thoroughly.
 
@@
 
-\paragraph*{}Consider the biological process of hearing a sound wave and matching it to a source.
+\paragraph*{}To automate the process of classifying audio files, we require a program or algorithm that can make practical decisions based on a prescribed set of information.
+This is to say that we need a \textit{function} to process an input or set of inputs, and return a predicted label that corresponds to a musical instrument.
+Consider the biological process of hearing a sound wave and matching it to a source.
 We can model this behavior by some unknown function $F$ and approximate it with the function $F^*$.
-This can map the contents of a sound file to a potential source as to mimic the behavior of $F$.
-For a set of inputs (called features or predictors) $\vec{x} = \big\{ x_0 , x_1 , x_2 , ...
+This approximate function is composed of smaller functions that collectively work together to direct the flow of information and allow for the mapping of the contents of a sound file to a potential source as to mimic the behavior of $F$.
+For a set of inputs $\vec{x} = \big\{ x_0 , x_1 , x_2 , ...
 , x_{p-1} \big\}$ and a set of classes $0$ through $k-1$, we denote this function as:
@@
 \label{eqn-MappingFunction}
-F^*: \vec{x} \rightarrow \big\{ 0 , 1 , 2 , ... , k-1 \big\}
-\end{equation}
-
-\paragraph*{}In secs.
+F^*: \vec{x} \rightarrow \big\{ 0, 1, 2, ... ,k-2, k-1 \big\}
+\end{equation}
+
+\paragraph*{}The smaller functions that comprise $F^*$ are called \textit{layers} \cite{Loy,Goodfellow}.
+Each type of layer performs a different operation and processes different types of input.
+In secs.
 (\ref{subsec-NerualNetworkIntro}) and (\ref{subsec-NetworkStructure}), we introduce the nature and structure of a neural network and how it can use used in part to solve this problem.
-We discuss it's inspiration from a biological brain,and show how different layer types are influenced from the brain's functions as well as how they are used in this problem.
+We discuss it is inspired from a biological brain and show how different layer types are influenced from the brain's functions as well as how they are used in this problem.
+Using information about the problem, we carefully design the inputs, outputs and structure of the neural network function to be able to complete this task in a practical manner.
 
@@
 
-\paragraph*{}In order to train the neural network to be able to identify musical instrument sources, we need a suitable data set to present to the model as training data.
-University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files (See acknowledgments).
-These files contain short segments of musical instruments performing a single note, and is labeled according to the instrument that produced the sound.
+\paragraph*{}In order to train the neural network to be able to identify musical instrument sources, we need a suitable data set to present to the model as training and validation data.
+The models uses this data and corresponding labels in the training process to modify it's function to allow for it to complete the task.
+University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \cite{Philharmonia,UnivIowa}.
+These files contain short segments of musical instruments performing a single note, and are labeled according to the instrument that produced the sound.
 The files and labels make up the core of the data set that we use to train the model.
 
-\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 24-bit depth.
+\paragraph*{}To ensure that these data sets are formatted consistently, we have designed a MATLAB program to read each audio file from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 24-bit depth.
 This ensures that all data will have a consistent format when features are extracted.
 This stage is detailed in section (\ref{subsubsec-Preprocessing}).
+After the samples are formatted, we have produced a Python script with iterates through each new file and assigns a class label based on the title of the instrument.
+This has been design to account for the specific naming cases that arise.
+We assemble a dictionary-like structure of all training file with organizes the local file location of each sample and provides an integer and string label for all samples.
 
@@
 \paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of predictors or features which represent the raw input given to the model.
-These inputs are designed to represent properties of wave forms that can be expressed by a single or multiple numerical values.
+These inputs are designed to represent prolific properties of wave forms that can be expressed by a single or multiple numerical values.
 We detail these features in section (\ref{sec-Features}).
-These are used in place of a full waveform to represent a file's contents in a low-dimensional array.
 We use tools from physics, mathematics, and signal processing to define and explore a comprehensive set of features that enables a high performance of the classifier.
@@
 This network is designed to evaluate each input independently, and concatenate the results to produce a single outputted prediction.
+Out nueral network was implemented using the tools available with the \textit{Tensorflow} module \cite{Tensorflow}.
 
@@
 We explore the explore this is section (\ref{sec-PerfEval}).
-
-% ================================================================
-
-\subsubsection{Running Predictions of Chaotic Synthesizer Files}
-
-\paragraph*{}Once we have established a suitable performance of the model, we allow the model to run predictions on the un-labeled chaotic synthesizer wave forms.
-We output the prediction results to a file, and compare the neural network predictions against human predictions.
-If further corrections are needed, we revert and re-deign the features, architecture, or hyper-parameters as needed.
-We explore thisas part of our conclusions in section (\ref{sec-Conclusion}).
+Results of all metrics are computed with the \textit{numpy},\textit{scipy}, and \textit{scikit learn} python modules \cite{numpy,scipy,sklearn}.
+All performance evaluate visualiztions are produced with the matplotlib python package \cite{matplotlib}.
 
@@
 
-\paragraph*{}The task of automatically matching sound files to musical instrument classes is exceedingly challenging through conventional computer programming techniques.
-Because of the complexity of sound recognition, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
+\paragraph*{} Because of the complexity of sound recognition, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules.
 Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an solution that allows for a computer to \textit{learn} from labeled training examples in order \textit{teach} itself \cite{Bishop,Mitchell}.
@@
 The result is a computer program that is reminiscent of the a brain in that it structured much like the brain, and can\textit{learn} from new data.
+We model operations with collections are artificial neurons that are capable of connect and interacting with other neurons \cite{Levine}.
 Where a biological brain uses connections of chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Levine,Bishop}.
 Where a brain uses physical connection of neurons through axons, the neural network uses mathematical connections of neurons through mathematical operations \cite{Geron,Levine}.
+We call the numerical value contained within an artificial neuron the \textit{activation} of that neuron \cite{Goodfellow,Geron}.
 
@@
 \paragraph*{}A Neural Network is a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Goodfellow,Loy}.
-Each layer represents an operation that takes an input, typically an array of real double-precision floating-point numbers, and returns an output which is a modified array of new double-precision floating-point numbers.
+Each layer represents an operation that takes an input, and returns an output .
 The exact nature of this operation can be very different depending on the layer type or where it sits within the network.
@@
 For example, in classifying types of animals, a feature could be the mass, volume or number of teeth on the animal.
-Typically, we produce a set of features $p$ for each sample and assemble them into a $p$-dimensional vector called a \textit{feature vector} which acts as a list of descriptive qualities of the sample \cite{Geron,James}.
+Typically, we produce a set of $p$ features for each sample and assemble them into a $p$-dimensional vector called a \textit{feature vector} which acts as a list of descriptive qualities of the sample \cite{Geron,James}.
+This list is presented to the neural network and used to
 Audio machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib describe the vitality of feature selection \cite{Khan}:
@@
 The Hanning window uses the raised cosine function to taper the signal off to zero at the end-points, thus eliminate discontinuities at the edges while weighting the samples at the center much more heavily.
-This allows for a much cleaner transform array.
+This allows for a much cleaner transform into frequency space.
 
@@
 (\ref{fig-PercussionScores}c).
-over the cross validations, it was found that the multilayer perceptron architecture produced a better precision, recall, and F1 score than either the convolution or the hybrid network architecture.
-This can be contrasted with most other classes showing hat the hyrbidg model performed better than either individual mode, with the convolution architecture as a close second.
+Over the cross validations, it was found that the multilayer perceptron architecture produced a better precision, recall, and F1 score than either the convolution or the hybrid network architecture.
+
+ This can be contrasted with most other classes showing hat the hybrid model performed better than either individual mode, with the convolution architecture as a close second.
+
+\paragraph*{}While the hybrid model can differentiate between many types of instruments, each uni-modal variant shows slightly less success over the full data set.
+In many instances, the MLP-only architecture particularly shows unstable and inconsistent performance.
+For certain instruments like the $E\flat$ clarinet, tenor saxophone, tenor trombone, and hi-hat cymbal, the feature vector does a very poor job of isolating and identifying those classes.
+However, for instruments such as the soprano saxophone, tuba, and square wave the feature-vector allows the MLP to perform very reasonably.
+We see a similar imbalance with the CNN-only architecture where classes such as alto flute, bass flute, bass trombone, and mandolin show poor classification rates.
+This can be contrasted with English horn, tuba, bells, and double bass, where a much higher classification performance is found.
+Further exploration is required to provide a full explanation and justification of why this wide range of performance is observed.
 
@@
 In both confusion matrices of Fig.
-(\ref{fig-MultimodalConfs}), we see a realty small entry in $C_{0,0}$ (alto flutes) compared to $C_{14,14}$ ( English horn).
+(\ref{fig-MultimodalConfs}), we see a relatively small entry in $C_{0,0}$ (alto flutes) compared to $C_{14,14}$ ( English horn).
 This indicates that fewer correction predictions were made, and the normalized matrix shows that fewer predictions were made at all.
-Contrast this with the english horn having a dark red square in both matrices shows many predictions, and many correction predictions.
-
-\paragraph*{}
-\textcolor{red}{Also not done here}
-
-% ================================================================
+Contrast this with the English horn having a dark red square in both matrices shows many predictions, and many correction predictions.
+
+\paragraph*{}Future work on this project would benefit from a further exploration and development of input features.
+While the ability to discern classes is present, classification scores are still unstable and we observe a wide range of performances.
+To combat this, we would produce additional feature that convey characteristic properties of the digital audio files that allow for the generation of more distinctive decision boundaries.
+In addition to new features, it would be beneficial to further study the distribution of samples in feature space and execute some form of $K$-best features algorithm.
+This would indicate which are the chosen predictors show properties that are inconsistency with the ideas of intra-class and inter-class variability.
+
+\paragraph*{}In addition to input features, it may be beneficial to group for the the related classes together.
+For example, violins and violas have very similar physic construction, have very similar formant structures, and thus have very similar behaviors in our feature-space.
+As a result, some humans may also have difficulty differentiating the two, so it may be forgiven that a classification neural network would do the same.
+We can also consider grouping range variants of parent instruments together such as flutes, alto flutes, bass flutes into a single \textit{flutes} category.
+It is possible that the new distribution of properties in feature-space may also warrant the development of a new set of predictors again.
+It would also be worth exploring how classification performance would be affected when weighting each class inversely to it's number of samples in the data set.
+This would allow each class to be weighted uniformly in the training process and may potentially mitigate some of the variability of the performances across classes.
+
+\paragraph*{}Finally as a practical demonstration, future work entails the deployment of this classifier to generally unlabeled audio samples, provided that they have the same format.
+In particular, we would like to explore how classification would behave when testing it on digitally generated chaotic synthesizer wave forms.
+These signals are representations of chaotic systems that resemble some of the acoustic the periodic properties of acoustic waveforms.
+By suing the automated classifier, we would like to test the versatility of the classifier when subject to samples that may differ drastically in same ways from the training data set.
+This demonstration would be a fantastic exploration into the ability for the model to generalize, and the strength of the learned function parameters.
 
@@
 (\ref{fig-MultimodalConfs}) indicates that the neural network is consistently making correct categorical predictions.
-The presence of off-diagonal entries in the confusion matrices indicates that misclassifications are a possibility due to an imperfect set features.
+The presence of off-diagonal entries in the confusion matrices indicates that misclassifications are a common possibility.
 Averaged across $37$ classes, we see in Fig.
 (\ref{fig-MultimodalXval}) that the classification accuracy score averages around $0.98$ and precision and recall scores around $0.83$ and $0.82$ respectively.
-On average, examining each class in an \textit{one-versus-all} context, the model selects $83\%$ of relevant samples, and $82\%$ of relevant samples are selected.
-This indicates a neural network that can reasonably differentiate between $37$ classes of musical instruments.
-
-\paragraph*{}Additionally, we conclude that on average, the hybrid neural network architecture in Fig.
+This means that examining each class in an \textit{one-versus-all} context, the model selects $83\%$ of relevant samples, and $82\%$ of relevant samples are selected.
+This indicates that the multimodal neural network that can reasonably differentiate between $37$ classes of musical instruments.
+
+\paragraph*{}We conclude that on average, the hybrid neural network architecture in Fig.
 (\ref{fig-NetworkArchitecture}) exhibits superior classification performance over either of it's unimodal counterpart architectures.
@@
 
-\text{red}{Also plz help here}
-
 % ================================================================
@@
 
-\item[•]Dakota Buell, Tan Dao, John Parker, Nathan Richard, and Morgan Saidel for consultation on physics, mathematics, and programming topics.
-
-\item[•]Madeline Edwards for differing me to this project, as well as constant support and consultation on mathematical topics.
+\item[•]Dakota Buell, Tan Dao, Nathan Richard, and Morgan Saidel for consultation on physics, mathematics, and programming topics.
+
+\item[•]Madeline Edwards and John Parker for differing me to this project, as well as constant support and consultation on mathematical topics.
 
@@
 
-\bibitme{Matplotlib}
-John D. Hunter. Matplotlib: A 2D Graphics Environment, Computing in Science & Engineering, 9, 90-95 (2007), DOI:10.1109/MCSE.2007.55
+\bibitem{Matplotlib}
+John D. Hunter. Matplotlib: A 2D Graphics Environment, Computing in Science \& Engineering, 9, 90-95 (2007), DOI:10.1109/MCSE.2007.55
 
@@
 Petrik, Marek. "Introduction to Deep Learning." Machine Learning. 20 April. 2020, Durham, New Hampshire.
+
+\bibitem{Philharmonia}
+Philharmonia Symphony Orchestra home page- \textit{https://philharmonia.co.uk/}
 
@@
 Virtanen, Tuomas, et al. \textit{Computational Analysis of Sound Scenes and Events.} Springer, 2018.
+
+\bibitem{UnivIowa}
+University of Iowa Electronic Music Studios home page- \textit{http://theremin.music.uiowa.edu/}
 

### 2020-12-16 Thesis/Drafts/Buell-PHYS799-ThesisDraft3.tex
Edits to written thesis

@@
 
-\paragraph*{}This project includes a number of steps from taking raw input data to the final classification task.
+\paragraph*{}This project includes a number of steps from taking raw input data to the final classification program.
 In this section, we provide a very high level outline of the parts of this projects and show how each one influence the final product.
@@
 \paragraph*{}With the appropriate set of features designed, and the number of output categories determined, we can organize the structure of the neural network function.
-The shape of the network defines the flow of information, and the hypothesis space.
-The nature of all possible solutions that the trained model could arrive at is subject to the architecture \cite{Goodfellow,Loy}.
+The shape of the network defines the flow of information and the hypothesis space.
+The nature of all possible solutions that the trained model could arrive at is subject to the architecture \cite{Goodfellow}.
 We construct a multimodal neural network, explored in section (\ref{subsec-Architecture}), that processes two distinct entry points derived from the same audio sample.
 This network is designed to evaluate each input independently, and concatenate the results to produce a single outputted prediction.
-Out nueral network was implemented using the tools available with the \textit{Tensorflow} module \cite{Tensorflow}.
+This hybrid architecture combines the predictive power of the both a multilayer perceptron and a convolutional neural network.
+Our neural network was implemented using the tools available with the \textit{Tensorflow} module \cite{Tensorflow}.
 
@@
 This ensures that the model can perform consistently and reliably given small changes in initial conditions.
-In this stage, we also choose the value of hyper-parameters, activation functions and layer widths to best compliment the chosen features.
+In this stage, we also examine the value of hyper-parameters, activation functions, and layer widths to best compliment the properties of the data set.
 This process is repeated and expanded upon until we have produced a model with a sufficient performance.
-We explore the explore this is section (\ref{sec-PerfEval}).
+We explore this in section (\ref{sec-PerfEval}).
 Results of all metrics are computed with the \textit{numpy},\textit{scipy}, and \textit{scikit learn} python modules \cite{numpy,scipy,sklearn}.
-All performance evaluate visualiztions are produced with the matplotlib python package \cite{matplotlib}.
+All performance visualizations are produced with the \textit{matplotlib} python package \cite{matplotlib}.
 
@@
 \begin{enumerate}
-\item Roughly $18,000$ audio files Professionally or semi-professionally recorded in a studio(see acknowldgements) All ampltiudes have been normalized to $\pm 1$ unit.
+\item Roughly $18,000$ audio files Professionally or semi-professionally recorded in a studio \cite{Philharmonia,UnivIowa} All ampltiudes have been normalized to $\pm 1$ unit.
 \item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
@@
 	\end{subfigure}
-
-\caption{Spectrogram representations of various waveforms}
+\caption{Spectrogram representations of various waveforms. Note that all spectrograms are color-coded according to the log-power spectrum.}
 \label{fig-Spectrograms}
@@
 	\includegraphics[scale=0.3]{../FiguresMetrics/AvgXval-Convolution}
-	\caption{Convolutional Unimodal Architecture, See left side of Fig. (\ref{fig-NetworkArchitecture})}
+	\caption{Convolutional Unimodal Architecture, see left side of Fig. (\ref{fig-NetworkArchitecture})}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.3]{../FiguresMetrics/AvgXval-Perceptron}
-	\caption{Perceptron Unimodal Architecture, See right side of Fig. (\ref{fig-NetworkArchitecture})}
+	\caption{Perceptron Unimodal Architecture, see right side of Fig. (\ref{fig-NetworkArchitecture})}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.18]{../FiguresMetrics/XValGammaCNN_Avg_Standard_Confusion}
-	\caption{Standard confusion Matrix for the convolution branch}
+	\caption{Standard confusion matrix for the convolution branch}
 	\end{subfigure}
@@
 	\includegraphics[scale=0.18]{../FiguresMetrics/XValGammaCNN_Avg_Hits_Weighted_Confusion}
-	\caption{Occurrence Weighted confusion matrix for the convolution branch}
+	\caption{Occurrence weighted confusion matrix for the convolution branch}
 	\end{subfigure}
@@
 
-\paragraph*{}Comparing the results within each class, as averaged over $10$ folds of cross validation indicate that our model performs very well at the ability to a match sound waves to their sources.
+\paragraph*{}Comparing the results within each class, as averaged over $10$ folds of cross validation indicates that our model performs very well at the ability to a match a sound waves in digital audio files to their sources.
 We see this behavior in the plots in section (\ref{subsec-ClassScores}) as well as the confusion matrices in Fig.
 (\ref{fig-MultimodalConfs}).
-For the chosen set of classes, features and architecture, the model can generalize to new information allowing it to distinguish between different type of musical instruments reasonably well.
-Additionally, we show that predictive power of the model improves through our development of the multimodal architecture.
-By choosing to express the waveform in two different modalities in the form of the spectrogram matrix and the feature vector, the hybrid model demonstrates a generally higher classification performance across the same number of samples and splits.
+For the chosen set of classes, features and architecture, the model can generalize to new information allowing it to distinguish between different types of musical instruments reasonably well for samples that it has not yet interacted with.
+Additionally, we show that the predictive power of the model improves through our development of the multimodal architecture.
+By choosing to express the audio file contents in two different modalities of the spectrogram matrix and the feature vector, the hybrid model demonstrates a generally higher classification performance across the same number of samples and splits.
 
@@
 Over the cross validations, it was found that the multilayer perceptron architecture produced a better precision, recall, and F1 score than either the convolution or the hybrid network architecture.
-
- This can be contrasted with most other classes showing hat the hybrid model performed better than either individual mode, with the convolution architecture as a close second.
-
-\paragraph*{}While the hybrid model can differentiate between many types of instruments, each uni-modal variant shows slightly less success over the full data set.
+This can be contrasted with most other classes showing that the hybrid model performed better than either individual mode, with the convolution architecture as a close second.
+
+\paragraph*{}While the hybrid model can differentiate between many types of instruments, each unimodal variant shows slightly less success over the full data set.
 In many instances, the MLP-only architecture particularly shows unstable and inconsistent performance.
-For certain instruments like the $E\flat$ clarinet, tenor saxophone, tenor trombone, and hi-hat cymbal, the feature vector does a very poor job of isolating and identifying those classes.
-However, for instruments such as the soprano saxophone, tuba, and square wave the feature-vector allows the MLP to perform very reasonably.
+For certain instruments like the $E\flat$ clarinet, tenor saxophone, tenor trombone, and hi-hat, the feature vector does a very poor job of isolating and identifying those classes.
+However, for instruments such as the soprano saxophone, tuba, and square wave, the feature-vector allows the MLP to perform very reasonably.
 We see a similar imbalance with the CNN-only architecture where classes such as alto flute, bass flute, bass trombone, and mandolin show poor classification rates.
@@
 \paragraph*{}We can also observe a loose correlation to the number of samples in each class compared to the classification metric scores.
-When a model is trained on one class more than another we are more likely to generate predictions in that class too.
+When a model is trained on one class more than another we are more likely to generate predictions for that class too.
 This can be seen in the scores and occurrences of alto flutes (\ref{fig-HighWindsScores}a) with $72$ samples compared to that of English horns (\ref{fig-HighWindsScores}e) with $1382$ samples.
@@
 Contrast this with the English horn having a dark red square in both matrices shows many predictions, and many correction predictions.
+Future work could explore how classification performance would be affected when weighting each class inversely to it's number of samples in the data set.
+This would allow each class to be weighted uniformly in the training process and may potentially mitigate some of the variability of the performances across classes.
 
@@
 In addition to new features, it would be beneficial to further study the distribution of samples in feature space and execute some form of $K$-best features algorithm.
-This would indicate which are the chosen predictors show properties that are inconsistency with the ideas of intra-class and inter-class variability.
+This would indicate which of the  chosen predictors consistent or inconsistent with our requirements of intra-class and inter-class variability.
 
 \paragraph*{}In addition to input features, it may be beneficial to group for the the related classes together.
-For example, violins and violas have very similar physic construction, have very similar formant structures, and thus have very similar behaviors in our feature-space.
+For example, violins and violas have very similar physical constructions, have very similar formant structures, and thus have very similar behaviors in our feature-space.
 As a result, some humans may also have difficulty differentiating the two, so it may be forgiven that a classification neural network would do the same.
-We can also consider grouping range variants of parent instruments together such as flutes, alto flutes, bass flutes into a single \textit{flutes} category.
+We can also consider grouping range variants of parent instruments such as flutes, alto flutes, bass flutes into a single \textit{flutes} category.
 It is possible that the new distribution of properties in feature-space may also warrant the development of a new set of predictors again.
-It would also be worth exploring how classification performance would be affected when weighting each class inversely to it's number of samples in the data set.
-This would allow each class to be weighted uniformly in the training process and may potentially mitigate some of the variability of the performances across classes.
 
@@
 In particular, we would like to explore how classification would behave when testing it on digitally generated chaotic synthesizer wave forms.
-These signals are representations of chaotic systems that resemble some of the acoustic the periodic properties of acoustic waveforms.
-By suing the automated classifier, we would like to test the versatility of the classifier when subject to samples that may differ drastically in same ways from the training data set.
+These signals are representations of chaotic systems that resemble some of the acoustic the periodic properties of digital audio waveforms.
+By using the automated classifier, we would like to test the versatility of the classifier when subject to samples that may differ drastically in oame ways from the training data set.
 This demonstration would be a fantastic exploration into the ability for the model to generalize, and the strength of the learned function parameters.
@@
 (\ref{fig-MultimodalXval}).
-This behavior indicates a neural network architecture and features that can generalize to unseen data.
+This behavior indicates a neural network architecture and features that can generalize to unseen data samples.
 
@@
 (\ref{fig-MultimodalXval}) that the classification accuracy score averages around $0.98$ and precision and recall scores around $0.83$ and $0.82$ respectively.
-This means that examining each class in an \textit{one-versus-all} context, the model selects $83\%$ of relevant samples, and $82\%$ of relevant samples are selected.
+This means that examining each class in an \textit{one-versus-all} context, the model selects more than $83\%$ of relevant samples, and more than $82\%$ of relevant samples are selected.
 This indicates that the multimodal neural network that can reasonably differentiate between $37$ classes of musical instruments.
@@
 However, in comparing this to the multimodal network confusion matrix from Fig.
-(\ref{fig-MultimodalConfs}), we see that the multimodal network has a much stronger main diagonal entry.
-This indicates that my aggregating to the output of each modal branch with a concatenation layer, we can benefit from the predictive power of both branches together.
-This indicates that both a multilayer perceptron and convolutional network are producing generally appropriate classification labels, but an aggregation of two architectures yields and even higher classification performance.
+(\ref{fig-MultimodalConfs}), we see that the multimodal network has a much more pronounced main diagonal.
+This indicates that by aggregating to the output of each modal branch with a concatenation layer, we can benefit from the predictive power of both architectures together.
 
@@
 
-\paragraph*{}The completion of this project would not have been possible without the various contributions from the following people:
+\paragraph*{}The completion of this project would not have been possible without the various contributions from the following people and organizations:
 

### 2020-12-17 Thesis/Drafts/Buell-PHYS799-ThesisDraft3.tex
Added Draft 4, Fixed some figures

@@
 
-\bibitem{UnivIowa}
-University of Iowa Electronic Music Studios home page- \textit{http://theremin.music.uiowa.edu/}
-
-\bibitem{White}
-White, Harvey Elliott, and Donald H. White. \textit{Physics and Music: the Science of Musical Sound}. Dover Publications, Inc., 2019.
-
-\bibitem{Zhang}
-Zhang, Tong, and C.-C.
-Jay Kuo.
-“Content-Based Classification and Retrieval of Audio.” \textit{Advanced Signal Processing Algorithms, Architectures, and Implementations VIII}, 2 Oct.
-1998, pp.
-432–443., doi:10.1117/12.325703.
+^{•}
 

### 2020-12-17 Thesis/Drafts/Buell-PHYS799-ThesisDraft4.tex
Added Draft 4, Fixed some figures

--- 2020-12-16 Thesis/Drafts/Buell-PHYS799-ThesisDraft3.tex
@@
 We explore this in section (\ref{sec-PerfEval}).
-Results of all metrics are computed with the \textit{numpy},\textit{scipy}, and \textit{scikit learn} python modules \cite{numpy,scipy,sklearn}.
-All performance visualizations are produced with the \textit{matplotlib} python package \cite{matplotlib}.
+Results of all metrics are computed with the \textit{numpy},\textit{scipy}, and \textit{scikit learn} python modules \cite{Numpy,Scipy,Sklearn}.
+All performance visualizations are produced with the \textit{matplotlib} python package \cite{Matplotlib}.
 
@@
 
-\paragraph*{}A Neural Network is a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Goodfellow,Loy}.
+\paragraph*{}A neural network is a model of a mathematical function, composed of several smaller mathematical functions called \textit{layers} \cite{Goodfellow,Loy}.
 Each layer represents an operation that takes an input, and returns an output .
@@
 
-\paragraph*{}Other than inspiration from the brain, Neural Networks are named \textit{networks} due to their successive chained or nested composition nature.
-A standard representation of a neural network is often a linked list or computational graph structure \cite{Goodfellow}.
+\paragraph*{}Other than inspiration from the brain, neural networks are named \textit{networks} due to their successive chained or nested composition nature.
+A standard representation is often based on a linked list or computational graph structure \cite{Goodfellow}.
 This maps out exactly how the repeated compositions are structured and organizes the flow of information in more complicated networks.
@@
 (\ref{eqn-altLayerFunction}), each function feeds directly into the next as to form a chain-like computational graph \cite{Goodfellow}.
-There are multiple type of layers that we use to construct the network in this project, but the two most important are called a \textit{dense} layer and a \textit{convoltuion} layer.
-These layers each contain a set of parameters which makeupa  subset of the trainable elements in $\Theta$.
+There are multiple type of layers that we use to construct the network in this project, but the two most important are called a \textit{dense} layer and a \textit{convolution} layer.
+These layers each contain a set of parameters which makeup a subset of the trainable elements in $\Theta$.
 These two layer functions can be divided into two portions: (i.) a Linear transformation, with a bias addition, and (ii.) an element-wise activation transformation.
@@
 Notice the terms arise by the many a parallel yellow and orange lines in each spectrogram in Fig.
-(\ref{fig-PropertiesChordophone}).
+(\ref{fig-PropertiesChordophones}).
 The verical position of any line is given by the linear frequency of the sinusoid, and the brightness is proportional to the coefficient of the combination.
@@
 Eq.
-(\cite{eqn-OpenClosedCol}) gives the lowest pitch that such an instrument with a length $L$ can play.
+(\ref{eqn-OpenClosedCol}) gives the lowest pitch that such an instrument with a length $L$ can play.
 Lower woodwinds such as bass clarinets, have a much longer vibrating air column that that of the much shorter piccolo, thus can produce considerably lower notes.
@@
 
+\bibitem{White}
+White, Harvey Elliott, and Donald H. White. \textit{Physics and Music: the Science of Musical Sound}. Dover Publications, Inc., 2019.
+
 \bibitem{UnivIowa}
 University of Iowa Electronic Music Studios home page- \textit{http://theremin.music.uiowa.edu/}
-
-\bibitem{White}
-White, Harvey Elliott, and Donald H. White. \textit{Physics and Music: the Science of Musical Sound}. Dover Publications, Inc., 2019.
 

### 2020-12-22 Thesis/Drafts/Buell-PHYS799-ThesisDraft4.tex
Proofreading more Thesis

@@
 The task of recognizing the source of a sound wave in a digital audio file is trivial and almost effortless to a human being in many cases, but is far more difficult for a computer to do.
-In order to automate source source identification, we have designed and constructed a multimodal neural network that can classify audio files by what musical instrument the sound most resembles.
+In order to automate audio source identification, we have designed and constructed a multimodal neural network that can classify audio files by what musical instrument the sound within it most resembles.
 The network uses two different input branches, one being a convolutional neural network (CNN), and the other, a multilayer perceptron (MLP).
@@
 
-\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan,Mierswa}.
+\paragraph*{}The ability to classify time-series data into unique categories has become a topic of much attention in the last few decades \cite{Khan,Mierswa}.
 From climate measurements, to financial reports, to audio-visual media, or to medicine, time-domain signals surround the modern world at every corner \cite{Virtanen}.
@@
 
-\paragraph*{}It has long been a goal of computer scientists and engineers alike to develop a program, algorithm, or machine that could perform a certain task to the level of human-being \cite{Bishop,Geron,Loy}.
+\paragraph*{}It has long been a goal of computer scientists and engineers alike to develop a program, algorithm, or machine that could perform certain tasks to the level of human-being \cite{Bishop,Geron,Loy}.
 While humans are intricate organisms capable of recognition or classification in many contexts, we do not have the ability to process millions of raw numerical values in the course of a few seconds.
 Similarly, modern computers are also complex systems that can filter through exabytes of information on a daily basis, but are not generally known for being able to distinguish cats from dogs \cite{Geron}.
-The compromise between humans and machines an algorithm called a \textit{neural network} that combines the computation speed of a computer with the decision-making power modeled from human brain \cite{Goodfellow,Levine,Loy}.
+The compromise between humans and machines an algorithm called a \textit{neural network} that combines the computational speed of a computer with the decision-making power modeled from a biological brain \cite{Goodfellow,Levine,Loy}.
 
 \paragraph*{}In this work, we have developed an automated neural network program that can classify digital sound waves as one of $37$ musical instruments that it most closely resembles.
-The general use of machine learning algorithms for audio information classification or identification is well explored, and a topic of much modern research \cite{Khan,Liu,Mierswa,Serizel,Zhang}.
+The general use of machine learning algorithms for audio information classification or identification is well explored, and is a steady topic of modern research \cite{Khan,Liu,Mierswa,Serizel,Zhang}.
 From previous work, it has been found that various types of audio classification are possible, and are still being expanded upon.
@@
 
-\paragraph*{}As the name implies, a neural network is a computation a model or graph that is loosely structured off of the biological brain \cite{Geron,Loy}.
+\paragraph*{}As the name implies, a neural network is a computational a model or graph that is loosely structured off of the biological brain \cite{Geron,Loy}.
 Where a biological brain uses physical connects through axons to exchanges chemicals to communicate information, a neural network uses a chain of mathematical operations to communicate information \cite{Goodfellow}.
@@
 \paragraph*{}This project includes a number of steps from taking raw input data to the final classification program.
-In this section, we provide a very high level outline of the parts of this projects and show how each one influence the final product.
+In this section, we provide a very high level outline of the parts of this project and show how each one influences the final product.
 Additionally, we indicate the sections in this thesis where the particular material is introduced and developed much more thoroughly.
@@
 
-\paragraph*{}The smaller functions that comprise $F^*$ are called \textit{layers} \cite{Loy,Goodfellow}.
+\paragraph*{}We implement this function in the form of a \textit{neural network}.
+The smaller functions that comprise $F^*$ are called \textit{layers} \cite{Loy,Goodfellow}.
 Each type of layer performs a different operation and processes different types of input.
@@
 (\ref{subsec-NerualNetworkIntro}) and (\ref{subsec-NetworkStructure}), we introduce the nature and structure of a neural network and how it can use used in part to solve this problem.
-We discuss it is inspired from a biological brain and show how different layer types are influenced from the brain's functions as well as how they are used in this problem.
-Using information about the problem, we carefully design the inputs, outputs and structure of the neural network function to be able to complete this task in a practical manner.
+We discuss its inspired from a biological brain and show how different layer types are influenced from the brain's functions as well as how they are used in this problem.
+Using information about the problem, we carefully design the inputs, outputs and structure of the function to be able to complete this task as needed.
 
@@
 \paragraph*{}In order to train the neural network to be able to identify musical instrument sources, we need a suitable data set to present to the model as training and validation data.
-The models uses this data and corresponding labels in the training process to modify it's function to allow for it to complete the task.
-University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \cite{Philharmonia,UnivIowa}.
+The model uses this data and corresponding labels in the training process to modify its function to allow for it to complete the task.
+University of Iowa Electronic Music Studio, and the London-Based Philharmonia Orchestra each have a large collection of publicly available audio files \cite{UnivIowa,Philharmonia}.
 These files contain short segments of musical instruments performing a single note, and are labeled according to the instrument that produced the sound.
@@
 This stage is detailed in section (\ref{subsubsec-Preprocessing}).
-After the samples are formatted, we have produced a Python script with iterates through each new file and assigns a class label based on the title of the instrument.
-This has been design to account for the specific naming cases that arise.
-We assemble a dictionary-like structure of all training file with organizes the local file location of each sample and provides an integer and string label for all samples.
+After the samples are formatted, we have produced a Python script which iterates through each new file and assigns a class label based on the name of the audio file.
+This has been design to account for the specific naming cases that may arise.
+We assemble a dictionary-like structure of all training files with organizes the local file location of each sample and provides an integer class label and string class label for each sample.
 
@@
 
-\paragraph*{}The performance of a neural network is largely dependent of designing an appropriate set of predictors or features which represent the raw input given to the model.
-These inputs are designed to represent prolific properties of wave forms that can be expressed by a single or multiple numerical values.
+\paragraph*{}The performance of a neural network is largely dependent on designing an appropriate set of predictors or features which represent the raw input given to the model.
+These inputs are designed to represent prolific properties of audio data that can be expressed by a single or multiple numerical values.
 We detail these features in section (\ref{sec-Features}).
@@
 This network is designed to evaluate each input independently, and concatenate the results to produce a single outputted prediction.
-This hybrid architecture combines the predictive power of the both a multilayer perceptron and a convolutional neural network.
+This hybrid architecture combines the predictive power of both a multilayer perceptron and a convolutional neural network.
 Our neural network was implemented using the tools available with the \textit{Tensorflow} module \cite{Tensorflow}.
@@
 Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an solution that allows for a computer to \textit{learn} from labeled training examples in order \textit{teach} itself \cite{Bishop,Mitchell}.
-We choose to employ a neural network, which a computer algorithm that is designed to update itself to perform a task with increasing proficiency as it is presented with new information \cite{Geron2,Goodfellow,Levine,Mitchell}.
+We choose to employ a neural network, which is a computer algorithm that is designed to update pieces of itself in order to perform a task with increasing proficiency as it is presented with new information \cite{Geron2,Goodfellow,Levine,Mitchell}.
 
@@
 \end{quote}
-The result is a computer program that is reminiscent of the a brain in that it structured much like the brain, and can\textit{learn} from new data.
-We model operations with collections are artificial neurons that are capable of connect and interacting with other neurons \cite{Levine}.
+The result is a computer program that is structured much like the brain, and can\textit{learn} from new data.
+We model operations with collections of artificial neurons that are capable of connecting and interacting with other neurons \cite{Levine}.
 Where a biological brain uses connections of chemical and electrical exchanges to process input and make decisions, the computational counterpart uses arithmetic and numerical exchanges to similarly process input and make decisions \cite{Levine,Bishop}.
-Where a brain uses physical connection of neurons through axons, the neural network uses mathematical connections of neurons through mathematical operations \cite{Geron,Levine}.
+Where a brain uses physical connection of neurons through axons, the neural network uses mathematical connections of neurons through operations \cite{Geron,Levine}.
 We call the numerical value contained within an artificial neuron the \textit{activation} of that neuron \cite{Goodfellow,Geron}.
@@
 More conceptually, we can say that a listener is presented with a set of information $x$, which is air molecules vibrating near their tympanic membrane \cite{White,Olson}.
-That information is then passed into the brain where some function $F$ is used to model the incredibly complex set of neural connections.
+That information is passed into the brain where some function $F$ is used to model the incredibly complex set of neural connections.
 The output of that function is some label $y$, which the listener associates with a particular source \cite{Olson}.
@@
 
-\paragraph*{}The neural network function $F^*$ uses a set of parameters $\Theta$, to map those inputs, $x$ to outputs, $y$ \cite{Goodfellow,James,Virtanen}.
+\paragraph*{}The neural network function $F^*$ uses a set of parameters $\Theta$, to map those inputs, $x$ to predicted outputs, $y^*$ \cite{Goodfellow,James,Virtanen}.
 It is the process of updating the elements in the object $\Theta$ which allow us to train a neural network to perform the desired task.
-Similarly, it is the process of organizing and connecting neurons in the brain that allow humans to perform any specific task \cite{Geron,Levine}.
+Similarly, it is the process of organizing and connecting neurons in the brain that allow humans to perform a given task \cite{Geron,Levine}.
 Over the course of their lives, humans will be able to learn to match sounds to sources with relative ease, given the appropriate labels.
 In a similar manner, our neural network is presented a collection of predictors from sound files and a complementary set of labels indicating the source of each sound.
-This type of task is called \textit{classification}, which involves mapping the input data, $x$ to one of $k$ possible \textit{classes}, each represented by an integer, $0$ through $k-1$.
+This type of task is called \textit{supervised classification}, which involves mapping the input data, $x$ to one of $k$ possible \textit{classes}, each represented by an integer, $0$ through $k-1$.
 Each of the $k$ classes represents a particular musical instrument or sound source that could have produced the sound-wave in the audio file \cite{Goodfellow,Loy,Virtanen}.
@@
 \end{equation}
-Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-LinearTransform}).
+Where $x^{(l)}$ is the final activations for layer $(l)$ and $z^{(l)}$ is given in equation (\ref{eqn-LinearTransform}).
 $\sigma^{(l)}$ is some activation function which introduces the ability to account for complicated non-linear decision boundaries which the neural network uses to make predictions.
@@
 (\ref{eqn-LinearTransform}) and Eq.
-(\ref{eqn-elementActivation}), for a layer $l$ , make up the function represented by that layer, as in Eq.
+(\ref{eqn-elementActivation}), for a layer $(l)$ , make up the function represented by that layer, as in Eq.
 (\ref{eqn-altLayerFunction}).
@@
 \paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer, or \textit{Fully-Connected} layer, was one of the earliest and most common function types used in artificial neural network models \cite{Geron2,Loy,McCulloch}.
-A dense layer is composed of a layer of \textit{artificial neurons}, each of which holds a numerical value within it, (usually a double-precision floating point number) called the \textit{activation} of that neuron.
-The activation of a dense layer are given by a linear combination of the layers inputs.
+A dense layer is composed of a collection of \textit{artificial neurons}, each of which holds a numerical value within it, (usually a double-precision floating point number) called the \textit{activation} of that neuron.
+The activations of a dense layer are given by a linear combination of the layers input activations.
 This idea was developed from McCulloch and Pitts' work \cite{McCulloch} in attempting to model cognitive processes as mathematical functions by connecting neurons through a series of weighting values.
@@
 
-\paragraph*{}Convolution layers emerged from studying the brain's visual cortex, and have been used from image recognition related tasks for around 40 years.
+\paragraph*{}Convolution layers emerged from studying the brain's visual cortex, and have been used for image recognition related tasks for around 40 years.
 \cite{Geron,Loy}.
@@
 We implement a convolutional layer $f^{(l)}$ by creating a series of $K$ weighting matrices, called \textit{filters}, each of size $m \times n$, where $m,n \in \mathbb{Z}$.
-Often we choose $m = n$ and we call the shape the \textit{convolution kernel size} \cite{Loy, Goodfellow}.
+We call the shape the \textit{convolution kernel size}, and often choose $m = n$ \cite{Loy, Goodfellow}.
 The step size in each of the two dimensions is known as the \textit{stride size}, which we choose to be $1$ in both dimensions.
@@
 
-\paragraph*{}In general, for an $M \times N$ input, with kernel size $m \times n$, with stride size $1 \times 1$, and $K$ feature maps.
+\paragraph*{}In general, for an $M \times N$ input, with kernel size $m \times n$, with stride size $1 \times 1$, and $K$ feature maps:
 \begin{equation}
@@
 \paragraph*{}Pooling layers, such as maximum pooling, average pooling, or similar are typically placed after a layer or a set of layers of convolution \cite{Loy}.
-The purpose of this arrangement is to reduce the number of activations by selecting only the largest valus, thereby dropping the width of the model and ensuring only features with large activation values are preserved \cite{Geron,Loy,Goodfellow}.
-This layer "non-trainable" because it does not use any weights or transformations, only a fixed procedure that cannot be updated.
+The purpose of this arrangement is to reduce the width of the model and ensure that only features with large activation values are preserved \cite{Geron,Loy,Goodfellow}.
+This layeris considered to be "non-trainable" because it does not use any weights or transformations, only a fixed procedure that cannot be updated.
 Below, we detail what the "Call" method for a 2D maximum pooling layer might look like.
@@
 
-\FOR {$i \in [0,1,...,M-2,M-1$}
-	\FOR {$j \in [0,1,...,N-2,N-1$}
+\FOR {$i \in [0,1,...,M-2,M-1]$}
+	\FOR {$j \in [0,1,...,N-2,N-1]$}
 		\item Collect local activations in $P$, zero pad if necessary
@@
 Note that a batch of samples will still be two-dimensional.
-This is not like projecting the data into a lower dimension, but rather is the reorganization of values into an array of a row of column array.
+This is not like projecting the data into a lower dimension, but rather is the reorganization of values into a row or column array.
 We can use function notation to express this for a single sample as:
@@
 \paragraph*{}Flattening Layer are most commonly used to prepare activations for entry into dense layer or series of dense layers.
-For example, an image may contain two or three dimension, and convolution over it will return two or three dimensional activations per sample.
-Each sample must be compressed into one dimensions so that it can be processed by dense layers.
-This layer also is "non-trainable" because it does no use any weights or transformations, only a fixed procedure.
+For example, an image may contain two or three dimensions, and convolution over it will return two or three dimensional activations per sample.
+Each sample must be compressed into one dimension so that it can be properly processed by dense layers.
+This layer also is "non-trainable" because it does not use any weights or transformations, only a fixed procedure.
 
@@
 For the convolution or dense layer, activation functions make up the second transformation step as in Eq.
-(\ref{eqn-elementActivation}) which allows for the neural network to produce non-linear decisions.
+(\ref{eqn-elementActivation}) which allows for the neural network to model complicated non-linear decision boundaries that arise in real-world problems.
 In this section, we detail the activation functions used in this classification model.
@@
 \paragraph*{}The Rectified Linear Unit (ReLU) activation function acts element-wise on the activations in a given layer.
-If the activation of a neurons is non-negative, the value is untouched, otherwise a $0$ is returned.
+If the activation of a neuron is non-negative, the value is untouched, otherwise a $0$ is returned.
 For an input activation array $x$, ReLU is defined by:
@@
 \end{equation}
-The arrays $W^{(l)}$and bias vectors $b^{(l)}$ are not trainable parameters themselves, but the the floating-point entries within them are the values that can be adjusted.
+The arrays $W^{(l)}$and bias vectors $b^{(l)}$ are not trainable parameters themselves, but the floating-point entries within them are the values that can be adjusted.
 Each element in this set may contain hundreds or thousands of parameters, so we represent these indirectly as parameters within their respective layers.
-We choose this representation of $\Theta$ for notation simplicity.
+
+\paragraph*{}We choose this representation of $\Theta$ for notation simplicity.
 Note that not all layers have trainable parameters, and activations functions themselves are not trainable, but fixed functions.
@@
 For the network that we have designed in this project, there are roughly $33,000$ parameters across $20$ layers.
-In this sections we motivate and explore how the we can update the parameters in $\Theta$ as to train the neural network.
+In this section we motivate and explore how the parameters in $\Theta$ re updated as to train the neural network.
 
@@
 \end{equation}
+Note that in this case, $1$ can be the scalar value, or an appropriately shaped identity matrix.
 
@@
 Since a neural network is a computational graph with each layer represented by a node, it can take on a nearly infinite number of different shapes and structures \cite{Goodfellow,Virtanen}.
-The structure of the network defines the composition of it's function, $F^*$ as in Eq.(\ref{eqn-FunctionGraph}), and thus affects it's performance in completing any given task \cite{Geron}.
-The layer structure of the neural network is referred to as it's \textit{architecture}, and define it's \textit{hypothesis - space} \cite{Goodfellow}.
+The structure of the network defines the composition of it's function, $F^*$ as in Eq.(\ref{eqn-FunctionGraph}), and thus affects its performance in completing any given task \cite{Geron}.
+The layer structure of the neural network is referred to as its \textit{architecture}, and define the networks \textit{hypothesis - space} \cite{Goodfellow}.
 

### 2020-12-23 Thesis/Drafts/Buell-PHYS799-ThesisDraft4.tex
Organized Final Draft

@@
 To classify the audio files based on predicted sources, we aggregate and transform the activations from the final layers of each branch, and produce a single prediction label.
-We find that this architecture allows for reasonable classification performance, and demonstrates superior classification performance on average, when compared to either of it's constituent unimodal architectures.
-Training data for this experiment is from studio recordings of the Philharmonia Symphony Orchestra and the University of Iowa's Electronic Music Studios.
+We find that this architecture allows for reasonable classification performance, and demonstrates superior classification performance on average, when compared to either of its constituent unimodal architectures.
+Training data for this experiment is from studio recordings of the London Philharmonia Symphony Orchestra and the University of Iowa's Electronic Music Studios.
 
@@
 \paragraph*{}The ability to classify time-series data into unique categories has become a topic of much attention in the last few decades \cite{Khan,Mierswa}.
-From climate measurements, to financial reports, to audio-visual media, or to medicine, time-domain signals surround the modern world at every corner \cite{Virtanen}.
+From climate measurements, to financial reports, to audio-visual media, or to medicine, time-domain signals exist all over the modern world \cite{Virtanen}.
 In each context, the general idea is to place information into distinct categories called \textit{classes} based on inherent properties of the data.
@@
 Our model contains a convolutional neural network (CNN) that processes an image-like representation of an audio waveform, and a multilayer perceptron (MLP) that processes a list-like representation of an audio wave form.
-Each arm of the network is it's own computational graph that is designed to process it's respective inputs types.
+Each arm of the network is its own computational graph that is designed to process its respective inputs types.
 The activations at the end of each layer are concatenated into a new layer, which is further processed and then used to generate a single prediction.
-This output that is aggregated from two inputs shows on average, superior classification performance when compared to either of it's constituent unimodal architectures alone.
+This output that is aggregated from two inputs shows on average, superior classification performance when compared to either of its constituent unimodal architectures alone.
 
@@
 
-\paragraph*{}To ensure that these data sets are formatted consistently, we have designed a MATLAB program to read each audio file from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 24-bit depth.
+\paragraph*{}To ensure that these data sets are formatted consistently, we have designed a MATLAB program to read each audio file from its original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 24-bit depth.
 This ensures that all data will have a consistent format when features are extracted.
@@
 Additionally, each node contains a pointer "\textit{next}" which gives the next layer in the network chain.
-Each layer should also store it's linear activations, $z^{(l)}$ and it's output activations $x^{(l)}$ for training purposes.
+Each layer should also store its linear activations, $z^{(l)}$ and its output activations $x^{(l)}$ for training purposes.
 This algorithm is adapted from Goodfellow, \cite{Goodfellow}.
@@
 \cite{Geron,Loy}.
-The layer function get's it's name from it's implementation of the mathematical \textit{convolution} operation.
+The layer function get's its name from the implementation of the mathematical \textit{convolution} operation.
 The 2D discrete-convolution of function or 2D array $A[i,j]$ and $B[i,j]$ is given by \cite{Goodfellow}:
@@
 \end{equation}
-This operation repeats for each of the $K$ feature maps. Each maps has it's own $n \times m$ weighting matrix and appropriately shaped bias .
+This operation repeats for each of the $K$ feature maps. Each maps has its own $n \times m$ weighting matrix and appropriately shaped bias .
 
@@
 \begin{quote}
-A computer program is said to learn from experience $E$ with respect to some class of tasks $T$ and performance measure $P$, if it's performance at tasks in $T$, as measured by $P$, improves with experience $E$.
+A computer program is said to learn from experience $E$ with respect to some class of tasks $T$ and performance measure $P$, if its performance at tasks in $T$, as measured by $P$, improves with experience $E$.
 \end{quote}
-Without any direct human intervention, a model must update itself to improve it's performance at a give task as new information is presented to it.
+Without any direct human intervention, a model must update itself to improve its performance at a give task as new information is presented to it.
 To do this, the model must be constructed with a training procedure in mind.
@@
 This sample is represented by the feature-vector $x^{(0)}$, with an expected outcome given by the one-hot-encoded vector $y$.
-After the network finishes processing, it's output activations, given by the vector $x^{(L-1)}$, also noted as $y^*$, represents the prediction for the class label.
+After the network finishes processing, its output activations, given by the vector $x^{(L-1)}$, also noted as $y^*$, represents the prediction for the class label.
 For a reasonably trained model, we expect the vector $y^*$ to be "similar" to $y$, indicating that model has made a a reasonable prediction with the given input values.
@@
 A standard stochastic gradient-based or batch gradient descent learning algorithm can be fast, but are often prone errors such as vanishing or exploding gradients \cite{Geron,Goodfellow,Loy}.
-To combat this, model must often implement an optimizer that is more stable, and robust in it's ability to drive the cost function to a successively lower value.
+To combat this, model must often implement an optimizer that is more stable, and robust in its ability to drive the cost function to a successively lower value.
 
@@
 Since a neural network is a computational graph with each layer represented by a node, it can take on a nearly infinite number of different shapes and structures \cite{Goodfellow,Virtanen}.
-The structure of the network defines the composition of it's function, $F^*$ as in Eq.(\ref{eqn-FunctionGraph}), and thus affects its performance in completing any given task \cite{Geron}.
+The structure of the network defines the composition of its function, $F^*$ as in Eq.(\ref{eqn-FunctionGraph}), and thus affects its performance in completing any given task \cite{Geron}.
 The layer structure of the neural network is referred to as its \textit{architecture}, and define the networks \textit{hypothesis - space} \cite{Goodfellow}.
@@
 To ensure that the classifier model performs adequately and consistently, we must choose these features to have high variance between classes, and low variance within each class.
-This enables a neural network to development clear decision boundaries between each unique class \cite{James,Serizel}.
+This enables a neural network to develop clear decision boundaries between each unique class \cite{James,Serizel}.
 To develop this set of features, we explore the physical and mechanical properties of musical instruments and the sounds that they create.
 
-\paragraph*{}Since computer algorithms such are neural networks are built to handle exclusively quantitative information, we must ensure that each property can be represented by a numerical quantity \cite{Geron,Levine}.
+\paragraph*{}Since computer algorithms such as neural networks are built to handle mostly quantitative information, we must ensure that each property can be represented by a numerical quantity \cite{Geron,Levine}.
 Where a human would use qualitative adjectives such as \textit{bright} or \textit{harsh} or \textit{percussive} to describe sound, computers require a numerical descriptor instead.
@@
 \paragraph*{}Idiophones in particular can be characterized by their \textit{transient response} \cite{White}.
-The transient response is the time-evolution response of the waveform in time, which we normally break into \textit{attack}, \textit{decay}, \textit{sustain}, and \textit{release}.
+The transient response is the time-evolution response of the waveform, which we normally break into \textit{attack}, \textit{decay}, \textit{sustain}, and \textit{release}.
 For most idiophones, the system is struck once and left to a free or dampened vibration; which we can mathematically model as a rigid body reacting to an impulse \cite{Hunter,Olson}.
@@
 \paragraph*{}The wave equation is a \textit{linear} partial differential equation which allows for a linear combination of solutions to form a sound wave.
-In the case of the taught finite string that is fixed at both ends, such a guitar, viola or cello, the a solution tends to take the form of a sine or cosine function \cite{Hunter, Taylor, White}.
+In the case of the taught finite string that is fixed at both ends, such a guitar, viola or cello, the a solution tends to take the form of a linear combination of sine or cosine function \cite{Hunter, Taylor, White}.
 Notice the terms arise by the many a parallel yellow and orange lines in each spectrogram in Fig.
 (\ref{fig-PropertiesChordophones}).
-The verical position of any line is given by the linear frequency of the sinusoid, and the brightness is proportional to the coefficient of the combination.
-The boundary conditions, and most forms of standard initial conditions allow for the each sinusoidal to fit exactly an integer or half-integer number wavelengths into the region $0 \leq x \leq L$ \cite{Haberman,Hunter}.
+The vertical position of any line is given by the linear frequency of the sinusoid, and the brightness is proportional to the coefficient of the combination.
+The boundary conditions, and most forms of standard initial conditions allow for the each sinusoidal to fit exactly an integer number wavelengths into the region $0 \leq x \leq L$ \cite{Haberman,Hunter}.
 Players of chordophones change pitch by shortening the length of the vibrating string or applying additional tension to the string.
@@
 
-\paragraph*{}Each chordophone instrument does produce a slightly different frequency spectrum, hence each provides a slightly different timbre to the listener, so differentiating between them is possible.
+\paragraph*{}Each chordophone instrument does produces a slightly different frequency spectrum, hence each provides a slightly different timbre to the listener, so differentiating between them is possible but can be challenging.
 Because of this, we find that the spectrogram representation of the waveform is so critical to classification success because the convolution layers allow for the detection of small variations in the frequency-time domain where humans would otherwise be unable to \cite{Loy,Virtanen}.
@@
 
-\paragraph*{}An aerophone is a musical instrument that produces sounds through the vibration of an air molecules in a column-like structure.
+\paragraph*{}An aerophone is a musical instrument that produces sounds through the vibration of air molecules in a column-like structure.
 This is the largest category of instruments that we have, and is commonly broken down into smaller subcategories such as \textit{woodwind} and \textit{brass} instruments.
@@
 \paragraph*{}We group sounds produced from non-physical musical instruments in this final category because they are not considered in the original Hornbostel-Sachs system.
-From our data set, this category includes the four simplest waveforms begin, sine waves, sawtooth waves, square waves, and triangle waves, as well as white colored noise \cite{White}.
+From our data set, this category includes the four simplest waveforms being, sine waves, sawtooth waves, square waves, and triangle waves, as well as white colored noise \cite{White}.
 These sounds have been produced synthetically through a MATLAB program specifically for this project.
@@
 
-\paragraph*{}Each of the five synthetically generated waveform types were produce to have a constant envelope with all time.
+\paragraph*{}Each of the five synthetically generated waveform types were produced to have a constant amplitude envelope with all time.
 This means that each waveform has no characteristic amplitude shape and the spectrogram shows no time-evolution of energy as expected.
@@
 
-\paragraph*{}Classification tasks require a set of inputs called \textit{predictors} or \textit{features} \cite{James,Loy,Serizel}.
-A feature is a quantitative, low-dimensional representation of a sample that conveys its important characteristics.
+\paragraph*{}Classification tasks require a set of inputs called \textit{predictors} or \textit{features}.
+A feature is a quantitative, low-dimensional representation of a sample that conveys its important characteristics \cite{James,Loy,Virtanen}.
 For example, in classifying types of animals, a feature could be the mass, volume or number of teeth on the animal.
 Typically, we produce a set of $p$ features for each sample and assemble them into a $p$-dimensional vector called a \textit{feature vector} which acts as a list of descriptive qualities of the sample \cite{Geron,James}.
-This list is presented to the neural network and used to
-Audio machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib describe the vitality of feature selection \cite{Khan}:
+This list is presented to the neural network and is transformed through the layers to produce an output.
+Audio machine learning researchers M.
+Kashif Saeed Khan and Wasfi G.
+Al-Khatib describe the vitality of feature selection \cite{Khan}:
 \begin{quote}
@@
 \paragraph*{}In the biological process of categorizing sound sources, the time-domain waveform is usually enough to match the sound to a source \cite{Olson}.
-However, a computer representation of a waveform is an array-like structure of values sampled discretely in time and volume \cite{Virtanen,Liu}.
-Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks so we must develop a set of features that can describe important properties of the waveform in a far more efficient manner \cite{Goodfellow,James,Serizel}.
-To ensure the construction of a suitable model, we derive features based from three representations of the audio file: (i) a spectrogram matrix, (ii) the time-space, and (iii) the frequency-space.
+However, a computer representation of a waveform is an array-like structure of values sampled discretely in time and amplitude \cite{Virtanen,Liu}.
+Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable for classification tasks so we must develop a set of features that can describe important properties of the waveform more efficiently \cite{Goodfellow,James,Serizel}.
+To ensure the construction of a suitable model, we derive features from three representations of the audio file: (i) a spectrogram matrix, (ii) time-space, (iii) the frequency-space.
 It is important to note that although this algorithm will map audio files to source instruments, it will never actually be presented with a waveform directly, and instead will rely solely on the features to make predictions.
@@
 For samples $x^{(a)}$ and $x^{(b)}$ that belong to the same class, we expect the vector to be similar, $x^{(a)} \approx x^{(b)}$ in some way.
-This indicates that the two samples lie "close together" in space.
-Similarly, for samples $x^{(c)}$ and $x^{(d)}$ that belong to different classes, we expect the vectors to be very different, indicating that the two sample lie "far apart" in space.
+This indicates that the two samples have similar properties in this space.
+Alternatively, for samples $x^{(c)}$ and $x^{(d)}$ that belong to different classes, we expect the vectors to be very different, indicating that the two samples have very different properties in this space.
 Note that this is an idealization, and not always the defining case for the decision function behavior.
@@
 \end{quote}
-This is to say, features should \textit{ideally} form non-overlapping groups or bubbles that allows classifiers to effectively differentiate categories.
+This is to say, features should \textit{ideally} form non-overlapping groups or bubbles that allows the classifier model to effectively differentiate categories.
 Given the complexity of real-world problems, this is an often unobtainable \cite{Goodfellow,James}.
 Under the right circumstances, classifiers can still produce parameters that allow for reasonable performance \cite{Geron,Loy}.
-In practice, a neural network does not rely on comparing the norms of different samples in feature space, but rather uses something called a \textit{decision boundary}.
+In practice, a neural network does not rely on comparing the vectors directly for classification, but rather uses something called a \textit{decision boundary}.
+
+% ===============================
 
@@
 A $k$- categories classifier contains $k$ output neurons, each one representing a different class.
-When a set of features is presented to the classifier, the value contained within each neuron is the "confidence" on the interval $[0,1]$ that a sample belongs to that class.
+When a set of features is presented to and transformed by the neural network, the value contained within each output neuron is the "confidence" on the interval $[0,1]$ that a sample belongs to that class.
 For example, if neuron $q$ has an activation value of $0.25$, we say that there is a $25\%$ chance that the sample belongs to class $q$.
@@
 To explore decision boundaries, consider a simplified toy data set with a 2D feature space for a classifier that must only discern between \textit{Class A} and \textit{Class B}.
-We can visualize each sample in this 2D space, and color-code each sample according according to it's class label as in Fig.
+We can visualize each sample in this 2D space, and color-code each sample according to its class label as in Fig.
 (\ref{fig-LinSep1}).
@@
 
-\paragraph*{}In the case of these chosen, features, we can see a clear, well-defined separation between samples in each class.
+\paragraph*{}In the case of these chosen features, we can see a clear and well-defined separation between samples in each class.
 In practice, this is rarely the case, but shows graphically an example where a linear decision boundary arises \cite{James}.
@@
 \end{center}
-\caption{Feature Space with near linear non-separability between two classes}
+\caption{Feature Space with linear non-separability between two classes}
 \label{fig-LinNonSep}
@@
 Since the elements of the DFT matrix lie on the complex unit circle, each real-valued analysis frame will be moved into complex space.
-This means we compute the element-wise product of the transformed signal matrix and it's complex-conjugate matrix.
+This means we compute the element-wise product of the transformed signal matrix and its complex-conjugate matrix.
 This is the $N \times k$
@@
 
-\paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses it's equilibrium point.
+\paragraph*{}The zero crossing rate (ZXR) of a signal or frame is use to measure how many times that a signal crosses its equilibrium point.
 This can be computed per total sound wave, per analysis-frame, or per unit time.
@@
 \paragraph*{}The frequency center-of-mass (FCM) for an audio file provides a representation of how overtones and energy is distributed in the signal's frequency domain.
-As with the temporal center-of-mass, we treat each column of the $S$ matrix as it's own one-dimensional mass distribution, and compute the center of mass of each column.
+As with the temporal center-of-mass, we treat each column of the $S$ matrix as its own one-dimensional mass distribution, and compute the center of mass of each column.
 This encodes the FCM for a single analysis frame (in frequency-space) in the waveform.
@@
 The exact ratio of sizes between these subsets varies depending on the task \cite{Goodfellow,Geron2,Mitchell}, however we choose to generally use around $90\%$ training samples and $10\%$ testing samples.
-If the model performs well within it's training subset, but poorly within the testing subset, this can indicate a model that is \textit{overfitted}, and will not perform well on other unseen samples \cite{Geron}.
+If the model performs well within its training subset, but poorly within the testing subset, this can indicate a model that is \textit{overfitted}, and will not perform well on other unseen samples \cite{Geron}.
 
@@
 We use the remaining $K-1$ subsets as training data.
-We fit the model with the data and labels to produce a model $F^{*(k)}$ which as set of parameters $\Theta^{k}$.
-We return the the test set, and run predictions on this unseen data subset.
+We fit the model with the data and labels to produce a model $F^{*(k)}$ which trains a set of parameters $\Theta^{(k)}$.
+We return the the test set, $X^{(k)}$ and run predictions on this unseen data subset.
 We compare those predictions to the corresponding set of labels $Y^{(k)}$ and evaluate the result of any selected performance metrics.
@@
 
-\paragraph*{}In the case of the multi-category classifier, it is important that we choose the appropriate performance metrics to confirm that the network is completing it's assigned as as expected \cite{Geron}.
-While the neural network itself uses the cost function as it's sole objective to optimize, we also require a set of more human-readable functions.
-For example, an average loss score of $1.075$ over a given subset of previously unseen samples provides us with no real information as to how well the network is performing at it's designed task.
+\paragraph*{}In the case of the multi-category classifier, it is important that we choose the appropriate performance metrics to confirm that the network is completing its assigned as as expected \cite{Geron}.
+While the neural network itself uses the cost function as its sole objective to optimize, we also require a set of more human-readable functions.
+For example, an average loss score of $1.075$ over a given subset of previously unseen samples provides us with no real information as to how well the network is performing at its designed task.
 In this section, we introduce a set of functions and metrics that allow for a more tangible interpretation of the model's performance.
@@
 Some models allow for the ability to adjust the threshold of the decision function.
-This means that by changing a few parameters that are external to the classifier itself, we can change how sensitive or specific a model is when making it's class decision.
+This means that by changing a few parameters that are external to the classifier itself, we can change how sensitive or specific a model is when making its class decision.
 In the case of this multi-category classifier, this is somewhat like modifying the generated decision boundaries as to change the outputted probability distribution.
@@
 	\end{subfigure}	
-	\caption{Confusion matrices, each is averaged over 10 folds of cross validation. Recall that each integer represents a class labeled, as given in Tab. (\ref{fig-ClassList})}
+	\caption{Confusion matrices, each is averaged over 10 folds of cross validation. Recall that each integer represents a class label, as given in Tab. (\ref{fig-ClassList})}
 	\label{fig-MultimodalConfs}
@@
 
-\paragraph*{}Comparing the results within each class, as averaged over $10$ folds of cross validation indicates that our model performs very well at the ability to a match a sound waves in digital audio files to their sources.
+\paragraph*{}Comparing the results within each class, as averaged over $10$ folds of cross validation indicates that our model performs very well at the ability to match a sound wave in a digital audio files to its source.
 We see this behavior in the plots in section (\ref{subsec-ClassScores}) as well as the confusion matrices in Fig.
 (\ref{fig-MultimodalConfs}).
-For the chosen set of classes, features and architecture, the model can generalize to new information allowing it to distinguish between different types of musical instruments reasonably well for samples that it has not yet interacted with.
+For the chosen set of classes, features, and architecture, the model can generalize to new information allowing it to distinguish between different types of musical instruments reasonably well for samples that it has not yet interacted with.
 Additionally, we show that the predictive power of the model improves through our development of the multimodal architecture.
@@
 (\ref{fig-MultimodalConfs}), we see a relatively small entry in $C_{0,0}$ (alto flutes) compared to $C_{14,14}$ ( English horn).
-This indicates that fewer correction predictions were made, and the normalized matrix shows that fewer predictions were made at all.
+This indicates that fewer correct predictions were made, and the normalized matrix shows that fewer predictions were made at all.
 Contrast this with the English horn having a dark red square in both matrices shows many predictions, and many correction predictions.
-Future work could explore how classification performance would be affected when weighting each class inversely to it's number of samples in the data set.
+Future work could explore how classification performance would be affected when weighting each class inversely to its number of samples in the data set.
 This would allow each class to be weighted uniformly in the training process and may potentially mitigate some of the variability of the performances across classes.
@@
 In addition to new features, it would be beneficial to further study the distribution of samples in feature space and execute some form of $K$-best features algorithm.
-This would indicate which of the  chosen predictors consistent or inconsistent with our requirements of intra-class and inter-class variability.
-
-\paragraph*{}In addition to input features, it may be beneficial to group for the the related classes together.
+This would indicate which of the  chosen predictors are consistent or inconsistent with our requirements of intra-class and inter-class variability.
+
+\paragraph*{}In addition to input features, it may be beneficial to group for the related classes together.
 For example, violins and violas have very similar physical constructions, have very similar formant structures, and thus have very similar behaviors in our feature-space.
@@
 These signals are representations of chaotic systems that resemble some of the acoustic the periodic properties of digital audio waveforms.
-By using the automated classifier, we would like to test the versatility of the classifier when subject to samples that may differ drastically in oame ways from the training data set.
+By using the automated classifier, we would like to test the versatility of the classifier when subject to samples that may differ drastically in some ways from the training data set.
 This demonstration would be a fantastic exploration into the ability for the model to generalize, and the strength of the learned function parameters.
@@
 \paragraph*{}We conclude that on average, the hybrid neural network architecture in Fig.
-(\ref{fig-NetworkArchitecture}) exhibits superior classification performance over either of it's unimodal counterpart architectures.
+(\ref{fig-NetworkArchitecture}) exhibits superior classification performance over either of its unimodal counterpart architectures.
 In examining confusion matrices from both unimodal models in Fig.
@@
 
+\item[•]University of New Hampshire College of Engineering and Physical Sciences, Department of Physics and Astronomy, and Department of Mathematics and Statistics.
+
 \item[•]Dakota Buell, Tan Dao, Nathan Richard, and Morgan Saidel for consultation on physics, mathematics, and programming topics.
 
-\item[•]Madeline Edwards and John Parker for differing me to this project, as well as constant support and consultation on mathematical topics.
+\item[•]Madeline Edwards and John Parker for differing me to this project, and consultation on mathematical topics.
 

### 2021-01-03 JMMPaper/JMM-Paper-v0.tex
Create JMM-Paper-v0.tex

% ================
% Landon Buell, Kevin Short
% JMM Paper
% PHYS 705.01 - Lab00
% 21 Sept 2020
% ================

\documentclass[conference,twocolumn,letterpaper]{IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{color}
\usepackage{subfigure}
\usepackage[top=1.5cm,left=1.5cm,right=1.5cm]{geometry}

% ================================================================

\title{Musical Instrument Classification Using a Hybrid Neural Network}
\author{Landon H. Buell$^1$ and Kevin M. Short$^2$ \\
        $^1$lhb1007@wildcats.unh.edu and $^2$kevin.short@unh.edu\\
        $^1$Department of Physics and Astronomy\\
        $^2$Department of Mathematics and Statistics\\
        University of New Hampshire, Durham, New Hampshire, USA \\}
\date{December 2020}

% ================================================================

\begin{document}

\maketitle

% ================================================================================================================================

\begin{abstract}
    Classifying audio signals with machine learning has become an important topic of research in the past few years. Models often involve the input of a 2-D spectrogram or 1-D feature vector into a unimodal network such as a Convolutional Neural Network (CNN) or Multilayer Perceptron (MLP). In this study, we explore automatic classification of musical instruments using new hybrid neural-network architecture that combines the CNN and MLP models and provides superior performance over models that rely solely on one or the other. This hybrid network uses two branches, one being a CNN to process an image-like 2-D spectrogram, and the other being an MLP to process a 1-D feature vector. Within the model, a hidden layer combines activations from the two branches by concatenating them into a single 1-D dense layer, thus all predictions are a product of both branches. We describe in detail the creating of the spectrogram and features, as well as how they influence the chosen network architecture. We finish with a practical demonstration that uses this classifier model to match waveforms from a chaotic music synthesizer to real-world musical instruments. Training data is from studio recordings of the Philharmonia Symphony Orchestra and University of Iowa's Electronic Music Studios
\end{abstract}

% ================================================================================================================================

\section{Introduction}
\label{sec:Intro}

% ================================================================

Digital audio analysis and classification has become a very prolific field in the last few years. The exact nature of each task can differ drastically from archival management, to security, or to commercial usage. In each case, we seek to place audio files into distinct categories called \textit{classes} based in inherent properties within the data \cite{James,Khan,Liu}. Consider a collection of audio files, each containing a single note performed by some musical instrument and the task of matching the contents of the file to the instrument that it most closely resembles. This type of classification task is near trivial for humans, but given the volume of audio data in the modern world, it is impractical at a large scale. However, a computer has no difficulty processing large volumes of raw information, but encoding an explicit instruction set for classification is unreasonable. For this reason, we turn to a \textit{neural network} to combine the computational efficiency of a computer, with the decision-marking architecture of a brain \cite{Geron}.

A neural network is a machine learning model that allows a set of inputs, $x$, called \textit{features}, to be transformed into a set of outputs, $y$,  called \textit{predictions} using a set of \textit{parameters}, $\Theta$ \cite{Geron,Goodfellow,Virtanen}. Audio classification with machine learning is also a well-explored field, with much research in developing an appropriate set of features, also called \textit{predictors}, for input \cite{James,Liu,Mierswa,Zhang}. Since the each classification task or data set may differ greatly from any other, each model often requires a unique combination of features which allows for the best possible performance \cite{Virtanen}. For musical instrument classification we have chosen predictors that represent the contents of an audio file using two different \textit{modalities}. We call this type of classification \textit{multimodal learning} \cite{Ngiam}.

Multimodal learning differs from other types of supervised learning in that a model accepts and processes multiple inputs that are each different representations of the same data sample. Data sets that include or can be transformed into audio + visual, audio + text, or even text + text information, are all examples of multimodal data sets \cite{Li}. For digital audio classification, we have chosen to represent the contents of an audio file by decomposing it into \textit{image + vector} information format. We do this by constructing a 2D spectrogram and a 1D vector of features from the same waveform. Data from these different modes encodes complementary information which allows a model to develop parameters that can more thoroughly describe a sample when compared to it's unimodal learning methods \cite{Li}

To account for this multimodal input, we have constructed a \textit{hybrid neural network} that utilizes two input branches, each with its own set of layers to process an input mode. The spectrogram image is transformed with a Convolutional Neural Network (CNN) which uses layers of 2D convolution and 2D pooling to generate a feature map, which is then flattened and transformed by repeated matrix-vector equations, this is visualized on the left side of Fig. (\ref{fig:Architecture}). The feature vector input is transformed through multiple matrix-vector equations which can be seen on the right side of Fig. (\ref{fig:Architecture}). The activations for each sample in each branch are concatenated into a single layer, which is further transformed into a single output prediction found at the bottom on Fig. (\ref{fig:Architecture}). This means that the neural network learns a set of parameters which allows for mapping of \textit{both} input modes into a single prediction. Since the properties of the input features are critically important to classification success, multi-representation learning shows a great deal of promise and wide spread applicability \cite{Khan,Li,Liu,Virtanen}. We find the the implementation of this hybrid architecture demonstrates an average superior classification performance when compared to either of its constituent unimodal architectures.

% ================================================================================================================================

\section{The Neural Network}
\label{sec:NeuralNetwork}

% ================================================================

\subsection{Structure}
\label{subsec:Intro}

A neural network is a type of machine learning algorithm that is inspired from the human brain \cite{Geron,Goodfellow}. Where biological brains are constructed from neurons and connected through axons, neural networks are constructed from artificial neurons and connected through weighting functions.

% ================================================================

\subsection{Input and Output}
\label{subsec:InputOutput}

The inputs to a neural network or any machine learning algorithm are called \textit{features} or \textit{predictors} \cite{James}. These are compact, low-dimensional representations of a data sample reflect its important characteristics \cite{Liu}. Features should be chosen as to have low variance within each class and high variance between classes. For digital audio classification of musical instruments, features of the same musical instruments should exhibit very similar properties, while features from difference musical instruments should exhibit non-similar properties. In any learning algorithm, the role of feature extraction is to translate the raw information into descriptors that maximize the classification performance \cite{Virtanen}. Although the neural network will classify the musical instrument within the digital audio sample, it will never interact with the raw waveform directly, instead will rely solely on these features. Suppose we use $p$ predictors, for a classifier model. These features are usually combined into a single vector-like object for each sample, and then presented as input to the neural network \cite{Geron}. We detail the classification features for this neural network in section (\ref{subsec:Features}).

The outputs to a classification neural network encodes the prediction that model has made for a particular sample. For a classifier with $k$ classes, there are $k$ output neurons transformed such that the sum of the activations 
neurons to be treated as a probability density \cite{Goodfellow,James}.  The neuron with the highest activation value is the class that it is chosen to belong to. For classification of musical instruments, each class represents a musical instrument type. We use $37$ classes of instruments ranging from woodwinds, to brass, to strings, to mallet percussion, to synthesizers. Each audio file contains exactly one musical instrument sustaining one note.

% ================================================================

\subsection{The Cost Function}
\label{subsec:CostFunction}

A neural network is trained by providing a batch of input samples $X$, with a corresponding set of expected predictions $Y$. Each sample $x$ in the batch input is expected to produce the label $y$, and when passed through the network, creates the prediction $y^*$. For an untrained network, we anticipate that $y^*$ and $y$ may differ greatly- meaning that the prediction is very different that the expected output, and classification performance is likely to be very poor. Since we know each sample in the data set to contain one, and only one musical instrument, we \textit{one-hot-encode} the expected label $y$. For any sample $x^{(i)}$ that belongs to class $j$, we have a corresponding target vector $y^{(i)}$ given by:
\begin{equation}
    \label{eqn:OneHotEnc}
    y^{(i)} = \big[ y_{0} , y_{1}, ... , y_{j}, ... , y_{k-1} \big] = \big[ 0, 0, ... , 1, ... , 0 \big]
\end{equation}
The same sample will produce a similarly sized vector, $y^{*(i)}$, which all elements sum to $1$.

To quantity the difference between $y$ and $y^*$, we introduce a \textit{cost function}, $J(y,y^*)$ which is also called an objective function or a loss function \cite{James}. The exact cost function used can differ based on the nature of the machine learning model or task, but typically multiple - category classification tasks use a \textit{categorical cross-entropy} (CXE) function \cite{Geron,Goodfellow}. The CXE cost for a single sample is defined as \cite{Goodfellow,Virtanen}:
\begin{equation}
    \label{eqn:CXELoss}
    \text{CXE}[y,y^*] = - \sum_{i=0}^{k-1} y_{i} \ln(y^*_{i})
\end{equation}
Since $y$ is one-hot-encoded, the only non-zero term in the sum is $y_{j} \ln(y^*_{j})$, where $y^*_{j} \in [0,1]$ This returns a negative number, which we multiple by $-1$ to always yield a positive cost. When a sample produces $y^*_{j} << 1$, the CXE cost returns a large value and when $y^*_{j} \approx 1$, then the CXE cost returns a small value. We provide a visualization of this behavior in Fig. (\ref{fig:CXELoss}).

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.14]{figures/CXELoss.png}
    \caption{Categorical Cross Entropy Cost Function given values for $y^*_{j} \in [0,1]$}
    \label{fig:CXELoss}
\end{figure}

We characterize the cost function as producing a value inversely proportional to the prediction confidence- A large cost value indicates a \textit{poor} prediction label and a low cost value indicates a \textit{good} prediction label \cite{James,Virtanen}. Thus, we expect a trained neural network to produce consistently low cost function values across all samples in a data set. When a neural network does return consistently low cost function values for previously unseen samples, we consider it to be a \textit{fitted} or \textit{trained} network \cite{Geron,Goodfellow,James}.

% ================================================================

\subsection{The Training}
\label{subsec:CostFunction}

A neural network makes predictions by successive transformations of input features through layer functions until a final output array is produced. Each layer $f^(l)$, of the model is a function that contains a set of parameters $\Theta^{(l)}$ which is used to transform activations which are passed to the next layer in the chain \cite{Goodfellow}. The process of training the network is the manipulation of these parameters in each layer, such that each input $x$ can produce a reasonably accurate output, $y^*$. Since we can quantify the difference between the expected output and the given output with a cost function, we can use this as a metric for measuring how "trained" a model is \cite{James}. Specifically, we train a neural network by \textit{optimizing} the parameters in each layer to allow for this consistently low cost function value \cite{Geron}. Note that although we are interested in classification performance, we instead optimize the cost function under the assumption that doing so will also improve the performance. This is called indirect optimization \cite{Goodfellow}.

Since a the function chain that comprises a neural network can become exceedingly complicated for deeper and wider networks, producing a single analytical expression for the optimization of every single is either impractical or impossible. We instead optimize the network with a numerical iterative-based method called \textit{gradient descent} \cite{Geron,Goodfellow}. Gradient descent is the process of (i.) computing the gradient of the cost function with respect to every element in $\Theta$ and (ii.) adjusting each parameter in $\Theta$ according to the gradient. This is typically done with groups of samples at the same time called \textit{batches} to improve computational efficiency.

% ================================================================================================================================

\section{Features and the Multimodal Network}
\label{sec:Features}

% ================================================================

\subsection{Convolutional Network Features}
\label{subsec:Features}

A spectrogram is a 2D representation of the energy distribution as a function of time and frequency in a periodic waveform-like signal \cite{Virtanen}. The spectrogram is particularly useful because it allows us to examine the frequency composition of a signal, and how that composition evolves over time. On a typical spectrogram, the passing on time is shown on the x-axis, and frequency is shown on the y-axis. Because it is represented as a 2D array or floating-point numbers, the spectrogram is effectively an image-like representation of a sound wave. Since each musical instrument produces it's own harmonic structure, and transient response, each instrument can be identified by patterns within the spectrogram. This means than when only use this modality, the audio classification becomes very similar to an image classification task \cite{Ngiam}. We provide a few example spectrograms for reference in Fig. (\ref{fig:Example Spectrograms}).

\begin{figure}[h]
    \centering
    \subfigure[]{\includegraphics[width=0.45\textwidth]{figuresSpectrograms/AltoSax-A4.png}}
    \subfigure[]{\includegraphics[width=0.45\textwidth]{figuresSpectrograms/GUITAR-B2.png}}
    \caption{Spectrograms of (a) an alto saxophone playing an $A4$ and (b) an acoustic guitar playing a $B2$}
    \label{fig:Example Spectrograms}
\end{figure}

A spectrogram is produced by applying the technique of \textit{frame-blocking} to a waveform to produce a matrix of short-time analysis frames \cite{Liu,Virtanen}. We choose each frame to contain $N = 1024$ samples, with a $768$ sample overlap between adjacent frames. 
\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/AnalysisFrames.png}
    \caption{Analysis frames in relation to a full waveform. This figures has been adapted from \cite{Liu}.}
    \label{fig:AnalysisFrames}
\end{figure}
We organize the analysis frames into a matrix, $A$ with shape $N \times k$, such that each row is a frame. We apply a Hanning window of length $N$ to each row of $A$. This eliminates discontinuities at the edges of each analysis frame, and allows for a cleaner transform into frequency-space \cite{Virtanen}.

% ================================================================

\subsection{Multilayer Perceptron Features}
\label{subsec:Features}

The feature is this section are derived from the time-domain or frequency-domain representation of a waveform. Each feature explored represents the values computed from each audio file, which are then assembled into a 1D array-like object called a feature vector. This vector is provided as input to the MLP branch of the neural network, which can be found on right side of Fig. (\ref{fig:Architecture}). To ensure a consistency of all extracted features, all waveforms have been truncated or zero-padded to contain a consistent $M$ samples.

\begin{enumerate}

\item\textbf{Time Domain Envelope} (TDE) - 
The TDE is a method of approximating the energy in the full or subset of the time-series waveform of a signal. We divide the waveform into $5$ non-overlapping analysis frames and compute the RMS energy of the waveform in each section. This allows for an approximation of the amplitude envelope of the time-domain signal \cite{Virtanen}. For a signal $s$, the RMS energy in the $j$-th frame containing $Q$ sample sis given by:
\begin{equation}
    \label{eqn:TDE}
    \text{TDE}_j[s] = \sqrt{\frac{1}{Q}\sum_{i=n}^{n+Q}s[i]^2}
\end{equation}
These features allow us to characterize the time-evolution of energy in a signal. Instruments with heavy attacks, and sudden decays show large TDE values in early frames, and low TDE values in later frames. Instruments with longer sustains will show consistently decaying TDE values throughout the duration of the file.

\item\textbf{Zero Crossing Rate} (ZXR) - 
The ZXR of a waveform measures how many time that a signal crosses it's equilibrium value, often normalized per unit time. This feature is commonly used to differentiate speech from music because speech often has a more jagged and less periodic structure, giving it a characteristically higher ZXR value \cite{Virtanen,Khan,Zhang}. We adapt this feature to compute the zero-crossing rate over the full waveform. The zero crossing rate for a waveform $s$ with $M$ samples is given by:
\begin{equation}
    \label{eqn:ZXR}
    \text{ZXR}[s] = \frac{1}{2}\sum_{i=i}^{M-1}\Big| \text{sign}\big(s[i]\big) - \text{sign}\big(s[i-1]\big) \Big|
\end{equation}
Where $\text{sign}(x)$  returns $+1$ if $x > 0$, $−1$ if $x < 0$ and $0$ if $x = 0$. In generally, the zero crossing rate can also be used as a rough frequency measurement, where instruments that can produce higher fundamental frequencies often have higher ZXR values, where instruments that can produce lower fundamental frequencies have lower ZXR values \cite{Zhang}.

\item\textbf{Temporal Center of Mass} (TCM) - 
The TCM of a waveform computes approximately where in time, the energy of a waveform is centered around, and can conveniently summarize characteristics of the transient response into a single scalar value. The temporal center of mass of a signal $s$ with $M$ samples is given by:
\begin{equation}
    \label{eqn:TCM}
    \text{TCM}[s] = \frac{\sum_{i=0}^{M-1}i\big|s[i]\big|}{\sum_{i=0}^{M-1}\big|s[i]\big|}
\end{equation}
For instruments with heavier attacks and short decay and release times, such as plucked strings or percussion, we expect the energy of the waveform to be very early on, thus providing a very low TCM value. For instruments with shorter attacks, with long sustain and release times, such as bowed strings or woodwinds, we expect the energy of the waveform to be more spread out, thus have a higher TCM value.

\item\textbf{Auto Correlation Coefficients} (ACC) -
ACC's are rough estimates of the signal spectral distribution. They are computed by taking the dot product of a signal with a time-expedited variant of itself, then the normalized to lie between $0$ and $1$ \cite{Virtanen}. We can compute any number of ACC's and it's value will change according to the index chosen. In practice, it is common to compute the first $K$ ACC's, with the $k$-th ACC for a signal $s$, with $M$ samples is given by:
\begin{equation}
    \label{eqn:ACC}
    \text{ACC}_k[s] = \frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]}{\sqrt{\sum_{i=0}^{M-k-1}s^2[i]}\sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
\end{equation}
Dotting this signal with the time-shifted version of itself allows us to measure periodicity in frequency-space.

\item\textbf{Mel Frequency Ceptrum Coefficients} (MFCC) - 
In the MFCC computation process, a frequency spectrum is passed through overlapping triangle filter branks that are spaced according to the Mel scale \cite{Sahidullah}. This is done by calculating the dot product between the power spectrum of a signal and each of $R$ Mel filter banks, which yields an approximation of energy in that frequency band. These are called Mel Filter bank energies (MFBE's). Each MFCC is found by computing the inverse discrete cosine transform of the log of the MFBE's. For $R$ filter banks, the $k$-th MFCC is given by \cite{Virtanen}:
\begin{equation}
    \label{eqn:MFCC}
    \text{MFCC}_k[B] = \sqrt{\frac{2}{R}}\sum_{i=1}^{R}\log{(B[i])}
    \cos\Big(\frac{k(i-\frac{1}{2})\pi}{R}\Big)
\end{equation}
Where $B[i]$ is the $i$-th MFBE value. MFCC's allow for the investigation of periodicity in frequency-space, which would allow for the identification of overtones, echoes, etc.

\item\textbf{Frequency Center of Mass} (FCM) - 
FCM computes approximately where in the frequency spectrum, the energy of a waveform is centered around. It is calculated by treating the power spectrum of a signal (or analysis frame) as a 1D discrete mass distribution. The FCM of a power spectrum $\widetilde{s}$, containing $M$ samples is found by:
\begin{equation}
    \label{eqn:FCM}
    \text{FCM}[s] = 
    \frac{\sum_{i=0}^{M-1}i\big|\widetilde{s}[i]\big|}
    {\sum_{i=0}^{M-1}\big|\widetilde{s}[i]\big|}
\end{equation}
For instruments with lower ranges and fundamental frequencies such as basses, bassoons or cellos, we find a consistently low FCM. For instruments with higher ranges and fundamental frequencies such as flutes, bells, or oboes, we find a consistently large FCM.

\end{enumerate}

% ================================================================

\subsection{Two Modalities of Learning}
\label{subsec:two modes}

Just like the choice of features, the choice and organization of layer functions can differ drastically between tasks or data sets. This structure of the model defines the hypothesis For this classification task, the structure of our network, called its \textit{architecture}, is chosen to reflect the multimodal nature of the classification features. Since the inputs are two different representations of the same audio sample, they must be used concurrently in the training process. However, since the inputs have different structures and physical interpretations, they cannot be combined into a single input object.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/NeuralNetworkArchitecture.png}
    \caption{Classification architecture for Hybrid Neural Network model}
    \label{fig:Architecture}
\end{figure}

% ================================================================

\subsection{MultiRepresentation Learning}
\label{subsec:Multimodal}

% ================================================================================================================================

\section{Experimental Results}
\label{sec:Results}

% ================================================================================================================================

\section{Discussion and Conclusion}
\label{sec:conclusion}

% ================================================================================================================================

\begin{thebibliography}{9}

\bibitem{Geron}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. O'Reilly, 2017.

\bibitem{Goodfellow}
Goodfellow, Ian, et al.\textit{Deep Learning}. MIT Press, 2017.

\bibitem{James}
James, Gareth, et al. An Introduction to Statistical Learning with Applications in R. Springer, 2017

\bibitem{Khan}
Khan, M. Kashif Saeed, and Wasfi G. Al-Khatib. “Machine-Learning Based Classification of Speech and Music.” Multimedia Systems, vol. 12, no. 1, 2006, pp. 55–67., doi:10.1007/s00530-006-0034-0.

\bibitem{Levine}
Levine, Daniel S. Introduction to Neural and Cognitive Modeling. 2nd ed., Routledge, 2000.

\bibitem{Li}
Li, Yingming, and Ming Yang. “A Survey of Multi-View Representation Learning.” Journal of LateX Class Files, vol. 14, no. 8, Aug. 2015.

\bibitem{Liu}
Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classification." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.

\bibitem{McCulloch}
McCulloch, Warren S., and Walter Pitts. "A Logical Calculus of the Ideas Immanent in Nervous Activity." \textit{The Bulletin of Mathematical Biophysics}, vol. 5, no. 4, 1943, pp. 115–133.

\bibitem{Mierswa}
Mierswa, Ingo, and Katharina Morik. ”Automatic Feature Extraction for Classifying Audio Data.” Machine Learning, vol. 58, no. 2-3, 2005, pp. 127–149., doi:10.1007/s10994-005-5824-7.

\bibitem{Ngiam}
Ngiam, Jiquan, et al. "Multimodal Deep Learning." 2011.

\bibitem{Philharmonia}
Philharmonia Symphony Orchestra home page- \textit{https://philharmonia.co.uk/}

\bibitem{Sahidullah}
Sahidullah, Goutam S. “Design, Analysis and Experimental Evaluation of Block Based Transformation in MFCC Computation for Speaker Recognition.” 18 Nov. 2011.

\bibitem{Tensorflow}
TensorFlow: Large-scale machine learning on heterogeneous systems,
2015. Software available from tensorflow.org.

\bibitem{Virtanen}
Virtanen, Tuomas, et al. \textit{Computational Analysis of Sound Scenes and Events.} Springer, 2018.

\bibitem{UnivIowa}
University of Iowa Electronic Music Studios home page- \textit{http://theremin.music.uiowa.edu/}

\bibitem{Zhang}
Zhang, Tong, and C.-C. Jay Kuo. “Content-Based Classification and Retrieval of Audio.” \textit{Advanced Signal Processing Algorithms, Architectures, and Implementations VIII}, 2 Oct. 1998, pp. 432–443., doi:10.1117/12.325703.

\end{thebibliography}

% ================================================================================================================================

\end{document}

### 2021-02-13 JMMPaper/PaperDrafts/main.tex
Added Figures ffrom JMM paper

% ================
% Landon Buell, Kevin Short
% JMM Paper
% PHYS 705.01 - Lab00
% 21 Sept 2020
% ================

%\documentclass[conference,twocolumn,letterpaper]{IEEEtran}
\documentclass[conference,letterpaper]{report}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{cite}
\usepackage{color}
\usepackage{subfigure}
\usepackage[top=2cm,left=1.5cm,right=1.5cm]{geometry}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Buell, Short}
\rhead{Hybrid Neural Network Classification}
\cfoot{\thepage}

% ================================================================

\title{Musical Instrument Classification Using a Hybrid Neural Network}
\author{Landon H. Buell$^1$ and Kevin M. Short$^2$\\
        $^1$lhb1007@wildcats.unh.edu and $^2$kevin.short@unh.edu\\
        $^1$Department of Physics and Astronomy\\
        $^2$Department of Mathematics and Statistics\\
        University of New Hampshire, Durham, New Hampshire, USA\\
       }

% ================================================================

\begin{document}

\maketitle

% ================================================================================================================================

\begin{abstract}
    Classifying audio signals with machine learning has become an important topic of research in the past few years. Models often involve the input of a 2-D spectrogram or 1-D feature vector into a unimodal network such as a Convolutional Neural Network (CNN) or Multilayer Perceptron (MLP). In this study, we explore automatic classification of musical instruments using new hybrid neural-network (HNN)  architecture that combines the CNN and MLP models and provides superior performance over models that rely solely on one or the other. This hybrid network uses two branches, one being a CNN to process an image-like 2-D spectrogram, and the other being an MLP to process a 1-D feature vector. Within the model, a hidden layer combines activations from the two branches by concatenating them into a single 1-D dense layer, thus all predictions are a product of both branches. We describe in detail the creating of the spectrogram and features, as well as how they influence the chosen network architecture. We finish with a practical demonstration that uses this classifier model to match waveforms from a chaotic music synthesizer to real-world musical instruments. Training data is from studio recordings of the Philharmonia Symphony Orchestra and University of Iowa's Electronic Music Studios
\end{abstract}

% ================================================================================================================================

\section{Introduction}
\label{sec:Intro}

% ================================================================

Digital audio analysis and classification has become a very prolific field in the last few years. The exact nature of each task can differ drastically from archival management, to security, or to commercial usage. In each case, we seek to place audio files into distinct categories called \textit{classes} based in inherent properties within the data \cite{James,Khan,Liu}. Consider a collection of audio files, each containing a single note performed by some musical instrument and the task of matching the contents of the file to the instrument that it most closely resembles. This type of classification task is near trivial for humans, but given the volume of audio data in the modern world, it is impractical at a large scale. However, a computer has no difficulty processing large volumes of raw information, but encoding an explicit instruction set for classification is unreasonable. For this reason, we turn to a \textit{neural network} to combine the computational efficiency of a computer, with the decision-marking architecture of a brain \cite{Geron}.

A neural network is a machine learning model that allows a set of inputs, $x$, called \textit{features}, to be transformed into a set of outputs, $y$,  called \textit{predictions} using a set of \textit{parameters}, $\Theta$ \cite{Geron,Goodfellow,Virtanen}. Audio classification with machine learning is also a well-explored field, with much research in developing an appropriate set of features, also called \textit{predictors}, for input \cite{James,Liu,Mierswa,Zhang}. Since the each classification task or data set may differ greatly from any other, each model often requires a unique combination of features which allows for the best possible performance \cite{Virtanen}. For musical instrument classification we have chosen predictors that represent the contents of an audio file using two different \textit{modalities}. We call this type of classification \textit{multimodal learning} \cite{Ngiam}.

Multimodal learning differs from other types of supervised learning in that a model accepts and processes multiple inputs that are each different representations of the same data sample. Data sets that include or can be transformed into audio + visual, audio + text, or even text + text information, are all examples of multimodal data sets \cite{Li}. For digital audio classification, we have chosen to represent the contents of an audio file by decomposing it into \textit{image + vector} information format. We do this by constructing a 2D spectrogram and a 1D vector of features from the same waveform. Data from these different modes encodes complementary information which allows a model to develop parameters that can more thoroughly describe a sample when compared to it's unimodal learning methods \cite{Li}

To account for this multimodal input, we have constructed a \textit{hybrid neural network} (HNN) that utilizes two input branches, each with its own set of layers to handle an input mode. The spectrogram image is processed with a Convolutional Neural Network (CNN) which uses layers of 2D convolution and 2D pooling to generate a feature map, which is then flattened and transformed by repeated dense layers, and is visualized on the left side of Fig. (\ref{fig:Architecture}). The feature vector input is processed by a Multilayer Perceptron (MLP) which uses repeated dense layers to transform the input, and is visualized on the right side of Fig. (\ref{fig:Architecture}). The output each branch are concatenated into a single layer, which is further transformed into a single output prediction found at the bottom on Fig. (\ref{fig:Architecture}). This means that the neural network learns a set of parameters which allows for mapping of \textit{both} input modes into a single prediction. Since the properties of the input features are critically important to classification success, multi-representation learning shows a great deal of promise and wide spread applicability \cite{Khan,Li,Liu,Virtanen}.

% ================================================================================================================================

\section{The Neural Network}
\label{sec:NeuralNetwork}

% ================================================================

\subsection{Structure}
\label{subsec:Intro}

A neural network is a type of machine learning algorithm that is inspired from the human brain \cite{Geron,Goodfellow}. Where biological brains are constructed from neurons and connected through axons, neural networks are constructed from artificial neurons and connected through transformation functions. The numerical value contained within an artificial neuron is the \textit{activation} of that neuron \cite{Levine}. Neurons are organized into groups called \textit{layers}, which interact with other layers through mathematical transformations such as matrix multiplications or convolutions \cite{Goodfellow}. Because of this, layers in the network can be considered a function, $f^{(l)}$ that accepts an array of activations from the previous layer $x^{(l-1)}$ and used a set of parameters to return an array of modified activations for the current layer, $x^{(l)}$.
\begin{equation}
    \label{eqn:LayerFunction}
    f^{(l)} : x^{(l-1)} \rightarrow x^{(l)}
\end{equation}

By connecting multiple layers in succession, we form a layer-chain structure that describes the flow of information in the neural network, and lets us model a neural network as a computational graph \cite{Geron,Goodfellow}. In a feed-forward network with $L$ layers, inputs $x^{(0)}$ and outputs $y^*$, we can represent a layer-chain such as:
\begin{equation}
    \label{eqn:LayerChain}
    x^{(0)} \rightarrow f^{(0)} \rightarrow f^{(1)} \rightarrow ... \rightarrow f^{(L-2)} \rightarrow f^{(L-1)} \rightarrow y^*
\end{equation}
The structure of a neural network's layer-chain defines it's \textit{architecture}. The choice of architecture indicates the \textit{hypothesis-space} of the model a determines that set of all possible solutions that a trained model can arrive at. For deep neural networks this function chain can be dozens of layers long, and contain upwards of millions of parameters. Increasingly complicated networks allow for a high dimensional solution space, which potentially enables the modeling of more complex systems.

The hybrid neural network differs from this standard architecture in Eq. (\ref{eqn:LayerChain}) in that the function chain consists of two input layers, which push activations through two separate layer chains. We detail the structure an function of each layer chain in section (\ref{subsec:CNN}) and (\ref{subsec:MLP}). After the activations have been transformed into mutually compatible format, they can be concatenated into a single array. This array then represents the start of a new layer chain whose output represents a a prediction that is aggregated from the two aforementioned input layers. We represents the layer-chain structure for a generalized HNN, with inputs $x^{(0)}_a$ and $x^{(0)}_b$ and outputs $y^*$ as :
\begin{equation}
    \label{eqn:LayerGraph}
    \begin{split}
        x^{(0)}_a \rightarrow f^{(0)}_a \rightarrow  ... \rightarrow f^{(\alpha)}_a \searrow &\\
                & f^{(\gamma)}_c \rightarrow ... \rightarrow f^{(L-1)}_c \rightarrow y^* \\
        x^{(0)}_b \rightarrow f^{(0)}_b \rightarrow  ... \rightarrow f^{(\beta)}_b \nearrow &\\
    \end{split}
\end{equation}

This structure allows us to consider and design each branch $a$ and $b$ as if they were separate neural networks. The outputs from $f^{(\alpha)}_a$ and $f^{(\beta)}_b$ represents the outputs of the branches respectively, which are concatenated at layer $f^{(\gamma)}_c$. This marks the entry point of a new chain, which ends at the final output of the full model. Although we may consider the functionality of each layer-chain individually, they still are subsets of the same computational graph. This means that the full graph in Eq. (\ref{eqn:LayerGraph}) is considered as one neural network model in the training and validation process.

% ================================================================

\subsection{Input and Output}
\label{subsec:InputOutput}

The inputs to a neural network or any machine learning algorithm are called \textit{features} or \textit{predictors} \cite{James}. These are compact, low-dimensional representations of a data sample reflect its important characteristics \cite{Liu}. Features should be chosen as to have low variance within each class and high variance between classes. For digital audio classification of musical instruments, features of the same musical instruments should exhibit very similar properties, while features from difference musical instruments should exhibit non-similar properties. In any learning algorithm, the role of feature extraction is to translate the raw information into descriptors that maximize the classification performance \cite{Virtanen}. Although the neural network will classify the musical instrument within the digital audio sample, it will never interact with the raw waveform directly, instead will rely solely on these features. Suppose we implement a classification model that uses $p$ predictors. These features are usually combined into a single vector-like object for each sample, and then presented as input to the neural network \cite{Geron}. We detail the classification features for this neural network in section (\ref{subsec:FeaturesMLP}) and (\ref{subsec:FeaturesCNN}).

The outputs to a classification neural network encodes the prediction that model has made for a particular sample. For a classifier with $k$ classes, there are $k$ output neurons transformed such that the sum of the activations is identically $1$ \cite{Goodfellow,James}. This means the $k$ neurons can be treated as a probability density for each of the classes, where the neuron with the highest activation value is the prediction of the sample. For classification of musical instruments, each class represents a musical instrument type. We use $37$ classes of instruments ranging from woodwinds, to brass, to strings, to mallet percussion, to synthesizers. Each audio file contains exactly one musical instrument sustaining one note.

% ================================================================

\subsection{The Cost Function}
\label{subsec:CostFunction}

A neural network is trained by providing a batch of input samples $X$, with a corresponding set of expected predictions $Y$. Consider a sample $x \in X$ that is expected to produce corresponding label $y \in Y$. When passed into the network, $x$ produces some prediction label denoted as $y^*$. For an untrained network, we anticipate that $y^*$ and $y$ may differ greatly - meaning that the prediction is very different that the expected output, and classification performance is likely to be very poor. Since we know each sample in the data set to contain one, and only one musical instrument, we \textit{one-hot-encode} the expected label $y$. For any sample $x^{(i)}$ that belongs to class $j$, we have a corresponding target vector $y^{(i)}$ given by:
\begin{equation}
    \label{eqn:OneHotEnc}
    y^{(i)} = \big[ y_{0} , y_{1}, ... , y_{j}, ... , y_{k-1} \big] = \big[ 0, 0, ... , 1, ... , 0 \big]
\end{equation}
The same sample will produce a similarly sized vector, $y^{*(i)}$, which all elements sum to $1$.

To quantity the difference between $y$ and $y^*$, we introduce a \textit{cost function}, $J(y,y^*)$ which is also called an objective function or a loss function \cite{James}. The exact cost function used can differ based on the nature of the machine learning model or task, but typically multiple - category classification tasks use a \textit{categorical cross-entropy} (CXE) function \cite{Geron,Goodfellow}. The CXE cost for a single sample is defined as \cite{Goodfellow,Virtanen}:
\begin{equation}
    \label{eqn:CXELoss}
    \text{CXE}[y,y^*] = - \sum_{n=0}^{k-1} y_{n} \ln(y^*_{n})
\end{equation}
Recall a sample belongs to class $j$. Since $y$ is one-hot-encoded, the only non-zero term in the sum is $y_{j} \ln(y^*_{j})$, where $y^*_{j} \in [0,1]$.  This returns a negative number, which we multiply by $-1$ to always yield a positive cost value. When a sample produces $y^*_{j} << 1$, the CXE cost returns a large value and when $y^*_{j} \approx 1$, then the CXE cost returns a small value. We provide a visualization of this behavior in Fig. (\ref{fig:CXELoss}).

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.14]{figures/CXELoss.png}
    \caption{Categorical Cross Entropy Cost Function given values for $y^*_{j} \in [0,1]$}
    \label{fig:CXELoss}
\end{figure}

We characterize the cost function as producing a value inversely proportional to the prediction confidence- A large cost value indicates a \textit{poor} prediction label and a low cost value indicates a \textit{good} prediction label \cite{James,Virtanen}. Thus, we expect a trained neural network to produce consistently low cost function values across all samples in a data set. When a neural network does return consistently low cost function values for previously unseen samples, we consider it to be a \textit{fitted} or \textit{trained} network \cite{Geron,Goodfellow,James}.

% ================================================================

\subsection{Training and Optimization}
\label{subsec:Training}

A neural network makes predictions by successive transformations of input features through layer functions until a final output array is produced. Each layer $f^{(l)}$, of the model is a function that contains a set of parameters held within arrays $W^{(l)}$ and $b^{(l)}$ that are used to transform activations through the layer chain \cite{Goodfellow}. The process of training the network is the manipulation of these parameters in each layer, such that each input $x$ can produce a output, $y^*$ that is reasonably close to $y$. Since we can quantify the difference between the expected output and the given output with a cost function, we can use this as a metric for measuring how "trained" a model is \cite{James}. Specifically, we train a neural network by \textit{optimizing} the parameters in each layer to allow for this consistently low cost function value \cite{Geron,Goodfellow}. Note that we optimize the cost function under the assumption that doing so will also improve the classification performance. This is called \textit{indirect optimization} \cite{Goodfellow}.

Since a the function chain that comprises a neural network can become exceedingly complicated for deeper and wider networks, producing a single analytical expression for the optimization of every parameter may be either impractical at best or impossible at worst. We instead optimize the network with a numerical iterative method based on \textit{gradient descent} \cite{Geron,Goodfellow}. Gradient descent is the process of (i.) computing the gradient of the cost function with respect to every element in $\Theta$ and (ii.) adjusting each parameter in $\Theta$ according to the elements in that gradient vector, shown in Eq.(\ref{eqn:GradDesc}), often scaled by a \textit{learning rate} $\alpha$. We compute the gradient of the cost function, $\nabla_{\Theta}J$ through a process call \textit{backwards propagation} \cite{Geron}. This algorithms uses the derivative chain-rule from multivariate calculus to begin at the last layer of the network, and work backwards through the layer chain in Eq. (\ref{eqn:LayerChain}) to construct the elements of $\nabla_{\Theta}J$ \cite{Goodfellow,Virtanen}.

\begin{equation}
    \label{eqn:GradDesc}
    \Theta^{(i)} = \Theta^{(i-1)} + (-\alpha)\nabla_{\Theta}J
\end{equation}

Standard gradient descent optimization is cumbersome, prone to numerical errors, and may often become unstable when encountering discontinuities in solution-space \cite{James,Geron}. Because of this, we employ a more robust and aggressive optimization algorithm called \textit{Adaptive-Moments} or ADAM for short. ADAM uses adaptive learning rates, $s^{(i)}$ and $r^{(i)}$, that record and update exponentially decaying averages of past gradients and past squared gradients respectively. The ADAM update is given by Eq. (\ref{eqn:ADAM}).

\begin{equation}
    \label{eqn:ADAM}
        \begin{split}
        s^{(i)} &= \rho_1 s^{(i-1)} + (1 - \rho_1) \nabla_{\Theta} \bar{J}  \\
        r^{(i)} &= \rho_2 r^{(i-1)} + (1 - \rho_2) \Big[ \nabla_{\Theta} \bar{J} \odot \nabla_{\Theta} \bar{J} \Big]  \\
        s'^{(i)} &= \frac{s^{(i)}}{1-\rho_1^i} \\
        r'^{(i)} &= \frac{r^{(i)}}{1-\rho_2^i} \\
        \Theta^{(i)} &= \Theta^{(i-1)} + (-\alpha)\frac{s'^{(i)}}{\sqrt{r'^{(i)}}+\delta} \\
        \end{split}
\end{equation}

ADAM provides a much more powerful and stable optimization algorithm at a higher computational cost \cite{Geron}. Note that the superscript $(i)$ indicates an iteration index where a superscript $i$ is exponentiation. Typically we initialize $\rho_1 = 0.9$, $\rho_2 = 0.999$, and introduce $\delta \approx 10^{-7}$ to avoid possible division of near-zero values \cite{Goodfellow}. All operations in the final three steps are applied element-wise. ADAM has experimentally shown to be a very effective optimizer and useful for a wide range of data sets and architectures which is why we have chosen to implement it for this task \cite{Geron,Goodfellow}.

% ================================================================================================================================

\section{Features and the Hybrid Network}
\label{sec:Features}

The architecture that we have developed for this model incorporates a convolutional neural network (CNN) and a multilayer perceptron (MLP) and is visualized in Fig. (\ref{fig:Architecture}). The later hidden layers of the CNN branch flatten a 2D grid of activations into a 1D vector for each sample and pass it them into it's own MLP. The outputs of each branch are concatenated into a single dense layer, and a new output is drawn from the combined array of activations. We detail the structure and input features of each of the two input branches.

% ================================================================

\subsection{Multilayer Perceptron Features}
\label{subsec:FeaturesMLP}

The features for this branch are derived from the time-domain or frequency-domain representation of a waveform. Each feature explored represents the values computed from each audio file, which are then assembled into a 1D array-like object called a feature vector. This vector is provided as input to the MLP branch of the neural network, which can be found on right side of Fig. (\ref{fig:Architecture}). To ensure a consistency of all extracted features, all waveforms have been truncated or zero-padded to contain a consistent $M$ samples.

\begin{enumerate}

\item\textbf{Time Domain Envelope} (TDE) - 
The TDE is a method of approximating the energy in the full or a subset of the time-series waveform of a signal. We divide the waveform into $5$ non-overlapping analysis frames and compute the RMS energy of the waveform in each section. This allows for an approximation of the amplitude envelope of the time-domain signal \cite{Virtanen}. For a signal $s$, the RMS energy in the $j$-th frame containing $Q$ samples is given by:
\begin{equation}
    \label{eqn:TDE}
    \text{TDE}_j[s] = \sqrt{\frac{1}{Q}\sum_{i=n}^{n+Q}s[i]^2}
\end{equation}
These features allow us to characterize the time-evolution of energy in a signal. Instruments with heavy attacks, and sudden decays show large TDE values in early frames, and low TDE values in later frames. Instruments with longer sustains will show consistently decaying TDE values throughout the duration of the file.

\item\textbf{Zero Crossing Rate} (ZXR) - 
The ZXR of a waveform measures how many time that a signal crosses it's equilibrium value, often normalized per unit time. This feature is commonly used to differentiate speech from music because speech often has a more jagged and less periodic structure, giving it a characteristically higher ZXR value \cite{Virtanen,Khan,Zhang}. We adapt this feature to compute the zero-crossing rate over the full waveform. The zero crossing rate for a waveform $s$ with $M$ samples is given by:
\begin{equation}
    \label{eqn:ZXR}
    \text{ZXR}[s] = \frac{1}{2}\sum_{i=i}^{M-1}\Big| \text{sign}\big(s[i]\big) - \text{sign}\big(s[i-1]\big) \Big|
\end{equation}
Where $\text{sign}(x)$  returns $+1$ if $x > 0$, $-1$ if $x < 0$ and $0$ if $x = 0$. In generally, the zero crossing rate can also be used as a rough frequency measurement, where instruments that can produce higher fundamental frequencies often have higher ZXR values, where instruments that can produce lower fundamental frequencies have lower ZXR values \cite{Zhang}.

\item\textbf{Temporal Center of Mass} (TCM) - 
The TCM of a waveform computes approximately where in time the energy of a waveform is centered around and can conveniently summarize characteristics of the transient response into a single scalar value. The temporal center of mass of a signal $s$ with $M$ samples is given by:
\begin{equation}
    \label{eqn:TCM}
    \text{TCM}[s] = \frac{\sum_{i=0}^{M-1}i\big|s[i]\big|}{\sum_{i=0}^{M-1}\big|s[i]\big|}
\end{equation}
For instruments with heavier attacks and short decay and release times, such as plucked strings or percussion, we expect the energy of the waveform to be very early on, thus providing a very low TCM value. For instruments with shorter attacks, with long sustain and release times, such as bowed strings or woodwinds, we expect the energy of the waveform to be more spread out, thus have a higher TCM value.

\item\textbf{Auto Correlation Coefficients} (ACC) -
ACC's are rough estimates of the signal spectral distribution. They are computed by taking the dot product of a signal with a time-expedited variant of itself, then the normalized to lie between $0$ and $1$ \cite{Virtanen}. We can compute any number of ACC's and it's value will change according to the index chosen. In practice, it is common to compute the first $K$ ACC's, with the $k$-th ACC for a signal $s$, with $M$ samples is given by:
\begin{equation}
    \label{eqn:ACC}
    \text{ACC}_k[s] = \frac{\sum_{i=0}^{M-k-1}s[i]s[i+k]}{\sqrt{\sum_{i=0}^{M-k-1}s^2[i]}\sqrt{\sum_{i=0}^{M-k-1}s^2[i+k]}}
\end{equation}
Dotting this signal with the time-shifted version of itself allows us to measure periodicity in time-space.

\item\textbf{Mel Frequency Ceptrum Coefficients} (MFCC) - 
In the MFCC computation process, a frequency spectrum is passed through overlapping triangle filter branks that are spaced according to the Mel scale \cite{Sahidullah}. This is done by calculating the dot product between the power spectrum of a signal and each of $R$ Mel filter banks, which yields an approximation of energy in that frequency band. These are called Mel Filter bank energies (MFBE's). Each MFCC is found by computing the inverse discrete cosine transform of the log of the MFBE's. For $R$ filter banks, the $k$-th MFCC is given by \cite{Virtanen}:
\begin{equation}
    \label{eqn:MFCC}
    \text{MFCC}_k[B] = \sqrt{\frac{2}{R}}\sum_{i=1}^{R}\log{(B[i])}
    \cos\Big(\frac{k(i-\frac{1}{2})\pi}{R}\Big)
\end{equation}
Where $B[i]$ is the $i$-th MFBE value. MFCC's allow for the investigation of periodicity in frequency-space, which identifies phenomena of overtones, echoes, etc \cite{Sahidullah,Virtanen}.

\item\textbf{Frequency Center of Mass} (FCM) - 
FCM computes approximately where in the frequency spectrum, the energy of a waveform is centered around. It is calculated by treating the power spectrum of a signal (or analysis frame) as a 1D discrete mass distribution. The FCM of a power spectrum $\widetilde{s}$, containing $M$ samples is found by:
\begin{equation}
    \label{eqn:FCM}
    \text{FCM}[\widetilde{s}] = 
    \frac{\sum_{i=0}^{M-1}i\big|\widetilde{s}[i]\big|}
    {\sum_{i=0}^{M-1}\big|\widetilde{s}[i]\big|}
\end{equation}
For instruments with lower ranges and fundamental frequencies such as basses, bassoons or cellos, we find a consistently low FCM. For instruments with higher ranges and fundamental frequencies such as flutes, bells, or oboes, we find a consistently large FCM.

\end{enumerate}

Each of these features represents an entry in a $1 \times 24$ \textit{feature-vector} that describes each sample. This object conveys important characterisitcs of each digital audio in a list-like fashion. It is presented as input to the multilayer perceptron branch of the HNN. This is the first of the two modalities that we choose to represent each data sample.

% ================================================================

\subsection{Convolutional Network Features}
\label{subsec:FeaturesCNN}

The features for this branch are the entries in a standard 2D spectrogram representation of a waveform. A spectrogram maps the energy distribution of a signal as a function of time and frequency. It is particularly useful because it allows us to examine the frequency composition of a signal, and how that composition evolves over time. On a typical spectrogram, the passing on time is shown on the x-axis, and frequency is shown on the y-axis. Because it is represented as a 2D array or floating-point numbers, the spectrogram is effectively an image-like representation of a sound wave. Since each musical instrument produces it's own harmonic structure and transient response, each instrument can be identified by patterns within the spectrogram \cite{Virtanen}. This means than when only use this modality, the audio classification becomes very similar to an image classification task \cite{Ngiam}. We provide a few example spectrograms for reference in Fig. (\ref{fig:Example Spectrograms}).

A spectrogram is produced by applying the technique of \textit{frame-blocking} to a waveform to produce a matrix of short-time analysis frames \cite{Liu,Virtanen}. We choose each frame to contain $N = 1024$ samples, with a $768$ sample overlap between adjacent frames. 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/AnalysisFrames.png}
    \caption{Analysis frames in relation to a full waveform. This figures has been adapted from \cite{Liu}.}
    \label{fig:AnalysisFrames}
\end{figure}
We organize the analysis frames into a matrix, $A$ with shape $N \times k$, such that each row is a frame. We apply a Hanning window of length $N$ to each row of $A$. This eliminates discontinuities at the edges of each analysis frame, and allows for a cleaner transform into frequency-space \cite{Virtanen}. The effect of applying an Hanning window function to an analysis frame of $1024$ samples can be found in Fig. (\ref{fig:WindowFrame}). We tail-pad each time-series analysis frame by an additional $1024$ zeros which brings each frame to $2048$ samples, and gives a higher frequency-space resolution \cite{Sahidullah}. The spectrogram, $S$, is produced by computing:
\begin{equation}
    \label{eqn:Spectrogram}
    S = \big( \mathbb{W}A^T \big) \odot \big( \mathbb{W}A^T \big)^* 
\end{equation}
Where $\mathbb{W}$ is the standard \textit{Discrete Fourier Transform} (DFT) matrix, and $^*$ indicate element-wise complex conjugation. For $k$ analysis frames, matrix $S$ has shape $2048 \times k$.

\begin{figure}[h]
    \centering
    \subfigure[]{\includegraphics[width=0.45\textwidth]{figures/AnalysisFrame.png}}
    \subfigure[]{\includegraphics[width=0.45\textwidth]{figures/WindowedFrame.png}}
    \caption{(a) A standard time-series analysis frame made up of $1024$ samples and (b) The same frame with a standard Hanning Window Applied to it. This sample is taken from a bowed violin playing an $A4$ note.}
    \label{fig:WindowFrame}
\end{figure}

The standard western concert musical instruments that make up our base data set rarely have fundamental frequencies that extend beyond $6,000$ Hz. This means, that we will rarely see much energy or characteristic behavior above the $12,000$ Hz mark in the spectrograms. For this reason, we choose to crop each matrix as to include only information corresponding to the region of frequency-space form $0$ Hz to $12$ kHz. We also choose to zero pad, or crop matrix $S$ so that there are exactly $k = 256$ columns. The result is an image-like representation of a digital audio file with shape $558 \times 256$, which is passed as a feature to the input of the CNN branch of the HNN. This is the second of the two modalities that we choose to represent our data sample.

\begin{figure}[h]
    \centering
    \subfigure[]{\includegraphics[width=0.45\textwidth]{figuresSpectrograms/AltoSax-A4.png}}
    \subfigure[]{\includegraphics[width=0.45\textwidth]{figuresSpectrograms/GUITAR-B2.png}}
    \caption{Spectrograms of (a) an alto saxophone playing an $A4$ and (b) an acoustic guitar playing a $B2$}
    \label{fig:Example Spectrograms}
\end{figure}

% ================================================================

\subsection{The Perceptron Branch}
\label{subsec:MLP}

The perceptron branch is an pictured on the left side of Fig. (\ref{fig:Architecture}) and is an implementation of multilayer perceptron (MLP) neural network. The MLP processed input by transforming activations through repeated layers of neurons, modeled as vectors of floating-point numbers. Each neurons in a given layer by a linear combination of every neuron in the previous layer. Practical implementations introduce the addition of a constant value to each neuron (called a \textit{bias}), and some form or non-linear activation function \cite{Geron,Goodfellow}. Transformations of this type are called \textit{dense} layers, which when compounded can model that highly non-linear decision boundaries than arise in real world problems \cite{James}.

The input to this branch is a vector of features, described in section (\ref{subsec:FeaturesMLP}), which are transformed through two dense layers, with $64$ neurons each. Passing through these dense layers allows these inputs to be handled just like any other multilayer perceptron model, which have shown experimental success in the last few decades. We choose to implement one here, enabling the training process to learn parameters that can effectively minimize the cost function and sucessfully classify inputs. The output of the last dense layer is provided to the concatenation layer, which merges it with the output of the convolution branch.

% ================================================================

\subsection{The Convolution Branch}
\label{subsec:CNN}

The Convolution branch is pictured on the left side of Fig. (\ref{fig:Architecture}) and is an implementation of a convolutional neural network (CNN), connected to a multilayer perceptron (MLP). This branch accepts 2D image-like input in the form of a spectrogram, described in section (\ref{subsec:FeaturesCNN}). The order and organization of the layers in this branch of the model was inspired from Oxford's \textit{VGG-16} network architecture \cite{Geron}. VGG-16 model uses successive 2D convolutions to identify characteristic features, followed by 2D pooling layers to reduce the size of the activations. Unlike VGG-16, our model does not use padding to keep the image resolution after each convolution layer, and instead the resolution of the image is dropeed with every layer.

The dominant structure in our convolution branch is the \textit{convolution layer group} with combines three layers in succession:
\begin{enumerate}
    \item \textbf{2D Convolution Layer} - $32$ features feature maps, $3 \times 3$ kernel size, $1 \times 1$ kernel stride, ReLU activation function.
    \item \textbf{2D Convolution Layer} - $32$ features feature maps, $3 \times 3$ kernel size, $1 \times 1$ kernel stride, ReLU activation function.
    \item \textbf{2D Maximum Pooling Layer} - $3 \times 3$ kernel size, $1 \times 1$ kernel stride, Identity activation function
\end{enumerate}
The combination of layers in this order allows for the convolutions to detect characteristic features in the spectrogram, while the pooling allows for minor positional in variance in those features. Additionally, the output of the layer group is smaller is size, causing each layer's activation to take up less memory, and allowing only the most prolific features of each input to survive. At the end of the final layer group, the remaining 2D image contain only a few pixels, and the activation are flattened, by reorganizing each sample such that it is a 1D array. The 1D array is appropriately shaped for processing in the branche own MLP structure. The output of the last dense layer of this MLP is provided to the concatenation layer, which merges it with the output of the Perceptron branch.

% ================================================================

\subsection{Multirepresentation Learning}
\label{subsec:Multimodal}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/NeuralNetworkArchitecture.png}
    \caption{Architecture for Hybrid Neural Network model, implemented with Tensorflow \cite{Tensorflow}}
    \label{fig:Architecture}
\end{figure}

The architecture of the HNN enables us to perform classify the contents of digital audio files as musical instruments through \textit{multimodal} learning. The combined architecture, using Google's \textit{Tensorflow} library for Python allows the model to be trained conveniently as a single object \cite{Tensorflow}. This means that although the HNN is composed of two separate branches, all parameters and layers in the network are included with each back-propagation pass. This HNN contains 319,365 trainable parameters.

% ================================================================================================================================

\section{Experimental Results}
\label{sec:Results}

% ================================================================

\subsection{Resampling}
\label{subsec:Resampling}

In the machine learning workflow, it is standard practice to divide a full data set into a \textit{training} subset and a \textit{testing} subset \cite{James,Virtanen}. The training subset is used to optimize the parameters, $\Theta$, in the model as to minimize the cost function, $J$, for the data set. The testing subset is used to evaluate how well the neural network performs on data that it has never interacted with \cite{Geron}. The training subset does contain corresponding labels, but they are withheld from the trained model such that it can make unbiased predictions.
We can expand this idea to a common resampling method called \textit{K-Folds Cross Validation}, or X-validation for short \cite{James}. X-validation divides a data set into $K$ equally-sized folds. The first $K-1$ folds are used to train the model, and the last fold is used to evaluate how well the network performs on unseen samples. This process repeats of all $K$ folds.

The result of X-validation is $K$ neural network models that have all been trained and evaluated on overlapping subsets of the full data set. Each model contains a set of learned parameters, $\Theta$ that represent a possible outcome if trained on the given data set \cite{James}. By repeating this and comparing the performance across each fold, we understand how the chosen architecture and hyper-parameters influence the stability of the performance of the network. Across each fold, we expect to observe a reasonably high, as well as consistent performance. This is indicates a model that can train effectively, and generalize appropriately. X-validation is critical to ensuring that a model is behaving as expected.

% ================================================================

\subsection{Performance Metrics}
\label{subsec:Metrics}

We choose the following metrics to evaluate the performance of our HNN. All metrics are define in relation to \textit{true-positive} (TP), \textit{true-negative} (TN), \textit{false-positive} (FP), and \textit{false-negative} (FN) predictions \cite{Geron,James}. These metrics are computed for each of $K$ cross validation folds. We visualize the results of each split in Fig.(\ref{fig:XvalScores}.

\begin{itemize}
    \item \textbf{Accuracy Score} - is the ratio of correct predictions to total predictions made by the model. While accuracy is convenient for quick estimates of performance, it does not provide much statistical information on the nature of predictions made of the model. This is especially true when classes have non-uniform representations in the data set. The accuracy score of a classification algorithm is given by:
    \begin{equation}
        \text{Accuracy} = \frac{TP + FN}{TP + TN + FP + FN}
    \end{equation}
    Accuracy is bound between $0$ and $1$ with a higher score indicating better performance.

    \item \textbf{Precision Score} - is the ratio of correctly identified elements, to all relevant elements in the data set. The higher the score, the \textit{specific} a model is to a particular category. The precision score of a classification algorithm is given by:
    \begin{equation}
        \text{Precision} = \frac{TP}{TP + FP}
    \end{equation}
    This metric determines how many of the selected items are relevant to the problem and is bound between $0$ and $1$ with a higher score indicating better performance.

    \item \textbf{Recall Score} - is the ratio of correctly identified elements, to all relevant elements in the data set. The higher the score, the \textit{sensitive} a model is to a particular category. The recall score of a classification algorithm is given by:
    \begin{equation}
        \text{Recall} = \frac{TP}{TP + FN}
    \end{equation}
    This metric determines how many of the relevant items have been selected and is bound between $0$ and $1$ with a higher score indicating better performance.

    \item \textbf{F1 Score} - is the harmonic mean of the precision and recall scores. The higher the score, the more sensitive and specific a model is to a particular category. A high score indicate a model with both high precision and recall values. The $F1$ of a classification algorithm is given by:
    \begin{equation}
        F1 = 2 \times \frac{\text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}}
    \end{equation}
    $F1$ score is bound between $0$ and $1$ with a higher score indicating better performance.
\end{itemize}

% ================================================================

\subsection{Confusion Matrices}
\label{subsec:Confusion}

A confusion matrix is a square array that counts the number of times a sample was predicted to be in a given class. For a $k$-categories classifier, the confusion matrix, $C$ has shape $k \times k$ where $C[i,j]$ is the number of times a sample known to be in class $i$ was predicted to be in class $j$ \cite{Geron}. A value added to the main-diagonal indicates a \textit{correct} classification, while a value on the off-diagonal indicates an \textit{incorrect} classification. We expect a well-performing classifier model to produce a diagonally-dominant confusion matrix.

A standard confusion matrix does not account for any non-uniformity in the number of samples in each class in the data set. To combat this, we divide the entries of each row of the confusion matrix by the sum of that row. This has the effect of "normalizing" the confusion matrix according to how often class appears in a data set. Just like the metrics in section (\ref{subsec:Metrics}), we construct the confusion matrix for each fold of cross validation, and then normalize it according to class occurrence. We average the $K$ matrices together and visualize the result in Fig. (\ref{fig:ConfScores}).

% ================================================================

\subsection{Cross Validation Results}
\label{subsec:Results}

We have chosen to run a $K = 10$ fold cross validation program on our model, and compute the value of the each of the four metrics described in section (\ref{subsec:Metrics}). We have also run X-validation on two similar models that represent either mode of the network. The first variant uses just a 2D spectrogram input, fed through an identical CNN + MLP as shown on the left of Fig. (\ref{fig:Architecture}). The activations are passed directly to the output layer where a prediction is made using this mode alone. Similarly, the second variant uses just a 1D feature-vector input, fed through an identical MLP as shown on the right side of Fig.(\ref{fig:Architecture}). The activations bypass the concatenation layer, and are passed directly to the output layer where a prediction is made using this mode alone. This allows us to produce an approximate comparison of how the HNN compares to the CNN or MLP models individually. Cross validation was performed on each model using a different set of random splits from the same data set. The reported scores are averged over all samples in each training data subset.

\begin{figure}[H]
    \centering
    \subfigure[]{\includegraphics[width=0.45\textwidth]{figures/AvgXval-Convolution.png}}
    \subfigure[]{\includegraphics[width=0.45\textwidth]{figures/AvgXval-Perceptron.png}}
    \subfigure[]{\includegraphics[width=0.45\textwidth]{figures/AvgXval-Multimodal.png}}
    \caption{Performances of the (a) CNN + MLP with spectrogram input, (b) MLP with feature-vector input, and (c) the HNN with spectrogram and feature-vector input}
    \label{fig:XvalScores}
\end{figure}

We observe the classification scores for each of the three model variants in Fig. (\ref{fig:XvalScores}). The CNN + MLP variant in (\ref{fig:XvalScores}-a) shows metric scores consistently averaging close to $0.8$. with a few splits above or below this value. Similarly, the MLP variant in (\ref{fig:XvalScores}-b) shows scores all consistently close to $0.7$.  This indicates that each input mode and complementary architecture allows for the optimization of a set of parameters to enable reasonable classification performance on unseen samples. Both models do exhibit fluctuation in the range of scores between each fold, which indicates that each model is vulnerable to small changes in initial conditions.

The HNN architecture variant in (\ref{fig:XvalScores}-c) shows improved performance when compared to either the CNN or MLP variant alone. Where the single input mode models shows performance scores averaging around $0.8$ and $0.7$, in (\ref{fig:XvalScores}-a) and (\ref{fig:XvalScores}-b) respectivly, the HNN boasts a higher average, around $0.84$ for both precision and recall. We also observe a lower variance between the performances of each split, indicating a more stable architecture that is less susceptible to changes in initial condition.

We also choose to examine and compare the normalized confusion matrices of the three modal variants. In Fig. (\ref{fig:ConfScores}-a) we see a confusion matrix for the CNN + MLP, which shows a strong main diagonal, indicated by the dark reds, oranges, and yellows which indicated a high-level of correct classifications. We do observe indexes such as $C[0,5]$, $C[0,15]$, $C[7,27]$, and $C[28,24]$ that contain unusually large entries indicated by the bright blue color. In Fig. (\ref{fig:ConfScores}-b) we see a weaker diagonally dominant matrix for the MLP, which displayed even more misclassified samples, spread through the matrix. Note how each confusion matrix represents the average of $10$ confusion matrices produced from cross validation.

Finally, we observe the normalized confusion matrix of the HNN model in Fig. (\ref{fig:ConfScores}-c). This matrix is the most-diagonally dominant, showing only a few commonly confused classes. The smaller number of mis-classifications in this model indicates a greater performance, and a generally stronger classifier. We observe $C[0,15]$, $C[7,27]$, and $C[27,7]$ to have unusually large entries also indicated by the bright blue pixels. Consulting the list of instrument classes reveals that class $0$ and $15$ represent \textit{alto flutes} and \textit{flutes} respectively.  Classes $7$ and $27$ represents \textit{bass trombones} and \textit{tenor trombones}. These pairs of instruments are similar in build and in timbre, meaning that they likely have similar properties in feature space, and that a human listener may also show difficulty differentiating them.

% ================================================================

\subsection{Practical Example}
\label{subsec:Example}

As a practical demonstration of the classification ability of the Hybrid Neural Network, we choose to test the model on an unlabeled digital audio file, "\textit{zcombo.wav}". This audio file contains a waveform that is generated through

\textcolor{red}{I'll need your help to introduce the chaotic Synth files, and address how they are generated, and why we use and "care" about them}

\begin{figure}[H]
    \centering
    \subfigure[]{\includegraphics[width=0.35\textwidth]{figures/XValGammaCNN_Avg_Hits_Weighted_Confusion.png}}
    \subfigure[]{\includegraphics[width=0.35\textwidth]{figures/XValBetaMLP_Avg_Hits_Weighted_Confusion.png}}
    \subfigure[]{\includegraphics[width=0.35\textwidth]{figures/XValAlphaCLF_Avg_Hits_Weighted_Confusion.png}}
    \caption{Performances of the (a) CNN + MLP with spectrogram input, (b) MLP with feature-vector input, and (c) the HNN with spectrogram and feature-vector input}
    \label{fig:ConfScores}
\end{figure}

% ================================================================================================================================

\section{Discussion and Conclusion}
\label{sec:conclusion}

Multimodal learning itself shows great promise to machine learning algorithms in numerous domains. For data sets that lend themselves to multiple representations of a single sample, the ability to use those different modes allows for a more comprehensive representation of data. Across full data set, this will enable a model to generate a more stable set of parameters for classification which has the potential to yield better performance. Multimodal learning does not limit itself to classification of digital audio, but instead opens the door to many genres of machine learning such a medicine, finance, and other media classification.

The results of cross validation indicate that we have constructed a hybrid neural network that accept two input modes, and can effectivly classify the contents of a digital audio file as one of $37$ different musial instruments. The design of this HNN enables the input of two non-compatible modal representations of a sample to be processed and combined to form a single output prediction. We find that this model demonstrates better and more consistent performance at musical instrumental classification when compared to that of either the constituent CNN or MLP models. By transforming each input sample into multiple representations of itself, the HNN learns a more robust set of parameters that can more thoroughly differentiate each class. While some common misclassfications are present, many of them are due to the related nature of musical instruments, which may also cause similar confusion in human listeners.

\textcolor{red}{I sure cannot write a conclusion to save my life}

% ================================================================================================================================

\begin{thebibliography}{9}

\bibitem{Geron}
Geron, Aurelien. \textit{Hands-on Machine Learning with Scikit-Learn and TensorFlow: Concepts, Tools, and Techniques to Build Intelligent Systems}. O'Reilly, 2017.

\bibitem{Goodfellow}
Goodfellow, Ian, et al.\textit{Deep Learning}. MIT Press, 2017.

\bibitem{James}
James, Gareth, et al. An Introduction to Statistical Learning with Applications in R. Springer, 2017

\bibitem{Khan}
Khan, M. Kashif Saeed, and Wasfi G. Al-Khatib. “Machine-Learning Based Classification of Speech and Music.” Multimedia Systems, vol. 12, no. 1, 2006, pp. 55–67., doi:10.1007/s00530-006-0034-0.

\bibitem{Levine}
Levine, Daniel S. Introduction to Neural and Cognitive Modeling. 2nd ed., Routledge, 2000.

\bibitem{Li}
Li, Yingming, and Ming Yang. “A Survey of Multi-View Representation Learning.” Journal of LateX Class Files, vol. 14, no. 8, Aug. 2015.

\bibitem{Liu}
Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classification." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.

\bibitem{McCulloch}
McCulloch, Warren S., and Walter Pitts. "A Logical Calculus of the Ideas Immanent in Nervous Activity." \textit{The Bulletin of Mathematical Biophysics}, vol. 5, no. 4, 1943, pp. 115–133.

\bibitem{Mierswa}
Mierswa, Ingo, and Katharina Morik. ”Automatic Feature Extraction for Classifying Audio Data.” Machine Learning, vol. 58, no. 2-3, 2005, pp. 127–149., doi:10.1007/s10994-005-5824-7.

\bibitem{Ngiam}
Ngiam, Jiquan, et al. "Multimodal Deep Learning." 2011.

\bibitem{Philharmonia}
Philharmonia Symphony Orchestra home page- \textit{https://philharmonia.co.uk/}

\bibitem{Sahidullah}
Sahidullah, Goutam S. “Design, Analysis and Experimental Evaluation of Block Based Transformation in MFCC Computation for Speaker Recognition.” 18 Nov. 2011.

\bibitem{Tensorflow}
TensorFlow: Large-scale machine learning on heterogeneous systems,
2015. Software available from tensorflow.org.

\bibitem{Virtanen}
Virtanen, Tuomas, et al. \textit{Computational Analysis of Sound Scenes and Events.} Springer, 2018.

\bibitem{UnivIowa}
University of Iowa Electronic Music Studios home page- \textit{http://theremin.music.uiowa.edu/}

\bibitem{Zhang}
Zhang, Tong, and C.-C. Jay Kuo. “Content-Based Classification and Retrieval of Audio.” \textit{Advanced Signal Processing Algorithms, Architectures, and Implementations VIII}, 2 Oct. 1998, pp. 432–443., doi:10.1117/12.325703.

\end{thebibliography}

% ================================================================================================================================

\end{document}

### 2021-03-11 Thesis/SignalClassifierREADME/ClassifierREADME.tex
Updated README For signal Classifier

@@
 
-\usepackage[top=2.5cm,left=2.5cm,right=2.5cm]{geometry}
+\usepackage[top=2cm,left=2cm,right=2cm]{geometry}
 \usepackage{fancyhdr}
@@
 \begin{abstract}
-The \textit{Signal Classifier} program uses a hybrid neural network algorithm to attempt to classify time-series signals to a set of pre-determined classes.
+The \textit{Signal Classifier} program uses a hybrid neural network architecture to attempt to classify time-series signals to a set of pre-determined classes (defined by the input labels).
 For the purpose of the algorithm's development, input samples were assumed to be .wav files of musical instruments performing one note, or several shorter notes in succession- totaling at around 100,000 - 200,000 samples each, sampled at 44.1 kHz.
@@
 
-\subsection{Getting the Signal Classifier on Your Machine}
+\section{Getting the Signal Classifier on Your Machine}
 
@@
 \begin{quote}
-../Buell-Senior-Thesis/SignalClassifier/ClassifierMain/ClassifierMAIN.py
+.../Buell-Senior-Thesis/SignalClassifier/ClassifierHybrid/ClassifierHybridMain.py
 \end{quote}
@@
 
-\subsection{Command Line Arguments}
+\section{Command Line Arguments}
 
 \paragraph*{}The Classifier requires 6 command-line arguments to function properly. These are:
-\begin{itemize}
 
-\item[•]\textbf{readPath} (str/path)\\
+\subsection{readPath (str/path)}
 The local directory path where "read" data files are stored. Each file in this path is a a particularly formatted csv file. The csv/excel files are formatted as follows:
+
+\begin{center}
+\begin{tabular}{|c|c|c|}
+\hline \\
+Full (local) directory path to .wav file & Integer Class name & String Class Name \\
+\hline
+\end{tabular}
+\end{center}
+
+The folder should otherwise be empty because CSV Files formatted any other way will not be handled, and the program will crash. As an example, a CSV file may contain a first few lines that resemble:
+
+\begin{center}
+\begin{tabular}{|c|c|c|}
+\hline \\
+Fullpath	 & Target Int & Target Str \\ \hline
+C:/Users/.../GUITAR.C5.wav	 
+& 16 & GUITAR \\ \hline
+C:/Users/.../BASSCLARINET.As4.wav 
+& 4 & BASSCLARINET \\ \hline
+C:/Users/.../CLARINET.Cs5.wav 
+& 8 & BBCLARINET \\ \hline
+C:/Users/.../VIOLIN.A4.wav	
+& 34 & VIOLIN  \\ \hline
+\end{tabular}
+\end{center}
+
+The repository directory
 \begin{quote}
-(Detail formatting here)
+.../Buell-Senior-Thesis/SignalClassifier/Target-Data
 \end{quote}
-The folder should otherwise be empty.
+is an example of a valid directory, which each file  being well-formatted. There are two a python scripts in:
+\begin{quote}
+.../Buell-Senior-Thesis/SignalClassifier-Preprocessing/FileLabelEncoder
+\end{quote}
+That will help with creating these files. See the "MAIN" file for arguments.
 
-\item[•]\textbf{exportPath} (str/path)\\
+\subsection{exportPath (str/path)}
 The local directory path where progress data is exported to.
-When finished, this path will contain \textit{.csv} files detailing the training history of the model at each epoch or the label predictions of each sample.
+When finished, this path will contain \textit{.csv} files detailing the training history of the model at each epoch as well ads the the label predictions of each sample.
 
-\item[•]\textbf{modelPath} (str/path)\\
+\subsection{modelPath (str/path)}
 The local directory oath where the TensorFlow models are exported to.
@@
 
-\item[•]\textbf{ProgramMode} (str)\\
-Indicates which mode the classifier program is executed as. Must be in ["train","predict","train-predict"]. \\
+\subsection{ProgramMode (str)}
+Indicates which mode the classifier program is executed as. Must be in ["train","predict","train-predict"].
 \paragraph*{}In \textit{train} mode, all collected samples will be used to train the classifier model.
@@
 A "PREDICTIONS" file will be exported to "exportPath".
-In \textit{train-predict} mode, a 90\% training, and 10\% testing split is made pseudo-randomly.
+In \textit{train-predict} mode, a 90\% training, and 10\% testing split is made pseudo-randomly (This ratio can be changed, by adjusting a hard coded parameter in the train/test mode class).
 The Classifier then runs \textit{train} mode and \textit{test} mode with the respective data subsets.
 
-\item[•]\textbf{modelName} (str)\\
-String representation used to name the classifier model in a human-readable format.
+\subsection{modelName (str)}
+String representation used to name the classifier model in a human-readable format. Another Tensorflow/Keras script can be used to reload this model in it's trained state for future or external use.
 
-\item[•]\textbf{newModel} (bool)\\
+\subsection{newModel (bool)}
 Determines weather or not to create a NEW model of the given name.
@@
 If \textit{False}, the program looks for an existing model of the name to resume training/predictions given last saved state.
-
-\end{itemize}
 
@@
 
+(I still have to finish this...)
+
 % ================================================================
@@
 
+(And this...)
+
 % ================================================================

### 2021-03-11 SignalClassifier-Preprocessing/FileLabelEncoder/PreprocessMAIN.py

@@ -16,9 +16,15 @@ if __name__ == '__main__':
 
     # ESTABLISH DIRECTORIES
     homePath = os.getcwd()
+
+    # Where to export the data to?
     exptPath = "C:\\Users\\lando\\Documents\\GitHub\\Buell-Senior-Thesis\\SignalClassifier\\Target-Data"
+
+    # Where the RAW audio files are stored?
     dataPath = ["C:\\Users\\lando\\Documents\\audioWAV1","C:\\Users\\lando\\Documents\\audioWAV2",
                 "C:\\Users\\lando\\Documents\\audioNoiseWAV","C:\\Users\\lando\\Documents\\audioSyntheticWav"]  
+
+    # What the output files will be named?
     exptFile = ["Y1.csv","Y2.csv","Y3.csv","Y4.csv"]
 
     # Iteate through pairs of files / directories

### 2021-07-08 JMMPaper/PaperDrafts/main.tex
Updates to JMM Paper

@@
 
+\documentclass[conference,onecolumn,letterpaper]{IEEEtran}
 %\documentclass[conference,twocolumn,letterpaper]{IEEEtran}
-\documentclass[conference,letterpaper]{report}
 
@@
         $^1$Department of Physics and Astronomy\\
-        $^2$Department of Mathematics and Statistics\\
+        $^2$Integrated Applied Mathematics Program, Department of Mathematics and Statistics\\
         University of New Hampshire, Durham, New Hampshire, USA\\
@@
 
-Digital audio analysis and classification has become a very prolific field in the last few years.
+Digital audio analysis and classification has become a very active field in the last few years.
 The exact nature of each task can differ drastically from archival management, to security, or to commercial usage.
-In each case, we seek to place audio files into distinct categories called \textit{classes} based in inherent properties within the data \cite{James,Khan,Liu}.
+In each case, we seek to place audio files into distinct categories called \textit{classes} based on inherent properties of the data \cite{James,Khan,Liu}.
 Consider a collection of audio files, each containing a single note performed by some musical instrument and the task of matching the contents of the file to the instrument that it most closely resembles.
-This type of classification task is near trivial for humans, but given the volume of audio data in the modern world, it is impractical at a large scale.
-However, a computer has no difficulty processing large volumes of raw information, but encoding an explicit instruction set for classification is unreasonable.
-For this reason, we turn to a \textit{neural network} to combine the computational efficiency of a computer, with the decision-marking architecture of a brain \cite{Geron}.
+This type of classification task is near trivial for humans, but given the terabytes and petabytes of audio data in the modern world, it is impractical at a large scale.
+However, a computer has no difficulty processing large volumes of raw information, but encoding an explicit and accurate instruction set for classification is unreasonably challenging.
+For this reason, we turn to a neural network to combine the computational efficiency of a computer, with the decision-making architecture of a simulated brain \cite{Geron}.
 
-A neural network is a machine learning model that allows a set of inputs, $x$, called \textit{features}, to be transformed into a set of outputs, $y$,  called \textit{predictions} using a set of \textit{parameters}, $\Theta$ \cite{Geron,Goodfellow,Virtanen}.
+At a basic level, a neural network is a machine learning model that allows a set of inputs, $x$, called \textit{features}, to be transformed into a set of outputs, $y$,  called \textit{predictions} using a set of \textit{parameters}, $\Theta$ \cite{Geron,Goodfellow,Virtanen}.
 Audio classification with machine learning is also a well-explored field, with much research in developing an appropriate set of features, also called \textit{predictors}, for input \cite{James,Liu,Mierswa,Zhang}.
-Since the each classification task or data set may differ greatly from any other, each model often requires a unique combination of features which allows for the best possible performance \cite{Virtanen}.
+Since the each classification task or data set may differ greatly from any other, each model and data set often requires a unique combination of features which allows for the best possible performance \cite{Virtanen}.
 For musical instrument classification we have chosen predictors that represent the contents of an audio file using two different \textit{modalities}.
@@
 
-Multimodal learning differs from other types of supervised learning in that a model accepts and processes multiple inputs that are each different representations of the same data sample.
+Multimodal learning differs from other types of supervised learning in that a model is designed to accept and process multiple inputs simultaneously that are each different representations of the same data sample.
 Data sets that include or can be transformed into audio + visual, audio + text, or even text + text information, are all examples of multimodal data sets \cite{Li}.
-For digital audio classification, we have chosen to represent the contents of an audio file by decomposing it into \textit{image + vector} information format.
+For digital audio classification, we have chosen to represent the contents of an audio file by decomposing it into an \textit{image + vector} information format.
 We do this by constructing a 2D spectrogram and a 1D vector of features from the same waveform.
-Data from these different modes encodes complementary information which allows a model to develop parameters that can more thoroughly describe a sample when compared to it's unimodal learning methods \cite{Li}
+Data from these different modes encodes complementary information which allows a model to develop parameters that can more thoroughly classify a sample when compared to unimodal learning methods \cite{Li}
 
-To account for this multimodal input, we have constructed a \textit{hybrid neural network} (HNN) that utilizes two input branches, each with its own set of layers to handle an input mode.
-The spectrogram image is processed with a Convolutional Neural Network (CNN) which uses layers of 2D convolution and 2D pooling to generate a feature map, which is then flattened and transformed by repeated dense layers, and is visualized on the left side of Fig.
+To accommodate for this multimodal input, we have constructed a \textit{hybrid neural network} (HNN) that utilizes two input branches, each with its own set of layers to handle an input mode.
+The spectrogram image is processed with a Convolutional Neural Network (CNN) which uses layers of 2D convolution and 2D pooling to generate a feature map, which is then flattened and transformed by repeated dense layers - this is visualized on the left side of Fig.
 (\ref{fig:Architecture}).
@@
 (\ref{fig:Architecture}).
-The output each branch are concatenated into a single layer, which is further transformed into a single output prediction found at the bottom on Fig.
+The output of each branch is concatenated into a single layer, which is further transformed into a single output prediction found at the bottom on Fig.
 (\ref{fig:Architecture}).
 This means that the neural network learns a set of parameters which allows for mapping of \textit{both} input modes into a single prediction.
-Since the properties of the input features are critically important to classification success, multi-representation learning shows a great deal of promise and wide spread applicability \cite{Khan,Li,Liu,Virtanen}.
+Since the properties of the input features are critically important to classification success, multi-representation learning shows a great deal of promise and widespread applicability \cite{Khan,Li,Liu,Virtanen}.
 
@@
 
-A neural network is a type of machine learning algorithm that is inspired from the human brain \cite{Geron,Goodfellow}.
+A neural network defines a type of machine learning algorithm that is inspired from the human brain \cite{Geron,Goodfellow}.
 Where biological brains are constructed from neurons and connected through axons, neural networks are constructed from artificial neurons and connected through transformation functions.
@@
 Neurons are organized into groups called \textit{layers}, which interact with other layers through mathematical transformations such as matrix multiplications or convolutions \cite{Goodfellow}.
-Because of this, layers in the network can be considered a function, $f^{(l)}$ that accepts an array of activations from the previous layer $x^{(l-1)}$ and used a set of parameters to return an array of modified activations for the current layer, $x^{(l)}$.
+Because of this, each layer $l$ in a network can be considered to as function, $f^{(l)}$ that accepts an array of activations from the previous layer $x^{(l-1)}$ and uses a set of parameters to return an array of modified activations for the current layer, $x^{(l)}$.
+Thus each layer can be generally characterized by the expression:
 \begin{equation}
@@
 The structure of a neural network's layer-chain defines it's \textit{architecture}.
-The choice of architecture indicates the \textit{hypothesis-space} of the model a determines that set of all possible solutions that a trained model can arrive at.
+The choice of architecture indicates the \textit{hypothesis-space} of the model a determines the set of all possible solutions that a trained network can attain \cite{Goodfellow,James}.
 For deep neural networks this function chain can be dozens of layers long, and contain upwards of millions of parameters.
@@
 
-The hybrid neural network differs from this standard architecture in Eq.
-(\ref{eqn:LayerChain}) in that the function chain consists of two input layers, which push activations through two separate layer chains.
+The hybrid neural network used in this instrument classification task differs from the more standard architecture in Eq.
+(\ref{eqn:LayerChain}) in that the function chain consists of two input layers, each of which feed into their own respective layer chains, noted by $f_a$ and $f_b$.
+Each chain transforms activations through a non-overlapping graph, and are then merged at a subsequent hidden layer to produce graph $f_c$.
+The aggregation of both graphs allows us to generate a single prediction, $y^*$ based on the behavior of both inputs, $x^{(0)}_a$ and $x^{(0)}_b$.
 We detail the structure an function of each layer chain in section (\ref{subsec:CNN}) and (\ref{subsec:MLP}).
-After the activations have been transformed into mutually compatible format, they can be concatenated into a single array.
-This array then represents the start of a new layer chain whose output represents a a prediction that is aggregated from the two aforementioned input layers.
-We represents the layer-chain structure for a generalized HNN, with inputs $x^{(0)}_a$ and $x^{(0)}_b$ and outputs $y^*$ as :
+We represent the layer-chain structure for a generalized double-input HNN, with inputs $x^{(0)}_a$ and $x^{(0)}_b$ and outputs $y^*$ as :
+
 \begin{equation}
@@
 This structure allows us to consider and design each branch $a$ and $b$ as if they were separate neural networks.
-The outputs from $f^{(\alpha)}_a$ and $f^{(\beta)}_b$ represents the outputs of the branches respectively, which are concatenated at layer $f^{(\gamma)}_c$.
+The outputs from $f^{(\alpha)}_a$ and $f^{(\beta)}_b$ can be chosen to represents the predictions of the branches respectively, which are concatenated at layer $f^{(\gamma)}_c$.
 This marks the entry point of a new chain, which ends at the final output of the full model.
-Although we may consider the functionality of each layer-chain individually, they still are subsets of the same computational graph.
-This means that the full graph in Eq.
-(\ref{eqn:LayerGraph}) is considered as one neural network model in the training and validation process.
+Although we may consider the each layer-chain to be it's own entity, it is more appropriate to consider the chains to be subsets of the same computational graph.
+This means that Eq.
+(\ref{eqn:LayerGraph}) is considered to be one hybrid neural network model in the training and validation process.
 
@@
 The inputs to a neural network or any machine learning algorithm are called \textit{features} or \textit{predictors} \cite{James}.
-These are compact, low-dimensional representations of a data sample reflect its important characteristics \cite{Liu}.
+These are compact, low-dimensional representations of a data sample that reflect its important characteristics \cite{Liu}.
 Features should be chosen as to have low variance within each class and high variance between classes.
 For digital audio classification of musical instruments, features of the same musical instruments should exhibit very similar properties, while features from difference musical instruments should exhibit non-similar properties.
-In any learning algorithm, the role of feature extraction is to translate the raw information into descriptors that maximize the classification performance \cite{Virtanen}.
+In any learning algorithm, the role of feature extraction is to translate the raw information from a digital audio file into descriptors that maximize the classification performance \cite{Virtanen}.
 Although the neural network will classify the musical instrument within the digital audio sample, it will never interact with the raw waveform directly, instead will rely solely on these features.
-Suppose we implement a classification model that uses $p$ predictors.
+Suppose we implement a classification model that uses $p$ unqiue predictors.
 These features are usually combined into a single vector-like object for each sample, and then presented as input to the neural network \cite{Geron}.
@@
 
-The outputs to a classification neural network encodes the prediction that model has made for a particular sample.
-For a classifier with $k$ classes, there are $k$ output neurons transformed such that the sum of the activations is identically $1$ \cite{Goodfellow,James}.
+The outputs to a classification neural network encodes the prediction that the model has made given a particular set of inputs from a sample.
+For a classifier with $k$ classes, there are $k$ output neurons transformed such that the sum (or $L-1$ norm) of the output activations is identically $1$ \cite{Goodfellow,James}.
 This means the $k$ neurons can be treated as a probability density for each of the classes, where the neuron with the highest activation value is the prediction of the sample.
 For classification of musical instruments, each class represents a musical instrument type.
-We use $37$ classes of instruments ranging from woodwinds, to brass, to strings, to mallet percussion, to synthesizers.
+We use $37$ classes of instruments encapsulating woodwinds, brass, strings, mallet percussion, and synthesizers.
 Each audio file contains exactly one musical instrument sustaining one note.
@@
 \end{equation}
-The same sample will produce a similarly sized vector, $y^{*(i)}$, which all elements sum to $1$.
+The neural network will output an equivalently sized vector, $y^{*(i)}$, which all elements sum to $1$.
 
-To quantity the difference between $y$ and $y^*$, we introduce a \textit{cost function}, $J(y,y^*)$ which is also called an objective function or a loss function \cite{James}.
+To quantify the difference between $y$ and $y^*$, we introduce a \textit{cost function}, $J(y,y^*)$ which is also called an \textit{objective function} or a \textit{loss function} \cite{James}.
 The exact cost function used can differ based on the nature of the machine learning model or task, but typically multiple - category classification tasks use a \textit{categorical cross-entropy} (CXE) function \cite{Geron,Goodfellow}.
@@
 This returns a negative number, which we multiply by $-1$ to always yield a positive cost value.
-When a sample produces $y^*_{j} << 1$, the CXE cost returns a large value and when $y^*_{j} \approx 1$, then the CXE cost returns a small value.
+When a sample produces $y^*_{j} << 1$, meaning a poor prediction, the CXE cost returns a large value and when $y^*_{j} \approx 1$, meaning a strong prediction, then the CXE cost returns a small value.
 We provide a visualization of this behavior in Fig.
@@
 
-We characterize the cost function as producing a value inversely proportional to the prediction confidence- A large cost value indicates a \textit{poor} prediction label and a low cost value indicates a \textit{good} prediction label \cite{James,Virtanen}.
+We characterize the cost function as producing a value inversely proportional to the prediction confidence- A large cost value indicates a \textit{poor} prediction label and a low cost value indicates a \textit{strong} prediction label \cite{James,Virtanen}.
 Thus, we expect a trained neural network to produce consistently low cost function values across all samples in a data set.
-When a neural network does return consistently low cost function values for previously unseen samples, we consider it to be a \textit{fitted} or \textit{trained} network \cite{Geron,Goodfellow,James}.
+When a neural network does show this behavior for previously unseen samples, we consider it to be a \textit{fitted} or \textit{trained} neural network \cite{Geron,Goodfellow,James}.
 

### 2021-07-11 JMMPaper/PaperDrafts/main_v2.tex
Revert "Removed Redundant TEX files, renamed "main_v2" to "main""
This reverts commit d3b8518d2b7a8d2c44e56d6ff4e7fc78bbd44f4d.

--- 2021-02-13 JMMPaper/PaperDrafts/main.tex
@@
 % JMM Paper
-% PHYS 705.01 - Lab00
-% 21 Sept 2020
+% 
+% 09 Feb 2021
 % ================
@@
 %\documentclass[conference,twocolumn,letterpaper]{IEEEtran}
-\documentclass[conference,letterpaper]{report}
 
+\documentclass[12pt,letterpaper]{article}
 \usepackage{amsmath,amssymb}
@@
 \author{Landon H. Buell$^1$ and Kevin M. Short$^2$\\
-        $^1$lhb1007@wildcats.unh.edu and $^2$kevin.short@unh.edu\\
+        $^1$lhb1007@wildcats.unh.edu and $^2$Kevin.Short@unh.edu\\
         $^1$Department of Physics and Astronomy\\
-        $^2$Department of Mathematics and Statistics\\
+        $^2$Integrated, Applied Mathematics Program, 
+        \\Department of Mathematics and Statistics\\
         University of New Hampshire, Durham, New Hampshire, USA\\
@@
 Models often involve the input of a 2-D spectrogram or 1-D feature vector into a unimodal network such as a Convolutional Neural Network (CNN) or Multilayer Perceptron (MLP).
-In this study, we explore automatic classification of musical instruments using new hybrid neural-network (HNN)  architecture that combines the CNN and MLP models and provides superior performance over models that rely solely on one or the other.
-This hybrid network uses two branches, one being a CNN to process an image-like 2-D spectrogram, and the other being an MLP to process a 1-D feature vector.
+In this study, we explore automatic classification of audio files containing sounds performed on musical instruments using a new hybrid neural-network (HNN) architecture that combines the CNN and MLP models to provides superior performance over models that rely solely on one mode.
+This hybrid network uses two input branches, one being a CNN to process an image-like 2-D spectrogram, and the other being an MLP to process a 1-D feature vector.
 Within the model, a hidden layer combines activations from the two branches by concatenating them into a single 1-D dense layer, thus all predictions are a product of both branches.
-We describe in detail the creating of the spectrogram and features, as well as how they influence the chosen network architecture.
-We finish with a practical demonstration that uses this classifier model to match waveforms from a chaotic music synthesizer to real-world musical instruments.
-Training data is from studio recordings of the Philharmonia Symphony Orchestra and University of Iowa's Electronic Music Studios
+We describe in detail the creation of the spectrogram and features, as well as how they influence the chosen network architecture.
+We conclude by quantitatively comparing the performance of the hybrid neural network  Training data is from studio recordings of the Philharmonia Symphony Orchestra and University of Iowa's Electronic Music Studios
 \end{abstract}
@@
 
-Digital audio analysis and classification has become a very prolific field in the last few years.
+Digital audio analysis and classification has become a very active field in the last few years.
 The exact nature of each task can differ drastically from archival management, to security, or to commercial usage.
-In each case, we seek to place audio files into distinct categories called \textit{classes} based in inherent properties within the data \cite{James,Khan,Liu}.
+In each case, we seek to place audio files into non-overlapping categories called \textit{classes} based on inherent properties of the data \cite{James,Khan,Liu}.
 Consider a collection of audio files, each containing a single note performed by some musical instrument and the task of matching the contents of the file to the instrument that it most closely resembles.
-This type of classification task is near trivial for humans, but given the volume of audio data in the modern world, it is impractical at a large scale.
-However, a computer has no difficulty processing large volumes of raw information, but encoding an explicit instruction set for classification is unreasonable.
-For this reason, we turn to a \textit{neural network} to combine the computational efficiency of a computer, with the decision-marking architecture of a brain \cite{Geron}.
+This type of classification task is near trivial for humans, but given the  terabytes or petabytes of audio data in the modern world, it is impractical at a large scale.
+However, a computer has no difficulty processing large volumes of raw information, but encoding an explicit and accurate instruction set for automated classification is challenging.
+For this reason, we turn to a neural network to combine the computational efficiency of a computer, with the decision-marking architecture of a simulated brain \cite{Geron}.
 
-A neural network is a machine learning model that allows a set of inputs, $x$, called \textit{features}, to be transformed into a set of outputs, $y$,  called \textit{predictions} using a set of \textit{parameters}, $\Theta$ \cite{Geron,Goodfellow,Virtanen}.
+At a basic level, A neural network is a machine learning model that allows a set of inputs, $x$, called \textit{features}, to be transformed into a set of outputs, $y$,  called \textit{predictions} using a set of \textit{parameters}, $\Theta$ \cite{Geron,Goodfellow,Virtanen}.
 Audio classification with machine learning is also a well-explored field, with much research in developing an appropriate set of features, also called \textit{predictors}, for input \cite{James,Liu,Mierswa,Zhang}.
-Since the each classification task or data set may differ greatly from any other, each model often requires a unique combination of features which allows for the best possible performance \cite{Virtanen}.
-For musical instrument classification we have chosen predictors that represent the contents of an audio file using two different \textit{modalities}.
-We call this type of classification \textit{multimodal learning} \cite{Ngiam}.
+Since the each classification task or data set may differ greatly from any other, each model often requires a unique combination of features which allows for the best possible performance in a classification setting \cite{Virtanen}.
+For musical instrument classification we have chosen predictors that represent the contents of an audio file using two different \textit{modalities}, using spectral inputs, as well as cepstral and time-series derived features.
+This type of classification can be categorized as \textit{multimodal learning} \cite{Ngiam}.
 
-Multimodal learning differs from other types of supervised learning in that a model accepts and processes multiple inputs that are each different representations of the same data sample.
+Multimodal learning differs from other types of supervised learning in that a model accepts and processes multiple forms inputs that are each different representations of the same data sample.
 Data sets that include or can be transformed into audio + visual, audio + text, or even text + text information, are all examples of multimodal data sets \cite{Li}.
-For digital audio classification, we have chosen to represent the contents of an audio file by decomposing it into \textit{image + vector} information format.
-We do this by constructing a 2D spectrogram and a 1D vector of features from the same waveform.
-Data from these different modes encodes complementary information which allows a model to develop parameters that can more thoroughly describe a sample when compared to it's unimodal learning methods \cite{Li}
+For digital audio classification, we have chosen to represent the contents of an audio file by decomposing it into and \textit{image + vector} information format.
+We do this by constructing a 2D spectrogram and a 1D vector of features, which are both derived from the same waveform.
+Data from these different modes encodes complementary information which allows a model to develop parameters that can more thoroughly describe a sample when compared to unimodal learning methods \cite{Li}
 
-To account for this multimodal input, we have constructed a \textit{hybrid neural network} (HNN) that utilizes two input branches, each with its own set of layers to handle an input mode.
+To accommodate for this multimodal input, we have constructed a \textit{hybrid neural network} (HNN) that utilizes two input branches, each with its own set of layers to handle an input mode.
 The spectrogram image is processed with a Convolutional Neural Network (CNN) which uses layers of 2D convolution and 2D pooling to generate a feature map, which is then flattened and transformed by repeated dense layers, and is visualized on the left side of Fig.
 (\ref{fig:Architecture}).
-The feature vector input is processed by a Multilayer Perceptron (MLP) which uses repeated dense layers to transform the input, and is visualized on the right side of Fig.
+The time-series and cepstral data is processed to create a feature vector that is processed by a Multilayer Perceptron (MLP) which uses repeated fully-connected layers to transform the input.
+This is visualized on the right side of Fig.
 (\ref{fig:Architecture}).
-The output each branch are concatenated into a single layer, which is further transformed into a single output prediction found at the bottom on Fig.
+The output from each branch is concatenated into a single vector-like object within a hidden layer, which is further transformed into a single outputed prediction found at the bottom on Fig.
 (\ref{fig:Architecture}).
 This means that the neural network learns a set of parameters which allows for mapping of \textit{both} input modes into a single prediction.
-Since the properties of the input features are critically important to classification success, multi-representation learning shows a great deal of promise and wide spread applicability \cite{Khan,Li,Liu,Virtanen}.
+Since the properties of the input features are critically important to classification success, multi-representation learning shows a great deal of promise and widespread applicability \cite{Khan,Li,Liu,Virtanen}.
 
@@
 Neurons are organized into groups called \textit{layers}, which interact with other layers through mathematical transformations such as matrix multiplications or convolutions \cite{Goodfellow}.
-Because of this, layers in the network can be considered a function, $f^{(l)}$ that accepts an array of activations from the previous layer $x^{(l-1)}$ and used a set of parameters to return an array of modified activations for the current layer, $x^{(l)}$.
+Because of this, layers in the network can be considered a function, $f^{(l)}$ that accepts an array of activations from the previous layer $x^{(l-1)}$ and uses a set of parameters, $\Theta^{(l)}$, to return an array of modified activations for the current layer, $x^{(l)}$.
 \begin{equation}
     \label{eqn:LayerFunction}
-    f^{(l)} : x^{(l-1)} \rightarrow x^{(l)}
+    f^{(l)} : x^{(l-1)},\Theta^{(l)} \rightarrow x^{(l)}
 \end{equation}
-
+For ease of notation, we often omit $\Theta^{(l)}$, but it is implied that the parameters are present.
 By connecting multiple layers in succession, we form a layer-chain structure that describes the flow of information in the neural network, and lets us model a neural network as a computational graph \cite{Geron,Goodfellow}.
@@
 The structure of a neural network's layer-chain defines it's \textit{architecture}.
-The choice of architecture indicates the \textit{hypothesis-space} of the model a determines that set of all possible solutions that a trained model can arrive at.
+The choice of architecture indicates the \textit{hypothesis-space} of the model and determines the set of all possible solutions that a trained model can attain .
 For deep neural networks this function chain can be dozens of layers long, and contain upwards of millions of parameters.
@@
     \centering
-    \includegraphics[scale=0.14]{figures/CXELoss.png}
+    \includegraphics[scale=0.14]{./figures/CXELoss.png}
     \caption{Categorical Cross Entropy Cost Function given values for $y^*_{j} \in [0,1]$}
@@
 The standard western concert musical instruments that make up our base data set rarely have fundamental frequencies that extend beyond $6,000$ Hz.
-This means, that we will rarely see much energy or characteristic behavior above the $12,000$ Hz mark in the spectrograms.
-For this reason, we choose to crop each matrix as to include only information corresponding to the region of frequency-space form $0$ Hz to $12$ kHz.
+This means that we will rarely see much energy or characteristic behavior above the $12,000$ Hz mark in the spectrograms.
+For this reason, we choose to crop each matrix as to include only information corresponding to the region of frequency-space from $0$ Hz to $12$ kHz.
 We also choose to zero pad, or crop matrix $S$ so that there are exactly $k = 256$ columns.

### 2021-07-18 JMMPaper/PaperDrafts/main.tex
Removed redundant "main_v2"
Update main.tex
Updates to Layer Groups  Subsection

@@
         $^1$Department of Physics and Astronomy\\
-        $^2$Integrated Applied Mathematics Program, Department of Mathematics and Statistics\\
+        $^2$Founder of Integrated Applied Mathematics Program, Department of Mathematics and Statistics\\
         University of New Hampshire, Durham, New Hampshire, USA\\
@@
 \subsection{Structure}
-\label{subsec:Intro}
+\label{subsec:structure}
 
@@
 For deep neural networks this function chain can be dozens of layers long, and contain upwards of millions of parameters.
-Increasingly complicated networks allow for a high dimensional solution space, which potentially enables the modeling of more complex systems.
+Increasingly complicated networks allow for a high dimensional solution spaces, which potentially enables the model to describe more complicated systems.
 
@@
 ADAM has experimentally shown to be a very effective optimizer and useful for a wide range of data sets and architectures which is why we have chosen to implement it for this task \cite{Geron,Goodfellow}.
+
+% ================================================================
+
+\subsection{Layers Used in this Classification Model}
+\label{sec:LayersUsed}
+
+As mentioned in section \ref{subsec:structure} Eq.
+\ref{eqn:LayerFunction}), each layer in the neural network acts as it's own self-contained function that operates on the activations of the previous layer to transform them into the activations for the current layer.
+This function can take many different forms depending on where the layer sits in the chain, the type of information in the previous layer, and the nature of the solution that the neural network is trying to model \cite{Goodfellow,Loy}.
+For this classification  task, we employ five different layer types - (i) Dense, (ii) 2-dimensional convolution, (iii) 2-dimensional maximum-pooling, (iv) flattening, and (v) concatenation.
+In this section, we detail the forward-pass process of each layer and in Fig.
+(\ref{fig:Architecture}) we show how the combination of these layers are used to form the multimodal architecture of this network.
+
+\begin{enumerate}
+
+\item\textbf{Dense Layer}
+The dense layer, also called \textit{fully-connected} or \textit{affine} layer is one of earliest layer types used in artificial neural networks \cite{Geron,Loy}.
+A dense layer is composed of a collection of artificial neurons, each of which contains a numerical value within it (usually a floating-point number), called the \textit{activation} of that neuron.
+To compute the activation of any neuron, $x^{(l)_{i}}$, we take a weighted linear-combination of every neuron in the previous layer and add a constant to it, called a \textit{bias} \cite{Geron,Goodfellow,Loy}.
+
+It then follows that a full \textit{layer} of activations, is produced from the matrix-vector product of a weight-matrix $W^{(l)}$, and the previous layers of neurons $x^{(l-1)}$, and then added to a bias $b^{(l)}$ \cite{Goodfellow,Tensorflow}.
+We can model this transformation as :
+\begin{equation}
+\label{eqn:DenseCall}
+x^{(l)} = W^{(l)}x^{(l-1)} + b^{(l)}
+\end{equation}
+Suppose the layer $(l-1)$ contains $m$ neurons, and layer $(l)$ contains $n$ neurons.
+Each object then belongs to space: $x^{(l)} \in \mathbb{R}^(n \times 1)$, $x^{(l-1)} \in \mathbb{R}^(m \times 1)$, $b^{(l)} \in \mathbb{R}^(n \times 1)$, and $W^{(l)} \in \mathbb{R}^(n \times m)$.
+This transformation allows for an affine-transformation of activations which enables this layer to learn roughly linear decision boundaries between adjacent layers of neurons.
+This property of connecting every neuron in one layer to every other neuron in the previous layer is called \textit{dense connectivity} which is what gives this layer its name.
+
+Formal implementations of this the affine transformation layer type introduce non-linearity into the hypothesis space by applying an \textit{activation} function to Eqn.
+(\ref{eqn:DenseCall}) \cite{Goodfellow}.
+This enables us to model the far more complicated decision boundaries found in real-world problems.
+For this classification network, we choose to use the \textit{ReLU} activation function, defined as:
+\begin{equation}
+\label{eqn:ReLU}
+ReLU \big[ x^{(l)} \big] = \text{max} \big( 0, x^{(l)} \big)
+\end{equation} 
+This activation function preserves only the positive portion of each activation. \textcolor{red}{Does this Seem Out of place to you?}
+
+\item\textbf{2-Dimensional Convolution Layer}
+Convolution Layers Emerged from studying the brain's visual cortex, and have been used for image recognition \cite{Geron,Goodfellow,Loy}.
+The layer gets it's name due to it's implementation of the mathematical 2D \textit{convolution} operation.
+The 2D discrete convolution of function or 2D array $A$ and $B$ is given by:
+\begin{equation}
+\label{eqn:Conv2D}
+C[i,j]  = (A * B)[i,j] = \sum_{y}\sum_{v} A[i,j]B[i-u,j-v]
+\end{equation} 
+We implement this function in the neural network by creating a series of $K$ weighting matrices, called filters, of size $m \times n$, each to take the place of $A$ above \cite{Geron}.
+The shape of the filters in referred to as the \textit{convolution filter size}, and step them along in two dimensions according to a set \textit{stride size} \cite{Goodfellow,Loy}.
+
+In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(M \times N)}$, the convolution filters step through the input data and repeatedly compute the element-wise producr of each $m \times n$ filter and the local activations of the $x^{(l)}$ array.
+Each of the $K$ filters generate a new array of activation.
+For an appropriately trained neural network, some filters may result in detecting vertical lines, horizontal lines, sharp edges, or areas of mostly one color, etc \cite{Loy}.
+
+Just like the dense layer, we also choose to add a bias term to each output neuron, and can further modify the array by applying a non-linear activation function.
+for 2D convolution layer $(l)$, given input $x^{(l-1)}$, we compute the actions of the $k$-th filter $x^{(l)}_k$ using filter $W^{(l)}_k$ and bias $b^{(l)}_k$ as \cite{Goodfellow}.
+\begin{equation}
+\label{eqn:Conv2DCall}
+x^{(l-1)}_{k}(i,j) = b^{(l)}_{k} + 
+\sum_{u=0}^{M-1}\sum_{v=0}^{N-1} W^{(l)}_{k}(i,j) x^{(l-1)}_{k}(i-u,j-v)
+\end{equation}
+
+The Convolution layer allows for a few advantages over the dense layer.
+Among these are (i) \textit{spare-connectivity}: not every input neuron is connected to every single output neuron, so it can be more computationally efficient, (ii) \textit{positional invariance}: key features can be identified regardless of where the are in the input array, and (iii) \textit{Automatic feature detection}: as the weighting kernels are trained, they update as to automatically determine dominant features in the data without explicit human instruction \cite{Geron,Goodfellow,Loy}.
+
+\item\textbf{2-Dimensional Maximum Pooling}
+A maximum-pooling layer returns the value of the maximum neuron activation in a local subset of neurons.
+In the case of 2D max-pooling, we choose a kernel size $m \times n$, and pass that kernel over the inputs according to a chosen stride size \cite{Tensorflow}.
+The kernel takes the largest value in that area of inputs, and then places it into the output activations array.
+This operation is particularly useful for compressing the amount of data down to a computational efficient size.
+
+Pooling layers are typically place after a layer or set of layers of convolution \cite{Loy}.
+The purpose of this is arrangement is to reduce the width of the model at the pooling layer and ensure that only the dominant features with the largest activations are preserved \cite{Geron,Loy}.
+This layer is considered to be "non-trainable" because it does not use any adjustable parameters in it's transformation, only a fixed procedure that cannot be updated.
+
+\item\textbf{Flattening}
+A flattening layer is used
+
+\item\textbf{Concatenation}
+
+\end{enumerate}
 

### 2021-08-13 JMMPaper/PaperDrafts/main.tex
Updates to Introduction Section

@@
 In each case, we seek to place audio files into distinct categories called \textit{classes} based on inherent properties of the data \cite{James,Khan,Liu}.
-Consider a collection of audio files, each containing a single note performed by some musical instrument and the task of matching the contents of the file to the instrument that it most closely resembles.
-This type of classification task is near trivial for humans, but given the terabytes and petabytes of audio data in the modern world, it is impractical at a large scale.
-However, a computer has no difficulty processing large volumes of raw information, but encoding an explicit and accurate instruction set for classification is unreasonably challenging.
+Consider a collection of audio files, each containing the sound of a single note performed by some musical instrument and the task of matching the categorizing the file based on what instrument the contents most closely resembles.
+This type of classification task is near trivial for humans but given the terabytes and petabytes of audio data in the modern world, it is impractical at a large scale.
+However a computer has no difficulty processing large volumes of raw information but encoding an explicit and reliable instruction set for classification is unreasonably challenging.
 For this reason, we turn to a neural network to combine the computational efficiency of a computer, with the decision-making architecture of a simulated brain \cite{Geron}.
 
-At a basic level, a neural network is a machine learning model that allows a set of inputs, $x$, called \textit{features}, to be transformed into a set of outputs, $y$,  called \textit{predictions} using a set of \textit{parameters}, $\Theta$ \cite{Geron,Goodfellow,Virtanen}.
-Audio classification with machine learning is also a well-explored field, with much research in developing an appropriate set of features, also called \textit{predictors}, for input \cite{James,Liu,Mierswa,Zhang}.
-Since the each classification task or data set may differ greatly from any other, each model and data set often requires a unique combination of features which allows for the best possible performance \cite{Virtanen}.
-For musical instrument classification we have chosen predictors that represent the contents of an audio file using two different \textit{modalities}.
+At a basic level, a neural network is a machine learning model that allows a collection of inputs, $x$, called \textit{features}, to be transformed into a collection of outputs, $y$,  called \textit{predictions} through a set of adjustable values, $\Theta$, called \textit{parameters} \cite{Geron,Goodfellow,Virtanen}.
+In machine learning audio classification, much research is devoted to engineering and developing an appropriate ensemble of features that can be used to improve classification ability \cite{James,Liu,Mierswa,Zhang}.
+Since the nature of classification tasks and audio datasets may differ greatly from any other - each task must often develop a unique model and combination of features that will allow for the best possible performance \cite{Virtanen}.
+For musical instrument classification we have produced features that will represent the contents of each audio file using two different \textit{modalities}.
+Consequently, we must craft the neural network structure so that it may simultaneously accommodate these different input forms.
 We call this type of classification \textit{multimodal learning} \cite{Ngiam}.
 
-Multimodal learning differs from other types of supervised learning in that a model is designed to accept and process multiple inputs simultaneously that are each different representations of the same data sample.
-Data sets that include or can be transformed into audio + visual, audio + text, or even text + text information, are all examples of multimodal data sets \cite{Li}.
+Multimodal learning differs from other types of supervised learning in that a model is designed to accept and process multiple inputs forms that are each different representations of the same data sample, at the same time.
+Data sets that include or can be transformed into multiple forms such as \textit{audio + visual}, \textit{audio + text}, or even \textit{text + text} information, are all examples of multimodal data sets \cite{Li}.
 For digital audio classification, we have chosen to represent the contents of an audio file by decomposing it into an \textit{image + vector} information format.
-We do this by constructing a 2D spectrogram and a 1D vector of features from the same waveform.
-Data from these different modes encodes complementary information which allows a model to develop parameters that can more thoroughly classify a sample when compared to unimodal learning methods \cite{Li}
+We do this by constructing a 2-dimensional spectrogram and a 1-dimensional vector of features from the same audio file.
+Data from these different modes encodes complementary information which allows a model to develop parameters that can more thoroughly classify a sample when compared to singlemodal learning methods \cite{Li}.
 
-To accommodate for this multimodal input, we have constructed a \textit{hybrid neural network} (HNN) that utilizes two input branches, each with its own set of layers to handle an input mode.
-The spectrogram image is processed with a Convolutional Neural Network (CNN) which uses layers of 2D convolution and 2D pooling to generate a feature map, which is then flattened and transformed by repeated dense layers - this is visualized on the left side of Fig.
+To account for this multimodal input, we have constructed a \textit{hybrid neural network} (HNN) that utilizes two different input layers where each receives its prescribes input format and is handled by an appropriate layer chain.
+The 2D spectrogram image is processed with a Convolutional Neural Network (CNN) which uses layers of 2D convolution and 2D pooling to generate a feature map, is then flattened and transformed by repeated dense layers.
+This behavior is visualized on the left side of Fig.
 (\ref{fig:Architecture}).
-The feature vector input is processed by a Multilayer Perceptron (MLP) which uses repeated dense layers to transform the input, and is visualized on the right side of Fig.
+The 1D feature vector is processed by a Multilayer Perceptron (MLP) which uses repeated dense layers to transform the input, and is visualized on the right side of Fig.
 (\ref{fig:Architecture}).
-The output of each branch is concatenated into a single layer, which is further transformed into a single output prediction found at the bottom on Fig.
+The output of each branch is concatenated into a single dense layer, which is further transformed into a single output prediction found at the bottom on Fig.
 (\ref{fig:Architecture}).
@@
 The numerical value contained within an artificial neuron is the \textit{activation} of that neuron \cite{Levine}.
-Neurons are organized into groups called \textit{layers}, which interact with other layers through mathematical transformations such as matrix multiplications or convolutions \cite{Goodfellow}.
-Because of this, each layer $l$ in a network can be considered to as function, $f^{(l)}$ that accepts an array of activations from the previous layer $x^{(l-1)}$ and uses a set of parameters to return an array of modified activations for the current layer, $x^{(l)}$.
+Neurons are organized into groups called \textit{layers}, which interact with other nuurons in other layers through mathematical transformations such as matrix multiplications or convolutions \cite{Goodfellow}.
+Because of this interaction, each layer $(l)$ in a network can be considered as function, $f^{(l)}$ that accepts an array (vector,matrix,tensor,etc.) of activations from the \textit{previous} layer $x^{(l-1)}$ and uses a set of \textit{parameters} to return an array of modified activations for the \textit{current} layer, $x^{(l)}$.
 Thus each layer can be generally characterized by the expression:
@@
 
-By connecting multiple layers in succession, we form a layer-chain structure that describes the flow of information in the neural network, and lets us model a neural network as a computational graph \cite{Geron,Goodfellow}.
-In a feed-forward network with $L$ layers, inputs $x^{(0)}$ and outputs $y^*$, we can represent a layer-chain such as:
+By connecting multiple layers in succession, we form a chain-like structure of layers that describes the flow of information in the neural network.
+This allows us to model a neural network as a directed computational graph where each node is a layer that performs an operation  \cite{Geron,Goodfellow}.
+In a feed-forward network with $L$ layers, inputs $x^{(0)}$ and outputs $x^{(L-1)} = y^*$, we can represent a layer-chain such as:
 \begin{equation}

### 2021-08-13 JMMPaper/PaperDrafts/main.tex
Major Updates to Section 2 and 3

@@
 
-By connecting multiple layers in succession, we form a chain-like structure of layers that describes the flow of information in the neural network.
-This allows us to model a neural network as a directed computational graph where each node is a layer that performs an operation  \cite{Geron,Goodfellow}.
+By connecting multiple layers in succession, we form a chain-like structure of layers that describes the flow of information and allows us to model a neural network as a directed computational graph where each node is a layer that performs an operation  \cite{Geron,Goodfellow}.
 In a feed-forward network with $L$ layers, inputs $x^{(0)}$ and outputs $x^{(L-1)} = y^*$, we can represent a layer-chain such as:
@@
 \end{equation}
-The structure of a neural network's layer-chain defines it's \textit{architecture}.
-The choice of architecture indicates the \textit{hypothesis-space} of the model a determines the set of all possible solutions that a trained network can attain \cite{Goodfellow,James}.
-For deep neural networks this function chain can be dozens of layers long, and contain upwards of millions of parameters.
-Increasingly complicated networks allow for a high dimensional solution spaces, which potentially enables the model to describe more complicated systems.
+The structure of a neural network's layer-chain is often referred to as its \textit{architecture} and chooses the \textit{hypothesis space} of the model.
+This is the set of all possible functions that the network can choose as a solution \cite{Goodfellow,James}.
+For deep neural networks this function chain can be dozens of layers long, contain upwards of millions of parameters, may enable the model to cover a much more diverse set of solutions \cite{Geron}.
+By carefully choosing the architecture to compliment the nature of the problem, we build a preference of solutions into the model which enables it to perform better \cite{Goodfellow}.
 
 The hybrid neural network used in this instrument classification task differs from the more standard architecture in Eq.
-(\ref{eqn:LayerChain}) in that the function chain consists of two input layers, each of which feed into their own respective layer chains, noted by $f_a$ and $f_b$.
-Each chain transforms activations through a non-overlapping graph, and are then merged at a subsequent hidden layer to produce graph $f_c$.
-The aggregation of both graphs allows us to generate a single prediction, $y^*$ based on the behavior of both inputs, $x^{(0)}_a$ and $x^{(0)}_b$.
-We detail the structure an function of each layer chain in section (\ref{subsec:CNN}) and (\ref{subsec:MLP}).
+(\ref{eqn:LayerChain}) in that the function chain consists of two input layers, $f_a$ and $f_b$ that receive inputs $x^{(0)}_a$ and $x^{(0)}_b$ respectively.
+Each layer chain uses a particular arrangement of layers to form a sub-graph that compliments each type of input data.
+The activations are processed and transformed into compatible 1-dimensional format before they are combined at a designated hidden layer that concatenation them into a new layer.
+This new layer marks the start of final sub-graph, $f_c$ that leads to the output of the neural network.
 We represent the layer-chain structure for a generalized double-input HNN, with inputs $x^{(0)}_a$ and $x^{(0)}_b$ and outputs $y^*$ as :
@@
 
-This structure allows us to consider and design each branch $a$ and $b$ as if they were separate neural networks.
-The outputs from $f^{(\alpha)}_a$ and $f^{(\beta)}_b$ can be chosen to represents the predictions of the branches respectively, which are concatenated at layer $f^{(\gamma)}_c$.
-This marks the entry point of a new chain, which ends at the final output of the full model.
-Although we may consider the each layer-chain to be it's own entity, it is more appropriate to consider the chains to be subsets of the same computational graph.
-This means that Eq.
-(\ref{eqn:LayerGraph}) is considered to be one hybrid neural network model in the training and validation process.
+The combination of two sub-graphs, $f_a$ and $f_b$, into a third sub-graph, $f_c$, allows us to generate a single prediction, $y^*$ based on the behavior of both inputs.
+This property means that all layers in the network are part of one aggregate computational graph, one training process, and collectively form one hypothesis space.
+We detail the structure and function of each layer in the neural network in section (\ref{subsec:CNN}) and (\ref{subsec:MLP}).
 
@@
 For digital audio classification of musical instruments, features of the same musical instruments should exhibit very similar properties, while features from difference musical instruments should exhibit non-similar properties.
-In any learning algorithm, the role of feature extraction is to translate the raw information from a digital audio file into descriptors that maximize the classification performance \cite{Virtanen}.
-Although the neural network will classify the musical instrument within the digital audio sample, it will never interact with the raw waveform directly, instead will rely solely on these features.
-Suppose we implement a classification model that uses $p$ unqiue predictors.
-These features are usually combined into a single vector-like object for each sample, and then presented as input to the neural network \cite{Geron}.
+In any learning algorithm, the role of feature engineering is to translate the raw time-series information from a digital audio file into descriptors that maximize the classification performance \cite{Virtanen}.
+Although the neural network will classify the musical instrument within the digital audio sample, it will never interact with the waveform directly and instead will rely solely on these features.
+In a classification model that uses $p$ unique predictors, the features typically usually combined into a single vector-like object for each sample, and then presented as input to the neural network \cite{Geron}.
 We detail the classification features for this neural network in section (\ref{subsec:FeaturesMLP}) and (\ref{subsec:FeaturesCNN}).
@@
 The outputs to a classification neural network encodes the prediction that the model has made given a particular set of inputs from a sample.
-For a classifier with $k$ classes, there are $k$ output neurons transformed such that the sum (or $L-1$ norm) of the output activations is identically $1$ \cite{Goodfellow,James}.
-This means the $k$ neurons can be treated as a probability density for each of the classes, where the neuron with the highest activation value is the prediction of the sample.
-For classification of musical instruments, each class represents a musical instrument type.
+For a classifier with $k$ classes, there are $k$ neurons in the output layer, each one representing a particular class.
+These output activations which are transformed such that the sum (or $L-1$ norm) of them is identically $1$ so that they are collectively treated as a discrete probability density \cite{Goodfellow,James}.
+The neuron with the highest activation value indicates the class that the models predicts in input sample originated from.
+For classification of musical instruments, each neurons represents a musical instrument type.
 We use $37$ classes of instruments encapsulating woodwinds, brass, strings, mallet percussion, and synthesizers.
-Each audio file contains exactly one musical instrument sustaining one note.
 
@@
 
-A neural network is trained by providing a batch of input samples $X$, with a corresponding set of expected predictions $Y$.
+A neural network that uses $p$ features, $k$ classes, and $b$ samples per batch is trained by providing inputs $X \in \mathbb{R}^{(b \times p)}$, with a corresponding set of labels $Y \in \mathbb{Z}^{(b \times k)}$.
 Consider a sample $x \in X$ that is expected to produce corresponding label $y \in Y$.
 When passed into the network, $x$ produces some prediction label denoted as $y^*$.
-For an untrained network, we anticipate that $y^*$ and $y$ may differ greatly - meaning that the prediction is very different that the expected output, and classification performance is likely to be very poor.
+For an untrained network, we anticipate that $y^*$ and $y$ may differ greatly - meaning that the prediction is very different that the expected output, which will lead to poor classification performance.
 Since we know each sample in the data set to contain one, and only one musical instrument, we \textit{one-hot-encode} the expected label $y$.
@@
 To quantify the difference between $y$ and $y^*$, we introduce a \textit{cost function}, $J(y,y^*)$ which is also called an \textit{objective function} or a \textit{loss function} \cite{James}.
-The exact cost function used can differ based on the nature of the machine learning model or task, but typically multiple - category classification tasks use a \textit{categorical cross-entropy} (CXE) function \cite{Geron,Goodfellow}.
+The exact cost function used can differ based on the nature of the learning model and task, but typically a multiple - category classification tasks uses a \textit{categorical cross-entropy} (CXE) function \cite{Geron,Goodfellow}.
 The CXE cost for a single sample is defined as \cite{Goodfellow,Virtanen}:
@@
 \end{equation}
-Recall a sample belongs to class $j$.
-Since $y$ is one-hot-encoded, the only non-zero term in the sum is $y_{j} \ln(y^*_{j})$, where $y^*_{j} \in [0,1]$.
-This returns a negative number, which we multiply by $-1$ to always yield a positive cost value.
-When a sample produces $y^*_{j} << 1$, meaning a poor prediction, the CXE cost returns a large value and when $y^*_{j} \approx 1$, meaning a strong prediction, then the CXE cost returns a small value.
+Consider again a sample belongs to class $j$.
+Since $y$ is one-hot-encoded, the only non-zero term in the sum is $y_{j} \ln(y^*_{j})$.
+Since $y^*_{j} \in [0,1]$, then $\ln(y^*_{j}) < 0$ which we multiply by $-1$ to always yield a positive cost value.
+When a sample produces $y^*_{j} << 1$, meaning a poor prediction for that class, the CXE cost returns a large value and when $y^*_{j} \approx 1$, meaning a strong prediction for that category, then the CXE cost returns a small value.
 We provide a visualization of this behavior in Fig.
@@
 All operations in the final three steps are applied element-wise.
-ADAM has experimentally shown to be a very effective optimizer and useful for a wide range of data sets and architectures which is why we have chosen to implement it for this task \cite{Geron,Goodfellow}.
+ADAM has experimentally shown to be a very effective optimizer and useful for a wide range of data sets and architectures which is why we have chosen to implement it for this project \cite{Geron,Goodfellow}.
 
@@
 \ref{eqn:LayerFunction}), each layer in the neural network acts as it's own self-contained function that operates on the activations of the previous layer to transform them into the activations for the current layer.
-This function can take many different forms depending on where the layer sits in the chain, the type of information in the previous layer, and the nature of the solution that the neural network is trying to model \cite{Goodfellow,Loy}.
-For this classification  task, we employ five different layer types - (i) Dense, (ii) 2-dimensional convolution, (iii) 2-dimensional maximum-pooling, (iv) flattening, and (v) concatenation.
-In this section, we detail the forward-pass process of each layer and in Fig.
-(\ref{fig:Architecture}) we show how the combination of these layers are used to form the multimodal architecture of this network.
+The combination and arrangement of these layers define the model's hypothesis space which is the set of functions that the network can use as a solution.
+For this classification task we employ five different layer types detailed below.
+We also describe the forward-pass process of each layer and in Fig.
+(\ref{fig:Architecture}) and show how the combination of these layers are used to form the multimodal architecture of this network.
 
@@
 \item\textbf{Dense Layer}
-The dense layer, also called \textit{fully-connected} or \textit{affine} layer is one of earliest layer types used in artificial neural networks \cite{Geron,Loy}.
-A dense layer is composed of a collection of artificial neurons, each of which contains a numerical value within it (usually a floating-point number), called the \textit{activation} of that neuron.
-To compute the activation of any neuron, $x^{(l)_{i}}$, we take a weighted linear-combination of every neuron in the previous layer and add a constant to it, called a \textit{bias} \cite{Geron,Goodfellow,Loy}.
+The dense layer, also called \textit{fully-connected} or \textit{affine} layer is one of earliest layer types used in artificial neural networks \cite{Geron}.
+It is composed of a collection of artificial neurons, each of which contains a numerical value (usually a floating-point number) called the \textit{activation} of that neuron.
+The activation of any neuron, is computed through a weighted linear-combination of every neuron in the previous layer with a \textit{bias} added as well \cite{Geron,Goodfellow,Tensorflow}.
+This property of connecting every neuron in one layer to every other neuron in the previous layer is called \textit{dense connectivity} which is what gives this layer its name.
 
-It then follows that a full \textit{layer} of activations, is produced from the matrix-vector product of a weight-matrix $W^{(l)}$, and the previous layers of neurons $x^{(l-1)}$, and then added to a bias $b^{(l)}$ \cite{Goodfellow,Tensorflow}.
+It then follows that a full \textit{layer} of activations is produced from the matrix-vector product of a weight-matrix $W^{(l)}$, and the previous layers of neurons $x^{(l-1)}$, and then added to a bias $b^{(l)}$ \cite{Goodfellow,Tensorflow}.
 We can model this transformation as :
@@
 Each object then belongs to space: $x^{(l)} \in \mathbb{R}^(n \times 1)$, $x^{(l-1)} \in \mathbb{R}^(m \times 1)$, $b^{(l)} \in \mathbb{R}^(n \times 1)$, and $W^{(l)} \in \mathbb{R}^(n \times m)$.
-This transformation allows for an affine-transformation of activations which enables this layer to learn roughly linear decision boundaries between adjacent layers of neurons.
-This property of connecting every neuron in one layer to every other neuron in the previous layer is called \textit{dense connectivity} which is what gives this layer its name.
-
-Formal implementations of this the affine transformation layer type introduce non-linearity into the hypothesis space by applying an \textit{activation} function to Eqn.
-(\ref{eqn:DenseCall}) \cite{Goodfellow}.
-This enables us to model the far more complicated decision boundaries found in real-world problems.
-For this classification network, we choose to use the \textit{ReLU} activation function, defined as:
-\begin{equation}
-\label{eqn:ReLU}
-ReLU \big[ x^{(l)} \big] = \text{max} \big( 0, x^{(l)} \big)
-\end{equation} 
-This activation function preserves only the positive portion of each activation. \textcolor{red}{Does this Seem Out of place to you?}
+This transformation models an multidimensional affine-transformation which enables this layer to learn roughly linear decision boundaries between adjacent layers of neurons.
 
@@
 The Convolution layer allows for a few advantages over the dense layer.
-Among these are (i) \textit{spare-connectivity}: not every input neuron is connected to every single output neuron, so it can be more computationally efficient, (ii) \textit{positional invariance}: key features can be identified regardless of where the are in the input array, and (iii) \textit{Automatic feature detection}: as the weighting kernels are trained, they update as to automatically determine dominant features in the data without explicit human instruction \cite{Geron,Goodfellow,Loy}.
+Among these are (i) \textit{spare-connectivity}: not every input neuron is connected to every single output neuron, so it can be more computationally efficient, (ii) \textit{positional invariance}: key features can be identified regardless of where the are in the input array, and (iii) \textit{Automatic feature detection}: as the weighting kernels are trained, they update as to automatically determine dominant features in the data without explicit human instruction \cite{Geron,Goodfellow}.
 
@@
 
-Pooling layers are typically place after a layer or set of layers of convolution \cite{Loy}.
-The purpose of this is arrangement is to reduce the width of the model at the pooling layer and ensure that only the dominant features with the largest activations are preserved \cite{Geron,Loy}.
+Pooling layers are typically places after a layer or set of layers of convolution.
+The purpose of this is arrangement is to reduce the width of the model at the pooling layer and ensure that only the dominant features with the largest activations are preserved \cite{Geron}.
 This layer is considered to be "non-trainable" because it does not use any adjustable parameters in it's transformation, only a fixed procedure that cannot be updated.
@@
 \item\textbf{Flattening}
-A flattening layer is used
+A flattening layer is used to rearrange the shape of an array of activations without actually changing the values stored within them \cite{Tensorflow}.
+In particular, we use this layer to transform the 2D output of the convolution and pooling layers into 1D activations which can be passed into a dense layer.
+For an array of activations , $x^{(l-1)} \in \mathbb{R}^{(m \times n)}$, a flattening layer $f^{(l)}$ transforms them such that $x^{(l)} \in \mathbb{R}^{(1 \times mn)}$.
+This layer is also considered to be "non-trainable" because it does not use any adjustable parameters.
 
@@
 \end{enumerate}
+
+Formal implementations of the dense layer and 2D convoltional layer types introduce non-linearity into the hypothesis space by applying an \textit{activation} function to Eq.
+(\ref{eqn:DenseCall}) and Eq (\ref{eqn:Conv2DCall}) \cite{Goodfellow}.
+For this classification network, we choose to use the \textit{ReLU} activation function, defined as:
+\begin{equation}
+\label{eqn:ReLU}
+ReLU \big[ x^{(l)} \big] = \text{max} \big( 0, x^{(l)} \big)
+\end{equation} 
+Successive use of affine and convolutional transformations combine with non-linear activation functions allow a neural network to model the increasingly complicated decision-boundaries that arise in real-world problems \cite{Geron,Goodfellow}.
 
@@
 
-The features for this branch are derived from the time-domain or frequency-domain representation of a waveform.
-Each feature explored represents the values computed from each audio file, which are then assembled into a 1D array-like object called a feature vector.
+The features for this branch are derived from the time-domain and frequency-domain representations of a waveform.
+Each feature explored represents the values computed from and audio file, which are then assembled into a 1D array-like object called a feature vector.
 This vector is provided as input to the MLP branch of the neural network, which can be found on right side of Fig.
 (\ref{fig:Architecture}).
-To ensure a consistency of all extracted features, all waveforms have been truncated or zero-padded to contain a consistent $M$ samples.
+To ensure a consistency of all extracted features, all waveforms are assumed to have been truncated or zero-padded to contain a consistent $M$ samples.
 
@@
 Because it is represented as a 2D array or floating-point numbers, the spectrogram is effectively an image-like representation of a sound wave.
-Since each musical instrument produces it's own harmonic structure and transient response, each instrument can be identified by patterns within the spectrogram \cite{Virtanen}.
+Since each musical instrument produces it's own spectral signature and transient response, each instrument can be identified by patterns within the spectrogram \cite{Virtanen}.
 This means than when only use this modality, the audio classification becomes very similar to an image classification task \cite{Ngiam}.
@@
 
-A spectrogram is produced by applying the technique of \textit{frame-blocking} to a waveform to produce a matrix of short-time analysis frames \cite{Liu,Virtanen}.
+A spectrogram is produced by applying the technique of \textit{frame-blocking} to a waveform to produce a matrix of \textit{short-time analysis frames} (STAF) \cite{Liu,Virtanen}.
+An STAF is a subsets of a waveform in the time-domain.
 We choose each frame to contain $N = 1024$ samples, with a $768$ sample overlap between adjacent frames.
@@
 \end{figure}
-We organize the analysis frames into a matrix, $A$ with shape $N \times k$, such that each row is a frame.
-We apply a Hanning window of length $N$ to each row of $A$.
-This eliminates discontinuities at the edges of each analysis frame, and allows for a cleaner transform into frequency-space \cite{Virtanen}.
+We organize the analysis frames into a matrix, $A$ with shape $k \times N$, such that each row is a frame.
+We apply a Hanning window of length $N$ to each row of $A$ which helps to eliminate discontinuities at the edges of each analysis frame and allows for a cleaner transform into frequency-space \cite{Virtanen}.
 The effect of applying an Hanning window function to an analysis frame of $1024$ samples can be found in Fig.
 (\ref{fig:WindowFrame}).
-We tail-pad each time-series analysis frame by an additional $1024$ zeros which brings each frame to $2048$ samples, and gives a higher frequency-space resolution \cite{Sahidullah}.
+We tail-pad each time-series analysis frame by an additional $1024$ zeros which brings each frame to $2048$ samples for a higher frequency-space resolution \cite{Sahidullah}.
 The spectrogram, $S$, is produced by computing:
@@
     \subfigure[]{\includegraphics[width=0.45\textwidth]{figures/WindowedFrame.png}}
-    \caption{(a) A standard time-series analysis frame made up of $1024$ samples and (b) The same frame with a standard Hanning Window Applied to it.
+    \caption{(a) A standard time-series analysis frame made up of $1024$ samples and (b) The same frame with a standard Hanning Window applied to it.
 This sample is taken from a bowed violin playing an $A4$ note.}
@@
 The standard western concert musical instruments that make up our base data set rarely have fundamental frequencies that extend beyond $6,000$ Hz.
-This means, that we will rarely see much energy or characteristic behavior above the $12,000$ Hz mark in the spectrograms.
+Similarly, we rarely find much energy or characteristic behavior above the $12,000$ Hz mark in the spectrograms.
 For this reason, we choose to crop each matrix as to include only information corresponding to the region of frequency-space form $0$ Hz to $12$ kHz.
-We also choose to zero pad, or crop matrix $S$ so that there are exactly $k = 256$ columns.
+Since the audio files were all sample at $44.1$ kHz, this nearly quarters the height of the spectrogram and choose to zero pad, or crop matrix $S$ so that there are exactly $k = 256$ columns.
+This combination of choices drastically reduces the width and complexity of the model at the entry layer saving significant computational resources.
 The result is an image-like representation of a digital audio file with shape $558 \times 256$, which is passed as a feature to the input of the CNN branch of the HNN.

### 2021-08-15 JMMPaper/PaperDrafts/main.tex
Updated Resampling + Metrics Section

@@
 % JMM Paper
-% PHYS 705.01 - Lab00
-% 21 Sept 2020
+% PHYS 799
+% January Sept 2021
 % ================
@@
 \author{Landon H. Buell$^1$ 				and Kevin M. Short$^2$\\
-        $^1$lhb1007@wildcats.unh.edu and 				$^2$kevin.short@unh.edu\\
+        $^1$lhb1007@wildcats.unh.edu  		$^2$kevin.short@unh.edu\\
         $^1$Department of Physics and Astronomy\\
@@
 
-The standard western concert musical instruments that make up our base data set rarely have fundamental frequencies that extend beyond $6,000$ Hz.
-Similarly, we rarely find much energy or characteristic behavior above the $12,000$ Hz mark in the spectrograms.
+The standard western concert musical instruments that make up our data set rarely have fundamental frequencies that extend beyond $6$ kHz.
+Similarly, we rarely find much energy or characteristic behavior above the $12$ kHz mark in the spectrograms.
 For this reason, we choose to crop each matrix as to include only information corresponding to the region of frequency-space form $0$ Hz to $12$ kHz.
-Since the audio files were all sample at $44.1$ kHz, this nearly quarters the height of the spectrogram and choose to zero pad, or crop matrix $S$ so that there are exactly $k = 256$ columns.
+Since the audio files were all sampled at $44.1$ kHz, this nearly quarters the number of rows in the spectrogram.
+We have also choosen to zero pad or crop the matrix $S$ so that there are exactly $k = 256$ columns.
 This combination of choices drastically reduces the width and complexity of the model at the entry layer saving significant computational resources.
@@
 (\ref{fig:Architecture}) and is an implementation of multilayer perceptron (MLP) neural network.
-The MLP processed input by transforming activations through repeated layers of neurons, modeled as vectors of floating-point numbers.
-Each neurons in a given layer by a linear combination of every neuron in the previous layer.
-Practical implementations introduce the addition of a constant value to each neuron (called a \textit{bias}), and some form or non-linear activation function \cite{Geron,Goodfellow}.
-Transformations of this type are called \textit{dense} layers, which when compounded can model that highly non-linear decision boundaries than arise in real world problems \cite{James}.
+The MLP processed input by transforming activations through repeated dense layer types explored in sec.
+(\ref{sec:LayersUsed}.1).
+The input to this branch is a vector of features, described in section (\ref{subsec:FeaturesMLP}), which are transformed through two dense layers, with $64$ neurons in each.
 
-The input to this branch is a vector of features, described in section (\ref{subsec:FeaturesMLP}), which are transformed through two dense layers, with $64$ neurons each.
-Passing through these dense layers allows these inputs to be handled just like any other multilayer perceptron model, which have shown experimental success in the last few decades.
-We choose to implement one here, enabling the training process to learn parameters that can effectively minimize the cost function and sucessfully classify inputs.
-The output of the last dense layer is provided to the concatenation layer, which merges it with the output of the convolution branch.
+\textcolor{red}{FINISH THIS!}
 
@@
 The Convolution branch is pictured on the left side of Fig.
-(\ref{fig:Architecture}) and is an implementation of a convolutional neural network (CNN), connected to a multilayer perceptron (MLP).
+(\ref{fig:Architecture}) and is an implementation of a convolutional neural network (CNN), connected to it's own multilayer perceptron (MLP).
 This branch accepts 2D image-like input in the form of a spectrogram, described in section (\ref{subsec:FeaturesCNN}).
-The order and organization of the layers in this branch of the model was inspired from Oxford's \textit{VGG-16} network architecture \cite{Geron}.
+The order and organization of the layers in this branch of the model was inspired from Oxford's \textit{VGG-16} network architecture \cite{Geron}\textcolor{red}{Add VGG citation!}.
 VGG-16 model uses successive 2D convolutions to identify characteristic features, followed by 2D pooling layers to reduce the size of the activations.
-Unlike VGG-16, our model does not use padding to keep the image resolution after each convolution layer, and instead the resolution of the image is dropeed with every layer.
+Unlike VGG-16, our model does not use padding to keep the image resolution after each convolution layer, and instead the resolution of the image is dropped with every layer.
 
@@
 \end{enumerate}
+
 The combination of layers in this order allows for the convolutions to detect characteristic features in the spectrogram, while the pooling allows for minor positional in variance in those features.
@@
 The first $K-1$ folds are used to train the model, and the last fold is used to evaluate how well the network performs on unseen samples.
-This process repeats of all $K$ folds.
+This process repeats of all $K$ folds, on $K$ unique models.
 
 The result of X-validation is $K$ neural network models that have all been trained and evaluated on overlapping subsets of the full data set.
-Each model contains a set of learned parameters, $\Theta$ that represent a possible outcome if trained on the given data set \cite{James}.
+Each model contains a collection of learned parameters, $\Theta$ that represent a possible outcome if trained on the given subset \cite{Geron,James}.
 By repeating this and comparing the performance across each fold, we understand how the chosen architecture and hyper-parameters influence the stability of the performance of the network.
+
 Across each fold, we expect to observe a reasonably high, as well as consistent performance.
-This is indicates a model that can train effectively, and generalize appropriately.
-X-validation is critical to ensuring that a model is behaving as expected.
+A model that does not perform well on all of the splits indicates a poor choice or architecture or features, and a model that performs inconsistently across the splits indicates a model that suffers from high-variance, where small changes in initial conditions can drastically affect it's classification abilities \cite{James}.
+When we see consistent and strong performance across multiple splits, we develop confidence that we have a model that can train effectively, and generalize appropriately \cite{Geron}.
 
@@
 We choose the following metrics to evaluate the performance of our HNN.
-All metrics are define in relation to \textit{true-positive} (TP), \textit{true-negative} (TN), \textit{false-positive} (FP), and \textit{false-negative} (FN) predictions \cite{Geron,James}.
+All metrics are defined in relation to \textit{true-positive} (TP), \textit{true-negative} (TN), \textit{false-positive} (FP), and \textit{false-negative} (FN) predictions \cite{Geron,James}.
 These metrics are computed for each of $K$ cross validation folds.
@@
     \item \textbf{Accuracy Score} - is the ratio of correct predictions to total predictions made by the model.
-While accuracy is convenient for quick estimates of performance, it does not provide much statistical information on the nature of predictions made of the model.
+While accuracy is convenient for quick estimates of performance, it does not provide much statistical information on the nature of choices made.
 This is especially true when classes have non-uniform representations in the data set.
@@
 
-    \item \textbf{Precision Score} - is the ratio of correctly identified elements, to all relevant elements in the data set.
-The higher the score, the \textit{specific} a model is to a particular category.
+    \item \textbf{Precision Score} - is the fraction of retrieved samples that were relevant.
+This means that the higher the score, the more \textit{specific} a model is when categorizing.
 The precision score of a classification algorithm is given by:
@@
 
-    \item \textbf{Recall Score} - is the ratio of correctly identified elements, to all relevant elements in the data set.
+    \item \textbf{Recall Score} - is the fraction of relevant samples that were retrieved.
 The higher the score, the \textit{sensitive} a model is to a particular category.

### 2021-08-22 JMMPaper/PaperDrafts/main.tex
Updates to Layer Types

@@
 We describe in detail the creating of the spectrogram and features, as well as how they influence the chosen network architecture.
-We finish with a practical demonstration that uses this classifier model to match waveforms from a chaotic music synthesizer to real-world musical instruments.
-Training data is from studio recordings of the Philharmonia Symphony Orchestra and University of Iowa's Electronic Music Studios
+\textcolor{red}{We finish with a practical demonstration that uses this classifier model to match waveforms from a chaotic music synthesizer to real-world musical instruments.} Training data is from studio recordings of the Philharmonia Symphony Orchestra and University of Iowa's Electronic Music Studios
 \end{abstract}
@@
 Where biological brains are constructed from neurons and connected through axons, neural networks are constructed from artificial neurons and connected through transformation functions.
-The numerical value contained within an artificial neuron is the \textit{activation} of that neuron \cite{Levine}.
-Neurons are organized into groups called \textit{layers}, which interact with other nuurons in other layers through mathematical transformations such as matrix multiplications or convolutions \cite{Goodfellow}.
+The numerical value contained within an artificial neuron its \textit{activation}\cite{Levine}.
+Neurons are often organized into groups called \textit{layers}, that interact with other neurons in other layers through mathematical transformations such as matrix multiplications or convolutions \cite{Goodfellow}.
 Because of this interaction, each layer $(l)$ in a network can be considered as function, $f^{(l)}$ that accepts an array (vector,matrix,tensor,etc.) of activations from the \textit{previous} layer $x^{(l-1)}$ and uses a set of \textit{parameters} to return an array of modified activations for the \textit{current} layer, $x^{(l)}$.
@@
 This is the set of all possible functions that the network can choose as a solution \cite{Goodfellow,James}.
-For deep neural networks this function chain can be dozens of layers long, contain upwards of millions of parameters, may enable the model to cover a much more diverse set of solutions \cite{Geron}.
+For deep neural networks this function chain can be dozens of layers long, contain upwards of millions of parameters, and may enable the model to cover a much more diverse set of solutions \cite{Geron}.
 By carefully choosing the architecture to compliment the nature of the problem, we build a preference of solutions into the model which enables it to perform better \cite{Goodfellow}.
@@
 (\ref{eqn:LayerChain}) in that the function chain consists of two input layers, $f_a$ and $f_b$ that receive inputs $x^{(0)}_a$ and $x^{(0)}_b$ respectively.
-Each layer chain uses a particular arrangement of layers to form a sub-graph that compliments each type of input data.
-The activations are processed and transformed into compatible 1-dimensional format before they are combined at a designated hidden layer that concatenation them into a new layer.
-This new layer marks the start of final sub-graph, $f_c$ that leads to the output of the neural network.
+Each chain uses a particular arrangement of layer to form a sub-graph that compliments each type of input data.
+The activations are processed and transformed into a compatible 1-dimensional format before they are combined at a designated hidden layer, $f_c^{\gamma}$ and then transform again to produce the model's final prediction .
 We represent the layer-chain structure for a generalized double-input HNN, with inputs $x^{(0)}_a$ and $x^{(0)}_b$ and outputs $y^*$ as :
@@
 The inputs to a neural network or any machine learning algorithm are called \textit{features} or \textit{predictors} \cite{James}.
-These are compact, low-dimensional representations of a data sample that reflect its important characteristics \cite{Liu}.
+These are compact, low-dimensional representations of a single data sample that reflect its important characteristics \cite{Liu}.
 Features should be chosen as to have low variance within each class and high variance between classes.
-For digital audio classification of musical instruments, features of the same musical instruments should exhibit very similar properties, while features from difference musical instruments should exhibit non-similar properties.
+We expect features drawn from different samples of the same musical instruments to have very similar properties while features drawn from samples of different musical instruments to exhibit non-similar properties.
 In any learning algorithm, the role of feature engineering is to translate the raw time-series information from a digital audio file into descriptors that maximize the classification performance \cite{Virtanen}.
 Although the neural network will classify the musical instrument within the digital audio sample, it will never interact with the waveform directly and instead will rely solely on these features.
-In a classification model that uses $p$ unique predictors, the features typically usually combined into a single vector-like object for each sample, and then presented as input to the neural network \cite{Geron}.
+In a classification model that uses $p$ unique predictors for each sample will typically combined into a single vector-like object which is then presented as input to the neural network \cite{Geron}.
 We detail the classification features for this neural network in section (\ref{subsec:FeaturesMLP}) and (\ref{subsec:FeaturesCNN}).
@@
 
-A neural network that uses $p$ features, $k$ classes, and $b$ samples per batch is trained by providing inputs $X \in \mathbb{R}^{(b \times p)}$, with a corresponding set of labels $Y \in \mathbb{Z}^{(b \times k)}$.
+Consider a neural network that uses $p$ features, $k$ classes, and $b$ samples per batch is trained by providing inputs $X \in \mathbb{R}^{(b \times p)}$, with a corresponding set of labels $Y \in \mathbb{Z}^{(b \times k)}$.
 Consider a sample $x \in X$ that is expected to produce corresponding label $y \in Y$.
@@
 Since $y^*_{j} \in [0,1]$, then $\ln(y^*_{j}) < 0$ which we multiply by $-1$ to always yield a positive cost value.
-When a sample produces $y^*_{j} << 1$, meaning a poor prediction for that class, the CXE cost returns a large value and when $y^*_{j} \approx 1$, meaning a strong prediction for that category, then the CXE cost returns a small value.
+When a sample produces $y^*_{j} << 1$, meaning a poor prediction for that category, the CXE cost returns a large value and when $y^*_{j} \approx 1$, meaning a strong prediction for that category, then the CXE cost returns a small value.
 We provide a visualization of this behavior in Fig.
@@
 Each layer $f^{(l)}$, of the model is a function that contains a set of parameters held within arrays $W^{(l)}$ and $b^{(l)}$ that are used to transform activations through the layer chain \cite{Goodfellow}.
-The process of training the network is the manipulation of these parameters in each layer, such that each input $x$ can produce a output, $y^*$ that is reasonably close to $y$.
-Since we can quantify the difference between the expected output and the given output with a cost function, we can use this as a metric for measuring how "trained" a model is \cite{James}.
-Specifically, we train a neural network by \textit{optimizing} the parameters in each layer to allow for this consistently low cost function value \cite{Geron,Goodfellow}.
-Note that we optimize the cost function under the assumption that doing so will also improve the classification performance.
-This is called \textit{indirect optimization} \cite{Goodfellow}.
+The process of training the network is the manipulation of these parameters in each layer such that each input $x$ can produce a output, $y^*$ that is reasonably close to $y$ \cite{Geron,Virtanen}.
+Since we can quantify the difference between $y^*$ and $y$ with a cost function, we use this as a metric for measuring how "trained" a model is \cite{James}.
+Specifically, we train a neural network by \textit{optimizing} the parameters in each layer to allow for a consistently low cost function value across multiple samples \cite{Geron,Goodfellow}.
+Note that we optimize the cost function under the assumption that doing so will also improve the classification performance when is a concept called \textit{indirect optimization} \cite{Goodfellow}.
 
@@
 We instead optimize the network with a numerical iterative method based on \textit{gradient descent} \cite{Geron,Goodfellow}.
-Gradient descent is the process of (i.) computing the gradient of the cost function with respect to every element in $\Theta$ and (ii.) adjusting each parameter in $\Theta$ according to the elements in that gradient vector, shown in Eq.(\ref{eqn:GradDesc}), often scaled by a \textit{learning rate} $\alpha$.
-We compute the gradient of the cost function, $\nabla_{\Theta}J$ through a process call \textit{backwards propagation} \cite{Geron}.
-This algorithms uses the derivative chain-rule from multivariate calculus to begin at the last layer of the network, and work backwards through the layer chain in Eq.
+Gradient descent is the process of repeatedly (i.) computing the gradient vector of the cost function with respect to every element in $\Theta$ and (ii.) adjusting each parameter in $\Theta$ according to the elements in that gradient vector, shown in Eq.(\ref{eqn:GradDesc}).
+For each iteration, we compute the gradient of the cost function, $\nabla_{\Theta}J$ through a process called \textit{backwards propagation} \cite{Geron}.
+This algorithm uses the derivative chain-rule from multivariate calculus to begin at the last layer of the network, and work backwards through the layer chain in Eq.
 (\ref{eqn:LayerChain}) to construct the elements of $\nabla_{\Theta}J$ \cite{Goodfellow,Virtanen}.
@@
 \end{equation}
+
+We introduce a parameter $\alpha$ as the \textit{learning rate} of the model.
+This scales each element in the gradient vector as t control the "step size" taken with each iteration \cite{Geron,Goodfellow,Virtanen}.
 
@@
 
-ADAM provides a much more powerful and stable optimization algorithm at a higher computational cost \cite{Geron}.
+ADAM provides a much more powerful and stable optimization algorithm at a higher computational cost \cite{Geron,Tensorflow}.
 Note that the superscript $(i)$ indicates an iteration index where a superscript $i$ is exponentiation.
@@
 
-As mentioned in section \ref{subsec:structure} Eq.
-\ref{eqn:LayerFunction}), each layer in the neural network acts as it's own self-contained function that operates on the activations of the previous layer to transform them into the activations for the current layer.
+As mentioned in sec.
+(\ref{subsec:structure}) Eq.
+(\ref{eqn:LayerFunction}), each layer in the neural network acts as it's own self-contained function that operates on the activations of the previous layer to transform them into the activations for the current layer.
 The combination and arrangement of these layers define the model's hypothesis space which is the set of functions that the network can use as a solution.
@@
 The dense layer, also called \textit{fully-connected} or \textit{affine} layer is one of earliest layer types used in artificial neural networks \cite{Geron}.
-It is composed of a collection of artificial neurons, each of which contains a numerical value (usually a floating-point number) called the \textit{activation} of that neuron.
-The activation of any neuron, is computed through a weighted linear-combination of every neuron in the previous layer with a \textit{bias} added as well \cite{Geron,Goodfellow,Tensorflow}.
-This property of connecting every neuron in one layer to every other neuron in the previous layer is called \textit{dense connectivity} which is what gives this layer its name.
-
-It then follows that a full \textit{layer} of activations is produced from the matrix-vector product of a weight-matrix $W^{(l)}$, and the previous layers of neurons $x^{(l-1)}$, and then added to a bias $b^{(l)}$ \cite{Goodfellow,Tensorflow}.
+It is composed of a collection of artificial neurons,where the activation of any neuron, is computed through a weighted linear-combination of every neuron in the previous layer with a \textit{bias} added as well \cite{Geron,Goodfellow,Tensorflow}.
 We can model this transformation as :
@@
 \end{equation}
-Suppose the layer $(l-1)$ contains $m$ neurons, and layer $(l)$ contains $n$ neurons.
-Each object then belongs to space: $x^{(l)} \in \mathbb{R}^(n \times 1)$, $x^{(l-1)} \in \mathbb{R}^(m \times 1)$, $b^{(l)} \in \mathbb{R}^(n \times 1)$, and $W^{(l)} \in \mathbb{R}^(n \times m)$.
+
+This property of connecting every neuron in one layer to every other neuron in the previous layer is called \textit{dense connectivity} which is what gives this layer its name.
 This transformation models an multidimensional affine-transformation which enables this layer to learn roughly linear decision boundaries between adjacent layers of neurons.
@@
 \item\textbf{2-Dimensional Convolution Layer}
-Convolution Layers Emerged from studying the brain's visual cortex, and have been used for image recognition \cite{Geron,Goodfellow,Loy}.
+Convolution Layers emerged from studying the brain's visual cortex, and have been used for image recognition for decades \cite{Geron,Goodfellow}.
 The layer gets it's name due to it's implementation of the mathematical 2D \textit{convolution} operation.
-The 2D discrete convolution of function or 2D array $A$ and $B$ is given by:
+The 2D discrete convolution of function of arrays $A$ and $B$ is given by:
 \begin{equation}
@@
 \end{equation} 
-We implement this function in the neural network by creating a series of $K$ weighting matrices, called filters, of size $m \times n$, each to take the place of $A$ above \cite{Geron}.
-The shape of the filters in referred to as the \textit{convolution filter size}, and step them along in two dimensions according to a set \textit{stride size} \cite{Goodfellow,Loy}.
+Where $A$, $B$, and $C$ are also 2D arrays themselves.
+In a neural network, we implement this function by creating a series of $K$ weighting matrices, called filters, each of size $m \times n$, and the place of $A$ above \cite{Geron}.
+The shape of the filters in referred to as the \textit{convolution filter size}, and step them along in two dimensions according to a set \textit{stride size} \cite{Goodfellow}.
 
-In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(M \times N)}$, the convolution filters step through the input data and repeatedly compute the element-wise producr of each $m \times n$ filter and the local activations of the $x^{(l)}$ array.
+In the case of a 2D input array, $x^{(l-1)} \in \mathbb{R}^{(M \times N)}$, the convolution filters step through the input data and repeatedly compute the element-wise product of each $m \times n$ filter and the local activations of the $x^{(l)}$ array.
 Each of the $K$ filters generate a new array of activation.
-For an appropriately trained neural network, some filters may result in detecting vertical lines, horizontal lines, sharp edges, or areas of mostly one color, etc \cite{Loy}.
+For an appropriately trained neural network, some filters may result in detecting vertical lines, horizontal lines, sharp edges, or areas of mostly one color, etc \cite{Geron}.
 
 Just like the dense layer, we also choose to add a bias term to each output neuron, and can further modify the array by applying a non-linear activation function.
-for 2D convolution layer $(l)$, given input $x^{(l-1)}$, we compute the actions of the $k$-th filter $x^{(l)}_k$ using filter $W^{(l)}_k$ and bias $b^{(l)}_k$ as \cite{Goodfellow}.
+for 2D convolution layer $(l)$, given input $x^{(l-1)}$, we compute the activations of the $k$-th filter $x^{(l)}_k$ using filter $W^{(l)}_k$ and bias $b^{(l)}_k$ as \cite{Goodfellow}.
 \begin{equation}
 \label{eqn:Conv2DCall}
-x^{(l-1)}_{k}(i,j) = b^{(l)}_{k} + 
-\sum_{u=0}^{M-1}\sum_{v=0}^{N-1} W^{(l)}_{k}(i,j) x^{(l-1)}_{k}(i-u,j-v)
+x^{(l)}_{k}(i,j) = b^{(l)}_{k} + 
+\sum_{u=0}^{M-1}\sum_{v=0}^{N-1} W^{(l)}_{k}(i,j) x^{(l-1)}(i-u,j-v)
 \end{equation}
@@
 The kernel takes the largest value in that area of inputs, and then places it into the output activations array.
-This operation is particularly useful for compressing the amount of data down to a computational efficient size.
+This operation is particularly useful for compressing the amount of data down to a more computational efficient size.
 
-Pooling layers are typically places after a layer or set of layers of convolution.
+Pooling layers are typically placed after a layer or set of layers of convolution.
 The purpose of this is arrangement is to reduce the width of the model at the pooling layer and ensure that only the dominant features with the largest activations are preserved \cite{Geron}.
@@
 For an array of activations , $x^{(l-1)} \in \mathbb{R}^{(m \times n)}$, a flattening layer $f^{(l)}$ transforms them such that $x^{(l)} \in \mathbb{R}^{(1 \times mn)}$.
+For example, for 2D input $x^{(l-1)}$, we would return a 1D output $x^{(l)}$:
+\begin{equation}
+\label{eqn:FlattenCall}
+\begin{bmatrix}
+a & b & c \\
+d & e & f \\
+\end{bmatrix}
+\rightarrow
+\begin{bmatrix}
+a & b & c & d & e & f 
+\end{bmatrix}
+\end{equation}
 This layer is also considered to be "non-trainable" because it does not use any adjustable parameters.
@@
 \item\textbf{Concatenation}
-
+The concatenation layer combines the activations of two similarly-dimensional arrays by concatenating them along a desired axis.
+In the layer graph shown in Eq.
+(\ref{eqn:LayerGraph}) this takes the place of layer $f_c^{\gamma}$.
+The output of the two previous layer chains are merged here before being fed to the output layer chain.
+This layer is what makes the aggregation of each subgraph possible and how we are able to generate one prediction from two input modalities.
+For inputs $x_a^{(l-1)}$ and $x_b^{(l-1)}$ this layer will return an output $x_c^{(l)}$:
+\begin{equation}
+\label{eqn:ConcatCall}
+\begin{bmatrix}
+a & b & c
+\end{bmatrix}
+\&
+\begin{bmatrix}
+d & e & f
+\end{bmatrix}
+\rightarrow
+\begin{bmatrix}
+a & b & c & d & e & f
+\end{bmatrix}
+\end{equation}
+This layer is also considered to be "non-trainable" because it does not use any adjustable parameters.
 \end{enumerate}
@@
 Formal implementations of the dense layer and 2D convoltional layer types introduce non-linearity into the hypothesis space by applying an \textit{activation} function to Eq.
-(\ref{eqn:DenseCall}) and Eq (\ref{eqn:Conv2DCall}) \cite{Goodfellow}.
+(\ref{eqn:DenseCall}) and Eq (\ref{eqn:Conv2DCall}) \cite{Goodfellow,Tensorflow}.
 For this classification network, we choose to use the \textit{ReLU} activation function, defined as:
@@
 \label{eqn:ReLU}
-ReLU \big[ x^{(l)} \big] = \text{max} \big( 0, x^{(l)} \big)
+ReLU \big[ x^{(l)} \big] = \text{max} \big( 0, x_i) \big)
 \end{equation} 
+for each element $x_i \in x^{(l)}$.
 Successive use of affine and convolutional transformations combine with non-linear activation functions allow a neural network to model the increasingly complicated decision-boundaries that arise in real-world problems \cite{Geron,Goodfellow}.

### 2021-12-02 JMMPaper/PaperDrafts/main.tex

@@
 
-\textcolor{red}{FINISH THIS!}
-
 % ================================================================
@@
 
-The architecture of the HNN enables us to perform classify the contents of digital audio files as musical instruments through \textit{multimodal} learning.
-The combined architecture, using Google's \textit{Tensorflow} library for Python allows the model to be trained conveniently as a single object \cite{Tensorflow}.
-This means that although the HNN is composed of two separate branches, all parameters and layers in the network are included with each back-propagation pass.
-This HNN contains 319,365 trainable parameters.
+The architecture of the HNN enables us to perform multimodal learning and classification of musical on digital audio samples.
+The multimodal nature comes from two distinct input layers that each accept information from a different representation of the same sample.
+These different modes of data are passed through a appropriate designed neural-network that learns a set of parameters to map that mode to an output.
+This combination of model and modes enables this neural network to learn a more robust set of parameters for clasification of unseen labels \cite{Li}.
+The combined architecture is implemented using Google's \textit{Tensorflow} library for Pytho and allows the model to be trained conveniently as a single neural network \cite{Tensorflow}.
+All parameters and layers in the network use the same optimizer, number of epochs, and objetive function.
+This HNN contains 319,365 trainable parameters stored a single precision floating-point numbers.
 
@@
 
-In the machine learning workflow, it is standard practice to divide a full data set into a \textit{training} subset and a \textit{testing} subset \cite{James,Virtanen}.
-The training subset is used to optimize the parameters, $\Theta$, in the model as to minimize the cost function, $J$, for the data set.
-The testing subset is used to evaluate how well the neural network performs on data that it has never interacted with \cite{Geron}.
-The training subset does contain corresponding labels, but they are withheld from the trained model such that it can make unbiased predictions.
-We can expand this idea to a common resampling method called \textit{K-Folds Cross Validation}, or X-validation for short \cite{James}.
-X-validation divides a data set into $K$ equally-sized folds.
-The first $K-1$ folds are used to train the model, and the last fold is used to evaluate how well the network performs on unseen samples.
-This process repeats of all $K$ folds, on $K$ unique models.
+In the \textit{end-to-end machine work flow} it is standard practice to divide a full data set into a \textit{training} subset and a \textit{testing} subset \cite{Geron,James,Virtanen}.
+The training subset is used to train the model by optimizing the parameters, $\Theta$, as to minimize the cost function, $J$, for that subset.
+The testing subset is used to evaluate and quantify how well optimization process performed by generating predictions on data that it has never interacted with \cite{Geron}.
+The training subset does contain corresponding labels but they are withheld from the trained model to make unbiased predictions, while used by the evaluation metrics to gauge performance.
+
+We expand this idea to a common resampling method called \textit{K-Folds Cross Validation}, or X-validation for short \cite{James}.
+X-validation divides a data set into $K$ equally-sized subsets, called folds.
+The first $K-1$ folds are used to train the model, and the last fold is used as the training set.
+This process repeats of all $K$ folds, using a freshly 'untrained' model each time, often with slightly different initial parameters as well.
 
 The result of X-validation is $K$ neural network models that have all been trained and evaluated on overlapping subsets of the full data set.
-Each model contains a collection of learned parameters, $\Theta$ that represent a possible outcome if trained on the given subset \cite{Geron,James}.
+Each model contains a different collection of learned parameters, $\Theta$ that represent a possible outcome if trained on the given subset \cite{Geron,James}.
 By repeating this and comparing the performance across each fold, we understand how the chosen architecture and hyper-parameters influence the stability of the performance of the network.
 
-Across each fold, we expect to observe a reasonably high, as well as consistent performance.
-A model that does not perform well on all of the splits indicates a poor choice or architecture or features, and a model that performs inconsistently across the splits indicates a model that suffers from high-variance, where small changes in initial conditions can drastically affect it's classification abilities \cite{James}.
-When we see consistent and strong performance across multiple splits, we develop confidence that we have a model that can train effectively, and generalize appropriately \cite{Geron}.
+Across each fold, we expect to observe a reasonably high, and consistent performance.
+A model that does not perform well on all of the splits indicates a poor choice or architecture or features, and a model that performs inconsistently across the splits indicates a model that suffers from high-variance, where small changes in initial conditions can drastically affect it's performance abilities \cite{James}.
+When consistent and strong performance across multiple splits is observed, we develop confidence that we have a model that can train effectively, and generalize appropriately \cite{Geron}.
 
@@
 While accuracy is convenient for quick estimates of performance, it does not provide much statistical information on the nature of choices made.
-This is especially true when classes have non-uniform representations in the data set.
+This is especially true when classes have non-uniform representations in the data set \cite{Geron}.
 The accuracy score of a classification algorithm is given by:
@@
 
-A confusion matrix is a square array that counts the number of times a sample was predicted to be in a given class.
+A confusion matrix is a square array that counts the number of times a sample from one class was predicted to be another class.
 For a $k$-categories classifier, the confusion matrix, $C$ has shape $k \times k$ where $C[i,j]$ is the number of times a sample known to be in class $i$ was predicted to be in class $j$ \cite{Geron}.
 A value added to the main-diagonal indicates a \textit{correct} classification, while a value on the off-diagonal indicates an \textit{incorrect} classification.
-We expect a well-performing classifier model to produce a diagonally-dominant confusion matrix.
+We expect a well-performing classifier model to produce a diagonally-dominant confusion matrix for it's testing set.
 
@@
 We have chosen to run a $K = 10$ fold cross validation program on our model, and compute the value of the each of the four metrics described in section (\ref{subsec:Metrics}).
-We have also run X-validation on two similar models that represent either mode of the network.
-The first variant uses just a 2D spectrogram input, fed through an identical CNN + MLP as shown on the left of Fig.
+We have also run X-validation on two similar models that represent either mode of the network in isolation.
+The first variant uses solely a 2D spectrogram input fed through an identical CNN + MLP as shown on the left of Fig.
 (\ref{fig:Architecture}).
 The activations are passed directly to the output layer where a prediction is made using this mode alone.
-Similarly, the second variant uses just a 1D feature-vector input, fed through an identical MLP as shown on the right side of Fig.(\ref{fig:Architecture}).
-The activations bypass the concatenation layer, and are passed directly to the output layer where a prediction is made using this mode alone.
-This allows us to produce an approximate comparison of how the HNN compares to the CNN or MLP models individually.
+Similarly, the second variant uses just a 1D feature-vector input fed through an identical MLP as shown on the right side of Fig.(\ref{fig:Architecture}).
+The activations also bypass the concatenation layer, and are passed directly to the output layer where a prediction is made using only this mode.
+This allows us to produce an approximate comparison of how the HNN compares to the CNN and MLP models individually.
 Cross validation was performed on each model using a different set of random splits from the same data set.
-The reported scores are averged over all samples in each training data subset.
+The reported scores are averaged over all samples in each training data subset.
 
@@
 This indicates that each input mode and complementary architecture allows for the optimization of a set of parameters to enable reasonable classification performance on unseen samples.
-Both models do exhibit fluctuation in the range of scores between each fold, which indicates that each model is vulnerable to small changes in initial conditions.
+Both models do exhibit fluctuation in the range of scores between each fold, which indicates that each could be vulnerable to small changes in initial conditions.
 
@@
 (\ref{fig:ConfScores}-b) we see a weaker diagonally dominant matrix for the MLP, which displayed even more misclassified samples, spread through the matrix.
-Note how each confusion matrix represents the average of $10$ confusion matrices produced from cross validation.
+Note that each confusion matrix represents the average of $10$ confusion matrices produced from cross validation.
 
@@
 (\ref{fig:ConfScores}-c).
-This matrix is the most-diagonally dominant, showing only a few commonly confused classes.
+This matrix appears to be the most-diagonally dominant, showing only a few commonly confused entries.
 The smaller number of mis-classifications in this model indicates a greater performance, and a generally stronger classifier.
@@
 
-\textcolor{red}{I'll need your help to introduce the chaotic Synth files, and address how they are generated, and why we use and "care" about them}
+\textcolor{red}{Should I Keep the details about the Chaotic Synths? It seem's out of place in the scheme of this paper.}
 
@@
 Multimodal learning itself shows great promise to machine learning algorithms in numerous domains.
-For data sets that lend themselves to multiple representations of a single sample, the ability to use those different modes allows for a more comprehensive representation of data.
-Across full data set, this will enable a model to generate a more stable set of parameters for classification which has the potential to yield better performance.
+For data sets that lend themselves to multiple representations of a single sample, the ability to leverage those different modes allows for a more comprehensive representation of data.
+Across full data set, this will enable a model to generate a more stable and substantial set of parameters for classification which has the potential to yield better performance.
 Multimodal learning does not limit itself to classification of digital audio, but instead opens the door to many genres of machine learning such a medicine, finance, and other media classification.
 
-The results of cross validation indicate that we have constructed a hybrid neural network that accept two input modes, and can effectivly classify the contents of a digital audio file as one of $37$ different musial instruments.
+The results of cross validation indicate that we have constructed a hybrid neural network that accept two input modes, and can effectively classify the contents of a digital audio file as one of $37$ different musical instruments.
 The design of this HNN enables the input of two non-compatible modal representations of a sample to be processed and combined to form a single output prediction.
@@
 
-\textcolor{red}{I sure cannot write a conclusion to save my life}
+\textcolor{red}{I sure cannot write a conclusion to save my life. Plz Halp.}
 
